### 2011-12-21 trunk/GUIErrorDetector/paper/abstract.tex
paper draft

\begin{abstract}
Graphical User Interface (GUI) is a critical component of today's software.
 It provides user-friendly access to the functionality provided by the application.
To keep GUIs responsive and active, a GUI application often spawns
 separate threads to handle lengthy operations in the background,
such as expensive computations, I/O tasks, and network requests.
However, many modern GUI frameworks require all GUI objects
must be accessed exclusively by the \textit{event dispatching thread}
(or called \textit{UI thread}). If a GUI object
is accessed through a non-UI thread, an \textit{invalid thread access} error
occurs and the whole application may abort consequently.

In this paper, we present a general technique to find such \textit{invalid thread access}
errors in multithreaded GUI applications. We formulate finding invalid
thread access errors as a call graph
reachability problem. Our technique starts from call graph entry nodes and statically explores
all possible paths that may cause a non-UI thread to access a GUI object.
However, the heavy use of reflection in modern GUI frameworks makes existing
call graph construction algorithms insufficent to build a both complete and precise
call graph. To overcome such limitations, we present a combined RTA and k-CFA
call graph analysis (that XXX). % to overcome such limitations.% of analyzing GUI applications.

We implemented our technique and instantiated it on four popular GUI
platforms, namely SWT, Eclipse plugin development framework, Java Swing, and Android. In an evaluation
on XX subjects over XXX LOC, our technique found a number of errors,
suggesting its effectiveness and showing good scalability.

\end{abstract}

### 2011-12-21 trunk/GUIErrorDetector/paper/conclusion.tex
paper draft

\section{Conclusion and Future Work}

In this paper, we presented a general technique to find invalid
thread access errors in multithreaded GUI applications. 
Our technique statically explores paths in a call graph to check
whether a non-UI thread can access any GUI object.
It uses a combined RTA and k-CFA algorithm to construct
a good call graph, and employs a set of heuristics to
filter likely false positives and redundant reports.
Since graphical user interfaces are often inadequately tested due
to the enormously large space of UI interactions and
extreme resource constraints during their development, we
believe that providing a static analysis can allow developers to find
more potential errors %before the application is released to customers (XXX),
and thus encourage GUI developers to improve software reliability.

We have demonstrated that our technique can be both practical and useful
by an evaluation on XXX subjects acrosss 4 popular GUI
frameworks. Our experiments have shown that we can find bugs
in real-world programs.

Besides general issues such as performance or ease of use, our future
work will concentrate on the following topics:

\begin{itemize}

\item \textbf{Integration with dynamic and symbolic analyses.} The technique 
presented in this paper is a pure static analysis. It
uses a combined RTA and k-CFA  algorithm to construct a relatively
complete and precise call graph. However, our technique still suffers from
a false positive rate for many GUI applications, due to the conservative
nature of static analysis. A possible way to reduce such false
positives is to integrate the current static analysis with
dynamic analyses~\cite{Jiang:2008:PPS:1453101.1453110, ZhangSBE2011}
or symbolic analyses~\cite{xie05:symstra, Pasareanu:2011, halfond09issta, BMF97}
by employing more accurate information to guide call graph exploration.

\item \textbf{Unit testing multithreaded GUI programs.} Besides
a static analysis,  software testing is another
way to improve software quality.  Although many
GUI testing techniques have been developed recently, few of them can be applied
to unit test multithreaded GUI programs to find potential errors \textit{earlier}. We
are interested to investigate how to apply recent advance in automated
software testing~\cite{Staats:2011:PTO:1985793.1985847, Jagannath:2011:IMU:2025113.2025145, Muccini_Bertolino_Inverardi_2004, Ricca:2001:ATW:381473.381476, Harman:2007}
to the context of multithreaded GUI applications.

\item \textbf{Fixing potential GUI errors.} After a potential error is revealed, fixing
it has often been another important and time-consuming process. Fixing concurrency
bugs has become especially critical in the multicore era.
Recently, a few work has been done
on automatically repairing test script for GUI applications~\cite{Daniel:2011:AGR:2002931.2002937, Huang:2010:RGT:1828417.1828465}. However, none of them focuses on reparing
the GUI program to fix a revealed bug. Thus, we are interested in further exploring 
along that line to investigate techniques to fix potential errors in
multithreaded GUI applications.

\end{itemize}

### 2011-12-21 trunk/GUIErrorDetector/paper/evaluation.tex
paper draft

\section{Empirical Evaluation}

Our experiment objective is three-fold: to demonstrate the effectiveness
of our approach in detecting real bugs in multithreaded GUI applications, to 
compare the combined RTA and k-CFA call graph construction algorithms
with existing ones , and to evaluate the usefulness of the proposed 
 heuristics. First, we describe our subject programs, our computing
environment and the experimental procedural. We then show that our technique
detects bugs in real-world GUI applications on
4 supported frameworks. We compare the combined RTA and k-CFA call graph
construction algorithms with existing algorithms, showing it improves
both precision and completeness of the constructed call graph.
 Finally, we show that the set of proposed heuristics are useful
in removing redundant warnings and eliminate false positivies.

\subsection{Subjects}

\begin{table}[t]
\begin{center}
 \fontsize{9pt}{\baselineskip}\selectfont
\hspace*{-0.2cm}
\begin{tabular}{|l||c|c|c|c|}
\hline
 Program (version) & LOC & Classes & Methods & Threads \\
\hline \hline
\multicolumn{5}{|l|}{SWT desktop applications}   \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx \\
 \hline
 \hline
\multicolumn{5}{|l|}{Eclipse plugins}   \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx \\
 \hline
 \hline
\multicolumn{5}{|l|}{Swing desktop applications}   \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx \\
 \hline
 \hline
\multicolumn{5}{|l|}{Android mobile applications}   \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx \\
\hline
\end{tabular}
\end{center}
\vspace{-15pt}
\Caption{{\label{table:subjects}Subject Programs.} }
\end{table}

\subsection{Procedural}

\subsection{Results}

\begin{table*}[t]
\begin{center}
 \fontsize{9pt}{\baselineskip}\selectfont
\hspace*{-0.2cm}
\begin{tabular}{|l||c|c|c||c|c|c||c|c|c|}
\hline
 Program  &  \multicolumn{3}{|c|}{RTA}& \multicolumn{3}{|c|}{0-CFA / Combined RTA and 0-CFA} & \multicolumn{3}{|c|}{1-CFA / Combined RTA and 1-CFA}  \\
\cline{2-10}
 (version) & CG Size & \#Warning & \#Bug & CG Size & \#Warning & \#Bug & CG Size & \#Warning & \#Bug\\
\hline \hline
\multicolumn{10}{|l|}{SWT desktop applications}   \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx \\
 \hline
 \hline
\multicolumn{10}{|l|}{Eclipse plugins}   \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx \\
 \hline
 \hline
\multicolumn{10}{|l|}{Swing desktop applications}   \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx \\
 \hline
 \hline
\multicolumn{10}{|l|}{Android mobile applications}   \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx \\
\hline
\end{tabular}
\end{center}
\vspace{-15pt}
\Caption{{\label{table:results}Experimental results.} }
\end{table*}

\subsubsection{Errors in Multithreaded GUI}

\subsubsection{Call Graph Construction Algorithms}

\subsubsection{Heuristic Filters}

Heuristic filter, effective.

\begin{table}[t]
\begin{center}
 \fontsize{9pt}{\baselineskip}\selectfont
\hspace*{-0.2cm}
\begin{tabular}{|l||c|c|c|c|}
\hline
 Program  & \#Warning & \#Warning & \#Warning & \#Warning \\
 (version) & $F_1$ & $F_2$ & $F_3$&$F_4$ \\
\hline \hline
\multicolumn{5}{|l|}{SWT desktop applications}   \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx \\
 \hline
 \hline
\multicolumn{5}{|l|}{Eclipse plugins}   \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx \\
 \hline
 \hline
\multicolumn{5}{|l|}{Swing desktop applications}   \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx \\
 \hline
 \hline
\multicolumn{5}{|l|}{Android mobile applications}   \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx \\
 \hline
 xxx &  xxxx &  xx &  xxx & xx \\
\hline
\end{tabular}
\end{center}
\vspace{-15pt}
\Caption{{\label{table:filters}Experimental results after applying heuristic filters.} }
\end{table}

\subsubsection{Performance and Scalability}

Runs in practical time, mention the largest time cost in the program.

The average analysis time per / bug

\subsection{Discussion}

\subsubsection{Threats to Validity}

### 2011-12-21 trunk/GUIErrorDetector/paper/implementation.tex
paper draft

\section{Implementation}

We implemented our technique using the WALA framework~\cite{walatutorial}.
Our prototype tool takes Java bytecode as inputs, works in a fully
automatic and push-button way to detect potential invalid thread access
errors, and scales to realistic programs.  
Optionally, the user may specify additional heuristics to guide call graph
traverse, and annotate calling relations for native methods (Section~\ref{}).

Our current implementation supports four widely-used GUI frameworks, namely
SWT, Eclipse plugin development environment, Java Swing, and Android.
Our implementation handles all of the Java language, and also takes
all dependent libraries (e.g., \CodeIn{rt.jar} and \CodeIn{android.jar})
into analysis. Since Android applications are often fully encrypted and shipped in Dalvik
bytecode as a single apk file, our implementation first uses
android-apktool\footnote{\url{http://code.google.com/p/android-apktool/}} to
decrypt the apk file, and then uses the 
ded translator~\cite{Enck:2011:SAA:2028067.2028088} to convert
Dalvik bytecode to Java bytecode before feeding to WALA.  The Android system
library (i.e., \CodeIn{android.jar}) uses many ``stub'' classes as
placeholder for the sake of efficiency. We manually re-compiled the whole
\CodeIn{android.jar} from its source code by replacing all ``stub'' classes
with real class files.

### 2011-12-21 trunk/GUIErrorDetector/paper/introduction.tex
paper draft

\section{Introduction}

Graphical User Interfaces (GUIs) are one of the most important parts of
software. Most software developed in recent years has a GUI, and the only
way for the end-user to interact with the software application is through
the GUI. Hence, end-user satisfaction and retention of a software application
 are largely determined by the usability and correctness of
its GUIs.

To make the GUIs more responsive and better utilize the increasingly available
computation power in the multi-core era, GUI applications often spawn separate
threads to handle time-consuming operations in the background, such as expensive
computations, I/O tasks, and network requests. Using threads for those lengthy tasks
makes a GUI active by allowing the timing of operations not delay unrelated parts of a 
GUI application.

\subsection{The Single-thread Rule}

Nowadays, many popular GUI frameworks such as Swing~\cite{swing}, SWT~\cite{swt}, Android~\cite{android},
Qt~\cite{qt}, MacOS Cocoa~\cite{macos}, and X Windows~\cite{xwindow} 
adapt the \textit{single-thread rule}:

\vspace{-2mm}

\begin{quote}
All GUI objects, including visual components and data models, must be
 accessed exclusively from the \textit{event dispatching thread}.
\end{quote}

\vspace{-2mm}

The \textit{event dispatching thread}, or called \textit{UI thread}, is a global special
thread initilized by the GUI framework, where all event-handling code
is executed. All code that interacts with GUI objects must also
execute on this thread.  There are several advantages to adapt the single-thread rule:

\begin{itemize}

\item GUI developers do not have to have an in-depth
unerstanding of concurrency programming. A GUI framework in which all components
must fully support multithreaded access can be difficult to extend, particularly
for developers who are not expert at threads programming.

\item Events are dispatched in a predictable order. Mouse and keyboard events, timer events, 
paint requests, and other user-defined events are dispatched from the same event queue.
In constrast, in a GUI framework without adapting the single-thread rule where components
support multithreaded access, any component changes can be interleaved with event
processing at the whim of the thread scheduler. This makes program behavior comprehension hard,
 and comprehensive testing difficult or impossible.

\item Single-thread rule incurs less overhead.
A GUI framework that attempts to carefully lock critical sections can spend a substantial
amount of time and space managing locks. Whenever the framework calls a method that might
be implemented in client code (for example, any public or protected method in a public class),
the framework must save its state and release all locks so that the client code can grab locks
if necessary. When GUI objects return from the method, the framework must regrab their locks and
restore states. Therefore, all applications using the framework will bear the cost of this, even though most
applications do not require concurrent access to the GUI.

\end{itemize}

%Single-threaded GUI frameworks are not unique to Java; ,
%and many others are also single-threaded.

\subsection{The Invalid Thread Access Error}

Despite the convenience that the single-thread rule brings to build a
GUI framework, it pushes the thread safety burden back onto the GUI application developers,
who must make sure all GUI objects are accessed by the UI thread.

In a multithreaded GUI application, the single-thread rule can be
easily violated since a spawned non-UI thread often needs to update
the GUI to display results after its computation task is finished.
An \textit{invalid thread access} error occurs when
a GUI object is accidentally accessed by a non-UI thread. In practice, such
invalid thread access error is \textit{frequent}, \textit{pervasive}, \textit{serverse}.
and \textit{difficult to avoid}.

Take the popular Standard Widget Toolkit (SWT)~\cite{swt} GUI framework as an example. 
In a recent survey~\footnote{\url{http://www.slideshare.net/lakshmip/top-3-swt-exceptions-3951224}}, the invalid thread access error
has been listed as the top 3 bugs in developing a SWT application. Searching
``SWTException:Invalid thread access'' in Google returns over 11,800 entries,
consisting of numerous bug reports, forum posts, and mailing list threads on
this problem. Eclipse~\cite{eclipse}, the de-facto standard IDE for Java development,
is built on top of SWT. As eclipse became open-sourced in 2001, the invalid thread access error has
been consistently reported during the past 11 years across different products, different components, and different releases.
Searching the same ``SWTException:Invalid thread access'' keyword in eclipse's bug repository
and discussion forum returns over 2732 bug reports and 351 distinct threads, respectively. 
We further manually studied all 156 \textit{confirmed} distinct bug reports, and 
found this error has been reported in at least 20 distinct eclipse projects
and 40 distinct eclipse components. Even after over 10-year's active development,
a recent release of eclipse still contains this error (bug id: 333533, reported in 01/2011).
 Furthermore, many reported invalid thread access errors are non-trivial. It is unintuitive
to fix them. Developers usually
need non-local reasoning to find the specific UI interactions that can trigger the bug; and
some reported bugs (e.g., bug id: 51757) even took developers 2 years to fix and verify the
patch. In addition, such invalid thread access error is UI-relevant and also user-perceivable;
it cannot be recovered by eclipse itself and often terminates the whole program.
In many circumstances (as described in the bug reports),
what users can only do is to restart the application to resort to an inconsistent status.

\begin{figure}[t]
\begin{CodeOut}
\begin{alltt}

     /* In class: org.mozilla.gecko.gfx.LayerView */
68.  public LayerView(Context context, LayerController controller) \{
69.     super(context);
        ....
73.     mRenderer = new LayerRenderer(this);
74.     setRenderer(mRenderer);
        ...
     \}

     /* In Android's lib class: android.opengl.GLSurfaceView */
272. public void setRenderer(Renderer renderer) \{
        ...
282.    mGLThread = new GLThread(renderer);
283.    mGLThread.start();   
     \}

     /* In class: org.mozilla.gecko.gfx.LayerRenderer */
220. public void onSurfaceChanged(GL10 gl, int width, int height) \{
221.    gl.glViewport(0, 0, width, height);
222.    mView.setViewportSize(new IntSize(width, height));
     \}

\end{alltt}
\end{CodeOut}
\vspace*{-2.0ex} \Caption{{\label{fig:androiderror} A real
bug reported in 11/17/2011 in Mozilla firefox release 10.0.a.rc3
for the Android platform (bugzilla ID: 703256). The \CodeIn{setRender}
method called inside \CodeIn{LayerView}'s constructor
spawns a new thread that violates the single-thread rule to inappropriately
access the GUI objects in line 222. Our tool
can find this bug and generate a warning as shown in
Figure~\ref{fig:report}.
}} %\vspace{-5mm}
\end{figure}

The invalid thread access error is not unique to the SWT framework. Other GUI frameworks
such as Android~\cite{android} also suffer from similar problems. For example, 
Figure~\ref{fig:androiderror} shows a recently reported bug on the Mozilla Firefox Android version.
In Figure~\ref{fig:androiderror}, \CodeIn{LayViewer}'s constructor calls the
\CodeIn{setRender} method (line 74), which spawns a new thread (line 283).
This newly created (non-UI) thread calls back the \CodeIn{onSurfaceChanged} method that
accesses the GUI objects at line 222, thus results in an invalid thread access error.
Compared to other reported errors, this bug is even more difficult to note, since the \CodeIn{setRender} method is in Android's
library whose source code is often not available to developers.

%It may work during development, but like most concurrent bugs, you'll start to see weird exceptions come up that seem completely unrelated, and occur non-deterministly - usually spotted AFTER you've shipped by real users. Not good.

%Also, you've got no confidence that your app will continue to work on future CPUs with more and more cores - which are more prone to encountering weird threading issues due to them being truely concurrent rather than just simulated by the OS.

\subsection{Finding Invalid Thread Access Errors}

The invalid thread access errors have significantly affect the
usability of GUIs, but have not been thoroughly studied in
the context of multithreaded GUI applications . To ensure GUIs
to behave correctly, effective
techniques must be devised to alleviate this problem.

%Effective techniques must be developed to
%find such errors.

Software testing, the most widely used method to ensure program correctness,
is often insufficient to detect such errors. That is because the space of possible interactions
with a GUI is enormous, in that each sequence of GUI events can result in
a difficult state, and each GUI event may need to be evaluated in all of
these states. It is almost impossible for testing to cover every possible
states in practice. In fact, for most reported bugs in eclipse, only very specific
UI interaction sequences can trigger the error. A large software system like eclipse
has a well-designed test suite that achieves failry high coverage; but many
 bug-triggering UI sequences are still not covered.

Program refactoring~\cite{Mens:2004}, another popular way to improve software quality,
is also inadaqute to eliminate this error.  A standard way to fix such
invalid thread access error is to replace direct GUI object accessing operations
with asynchronized message passing, to ensure GUI object are accessed in
the UI thread. For example, fixing the bug in Figure~\ref{fig:androiderror}
needs to wrap line 222 inside a \CodeIn{post} message passing method\footnote{The
\CodeIn{post} method is in class \CodeIn{android.widget.View}, providing
a standard utility to send messages to the UI-thread}, as follows:

\begin{CodeOut}
\begin{alltt}
     /* In class: org.mozilla.gecko.gfx.LayerRenderer */
220. public void onSurfaceChanged(GL10 gl, int width, int height) \{
221.     gl.glViewport(0, 0, width, height);
         \textbf{mView.post}(new Runnable() \{
             public void run() \{
222.             mView.setViewportSize(new IntSize(width, height));
             \}
         \});
     \}
\end{alltt}
\end{CodeOut}

One may wonder that a straightforward program transformation to wrap
every possible UI-accessing operation with asynchronized messsage passing
may solve this problem. However, such an approach is problematic,
because using asynchronized message passing has no timing
gurantee. It is entirely possible that, in some cases, a GUI object has already been
disposed before the message sent to arrives. Thus, programmers can not use
it everywhere; instead, they must choose carefully to put it in appropriate places
with extreme caution.

%Here are a few reasons, first, for the sake of efficiency, UI must use multi-thread to perform updates and processing user requests; second, there is no language level enforcement to prevent this error; and third, programmers often forget corner cases like an event listener that may init a non-UI thread to update a UI component.
%Furthermore, asyncExec has no timing guarantee, and programmers can not use it everywhere

In this paper, we choose to use static analysis to find such potential errors.
Static analysis has several advantages while comparing to dynamic approaches like testing for this problem.
First, a static analysis can explore every path of the program without executing the code, and
thus there is no need to construct non-trivial tests and harnesses.
Second, a static analysis can soundly find potentially errors: if it
reports no warnings, the code is guranteed to be bug-free.

\begin{figure}[t]
\begin{CodeOut}
\begin{alltt}

   org.mozilla.gecko.gfx.LayerView.<init>(Context;LayerController)
-> android.opengl.GLSurfaceView.setRenderer(GLSurfaceView\$Renderer;)
-> java.lang.Thread.start()
-> android.opengl.GLSurfaceView\$GLThread.run()
-> android.opengl.GLSurfaceView\$GLThread.guardedRun()
-> org.mozilla.gecko.gfx.LayerRenderer.onSurfaceChanged(GL10;II)
-> org.mozilla.gecko.gfx.LayerView.setViewportSize(IntSize;)
...
-> android.view.ViewRoot.checkThread()
\end{alltt}
\end{CodeOut}
\vspace*{-2.0ex} \Caption{{\label{fig:report} A report
generated by our tool to reveal the pontential bug in
Figure~\ref{fig:androiderror}. $\rightarrow$ represents the calling relations
between methods, and \CodeIn{checkThread} is an internal utility
method in Android's library that checks whether the current thread is the
event dispatching thread before accessing a GUI object.
}} %\vspace{-5mm}
\end{figure}

We formulate finding invalid thread access as a call graph reachability
problem. Our static analysis soundly constructs a call graph and starts
to traverse every possible paths from the entry points, checking whether
there exists a path to access a GUI object from a non-UI thread. If 
a suspicious path is found,
the static analysis issues a potential warning in the form of a method
call chain from the starting point, serving as the contextual information
for developers to understand the error.

As an example, Figure~\ref{fig:report} shows a report produced
by our static analysis for the buggy code in Figure~\ref{fig:androiderror}.
This report clearly indicates how a new, non-UI thread is spawned and
accesses GUI objects. 
The generated report is a great starting point for the developers, who can
inspect the method call chain, understand how the error
is triggered, and then determine if it is a real bug.

Our static analysis is independent of the call graph construction algorithms.
However, we find existing call graph construction algorithms~\cite{} are
insufficient to build a good call graph for GUI applications in the presence
of the heavy use of reflection. To alleviate this problem,
we present a combined RTA and k-CFA call graph analysis to balance the call
graph completeness and precision. (XXXX)

\subsection{Technique Instantiation and Evaluation}

(XXX)

We instantiate our technique on four popular GUI frameworks namely SWT,
eclipse plugin, Java Swing, and Android. Instantiating the general technique
for each framework only requires few human effort. The key issue to address
is to identify UI-thread

\subsection{Contributions}

This paper makes the following contributions:

\begin{itemize}
\item \textbf{Problem.} We explicitly identify the invalid thread
access error on multithreaded GUI programs, and formulate it
as a call graph reachability problem.

\item \textbf{Technique.} We present a general technique to find
such errors. In particular, to deal with the unique features in
multithreaded GUI programs, we propose a coombined RTA and k-CFA
call graph construction algorithm

\item \textbf{Implemetnation.} We instantiate our technique for four
popular GUI platforms: SWT, eclipse plugin, Swing, and Android. Our
tool implementation is publicly available at:
\url{http://guierrordetector.googlecode.com}

\item \textbf{Evaluation.} We performed an experiment on XXX subjects
from 4 different platforms over XXX LOC. As a result, our technique
found XXX bugs

\end{itemize}

### 2011-12-21 trunk/GUIErrorDetector/paper/related.tex
paper draft

\section{Related Work}

Work related to this paper falls into two main categories; (1)
techniques and tools to analyze and test GUI programs; and (2)
bug finding techniques for general multithreaded programs.

\subsection{Analysis and Testing for GUI Applications}

Automated GUI testing is a challenging tasks~\cite{Bertolino:2007:STR:1253532.1254712,
Harrold:2000:TR:336512.336532}.
 Many GUI analysis and testing techniques have been proposed in the past decade; some have been
implemented as tools and adopted by practitioners. Existing techniques automate
some aspect(s) of GUI testing including model creation
(for model-based testing)~\cite{androidtesting, Xie:2006:MTC:1172962.1172990},
test-case generation~\cite{YuanCohenMemonTSE2011, YuanMemonICSE2007},
test oracle creation~\cite{MemonFSE2000}, test execution~\cite{MemonFSE2001},
and test script repairing~\cite{Huang:2010:RGT:1828417.1828465, Daniel:2011:AGR:2002931.2002937}.
For example,
Kervinen et al.~\cite{Kervinen06model-basedtesting} present a formal model and architecture for testing
concurrently running applications. The behavior of the system under test
needs to be specified manually as a labeled transition system. 
Guitar~\cite{YuanCohenMemonTSE2011, YuanMemonICSE2007, Xie:2006:MTC:1172962.1172990}
is a GUI testing framework for Java and Microsoft Windows applications. 
Yuan and Memon~\cite{YuanMemonICSE2007} generate event-sequence based test cases for GUI
programs. They proposed a model-based approach for testing GUI-based applications.
Their technique can generate test cases automatically using a structural event
generation graph.

%Their approach targets Java desktop applications, which
%are quite different from the Android mobile environment (XXXX).

However, testing is often insufficient to ensure the correctness of a GUI program, for
a number of reasons. First of all, the space of possible interactions
with a GUI is enormous, in that each sequence of GUI
events can result in a different state, and each GUI event
may need to be evaluated in all of these states~\cite{YuanMemonICSE2007}.
The large number of possible states result in a large number of
test inputs requiring substantile human effort. The second
problem is to determine the coverage of a set of test
cases~\cite{MemonFSE2001}. For conventional software, coverage is measured
using the amount and type of underlying code exercised.
These measures do not work well for GUI testing, because
what matters is not only how much of the code is tested,
but in how many different possible states of the software
each piece of code is tested. This makes it hard to determine
the effectiveness of a test suite. %All of the (XXXXX, so that GUI is often not well tested)
In constrast, as advocated in this paper, the primary advantage of
using a static analysis is that it can potentially explore
all paths to find possible bugs without actually executing the tested code. % (XXX use heuristic filtering)
Compared with software testing, a static analysis tool may
report false positives due to its conservative nature. Netherless,
as we demonstrated in our experiments, using a few simple heuristics
can dramatically reduce the number of false positives  to
an acceptable level.

Michail and Xie~\cite{michail05:helping} proposed a tool-based approach to help users avoid bugs
in GUI applications. Their approach monitors user's action in the background,
and gives a user a warning as well as the opportunity to abort the action, when
a user attempts an action that has led to problems in the past. 
As a comparison, our work aims to find unknown errors in a multithreaded
GUI applications, while their work aims to prevent an existing bug
from happening again.
%is significantly different than their

Recently, Payet and Spoto~\cite{Payet:2011:SAA:2032266.2032299} presented a static
analysis framework for Android programs based on  abstract
interpretation. Their framework focuses on the Android platform, and
 consists of 7 existing static analyses such as
nullness analysis, class analysis, and termination analysis.  However,
their framework does not support detecting the invalid thread access
errors, and uses a quite different abstraction than ours.
To the best of our knowledge, we are the first to identify the invalid
thread access problem on multithreaded GUI applications, and
our technique is a general one that is specifically designed to detect
the invalid thread access errors.

%To the best of our knowledge, there is no prior work to tackle this invalid thread access problem
% on multithreaded GUI applications.

\subsection{Finding Bugs in Multithreaded Programs}

A rich body of techniques have been developed to detect bugs in multithreaded programs~\cite{Huang:2011:PPC:2001420.2001438, Weeratunge:2010, Huang:2011:EST}.
Active testing frameworks like AssertFuzzer~\cite{Sen:2008} uses the trace information to detect
and create atomicity schedule violations. Static analysis tools such as Chord~\cite{Naik:2006}
 explore multithreaded bugs by statically analyzing the program. On the
other hand, runtime analysis tools such as Eraser~\cite{Savage:1997}  dynamically detect concurrency bugs using the lockset
algorithms or some criteria based automata. Bodden and Havelund~\cite{Bodden:2008} uses AOP for
race detection by providing three novel pointcuts to the AspectJ language. More recently,
Goldilock~\cite{Elmas:2007} uses the hybrid model that combines the happens-before and lock-based
approaches to identify data races based on an execution. By exploiting the insight
that a full generality of the happens-before is unnecessary in most data accesses,
FastTrack~\cite{Flanagan:2009} proposes an adaptive representation for the happen-before
relation to efficiently and precisely detect races at runtime. However, finding
invalid thread errors is quite different than detecting data races in
a multithreaded program. A data race occurs when two concurrent threads access
a shared variable and when at least one access is a write and the threads
use no explicit mechanism to prevent the accesses from being simultaneous. In contrast,
an invalid thread access error occurs when a non-UI thread accesses (reads or writes) a GUI object.
Detecting invalid thread access error does not require monitoring every shared-memory
reference and verify that consistent locking behavior is observed among different threads. Instead,
our technique only needs to track whether a non-UI thread can reach a GUI object or not.
How to adapt existing data race detection technique to find potential
GUI errors is one of our future work.

%Significantly different from the concurrency bug finding work....

%They are often limited to detect errors manifested in a specific concrete execution.

An alternative way to find bugs in multithreaded programs is using model checking~\cite{Nori:2010:ESO, Inverardi:2000, Siegel:2008}.
By exhaustively exploring the thread scheduling space, a model checker can
report counter examples for the potential bugs with a counter example. For example,
CHESS~\cite{chess} dynamically explores the thread scheduling decisions to expose
concurrency bugs using a context-bounded approach. Shacham et al~\cite{Shacham:2007} uses
a model checker to construct the witness for data races reported by the lockset algorithm.
%(XXXX problem for applying to GUI).
Unfortunately, due to the exponential size of the search space,
 it is hard for model checking approaches to scale to a realistic multithreaded GUI application
 without compromising the detection capability. To our best knowledge,
we are not aware of any software model checking approach can scale to the subjects
as large as those used in our experiments. Compared with model checking, the static analysis
algorithm presented in this paper chooses call graph as the
abstraction level with a set of heuristics, and is much lightweighted. It is highly tailored to find the invalid thread
access errors instead of being a general property checking tool. For this reason,
our technique achieves good scalability and reasonable precision.

### 2011-12-21 GUIErrorDetector/paper/technique.tex
paper draft

\section{Technique}

\subsection{Problem Formulation}

formulate it as a graph reachability

\subsection{Error Detection Algorithm}

\begin{figure}[t]
\textbf{Input}: a Java program $P$\\
\textbf{Output}: a set of potential $errors$\\
\vspace{-5mm}
\begin{algorithmic}[1]
\STATE errors $\leftarrow$ $\emptyset$
\STATE cg $\leftarrow$ $constructCallGraph$($P$)
\STATE entryNodes $\leftarrow$ $getEntryNodes$(cg)
\STATE uiAccessNodes $\leftarrow$ $getUIAccessNodes$(cg)
\STATE safeNodes $\leftarrow$ $getSafeNodes$(cg)
\FOR{each entryNode in entryNodes}
\STATE threadStartNodes $\leftarrow$ $getReachableStartsByBFS$(cg)
\FOR{each threadStart in threadStartNodes}
\STATE queue $\leftarrow$ an empty queue
\STATE queue.enqueueAll(threadStart.$getAllSuccNodes$())
\WHILE{queue.isNotEmpty()}
\STATE nextNode $\leftarrow$ queue.dequeue()
\FOR{each succNode in cg.$getSuccNodes$(nextNode)}
\IF{succNode $\in$ uiAccessNodes}
\STATE errors $\leftarrow$ errors $\cup$ $createErrorReport$(succNode)
\ELSIF{succNode $\in$ safeNodes}
\STATE continue
\ELSE
\STATE queue.enqueue(succNode)
\ENDIF 
\ENDFOR
\ENDWHILE
\ENDFOR
\ENDFOR
\RETURN $errors$
%\ENDWHILE
\vspace{-2mm}
\end{algorithmic}
\caption{Algorithm for detecting errors in multithreaded GUI programs. 
Four utility methods in lines 2 -- 4 are customized for each GUI platforms
(not each program) as described in Section~\ref{sec:platforms}.
} \label{fig:detectalgorithm}
\end{figure}

\subsubsection{Call Graph Construction}

For desktop applications which have main method, it is straigtforward to apply
the above algorithm. However, for applications on platforms like eclipse plugin
and Android. presents new challenges. Two technical challenges must be solve.
First, use reflection extensively, Second, it is possible to interact with
native code.

Android features an extended event-based library and dynamic inflation of
graphical views from declarative XML layout files.
A static analyzer for Android programs must consider such features, for
correctness and precision.

\begin{figure}[t]
%\centering
\begin{CodeOut}
\begin{alltt}

<LinearLayout>
    <Button android:id="@+id/\textbf{button\_id}" android:text="A Button" />
</LinearLayout>

1. public class MyActivity extends Activity \{
2.    final List<View> cachedViews = new LinkedList<View>();
3.    @Override
4.    public void onCreate(Bundle savedInstanceState) \{
5.        super.onCreate(savedInstanceState);
6.        setContentView(R.layout.main);
7.        Button button = (Button) findViewById(R.id.\textbf{button\_id});
8.        button.setOnClickListener(new Button.OnClickListener() \{
9.            @Override
10.           public void onClick(View v) \{
11.               button.setText("Button Clicked.");
12.               cachedViews.add(v);
13.           \}
14.       \});
15.   \}
16. \}
\end{alltt}
\end{CodeOut}
\label{fig:sampleandroid}
\caption{A Sample Android Code ..}
\end{figure}

Give an example of how reflection affect call graph precision.

The Android button example.

Using RTA is not enough, since that maintains a global

So, we present a new call graph construction algorithm

reflected classes are known, use RTA.

reflection code

native code

\begin{figure}[t]
\textbf{Input}: a Java program $P$, a list of classes $cls$\\
\textbf{Output}: a call graph $cg$\\
\vspace{-5mm}
\begin{algorithmic}[1]
\STATE callSiteMap $\leftarrow$ new Map$\langle$CallSite, List$\langle$Type$\rangle$$\rangle$
\STATE rta\_cg $\leftarrow$ $constructCallGraphByRTA$($P$)
\FOR{each $method$ in $P$}
\FOR{each  $callSite$ in $method$}
\STATE type $\leftarrow$ $staticType$(callSite)
\IF{type $\in$ $cls$}
\FOR{each subType of $subType$(type)}
\IF{$hasObjectCreated$(subType, rta\_cg)}
\STATE callSiteMap[callSite].add(subType)
\ENDIF
\ENDFOR
\ENDIF
\ENDFOR
\ENDFOR
\STATE $cg$ $\leftarrow$ $constructCallGraphByKCFA$($P$, callSiteMap)
\RETURN $cg$
%\ENDWHILE
\vspace{-2mm}
\end{algorithmic}
\caption{Algorithm for constructing a call graph using a combination of the RTA~\cite{rta} and k-CFA~\cite{kcfa} algorithms.
$cls$ is a list of class XXXX, whose invocatioon is treated using RTA; while the remaining call graph
part is constructed using k-CFA.
} \label{fig:cgalgorithm}
\end{figure}

\subsubsection{Heuristic Filters and Annotations}
(XXX)

Static analysis exhaustively check possible error path; it may report
paths that indicate the same bug. The potentially huge volume of
reported warnings impose great burden for programmers to check
its validity.

a few useful static heuristic filtering rules.

\begin{itemize}
\item \textbf{Method call chain sumbsumption}. Remove redundant
results

\item \textbf{Remove system calls}. Method call chain involves typical
system methods like \CodeIn{toString} are unlikely to reveal a real bug.

\item \textbf{Method call chain with the same entry}. such
call chains may reveal the same bug

\item \textbf{Method call chain with the same tail}.  different ways
to reach the same bug

\item \textbf{User-defined rules}.  to overcome the limitation

\end{itemize}

The above filtering rules are not sound, it may filter real bugs but works
well in practice.

We also provide annotations for native methods which are beyond the ability
of most static analyses

\subsection{Instantiation for Different Frameworks}
\label{sec:platforms}

We instantiate our error detection techniques for 4 popular GUI frameworks,
namely SWT, Eclipse plugin environment, Swing, and Android.
For each GUI platform, we customize the \textit{call graph entry nodes},
\textit{UI accessing nodes}, and \textit{safe methods} on lines 3 -- 5 of the
algorithm in Figure~\ref{fig:detectalgorithm}.

%For the sake of efficiency, they are all using the single thread model.

%Why these platforms? popularity? account for xxx\% of the GUI.

%customizing for: entry points, starting points, error checking, thread
%safe methods, what is the event dispatching thread?

\subsubsection{SWT}

SWT is an open source widget toolkit for Java designed to provide efficient,
portable access to the GUI facilities of the operating systems on which it is implemented.

Like normal Java applications, a SWT desktop application starts from its main method.
By default, the thread that the main method executes is the UI thread. Thus, we instantiate
our technique as follows:

\begin{itemize}

\item \textbf{Call graph entry points: } the single main method

\item \textbf{UI accessing nodes: } any methods that calls \CodeIn{org.eclipse.swt.widgets.Display.checkWidget}
or \CodeIn{org.eclipse.swt.widgets.Display.checkDevice} methods, since these two methods are the
only place where the SWT framework checks whether the current thread is the UI thread or not. Thus, any
methods that calls the checking method must be invoked in the UI thread.

\item \textbf{Safe methods: } SWT provides two utility methods (\CodeIn{Display.asyncExec}
and \CodeIn{Display.syncExec}) that pass messages to the UI thread.
 Invoking these two methods are generally considered to be safe, and would not
cause an invalid thread access error.

\end{itemize}

\subsubsection{Eclipse plugin}

Unlike a SWT desktop application, an eclipse plugin, though is developed in SWT,
has no single main method. Instead, (XXX) it extends certain extension points
exposed by the eclipse framework, and eclipse will XXX. To instantiate our
technique for the Eclipse plugin environment, we need to redefine the
call graph entry points.

\begin{itemize}

\item \textbf{Call graph entry points: } all overriden methods of the classes inside
 a plugin's \CodeIn{ui} package.  Such methods are normally called by the eclipse framework
by the UI thread. XXX This rule, though quite heuristical, works quite well in practice.

\item \textbf{UI accessing nodes} and \textbf{Safe methods} are the same as SWT desktop applications.

\end{itemize}

\subsubsection{Swing}

%The collections classes from the original JDK (\CodeIn{Vector}
%and \CodeIn{Hashtable}) and the AWT library are designed as
%thread-safe. That is, two separate threads of execution can
%access the UI element at the same time without the developer having
%to worry about the threads interfering with one another. However, the
%safety comes at a cost. Because there is a great deal of overhead
%necessary to build thread-safe artifacts, the tend to be much slower
%than nonthread-safe alternatives.

%The design decisions for Swing changed. This does not mean the controls
%can never be accessed from multiple threads, but the developer is now
%responsible for adding code to ensure that no ill effects occur.

A Swing application often contains three kinds of threads: \textit{initial thread}
that executes initial application code, the \textit{event dispatch thread},
where all GUI manipulation code is executed, and the \textit{worker thread} where
time-consuming background tasks are executed. After Swing UIs are launched,
the initial thread exits and the event dispatch thread starts to execute all
event-handling code or spawns new worker threads. XXXX Therefore, we can not directly
use the main method as the call graph entry point, since it is not invoked
by the UI thread. We customize our technique for Swing as follows:

\begin{itemize}

\item \textbf{Call graph entry points: } all overriden callback methods of the listerner classes.
Specifically, for each class, we check whether it is a Swing listerner class. If so,
we extract all its overriden callback methods as the call graph entry points.
 %Such methods are normally called by the eclipse framework
%by the UI thread. XXX This rule, though quite heuristical, works quite well in practice.

\item \textbf{UI accessing nodes:} unlike SWT, Swing does not explicitly check
whether the current thread is the UI thread or not, when a GUI object is accessed. Except
for three documented thread-safe method (\CodeIn{repaint}, XXXX), our technique
treat all methods defined in each GUI object as UI accessing nodes.

\item \textbf{Safe methods: } similar to SWT, Swing provides two utility methods
(\CodeIn{SwingUtilities.invokeLater} and \CodeIn{SwingUtilities.invokeDelay}) to pass messages to the UI thread. These two methods are regarded as safe methods.

\end{itemize}

%A key tasks in instantiating
%our technique to the Swing framework is to identify its event dispatch thread.
%We use

\subsubsection{Android}

Android is a Java-based platform for embedded or mobile devices. 
Android features an extended event-based library and dynamic inflation of
graphical views from declarative XML layout files. Android applications are
written in Java, running in their own process within their own virtual machine.
Unlike desktop applications, they do not have a single entry point but can
rather use parts of other Android applications on-demand and can require their
services by calling corresponding event handlers, directly or through the
operating system. In particular, Android applications use \textit{activities}
as code interacting with the user through a visual interface. Event handlers
are scheduled in no particular ordering, with some notable exceptions such as the
lifecycle of activities.

An XML \textit{manifest file} registers the components of an application. Other XML
fies describe the visual layout of the activities. Activities \textit{inflate}
layout files into
visual objects (a hierarchy of views), through an \textit{inflater} provided by the An-
droid library. This means that library or user-defined views are not explicitly
created by new statements but rather inflated through \textit{reflection}. Library meth-
ods such as \CodeIn{findViewById} access the inflated views.

We instantiate the technique for Android programs as follows.

\begin{itemize}

\item \textbf{Call graph entry points: } all overriden callback methods of the event
listerner classes, and all overriden callback methods of an Activity.

\item \textbf{UI accessing nodes: } any methods that calls the \CodeIn{ViewRoot.checkThread}
method. This method is the only place where Android checks
whether the current thread is the UI thread or not. Thus, any
methods that calls the checking method must be invoked in the UI thread.

\item \textbf{Safe methods: } Android provides two utility methods (\CodeIn{View.post}
and \CodeIn{View.XXX}) that pass messages to the UI thread.
 Invoking these two methods are generally considered to be safe, and would not
cause an invalid thread access error.

\end{itemize}

### 2011-12-22 GUIErrorDetector/paper/abstract.tex
tweak

--- 2011-12-21 trunk/GUIErrorDetector/paper/abstract.tex
@@
 However, the heavy use of reflection in modern GUI frameworks makes existing
-call graph construction algorithms insufficent to build a both complete and precise
+call graph construction algorithms insufficient to build a both complete and precise
 call graph. To overcome such limitations, we present a combined RTA and k-CFA

### 2011-12-22 GUIErrorDetector/paper/introduction.tex
tweak

--- 2011-12-21 trunk/GUIErrorDetector/paper/introduction.tex
@@
 The \textit{event dispatching thread}, or called \textit{UI thread}, is a global special
-thread initilized by the GUI framework, where all event-handling code
+thread initialized by the GUI framework, where all event-handling code
 is executed. All code that interacts with GUI objects must also
@@
 \item GUI developers do not have to have an in-depth
-unerstanding of concurrency programming. A GUI framework in which all components
+understanding of concurrency programming. A GUI framework in which all components
 must fully support multithreaded access can be difficult to extend, particularly
@@
 paint requests, and other user-defined events are dispatched from the same event queue.
-In constrast, in a GUI framework without adapting the single-thread rule where components
+In contrast, in a GUI framework without adapting the single-thread rule where components
 support multithreaded access, any component changes can be interleaved with event
@@
 the framework must save its state and release all locks so that the client code can grab locks
-if necessary. When GUI objects return from the method, the framework must regrab their locks and
+if necessary. When GUI objects return from the method, the framework must re-grab their locks and
 restore states. Therefore, all applications using the framework will bear the cost of this, even though most
@@
 the GUI to display results after its computation task is finished.
-An \textit{invalid thread access} error occurs when
-a GUI object is accidentally accessed by a non-UI thread. In practice, such
-invalid thread access error is \textit{frequent}, \textit{pervasive}, \textit{serverse}.
+For example, a server program can get requests from other programs
+that might be running on different machines. These requests can come at any time,
+and they result in one of the server's methods being invoked in some thread.
+After handling the request, the GUI-update code must be executed on the UI-thread.
+If not, an \textit{invalid thread access} will error occur. In practice, such
+invalid thread access error is \textit{frequent}, \textit{pervasive}, \textit{severe}.
 and \textit{difficult to avoid}.
@@
 UI interaction sequences can trigger the error. A large software system like eclipse
-has a well-designed test suite that achieves failry high coverage; but many
+has a well-designed test suite that achieves fairly high coverage; but many
  bug-triggering UI sequences are still not covered.
@@
 Program refactoring~\cite{Mens:2004}, another popular way to improve software quality,
-is also inadaqute to eliminate this error.  A standard way to fix such
+is also inadequate to eliminate this error.  A standard way to fix such
 invalid thread access error is to replace direct GUI object accessing operations
@@
 One may wonder that a straightforward program transformation to wrap
-every possible UI-accessing operation with asynchronized messsage passing
+every possible UI-accessing operation with asynchronized message passing
 may solve this problem. However, such an approach is problematic,
 because using asynchronized message passing has no timing
-gurantee. It is entirely possible that, in some cases, a GUI object has already been
+guarantee. It is entirely possible that, in some cases, a GUI object has already been
 disposed before the message sent to arrives. Thus, programmers can not use
@@
 Second, a static analysis can soundly find potentially errors: if it
-reports no warnings, the code is guranteed to be bug-free.
+reports no warnings, the code is guaranteed to be bug-free.
 
@@
 such errors. In particular, to deal with the unique features in
-multithreaded GUI programs, we propose a coombined RTA and k-CFA
+multithreaded GUI programs, we propose a combined RTA and k-CFA
 call graph construction algorithm
 
-\item \textbf{Implemetnation.} We instantiate our technique for four
+\item \textbf{Implementation.} We instantiate our technique for four
 popular GUI platforms: SWT, eclipse plugin, Swing, and Android. Our

### 2011-12-22 GUIErrorDetector/paper/technique.tex
tweak

@@
 
-\subsection{Problem Formulation}
+We first gives our high-level approach formulation, then present
+an error detection algorithm. Finally, we show how to instantiate
+the error detection to different GUI frameworks.
 
-formulate it as a graph reachability
+\subsection{Approach Formulation}
+
+This section formulates our high-level approach. We define the
+notations of \textit{UI thread}, \textit{non-UI threads},
+\textit{UI accessing methods},
+ \textit{Safe methods}, and \textit{invalid thread access error}, and
+two assumptions we make with regard to error detection.
+
+\noindent {\textsc{\textbf{Definition 1 (UI Thread).}}} {UI thread
+is a special thread created by the GUI framework during
+GUI initialization. After the GUI becomes visible, the UI thread
+takes charge of the application, handle events from the GUIs,
+or spawn new threads to process lengthy operations in the background. }\vspace{1mm}
+
+\noindent {\textsc{\textbf{Assumption 1.}}} {We assume that each multithreaded
+GUI application has a single global UI thread. This is true for applications
+built on top of GUI frameworks that adapt the single-thread rule. It is
+possible that an application launches another application with its own UI thread
+by initializing a different process. In that case, we require the new
+launched application to be analyzed separately.}\vspace{1mm}
+
+\noindent {\textsc{\textbf{Definition 2 (non-UI Thread).}}} {Any other
+threads except for the UI thread is called non-UI threads.}\vspace{1mm}
+
+\noindent {\textsc{\textbf{Assumption 2.}}} { We assume that each non-UI
+thread can only be spawned by the UI thread. Under this assumption, all post-initialization
+GUI work naturally occurs in the UI-thread. Once the GUI is visible, the
+application is driven by events, which are always handled in the UI thread. We
+believe this assumption is reasonable, since if a non-UI
+thread is spawned during pre-initialization GUI work and that thread accesses
+a GUI object, an exception becomes apparent and the whole application may abort. This
+is unlikely for most of the realistic GUI applications.
+}\vspace{1mm}
+
+\noindent {\textsc{\textbf{Definition 3 (UI Accessing Methods).}}} { A method
+whose execution may read or write a UI object is called a UI Accessing Method.}\vspace{1mm}
+
+\noindent  {\textsc{\textbf{Definition 4 (Safe Methods).}}} {GUI frameworks that
+adapt the single-thread rule must provide methods to permit non-UI threads
+to run code in the UI thread. We can such methods \textit{safe methods}, since
+they can be invoked safely by any threads.}\vspace{1mm}
+
+\noindent  {\textsc{\textbf{Definition 5 (Invalid Thread Access).}}} {An invalid
+thread access error occurs if the UI thread spawns a non-UI thread, and there
+exists a path from the non-UI thread's \CodeIn{start} method to any UI accessing methods
+without going through any safe methods. }\vspace{2mm}
+
+At a high level, to detect an invalid thread access error, an analysis only needs to track all
+non-UI threads spawned by the UI thread, and check whether those non-UI threads
+may invoke a UI accessing method.
 
 \subsection{Error Detection Algorithm}
+
+We cast the problem of finding invalid thread
+
+Choose a right abstraction, why call graph is good?
+
+a call graph is a good approximation
+
+Given a sound call graph, our algorithm is sound in that it does not
+miss true positives. We note, however, that coomputing a sound
+call graph for partial programs such as an eclipse plugin,
+or in the presence of reflection, is non-trivial. Existing
+call graph construction algorithms either suffer from incompleteness
+or imprecision.  XX We describe our combined xxx in Section XXX.
+
+We also note that static analysis may report redundant
 

### 2011-12-22 trunk/GUIErrorDetector/paper/related.tex
tweak

@@
 generation graph. 
-
 %Their approach targets Java desktop applications, which
 %are quite different from the Android mobile environment (XXXX).
-
 However, testing is often insufficient to ensure the correctness of a GUI program, for
@@
 the effectiveness of a test suite. %All of the (XXXXX, so that GUI is often not well tested)
-In constrast, as advocated in this paper, the primary advantage of
+In contrast, as advocated in this paper, the primary advantage of
 using a static analysis is that it can potentially explore
@@
 algorithm presented in this paper chooses call graph as the
-abstraction level with a set of heuristics, and is much lightweighted. It is highly tailored to find the invalid thread
+abstraction level with a set of heuristics, and thus is much lightweighted. It is highly tailored to find the invalid thread
 access errors instead of being a general property checking tool. For this reason,
-our technique achieves good scalability and reasonable precision.
+our technique achieves good scalability with reasonable precision.

### 2011-12-25 trunk/GUIErrorDetector/paper/conclusion.tex
tweak
paper tweak

@@
 Our technique statically explores paths in a call graph to check
-whether a non-UI thread can access any GUI object.
+whether a non-UI thread can access a GUI object.
 It uses a combined RTA and k-CFA algorithm to construct
@@
 \item \textbf{Fixing potential GUI errors.} After a potential error is revealed, fixing
-it has often been another important and time-consuming process. Fixing concurrency
+it and verifing the patch has often been another important and time-consuming process. Fixing concurrency
 bugs has become especially critical in the multicore era.
 Recently, a few work has been done
-on automatically repairing test script for GUI applications~\cite{Daniel:2011:AGR:2002931.2002937, Huang:2010:RGT:1828417.1828465}. However, none of them focuses on reparing
-the GUI program to fix a revealed bug. Thus, we are interested in further exploring 
-along that line to investigate techniques to fix potential errors in
+on automatically repairing test script for GUI applications~\cite{Daniel:2011:AGR:2002931.2002937, Huang:2010:RGT:1828417.1828465}. However, none of them focuses on repairing
+the GUI program to fix a revealed bug. Thus, we are interested in 
+developing automated error fixing techniques for
 multithreaded GUI applications.

### 2011-12-25 trunk/GUIErrorDetector/paper/implementation.tex
paper tweak

@@
 \section{Implementation}
+\label{sec:implementation}
 
@@
 Optionally, the user may specify additional heuristics to guide call graph
-traverse, and annotate calling relations for native methods (Section~\ref{}).
+traverse, and annotate calling relations for native methods (Section~\ref{sec:heuristic}).
 

### 2011-12-25 trunk/GUIErrorDetector/paper/introduction.tex
paper tweak

@@
 software. Most software developed in recent years has a GUI, and the only
-way for the end-user to interact with the software application is through
+way for the most end-users to interact with the software application is through
 the GUI. Hence, end-user satisfaction and retention of a software application
@@
 The \textit{event dispatching thread}, or called \textit{UI thread}, is a global special
-thread initilized by the GUI framework, where all event-handling code
+thread initialized by the GUI framework, where all event-handling code
 is executed. All code that interacts with GUI objects must also
-execute on this thread.  There are several advantages to adapt the single-thread rule:
+execute on that thread.  There are several advantages to adapt the single-thread rule:
 
@@
 \item GUI developers do not have to have an in-depth
-unerstanding of concurrency programming. A GUI framework in which all components
-must fully support multithreaded access can be difficult to extend, particularly
+understanding of concurrency programming. A GUI framework in which all GUI objects
+fully support multithreaded access can be difficult to extend, particularly
 for developers who are not expert at threads programming.
 
-\item Events are dispatched in a predictable order. Mouse and keyboard events, timer events, 
-paint requests, and other user-defined events are dispatched from the same event queue.
-In constrast, in a GUI framework without adapting the single-thread rule where components
+\item GUI events are dispatched in a predictable order from the same event queue.
+In contrast, in a GUI framework without adapting the single-thread rule where GUI objects 
 support multithreaded access, any component changes can be interleaved with event
@@
 easily violated since a spawned non-UI thread often needs to update
-the GUI to display results after its computation task is finished.
-An \textit{invalid thread access} error occurs when
-a GUI object is accidentally accessed by a non-UI thread. In practice, such
-invalid thread access error is \textit{frequent}, \textit{pervasive}, \textit{serverse}.
+the GUI  after its  task is finished.
+For example, a server program can get requests from other programs
+that might be running on different machines. These requests can come at any time,
+and they result in one of the server's methods being invoked in some thread.
+After handling the request, the GUI-update code that displays the response must be executed on the UI-thread.
+If not, an \textit{invalid thread access} will error occur. In practice, such
+invalid thread access error is \textit{frequent}, \textit{pervasive}, \textit{severe}.
 and \textit{difficult to avoid}.
@@
 In a recent survey~\footnote{\url{http://www.slideshare.net/lakshmip/top-3-swt-exceptions-3951224}}, the invalid thread access error
-has been listed as the top 3 bugs in developing a SWT application. Searching
+has been listed as the top 3 bugs in developing a SWT application, and treated
+as the source of many relevant concurrency bugs. Searching
 ``SWTException:Invalid thread access'' in Google returns over 11,800 entries,
@@
 a recent release of eclipse still contains this error (bug id: 333533, reported in 01/2011).
- Furthermore, many reported invalid thread access errors are non-trivial. It is unintuitive
+ Furthermore, many reported  errors are non-trivial. It is unintuitive
 to fix them. Developers usually
 need non-local reasoning to find the specific UI interactions that can trigger the bug; and
-some reported bugs (e.g., bug id: 51757) even took developers 2 years to fix and verify the
+some reported errors (e.g., bug id: 51757) even took developers 2 years to fix it and verify the
 patch. In addition, such invalid thread access error is UI-relevant and also user-perceivable;
-it cannot be recovered by eclipse itself and often terminates the whole program.
-In many circumstances (as described in the bug reports),
+it cannot be recovered by the program itself and often terminates the whole application.
+In many circumstances as described in the bug reports,
 what users can only do is to restart the application to resort to an inconsistent status.
@@
 bug reported in 11/17/2011 in Mozilla firefox release 10.0.a.rc3
-for the Android platform (bugzilla ID: 703256). The \CodeIn{setRender}
-method called inside \CodeIn{LayerView}'s constructor
-spawns a new thread that violates the single-thread rule to inappropriately
-access the GUI objects in line 222. Our tool
-can find this bug and generate a warning as shown in
+for the Android platform (bugzilla ID: 703256). \CodeIn{LayerView}'s constructor
+calls method \CodeIn{setRender} that
+spawns a new thread at line 283. The new thread calls back method
+\CodeIn{onSurfaceChanged} that access GUI objects at line 222, and
+causes an invalid thread access error.
+Our tool
+can find this error and generate a warning as shown in
 Figure~\ref{fig:report}.
@@
 
-The invalid thread access error is not unique to the SWT framework. Other GUI frameworks
-such as Android~\cite{android} also suffer from similar problems. For example, 
+The invalid thread access error is not unique to the SWT framework. Other recent GUI frameworks
+like Android~\cite{android} also suffer from similar problems. For example, 
 Figure~\ref{fig:androiderror} shows a recently reported bug on the Mozilla Firefox Android version.
@@
 \CodeIn{setRender} method (line 74), which spawns a new thread (line 283).
-This newly created (non-UI) thread calls back the \CodeIn{onSurfaceChanged} method that
-accesses the GUI objects at line 222, thus results in an invalid thread access error.
-Compared to other reported errors, this bug is even more difficult to note, since the \CodeIn{setRender} method is in Android's
-library whose source code is often not available to developers.
+This newly created, non-UI thread calls back the \CodeIn{onSurfaceChanged} method that
+accesses the GUI objects at line 222, causing an invalid thread access error.
+Compared to other reported errors, this bug is even more difficult to note, 
+since the code that spawns a new thread inside the \CodeIn{setRender} method is
+in Android's library whose source code is often not available to developers.
 
@@
 to behave correctly, effective
-techniques must be devised to alleviate this problem.
+techniques must be developed to alleviate this problem.
 
@@
 Software testing, the most widely used method to ensure program correctness,
-is often insufficient to detect such errors. That is because the space of possible interactions
+is insufficient to detect such errors. That is because the space of possible interactions
 with a GUI is enormous, in that each sequence of GUI events can result in
@@
 these states. It is almost impossible for testing to cover every possible
-states in practice. In fact, for most reported bugs in eclipse, only very specific
-UI interaction sequences can trigger the error. A large software system like eclipse
-has a well-designed test suite that achieves failry high coverage; but many
+states. In fact, for a widely-used software system like eclipse
+often has a well-designed test suite that achieves fairly high coverage; but many
  bug-triggering UI sequences are still not covered.
@@
 Program refactoring~\cite{Mens:2004}, another popular way to improve software quality,
-is also inadaqute to eliminate this error.  A standard way to fix such
-invalid thread access error is to replace direct GUI object accessing operations
+is also inadequate to eliminate this error.  A standard way to fix such
+invalid thread access error is to replace direct GUI object accessing code 
 with asynchronized message passing, to ensure GUI object are accessed in
@@
 needs to wrap line 222 inside a \CodeIn{post} message passing method\footnote{The
-\CodeIn{post} method is in class \CodeIn{android.widget.View}, providing
-a standard utility to send messages to the UI-thread}, as follows:
+\CodeIn{post} method in class \CodeIn{android.widget.View} is a
+a standard way to send messages to the UI-thread}, as follows:
 
@@
 In this paper, we choose to use static analysis to find such potential errors.
-Static analysis has several advantages while comparing to dynamic approaches like testing for this problem.
+Static analysis has two attractive advantages while comparing to dynamic approaches such as
+ testing.
 First, a static analysis can explore every path of the program without executing the code, and
@@
 \vspace*{-2.0ex} \Caption{{\label{fig:report} A report
-generated by our tool to reveal the pontential bug in
-Figure~\ref{fig:androiderror}. $\rightarrow$ represents the calling relations
-between methods, and \CodeIn{checkThread} is an internal utility
-method in Android's library that checks whether the current thread is the
+generated by our tool to reveal the pontential error in
+Figure~\ref{fig:androiderror}. This report indicates a 
+full method call chain that causes the error. $\rightarrow$ represents
+the call relationship
+between methods, and \CodeIn{checkThread} is an Android library
+method  that checks whether the current thread is the
 event dispatching thread before accessing a GUI object.
@@
 We formulate finding invalid thread access as a call graph reachability
-problem. Our static analysis soundly constructs a call graph and starts
-to traverse every possible paths from the entry points, checking whether
+problem. Given a call graph, our technique traverses
+every possible paths from its entry nodes, checking whether
 there exists a path to access a GUI object from a non-UI thread. If 
@@
 for developers to understand the error.
-
 As an example, Figure~\ref{fig:report} shows a report produced
@@
 Our static analysis is independent of the call graph construction algorithms.
-However, we find existing call graph construction algorithms~\cite{} are
-insufficient to build a good call graph for GUI applications in the presence
-of the heavy use of reflection. To alleviate this problem,
-we present a combined RTA and k-CFA call graph analysis to balance the call
-graph completeness and precision. (XXXX)
+Given a sound call graph, our analysis is sound in that it does
+not miss true positives. We note, however, that computing a sound
+call graph for GUI applications in the presence of reflection,
+is non-trivial.
+Existing call graph construction algorithms such as RTA~\cite{} and k-CFA~\cite{}
+either suffer from the problem of imprecision or incompleteness .
+To alleviate this problem,
+we present a combined RTA and k-CFA call graph construction algorithm, and
+also compare its usefulness with other algorithms in  our experiments.
 
@@
 
-(XXX)
+We instantiate our technique for four popular GUI frameworks namely SWT,
+eclipse plugin environment, Java Swing, and Android. Swing and SWT are
+two dominating GUI frameworks in developing desktop Java applications.
+Eclipse and its plugin development envrionment is the de-facto standard
+IDE for Java. Android market share reaches 56\% in the mobile computing
+world as of Sep 2011, and becomes the No. 1 platform for mobile applications.
+Instantiating the general technique for each framework only requires few
+human effort. The primary framework-specific part is to specify
+the \textit{UI thread} and \textit{call graph entry nodes}.
 
-We instantiate our technique on four popular GUI frameworks namely SWT,
-eclipse plugin, Java Swing, and Android. Instantiating the general technique
-for each framework only requires few human effort. The key issue to address
-is to identify UI-thread
+We further implement a prototype tool that supports detecting invalid
+thread access errors in the above four GUI frameworks, and evaluate
+it on XXX subjects over XXX LOC. The experiment results demonstrate
+the effectiveness of the proposed technique. Our tool found XXX
+from XXX subjects on all supported GUI frameworks with an acceptable
+false positives.
 
@@
 \item \textbf{Problem.} We explicitly identify the invalid thread
-access error on multithreaded GUI programs, and formulate it
-as a call graph reachability problem.
+access error on multithreaded GUI programs.
+%, and formulate it
+%as a call graph reachability problem.
 
-\item \textbf{Technique.} We present a general technique to find
-such errors. In particular, to deal with the unique features in
-multithreaded GUI programs, we propose a coombined RTA and k-CFA
-call graph construction algorithm
+\item \textbf{Technique.} We formulate finding
+the invalid thread access error as a call graph reachability problem,
+and present a general technique to find such errors. 
+In particular, to deal with the unique features in
+multithreaded GUI programs, we propose a combined RTA and k-CFA
+call graph construction algorithm (Section~\ref{sec:technique}).
 
-\item \textbf{Implemetnation.} We instantiate our technique for four
-popular GUI platforms: SWT, eclipse plugin, Swing, and Android. Our
+\item \textbf{Implementation.} We implement our technique, and
+instantiate it for four
+popular GUI platforms: SWT, eclipse plugin, Swing, and Android (Section~\ref{sec:implementation}). Our
 tool implementation is publicly available at:
@@
 from 4 different platforms over XXX LOC. As a result, our technique
-found XXX bugs
+found XXX bugs (Section~\ref{sec:evaluation}).
 

### 2011-12-25 trunk/GUIErrorDetector/paper/related.tex
paper tweak

@@
 %are quite different from the Android mobile environment (XXXX).
-However, testing is often insufficient to ensure the correctness of a GUI program, for
-a number of reasons. First of all, the space of possible interactions
-with a GUI is enormous, in that each sequence of GUI
-events can result in a different state, and each GUI event
-may need to be evaluated in all of these states~\cite{YuanMemonICSE2007}.
-The large number of possible states result in a large number of
-test inputs requiring substantile human effort. The second
+However, testing is often insufficient to ensure the correctness of a GUI program
+due to the huge space of possible interactions
+with a GUI. The large number of possible interactions
+result in a large number of
+test inputs requiring substantile human effort.
+The second
 problem is to determine the coverage of a set of test
@@
 each piece of code is tested. This makes it hard to determine
-the effectiveness of a test suite. %All of the (XXXXX, so that GUI is often not well tested)
+the completeness of a test suite. %All of the (XXXXX, so that GUI is often not well tested)
 In contrast, as advocated in this paper, the primary advantage of
@@
 Compared with software testing, a static analysis tool may
-report false positives due to its conservative nature. Netherless,
-as we demonstrated in our experiments, using a few simple heuristics
+report false positives due to its conservative nature.
+Nevertheless, as we demonstrated in our experiments, using a few simple heuristics
 can dramatically reduce the number of false positives  to
@@
 an invalid thread access error occurs when a non-UI thread accesses (reads or writes) a GUI object.
-Detecting invalid thread access error does not require monitoring every shared-memory
+Unlike detecting potential data races, finding invalid thread access error does not require monitoring every shared-memory
 reference and verify that consistent locking behavior is observed among different threads. Instead,
 our technique only needs to track whether a non-UI thread can reach a GUI object or not.
-How to adapt existing data race detection technique to find potential
-GUI errors is one of our future work.
+How to adapt existing data race detection approaches to 
+improve our technique is one of our future work.
 

### 2011-12-25 trunk/GUIErrorDetector/paper/technique.tex
paper tweak

--- 2011-12-22 GUIErrorDetector/paper/technique.tex
@@
 \section{Technique}
+\label{sec:technique}
 
@@
 an error detection algorithm. Finally, we show how to instantiate
-the error detection to different GUI frameworks.
+the error algorithm to different GUI frameworks.
 
@@
 GUI initialization. After the GUI becomes visible, the UI thread
-takes charge of the application, handle events from the GUIs,
+takes charge of the application to handle events from the GUIs,
 or spawn new threads to process lengthy operations in the background. }\vspace{1mm}
@@
 GUI application has a single global UI thread. This is true for applications
-built on top of GUI frameworks that adapt the single-thread rule. It is
-possible that an application launches another application with its own UI thread
-by initializing a different process. In that case, we require the new
+built on top of GUI frameworks adapting the single-thread rule. The
+only exception is that 
+ an application may folk a new process to launch another
+application with its own UI thread. In that case, we require the new
 launched application to be analyzed separately.}\vspace{1mm}
@@
 \noindent {\textsc{\textbf{Definition 2 (non-UI Thread).}}} {Any other
-threads except for the UI thread is called non-UI threads.}\vspace{1mm}
+threads except for the UI thread in a multithreaded GUI application
+ are called non-UI threads.}\vspace{1mm}
 
 \noindent {\textsc{\textbf{Assumption 2.}}} { We assume that each non-UI
-thread can only be spawned by the UI thread. Under this assumption, all post-initialization
+thread can only be spawned by the UI thread. Under this assumption,
+ all post-initialization
 GUI work naturally occurs in the UI-thread. Once the GUI is visible, the
-application is driven by events, which are always handled in the UI thread. We
-believe this assumption is reasonable, since if a non-UI
-thread is spawned during pre-initialization GUI work and that thread accesses
-a GUI object, an exception becomes apparent and the whole application may abort. This
-is unlikely for most of the realistic GUI applications.
+application is driven by events, which are always handled in the UI thread.
+We can safely ignore non-UI threads that are spawned during pre-initilaizaiton
+GUI work, since if such threads access a GUI object, an exception becomes
+immediately apparent and the whole application may abort even before the
+GUI is visible. This is highly unlikely for most of the realistic GUI
+applications.
 }\vspace{1mm}
@@
 \noindent {\textsc{\textbf{Definition 3 (UI Accessing Methods).}}} { A method
-whose execution may read or write a UI object is called a UI Accessing Method.}\vspace{1mm}
+whose execution may read or write a UI object is called a UI accessing method.}\vspace{1mm}
 
@@
 \noindent  {\textsc{\textbf{Definition 5 (Invalid Thread Access).}}} {An invalid
-thread access error occurs if the UI thread spawns a non-UI thread, and there
+thread access error occurs when the UI thread spawns a non-UI thread, and there
 exists a path from the non-UI thread's \CodeIn{start} method to any UI accessing methods
@@
 
-We cast the problem of finding invalid thread
+The algorithm for detecting potential invalid thread access errors
+is shown in Figure~\ref{fig:detectalgorithm}. Our algorithm uses a
+static call graph as the program representation for a multithreaded
+GUI application. A Java call graph represents calling relationships
+between methods. Specially, each node represents a method and each
+edge ($f$, $g$) indicates that method $f$ may call method $g$.
+A theoretical ideal call graph can be defined as the union of the
+dynamic call graphs over all possible executions of the program. 
+A conservative static call graph is a superset of the ideal call graph;
+it over-approximates the
+dynamic call graph of every possible execution. 
+We believe call graph has a suitable granularity for this problem while
+Compared with other
+program representations like control flow graph or program dependence
+graph. That is because, in an object-oriented programming language like
+Java, a method is the basic unit of a program. Thus, reporting errors
+at the method level can be sufficient in most cases.
 
-Choose a right abstraction, why call graph is good?
+Our algorithm in Figure~\ref{fig:detectalgorithm} works as follows. It
+constructs a static call graph for the tested program (line 2),
+and specifies entry nodes for it. The algorithm starts to perform
+call graph traverse from every entry node (line 6). For every entry node,
+it first uses Breadth First Search (BFS) to find all reachable
+\CodeIn{Thread.start()} method (line 7). Each \CodeIn{Thread.start()} method
+indicates a new, non-UI thread is spawned.  Then, from each
+\CodeIn{Thread.start()} node, the algorithm uses a slightly modified 
+BFS algorithm to find reachable UI accessing methods (lines 9 -- 23).
+Specifially, it uses a queue to keep track of all visited nodes, and
+the algorithm checks every successive node to be visited;
+it reports an error if that node
+is a UI accessing method (line 15), or skips it if it is
+a safe method (line 17), or simply keeps traversing (line 19).
 
-a call graph is a good approximation
+If the algorithm determines that a UI accessing method may be invoked
+by a non-UI thread, it creates an error report containing the full
+method call chain from the entry node (line 15, the \CodeIn{createErrorReport}
+method). An example call chain for
+the motivating example in Figure~\ref{fig:androiderror} is shown
+in Figure~\ref{fig:report}.
 
 Given a sound call graph, our algorithm is sound in that it does not
-miss true positives. We note, however, that coomputing a sound
+miss true positives. We note, however, that computing a sound
 call graph for partial programs such as an eclipse plugin,
@@
 call graph construction algorithms either suffer from incompleteness
-or imprecision.  XX We describe our combined xxx in Section XXX.
+or imprecision. GUI applications built on some popular frameworks
+often use configuration files and reflection to specify GUI layout
+or extension points, therefore, reflection must be properly handled.
+We developed a combined RTA
+and k-CFA call graph construction algorithm in Section~\ref{sec:cg}
+to alleviate this problem.
 
-We also note that static analysis may report redundant
+We also note that static analysis may report false positives due
+to its conservative nature, and multiple warnings that acutally corrspond to
+the same error. In addition, some GUI applications may even use
+Java native methods to interact with the underlying operating system.
+Native methods are often beyond the ability of a static analysis, but
+must be considered to make the call graph sound. To address the
+above two limitations, we present a set of heuristics to filter
+highly likely false positives and remove redundant reports, and annotation
+support for programmers to specify call relationship for native methods.
 
@@
 \end{algorithmic}
-\caption{Algorithm for detecting errors in multithreaded GUI programs. 
-Four utility methods in lines 2 -- 4 are customized for each GUI platforms
-(not each program) as described in Section~\ref{sec:platforms}.
+\caption{Algorithm for detecting invalid thread access errors in multithreaded GUI programs. 
+Any call graph construction algorithm can be used (line 2).
+Three utility methods in lines 3 -- 5 are specific for each GUI framework
+ as described in Section~\ref{sec:platforms}.
 } \label{fig:detectalgorithm}
@@
 \subsubsection{Call Graph Construction}
-
-For desktop applications which have main method, it is straigtforward to apply
-the above algorithm. However, for applications on platforms like eclipse plugin
-and Android. presents new challenges. Two technical challenges must be solve.
-First, use reflection extensively, Second, it is possible to interact with
-native code.
-
-Android features an extended event-based library and dynamic inflation of
-graphical views from declarative XML layout files.
-A static analyzer for Android programs must consider such features, for
-correctness and precision.
+\label{sec:cg}
 
@@
 \label{fig:sampleandroid}
-\caption{A Sample Android Code ..}
+\caption{Sample GUI application code on the Android platform. The layout
+XML file (the top) specifies a Button object declaratively, 
+and the Java code (the bottom)
+first loads the XML file (line 6) and then uses reflection to create
+a Button object by its ID (line 7, the \CodeIn{findViewByd} method).}
 \end{figure}
+
+In the context of object-oriened languages wth dynamic dispatch, the
+crucial step in constructing a call graph is to compute a conservative
+approximation of the set of methods that can be invoked by a given
+virtual method call. Call graph construction algorithms have been
+studied intensively in the 1990s. While their original formulations
+use a variety of formalisms, most of them can be recast as set-based
+analyses. Various algorithms differ primarily in the number of sets
+that are used to approximate run-time values of expressions. 
+In practice, algorithms such as RTA that use a single set for the whole
+program scale well but achieves relatively lower precision. The
+k-CFA algorithms maintains one set per expression achieves better
+precision than RTA.
+
+Unfortunately, for GUI applications that use reflection, we found both
+RTA and k-CFA is insufficient to build a satisfactory call graph. Here
+is an example in Figure~\ref{fig:sampleandroid} to illustrate their limitations.
+
+(XXX)
+
+For desktop applications which have main method, it is straigtforward to apply
+the above algorithm. However, for applications on platforms like eclipse plugin
+and Android. presents new challenges. Two technical challenges must be solve.
+First, use reflection extensively, Second, it is possible to interact with
+native code.
+
+Android features an extended event-based library and dynamic inflation of
+graphical views from declarative XML layout files.
+A static analyzer for Android programs must consider such features, for
+correctness and precision.
 
@@
 \end{algorithmic}
-\caption{Algorithm for constructing a call graph using a combination of the RTA~\cite{rta} and k-CFA~\cite{kcfa} algorithms.
-$cls$ is a list of class XXXX, whose invocatioon is treated using RTA; while the remaining call graph
-part is constructed using k-CFA.
+\caption{A combined  RTA~\cite{rta} and k-CFA~\cite{kcfa} call graph construction algorithm.
+$cls$ is a list of classes whose method invocations are added to the
+call graph using the RTA algorithm; while method invocations from other classes
+are added to the call graph using the k-CFA algorithm.
 } \label{fig:cgalgorithm}
@@
 \subsubsection{Heuristic Filters and Annotations}
-(XXX)
+\label{sec:heuristic}
 

### 2011-12-25 GUIErrorDetector/paper/abstract.tex
paper tweak

@@
 thread access errors as a call graph
-reachability problem. Our technique starts from call graph entry nodes and statically explores
-all possible paths that may cause a non-UI thread to access a GUI object.
+reachability problem. Our technique starts from call graph entry nodes to
+statically explore all possible paths that may cause a non-UI thread
+to access a GUI object.
 However, the heavy use of reflection in modern GUI frameworks makes existing
 call graph construction algorithms insufficient to build a both complete and precise
-call graph. To overcome such limitations, we present a combined RTA and k-CFA
-call graph analysis (that XXX). % to overcome such limitations.% of analyzing GUI applications.
+call graph. Thus, we present a combined RTA and k-CFA
+call graph construction algorithm to overcome the limitations.% of analyzing GUI applications.
 

### 2011-12-31 GUIErrorDetector/paper/implementation.tex
tweak

--- 2011-12-25 trunk/GUIErrorDetector/paper/implementation.tex
@@
 
-We implemented our technique using the WALA framework~\cite{walatutorial}.
+We implemented the proposed technique using the WALA framework~\cite{walatutorial}.
 Our prototype tool takes Java bytecode as inputs, works in a fully
@@
 Optionally, the user may specify additional heuristics to guide call graph
-traverse, and annotate calling relations for native methods (Section~\ref{sec:heuristic}).
+traverse, and annotate call relationships for native methods (Section~\ref{sec:heuristic}).
 

### 2011-12-31 GUIErrorDetector/paper/introduction.tex
tweak

@@
 
-Nowadays, many popular GUI frameworks such as Swing~\cite{swing}, SWT~\cite{swt}, Android~\cite{android},
-Qt~\cite{qt}, MacOS Cocoa~\cite{macos}, and X Windows~\cite{xwindow} 
+Nowadays, many popular GUI frameworks such as Swing\footnote{\url{http://docs.oracle.com/javase/6/swing/}},
+SWT\footnote{\url{http://eclipse.org/swt/}}, Android\footnote{\url{http://www.android.com/}},
+Qt\footnote{\url{http://qt.nokia.com/products/}}, MacOS Cocoa\footnote{\url{http://developer.apple.com/cocoa.html}},
+and X Windows\footnote{\url{http://www.x.org/}}
 adapt the \textit{single-thread rule}:
@@
 is executed. All code that interacts with GUI objects must also
-execute on this thread.  There are several advantages to adapt the single-thread rule:
+execute on that thread.  There are several advantages to adapt the single-thread rule:
 
@@
 \item GUI developers do not have to have an in-depth
-understanding of concurrency programming. A GUI framework in which all components
-must fully support multithreaded access can be difficult to extend, particularly
+understanding of concurrency programming. A GUI framework in which all GUI objects
+fully support multithreaded access can be difficult to extend, particularly
 for developers who are not expert at threads programming.
 
-\item Events are dispatched in a predictable order. Mouse and keyboard events, timer events, 
-paint requests, and other user-defined events are dispatched from the same event queue.
-In contrast, in a GUI framework without adapting the single-thread rule where components
+\item GUI events are dispatched in a predictable order from the same event queue.
+In contrast, in a GUI framework without adapting the single-thread rule where GUI objects 
 support multithreaded access, any component changes can be interleaved with event
@@
 easily violated since a spawned non-UI thread often needs to update
-the GUI to display results after its computation task is finished.
+the GUI  after its  task is finished.
 For example, a server program can get requests from other programs
@@
 and they result in one of the server's methods being invoked in some thread.
-After handling the request, the GUI-update code must be executed on the UI-thread.
-If not, an \textit{invalid thread access} will error occur. In practice, such
-invalid thread access error is \textit{frequent}, \textit{pervasive}, \textit{severe}.
-and \textit{difficult to avoid}.
+After handling the request, the GUI-update code that displays the response must be executed on the UI-thread.
+If not, an \textit{invalid thread access error} will occur. In practice, such
+invalid thread access error is \textit{frequent}, \textit{pervasive}, and \textit{severe}.
+%and \textit{difficult to avoid}.
 
-Take the popular Standard Widget Toolkit (SWT)~\cite{swt} GUI framework as an example. 
+Take the popular Standard Widget Toolkit (SWT) GUI framework as an example. 
 In a recent survey~\footnote{\url{http://www.slideshare.net/lakshmip/top-3-swt-exceptions-3951224}}, the invalid thread access error
-has been listed as the top 3 bugs in developing a SWT application. Searching
+has been listed as the top 3 bugs in developing a SWT application, and treated
+as the source of many relevant concurrency bugs. Searching
 ``SWTException:Invalid thread access'' in Google returns over 11,800 entries,
 consisting of numerous bug reports, forum posts, and mailing list threads on
-this problem. Eclipse~\cite{eclipse}, the de-facto standard IDE for Java development,
+this problem. Eclipse, the de-facto standard IDE for Java development,
 is built on top of SWT. As eclipse became open-sourced in 2001, the invalid thread access error has
@@
 and discussion forum returns over 2732 bug reports and 351 distinct threads, respectively. 
-We further manually studied all 156 \textit{confirmed} distinct bug reports, and 
+We manually studied all 156 \textit{confirmed} distinct bug reports, and 
 found this error has been reported in at least 20 distinct eclipse projects
@@
 a recent release of eclipse still contains this error (bug id: 333533, reported in 01/2011).
- Furthermore, many reported invalid thread access errors are non-trivial. It is unintuitive
+ Furthermore, many reported  errors are non-trivial, and it is unintuitive
 to fix them. Developers usually
 need non-local reasoning to find the specific UI interactions that can trigger the bug; and
-some reported bugs (e.g., bug id: 51757) even took developers 2 years to fix and verify the
-patch. In addition, such invalid thread access error is UI-relevant and also user-perceivable;
-it cannot be recovered by eclipse itself and often terminates the whole program.
-In many circumstances (as described in the bug reports),
+some reported errors (e.g., bug id: 51757) even took developers 2 years to fix it and verify the
+patch. In addition, such invalid thread access error is UI-relevant and user-perceivable;
+it cannot be recovered by the program itself and often terminates the whole application.
+In many circumstances as described in the bug reports,
 what users can only do is to restart the application to resort to an inconsistent status.
@@
 
-The invalid thread access error is not unique to the SWT framework. Other GUI frameworks
-such as Android~\cite{android} also suffer from similar problems. For example, 
+The invalid thread access error is not unique to the SWT framework. Other recent GUI frameworks
+like Android also suffer from similar problems. For example, 
 Figure~\ref{fig:androiderror} shows a recently reported bug on the Mozilla Firefox Android version.
@@
 these states. It is almost impossible for testing to cover every possible
-states in practice. In fact, for most reported bugs in eclipse, only very specific
-UI interaction sequences can trigger the error. A large software system like eclipse
-has a well-designed test suite that achieves fairly high coverage; but many
+states. In fact, a widely-used software system like eclipse
+often has a well-designed test suite that achieves fairly high coverage; but many
  bug-triggering UI sequences are still not covered.
@@
 Program refactoring~\cite{Mens:2004}, another popular way to improve software quality,
-is also inadequate to eliminate this error.  A standard way to fix such
-invalid thread access error is to replace direct GUI object accessing operations
-with asynchronized message passing, to ensure GUI object are accessed in
+is also inadequate to eliminate this error.  A standard way to fix an
+invalid thread access error is to replace direct GUI object accessing code 
+with asynchronized message passing, to ensure a GUI object are accessed in
 the UI thread. For example, fixing the bug in Figure~\ref{fig:androiderror}
 needs to wrap line 222 inside a \CodeIn{post} message passing method\footnote{The
-\CodeIn{post} method is in class \CodeIn{android.widget.View}, providing
-a standard utility to send messages to the UI-thread}, as follows:
+\CodeIn{post} method in class \CodeIn{android.widget.View} is a
+a standard way to send messages to the UI-thread}, as follows:
 
@@
 guarantee. It is entirely possible that, in some cases, a GUI object has already been
-disposed before the message sent to arrives. Thus, programmers can not use
+disposed before the message sent to arrives, causing other bugs. Thus, programmers can not use
 it everywhere; instead, they must choose carefully to put it in appropriate places
@@
 
-In this paper, we choose to use static analysis to find such potential errors.
-Static analysis has several advantages while comparing to dynamic approaches like testing for this problem.
+Another approach, as we follow in this paper, is to
+use static analysis to find such potential errors.
+Static analysis has two attractive advantages while comparing to dynamic approaches such as
+ testing.
 First, a static analysis can explore every path of the program without executing the code, and
@@
 
-We formulate finding invalid thread access as a call graph reachability
-problem. Our static analysis soundly constructs a call graph and starts
-to traverse every possible paths from the entry points, checking whether
+In our static analysis, we formulate finding invalid thread access as a call graph reachability
+problem. Given a call graph, our technique traverses
+every possible paths from its entry nodes, checking whether
 there exists a path to access a GUI object from a non-UI thread. If 
@@
 Our static analysis is independent of the call graph construction algorithms.
-However, we find existing call graph construction algorithms~\cite{} are
-insufficient to build a good call graph for GUI applications in the presence
-of the heavy use of reflection. To alleviate this problem,
-we present a combined RTA and k-CFA call graph analysis to balance the call
-graph completeness and precision. (XXXX)
+Given a sound call graph, our analysis is sound in that it does
+not miss true positives. We note, however, that computing a sound
+call graph for GUI applications in the presence of reflection,
+is non-trivial.
+Existing call graph construction algorithms such as RTA~\cite{} and k-CFA~\cite{}
+either suffer from the problem of imprecision or incompleteness .
+To alleviate this problem,
+we present a combined RTA and k-CFA call graph construction algorithm, and
+also compare its usefulness with other algorithms in  our experiments. We
+also note that static analysis may report false positives due to its
+conservative nature, or multiple warnings that actually correspond
+to the same error. To alleviate such limitations, we devise a set
+ of heuristics to filter likely false positives and redundant warnings.
 
@@
 
-(XXX)
+We instantiate our technique for four GUI frameworks namely SWT,
+eclipse plugin environment, Java Swing, and Android. 
+The reason of choosing these four GUI frameworks is because of
+their popularity. Swing and SWT are unquestionably (XXX)
+two dominating GUI frameworks in developing desktop Java applications.
+Eclipse with its plugin development envrionment is the de-facto standard
+IDE for Java. Android becomes the No. 1 platform for
+developing mobile applications with market share 56\% as of Sep 2011.
+Although our technique is generally applicable for GUI
+frameworks adapting the single-thread rule, a specific framework
+may have its own treatment of \textit{UI thread} and \textit{call graph
+entry nodes}. Thus, we must explicitly identify those framework-specific
+parts in our prototype tool implementation.
 
-We instantiate our technique on four popular GUI frameworks namely SWT,
-eclipse plugin, Java Swing, and Android. Instantiating the general technique
-for each framework only requires few human effort. The key issue to address
-is to identify UI-thread
+%Applications built on top of different GUI frameworks have different
+%treatment of \textit{UI thread} and \textit{call graph entry nodes}.
+%Instantiating the general technique for each framework only requires few
+%human effort. The primary framework-specific part is to specify
+%the \textit{UI thread} and \textit{call graph entry nodes}.
+
+We implement an invalid thread error detection tool that supports
+the above four GUI frameworks. Our tool works in a fully-automatic,
+push-button manner, and scales to realistic programs.
+We evaluate our implementation on XXX subjects from four different
+frameworks over XXX LOC. The experiment results demonstrate
+that: our technique is effective (it found XXX real-world errors
+on all supported frameworks); our combined RTA and k-CFA call
+graph construction algorithm is useful (XXX it improves both completeness
+and precision over the existing algorithms), and our proposed
+heuristics are useful (it signficantly reduces the number of
+false positives and redundant warnings).
 
@@
 \item \textbf{Problem.} We explicitly identify the invalid thread
-access error on multithreaded GUI programs, and formulate it
-as a call graph reachability problem.
+access error on multithreaded GUI programs.
+%, and formulate it
+%as a call graph reachability problem.
 
-\item \textbf{Technique.} We present a general technique to find
-such errors. In particular, to deal with the unique features in
+\item \textbf{Technique.} We formulate finding
+the invalid thread access error as a call graph reachability problem,
+and present a general error detection technique.
+In particular, to deal with the unique features in
 multithreaded GUI programs, we propose a combined RTA and k-CFA
-call graph construction algorithm
+call graph construction algorithm (Section~\ref{sec:technique}).
 
-\item \textbf{Implementation.} We instantiate our technique for four
-popular GUI platforms: SWT, eclipse plugin, Swing, and Android. Our
+\item \textbf{Implementation.} We implement our technique, and
+instantiate it for four
+popular GUI platforms: SWT, eclipse plugin, Swing, and Android (Section~\ref{sec:implementation}). Our
 tool implementation is publicly available at:
@@
 \item \textbf{Evaluation.} We performed an experiment on XXX subjects
-from 4 different platforms over XXX LOC. As a result, our technique
-found XXX bugs
+from 4 different platforms over XXX LOC to show the usefulness
+of the proposed techinque (Section~\ref{sec:evaluation}).
 

### 2011-12-31 trunk/GUIErrorDetector/paper/abstract.tex
tweak

@@
 thread access errors as a call graph
-reachability problem. Our technique starts from call graph entry nodes and statically explores
-all possible paths that may cause a non-UI thread to access a GUI object.
-However, the heavy use of reflection in modern GUI frameworks makes existing
-call graph construction algorithms insufficent to build a both complete and precise
-call graph. To overcome such limitations, we present a combined RTA and k-CFA
-call graph analysis (that XXX). % to overcome such limitations.% of analyzing GUI applications.
+reachability problem. Our technique starts from call graph entry nodes to
+statically explore all possible paths that may cause a non-UI thread
+to access a GUI object.
+However, the heavy use of reflection in modern GUI applications makes existing
+call graph construction algorithms insufficient to build a both complete and precise
+call graph. Thus, we present a combined RTA and k-CFA
+call graph construction algorithm to overcome the limitations.% of analyzing GUI applications.
 
@@
 platforms, namely SWT, Eclipse plugin development framework, Java Swing, and Android. In an evaluation
-on XX subjects over XXX LOC, our technique found a number of errors,
+on XX subjects over XXX LOC, our technique found a number of real-world errors,
 suggesting its effectiveness and showing good scalability.

### 2011-12-31 trunk/GUIErrorDetector/paper/technique.tex
tweak

@@
 
-At a high level, to detect an invalid thread access error, an analysis only needs to track all
+At a high level, to detect an invalid thread access error, an analysis needs to track all
 non-UI threads spawned by the UI thread, and check whether those non-UI threads
@@
 dynamic call graphs over all possible executions of the program. 
-A conservative static call graph is a superset of the ideal call graph;
-it over-approximates the
+A conservative static call graph used in practice is a superset of
+the ideal call graph; it over-approximates the
 dynamic call graph of every possible execution. 
-We believe call graph has a suitable granularity for this problem while
-Compared with other
+In an object-oriented programming language like
+Java, a method is the basic logic unit in a program. Reporting
+potential errors at the method level can be sufficient in most cases.
+Thus, we believe using call graph is well suited for this problem while
+compared with other
 program representations like control flow graph or program dependence
-graph. That is because, in an object-oriented programming language like
-Java, a method is the basic unit of a program. Thus, reporting errors
-at the method level can be sufficient in most cases.
+graph.
 
 Our algorithm in Figure~\ref{fig:detectalgorithm} works as follows. It
-constructs a static call graph for the tested program (line 2),
-and specifies entry nodes for it. The algorithm starts to perform
-call graph traverse from every entry node (line 6). For every entry node,
+first constructs a static call graph for the tested program (line 2),
+then specifies entry nodes for it (line 3). The algorithm starts to traverse
+the call graph from every entry node (line 6). For every entry node,
 it first uses Breadth First Search (BFS) to find all reachable
 \CodeIn{Thread.start()} method (line 7). Each \CodeIn{Thread.start()} method
-indicates a new, non-UI thread is spawned.  Then, from each
-\CodeIn{Thread.start()} node, the algorithm uses a slightly modified 
-BFS algorithm to find reachable UI accessing methods (lines 9 -- 23).
+indicates that a new, non-UI thread is spawned.  After that, 
+the algorithm uses a slightly modified 
+BFS algorithm to find reachable UI accessing methods (lines 9 -- 23)
+from each \CodeIn{Thread.start()} node.
 Specifially, it uses a queue to keep track of all visited nodes, and
-the algorithm checks every successive node to be visited;
+then checks every successive node to be visited (line 12);
 it reports an error if that node
 is a UI accessing method (line 15), or skips it if it is
-a safe method (line 17), or simply keeps traversing (line 19).
+a safe method (line 17), or simply keeps traversing otherwise (line 19).
 
@@
 call graph for partial programs such as an eclipse plugin,
-or in the presence of reflection, is non-trivial. Existing
-call graph construction algorithms either suffer from incompleteness
-or imprecision. GUI applications built on some popular frameworks
+or in the presence of reflection, is non-trivial. 
+In particular, GUI applications built on some popular frameworks
 often use configuration files and reflection to specify GUI layout
-or extension points, therefore, reflection must be properly handled.
-We developed a combined RTA
-and k-CFA call graph construction algorithm in Section~\ref{sec:cg}
-to alleviate this problem.
+or extension points.
+Existing call graph construction algorithms either suffer from incompleteness
+or imprecision.  To alleviate this problem, 
+We proposed a combined RTA
+and k-CFA call graph construction algorithm in Section~\ref{sec:cg}.
 
-We also note that static analysis may report false positives due
-to its conservative nature, and multiple warnings that acutally corrspond to
-the same error. In addition, some GUI applications may even use
+We also note that a static analysis may report false positives due
+to its conservative nature, or multiple warnings that acutally corrspond to
+the same error. In addition, some GUI applications may use
 Java native methods to interact with the underlying operating system.
 Native methods are often beyond the ability of a static analysis, but
-must be considered to make the call graph sound. To address the
+should be considered to construct a good call graph. To address the
 above two limitations, we present a set of heuristics to filter
-highly likely false positives and remove redundant reports, and annotation
-support for programmers to specify call relationship for native methods.
+highly likely false positives and remove redundant reports, and provide
+annotation support for programmers to specify call relationship for
+ native methods.
 
@@
 k-CFA algorithms maintains one set per expression achieves better
-precision than RTA.
-
-Unfortunately, for GUI applications that use reflection, we found both
-RTA and k-CFA is insufficient to build a satisfactory call graph. Here
-is an example in Figure~\ref{fig:sampleandroid} to illustrate their limitations.
-
-(XXX)
-
-For desktop applications which have main method, it is straigtforward to apply
-the above algorithm. However, for applications on platforms like eclipse plugin
-and Android. presents new challenges. Two technical challenges must be solve.
-First, use reflection extensively, Second, it is possible to interact with
-native code.
-
-Android features an extended event-based library and dynamic inflation of
-graphical views from declarative XML layout files.
-A static analyzer for Android programs must consider such features, for
-correctness and precision.
-
-Give an example of how reflection affect call graph precision.
-
-The Android button example.
-
-Using RTA is not enough, since that maintains a global
-
-So, we present a new call graph construction algorithm
-
-reflected classes are known, use RTA.
-
-reflection code
-
-native code
+precision than RTA (\textit{k} is the context length, which is
+orthogonal to the number of maintained sets).
 
@@
 \end{algorithmic}
+\label{fig:cgalgorithm}
 \caption{A combined  RTA~\cite{rta} and k-CFA~\cite{kcfa} call graph construction algorithm.
@@
 are added to the call graph using the k-CFA algorithm.
-} \label{fig:cgalgorithm}
+} 
 \end{figure}
+
+Unfortunately, GUI applications often use reflection, which makes either
+RTA or k-CFA insufficient to build a satisfactory call graph. 
+The example code in Figure~\ref{fig:sampleandroid}  illustrates their limitations.
+In Figure~\ref{fig:sampleandroid}, line 7 uses reflection to create a \CodeIn{Button}
+object by looking up its id declared in the XML file. Due to
+its limitation in handling reflection, the k-CFA algorithm
+will conclude that variable \CodeIn{button} at line 7 does not point to any
+concrete \CodeIn{Button} object. Thus, it will miss the call edge \CodeIn{setText}
+while processing line 11. On the other hand, a less precise algorithm like RTA~\cite{}
+can not solve this problem. By explicitly specifying that GUI objects
+like \CodeIn{Button} as declared in the XML file will be created, RTA maintains
+a global value set for those GUI object type, and concludes that the \CodeIn{button} variable
+at line 7 points to a concrete Button object. So the algorithm  adds a
+call edge \CodeIn{setText} to the call graph. However, using RTA for
+the whole program results in unnecessary precision loss. Note that,
+RTA may conclude that the \CodeIn{cachedViews} variable at line 2
+may point to any created \CodeIn{List} objects, despite the
+fact that \CodeIn{cachedViews} can only be a \CodeIn{LinkedList} object at line 12.
+
+To alleviate the above problems, we present a combined RTA and k-CFA
+call graph construction algorithm as shown in Figure~\ref{fig:cgalgorithm}.
+This algorithm uses the RTA algorithm to construct call graph for part of the program that
+uses reflection to creating GUI objects (to ensure call graph completeness), while still uses
+the k-CFA algorithm for the remaining part of the program (to avoid precision loss). Specifically,
+users provide a list of classes, which can either be encoded manually or
+automatically extracted from the XML configuration file, whose method invocations should be
+constructed in a RTA way. The algorithm maintains a global set for
+each  provided class, but a separate set for expressions of other
+types.  For the example in Figure~\ref{fig:sampleandroid}, this
+combined algorithm concludes that a \CodeIn{Button} object has been
+created at line 7 and then adds the call edge \CodeIn{setText} to the
+graph. It also concludes that the \CodeIn{cachedViews} variable can only
+point to a \CodeIn{LinkedList} object, avoiding unnecessary precision loss.
+
+%For desktop applications which have main method, it is straigtforward to apply
+%the above algorithm. However, for applications on platforms like eclipse plugin
+%and Android. presents new challenges. Two technical challenges must be solve.
+%First, use reflection extensively, Second, it is possible to interact with
+%native code.
+
+%Android features an extended event-based library and dynamic inflation of
+%graphical views from declarative XML layout files.
+%A static analyzer for Android programs must consider such features, for
+%correctness and precision.
+
+%Give an example of how reflection affect call graph precision.
+
+%So, we present a new call graph construction algorithm
+
+%reflected classes are known, use RTA.
+
+%reflection code
+
+%native code
 

### 2012-01-01 GUIErrorDetector/paper/technique.tex
tweak

--- 2011-12-21 GUIErrorDetector/paper/technique.tex
@@
 \section{Technique}
+\label{sec:technique}
 
-\subsection{Problem Formulation}
+We first gives our high-level approach formulation, then present
+an error detection algorithm. Finally, we show how to instantiate
+the error algorithm to different GUI frameworks.
 
-formulate it as a graph reachability
+\subsection{Approach Formulation}
+
+This section formulates our high-level approach. We define the
+notations of \textit{UI thread}, \textit{non-UI threads},
+\textit{UI accessing methods},
+ \textit{Safe methods}, and \textit{invalid thread access error}, and
+two assumptions we make with regard to error detection.
+
+\noindent {\textsc{\textbf{Definition 1 (UI Thread).}}} {UI thread
+is a special thread created by the GUI framework during
+GUI initialization. After the GUI becomes visible, the UI thread
+takes charge of the application to handle events from the GUIs,
+or spawn new threads to process lengthy operations in the background. }\vspace{1mm}
+
+\noindent {\textsc{\textbf{Assumption 1.}}} {We assume that each multithreaded
+GUI application has a single global UI thread. This is true for applications
+built on top of GUI frameworks adapting the single-thread rule. The
+only exception is that 
+ an application may folk a new process to launch another
+application with its own UI thread. In that case, we require the new
+launched application to be analyzed separately.}\vspace{1mm}
+
+\noindent {\textsc{\textbf{Definition 2 (non-UI Thread).}}} {Any other
+threads except for the UI thread in a multithreaded GUI application
+ are called non-UI threads.}\vspace{1mm}
+
+\noindent {\textsc{\textbf{Assumption 2.}}} { We assume that each non-UI
+thread can only be spawned by the UI thread. Under this assumption,
+ all post-initialization
+GUI work naturally occurs in the UI-thread. Once the GUI is visible, the
+application is driven by events, which are always handled in the UI thread.
+We can safely ignore non-UI threads that are spawned during pre-initilaizaiton
+GUI work, since if such threads access a GUI object, an exception becomes
+immediately apparent and the whole application may abort even before the
+GUI is visible. This is highly unlikely for most of the realistic GUI
+applications.
+}\vspace{1mm}
+
+\noindent {\textsc{\textbf{Definition 3 (UI Accessing Methods).}}} { A method
+whose execution may read or write a UI object is called a UI accessing method.}\vspace{1mm}
+
+\noindent  {\textsc{\textbf{Definition 4 (Safe Methods).}}} {GUI frameworks that
+adapt the single-thread rule must provide methods to permit non-UI threads
+to run code in the UI thread. We can such methods \textit{safe methods}, since
+they can be invoked safely by any threads.}\vspace{1mm}
+
+\noindent  {\textsc{\textbf{Definition 5 (Invalid Thread Access).}}} {An invalid
+thread access error occurs when the UI thread spawns a non-UI thread, and there
+exists a path from the non-UI thread's \CodeIn{start} method to any UI accessing methods
+without going through any safe methods. }\vspace{2mm}
+
+At a high level, to detect an invalid thread access error, an analysis needs to track all
+non-UI threads spawned by the UI thread, and check whether those non-UI threads
+may invoke a UI accessing method.
 
 \subsection{Error Detection Algorithm}
+
+The algorithm for detecting potential invalid thread access errors
+is shown in Figure~\ref{fig:detectalgorithm}. Our algorithm uses a
+static call graph as the program representation for a multithreaded
+GUI application. A Java call graph represents calling relationships
+between methods. Specially, each node represents a method and each
+edge ($f$, $g$) indicates that method $f$ may call method $g$.
+A theoretical ideal call graph can be defined as the union of the
+dynamic call graphs over all possible executions of the program. 
+A conservative static call graph used in practice is a superset of
+the ideal call graph; it over-approximates the
+dynamic call graph of every possible execution. 
+In an object-oriented programming language like
+Java, a method is the basic logic unit in a program. Reporting
+potential errors at the method level can be sufficient in most cases.
+Thus, we believe using call graph is well suited for this problem while
+compared with other
+program representations like control flow graph or program dependence
+graph.
+
+Our algorithm in Figure~\ref{fig:detectalgorithm} works as follows. It
+first constructs a static call graph for the tested program (line 2),
+then specifies entry nodes for it (line 3). The algorithm starts to traverse
+the call graph from every entry node (line 6). For every entry node,
+it first uses Breadth First Search (BFS) to find all reachable
+\CodeIn{Thread.start()} method (line 7). Each \CodeIn{Thread.start()} method
+indicates that a new, non-UI thread is spawned.  After that, 
+the algorithm uses a slightly modified 
+BFS algorithm to find reachable UI accessing methods (lines 9 -- 23)
+from each \CodeIn{Thread.start()} node.
+Specifially, it uses a queue to keep track of all visited nodes, and
+then checks every successive node to be visited (line 12);
+it reports an error if that node
+is a UI accessing method (line 15), or skips it if it is
+a safe method (line 17), or simply keeps traversing otherwise (line 19).
+
+If the algorithm determines that a UI accessing method may be invoked
+by a non-UI thread, it creates an error report containing the full
+method call chain from the entry node (line 15, the \CodeIn{createErrorReport}
+method). An example call chain for
+the motivating example in Figure~\ref{fig:androiderror} is shown
+in Figure~\ref{fig:report}.
+
+Given a sound call graph, our algorithm is sound in that it does not
+miss true positives. We note, however, that computing a sound
+call graph for partial programs such as an eclipse plugin,
+or in the presence of reflection, is non-trivial. 
+In particular, GUI applications built on some popular frameworks
+often use configuration files and reflection to specify GUI layout
+or extension points.
+Existing call graph construction algorithms either suffer from incompleteness
+or imprecision.  To alleviate this problem, 
+We proposed a combined RTA
+and k-CFA call graph construction algorithm in Section~\ref{sec:cg}.
+
+We also note that a static analysis may report false positives due
+to its conservative nature, or multiple warnings that acutally corrspond to
+the same error. In addition, some GUI applications may use
+Java native methods to interact with the underlying operating system.
+Native methods are often beyond the ability of a static analysis, but
+should be considered to construct a good call graph. To address the
+above two limitations, we present a set of heuristics to filter
+highly likely false positives and remove redundant reports, and provide
+annotation support for programmers to specify call relationship for
+ native methods.
 
@@
 \label{fig:sampleandroid}
-\caption{A Sample Android Code ..}
+\caption{Sample GUI application code on the Android platform. The layout
+XML file (the top) specifies a Button object declaratively, 
+and the Java code (the bottom)
+first loads the XML file (line 6) and then uses reflection to create
+a Button object by its ID (line 7, the \CodeIn{findViewByd} method).}
 \end{figure}
 
-Give an example of how reflection affect call graph precision.
-
-The Android button example.
-
-Using RTA is not enough, since that maintains a global
-
-So, we present a new call graph construction algorithm
-
-reflected classes are known, use RTA.
-
-reflection code
-
-native code
+In the context of object-oriened languages wth dynamic dispatch, the
+crucial step in constructing a call graph is to compute a conservative
+approximation of the set of methods that can be invoked by a given
+virtual method call. Call graph construction algorithms have been
+studied intensively in the 1990s. While their original formulations
+use a variety of formalisms, most of them can be recast as set-based
+analyses. Various algorithms differ primarily in the number of sets
+that are used to approximate run-time values of expressions. 
+In practice, algorithms such as RTA that use a single set for the whole
+program scale well but achieves relatively lower precision. The
+k-CFA algorithms maintains one set per expression achieves better
+precision than RTA (\textit{k} is the context length, which is
+orthogonal to the number of maintained sets).
 
@@
 \end{algorithmic}
-\caption{Algorithm for constructing a call graph using a combination of the RTA~\cite{rta} and k-CFA~\cite{kcfa} algorithms.
-$cls$ is a list of class XXXX, whose invocatioon is treated using RTA; while the remaining call graph
-part is constructed using k-CFA.
-} \label{fig:cgalgorithm}
+\label{fig:cgalgorithm}
+\caption{A combined  RTA~\cite{rta} and k-CFA~\cite{kcfa} call graph construction algorithm.
+$cls$ is a list of classes whose method invocations are added to the
+call graph using the RTA algorithm; while method invocations from other classes
+are added to the call graph using the k-CFA algorithm.
+} 
 \end{figure}
 
-\subsubsection{Heuristic Filters and Annotations}
-(XXX)
+Unfortunately, GUI applications often use reflection, which makes either
+RTA or k-CFA insufficient to build a satisfactory call graph. 
+The example code in Figure~\ref{fig:sampleandroid}  illustrates their limitations.
+In Figure~\ref{fig:sampleandroid}, line 7 uses reflection to create a \CodeIn{Button}
+object by looking up its id declared in the XML file. When this button
+is clicked, its event handling code (line 10 -- 13) updates the text and cached
+the current view to a list declared at line 2.
 
-Static analysis exhaustively check possible error path; it may report
-paths that indicate the same bug. The potentially huge volume of
-reported warnings impose great burden for programmers to check
-its validity.
+Existing call graph algorithms either suffer from the problem of incompleteness
+or imprecision. The k-CFA algorithm performs points-to analysis with call
+graph construction interleavingly, and maintains a value set for every expression.
+For example, it concludes that variable \CodeIn{cachedViews} can only point
+to a \CodeIn{LinkedList} object and the method call \CodeIn{add} at line 12
+can only correspond to \CodeIn{LinkedList.add}. However, k-CFA fails to
+conclude that variable \CodeIn{button} declared at line 7 points to
+a \CodeIn{Button} object due to its limitation in dealing with reflection. Thus, k-CFA
+may miss the call graph edge corresponding to the method call \CodeIn{setText} at line 11. 
+On the other hand, using a coarse-grained algorithm like RTA~\cite{} can not still
+fully solve this problem. RTA adds an edge for a method invocation 
+to the call graph if an object of the receiver's type (or subtype)
+has been created.  By explicitly specifying that all GUI classes declared in the XML file will be created,
+RTA maintains a global value set for those GUI object type, and  adds a
+call edge \CodeIn{setText} to the call graph. However, RTA introduces 
+unnecessary precision loss: it may
+may conclude that the \CodeIn{cachedViews} variable at line 2
+point to any created \CodeIn{List} objects created somewhere else in the program, despite the
+fact that \CodeIn{cachedViews} can only be a \CodeIn{LinkedList} object.
 
-a few useful static heuristic filtering rules.
+To alleviate the above problems, we present a combined RTA and k-CFA
+call graph construction algorithm as shown in Figure~\ref{fig:cgalgorithm}.
+The algorithm shares the same spirit as k-CFA to maintain a value set
+for each expression. However, the only difference is that our
+algorithm uses a RTA-style treatment for constructing the value set for
+GUI classes: it parses the XML configuration file and explicitly
+adds a raw object to each declared GUI variable's value set. Thus,
+For the example in Figure~\ref{fig:sampleandroid}, this
+combined algorithm concludes that a \CodeIn{Button} object has been
+created at line 7 and then adds the call edge \CodeIn{setText} to the
+graph. It also concludes that the \CodeIn{cachedViews} variable can only
+point to a \CodeIn{LinkedList} object, avoiding unnecessary precision loss.
+%For desktop applications which have main method, it is straigtforward to apply
+%the above algorithm. However, for applications on platforms like eclipse plugin
+%and Android. presents new challenges. Two technical challenges must be solve.
+%First, use reflection extensively, Second, it is possible to interact with
+%native code.
 
-\begin{itemize}
-\item \textbf{Method call chain sumbsumption}. Remove redundant
-results
+%Android features an extended event-based library and dynamic inflation of
+%graphical views from declarative XML layout files.
+%A static analyzer for Android programs must consider such features, for
+%correctness and precision.
 
-\item \textbf{Remove system calls}. Method call chain involves typical
-system methods like \CodeIn{toString} are unlikely to reveal a real bug.
+%Give an example of how reflection affect call graph precision.
 
-\item \textbf{Method call chain with the same entry}. such
-call chains may reveal the same bug
+%So, we present a new call graph construction algorithm
 
-\item \textbf{Method call chain with the same tail}.  different ways
-to reach the same bug
+%reflected classes are known, use RTA.
 
-\item \textbf{User-defined rules}.  to overcome the limitation
+%reflection code
 
-\end{itemize}
+%native code
 
-The above filtering rules are not sound, it may filter real bugs but works
-well in practice.
+\subsubsection{Heuristic Filtering and Annotation}
+\label{sec:heuristic}
 
-We also provide annotations for native methods which are beyond the ability
-of most static analyses
+A static analysis can exhaustively check possible error path; but may report
+paths that do not actually exist (i.e., false positives) or different paths
+ that correspond to the same error (i.e., redundant warnings). We devise
+a set of heuristics below to filter out likely false positives and redundant warnings.
+The first two heuristics are for reducing false positives, while the
+remaining ones are for removing redundant warnings.
+
+%To remove those 
+%The potentially huge volume of
+%reported warnings impose great burden for programmers to check
+%its validity.
+
+\begin{enumerate}
+
+\item \textbf{Filter Reports Containing Library Calls}. A
+reported method call chain involving common Library calls
+like \CodeIn{Object.toString} or \CodeIn{Runtime.shutDown} are unlikely to
+be buggy, and should be filtered. In addition, a method call chain that \textit{only}
+consists of library calls after the entry method is also unlikely
+to reveal a valid bug, since it has no interaction with the UI. 
+We encode a list of common library calls, and remove
+a report if it contaiins one of them.
+%Method call chain involves typical
+%system methods like \CodeIn{toString} are unlikely to reveal a real bug.
+
+\item \textbf{Filter Reports With User-Annotated Methods}. Besides general
+library calls, users are also permitted
+to explicitly annotate methods that will never trigger an error.
+For example, the Android GUI framework provides a utility method 
+\CodeIn{runOnUIThread} to check whether the current thread is the UI thread
+before executing the code; if
+not, it executes the code on the UI thread using message passing.
+A reported call chain containing a annotated 
+can be safely removed.
+%method will never cause an
+%invalid thread error and should be removed.
+
+\item \textbf{Filter Lexically Redundant Reports}. One reported method call
+chain can lexically subsume another one. For example, suppose that a reported method
+call chain \CodeIn{a()} $\rightarrow$ \CodeIn{b()} $\rightarrow$ \CodeIn{c()}
+leads to a potential error, and another entry method \CodeIn{d()} calls \CodeIn{a()}.
+Therefore, a static analysis might also report another method call chain
+\CodeIn{d()} $\rightarrow$ \CodeIn{a()} $\rightarrow$ \CodeIn{b()} $\rightarrow$ \CodeIn{c()}
+that actually corresponds to the same error root as the previous one. In this case, 
+ removing the second call chain would not reduce the error detection capability:
+the first call chain already reveals the same error and is shorter 
+for programmers to interpret.
+
+\item \textbf{Filter Report With the Same $k$ Head Methods}. A method can call
+multiple methods that access GUI objects, such as:
+\begin{CodeOut}
+\begin{alltt}
+     public void m() \{
+         accessUIObject1();
+         accessUIObject2();
+     \}
+\end{alltt}
+\end{CodeOut}
+If method \CodeIn{m()} is invoked by a non-UI thread, two method call chains
+only different at last few method nodes will be reported:
+
+\CodeIn{a()} $\rightarrow$ ...\CodeIn{Thread.start()} ... $\rightarrow$ \CodeIn{m()} $\rightarrow$ \CodeIn{accessUIObject1()} ...
+
+\CodeIn{a()} $\rightarrow$ ...\CodeIn{Thread.start()} ... $\rightarrow$ \CodeIn{m()} $\rightarrow$ \CodeIn{accessUIObject2()} ...
+
+In fact, these two call chains correspond to the same error root: knowning
+method \CodeIn{m()} is called by a non-UI thread is sufficient to understand and fix this error.
+This filter compares every two reported method call chains that share the same
+$k$ ($k$ is user-settable with a default value 5) head nodes, and removes the longer one.
+
+\item \textbf{Filter Report With the Same $k$ Tail Methods}. A method
+can have multiple callers, so that method call chains with the same tail are likely
+to represent different ways to trigger the same error. This filter compares every
+two reported method call chains that share the same 
+$k$ ($k$ is user-settable with a default value 5) tail nodes, and removes the longer one.
+
+\end{enumerate}
+
+All above filters are based on heuristics, and thus not sound in
+that it may filter real bugs. However, as we will show in
+the next experiment section, all these filters work well, and significantly
+reduces the number of false positives and redundant reports in practice.
+
+A GUI application may also use native methods to interact with the underlying
+operating system or platforms. However, native methods are often
+beyond the ability of a static analysis but should be considered to make
+the call graph more complete. To do so, we provide an annotation \CodeIn{@CallByNativeMethods}
+for users to specify which native methods may call the current method. For example,
+the following code snippet indicates that native methods \CodeIn{native1()} and \CodeIn{native2()}
+will call method \CodeIn{javaMethod()}.
+
+%\noindent 
+\CodeIn{@CallByNativeMethods(callers=\{"native1", "native2"\})}
+
+%\noindent
+\CodeIn{public void javaMethod() \{ ... \}}
+
+Our static analysis will take the call relationship as indicated by this
+annotation into consideration when traversing the call graph. In our experiment,
+we found such an annotation was useful: one real-world bug can only be reported
+with the user-provided annotations.
 
@@
 
-We instantiate our error detection techniques for 4 popular GUI frameworks,
+We instantiate our error detection techniques for four popular GUI frameworks,
 namely SWT, Eclipse plugin environment, Swing, and Android.
-For each GUI platform, we customize the \textit{call graph entry nodes},
-\textit{UI accessing nodes}, and \textit{safe methods} on lines 3 -- 5 of the
-algorithm in Figure~\ref{fig:detectalgorithm}.
+Each framework has different settings for UI thread (i.e., \textbf{call graph entry nodes}),
+\textbf{UI accessing nodes}, and \textbf{safe methods}, which correspond
+to lines 3 -- 5 in Figure~\ref{fig:detectalgorithm}. We customize those
+framework-specific parts as follows.
+
+%For each framework, we customize the \textit{call graph entry nodes},
+%\textit{UI accessing nodes}, and \textit{safe methods} on lines 3 -- 5 of the
+%algorithm in
 
@@
 portable access to the GUI facilities of the operating systems on which it is implemented.
+Like a normal Java application, a SWT desktop application has a single main method
+as the starting point. By default, the main method launches
+the UI thread and pops up the GUI. We instantiate our technique as follows:
 
-Like normal Java applications, a SWT desktop application starts from its main method.
-By default, the thread that the main method executes is the UI thread. Thus, we instantiate
-our technique as follows:
+%starts from its main method.
+%By default, the thread that the main method executes is the UI thread. Thus, we instantiate
+%our technique as follows:
 
@@
 
-\item \textbf{Call graph entry points: } the single main method
+\item \textbf{Call graph entry nodes: } the single main method
 
-\item \textbf{UI accessing nodes: } any methods that calls \CodeIn{org.eclipse.swt.widgets.Display.checkWidget}
-or \CodeIn{org.eclipse.swt.widgets.Display.checkDevice} methods, since these two methods are the
-only place where the SWT framework checks whether the current thread is the UI thread or not. Thus, any
-methods that calls the checking method must be invoked in the UI thread.
+\item \textbf{UI accessing nodes: } in STW, a thread-unsafe method calls \CodeIn{Display.checkWidget}
+or \CodeIn{Display.checkDevice} methods to check whether the current thread is the UI thread or not. Thus,
+we treat all such methods that must be accessed in UI thread as the UI accessing nodes.
+% any
+%methods that calls the checking method must be invoked in the UI thread.
 
-\item \textbf{Safe methods: } SWT provides two utility methods (\CodeIn{Display.asyncExec}
-and \CodeIn{Display.syncExec}) that pass messages to the UI thread.
- Invoking these two methods are generally considered to be safe, and would not
-cause an invalid thread access error.
+\item \textbf{Safe methods: } SWT provides two helper methods (\CodeIn{Display.\\asyncExec}
+and \CodeIn{Display.syncExec}) as passing (a)synchronized messages to the UI thread.
+We treat these two methods as safe methods, since invoking
+them from any thread are generally considered to be safe and
+would not cause an invalid thread access error.
 
@@
 
-Unlike a SWT desktop application, an eclipse plugin, though is developed in SWT,
-has no single main method. Instead, (XXX) it extends certain extension points
-exposed by the eclipse framework, and eclipse will XXX. To instantiate our
-technique for the Eclipse plugin environment, we need to redefine the
-call graph entry points.
+An eclipse plugin is an open program. Unlike a SWT desktop application, it does not
+have a main method as a single program entry point. Instead, it extends certain
+extension points provided by the eclispe framework. As a plugin starts, the eclipse
+framework will calls back the overrided extension points and intializes the plugin code.
+We customize our technique for eclipse plugin as follows:
+
+%Unlike a SWT desktop application, an eclipse plugin, though is developed in SWT,
+%has no single main method. Instead, (XXX) it extends certain extension points
+%exposed by the eclipse framework, and eclipse will XXX. To instantiate our
+%technique for the Eclipse plugin environment, we need to redefine the
+%call graph entry points.
 
@@
 
-\item \textbf{Call graph entry points: } all overriden methods of the classes inside
- a plugin's \CodeIn{ui} package.  Such methods are normally called by the eclipse framework
-by the UI thread. XXX This rule, though quite heuristical, works quite well in practice.
+\item \textbf{Call graph entry nodes: } due to the complexity of the eclipse architecture,
+there is no rigorous way in eclipse to identify a UI thread. Here, we use a heuristic to determine call graph
+entry nodes from the UI thread. As a naming convention, source code in a plugin's \CodeIn{ui}
+package deals with the creation and maintainance of a plugin's GUI, and is thus
+invoked by the UI thread. We conservatively treat all public methods in the \CodeIn{ui}
+as call graph entry nodes.
 
-\item \textbf{UI accessing nodes} and \textbf{Safe methods} are the same as SWT desktop applications.
+%entry nodesall overriden methods of the classes inside
+% a plugin's \CodeIn{ui} package.  Such methods are normally called by the eclipse framework
+%by the UI thread. XXX This rule, though quite heuristical, works quite well in practice.
+
+\item \textbf{UI accessing nodes} and \textbf{Safe methods} are the same as SWT.
 
@@
 
-A Swing application often contains three kinds of threads: \textit{initial thread}
-that executes initial application code, the \textit{event dispatch thread},
-where all GUI manipulation code is executed, and the \textit{worker thread} where
-time-consuming background tasks are executed. After Swing UIs are launched,
-the initial thread exits and the event dispatch thread starts to execute all
-event-handling code or spawns new worker threads. XXXX Therefore, we can not directly
-use the main method as the call graph entry point, since it is not invoked
-by the UI thread. We customize our technique for Swing as follows:
+A Swing application has a single main method, but contains three kinds of
+threads: \textit{initial thread} that executes initial application code from the main method,
+the \textit{UI thread}, where all GUI manipulation code is executed,
+and the \textit{worker thread} where time-consuming background tasks are executed.
+After a Swing program starts, its initial thread exits and the UI thread takes charge
+of the application and starts to execute all event-handling code or spawns new worker threads. 
+We customized our technique for Swing as follows:
+%XXXX Therefore, we can not directly
+%use the main method as the call graph entry point, since it is not invoked
+%by the UI thread. We customize our technique for Swing as follows:
 
@@
 
-\item \textbf{Call graph entry points: } all overriden callback methods of the listerner classes.
-Specifically, for each class, we check whether it is a Swing listerner class. If so,
-we extract all its overriden callback methods as the call graph entry points.
+\item \textbf{Call graph entry nodes: } all overriden callback methods in the
+listerner classes are called from the UI thread. We treat those callback
+methods as the entry nodes.
+
+%Specifically, for each class, we check whether
+%it is a Swing listerner class. If so, we extract all its overriden callback methods as the call graph entry points.
  %Such methods are normally called by the eclipse framework
@@
 
-\item \textbf{UI accessing nodes:} unlike SWT, Swing does not explicitly check
-whether the current thread is the UI thread or not, when a GUI object is accessed. Except
-for three documented thread-safe method (\CodeIn{repaint}, XXXX), our technique
-treat all methods defined in each GUI object as UI accessing nodes.
+\item \textbf{UI accessing nodes:} as stated in Swing's documentation, methods
+in Swing GUI classes are not thread safe with three exceptions (\CodeIn{repaint()},
+\CodeIn{revalidate()}, and \CodeIn{invalidate()}). Thus, we
+treat all methods as defined in each GUI class as UI accessing nodes.
 
-\item \textbf{Safe methods: } similar to SWT, Swing provides two utility methods
-(\CodeIn{SwingUtilities.invokeLater} and \CodeIn{SwingUtilities.invokeDelay}) to pass messages to the UI thread. These two methods are regarded as safe methods.
+\item \textbf{Safe methods: }  Swing provides two helper methods
+(\CodeIn{SwingUti-\\lities.invokeLater} and \CodeIn{SwingUtilities.invokeDelay}) to pass messages to the UI thread.
+We treat these two methods as safe methods.
 
@@
 Android is a Java-based platform for embedded or mobile devices. 
-Android features an extended event-based library and dynamic inflation of
-graphical views from declarative XML layout files. Android applications are
-written in Java, running in their own process within their own virtual machine.
-Unlike desktop applications, they do not have a single entry point but can
+%Android features an extended event-based library and dynamic inflation of
+%graphical views from declarative XML layout files.
+Android applications are written in Java, running in their own process within their own virtual machine.
+An Android program does not have a single entry point but can
 rather use parts of other Android applications on-demand and can require their
@@
 operating system. In particular, Android applications use \textit{activities}
-as code interacting with the user through a visual interface. Event handlers
-are scheduled in no particular ordering, with some notable exceptions such as the
-lifecycle of activities.
+as code interacting with the user through a visual interface. GUI event handlers
+are handled in an activity  in no particular ordering.
+We instantiate our technique for Android programs as follows:
+%, with some notable exceptions such as the
+%lifecycle of activities.
 
-An XML \textit{manifest file} registers the components of an application. Other XML
-fies describe the visual layout of the activities. Activities \textit{inflate}
-layout files into
-visual objects (a hierarchy of views), through an \textit{inflater} provided by the An-
-droid library. This means that library or user-defined views are not explicitly
-created by new statements but rather inflated through \textit{reflection}. Library meth-
-ods such as \CodeIn{findViewById} access the inflated views.
-
-We instantiate the technique for Android programs as follows.
+%An XML \textit{manifest file} registers the components of an application. Other XML
+%fies describe the visual layout of the activities. Activities \textit{inflate}
+%layout files into
+%visual objects (a hierarchy of views), through an \textit{inflater} provided by the An-
+%droid library. This means that library or user-defined views are not explicitly
+%created by new statements but rather inflated through \textit{reflection}. Library meth-
+%ods such as \CodeIn{findViewById} access the inflated views.
 
@@
 
-\item \textbf{Call graph entry points: } all overriden callback methods of the event
-listerner classes, and all overriden callback methods of an Activity.
+\item \textbf{Call graph entry nodes: } in an Android application,
+an \CodeIn{Activity} object is created and manipulated by the UI thread. We treat
+all public methods from an \CodeIn{Activity} class as call graph entry nodes. Additionally,
+we also add all overriden callback methods in event listener classes as entry nodes.
 
-\item \textbf{UI accessing nodes: } any methods that calls the \CodeIn{ViewRoot.checkThread}
-method. This method is the only place where Android checks
-whether the current thread is the UI thread or not. Thus, any
-methods that calls the checking method must be invoked in the UI thread.
+\item \textbf{UI accessing nodes: } like SWT, Android explicitly checks the current
+thread validity before accessing a GUI object using the \CodeIn{ViewRoot.checkThread} method.
+Thus, we treat every methods that calls \CodeIn{ViewRoot.checkThread} as a UI accessing node
+in the call graph.
+%method. This method is the only place where Android checks
+%whether the current thread is the UI thread or not. Thus, any
+%methods that calls the checking method must be invoked in the UI thread.
 
-\item \textbf{Safe methods: } Android provides two utility methods (\CodeIn{View.post}
-and \CodeIn{View.XXX}) that pass messages to the UI thread.
- Invoking these two methods are generally considered to be safe, and would not
-cause an invalid thread access error.
+\item \textbf{Safe methods: } Android provides two helper methods (\CodeIn{View.post}
+and \CodeIn{View.postDelay}) to execute code on the UI thread. Thus, we treat
+these two methods as safe methods, since invoking them on any thread
+would not cause an invalid thread access error.
+ %Invoking these two methods are generally considered to be safe, and would not
+%cause an invalid thread access error.
 
 \end{itemize}
+
+In our experience, instantiating our general technique to  a specific framework
+requires moderate human effort. We wrote around 500 lines of Java code in total to achieve
+the above four instantiations.

### 2012-01-04 GUIErrorDetector/paper/abstract.tex
revise abstract according to mike's comments

@@
 \begin{abstract}
-Graphical User Interface (GUI) is a critical component of today's software.
- It provides user-friendly access to the functionality provided by the application.
-To keep GUIs responsive and active, a GUI application often spawns
- separate threads to handle lengthy operations in the background,
-such as expensive computations, I/O tasks, and network requests.
-However, many modern GUI frameworks require all GUI objects
-must be accessed exclusively by the \textit{event dispatching thread}
-(or called \textit{UI thread}). If a GUI object
-is accessed through a non-UI thread, an \textit{invalid thread access} error
-occurs and the whole application may abort consequently.
+To keep a Graphical User Interface (GUI) responsive and active, a GUI
+application often has a main \textit{UI thread} (or \textit{event dispatching thread})
+and spawns separate threads to handle lengthy operations in the background,
+such as expensive computation, I/O tasks, and network requests.
+Many GUI frameworks require all GUI objects to be accessed exclusively by the
+UI thread. If a GUI object is accessed through a non-UI thread,
+an \textit{invalid thread access} error occurs and the whole
+application may abort.
 
-In this paper, we present a general technique to find such \textit{invalid thread access}
+This paper presents a general technique to find such \textit{invalid thread access}
 errors in multithreaded GUI applications. We formulate finding invalid
-thread access errors as a call graph
-reachability problem. Our technique starts from call graph entry nodes to
-statically explore all possible paths that may cause a non-UI thread
-to access a GUI object.
-However, the heavy use of reflection in modern GUI frameworks makes existing
-call graph construction algorithms insufficient to build a both complete and precise
-call graph. Thus, we present a combined RTA and k-CFA
+thread access errors as a call graph reachability problem with
+thread spawning as the sources and GUI object accessing as the sinks. 
+Heavy use of reflection in modern GUI applications makes existing
+call graph construction algorithms fail to build a sufficiently complete
+and precise call graph. Thus, we present a combined RTA and k-CFA
 call graph construction algorithm to overcome the limitations.% of analyzing GUI applications.
@@
 We implemented our technique and instantiated it on four popular GUI
-platforms, namely SWT, Eclipse plugin development framework, Java Swing, and Android. In an evaluation
-on XX subjects over XXX LOC, our technique found a number of errors,
-suggesting its effectiveness and showing good scalability.
+platforms: SWT, Eclipse plugin development framework, Java Swing, and
+Android. In an evaluation on XX subjects over XXX LOC, our technique
+found a number of real-world errors, suggesting its effectiveness
+and showing good scalability.
 

### 2012-01-04 trunk/GUIErrorDetector/paper/introduction.tex
address mike's comments on introduction

@@
 
-Graphical User Interfaces (GUIs) are one of the most important parts of
-software. Most software developed in recent years has a GUI, and the only
-way for the most end-users to interact with the software application is through
-the GUI. Hence, end-user satisfaction and retention of a software application
- are largely determined by the usability and correctness of
+End-user satisfaction and retention of a software application
+ are largely dependent on the usability and correctness of
 its GUIs.
 
-To make the GUIs more responsive and better utilize the increasingly available
-computation power in the multi-core era, GUI applications often spawn separate
-threads to handle time-consuming operations in the background, such as expensive
-computations, I/O tasks, and network requests. Using threads for those lengthy tasks
-makes a GUI active by allowing the timing of operations not delay unrelated parts of a 
-GUI application.
+To make the GUI more responsive and utilize multi-core computation,
+GUI applications often spawn separate threads to handle time-consuming
+operations in the background, such as expensive computation, I/O tasks,
+and network requests. This permits the GUI to respond to new events
+even before the lengthy task completes.
 
@@
 
-Nowadays, many popular GUI frameworks such as Swing~\cite{swing}, SWT~\cite{swt}, Android~\cite{android},
-Qt~\cite{qt}, MacOS Cocoa~\cite{macos}, and X Windows~\cite{xwindow} 
+Many popular GUI frameworks such as Swing\footnote{\url{http://docs.oracle.com/javase/6/swing/}},
+SWT\footnote{\url{http://eclipse.org/swt/}}, Android\footnote{\url{http://www.android.com/}},
+Qt\footnote{\url{http://qt.nokia.com/products/}}, MacOS Cocoa\footnote{\url{http://developer.apple.com/cocoa.html}},
+and X Windows\footnote{\url{http://www.x.org/}}
 adapt the \textit{single-thread rule}:
@@
 
-The \textit{event dispatching thread}, or called \textit{UI thread}, is a global special
-thread initialized by the GUI framework, where all event-handling code
+The \textit{event dispatching thread}, also called the \textit{UI thread}, is a single
+special thread initialized by the GUI framework, where all event-handling code
 is executed. All code that interacts with GUI objects must also
-execute on that thread.  There are several advantages to adapt the single-thread rule:
+execute on that thread.  There are several advantages to the single-thread rule:
 
@@
 
-\item GUI developers do not have to have an in-depth
-understanding of concurrency programming. A GUI framework in which all GUI objects
+\item GUI developers do not need an in-depth
+understanding of concurrent programming. A GUI framework in which all GUI objects
 fully support multithreaded access can be difficult to extend, particularly
@@
 
-\item Single-thread rule incurs less overhead.
+\item The single-thread rule incurs less overhead.
 A GUI framework that attempts to carefully lock critical sections can spend a substantial
@@
 
-Despite the convenience that the single-thread rule brings to build a
-GUI framework, it pushes the thread safety burden back onto the GUI application developers,
-who must make sure all GUI objects are accessed by the UI thread.
+The single-thread rule pushes a burden back on GUI application developers,
+who must ensure all GUI objects are accessed by the UI thread.
 
@@
 After handling the request, the GUI-update code that displays the response must be executed on the UI-thread.
-If not, an \textit{invalid thread access} will error occur. In practice, such
-invalid thread access error is \textit{frequent}, \textit{pervasive}, \textit{severe}.
-and \textit{difficult to avoid}.
+If not, an \textit{invalid thread access error} will occur. In practice, such
+invalid thread access error is \textit{frequent}, \textit{pervasive}, and \textit{severe}.
+%and \textit{difficult to avoid}.
 
-Take the popular Standard Widget Toolkit (SWT)~\cite{swt} GUI framework as an example. 
-In a recent survey~\footnote{\url{http://www.slideshare.net/lakshmip/top-3-swt-exceptions-3951224}}, the invalid thread access error
-has been listed as the top 3 bugs in developing a SWT application, and treated
-as the source of many relevant concurrency bugs. Searching
-``SWTException:Invalid thread access'' in Google returns over 11,800 entries,
+Take the popular Standard Widget Toolkit (SWT) GUI framework as an example. 
+The invalid thread access error is one of the top 3 bugs in developing a SWT application, and is
+the source of many relevant concurrency bugs~\footnote{\url{http://www.slideshare.net/lakshmip/top-3-swt-exceptions-3951224}}.
+A Google search for ``SWTException:Invalid thread access''  returns over 11,800 entries,
 consisting of numerous bug reports, forum posts, and mailing list threads on
-this problem. Eclipse~\cite{eclipse}, the de-facto standard IDE for Java development,
-is built on top of SWT. As eclipse became open-sourced in 2001, the invalid thread access error has
-been consistently reported during the past 11 years across different products, different components, and different releases.
-Searching the same ``SWTException:Invalid thread access'' keyword in eclipse's bug repository
+this problem. Eclipse, the IDE for Java development, is built on top of SWT.
+Searching for ``SWTException:Invalid thread access'' in Eclipse's bug repository
 and discussion forum returns over 2732 bug reports and 351 distinct threads, respectively. 
-We further manually studied all 156 \textit{confirmed} distinct bug reports, and 
+We manually studied all 156 \textit{confirmed} distinct bug reports, and 
 found this error has been reported in at least 20 distinct eclipse projects
-and 40 distinct eclipse components. Even after over 10-year's active development,
-a recent release of eclipse still contains this error (bug id: 333533, reported in 01/2011).
- Furthermore, many reported  errors are non-trivial. It is unintuitive
-to fix them. Developers usually
-need non-local reasoning to find the specific UI interactions that can trigger the bug; and
-some reported errors (e.g., bug id: 51757) even took developers 2 years to fix it and verify the
-patch. In addition, such invalid thread access error is UI-relevant and also user-perceivable;
-it cannot be recovered by the program itself and often terminates the whole application.
-In many circumstances as described in the bug reports,
-what users can only do is to restart the application to resort to an inconsistent status.
+and 40 distinct eclipse components. Even after over 10 years of active development,
+a recent release of Eclipse still contains this error (bug id: 333533, reported in 01/2011).
+ Furthermore, many reported  errors are non-trivial, and it is unintuitive
+to fix them. Developers usually need non-local reasoning to find the specific
+UI interactions that can trigger the bug;  it even took developers 2 years
+to fix bug: 51757 and verify the patch. In addition, the invalid thread access error
+is UI-relevant and user-perceivable; it cannot be recovered by the program itself
+and often terminates the whole application. In many circumstances as described in the bug reports,
+users can only restart the application to recover from the error.
 
@@
 \vspace*{-2.0ex} \Caption{{\label{fig:androiderror} A real
-bug reported in 11/17/2011 in Mozilla firefox release 10.0.a.rc3
+bug reported on 11/17/2011 in Mozilla firefox release 10.0.a.rc3
 for the Android platform (bugzilla ID: 703256). \CodeIn{LayerView}'s constructor
@@
 The invalid thread access error is not unique to the SWT framework. Other recent GUI frameworks
-like Android~\cite{android} also suffer from similar problems. For example, 
-Figure~\ref{fig:androiderror} shows a recently reported bug on the Mozilla Firefox Android version.
+like Android also suffer from similar problems. For example, 
+Figure~\ref{fig:androiderror} shows a recently reported bug on Android version of Mozilla Firefox.
 In Figure~\ref{fig:androiderror}, \CodeIn{LayViewer}'s constructor calls the
@@
 since the code that spawns a new thread inside the \CodeIn{setRender} method is
-in Android's library whose source code is often not available to developers.
+in an Android library whose source code may not be available to developers.
 
@@
 
-The invalid thread access errors have significantly affect the
-usability of GUIs, but have not been thoroughly studied in
-the context of multithreaded GUI applications . To ensure GUIs
-to behave correctly, effective
-techniques must be developed to alleviate this problem.
-
-%Effective techniques must be developed to
-%find such errors.
+Invalid thread access errors have significantly affect the
+usability of GUIs, but they have not been thoroughly studied in
+the context of multithreaded GUI applications. To ensure GUIs
+behave correctly, effective techniques must be developed to alleviate this problem.
 
 Software testing, the most widely used method to ensure program correctness,
-is insufficient to detect such errors. That is because the space of possible interactions
+is insufficient to detect such errors. The space of possible interactions
 with a GUI is enormous, in that each sequence of GUI events can result in
@@
 these states. It is almost impossible for testing to cover every possible
-states. In fact, for a widely-used software system like eclipse
-often has a well-designed test suite that achieves fairly high coverage; but many
- bug-triggering UI sequences are still not covered.
+state. In fact, a widely-used software system like Eclipse
+often has a well-designed test suite that achieves fairly high statement coverage;
+but many paths executed by bug-triggering UI sequences are still not covered.
 
-Program refactoring~\cite{Mens:2004}, another popular way to improve software quality,
-is also inadequate to eliminate this error.  A standard way to fix such
+%Program refactoring~\cite{Mens:2004}, another popular way to improve software quality,
+%is also inadequate to eliminate this error. 
+A standard way to fix an
 invalid thread access error is to replace direct GUI object accessing code 
-with asynchronized message passing, to ensure GUI object are accessed in
-the UI thread. For example, fixing the bug in Figure~\ref{fig:androiderror}
-needs to wrap line 222 inside a \CodeIn{post} message passing method\footnote{The
+with asynchronized message passing, to ensure a GUI object are accessed in
+the UI thread. For example, to fix the bug in Figure~\ref{fig:androiderror},
+a developer would wrap line 222 inside a \CodeIn{post} message passing method\footnote{The
 \CodeIn{post} method in class \CodeIn{android.widget.View} is a
-a standard way to send messages to the UI-thread}, as follows:
+a standard way to send messages to the UI-thread.}, as follows:
 
@@
 221.     gl.glViewport(0, 0, width, height);
-         \textbf{mView.post}(new Runnable() \{
-             public void run() \{
+         \textbf{mView.post(new Runnable() \{}
+             \textbf{public void run() \{}
 222.             mView.setViewportSize(new IntSize(width, height));
-             \}
-         \});
+             \textbf{\}}
+         \textbf{\});}
      \}
@@
 every possible UI-accessing operation with asynchronized message passing
-may solve this problem. However, such an approach is problematic,
+may avoid the invalid thread error. However, such an approach is problematic,
 because using asynchronized message passing has no timing
 guarantee. It is entirely possible that, in some cases, a GUI object has already been
-disposed before the message sent to arrives. Thus, programmers can not use
+disposed before the message sent to arrives, causing other bugs. Thus, programmers can not use
 it everywhere; instead, they must choose carefully to put it in appropriate places
-with extreme caution.
+with extreme caution. This makes invalid thread errors even harder to avoid,
+and demands a proactive technique to detect them.
 
@@
 
-In this paper, we choose to use static analysis to find such potential errors.
-Static analysis has two attractive advantages while comparing to dynamic approaches such as
- testing.
-First, a static analysis can explore every path of the program without executing the code, and
-thus there is no need to construct non-trivial tests and harnesses.
-Second, a static analysis can soundly find potentially errors: if it
+This paper uses static analysis to find such potential errors.
+Static analysis has two advantages while compared to dynamic approaches such as
+ testing. First, a static analysis can explore every path of the program without
+executing the code, and without the need for a test suite.
+Second, a static analysis can verify the code: if it
 reports no warnings, the code is guaranteed to be bug-free.
@@
 
-We formulate finding invalid thread access as a call graph reachability
+In our static analysis, we formulate finding invalid thread access as a call graph reachability
 problem. Given a call graph, our technique traverses
@@
 not miss true positives. We note, however, that computing a sound
-call graph for GUI applications in the presence of reflection,
+call graph with acceptable precision for GUI applications in the presence of reflection
 is non-trivial.
 Existing call graph construction algorithms such as RTA~\cite{} and k-CFA~\cite{}
-either suffer from the problem of imprecision or incompleteness .
+either suffer from either imprecision or incompleteness .
 To alleviate this problem,
 we present a combined RTA and k-CFA call graph construction algorithm, and
-also compare its usefulness with other algorithms in  our experiments.
+also compare its usefulness with other algorithms in  our experiments. We
+also note that static analysis may report false positives due to its
+conservative nature, or multiple warnings that actually correspond
+to the same error. To alleviate such limitations, we devise a set
+ of heuristics to filter likely false positives and redundant warnings.
 
@@
 
-We instantiate our technique for four popular GUI frameworks namely SWT,
-eclipse plugin environment, Java Swing, and Android. Swing and SWT are
+We instantiated our technique for popular four GUI frameworks namely SWT,
+eclipse plugin environment, Java Swing, and Android. 
+Swing and SWT are unquestionably 
 two dominating GUI frameworks in developing desktop Java applications.
-Eclipse and its plugin development envrionment is the de-facto standard
-IDE for Java. Android market share reaches 56\% in the mobile computing
-world as of Sep 2011, and becomes the No. 1 platform for mobile applications.
-Instantiating the general technique for each framework only requires few
-human effort. The primary framework-specific part is to specify
-the \textit{UI thread} and \textit{call graph entry nodes}.
+Eclipse with its plugin development envrionment is the de-facto standard
+IDE for Java. Android is the No. 1 platform for
+developing mobile applications with market share 56\% as of Sep 2011.
+Although our technique is generally applicable for GUI
+frameworks adapting the single-thread rule, a specific framework
+may have its own treatment of \textit{UI thread} and \textit{call graph
+entry nodes}. Thus, we must explicitly identify those framework-specific
+parts in our prototype tool implementation.
 
-We further implement a prototype tool that supports detecting invalid
-thread access errors in the above four GUI frameworks, and evaluate
-it on XXX subjects over XXX LOC. The experiment results demonstrate
-the effectiveness of the proposed technique. Our tool found XXX
-from XXX subjects on all supported GUI frameworks with an acceptable
-false positives.
+%Applications built on top of different GUI frameworks have different
+%treatment of \textit{UI thread} and \textit{call graph entry nodes}.
+%Instantiating the general technique for each framework only requires few
+%human effort. The primary framework-specific part is to specify
+%the \textit{UI thread} and \textit{call graph entry nodes}.
+
+We implement an invalid thread error detection tool that supports
+the above four GUI frameworks. Our tool works in a fully-automatic,
+push-button manner, and scales to realistic programs.
+We evaluate our implementation on XXX subjects from four different
+frameworks over XXX LOC. The experiment results demonstrate
+that: our technique is effective (it found XXX real-world errors
+on all supported frameworks); our combined RTA and k-CFA call
+graph construction algorithm is useful (XXX it improves both completeness
+and precision over the existing algorithms), and our proposed
+heuristics are useful (it signficantly reduces the number of
+false positives and redundant warnings).
 
@@
 the invalid thread access error as a call graph reachability problem,
-and present a general technique to find such errors. 
+and present a general error detection technique.
 In particular, to deal with the unique features in
@@
 \item \textbf{Evaluation.} We performed an experiment on XXX subjects
-from 4 different platforms over XXX LOC. As a result, our technique
-found XXX bugs (Section~\ref{sec:evaluation}).
+from 4 different platforms over XXX LOC to show the usefulness
+of the proposed techinque (Section~\ref{sec:evaluation}).
 

### 2012-01-04 GUIErrorDetector/paper/technique.tex
address Mike's comments on the technique section

@@
 
-We first gives our high-level approach formulation, then present
+We first give our high-level approach formulation, then present
 an error detection algorithm. Finally, we show how to instantiate
@@
 \textit{UI accessing methods},
- \textit{Safe methods}, and \textit{invalid thread access error}, and
+ \textit{safe methods}, and \textit{invalid thread access error}, and
 two assumptions we make with regard to error detection.
 
-\noindent {\textsc{\textbf{Definition 1 (UI Thread).}}} {UI thread
+\noindent {\textsc{\textbf{Definition 1 (UI Thread).}}} {The UI thread
 is a special thread created by the GUI framework during
 GUI initialization. After the GUI becomes visible, the UI thread
-takes charge of the application to handle events from the GUIs,
-or spawn new threads to process lengthy operations in the background. }\vspace{1mm}
+takes charge of the application to handle events from the GUI,
+and spawns new threads to process lengthy operations in the background. }\vspace{1mm}
 
@@
 only exception is that 
- an application may folk a new process to launch another
+ an application may fork a new process to launch another
 application with its own UI thread. In that case, we require the new
@@
 \noindent {\textsc{\textbf{Assumption 2.}}} { We assume that each non-UI
-thread can only be spawned by the UI thread. Under this assumption,
- all post-initialization
-GUI work naturally occurs in the UI-thread. Once the GUI is visible, the
+thread is spawned by the UI thread. Under this assumption,
+we ignore all non-UI threads created by the GUI framework
+before the UI thread has been initialized. That is, all post-initialization
+GUI work naturally occurs in the UI thread. Once the GUI is visible, the
 application is driven by events, which are always handled in the UI thread.
-We can safely ignore non-UI threads that are spawned during pre-initilaizaiton
-GUI work, since if such threads access a GUI object, an exception becomes
+We believe this assumption is reasonable, since if a non-UI thread 
+spawned during pre-initialization GUI work accesses a GUI object, an exception becomes
 immediately apparent and the whole application may abort even before the
-GUI is visible. This is highly unlikely for most of the realistic GUI
+GUI is visible. This is highly unlikely for realistic GUI
 applications.
@@
 
-\noindent {\textsc{\textbf{Definition 3 (UI Accessing Methods).}}} { A method
+\noindent {\textsc{\textbf{Definition 3 (UI-Accessing Methods).}}} { A method
 whose execution may read or write a UI object is called a UI accessing method.}\vspace{1mm}
@@
 \noindent  {\textsc{\textbf{Definition 4 (Safe Methods).}}} {GUI frameworks that
-adapt the single-thread rule must provide methods to permit non-UI threads
+adopt the single-thread rule must provide methods to permit non-UI threads
 to run code in the UI thread. We can such methods \textit{safe methods}, since
-they can be invoked safely by any threads.}\vspace{1mm}
+they can be invoked safely by any thread.}\vspace{1mm}
 
@@
 thread access error occurs when the UI thread spawns a non-UI thread, and there
-exists a path from the non-UI thread's \CodeIn{start} method to any UI accessing methods
-without going through any safe methods. }\vspace{2mm}
+exists a path from the non-UI thread's \CodeIn{start} method to any UI-accessing method
+without going through any safe method. }\vspace{2mm}
 
@@
 edge ($f$, $g$) indicates that method $f$ may call method $g$.
-A theoretical ideal call graph can be defined as the union of the
+A theoretically ideal call graph can be defined as the union of the
 dynamic call graphs over all possible executions of the program. 
@@
 potential errors at the method level can be sufficient in most cases.
-Thus, we believe using call graph is well suited for this problem while
-compared with other
-program representations like control flow graph or program dependence
-graph.
+Thus, we believe using the call graph is well suited for this problem while
+compared with other program representations like control flow graph or
+program dependence graph.
 
@@
 it first uses Breadth First Search (BFS) to find all reachable
-\CodeIn{Thread.start()} method (line 7). Each \CodeIn{Thread.start()} method
+\CodeIn{Thread.start()} calls (line 7). Each \CodeIn{Thread.start()} call
 indicates that a new, non-UI thread is spawned.  After that, 
-the algorithm uses a slightly modified 
-BFS algorithm to find reachable UI accessing methods (lines 9 -- 23)
+the algorithm uses a BFS to find reachable UI accessing methods (lines 9 -- 23)
 from each \CodeIn{Thread.start()} node.
@@
 miss true positives. We note, however, that computing a sound
-call graph for partial programs such as an eclipse plugin,
+call graph for partial programs such as an Eclipse plugin,
 or in the presence of reflection, is non-trivial. 
@@
 or extension points.
-Existing call graph construction algorithms either suffer from incompleteness
-or imprecision.  To alleviate this problem, 
-We proposed a combined RTA
+Existing call graph construction algorithms suffer from incompleteness
+, imprecision, or both.  To alleviate this problem, 
+we proposed a combined RTA
 and k-CFA call graph construction algorithm in Section~\ref{sec:cg}.
@@
 We also note that a static analysis may report false positives due
-to its conservative nature, or multiple warnings that acutally corrspond to
+to its conservative nature, or multiple warnings that actually correspond to
 the same error. In addition, some GUI applications may use
@@
 highly likely false positives and remove redundant reports, and provide
-annotation support for programmers to specify call relationship for
+annotation support for programmers to specify call relationships for
  native methods.
@@
 first loads the XML file (line 6) and then uses reflection to create
-a Button object by its ID (line 7, the \CodeIn{findViewByd} method).}
+a Button object by its ID (line 7, the \CodeIn{findViewById} method).}
 \end{figure}
@@
 object by looking up its id declared in the XML file. When this button
-is clicked, its event handling code (line 10 -- 13) updates the text and cached
+is clicked, its event handling code (line 10 -- 13) updates the text and caches
 the current view to a list declared at line 2.

### 2012-01-05 GUIErrorDetector/src/edu/washington/cs/detector/CGEntryManager.java
Add utility method to fetch all methods in a class (including the inherited ones)

@@ -146,6 +146,14 @@ public class CGEntryManager {
 		return getAllPublicMethods(scope, cha, uiClasses);
 	}
 	
+	public static Iterable<Entrypoint> getAllPublicMethods(CGBuilder builder, List<String> uiClasses, boolean includeInherited) {
+		if(!includeInherited) {
+			return getAllPublicMethods(builder, uiClasses);
+		} else {
+			return getAllPublicMethods(builder.getAnalysisScope(), builder.getClassHierarchy(), uiClasses, true);
+		}
+	}
+	
 	public static Iterable<Entrypoint> getAllPublicMethods(AnalysisScope scope, ClassHierarchy cha, String... methodClasses) {
 		List<String> clazzList = new LinkedList<String>();
 		for(String uiClass : methodClasses) {
@@ -169,6 +177,27 @@ public class CGEntryManager {
 				return result.iterator();
 			}
 		}; 
+	}
+	
+	public static Iterable<Entrypoint> getAllPublicMethods(AnalysisScope scope, ClassHierarchy cha, List<String> methodClasses, boolean includeInherited) {
+		if(!includeInherited) {
+			return getAllPublicMethods(scope, cha, methodClasses);
+		} else {
+			final HashSet<Entrypoint> result = HashSetFactory.make();
+			for(String methodClass : methodClasses) {
+				//System.out.println("method class: " + methodClass);
+			    Iterable<Entrypoint> entries = getAppPublicMethodsByClass(scope, cha, methodClass, false, includeInherited /*include inherited*/);
+			    for(Entrypoint ep : entries) {
+			    	result.add(ep);
+			    }
+			}
+			
+			return new Iterable<Entrypoint>() {
+				public Iterator<Entrypoint> iterator() {
+					return result.iterator();
+				}
+			}; 
+		}
 	}
 	
 	public static Iterable<Entrypoint> getAndroidActivityCallBackMethods(CGBuilder builder, Collection<String> activityClasses) {
@@ -233,6 +262,46 @@ public class CGEntryManager {
 				}
 			}
 		}
+		
+		return new Iterable<Entrypoint>() {
+			public Iterator<Entrypoint> iterator() {
+				return result.iterator();
+			}
+		}; 
+	}
+	
+	//XXX largely duplicated with the above one, but it does not check class loader
[…]

### 2012-01-05 GUIErrorDetector/src/edu/washington/cs/detector/util/Utils.java

@@ -242,6 +242,14 @@ public class Utils {
 		coll.addAll(set);
 	}
 	
+	public static <T> Iterable<T> returnUniqueIterable(Iterable<T> coll) {
+		Set<T> set = new LinkedHashSet<T>();
+		for(T t : coll) {
+			set.add(t);
+		}
+		return set;
+	}
+	
 	//check if every element of its is included in all
 	public static <T> boolean includedIn(Iterable<T> its, Iterable<T> all) {
 		Collection<T> collection_its = iterableToCollection(its);
@@ -257,6 +265,11 @@ public class Utils {
 		}
 		return count;
 	}
+	
+	public static <T> void logCollection(Iterable<T> c) {
+		Log.logln(dumpCollection(c));
+	}
+	
 	public static <T> void dumpCollection(Iterable<T> c, PrintStream out) {
 		out.println(dumpCollection(c));
 	}

### 2012-01-05 GUIErrorDetector/src/edu/washington/cs/detector/util/WALAUtils.java

@@ -188,6 +188,15 @@ public class WALAUtils {
 			}
 		}
 		
+		//also remove repetition
+		public static Collection<String> convertIClassToStrings(Collection<IClass> coll) {
+			Collection<String> strs = new LinkedHashSet<String>();
+			for(IClass ic : coll) {
+				strs.add(WALAUtils.getJavaFullClassName(ic));
+			}
+			return strs;
+		}
+		
 		public static Set<String> getUnloadedClasses(ClassHierarchy cha, Collection<String> jars) throws IOException {
 			Set<String> unloadedClasses = new LinkedHashSet<String>();
 			for(String jarFile : jars) {

### 2012-01-20 trunk/GUIErrorDetector/tests/edu/washington/cs/detector/experiments/eclipseplugin/TestPyDev.java
pydev is too large to analyze

@@ -21,6 +21,7 @@ import edu.washington.cs.detector.util.Log;
 import edu.washington.cs.detector.util.Utils;
 
 //project page: http://marketplace.eclipse.org/content/pydev-python-ide-eclipse
+//too large to analyze
 public class TestPyDev extends AbstractEclipsePluginTest {
 	
 	private String[] allPluginFiles = new String[] {
@@ -132,7 +133,7 @@ public class TestPyDev extends AbstractEclipsePluginTest {
 //		super.setCGType(CG.ZeroCFA);
 		super.setCGType(CG.OneCFA);
 		super.setCGType(CG.RTA);
-		super.setCGType(CG.ZeroCFA);
+//		super.setCGType(CG.ZeroCFA);
 		super.setThreadStartGuider(new CGTraverseSWTGuider());
 		super.setUIAnomalyGuider(new CGTraverseSWTGuider());
 		super.setPackages(new String[]{"com.python.pydev", "org.python.pydev"});

### 2012-01-20 trunk/GUIErrorDetector/paper/technique.tex
revise implementation and evaluation sections

@@
 or extension points.
-Existing call graph construction algorithms either suffer from incompleteness
-or imprecision.  To alleviate this problem, 
-We proposed a combined RTA
+Existing call graph construction algorithms suffer from incompleteness
+, imprecision, or both.  To alleviate this problem, 
+we proposed a combined RTA
 and k-CFA call graph construction algorithm in Section~\ref{sec:cg}.
 
+%we augument k-CFA with value set
+
 We also note that a static analysis may report false positives due
-to its conservative nature, or multiple warnings that acutally corrspond to
+to its conservative nature, or multiple warnings that actually correspond to
 the same error. In addition, some GUI applications may use
@@
 
+%In OO program, translate k-CFA as:
+%k-call-site sensitive interprocedural pointer
+%analysis with a k-context-sensitive heap and onthe-
+%fly call-graph construction
+%
+
 \begin{figure}[t]
@@
 orthogonal to the number of maintained sets).
+
+%this is wrong for k-CFA, k-CFA maintains several sets per expression, which k > 0
+%should cite Ben Livshit's paper on "Reflection analysis for Java"
+%Donot overclaim "say propose a new technique", instead, say "refine the technique"
+%also need to cite Yannis's paper on solving k-CFA paradox
+
+\textbf{need to describe why need to traverse from the UI entry, not just from the thread entry}
 
@@
 In Figure~\ref{fig:sampleandroid}, line 7 uses reflection to create a \CodeIn{Button}
-object by looking up its id declared in the XML file. Due to
-its limitation in handling reflection, the k-CFA algorithm
-will conclude that variable \CodeIn{button} at line 7 does not point to any
-concrete \CodeIn{Button} object. Thus, it will miss the call edge \CodeIn{setText}
-while processing line 11. On the other hand, a less precise algorithm like RTA~\cite{}
-can not solve this problem. By explicitly specifying that GUI objects
-like \CodeIn{Button} as declared in the XML file will be created, RTA maintains
-a global value set for those GUI object type, and concludes that the \CodeIn{button} variable
-at line 7 points to a concrete Button object. So the algorithm  adds a
-call edge \CodeIn{setText} to the call graph. However, using RTA for
-the whole program results in unnecessary precision loss. Note that,
-RTA may conclude that the \CodeIn{cachedViews} variable at line 2
-may point to any created \CodeIn{List} objects, despite the
-fact that \CodeIn{cachedViews} can only be a \CodeIn{LinkedList} object at line 12.
+object by looking up its id declared in the XML file. When this button
+is clicked, its event handling code (line 10 -- 13) updates the text and caches
+the current view to a list declared at line 2.
+
+Existing call graph algorithms either suffer from the problem of incompleteness
+or imprecision. The k-CFA algorithm performs points-to analysis with call
+graph construction interleavingly, and maintains a value set for every expression.
+For example, it concludes that variable \CodeIn{cachedViews} can only point
+to a \CodeIn{LinkedList} object and the method call \CodeIn{add} at line 12
+can only correspond to \CodeIn{LinkedList.add}. However, k-CFA fails to
+conclude that variable \CodeIn{button} declared at line 7 points to
+a \CodeIn{Button} object due to its limitation in dealing with reflection. Thus, k-CFA
+may miss the call graph edge corresponding to the method call \CodeIn{setText} at line 11. 
+On the other hand, using a coarse-grained algorithm like RTA~\cite{} can not still
+fully solve this problem. RTA adds an edge for a method invocation 
+to the call graph if an object of the receiver's type (or subtype)
+has been created.  By explicitly specifying that all GUI classes declared in the XML file will be created,
+RTA maintains a global value set for those GUI object type, and  adds a
+call edge \CodeIn{setText} to the call graph. However, RTA introduces 
+unnecessary precision loss: it may
+may conclude that the \CodeIn{cachedViews} variable at line 2
+point to any created \CodeIn{List} objects created somewhere else in the program, despite the
+fact that \CodeIn{cachedViews} can only be a \CodeIn{LinkedList} object.
 
@@
 call graph construction algorithm as shown in Figure~\ref{fig:cgalgorithm}.
-This algorithm uses the RTA algorithm to construct call graph for part of the program that
-uses reflection to creating GUI objects (to ensure call graph completeness), while still uses
-the k-CFA algorithm for the remaining part of the program (to avoid precision loss). Specifically,
-users provide a list of classes, which can either be encoded manually or
-automatically extracted from the XML configuration file, whose method invocations should be
-constructed in a RTA way. The algorithm maintains a global set for
-each  provided class, but a separate set for expressions of other
-types.  For the example in Figure~\ref{fig:sampleandroid}, this
+The algorithm shares the same spirit as k-CFA to maintain a value set
+for each expression. However, the only difference is that our
+algorithm uses a RTA-style treatment for constructing the value set for
+GUI classes: it parses the XML configuration file and explicitly
+adds a raw object to each declared GUI variable's value set. Thus,
+For the example in Figure~\ref{fig:sampleandroid}, this
 combined algorithm concludes that a \CodeIn{Button} object has been
@@
 point to a \CodeIn{LinkedList} object, avoiding unnecessary precision loss.
-
 %For desktop applications which have main method, it is straigtforward to apply
@@
 
-\subsubsection{Heuristic Filters and Annotations}
+\subsubsection{Heuristic Filtering and Annotation}
 \label{sec:heuristic}
 
-Static analysis exhaustively check possible error path; it may report
-paths that indicate the same bug. The potentially huge volume of
-reported warnings impose great burden for programmers to check
-its validity.
+A static analysis can exhaustively check possible error path; but may report
+paths that do not actually exist (i.e., false positives) or different paths
+ that correspond to the same error (i.e., redundant warnings). We devise
+a set of heuristics below to filter out likely false positives and redundant warnings.
+The first two heuristics are for reducing false positives, while the
+remaining ones are for removing redundant warnings.
 
-a few useful static heuristic filtering rules.
+%To remove those 
+%The potentially huge volume of
+%reported warnings impose great burden for programmers to check
+%its validity.
 
-\begin{itemize}
-\item \textbf{Method call chain sumbsumption}. Remove redundant
-results
+\begin{enumerate}
 
-\item \textbf{Remove system calls}. Method call chain involves typical
-system methods like \CodeIn{toString} are unlikely to reveal a real bug.
+\item \textbf{Filter Reports Containing Library Calls}. A
+reported method call chain involving common Library calls
+like \CodeIn{Object.toString} or \CodeIn{Runtime.shutDown} are unlikely to
+be buggy, and should be filtered. In addition, a method call chain that \textit{only}
+consists of library calls after the entry method is also unlikely
+to reveal a valid bug, since it has no interaction with the UI. 
+We encode a list of common library calls, and remove
+a report if it contaiins one of them.
+%Method call chain involves typical
+%system methods like \CodeIn{toString} are unlikely to reveal a real bug.
 
-\item \textbf{Method call chain with the same entry}. such
-call chains may reveal the same bug
+\item \textbf{Filter Reports With User-Annotated Methods}. Besides general
+library calls, users are also permitted
+to explicitly annotate methods that will never trigger an error.
+For example, the Android GUI framework provides a utility method 
+\CodeIn{runOnUIThread} to check whether the current thread is the UI thread
+before executing the code; if
+not, it executes the code on the UI thread using message passing.
+A reported call chain containing a annotated 
+can be safely removed.
+%method will never cause an
+%invalid thread error and should be removed.
 
-\item \textbf{Method call chain with the same tail}.  different ways
-to reach the same bug
+\item \textbf{Filter Lexically Redundant Reports}. One reported method call
+chain can lexically subsume another one. For example, suppose that a reported method
+call chain \CodeIn{a()} $\rightarrow$ \CodeIn{b()} $\rightarrow$ \CodeIn{c()}
+leads to a potential error, and another entry method \CodeIn{d()} calls \CodeIn{a()}.
+Therefore, a static analysis might also report another method call chain
+\CodeIn{d()} $\rightarrow$ \CodeIn{a()} $\rightarrow$ \CodeIn{b()} $\rightarrow$ \CodeIn{c()}
+that actually corresponds to the same error root as the previous one. In this case, 
+ removing the second call chain would not reduce the error detection capability:
+the first call chain already reveals the same error and is shorter 
+for programmers to interpret.
 
-\item \textbf{User-defined rules}.  to overcome the limitation
+\item \textbf{Filter Report With the Same $k$ Head Methods}. A method can call
+multiple methods that access GUI objects, such as:
+\begin{CodeOut}
+\begin{alltt}
+     public void m() \{
+         accessUIObject1();
+         accessUIObject2();
+     \}
+\end{alltt}
+\end{CodeOut}
+If method \CodeIn{m()} is invoked by a non-UI thread, two method call chains
+only different at last few method nodes will be reported:
 
-\end{itemize}
+\CodeIn{a()} $\rightarrow$ ...\CodeIn{Thread.start()} ... $\rightarrow$ \CodeIn{m()} $\rightarrow$ \CodeIn{accessUIObject1()} ...
 
-The above filtering rules are not sound, it may filter real bugs but works
-well in practice.
+\CodeIn{a()} $\rightarrow$ ...\CodeIn{Thread.start()} ... $\rightarrow$ \CodeIn{m()} $\rightarrow$ \CodeIn{accessUIObject2()} ...
 
-We also provide annotations for native methods which are beyond the ability
-of most static analyses
+In fact, these two call chains correspond to the same error root: knowning
+method \CodeIn{m()} is called by a non-UI thread is sufficient to understand and fix this error.
+This filter compares every two reported method call chains that share the same
+$k$ ($k$ is user-settable with a default value 5) head nodes, and removes the longer one.
+
+\item \textbf{Filter Report With the Same $k$ Tail Methods}. A method
+can have multiple callers, so that method call chains with the same tail are likely
+to represent different ways to trigger the same error. This filter compares every
+two reported method call chains that share the same 
+$k$ ($k$ is user-settable with a default value 5) tail nodes, and removes the longer one.
+
+\end{enumerate}
+
+All above filters are based on heuristics, and thus not sound in
+that it may filter real bugs. However, as we will show in
+the next experiment section, all these filters work well, and significantly
+reduces the number of false positives and redundant reports in practice.
+
+A GUI application may also use native methods to interact with the underlying
+operating system or platforms. However, native methods are often
+beyond the ability of a static analysis but should be considered to make
+the call graph more complete. To do so, we provide an annotation \CodeIn{@CallByNativeMethods}
+for users to specify which native methods may call the current method. For example,
+the following code snippet indicates that native methods \CodeIn{native1()} and \CodeIn{native2()}
+will call method \CodeIn{javaMethod()}.
+
+%\noindent 
+\CodeIn{@CallByNativeMethods(callers=\{"native1", "native2"\})}
+
+%\noindent
+\CodeIn{public void javaMethod() \{ ... \}}
+
+Our static analysis will take the call relationship as indicated by this
+annotation into consideration when traversing the call graph. In our experiment,
+we found such an annotation was useful: one real-world bug can only be reported
+with the user-provided annotations.
 
@@
 
-\item \textbf{UI accessing nodes:} unlike SWT, Swing does not explicitly check
-whether the current thread is the UI thread or not, when a GUI object is accessed. Except
-for three documented thread-safe method (\CodeIn{repaint}, XXXX), our technique
-treat all methods defined in each GUI object as UI accessing nodes.
+\item \textbf{UI accessing nodes:} as stated in Swing's documentation, methods
+in Swing GUI classes are not thread safe with three exceptions (\CodeIn{repaint()},
+\CodeIn{revalidate()}, and \CodeIn{invalidate()}). Thus, we
+treat all methods as defined in each GUI class as UI accessing nodes.
 
-\item \textbf{Safe methods: } similar to SWT, Swing provides two utility methods
-(\CodeIn{SwingUtilities.invokeLater} and \CodeIn{SwingUtilities.invokeDelay}) to pass messages to the UI thread. These two methods are regarded as safe methods.
+\item \textbf{Safe methods: }  Swing provides two helper methods
+(\CodeIn{SwingUti-\\lities.invokeLater} and \CodeIn{SwingUtilities.invokeAndWait}) to pass messages to the UI thread.
+We treat these two methods as safe methods.
 

### 2012-01-20 GUIErrorDetector/paper/evaluation.tex
paper tweak
revise implementation and evaluation sections

--- 2011-12-21 trunk/GUIErrorDetector/paper/evaluation.tex
@@
 \section{Empirical Evaluation}
+\label{sec:evaluation}
+
+%Our experiment investigate the followinig four research questions:
+
+%\begin{itemize}
+%\Item can our approach detect real bugs in multithreaded GUI applications?
+
+%\Item is the reflection-aware call graph construction algorithm useful?
+
+%\Item how effective is the proposed heuristic? is the reflection-aware call graph construction algorithm useful?
+%\end{itemize}
 
@@
 of our approach in detecting real bugs in multithreaded GUI applications, to 
-compare the combined RTA and k-CFA call graph construction algorithms
+compare the reflection-aware call graph construction algorithms
 with existing ones , and to evaluate the usefulness of the proposed 
- heuristics. First, we describe our subject programs, our computing
-environment and the experimental procedural. We then show that our technique
-detects bugs in real-world GUI applications on
-4 supported frameworks. We compare the combined RTA and k-CFA call graph
-construction algorithms with existing algorithms, showing it improves
-both precision and completeness of the constructed call graph.
- Finally, we show that the set of proposed heuristics are useful
-in removing redundant warnings and eliminate false positivies.
+ heuristics.
 
-\subsection{Subjects}
+First, we describe our subject programs (Section~\ref{sec:subjects}) and the experimental procedural (Section~\ref{sec:procedural}).
+We then show that our technique detects bugs in real-world GUI applications on
+four supported frameworks (Section~\ref{sec:errors}). We also compare our technique with
+a straightfoward approach in Section~\ref{sec:straightforward}. We further compare the reflection-aware call graph
+construction algorithms with existing algorithms, showing its usefulness (Section~\ref{sec:reflectionaware}).
+ Finally, we show that the set of proposed heuristics are effective
+in removing redundant warnings and eliminate false positivies (Section~\ref{sec:filters}).
+
+\subsection{Subject Programs}
+\label{sec:subjects}
+
+We use a set of open-source projects from Sourceforge, Google code and Eclipse plugin
+market as evaluation subjects. We choose subjects for each supported GUI framework
+as follows. We search the framework keywords (e.g., ``Java Swing'' or ``Java SWT'')
+in the above three source repositories, and select subjects based on the following
+criterias: first, the subject must be a multithread GUI application, not
+an open library. Second, the subject must undergone at least two years of active development,
+and is listed in the first 3 results pages based on popularity. This permits us
+to exclude all pre-mature subjects, which may contain obvious errors.
+
+The subjects used in our experiment are shown in Table~\ref{table:subjects}. Our
+subjects range from end-user applications, programming tools, to games. Specifically:
+
+\begin{itemize}
+\Item CelarFTP\footnote{\url{http://celerftp.sourceforge.net/}}
+and FileBunker\footnote{\url{http://filebunker.sourceforge.net/}} are two SWT desktop applications.
+CelarFTP implements a simple FTP client based on Java and SWT UI library, and
+FileBunker is a file backup application which uses one or more GMail accounts as its backup repository.
+
+\Item  AnyEdit\footnote{\url{http://andrei.gmxhome.de/anyedit/}}, FileSync4Eclipse\footnote{\url{andrei.gmxhome.de/filesync/}}, and
+EclipseRunner\footnote{\url{http://eclipserunnerplugin.googlecode.com/}} are three popular eclipse plugins.
+AnyEdit adds several new tools to  Eclipse editors, output consoles, and main menu. 
+FileSync4Eclipse is a file synchronisation tool to keep files outside of Eclipse projects in synchronized
+with Eclipse project files. EclipseRunner extends capability of running launch configurations in Eclipse IDE.
+
+\Item  S3dropbox\footnote{\url{http://s3dropbox.googlecode.com}} and SudokuPuzzleSolver\footnote{\url{http://sudokupuzzlesol.sourceforge.net/}}
+are two Swing desktop applications. S3dropbox implements a client that allows users
+to drag and drop files, which are then uploaded to their Amazon S3 accounts. SodokuPuzzleSolver
+computes Sodoku solutions efficiently using mutlithreading execution.
+
+\Item  MyTracks\footnote{\url{http://code.google.com/p/mytracks/}}, Fennec\footnote{\url{http://www.mozilla.org/en-US/mobile/}},
+and SGTPuzzles\footnote{\url{http://chris.boyle.name/projects/android-puzzles}} are three Android applications.
+MyTracks, developed by Google, records users' GPS tracks in outdoor activities, and provides
+interfaces to visualize them on Google Maps. Fennec, developed by Mozilla, is the Mozilla
+Firefox web browser for mobile devices. SGTPuzzles is a small logic single-player game.
+
+\end{itemize}
 
@@
 \hspace*{-0.2cm}
-\begin{tabular}{|l||c|c|c|c|}
+\begin{tabular}{|p{4.4cm}||c|c|c|c|}
 \hline
- Program (version) & LOC & Classes & Methods & Threads \\
+ Program (version) & LOC & Classes & Methods \\
 \hline \hline
-\multicolumn{5}{|l|}{SWT desktop applications}   \\
+\multicolumn{4}{|l|}{SWT desktop applications}   \\
  \hline
- xxx &  xxxx &  xx &  xxx & xx \\
+ CelarFTP (3.0 alpha) &  2293 &  20 &  165  \\
  \hline
- xxx &  xxxx &  xx &  xxx & xx \\
- \hline
- xxx &  xxxx &  xx &  xxx & xx \\
+ FileBunker (1.1.2)&  14237 &  150 &  1106  \\
  \hline
  \hline
-\multicolumn{5}{|l|}{Eclipse plugins}   \\
+\multicolumn{4}{|l|}{Eclipse plugins}   \\
  \hline
- xxx &  xxxx &  xx &  xxx & xx \\
+ EclipseRunner (1.1.0) &  3101 &  48 &  354\\
  \hline
- xxx &  xxxx &  xx &  xxx & xx \\
+ FileSync (1.4.0)&  7374 &  36 &  510 \\
  \hline
- xxx &  xxxx &  xx &  xxx & xx \\
+ AnyEdit (2.4.0)&  11077 &  74 &  649 \\
  \hline
  \hline
-\multicolumn{5}{|l|}{Swing desktop applications}   \\
+\multicolumn{4}{|l|}{Swing desktop applications}   \\
  \hline
- xxx &  xxxx &  xx &  xxx & xx \\
+ S3dropbox (1.7) &  2353 &  42  &  224 \\
  \hline
- xxx &  xxxx &  xx &  xxx & xx \\
- \hline
- xxx &  xxxx &  xx &  xxx & xx \\
+ Sudoku Solver (1.06)&  3555 &  10 &  62 \\
  \hline
  \hline
-\multicolumn{5}{|l|}{Android mobile applications}   \\
+\multicolumn{4}{|l|}{Android mobile applications}   \\
  \hline
- xxx &  xxxx &  xx &  xxx & xx \\
+ SGTPuzzler (v9306.11)&  2220 &  16 &  148 \\
  \hline
- xxx &  xxxx &  xx &  xxx & xx \\
+ Fennec (10.0.a.rc3)&  8577 &  51 &  620 \\
  \hline
- xxx &  xxxx &  xx &  xxx & xx \\
+ MyTracks (1.1.13.rc4)&  20297 &  143 &  1374 \\
+\hline
+\multicolumn{4}{l}{}   \\
+\hline
+ GUI framework (version) & LOC & Classes & Methods  \\
+\hline \hline
+ SWT (3.6.2)&  20297 &  143 &  1374  \\
+\hline
+ Eclipse plugin development (3.6.2)&  20297 &  143 &  1374  \\
+\hline
+Swing (1.6)&  20297 &  143 &  1374  \\
+\hline
+ Android (3.6)&  20297 &  143 &  1374  \\
+\hline
+\end{tabular}
+
+\end{center}
+\vspace{-15pt}
+\Caption{{\label{table:subjects} Open source programs
+used in our evaluation. Column ``LOC'' is the number of lines
+of code, as counted by LOCC~\cite{}.  Each program is analyzed
+together with its dependent GUI framework, as listed in
+the bottom table.} }
+\end{table}
+
+\subsection{Procedural}
+\label{sec:procedural}
+
+We run our tool on each subject with three call graph construction
+algorithms: RTA~\cite{}, 0-CFA, and 1-CFA~\cite{}.  When running
+each call graph construction algorithm on Android applications, we
+use two configurations: with and without taming reflection (Section~\ref{}).
+$k$-CFA ($k >$ 1) algorithm
+does not scale to large programs, and thus is not used in this experiment
+
+SGTPuzzler is the only subject that uses native methods to interact with
+underlying operating systems. Thus, we manually added XXX \CodeIn{@CalledByNative}
+annotations after inspecting its source code. In addition, two subjects XXXX and XXX use a self-defined
+way to interact with the GUI framework. In this experiment, none of the paper
+authors was faimilar with the subjects; but we found it is quite easy
+to add extra those annotations and heuristic filters and finished these
+manual parts in less than 20 minutes.
+
+After provided with necessary annotations and heuristic filters,
+our tool works in a fully-automatic, push-bottom manner. For each output
+warning, we manually determine its validity by either searching the
+bug repository to check whether the same bug has been reported before,
+or submitting a new bug report, or writing a test driver to reproduce
+the error.
+
+\begin{table*}[ht]
+\begin{center}
+ \fontsize{9pt}{\baselineskip}\selectfont
+\hspace*{-0.2cm}
+\setlength{\tabcolsep}{.75\tabcolsep}
+\begin{tabular}{|l||c|c|c||c|c|c||c|c|c||c|c|}
+\hline
+ Subject&  \multicolumn{9}{|c||}{Our Technique} & \multicolumn{2}{|c|}{The Approach in}  \\
+\cline{2-10}
+ Program  &  \multicolumn{3}{|c|}{RTA / reflection aware}& \multicolumn{3}{|c|}{0-CFA / reflection aware} & \multicolumn{3}{|c||}{1-CFA / reflection aware} & \multicolumn{2}{|c|}{Section~\ref{sec:straightforward}}  \\
+\cline{2-12}
+ & CG Size & \#Warning & \#Bug & CG Size & \#Warning & \#Bug & CG Size & \#Warning & \#Bug & \#Warning & \#Bug\\
+\hline \hline
+\multicolumn{12}{|l|}{SWT desktop applications}   \\
+ \hline
+ xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx& xx & xx \\
+ \hline
+ xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx& xx & xx \\
+ \hline
+ xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx& xx & xx \\
+ \hline
+ \hline
+\multicolumn{12}{|l|}{Eclipse plugins}   \\
+ \hline
+ xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx& xx & xx \\
+ \hline
+ xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx& xx & xx \\
+ \hline
+ xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx& xx & xx \\
+ \hline
+ \hline
+\multicolumn{12}{|l|}{Swing desktop applications}   \\
+ \hline
+ xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx& xx & xx \\
+ \hline
+ xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx& xx & xx \\
+ \hline
+ xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx& xx & xx \\
+ \hline
+ \hline
+\multicolumn{12}{|l|}{Android mobile applications}   \\
+ \hline
+ xxx &  xxxx / xxxx &  xx / xxxx &  xxx / xxxx & xx /xxx & xx / xxxx  & xx / xxxx& xx / xxx & xxxx / xxx  & xxxx / xxx& xx & xx \\
+ \hline
+ xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx& xx & xx \\
+ \hline
+ xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx& xx & xx \\
 \hline
@@
 \vspace{-15pt}
-\Caption{{\label{table:subjects}Subject Programs.} }
-\end{table}
-
-\subsection{Procedural}
+\Caption{{\label{table:results}Experimental results in finding errors
+in multithreaded GUI programs. Column ``CG Size'' shows the
+call graph size in terms of node number. Column ``\#Warning''
+shows the number of warnings issued by our tool. Column ``\#Bug'' shows
+the actual bugs found. Columns ``RTA / reflection aware '', ``0-CFA / reflection aware'',
+and ``1-CFA / reflection aware'' show the results of using different
+call graph construction algorithms with (before ``/'') or without (after ``/'')
+taming the reflection on Android applications. In each cell of the table
+for Android applications, a slash ``/'' separates the result of
+using normal call graph construction algorithm and the reflection-aware
+call graph construction algorithm. As a comparison, the
+results of a straightforward approach (Section~\ref{sec:straightforward}) are show at the far right.} }
+\end{table*}
 
 \subsection{Results}
+\label{sec:results}
 
-\begin{table*}[t]
-\begin{center}
- \fontsize{9pt}{\baselineskip}\selectfont
-\hspace*{-0.2cm}
-\begin{tabular}{|l||c|c|c||c|c|c||c|c|c|}
-\hline
- Program  &  \multicolumn{3}{|c|}{RTA}& \multicolumn{3}{|c|}{0-CFA / Combined RTA and 0-CFA} & \multicolumn{3}{|c|}{1-CFA / Combined RTA and 1-CFA}  \\
-\cline{2-10}
- (version) & CG Size & \#Warning & \#Bug & CG Size & \#Warning & \#Bug & CG Size & \#Warning & \#Bug\\
-\hline \hline
-\multicolumn{10}{|l|}{SWT desktop applications}   \\
- \hline
- xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx \\
- \hline
- xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx \\
- \hline
- xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx \\
- \hline
- \hline
-\multicolumn{10}{|l|}{Eclipse plugins}   \\
- \hline
- xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx \\
- \hline
- xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx \\
- \hline
- xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx \\
- \hline
- \hline
-\multicolumn{10}{|l|}{Swing desktop applications}   \\
- \hline
- xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx \\
- \hline
- xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx \\
- \hline
- xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx \\
- \hline
- \hline
-\multicolumn{10}{|l|}{Android mobile applications}   \\
- \hline
- xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx \\
- \hline
- xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx \\
- \hline
- xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx \\
-\hline
-\end{tabular}
-\end{center}
-\vspace{-15pt}
-\Caption{{\label{table:results}Experimental results.} }
-\end{table*}
+Table~\ref{table:results} show our results in finding errors in
+multithreaded GUI applications, and Table~\ref{table:filters} show
+the results of applying each heuristic filter.
 
 \subsubsection{Errors in Multithreaded GUI}
+\label{sec:errors}
+
+Swing is a single-threaded GUI toolkit, and is not thread-safe. 
+As the official documentation states, all Swing code must be executed in the UI-thread and
+invoking Swing code from multiple threads risks thread interference or memory-consistency errors.
+
+Since Swing does not provide any run-time checks for invalid thread access and, most of the time,
+programmers can get away with an apparently ``well behaved'' Swing GUI that actually breaks the
+single-thread rule.
+
+Example in Swing
+\begin{figure}[t]
+\begin{CodeOut}
+\begin{alltt}
+/* In class: com.tomczarniecki.s3.gui.DeleteBucketAction */
+59.private void deleteBucket() \{
+60.    executor.execute(new Runnable() \{
+61.        public void run() \{
+62.            try \{
+63.                controller.deleteCurrentBucket();
+64.            \} catch (Exception e) \{
+65.                logger.info("Delete failed", e);
+66.                deleteError(); 
+67.            \}
+68.       \}
+69.    \});
+70.\}
+
+77.private void deleteError() \{
+78.    String text = "Cannot delete folder .....";
+79.    display.showErrorMessage("Delete failed", 
+        String.format(text, controller.getSelectedBucketName())); 
+80.\}
+\end{alltt}
+\end{CodeOut}
+\vspace*{-2.0ex} \Caption{{\label{fig:swingerror} A
+potential invalid thread error reported by our tool
+in the S3dropbox Swing application. The error occurs when
+the invocation of \CodeIn{deleteCurrentBucket} at line 63 throws
+an exception, which lead to the \CodeIn{deleteError} method
+access a Swing GUI object \CodeIn{display} at line 79 from
+a non-UI thread. This error has been confirmed by S3dropbox developers.
+}} %\vspace{-5mm}
+\end{figure}
+
+Example in  Eclipse plugin
+\begin{figure}[t]
+\begin{CodeOut}
+\begin{alltt}
+179.private void initializeResourceChangeListener() \{
+180.  ResourcesPlugin.getWorkspace().addResourceChangeListener(
+        new IResourceChangeListener() \{
+181.      public void resourceChanged(IResourceChangeEvent event) \{
+182.        refresh();
+183.      \}
+184.  \}, IResourceChangeEvent.POST\_CHANGE);
+185.\}
+
+414.public void refresh() \{
+415.  getViewer().refresh();
+416.\}
+\end{alltt}
+\end{CodeOut}
+\vspace*{-2.0ex} \Caption{{\label{fig:pluginerror} A
+potential invalid thread error reported by our tool
+in the EclipseRunner plugin. The \CodeIn{IResourceChangeListener} object
+added at line 180 is invoked by a non-UI thread, and the
+callback method \CodeIn{resourceChanged} calls the \CodeIn{refresh}
+method at line 414. However, the \CodeIn{refresh} method
+directly accesses the GUI objects (at line 415) and triggers the error.
+This error has been reported by other users 13 months after the
+buggy code was checked in, and fixed by developers.
+}} %\vspace{-5mm}
+\end{figure}
+
+\vspace{1mm}
+
+\noindent \textbf{\textit{Summary.}}
+
+\subsubsection{Comparison with a Straightforward Approach}
+\label{sec:straightforward}
+
+As we mentioned in Section~\ref{sec:finding}, a standard way to avoid
+invalid thread access errors is to wrap every GUI access code
+with message passing methods (i.e., the safe methods). Thus, a
+straightforward way to detect potential invalid error
+is to check every method to determine whether all GUI-accessing
+are probably wrapping by safe methods. If not, this
+approach issues warnings.
+
+We implemented this naive approach and experimentally compared its
+results with the technique presented in Section~\ref{}.
+
+Algorithm:
+
+1. find all UI direct accessing methods
+
+2. to see is this methods called by non-safe
+
+The primary difference
+
+\vspace{1mm}
+
+\noindent \textbf{\textit{Summary.}}
 
 \subsubsection{Call Graph Construction Algorithms}
+\label{sec:reflectionaware}
+
+\vspace{1mm}
+
+\noindent \textbf{\textit{Summary.}}
 
 \subsubsection{Heuristic Filters}
+\label{sec:filters}
 
+\vspace{1mm}
+
+\noindent \textbf{\textit{Summary.}}
 Heuristic filter, effective.
@@
 \vspace{-15pt}
-\Caption{{\label{table:filters}Experimental results after applying heuristic filters.} }
+\Caption{{\label{table:filters}Number of warnings after applying a set of
+heuristic filters (Section~\ref{}). Column ``\#Warning $F_i$''
+represents the number of remaining warnings after applying
+filters 1 -- $i$, and the number of last column is taken
+from Table~\ref{} (Subcolumn ``\#Warning'' under column ``1-CFA / with taming reflection'').} }
 \end{table}
@@
 
-Runs in practical time, mention the largest time cost in the program.
+Our tool runs in a practical amount of time. Our evaluations
+were conducted on a 2.67GHz Intel Core PC with 4GB
+physical memory (1GB is allocated for JVM), running Fedora 16.
+For the largest subject, xxx, our tool finished the whole analysis
+within 286 seconds using the most expensive call graph construction
+algorithm (the reflection-aware 1-CFA analysis). Analyzing
+other subjects using different algorithms took less time.
+The performance has not been tuned, and we believe
+that it could be improved further.
 
-The average analysis time per / bug
+Our experiments also demonstrate that our approach has good scalability.
+Our tool has analyzed xxx LOC in total, and together with all dependent libraries,
+the largest subject our approach can analyze and detect errors has
+over XXX LOC, xx classes, and xxx methods.
 
-\subsection{Discussion}
+\subsection{Discussions}
 
 \subsubsection{Threats to Validity}
+
+Our evaluation was limited in several ways. First, the studied
+subjects were selected with a bias towards popularity. Second,
+our tool cannot compute call relationships
+for inter-process communication between components. Missing
+Future work could evaluate our technique on more subjects, and
+investigate the false negative rate.
+
+\subsubsection{Experimental Conclusions}
+Findings: programmers have noted this problem, but often overlook special cases like error handle, subtype
+
+ Reporting on violations is fine but what is more important are the pracitces and patterns that need to be adopted to make it easier to avoid the issue in the first place.
+That is why there is a Worker interface in this project

### 2012-01-20 GUIErrorDetector/paper/implementation.tex
revise implementation and evaluation sections

@@
 errors, and scales to realistic programs.  
-Optionally, the user may specify additional heuristics to guide call graph
+Optionally, users may specify additional heuristics to guide call graph
 traverse, and annotate call relationships for native methods (Section~\ref{sec:heuristic}).
@@
 all dependent libraries (e.g., \CodeIn{rt.jar} and \CodeIn{android.jar})
-into analysis. Since Android applications are often fully encrypted and shipped in Dalvik
-bytecode as a single apk file, our implementation first uses
+into analysis. We implement the reflection taming algorithm (Section~\ref{})
+using WALA's \textit{bypass logic}. Our tool parses the configuration file
+in an Android application and modifies the bytecode to replace all
+reflection calls with object creation instructions.
+Since Android applications are often fully encrypted and shipped in Dalvik
+bytecode as a single apk file, our tool first uses
 android-apktool\footnote{\url{http://code.google.com/p/android-apktool/}} to
@@
 with real class files.
+
+%Static Single Assignment (SSA) transformation to get limited flow sensitivity

### 2012-01-21 trunk/GUIErrorDetector/paper/evaluation.tex
more experiment

@@
 \hspace*{-0.2cm}
-\begin{tabular}{|l||c|c|c|c|}
+\begin{tabular}{|p{4.4cm}||c|c|c|c|}
 \hline
- Program (version) & LOC & Classes & Methods & Threads \\
+ Program (version) & LOC & Classes & Methods \\
 \hline \hline
-\multicolumn{5}{|l|}{SWT desktop applications}   \\
+\multicolumn{4}{|l|}{SWT desktop applications}   \\
  \hline
- xxx &  xxxx &  xx &  xxx & xx \\
+ CelarFTP (3.0 alpha) &  2293 &  20 &  165  \\
  \hline
- xxx &  xxxx &  xx &  xxx & xx \\
- \hline
- xxx &  xxxx &  xx &  xxx & xx \\
+ FileBunker (1.1.2)&  14237 &  150 &  1106  \\
  \hline
  \hline
-\multicolumn{5}{|l|}{Eclipse plugins}   \\
+\multicolumn{4}{|l|}{Eclipse plugins}   \\
  \hline
- xxx &  xxxx &  xx &  xxx & xx \\
+ EclipseRunner (1.1.0) &  3101 &  48 &  354\\
  \hline
- xxx &  xxxx &  xx &  xxx & xx \\
+ FileSync (1.4.0)&  7374 &  36 &  510 \\
  \hline
- xxx &  xxxx &  xx &  xxx & xx \\
+ AnyEdit (2.4.0)&  11077 &  74 &  649 \\
  \hline
  \hline
-\multicolumn{5}{|l|}{Swing desktop applications}   \\
+\multicolumn{4}{|l|}{Swing desktop applications}   \\
  \hline
- xxx &  xxxx &  xx &  xxx & xx \\
+ S3dropbox (1.7) &  2353 &  42  &  224 \\
  \hline
- xxx &  xxxx &  xx &  xxx & xx \\
- \hline
- xxx &  xxxx &  xx &  xxx & xx \\
+ Sudoku Solver (1.06)&  3555 &  10 &  62 \\
  \hline
  \hline
-\multicolumn{5}{|l|}{Android mobile applications}   \\
+\multicolumn{4}{|l|}{Android mobile applications}   \\
  \hline
- xxx &  xxxx &  xx &  xxx & xx \\
+ SGTPuzzler (v9306.11)&  2220 &  16 &  148 \\
  \hline
- xxx &  xxxx &  xx &  xxx & xx \\
+ Fennec (10.0.a.rc3)&  8577 &  51 &  620 \\
  \hline
- xxx &  xxxx &  xx &  xxx & xx \\
+ MyTracks (1.1.13.rc4)&  20297 &  143 &  1374 \\
+\hline
+\multicolumn{4}{l}{}   \\
+\hline
+ GUI framework (version) & LOC & Classes & Methods  \\
+\hline \hline
+ SWT (3.6.2)&  20297 &  143 &  1374  \\
+\hline
+ Eclipse plugin development (3.6.2)&  20297 &  143 &  1374  \\
+\hline
+Swing (1.6)&  20297 &  143 &  1374  \\
+\hline
+ Android (3.6)&  20297 &  143 &  1374  \\
+\hline
+\end{tabular}
+
+\end{center}
+\vspace{-15pt}
+\Caption{{\label{table:subjects} Open source programs
+used in our evaluation. Column ``LOC'' is the number of lines
+of code, as counted by LOCC~\cite{}.  Each program is analyzed
+together with its dependent GUI framework, as listed in
+the bottom table.} }
+\end{table}
+
+\subsection{Procedural}
+\label{sec:procedural}
+
+We run our tool on each subject with three call graph construction
+algorithms: RTA~\cite{}, 0-CFA, and 1-CFA~\cite{}.  When running
+each call graph construction algorithm on Android applications, we
+use two configurations: with and without taming reflection (Section~\ref{}).
+$k$-CFA ($k >$ 1) algorithm
+does not scale to large programs, and thus is not used in this experiment
+
+SGTPuzzler is the only subject that uses native methods to interact with
+underlying operating systems. Thus, we manually added XXX \CodeIn{@CalledByNative}
+annotations after inspecting its source code. In addition, two subjects XXXX and XXX use a self-defined
+way to interact with the GUI framework. In this experiment, none of the paper
+authors was faimilar with the subjects; but we found it is quite easy
+to add extra those annotations and heuristic filters and finished these
+manual parts in less than 20 minutes.
+
+After provided with necessary annotations and heuristic filters,
+our tool works in a fully-automatic, push-bottom manner. For each output
+warning, we manually determine its validity by either searching the
+bug repository to check whether the same bug has been reported before,
+or submitting a new bug report, or writing a test driver to reproduce
+the error.
+
+\begin{table*}[ht]
+\begin{center}
+ \fontsize{9pt}{\baselineskip}\selectfont
+\hspace*{-0.2cm}
+\setlength{\tabcolsep}{.65\tabcolsep}
+\begin{tabular}{|l||c|c|c||c|c|c||c|c|c||c|c|}
+\hline
+ Subject&  \multicolumn{9}{|c||}{Our Technique} & \multicolumn{2}{|c|}{The Approach in}  \\
+\cline{2-10}
+ Program  &  \multicolumn{3}{|c|}{RTA / reflection aware}& \multicolumn{3}{|c|}{0-CFA / reflection aware} & \multicolumn{3}{|c||}{1-CFA / reflection aware} & \multicolumn{2}{|c|}{Section~\ref{sec:straightforward}}  \\
+\cline{2-12}
+ & CG Size & \#Warning & \#Bug & CG Size & \#Warning & \#Bug & CG Size & \#Warning & \#Bug & \#Warning & \#Bug\\
+\hline \hline
+\multicolumn{12}{|l|}{SWT desktop applications}   \\
+ \hline
+ xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx& xx & xx \\
+ \hline
+ xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx& xx & xx \\
+ \hline
+ xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx& xx & xx \\
+ \hline
+ \hline
+\multicolumn{12}{|l|}{Eclipse plugins}   \\
+ \hline
+ xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx& xx & xx \\
+ \hline
+ xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx& xx & xx \\
+ \hline
+ xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx& xx & xx \\
+ \hline
+ \hline
+\multicolumn{12}{|l|}{Swing desktop applications}   \\
+ \hline
+ S3dropbox &  xxxx &  xx &  xxx & xx & xx & xx& xx & 1 & 1 & 210 & xx \\
+ \hline
+  Sudoku Solver&  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx& 356 & xx \\
+ \hline
+ \hline
+\multicolumn{12}{|l|}{Android mobile applications}   \\
+ \hline
+ xxx &  xxxx / xxxx &  xx / xxxx &  xxx / xxxx & xx /xxx & xx / xxxx  & xx / xxxx& xx / xxx & xxxx / xxx  & xxxx / xxx& xx & xx \\
+ \hline
+ xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx& xx & xx \\
+ \hline
+ xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx& xx & xx \\
 \hline
@@
 \vspace{-15pt}
-\Caption{{\label{table:subjects}Subject Programs.} }
-\end{table}
-
-\subsection{Procedural}
+\Caption{{\label{table:results}Experimental results in finding errors
+in multithreaded GUI programs. Column ``CG Size'' shows the
+call graph size in terms of node number. Column ``\#Warning''
+shows the number of warnings issued by our tool. Column ``\#Bug'' shows
+the actual bugs found. Columns ``RTA / reflection aware '', ``0-CFA / reflection aware'',
+and ``1-CFA / reflection aware'' show the results of using different
+call graph construction algorithms with (before ``/'') or without (after ``/'')
+taming the reflection on Android applications. In each cell of the table
+for Android applications, a slash ``/'' separates the result of
+using normal call graph construction algorithm and the reflection-aware
+call graph construction algorithm. As a comparison, the
+results of a straightforward approach (Section~\ref{sec:straightforward}) are show at the far right.} }
+\end{table*}
 
 \subsection{Results}
+\label{sec:results}
 
-\begin{table*}[t]
-\begin{center}
- \fontsize{9pt}{\baselineskip}\selectfont
-\hspace*{-0.2cm}
-\begin{tabular}{|l||c|c|c||c|c|c||c|c|c|}
-\hline
- Program  &  \multicolumn{3}{|c|}{RTA}& \multicolumn{3}{|c|}{0-CFA / Combined RTA and 0-CFA} & \multicolumn{3}{|c|}{1-CFA / Combined RTA and 1-CFA}  \\
-\cline{2-10}
- (version) & CG Size & \#Warning & \#Bug & CG Size & \#Warning & \#Bug & CG Size & \#Warning & \#Bug\\
-\hline \hline
-\multicolumn{10}{|l|}{SWT desktop applications}   \\
- \hline
- xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx \\
- \hline
- xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx \\
- \hline
- xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx \\
- \hline
- \hline
-\multicolumn{10}{|l|}{Eclipse plugins}   \\
- \hline
- xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx \\
- \hline
- xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx \\
- \hline
- xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx \\
- \hline
- \hline
-\multicolumn{10}{|l|}{Swing desktop applications}   \\
- \hline
- xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx \\
- \hline
- xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx \\
- \hline
- xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx \\
- \hline
- \hline
-\multicolumn{10}{|l|}{Android mobile applications}   \\
- \hline
- xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx \\
- \hline
- xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx \\
- \hline
- xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx \\
-\hline
-\end{tabular}
-\end{center}
-\vspace{-15pt}
-\Caption{{\label{table:results}Experimental results.} }
-\end{table*}
+Table~\ref{table:results} show the errors in
+our subject programs, and Table~\ref{table:filters} show
+the effect of applying each heuristic filter.
 
 \subsubsection{Errors in Multithreaded GUI}
+\label{sec:errors}
+
+characteristic of errors in various subjects
+
+False positive rate, and why?
+
+redundant rate
+
+response
+
+Swing
+
+Swing is a single-threaded GUI toolkit, and is not thread-safe. 
+As the official documentation states, all Swing code must be executed in the UI-thread and
+invoking Swing code from multiple threads risks thread interference or memory-consistency errors.
+
+Since Swing does not provide any run-time checks for invalid thread access and, most of the time,
+programmers can get away with an apparently ``well behaved'' Swing GUI that actually breaks the
+single-thread rule.
+
+Example in Swing
+\begin{figure}[t]
+\begin{CodeOut}
+\begin{alltt}
+/* In class: com.tomczarniecki.s3.gui.DeleteBucketAction */
+59.private void deleteBucket() \{
+60.    executor.execute(new Runnable() \{
+61.        public void run() \{
+62.            try \{
+63.                controller.deleteCurrentBucket();
+64.            \} catch (Exception e) \{
+65.                logger.info("Delete failed", e);
+66.                deleteError(); 
+67.            \}
+68.       \}
+69.    \});
+70.\}
+
+77.private void deleteError() \{
+78.    String text = "Cannot delete folder .....";
+79.    display.showErrorMessage("Delete failed", 
+        String.format(text, controller.getSelectedBucketName())); 
+80.\}
+\end{alltt}
+\end{CodeOut}
+\vspace*{-2.0ex} \Caption{{\label{fig:swingerror} A
+potential invalid thread error reported by our tool
+in the S3dropbox Swing application. The error occurs when
+the invocation of \CodeIn{deleteCurrentBucket} at line 63 throws
+an exception, which lead to the \CodeIn{deleteError} method
+access a Swing GUI object \CodeIn{display} at line 79 from
+a non-UI thread. This error has been confirmed by S3dropbox developers.
+}} %\vspace{-5mm}
+\end{figure}
+
+Example in  Eclipse plugin
+\begin{figure}[t]
+\begin{CodeOut}
+\begin{alltt}
+179.private void initializeResourceChangeListener() \{
+180.  ResourcesPlugin.getWorkspace().addResourceChangeListener(
+        new IResourceChangeListener() \{
+181.      public void resourceChanged(IResourceChangeEvent event) \{
+182.        refresh();
+183.      \}
+184.  \}, IResourceChangeEvent.POST\_CHANGE);
+185.\}
+
+414.public void refresh() \{
+415.  getViewer().refresh();
+416.\}
+\end{alltt}
+\end{CodeOut}
+\vspace*{-2.0ex} \Caption{{\label{fig:pluginerror} A
+potential invalid thread error reported by our tool
+in the EclipseRunner plugin. The \CodeIn{IResourceChangeListener} object
+added at line 180 is invoked by a non-UI thread, and the
+callback method \CodeIn{resourceChanged} calls the \CodeIn{refresh}
+method at line 414. However, the \CodeIn{refresh} method
+directly accesses the GUI objects (at line 415) and triggers the error.
+This error has been reported by other users 13 months after the
+buggy code was checked in, and fixed by developers.
+}} %\vspace{-5mm}
+\end{figure}
+
+\vspace{1mm}
+
+\noindent \textbf{\textit{Summary.}}Our technique finds real errors
+in multithreaded GUI applications on four different frameworks with
+an acceptable false positive rate.
+
+\subsubsection{Comparison with a Straightforward Approach}
+\label{sec:straightforward}
+
+As we mentioned in Section~\ref{sec:finding}, a standard way to avoid
+invalid thread access errors is to wrap every GUI access code
+with message passing methods (i.e., the safe methods). Thus, a
+straightforward way to detect potential invalid error
+is to check every method to determine whether all GUI-accessing code
+is probably wrapping by safe methods. This approach
+issues a warning for every violation. 
+%If not, this approach issues warnings.
+
+We implemented this straightforward approach and experimentally compared its
+effectiveness with the technique presented in Section~\ref{}.
+The far right column in Table~\ref{table:results} shows its result.
+The results show that this straightforward approach can identified every
+error as our technique does, but issues a tremendous number of false
+positives. The primary reason is that this simple approach
+does not globally reason about calling relationship between
+threads, UI-accessing methods, and safe methods, thus it often incorrectly
+classifies GUI accessing code which will never be executed
+in a non-UI thread as errenous. Furthermore, our technique
+outputs a method call chain in the error report, which can help
+developers understand how an invalid thread access error is triggered.
+
+\vspace{1mm}
+
+\noindent \textbf{\textit{Summary.}} Our technique provides
+richer contextually information for a potential error, and 
+is significantly more precise than the straightforward approach.
 
 \subsubsection{Call Graph Construction Algorithms}
+\label{sec:reflectionaware}
+
+We compare three call graph construction algorithms, RTA, 0-CFA, and 1-CFA,
+in our experiments. As shown in Table~\ref{table:results},  XXX found
+more errors with less warnings than the XXX and XXXX algorithms. This
+is because RTA and 0-CFA do not consider the context XXX, and it may
+mix the same methods called by different callers. Although the call graphs
+built by 1-CFA are significantly larger, XXX, the algorithm still runs
+in a practical amouont of time as presented in Section~\ref{}. For example,
+our tool finished building the call graph for the largest subject (xxx)
+within xxx minutes.
+
+The results in Table~\ref{table:results} also shown that using a reflection-aware
+call graph construction algorithm is critical in finding errors in Android
+applications. None of the errors in the studied Android applications
+can be found by using normal call graph construction algorithms, because their 
+limitation in handling reflection.
+
+\vspace{1mm}
+
+\noindent \textbf{\textit{Summary.}} XX The 1-CFA call graph construction
+algorithm is more effective in finding errors. XXX. Our reflection-aware call
+graph construction algorithm is useful to find errors in
+Android applications.
 
 \subsubsection{Heuristic Filters}
+\label{sec:filters}
 
+We measure the effectiveness of the proposed heuristic filters of
+Section~\ref{} via the number of removed warnings.
+
+Table~\ref{table:filters} tabulates the results. The results show that
+our technique outputs thousnads of warnings for each subject, due to
+the conservative nature of static analysis.  However, the
+set of proposed heuristic filters are highly effectively. They
+ reduce the false positive numbers and redundant warnings by up to a factor of
+XXX. Specifically, filters $XX_i$ and $XX_j$  identified xx\% of
+the warnings as likely false positives, and filters $YY_i$
+and $YY_j$ identified YY\% of the warnings as redundant warnings.
+We further manually check each filtered warning, and found no
+real errors have been removed.
+
+\vspace{1mm}
+
+\noindent \textbf{\textit{Summary.}} Although a static analysis may
+issue false postivies or redundant reports, a set of well-designed
+heuristics can still remove most of them.
 Heuristic filter, effective.
@@
 \vspace{-15pt}
-\Caption{{\label{table:filters}Experimental results after applying heuristic filters.} }
+\Caption{{\label{table:filters}Number of warnings after applying a set of
+heuristic filters (Section~\ref{}). Column ``\#Warning $F_i$''
+represents the number of remaining warnings after applying
+filters 1 -- $i$, and the number of last column is taken
+from Table~\ref{} (Subcolumn ``\#Warning'' under column ``1-CFA / with taming reflection'').} }
 \end{table}
+
+\subsection{Discussions}
+
+We next discuss several important issues in our evaluation.
 
@@
 
-Runs in practical time, mention the largest time cost in the program.
+Our tool runs in a practical amount of time. Our evaluations
+were conducted on a 2.67GHz Intel Core PC with 4GB
+physical memory (1GB is allocated for JVM), running Fedora 16.
+For the largest subject, xxx, our tool finished the whole analysis
+within 286 seconds using the most expensive call graph construction
+algorithm (the reflection-aware 1-CFA analysis). Analyzing
+other subjects using different algorithms took less time.
+The performance has not been tuned, and we believe
+that it could be improved further.
 
-The average analysis time per / bug
-
-\subsection{Discussion}
+Our experiments also demonstrate that our approach has good scalability.
+Our tool has analyzed xxx LOC in total, and together with all dependent libraries,
+the largest subject our approach can analyze and detect errors has
+over XXX LOC, xx classes, and xxx methods.
 
 \subsubsection{Threats to Validity}
+
+There are two major threats to validity in our evaluation. 
+The major threat is the degree to which the subject programs
+used in our experiment are representative of true practice.
+In our evaluation, the studied subjects were selected with a bias towards popularity from
+three open-source repositories. Another threat is that we only employed three
+well-known call graph construction algorithms (i.e., RTA, 0-CFA, and 1-CFA) 
+in our implementation. It is still unknown whether using other 
+call graph construction algorithms such XFA~\cite{} may achieve better results.
+
+\subsubsection{Limitations}
+
+Our technique is limited in two aspects. First, it only considers
+non-UI threads that are spawned by the UI-thread after the GUI
+is initialized, and ignores other possible non-UI threads
+that are created during the pre-initialization GUI work. One way
+to remedy this limitation is to design an analysis to identify
+such threads. Second, our tool cannot compute call relationships
+for inter-process communication between components. It also
+requires users to manually add annotations to characterize
+call relationships that involve native methods. This limitation
+may lead to false negatives. Investigating the false positive
+rate is ongoing work.
+
+%Future work could evaluate our technique on more subjects, and
+%investigate the false negative rate.
+
+%our technique requires developers to manually
+%add annotations to provide call relationships
+%Second,
+
+%Third, for subject program
+%that uses native methods,
+
+\subsubsection{Experimental Conclusions}
+Findings: programmers have noted this problem, but often overlook special cases like error handle, subtype
+
+ Reporting on violations is fine but what is more important are the pracitces and patterns that need to be adopted to make it easier to avoid the issue in the first place.
+That is why there is a Worker interface in this project

### 2012-01-21 trunk/GUIErrorDetector/tests/edu/washington/cs/detector/experiments/straightforward/TestS3DropboxNaive.java
Add the straightforward approach

@@ -1,0 +1,74 @@
+package edu.washington.cs.detector.experiments.straightforward;
+
+import java.io.IOException;
+import java.util.Collection;
+
+import com.ibm.wala.classLoader.IMethod;
+import com.ibm.wala.ipa.callgraph.Entrypoint;
+import com.ibm.wala.ipa.cha.ClassHierarchyException;
+import com.ibm.wala.util.io.FileProvider;
+
+import edu.washington.cs.detector.CGBuilder;
+import edu.washington.cs.detector.CGEntryManager;
+import edu.washington.cs.detector.CGBuilder.CG;
+import edu.washington.cs.detector.UIAnomalyDetector;
+import edu.washington.cs.detector.experiments.straightforward.UnsafeUIAccessMethodFinder.GUI;
+import edu.washington.cs.detector.experiments.swing.TestS3Dropbox;
+import edu.washington.cs.detector.util.Globals;
+import edu.washington.cs.detector.util.SwingUtils;
+import edu.washington.cs.detector.util.Utils;
+import junit.framework.TestCase;
+
+public class TestS3DropboxNaive extends TestS3Dropbox {
+
+	private String jarDir = "D:\\research\\guierror\\eclipsews\\S3dropbox\\jars\\";
+	private String getJar(String jarName) {
+		return jarDir + jarName;
+	}
+	
+	public void testSwingS3Dropbox() throws ClassHierarchyException, IOException {
+		String appPath =
+			"D:\\research\\guierror\\subjects\\swing-programs\\s3dropbox1.6-trunk.jar" + Globals.pathSep +
+			getJar("aws-java-sdk-1.2.15.jar") + Globals.pathSep + 
+			getJar("commons-cli-1.2.jar") + Globals.pathSep +
+			getJar("commons-codec-1.3.jar") + Globals.pathSep +
+			getJar("commons-io-1.4.jar") + Globals.pathSep +
+			getJar("commons-lang-2.4.jar") + Globals.pathSep +
+			getJar("forms-1.0.6.jar") + Globals.pathSep +
+			getJar("httpclient-4.1.1.jar") + Globals.pathSep +
+			getJar("httpcore-4.1.jar") + Globals.pathSep +
+			getJar("jcl-over-slf4j-1.6.1.jar") + Globals.pathSep +
+			getJar("joda-time-1.5.2.jar") + Globals.pathSep +
[…]

### 2012-01-21 trunk/GUIErrorDetector/tests/edu/washington/cs/detector/experiments/straightforward/UnsafeUIAccessMethodFinder.java

@@ -1,0 +1,260 @@
+package edu.washington.cs.detector.experiments.straightforward;
+
+import java.util.Collection;
+import java.util.HashSet;
+import java.util.Iterator;
+import java.util.LinkedList;
+import java.util.List;
+
+import com.ibm.wala.classLoader.IMethod;
+import com.ibm.wala.ipa.callgraph.CGNode;
+import com.ibm.wala.ipa.cha.ClassHierarchy;
+import com.ibm.wala.util.graph.Graph;
+
+import edu.washington.cs.detector.SwingUIMethodEvaluator;
+import edu.washington.cs.detector.experiments.straightforward.UnsafeUIAccessMethodFinder.GUI;
+import edu.washington.cs.detector.util.WALAUtils;
+
+public class UnsafeUIAccessMethodFinder {
+	
+	enum GUI {SWT, Android, Swing}
+	public final Graph<CGNode> callgraph;
+	public final String[] packages;
+	public UIAccessDecider decider = null;
+	public ClassHierarchy cha = null;
+	
+	public UnsafeUIAccessMethodFinder(Graph<CGNode> cg, String[] packages) {
+		this.callgraph = cg;
+		this.packages = packages;
+	}
+	public void setUIAccessDecider(GUI type) {
+		this.decider = UIAccessDecider.getAccessDecider(type);
+	}
+	
+	public void setClassHierarchy(ClassHierarchy cha) {
+		this.cha = cha;
+	}
+	
+	public Collection<IMethod> finalAllUnsafeUIAccessMethods() {
+		Collection<IMethod> allUIAccessMethods = this.findAllUIAccessMethod();
+		Collection<IMethod> allSafeMethods = this.alwaysCalledBySafeMethods();
+		allUIAccessMethods.removeAll(allSafeMethods);
+		return allUIAccessMethods;
+	}
+	
+	private Collection<IMethod> findAllUIAccessMethod() {
+		if(this.decider == null) {
+		    throw new RuntimeException("Must set UIAccessDecider first.");	
+		}
+		//all directly ui accessing methods
+		Collection<CGNode> directAccessNodes = new HashSet<CGNode>();
+		for(CGNode node : callgraph) {
+			Iterator<CGNode> itNode = this.callgraph.getSuccNodes(node);
+			//check if every node has
+			while(itNode.hasNext()) {
+				CGNode next = itNode.next();
[…]

### 2012-01-21 GUIErrorDetector/tests/edu/washington/cs/detector/experiments/straightforward/TestSudokuSolverNaive.java
Add the straightforward approach

@@ -1,0 +1,53 @@
+package edu.washington.cs.detector.experiments.straightforward;
+
+import java.io.IOException;
+import java.util.Collection;
+
+import com.ibm.wala.classLoader.IMethod;
+import com.ibm.wala.ipa.callgraph.Entrypoint;
+import com.ibm.wala.ipa.cha.ClassHierarchyException;
+import com.ibm.wala.util.io.FileProvider;
+
+import edu.washington.cs.detector.CGBuilder;
+import edu.washington.cs.detector.CGEntryManager;
+import edu.washington.cs.detector.UIAnomalyDetector;
+import edu.washington.cs.detector.CGBuilder.CG;
+import edu.washington.cs.detector.experiments.straightforward.UnsafeUIAccessMethodFinder.GUI;
+import edu.washington.cs.detector.experiments.swing.TestSudokuPuzzleSolver;
+import edu.washington.cs.detector.util.SwingUtils;
+import edu.washington.cs.detector.util.Utils;
+
+public class TestSudokuSolverNaive extends TestSudokuPuzzleSolver {
+	
+	private String appPath =
+		"D:\\research\\guierror\\subjects\\swing-programs\\sudoku_puzzle_solver.jar";
+	
+	private String[] packages = new String[]{"sudoku"};
+	
+	public void testSolver() throws ClassHierarchyException, IOException {
+		CGBuilder builder = new CGBuilder(appPath, FileProvider.getFile(UIAnomalyDetector.EXCLUSION_FILE_SWING));
+		builder.setCGType(CG.RTA);
+		
+		builder.makeScopeAndClassHierarchy();
+		Iterable<Entrypoint> eps = com.ibm.wala.ipa.callgraph.impl.Util.makeMainEntrypoints(builder.getAnalysisScope(),
+				builder.getClassHierarchy());
+		Iterable<Entrypoint> eventHandlers = SwingUtils.getAllAppEventhandlingMethodsAsEntrypoints(builder.getClassHierarchy(), packages);
+		eps = CGEntryManager.mergeEntrypoints(eps, eventHandlers);
+		eps = CGEntryManager.mergeEntrypoints(eps, getAdditonalEntrypoints(builder.getClassHierarchy()));
+		
+		//start build call graph
+		builder.buildCG(eps);
+		
+		//check the straightforward approach result
[…]

### 2012-01-23 GUIErrorDetector/paper/implementation.tex
paper revise

@@
 Our current implementation supports four widely-used GUI frameworks, namely
-SWT, Eclipse plugin development environment, Java Swing, and Android.
-Our implementation handles all of the Java language, and also takes
+SWT, Eclipse plugin development, Java Swing, and Android.
+Our implementation %handles all of the Java language, and
+also takes
 all dependent libraries (e.g., \CodeIn{rt.jar} and \CodeIn{android.jar})
-into analysis. We implement the reflection taming algorithm (Section~\ref{})
+into analysis. We implemented the reflection-aware call graph construction
+ algorithm (Section~\ref{sec:cg})
 using WALA's \textit{bypass logic}. Our tool parses the configuration file
@@
 bytecode as a single apk file, our tool first uses
-android-apktool\footnote{\url{http://code.google.com/p/android-apktool/}} to
+android-apktool~\cite{apktool} to
 decrypt the apk file, and then uses the 

### 2012-01-23 GUIErrorDetector/paper/introduction.tex
paper revise

@@
 \section{Introduction}
+\label{sec:introduction}
 
-Graphical User Interfaces (GUIs) are one of the most important parts of
-software. Most software developed in recent years has a GUI, and the only
-way for the most end-users to interact with the software application is through
-the GUI. Hence, end-user satisfaction and retention of a software application
- are largely determined by the usability and correctness of
+End-user satisfaction and retention of a software application
+ are largely dependent on the usability and correctness of
 its GUIs.
 
-To make the GUIs more responsive and better utilize the increasingly available
-computation power in the multi-core era, GUI applications often spawn separate
-threads to handle time-consuming operations in the background, such as expensive
-computations, I/O tasks, and network requests. Using threads for those lengthy tasks
-makes a GUI active by allowing the timing of operations not delay unrelated parts of a 
-GUI application.
+To make the GUI more responsive and utilize multi-core computation,
+GUI applications often spawn separate threads to handle time-consuming
+operations in the background, such as expensive computation, I/O tasks,
+and network requests. This permits the GUI to respond to new events
+even before the lengthy task completes.
 
@@
 
-Nowadays, many popular GUI frameworks such as Swing\footnote{\url{http://docs.oracle.com/javase/6/swing/}},
-SWT\footnote{\url{http://eclipse.org/swt/}}, Android\footnote{\url{http://www.android.com/}},
-Qt\footnote{\url{http://qt.nokia.com/products/}}, MacOS Cocoa\footnote{\url{http://developer.apple.com/cocoa.html}},
-and X Windows\footnote{\url{http://www.x.org/}}
+Many popular GUI frameworks such as Swing~\cite{swing},
+SWT~\cite{swt}, Android~\cite{android},
+Qt~\cite{qt}, MacOS Cocoa~\cite{macos},
+and X Windows~\cite{xwindow}
 adapt the \textit{single-thread rule}:
@@
 Take the popular Standard Widget Toolkit (SWT) GUI framework as an example. 
-In a recent survey~\footnote{\url{http://www.slideshare.net/lakshmip/top-3-swt-exceptions-3951224}}, the invalid thread access error
-has been listed as the top 3 bugs in developing a SWT application, and treated
-as the source of many relevant concurrency bugs. Searching
-``SWTException:Invalid thread access'' in Google returns over 11,800 entries,
+The invalid thread access error is one of the top 3 bugs in developing a SWT application, and is
+the source of many relevant concurrency bugs~\cite{top3bugs}.
+A Google search for ``SWTException:Invalid thread access''  returns over 11,800 entries,
 consisting of numerous bug reports, forum posts, and mailing list threads on
-this problem. Eclipse, the de-facto standard IDE for Java development,
-is built on top of SWT. As eclipse became open-sourced in 2001, the invalid thread access error has
-been consistently reported during the past 11 years across different products, different components, and different releases.
-Searching the same ``SWTException:Invalid thread access'' keyword in eclipse's bug repository
+this problem. Eclipse, the IDE for Java development, is built on top of SWT.
+Searching for ``SWTException:Invalid thread access'' in Eclipse's bug repository
 and discussion forum returns over 2732 bug reports and 351 distinct threads, respectively. 
@@
 found this error has been reported in at least 20 distinct eclipse projects
-and 40 distinct eclipse components. Even after over 10-year's active development,
-a recent release of eclipse still contains this error (bug id: 333533, reported in 01/2011).
+and 40 distinct eclipse components. Even after over 10 years of active development,
+a recent release of Eclipse still contains this error (bug id: 333533, reported in 01/2011).
  Furthermore, many reported  errors are non-trivial, and it is unintuitive
-to fix them. Developers usually
-need non-local reasoning to find the specific UI interactions that can trigger the bug; and
-some reported errors (e.g., bug id: 51757) even took developers 2 years to fix it and verify the
-patch. In addition, such invalid thread access error is UI-relevant and user-perceivable;
-it cannot be recovered by the program itself and often terminates the whole application.
-In many circumstances as described in the bug reports,
-what users can only do is to restart the application to resort to an inconsistent status.
+to fix them. Developers usually need non-local reasoning to find the specific
+UI interactions that can trigger the bug;  it even took developers 2 years
+to fix bug: 51757 and verify the patch. In addition, the invalid thread access error
+is UI-relevant and user-perceivable; it cannot be recovered by the program itself
+and often terminates the whole application. In many circumstances as described in the bug reports,
+users can only restart the application to recover from the error.
 
@@
 like Android also suffer from similar problems. For example, 
-Figure~\ref{fig:androiderror} shows a recently reported bug on the Mozilla Firefox Android version.
+Figure~\ref{fig:androiderror} shows a recently reported bug on Android version of Mozilla Firefox.
 In Figure~\ref{fig:androiderror}, \CodeIn{LayViewer}'s constructor calls the
@@
 \subsection{Finding Invalid Thread Access Errors}
+\label{sec:finding}
 
-The invalid thread access errors have significantly affect the
-usability of GUIs, but have not been thoroughly studied in
-the context of multithreaded GUI applications . To ensure GUIs
-to behave correctly, effective
-techniques must be developed to alleviate this problem.
-
-%Effective techniques must be developed to
-%find such errors.
+Invalid thread access errors have significantly affect the
+usability of GUIs, but they have not been thoroughly studied in
+the context of multithreaded GUI applications. To ensure GUIs
+behave correctly, effective techniques must be developed to alleviate this problem.
 
 Software testing, the most widely used method to ensure program correctness,
-is insufficient to detect such errors. That is because the space of possible interactions
+is insufficient to detect such errors. The space of possible interactions
 with a GUI is enormous, in that each sequence of GUI events can result in
@@
 these states. It is almost impossible for testing to cover every possible
-states. In fact, a widely-used software system like eclipse
-often has a well-designed test suite that achieves fairly high coverage; but many
- bug-triggering UI sequences are still not covered.
+state. In fact, a widely-used software system like Eclipse
+often has a well-designed test suite that achieves fairly high statement coverage;
+but many paths executed by bug-triggering UI sequences are still not covered.
 
-Program refactoring~\cite{Mens:2004}, another popular way to improve software quality,
-is also inadequate to eliminate this error.  A standard way to fix an
+%Program refactoring~\cite{Mens:2004}, another popular way to improve software quality,
+%is also inadequate to eliminate this error.
+
+%One way to find such invalid thread access error is to check every GUI object
+%accessing code to see whether
+
+A standard way to fix an
 invalid thread access error is to replace direct GUI object accessing code 
-with asynchronized message passing, to ensure a GUI object are accessed in
-the UI thread. For example, fixing the bug in Figure~\ref{fig:androiderror}
-needs to wrap line 222 inside a \CodeIn{post} message passing method\footnote{The
+with asynchronized message passing, to ensure a GUI object is accessed in
+the UI thread. For example, to fix the bug in Figure~\ref{fig:androiderror},
+a developer would wrap line 222 inside a \CodeIn{post} message passing method\footnote{The
 \CodeIn{post} method in class \CodeIn{android.widget.View} is a
-a standard way to send messages to the UI-thread}, as follows:
+a standard way to send messages to the UI-thread.}, as follows:
 
@@
 
-One may wonder that a straightforward program transformation to wrap
-every possible UI-accessing operation with asynchronized message passing
-may solve this problem. However, such an approach is problematic,
-because using asynchronized message passing has no timing
+One may wonder that a simple analysis to check whether every GUI object
+accessing code has been wrapped by (a)synchronized message passing may
+be capable to find invalid thread errors. However, such an approach is problematic,
+because not every GUI object access needs to be wrapped by a message passing
+method, e.g., methods that are only called from UI-thread can safely
+access any GUI object. On the other hand, using asynchronized message passing has no timing
 guarantee. It is entirely possible that, in some cases, a GUI object has already been
-disposed before the message sent to arrives, causing other bugs. Thus, programmers can not use
-it everywhere; instead, they must choose carefully to put it in appropriate places
-with extreme caution.
+disposed before the message sent to arrives, causing other bugs. 
+Thus, programmers can not use it everywhere to wrap all GUI object accessing code.
+In our evaluation on real world programs, we found this simple analysis 
+can not be used in practice: it issued
+an unacceptable number of false positives and redundant warnings.
+
+%program transformation to wrap
+%every possible UI-accessing operation with asynchronized message passing
+%may avoid the invalid thread error. However, such an approach is problematic,
+%because using asynchronized message passing has no timing
+%guarantee. It is entirely possible that, in some cases, a GUI object has already been
+%disposed before the message sent to arrives, causing other bugs. Thus, programmers can not use
+%it everywhere; instead, they must choose carefully to put it in appropriate places
+%with extreme caution. This makes invalid thread errors even harder to avoid,
+%and demands a proactive technique to detect them.
 
@@
 
-Another approach, as we follow in this paper, is to
-use static analysis to find such potential errors.
-Static analysis has two attractive advantages while comparing to dynamic approaches such as
- testing.
-First, a static analysis can explore every path of the program without executing the code, and
-thus there is no need to construct non-trivial tests and harnesses.
-Second, a static analysis can soundly find potentially errors: if it
+This paper uses static analysis to find such potential errors.
+Static analysis has two advantages while compared to dynamic approaches such as
+ testing. First, a static analysis can explore every path of the program without
+executing the code, and without the need for a test suite.
+Second, a static analysis can verify the code: if it
 reports no warnings, the code is guaranteed to be bug-free.
@@
 not miss true positives. We note, however, that computing a sound
-call graph for GUI applications in the presence of reflection,
+call graph with acceptable precision for GUI applications in the presence of reflection
 is non-trivial.
-Existing call graph construction algorithms such as RTA~\cite{} and k-CFA~\cite{}
-either suffer from the problem of imprecision or incompleteness .
-To alleviate this problem,
-we present a combined RTA and k-CFA call graph construction algorithm, and
-also compare its usefulness with other algorithms in  our experiments. We
-also note that static analysis may report false positives due to its
+Existing call graph construction algorithms such as RTA~\cite{rta}
+and k-CFA~\cite{kcfa}
+fails to build a sufficiently complete call graph, due to their limitations
+to reason about reflections.  To alleviate this problem,
+we present a method to build reflection-aware call graph, and
+also compare its usefulness with existing call graph construction algorithms in
+our experiments. We also note that static analysis may report false positives due to its
 conservative nature, or multiple warnings that actually correspond
@@
 
-We instantiate our technique for four GUI frameworks namely SWT,
+We instantiated our technique for four popular GUI frameworks namely SWT,
 eclipse plugin environment, Java Swing, and Android. 
-The reason of choosing these four GUI frameworks is because of
-their popularity. Swing and SWT are unquestionably (XXX)
+Swing and SWT are unquestionably 
 two dominating GUI frameworks in developing desktop Java applications.
-Eclipse with its plugin development envrionment is the de-facto standard
-IDE for Java. Android becomes the No. 1 platform for
+Eclipse and its plugin development envrionment is the de-facto standard
+IDE for Java. Android is the No. 1 platform for
 developing mobile applications with market share 56\% as of Sep 2011.
@@
 that: our technique is effective (it found XXX real-world errors
-on all supported frameworks); our combined RTA and k-CFA call
-graph construction algorithm is useful (XXX it improves both completeness
-and precision over the existing algorithms), and our proposed
+on all supported frameworks, and produced significantly less
+false positives and redundant warnings than the simple analysis);
+our reflection-aware call graph construction algorithm is
+critical in finding errors in Android applications,
+%graph construction algorithm is useful (XXX it improves both completeness
+%and precision over the existing algorithms), 
+and our proposed
 heuristics are useful (it signficantly reduces the number of
@@
 \begin{itemize}
-\item \textbf{Problem.} We explicitly identify the invalid thread
-access error on multithreaded GUI programs.
+\item \textbf{Problem.} We are the \textit{first} to address
+the invalid thread access error detection problem in the context of multithreaded GUI applications.
 %, and formulate it
@@
 In particular, to deal with the unique features in
-multithreaded GUI programs, we propose a combined RTA and k-CFA
-call graph construction algorithm (Section~\ref{sec:technique}).
+multithreaded GUI programs, we propose a reflection-aware
+call graph construction method. (Section~\ref{sec:technique}).
 

### 2012-01-23 GUIErrorDetector/paper/technique.tex
paper revise

@@
 notations of \textit{UI thread}, \textit{non-UI threads},
-\textit{UI accessing methods},
+\textit{UI-accessing methods},
  \textit{safe methods}, and \textit{invalid thread access error}, and
@@
 \noindent {\textsc{\textbf{Definition 3 (UI-Accessing Methods).}}} { A method
-whose execution may read or write a UI object is called a UI accessing method.}\vspace{1mm}
+whose execution may read or write a UI object is called a UI-accessing method.}\vspace{1mm}
 
@@
 non-UI threads spawned by the UI thread, and check whether those non-UI threads
-may invoke a UI accessing method.
+may invoke a UI-accessing method.
 
@@
 indicates that a new, non-UI thread is spawned.  After that, 
-the algorithm uses a BFS to find reachable UI accessing methods (lines 9 -- 23)
+the algorithm uses a BFS to find reachable UI-accessing methods (lines 9 -- 23)
 from each \CodeIn{Thread.start()} node.
@@
 it reports an error if that node
-is a UI accessing method (line 15), or skips it if it is
+is a UI-accessing method (line 15), or skips it if it is
 a safe method (line 17), or simply keeps traversing otherwise (line 19).
 
-If the algorithm determines that a UI accessing method may be invoked
+If the algorithm determines that a UI-accessing method may be invoked
 by a non-UI thread, it creates an error report containing the full
@@
 and k-CFA call graph construction algorithm in Section~\ref{sec:cg}.
+
+%we augument k-CFA with value set
 
@@
 
-\subsubsection{Call Graph Construction}
+\subsubsection{Reflection-aware Call Graph Construction}
 \label{sec:cg}
+
+%In OO program, translate k-CFA as:
+%k-call-site sensitive interprocedural pointer
+%analysis with a k-context-sensitive heap and onthe-
+%fly call-graph construction
+%
 
@@
 1. public class MyActivity extends Activity \{
-2.    final List<View> cachedViews = new LinkedList<View>();
-3.    @Override
-4.    public void onCreate(Bundle savedInstanceState) \{
-5.        super.onCreate(savedInstanceState);
-6.        setContentView(R.layout.main);
-7.        Button button = (Button) findViewById(R.id.\textbf{button\_id});
-8.        button.setOnClickListener(new Button.OnClickListener() \{
-9.            @Override
-10.           public void onClick(View v) \{
-11.               button.setText("Button Clicked.");
-12.               cachedViews.add(v);
+2.    @Override
+3.    public void onCreate(Bundle savedInstanceState) \{
+4.        super.onCreate(savedInstanceState);
+5.        setContentView(R.layout.main);
+6.        Button button = (Button) findViewById(R.id.\textbf{button\_id});
+7.        button.setOnClickListener(new Button.OnClickListener() \{
+8.            @Override
+9.            public void onClick(View v) \{
+10.               button.setText("Button Clicked.");
+11.           \}
+12.       \});
 13.   \}
-14.       \});
-15.   \}
-16. \}
+14. \}
 \end{alltt}
@@
 program scale well but achieves relatively lower precision.  The
-k-CFA algorithms maintains one set per expression achieves better
-precision than RTA (\textit{k} is the context length, which is
-orthogonal to the number of maintained sets).
+k-CFA algorithms maintains one or several sets per expression achieves better
+precision than RTA (\textit{k} is length of calling context).
+
+%this is wrong for k-CFA, k-CFA maintains several sets per expression, which k > 0
+%should cite Ben Livshit's paper on "Reflection analysis for Java"
+%Donot overclaim "say propose a new technique", instead, say "refine the technique"
+%also need to cite Yannis's paper on solving k-CFA paradox
+
+%\textbf{need to describe why need to traverse from the UI entry, not just from the thread entry}
 
 \begin{figure}[t]
-\textbf{Input}: a Java program $P$, a list of classes $cls$\\
+\textbf{Input}: a Java program $P$\\
 \textbf{Output}: a call graph $cg$\\
@@
 \begin{algorithmic}[1]
-\STATE callSiteMap $\leftarrow$ new Map$\langle$CallSite, List$\langle$Type$\rangle$$\rangle$
-\STATE rta\_cg $\leftarrow$ $constructCallGraphByRTA$($P$)
-\FOR{each $method$ in $P$}
-\FOR{each  $callSite$ in $method$}
-\STATE type $\leftarrow$ $staticType$(callSite)
-\IF{type $\in$ $cls$}
-\FOR{each subType of $subType$(type)}
-\IF{$hasObjectCreated$(subType, rta\_cg)}
-\STATE callSiteMap[callSite].add(subType)
+\FOR{each $statement$ in $P$}
+\IF{$statement$ is a reflection call}
+\STATE objectSet $\leftarrow$ getAllObjectsToCreate($statement$)
+\STATE $newInstr$ $\leftarrow$ createObjectCreationStatement(objectSet)
+\STATE replace $statement$ with $newInstr$
 \ENDIF
 \ENDFOR
-\ENDIF
-\ENDFOR
-\ENDFOR
-\STATE $cg$ $\leftarrow$ $constructCallGraphByKCFA$($P$, callSiteMap)
+\STATE $cg$ $\leftarrow$ $constructCallGraph$($P$, callSiteMap)
 \RETURN $cg$
@@
 \label{fig:cgalgorithm}
-\caption{A combined  RTA~\cite{rta} and k-CFA~\cite{kcfa} call graph construction algorithm.
-$cls$ is a list of classes whose method invocations are added to the
-call graph using the RTA algorithm; while method invocations from other classes
-are added to the call graph using the k-CFA algorithm.
+\caption{A reflection-aware call graph construction algorithm. Lines 1
+- 7 shows a simple program transformation to replace reflection calls
+with object creations, and line 8 constructs the call graph on
+the transformed program using the existing call graph algorithm. 
 } 
@@
 
-Unfortunately, GUI applications often use reflection, which makes either
-RTA or k-CFA insufficient to build a satisfactory call graph. 
-The example code in Figure~\ref{fig:sampleandroid}  illustrates their limitations.
-In Figure~\ref{fig:sampleandroid}, line 7 uses reflection to create a \CodeIn{Button}
+Unfortunately, GUI applications often use reflection extensively and make
+existing call graph construction algorithms fail to build a sufficiently complete
+call graph. The example code in Figure~\ref{fig:sampleandroid} from an Android application
+ illustrates the limitations.
+In Figure~\ref{fig:sampleandroid}, line 6 uses reflection to create a \CodeIn{Button}
 object by looking up its id declared in the XML file. When this button
-is clicked, its event handling code (line 10 -- 13) updates the text and caches
-the current view to a list declared at line 2.
+is clicked, its event handling code (line 9 -- 11) updates the text.
+%d caches
+%the current view to a list declared at line 2.
 
-Existing call graph algorithms either suffer from the problem of incompleteness
-or imprecision. The k-CFA algorithm performs points-to analysis with call
-graph construction interleavingly, and maintains a value set for every expression.
-For example, it concludes that variable \CodeIn{cachedViews} can only point
-to a \CodeIn{LinkedList} object and the method call \CodeIn{add} at line 12
-can only correspond to \CodeIn{LinkedList.add}. However, k-CFA fails to
-conclude that variable \CodeIn{button} declared at line 7 points to
-a \CodeIn{Button} object due to its limitation in dealing with reflection. Thus, k-CFA
-may miss the call graph edge corresponding to the method call \CodeIn{setText} at line 11. 
-On the other hand, using a coarse-grained algorithm like RTA~\cite{} can not still
-fully solve this problem. RTA adds an edge for a method invocation 
-to the call graph if an object of the receiver's type (or subtype)
-has been created.  By explicitly specifying that all GUI classes declared in the XML file will be created,
-RTA maintains a global value set for those GUI object type, and  adds a
-call edge \CodeIn{setText} to the call graph. However, RTA introduces 
-unnecessary precision loss: it may
-may conclude that the \CodeIn{cachedViews} variable at line 2
-point to any created \CodeIn{List} objects created somewhere else in the program, despite the
-fact that \CodeIn{cachedViews} can only be a \CodeIn{LinkedList} object.
+When using existing call graph algorithms to analyze the code in Figure~\ref{fig:sampleandroid},
+they fail to conclude that variable \CodeIn{button} declared at line 7
+point to a \CodeIn{Button} object due to its limitation in deal with the
+reflection call \CodeIn{findViewById}. Thus, the resulting
+call graph will miss the calling edge corresponding to the method
+call \CodeIn{setText} at line 10.
 
-To alleviate the above problems, we present a combined RTA and k-CFA
-call graph construction algorithm as shown in Figure~\ref{fig:cgalgorithm}.
-The algorithm shares the same spirit as k-CFA to maintain a value set
-for each expression. However, the only difference is that our
-algorithm uses a RTA-style treatment for constructing the value set for
-GUI classes: it parses the XML configuration file and explicitly
-adds a raw object to each declared GUI variable's value set. Thus,
-For the example in Figure~\ref{fig:sampleandroid}, this
-combined algorithm concludes that a \CodeIn{Button} object has been
-created at line 7 and then adds the call edge \CodeIn{setText} to the
-graph. It also concludes that the \CodeIn{cachedViews} variable can only
-point to a \CodeIn{LinkedList} object, avoiding unnecessary precision loss.
-%For desktop applications which have main method, it is straigtforward to apply
-%the above algorithm. However, for applications on platforms like eclipse plugin
-%and Android. presents new challenges. Two technical challenges must be solve.
-%First, use reflection extensively, Second, it is possible to interact with
-%native code.
+%Existing call graph algorithms failed either suffer from the problem of incompleteness
+%or imprecision. The k-CFA algorithm performs points-to analysis with call
+%graph construction interleavingly, and maintains a value set for every expression.
+%For example, it concludes that variable \CodeIn{cachedViews} can only point
+%to a \CodeIn{LinkedList} object and the method call \CodeIn{add} at line 12
+%can only correspond to \CodeIn{LinkedList.add}. However, k-CFA fails to
+%conclude that variable \CodeIn{button} declared at line 7 points to
+%a \CodeIn{Button} object due to its limitation in dealing with reflection. Thus, k-CFA
+%may miss the call graph edge corresponding to the method call \CodeIn{setText} at line 11. 
+%On the other hand, using a coarse-grained algorithm like RTA~\cite{} can not still
+%fully solve this problem. RTA adds an edge for a method invocation 
+%to the call graph if an object of the receiver's type (or subtype)
+%has been created.  By explicitly specifying that all GUI classes declared in the XML file will be created,
+%RTA maintains a global value set for those GUI object type, and  adds a
+%call edge \CodeIn{setText} to the call graph. However, RTA introduces 
+%unnecessary precision loss: it may
+%may conclude that the \CodeIn{cachedViews} variable at line 2
+%point to any created \CodeIn{List} objects created somewhere else in the program, despite the
+%fact that \CodeIn{cachedViews} can only be a \CodeIn{LinkedList} object.
 
-%Android features an extended event-based library and dynamic inflation of
-%graphical views from declarative XML layout files.
-%A static analyzer for Android programs must consider such features, for
-%correctness and precision.
+To alleviate this limitation, we present an algorithm to construct
+a reflection-aware call graph based on simple program transformation.
+The basic idea to replace reflection calls with explicit object
+creation instructions, pretending the corresponding concreate object
+has been created.  The algorithm is shown in Figure~\ref{fig:cgalgorithm}.
+It consists of two steps. The first step is a simple program
+transformation to replace reflection calls with object creations, and
+the second step is to use standard call graph construction algorithms
+to construct the graph on the transformed program. Lines 1 - 7 show
+the transformation step. The algorithm iterates through every statement
+in an analyzed program. When it sees a reflection call statement (e.g.,
+the \CodeIn{findViewById} method), the algorithm analyzes the
+program to determine a set of possible classes that may be created.
+After that, the algorithm creates a new instruction which non-deterministically
+returns a new object of the class set. The reflection-aware call graph
+construction algorithm is indepdent of the underlying call graph algorithm;
+any existing algorithm can be used to construct the resulting graph at line 8.
 
-%Give an example of how reflection affect call graph precision.
+For the example in Figure~\ref{fig:sampleandroid}, the algorithm
+first parses the XML configuration file to determine that the \CodeIn{button\_id}
+value is mapped to a \CodeIn{Button} instance declaration. Then it
+replaces the \CodeIn{findViewById(R.id.button\_id)} method call 
+with an explicit object creation instruction \CodeIn{new Button}.
+After that, the algorithm employs existing call graph construction
+algorithms to analyze the transformed program, and permits them
+to add the call edge \CodeIn{setText} to the resulting graph.
 
-%So, we present a new call graph construction algorithm
+Using this reflection-aware call graph construction algorithm is
+critical to detect bugs on realistic GUI applications.
+As demonstrated in our experiments, errors in all Android applications
+can only be detected using this algorithm.
 
-%reflected classes are known, use RTA.
+% combined RTA and k-CFA
+%call graph construction algorithm as shown in Figure~\ref{fig:cgalgorithm}.
+%The algorithm shares the same spirit as k-CFA to maintain a value set
+%for each expression. However, the only difference is that our
+%algorithm uses a RTA-style treatment for constructing the value set for
+%GUI classes: it parses the XML configuration file and explicitly
+%adds a raw object to each declared GUI variable's value set. Thus,
+%For the example in Figure~\ref{fig:sampleandroid}, this
+%combined algorithm concludes that a \CodeIn{Button} object has been
+%created at line 7 and then adds the call edge \CodeIn{setText} to the
+%graph. It also concludes that the \CodeIn{cachedViews} variable can only
+%point to a \CodeIn{LinkedList} object, avoiding unnecessary precision loss.
 
-%reflection code
-
-%native code
-
-\subsubsection{Heuristic Filtering and Annotation}
-\label{sec:heuristic}
-
-A static analysis can exhaustively check possible error path; but may report
-paths that do not actually exist (i.e., false positives) or different paths
- that correspond to the same error (i.e., redundant warnings). We devise
-a set of heuristics below to filter out likely false positives and redundant warnings.
-The first two heuristics are for reducing false positives, while the
-remaining ones are for removing redundant warnings.
-
-%To remove those 
-%The potentially huge volume of
-%reported warnings impose great burden for programmers to check
-%its validity.
-
-\begin{enumerate}
-
-\item \textbf{Filter Reports Containing Library Calls}. A
-reported method call chain involving common Library calls
-like \CodeIn{Object.toString} or \CodeIn{Runtime.shutDown} are unlikely to
-be buggy, and should be filtered. In addition, a method call chain that \textit{only}
-consists of library calls after the entry method is also unlikely
-to reveal a valid bug, since it has no interaction with the UI. 
-We encode a list of common library calls, and remove
-a report if it contaiins one of them.
-%Method call chain involves typical
-%system methods like \CodeIn{toString} are unlikely to reveal a real bug.
-
-\item \textbf{Filter Reports With User-Annotated Methods}. Besides general
-library calls, users are also permitted
-to explicitly annotate methods that will never trigger an error.
-For example, the Android GUI framework provides a utility method 
-\CodeIn{runOnUIThread} to check whether the current thread is the UI thread
-before executing the code; if
-not, it executes the code on the UI thread using message passing.
-A reported call chain containing a annotated 
-can be safely removed.
-%method will never cause an
-%invalid thread error and should be removed.
-
-\item \textbf{Filter Lexically Redundant Reports}. One reported method call
-chain can lexically subsume another one. For example, suppose that a reported method
-call chain \CodeIn{a()} $\rightarrow$ \CodeIn{b()} $\rightarrow$ \CodeIn{c()}
-leads to a potential error, and another entry method \CodeIn{d()} calls \CodeIn{a()}.
-Therefore, a static analysis might also report another method call chain
-\CodeIn{d()} $\rightarrow$ \CodeIn{a()} $\rightarrow$ \CodeIn{b()} $\rightarrow$ \CodeIn{c()}
-that actually corresponds to the same error root as the previous one. In this case, 
- removing the second call chain would not reduce the error detection capability:
-the first call chain already reveals the same error and is shorter 
-for programmers to interpret.
-
-\item \textbf{Filter Report With the Same $k$ Head Methods}. A method can call
-multiple methods that access GUI objects, such as:
-\begin{CodeOut}
-\begin{alltt}
-     public void m() \{
-         accessUIObject1();
-         accessUIObject2();
-     \}
-\end{alltt}
-\end{CodeOut}
-If method \CodeIn{m()} is invoked by a non-UI thread, two method call chains
-only different at last few method nodes will be reported:
-
-\CodeIn{a()} $\rightarrow$ ...\CodeIn{Thread.start()} ... $\rightarrow$ \CodeIn{m()} $\rightarrow$ \CodeIn{accessUIObject1()} ...
-
-\CodeIn{a()} $\rightarrow$ ...\CodeIn{Thread.start()} ... $\rightarrow$ \CodeIn{m()} $\rightarrow$ \CodeIn{accessUIObject2()} ...
-
-In fact, these two call chains correspond to the same error root: knowning
-method \CodeIn{m()} is called by a non-UI thread is sufficient to understand and fix this error.
-This filter compares every two reported method call chains that share the same
-$k$ ($k$ is user-settable with a default value 5) head nodes, and removes the longer one.
-
-\item \textbf{Filter Report With the Same $k$ Tail Methods}. A method
-can have multiple callers, so that method call chains with the same tail are likely
-to represent different ways to trigger the same error. This filter compares every
-two reported method call chains that share the same 
-$k$ ($k$ is user-settable with a default value 5) tail nodes, and removes the longer one.
-
-\end{enumerate}
-
-All above filters are based on heuristics, and thus not sound in
-that it may filter real bugs. However, as we will show in
-the next experiment section, all these filters work well, and significantly
-reduces the number of false positives and redundant reports in practice.
+\subsubsection{Annotation for Native Methods}
 
@@
 
-Our static analysis will take the call relationship as indicated by this
+Our static analysis will also take the call relationship as indicated by this
 annotation into consideration when traversing the call graph. In our experiment,
@@
 with the user-provided annotations.
+
+\subsubsection{Heuristic Filtering}
+\label{sec:heuristic}
+
+A static analysis can exhaustively check possible error path; but may report
+paths that do not actually exist (i.e., false positives) or multiple paths
+ that have the same error cause (i.e., redundant warnings). We devise
+5 heuristics below to remove likely false positives and redundant warnings.
+The first two are for eliminating false positives, while the
+other three are for reducing redundant warnings.
+
+%To remove those 
+%The potentially huge volume of
+%reported warnings impose great burden for programmers to check
+%its validity.
+
+\begin{enumerate}
+
+\item \textbf{Filter Reports Containing Library Calls}. A
+method call chain involving normal library calls
+like \CodeIn{Object.toString} or \CodeIn{Runtime.shutDown} are unlikely to
+be buggy. In addition, a method call chain that \textit{only}
+consists of library calls after the entry method is also unlikely
+to reveal a valid bug, since it has no UI interaction.
+We encode a list of common library calls, and remove
+a reported warning if it contains one of them.
+%Method call chain involves typical
+%system methods like \CodeIn{toString} are unlikely to reveal a real bug.
+
+\item \textbf{Filter Reports With User-Annotated Methods}. Besides general
+library calls, users are also permitted
+to explicitly annotate methods that will never trigger an error.
+For example, the Android GUI framework provides a utility method 
+\CodeIn{runOnUIThread} to check whether the current thread is the UI thread
+before executing the code. If the current thread is not the UI thread,
+this method will be executed on the UI thread via message passing.
+Thus, a reported method call chain containing an annotated 
+can be safely removed.
+%method will never cause an
+%invalid thread error and should be removed.
+
+\item \textbf{Filter Lexically Redundant Reports}. One reported method call
+chain can lexically subsume another one. For example, suppose that two
+reported method call chains: \CodeIn{a()} $\rightarrow$ \CodeIn{b()}
+$\rightarrow$ \CodeIn{c()} and 
+\CodeIn{d()} $\rightarrow$ \CodeIn{a()} $\rightarrow$ \CodeIn{b()} $\rightarrow$ \CodeIn{c()}
+both lead to a potential error, since $\CodeIn{d()}$ and \CodeIn{a()}
+are two separated entry methods. The second call chain should
+be removed and would not reduce the error detection capability, since
+the first chain reveals the same error and is shorter 
+for programmers to interpret.
+
+\item \textbf{Filter Report With the Same $k$ Head Methods}. A method can call
+multiple methods that access GUI objects, such as:
+\begin{CodeOut}
+\begin{alltt}
+     public void m() \{
+         accessUIObject1();
+         accessUIObject2();
+     \}
+\end{alltt}
+\end{CodeOut}
+If method \CodeIn{m()} is invoked by a non-UI thread, method call chains
+only different at the last few method nodes may be reported separately, such as:
+
+\CodeIn{a()} $\rightarrow$ ...\CodeIn{Thread.start()} ... $\rightarrow$ \CodeIn{m()} $\rightarrow$ \CodeIn{accessUIObject1()} ...
+
+\CodeIn{a()} $\rightarrow$ ...\CodeIn{Thread.start()} ... $\rightarrow$ \CodeIn{m()} $\rightarrow$ \CodeIn{accessUIObject2()} ...
+
+In fact, these two chains may have the same error root: knowning that
+method \CodeIn{m()} is called by a non-UI thread is sufficient to understand
+the error.
+This filter compares two reported chains that have the same
+$k$ ($k$ is user-settable with a default value 5) head nodes, and removes the longer one.
+
+\item \textbf{Filter Report With the Same $k$ Tail Methods}. A method
+can have multiple callers, so that method call chains with the same tail are likely
+to just represent different ways to trigger the same error. This filter compares 
+two reported method call chains that share the same 
+$k$ ($k$ is user-settable with a default value 5) tail nodes, and removes the longer one.
+
+\end{enumerate}
+
+All above 5 filters are based on heuristics, and thus are not sound in
+that it may filter real bugs. However, as we will show in
+our experiments, these filters work remarkably well in
+reducing the number of false positives and redundant reports in practice.
 
@@
 namely SWT, Eclipse plugin environment, Swing, and Android.
-Each framework has different settings for UI thread (i.e., \textbf{call graph entry nodes}),
-\textbf{UI accessing nodes}, and \textbf{safe methods}, which correspond
-to lines 3 -- 5 in Figure~\ref{fig:detectalgorithm}. We customize those
-framework-specific parts as follows.
+The major framework-specific parts, corresponding to
+lines 3 -- 5 in Figure~\ref{fig:detectalgorithm}, are to identify
+\textbf{call graph entry nodes}), \textbf{UI-accessing nodes},
+and \textbf{safe methods} for each framework.
 
 %For each framework, we customize the \textit{call graph entry nodes},
-%\textit{UI accessing nodes}, and \textit{safe methods} on lines 3 -- 5 of the
+%\textit{UI-accessing nodes}, and \textit{safe methods} on lines 3 -- 5 of the
 %algorithm in
@@
 
-SWT is an open source widget toolkit for Java designed to provide efficient,
-portable access to the GUI facilities of the operating systems on which it is implemented.
-Like a normal Java application, a SWT desktop application has a single main method
-as the starting point. By default, the main method launches
-the UI thread and pops up the GUI. We instantiate our technique as follows:
+%SWT is an open source widget toolkit for Java designed to provide efficient,
+%portable access to the GUI facilities of the operating systems
+%on which it is implemented.
+Like a normal Java application, a SWT desktop application
+has a single main method as the entry point. By default,
+the main method launches the UI thread when initializing the GUI.
+We instantiate our technique for SWT applications as follows:
 
@@
 
-\item \textbf{Call graph entry nodes: } the single main method
+\item \textbf{Call graph entry nodes: } the main method
 
-\item \textbf{UI accessing nodes: } in STW, a thread-unsafe method calls \CodeIn{Display.checkWidget}
-or \CodeIn{Display.checkDevice} methods to check whether the current thread is the UI thread or not. Thus,
-we treat all such methods that must be accessed in UI thread as the UI accessing nodes.
+\item \textbf{UI-accessing nodes: } SWT provides explicit
+runtime checking for illegal thread access. Any methods for manipulating
+GUI object must call methods \CodeIn{Display.checkWidget}
+or \CodeIn{Display.checkDevice} to check whether the current
+thread is the UI thread or not.
+Thus, we treat nodes corresponding to the methods
+calling these two methods as UI-accessing nodes.
+%must be invoked
+%in the UI thread and as
+%UI-accessing nodes.
+ %methods to check whether the current thread is the UI thread or not. Thus,
+%we treat all such methods that must be accessed in UI thread as the UI-accessing nodes.
 % any
@@
 \item \textbf{Safe methods: } SWT provides two helper methods (\CodeIn{Display.\\asyncExec}
-and \CodeIn{Display.syncExec}) as passing (a)synchronized messages to the UI thread.
+and \CodeIn{Display.syncExec}) to execute code (a)synchronizedly on the UI thread.
 We treat these two methods as safe methods, since invoking
-them from any thread are generally considered to be safe and
+them from any thread 
+%are generally considered to be safe and
 would not cause an invalid thread access error.
@@
 
-An eclipse plugin is an open program. Unlike a SWT desktop application, it does not
-have a main method as a single program entry point. Instead, it extends certain
-extension points provided by the eclispe framework. As a plugin starts, the eclipse
-framework will calls back the overrided extension points and intializes the plugin code.
-We customize our technique for eclipse plugin as follows:
+%An eclipse plugin is an open program. 
+Unlike a SWT desktop application, an Eclipse plugin does not
+have a main method as a single program entry point. Instead, it extends
+extension points provided by the Eclispe framework to implement
+functionalities. When a plugin starts, Eclipse
+calls back the overrided extension points to handle the
+upcoming events. We customize our technique for Eclipse plugin as follows:
 
@@
 
-\item \textbf{Call graph entry nodes: } due to the complexity of the eclipse architecture,
-there is no rigorous way in eclipse to identify a UI thread. Here, we use a heuristic to determine call graph
-entry nodes from the UI thread. As a naming convention, source code in a plugin's \CodeIn{ui}
-package deals with the creation and maintainance of a plugin's GUI, and is thus
-invoked by the UI thread. We conservatively treat all public methods in the \CodeIn{ui}
-as call graph entry nodes.
+\item \textbf{Call graph entry nodes: } all overriden SWT
+GUI event handling methods\footnote{Eclipse plugin is built
+on top of the SWT framework} are called from the UI thread.
+We treat these callback methods as the entry nodes.
+
+%due to the complexity of the eclipse
+%architecture,
+%there is no rigorous way in eclipse to identify a UI thread. Here, we use a heuristic to determine call graph
+%entry nodes from the UI thread. As a naming convention, source code in a plugin's \CodeIn{ui}
+%package deals with the creation and maintainance of a plugin's GUI, and is thus
+%invoked by the UI thread. We conservatively treat all public methods in the \CodeIn{ui}
+%as call graph entry nodes.
 
@@
 
-\item \textbf{UI accessing nodes} and \textbf{Safe methods} are the same as SWT.
+\item \textbf{UI-accessing nodes} and \textbf{Safe methods} are the same as SWT.
 
@@
 
-\item \textbf{Call graph entry nodes: } all overriden callback methods in the
-listerner classes are called from the UI thread. We treat those callback
+\item \textbf{Call graph entry nodes: } all overriden callback methods in 
+Swing's UI listerner classes are called from the UI thread. We treat those callback
 methods as the entry nodes.
@@
 
-\item \textbf{UI accessing nodes:} as stated in Swing's documentation, methods
+\item \textbf{UI-accessing nodes:} as stated in Swing's documentation, methods
 in Swing GUI classes are not thread safe with three exceptions (\CodeIn{repaint()},
 \CodeIn{revalidate()}, and \CodeIn{invalidate()}). Thus, we
-treat all methods as defined in each GUI class as UI accessing nodes.
+treat all methods defined in each GUI class as UI-accessing nodes.
 
 \item \textbf{Safe methods: }  Swing provides two helper methods
-(\CodeIn{SwingUti-\\lities.invokeLater} and \CodeIn{SwingUtilities.invokeDelay}) to pass messages to the UI thread.
+(\CodeIn{SwingUti-\\lities.invokeLater} and \CodeIn{SwingUtilities.invokeAndWait}) to pass messages to the UI thread.
 We treat these two methods as safe methods.
@@
 
-\item \textbf{UI accessing nodes: } like SWT, Android explicitly checks the current
-thread validity before accessing a GUI object using the \CodeIn{ViewRoot.checkThread} method.
-Thus, we treat every methods that calls \CodeIn{ViewRoot.checkThread} as a UI accessing node
+\item \textbf{UI-accessing nodes: } like SWT, Android explicitly checks whether
+the current thread is a UI thread or not before accessing a GUI object via
+the \CodeIn{ViewRoot.checkThread} method.
+Thus, we treat every methods calling \CodeIn{ViewRoot.checkThread} as a UI-accessing node
 in the call graph.

### 2012-01-23 trunk/GUIErrorDetector/paper/abstract.tex
paper revise

@@
 \begin{abstract}
-Graphical User Interface (GUI) is a critical component of today's software.
- It provides user-friendly access to the functionality provided by the application.
-To keep GUIs responsive and active, a GUI application often spawns
- separate threads to handle lengthy operations in the background,
-such as expensive computations, I/O tasks, and network requests.
-However, many modern GUI frameworks require all GUI objects
-must be accessed exclusively by the \textit{event dispatching thread}
-(or called \textit{UI thread}). If a GUI object
-is accessed through a non-UI thread, an \textit{invalid thread access} error
-occurs and the whole application may abort consequently.
+To keep a Graphical User Interface (GUI) responsive and active, a GUI
+application often has a main \textit{UI thread} (or \textit{event dispatching thread})
+and spawns separate threads to handle lengthy operations in the background,
+such as expensive computation, I/O tasks, and network requests.
+Many GUI frameworks require all GUI objects to be accessed exclusively by the
+UI thread. If a GUI object is accessed through a non-UI thread,
+an \textit{invalid thread access} error occurs and the whole
+application may abort.
 
-In this paper, we present a general technique to find such \textit{invalid thread access}
+This paper presents a general technique to find such \textit{invalid thread access}
 errors in multithreaded GUI applications. We formulate finding invalid
-thread access errors as a call graph
-reachability problem. Our technique starts from call graph entry nodes to
-statically explore all possible paths that may cause a non-UI thread
-to access a GUI object.
-However, the heavy use of reflection in modern GUI applications makes existing
-call graph construction algorithms insufficient to build a both complete and precise
-call graph. Thus, we present a combined RTA and k-CFA
-call graph construction algorithm to overcome the limitations.% of analyzing GUI applications.
+thread access errors as a call graph reachability problem with
+thread spawning as the sources and GUI object accessing as the sinks. 
+Heavy use of reflection in modern GUI applications makes existing
+call graph construction algorithms fail to build a good
+call graph. Thus, we present a method to overcome the limitations, and
+build reflection-aware call graphs.
+
+%call graph construction algorithm to overcome the limitations.% of analyzing GUI applications.
 
 We implemented our technique and instantiated it on four popular GUI
-platforms, namely SWT, Eclipse plugin development framework, Java Swing, and Android. In an evaluation
-on XX subjects over XXX LOC, our technique found a number of real-world errors,
-suggesting its effectiveness and showing good scalability.
+platforms: SWT, Eclipse plugin development framework, Java Swing, and
+Android. In an evaluation on XX subjects over XXX LOC, our technique
+found a number of real-world errors, suggesting its effectiveness
+and showing good scalability.
 

### 2012-01-23 trunk/GUIErrorDetector/paper/evaluation.tex
paper revise

@@
 We use a set of open-source projects from Sourceforge, Google code and Eclipse plugin
-market as evaluation subjects. We choose subjects for each supported GUI framework
-as follows. We search the framework keywords (e.g., ``Java Swing'' or ``Java SWT'')
-in the above three source repositories, and select subjects based on the following
-criterias: first, the subject must be a multithread GUI application, not
+market as evaluation subjects. To choose subjects for each supported GUI framework,
+we first search the framework keywords (e.g., ``Java Swing'' or ``Java SWT'')
+in the above three source repositories, and then select subjects based on the following
+criterias. First, the subject must be a multithread GUI application, not
 an open library. Second, the subject must undergone at least two years of active development,
 and is listed in the first 3 results pages based on popularity. This permits us
-to exclude all pre-mature subjects, which may contain obvious errors.
+to exclude many pre-mature subjects that may contain obvious errors.
 
 The subjects used in our experiment are shown in Table~\ref{table:subjects}. Our
-subjects range from end-user applications, programming tools, to games. Specifically:
+subjects include end-user applications, programming tools, and games. Specifically:
 
 \begin{itemize}
-\Item CelarFTP\footnote{\url{http://celerftp.sourceforge.net/}}
-and FileBunker\footnote{\url{http://filebunker.sourceforge.net/}} are two SWT desktop applications.
-CelarFTP implements a simple FTP client based on Java and SWT UI library, and
+\Item CelerFTP~\cite{celer} and FileBunker~\cite{filebunker} are two useful
+SWT desktop applications.
+CelerFTP implements a simple FTP client based on Java and SWT UI library, and
 FileBunker is a file backup application which uses one or more GMail accounts as its backup repository.
 
-\Item  AnyEdit\footnote{\url{http://andrei.gmxhome.de/anyedit/}}, FileSync4Eclipse\footnote{\url{andrei.gmxhome.de/filesync/}}, and
-EclipseRunner\footnote{\url{http://eclipserunnerplugin.googlecode.com/}} are three popular eclipse plugins.
+\Item  AnyEdit~\cite{anyedit}, FileSync~\cite{filesync}, and
+EclipseRunner~\cite{eclipserunner} are three popular eclipse plugins.
 AnyEdit adds several new tools to  Eclipse editors, output consoles, and main menu. 
-FileSync4Eclipse is a file synchronisation tool to keep files outside of Eclipse projects in synchronized
+FileSync is a file synchronisation tool to keep files outside of Eclipse projects in synchronized
 with Eclipse project files. EclipseRunner extends capability of running launch configurations in Eclipse IDE.
 
-\Item  S3dropbox\footnote{\url{http://s3dropbox.googlecode.com}} and SudokuPuzzleSolver\footnote{\url{http://sudokupuzzlesol.sourceforge.net/}}
+\Item  S3dropbox~\cite{s3dropbox} and SudokuPuzzleSolver~\cite{sudokusolver}
 are two Swing desktop applications. S3dropbox implements a client that allows users
@@
 
-\Item  MyTracks\footnote{\url{http://code.google.com/p/mytracks/}}, Fennec\footnote{\url{http://www.mozilla.org/en-US/mobile/}},
-and SGTPuzzles\footnote{\url{http://chris.boyle.name/projects/android-puzzles}} are three Android applications.
+\Item  MyTracks~\cite{mytracks}, Fennec~\cite{fennec},
+and SGTPuzzles~\cite{sgtpuzzles} are three Android applications.
 MyTracks, developed by Google, records users' GPS tracks in outdoor activities, and provides
@@
  \hline
- CelarFTP (3.0 alpha) &  2293 &  20 &  165  \\
+ CelerFTP (3.0 alpha) &  2293 &  20 &  165  \\
  \hline
@@
 \hline \hline
- SWT (3.6.2)&  20297 &  143 &  1374  \\
+ SWT (3.6.2)&  xxxxx &  xxx &  xxxx  \\
 \hline
- Eclipse plugin development (3.6.2)&  20297 &  143 &  1374  \\
+ Eclipse plugin development (3.6.2)&  xxxxx &  xxx &  xxxx  \\
 \hline
-Swing (1.6)&  20297 &  143 &  1374  \\
+Swing (1.6)&  xxxxx &  xxx &  xxxx  \\
 \hline
- Android (3.6)&  20297 &  143 &  1374  \\
+ Android (3.6)&  xxxxx &  xxx &  xxxx  \\
 \hline
@@
 used in our evaluation. Column ``LOC'' is the number of lines
-of code, as counted by LOCC~\cite{}.  Each program is analyzed
+of code, as counted by LOCC~\cite{locc}.  Each program is analyzed
 together with its dependent GUI framework, as listed in
@@
 We run our tool on each subject with three call graph construction
-algorithms: RTA~\cite{}, 0-CFA, and 1-CFA~\cite{}.  When running
+algorithms: RTA~\cite{rta}, 0-CFA, and 1-CFA~\cite{kcfa}.  When running
 each call graph construction algorithm on Android applications, we
-use two configurations: with and without taming reflection (Section~\ref{}).
-$k$-CFA ($k >$ 1) algorithm
-does not scale to large programs, and thus is not used in this experiment
+use two configurations: with and without the reflection-aware transformation
+(Section~\ref{sec:cg}).  We did not use more expensive algorithms like $k$-CFA ($k >$ 1),
+because they can not scale to large programs.
 
-SGTPuzzler is the only subject that uses native methods to interact with
+We inspect the source code of each subject to determine whether any
+native methods or project-specific GUI interaction patterns are implemented.
+We found SGTPuzzler is the only subject that uses native methods to interact with
 underlying operating systems. Thus, we manually added XXX \CodeIn{@CalledByNative}
-annotations after inspecting its source code. In addition, two subjects XXXX and XXX use a self-defined
-way to interact with the GUI framework. In this experiment, none of the paper
+annotations for it. Also two subjects XXXX and XXX employ a self-defined
+way to interact with the GUI framework. For example, the \CodeIn{safeInvokeXX}
+method in the XXX subject first checks whether the current thread is the UI-thread, and
+then determines whether to direct access a GUI object or wrap the code with
+message passing. We add XX heuristic filtering rules for those methods, to indicate
+that they are safe to be invoked from any thread. In this experiment, none of the paper
 authors was faimilar with the subjects; but we found it is quite easy
@@
 
-Table~\ref{table:results} show the errors in
-our subject programs, and Table~\ref{table:filters} show
-the effect of applying each heuristic filter.
+%Table~\ref{table:results} show the errors in
+%our subject programs, and Table~\ref{table:filters} show
+%the effect of applying each heuristic filter.
 
-\subsubsection{Errors in Multithreaded GUI}
+\subsubsection{Errors in Multithreaded GUI Applications}
 \label{sec:errors}
 
-characteristic of errors in various subjects
+Table~\ref{table:results} tabulates the results of running our
+tool with three different call graph construction algorithms
+on the subject programs. From these results, we can see our
+tool found real errors from each subject on all the 
+supported GUI frameworks. The results vary slightly according
+to the specific call graph algorithm used. In general, using
+the 1-CFA algorithm finds most errors (XXX in total) with least
+warnings (XXX in total). The tradeoffs of using other
+algorithms will be explained in Section~\ref{sec:reflectionaware}.
 
-False positive rate, and why?
+We further examined the detailed results for each subject.
+Among xxx warnings issued by using the 1-CFA algorithm, xxx
+are false positives, xxx are redundant:
+they have the same causes as the rest xxx warnings. (XXX why there
+are FP and redundant warnings?)
 
-redundant rate
-
-response
-
-Swing
-
-Swing is a single-threaded GUI toolkit, and is not thread-safe. 
-As the official documentation states, all Swing code must be executed in the UI-thread and
-invoking Swing code from multiple threads risks thread interference or memory-consistency errors.
-
-Since Swing does not provide any run-time checks for invalid thread access and, most of the time,
-programmers can get away with an apparently ``well behaved'' Swing GUI that actually breaks the
-single-thread rule.
-
-Example in Swing
 \begin{figure}[t]
@@
 \vspace*{-2.0ex} \Caption{{\label{fig:swingerror} A
-potential invalid thread error reported by our tool
+potential invalid thread access error reported by our tool
 in the S3dropbox Swing application. The error occurs when
-the invocation of \CodeIn{deleteCurrentBucket} at line 63 throws
-an exception, which lead to the \CodeIn{deleteError} method
+the method \CodeIn{deleteCurrentBucket} invoked at line 63 throws
+an exception, which leads method \CodeIn{deleteError} to
 access a Swing GUI object \CodeIn{display} at line 79 from
-a non-UI thread. This error has been confirmed by S3dropbox developers.
+a non-UI thread. This error is previously-unknown, and has been confirmed by the S3dropbox developers.
 }} %\vspace{-5mm}
@@
 
-Example in  Eclipse plugin
+Figures~\ref{fig:swingerror} amd~\ref{fig:pluginerror} show
+two real errors our tool has found. Figure~\ref{fig:swingerror}
+shows a potential invalid thread access error in the S3dropbox
+program. This error happens when the \CodeIn{deterCurrentBucket}
+method at line 63 throws an exception. This error can be hard to
+detect by testing, since the test must  execute that specific exception-handling
+path. We reported this error to the S3dropbox developers. Tom Czarniecki,
+a key developer of S3dropbox confirmed this potential single-thread
+violation. He mentioned that the S3dropbox project has already
+used certain design patterns and practice to avoid such violations (e.g.,
+actions for UI interaction are encapsulated into a \CodeIn{Worker} interface),
+but they still overlooked  the reported code snippet.
+
+Another reason of missing this violation is because some GUI frameworks like Swing
+do not provide any run-time checks for invalid thread access. Most
+of the time, programmers can get away with an apparently ``well behaved'' Swing
+GUI that actually breaks the single-thread rule. However, As clearly
+indicated in the official documentation, Swing is a single-threaded GUI
+toolkit, and is not thread-safe. All Swing code must be executed in the UI-thread and
+invoking Swing code from multiple threads risks thread interference
+or memory-consistency errors, particularly in the multi-core era.
+
 \begin{figure}[t]
@@
 \begin{alltt} 
+/* com.eclipserunner.views.impl.RunnerView */
 179.private void initializeResourceChangeListener() \{
@@
 \vspace*{-2.0ex} \Caption{{\label{fig:pluginerror} A
-potential invalid thread error reported by our tool
-in the EclipseRunner plugin. The \CodeIn{IResourceChangeListener} object
-added at line 180 is invoked by a non-UI thread, and the
-callback method \CodeIn{resourceChanged} calls the \CodeIn{refresh}
-method at line 414. However, the \CodeIn{refresh} method
-directly accesses the GUI objects (at line 415) and triggers the error.
+potential invalid thread access error reported by our tool
+for the EclipseRunner plugin. In Eclipse, the
+callback method \CodeIn{resourceChanged} at line 181
+is invoked by non-UI threads when a \CodeIn{ResourceChangeEvent}
+happens. However, the \CodeIn{refresh} method directly accesses
+GUI objects (refresh the view at line 415) without any
+protection and thus triggers the error.
 This error has been reported by other users 13 months after the
@@
 \end{figure}
+
+Figure~\ref{fig:pluginerror} shows an error found in the EclipseRunner
+plugin. This error is event-related. It happens when a 
+\CodeIn{ResourceChangeEvent} happen, which then invokes the \CodeIn{refresh}
+method at line 415 to update the user interface. In EclipseRunner
+, the \CodeIn{refresh} method has been
+called by XXX different methods in non-UI threads. Thus, our
+tool issues XXX separate warnings for each caller method to indicate
+different ways to trigger this error, despite that all these xxx warnings
+acutally have the same error cause.
+
+As reflected in our experiments, we found GUI developers have already
+used design patterns, runtime checks, and testing to avoid violating
+the single-thread rule. However, due to the huge space of
+possible UI interactions, potential
+invalid thread access errors still exist in many corner cases and
+can be hard to find. Thus, a static analysis as presented in this paper
+would be useful.
 
@@
 
-\subsubsection{Comparison with a Straightforward Approach}
+\subsubsection{Comparing to a Straightforward Approach}
 \label{sec:straightforward}
@@
 is to check every method to determine whether all GUI-accessing code
-is probably wrapping by safe methods. This approach
+is probably wrapping by safe methods. If not, this approach
 issues a warning for every violation. 
@@
 
-We implemented this straightforward approach and experimentally compared its
-effectiveness with the technique presented in Section~\ref{}.
-The far right column in Table~\ref{table:results} shows its result.
+We implemented this straightforward approach and experimentally compared it
+with the technique presented in Section~\ref{sec:technique}.
+The far right column in Table~\ref{table:results} shows the results.
 The results show that this straightforward approach can identified every
-error as our technique does, but issues a tremendous number of false
-positives. The primary reason is that this simple approach
+error as our technique does, but leads to a tremendous number of false
+positives and redundant warnings. The primary reason is that this simple approach
 does not globally reason about calling relationship between
@@
 
-\subsubsection{Call Graph Construction Algorithms}
+\subsubsection{Comparing Call Graph Construction Algorithms}
 \label{sec:reflectionaware}
 
-We compare three call graph construction algorithms, RTA, 0-CFA, and 1-CFA,
-in our experiments. As shown in Table~\ref{table:results},  XXX found
+We next compare three call graph construction algorithms (RTA, 0-CFA, and 1-CFA)
+used in our experiments. As shown in Table~\ref{table:results},  XXX found
 more errors with less warnings than the XXX and XXXX algorithms. This
@@
 built by 1-CFA are significantly larger, XXX, the algorithm still runs
-in a practical amouont of time as presented in Section~\ref{}. For example,
+in a practical amouont of time. For example,
 our tool finished building the call graph for the largest subject (xxx)
@@
 
-The results in Table~\ref{table:results} also shown that using a reflection-aware
+The results in Table~\ref{table:results} also show that using a reflection-aware
 call graph construction algorithm is critical in finding errors in Android
-applications. None of the errors in the studied Android applications
-can be found by using normal call graph construction algorithms, because their 
-limitation in handling reflection.
+applications. None of the errors from the Android applications
+can be found by using normal call graph construction algorithms, due to
+their limitation in handling platform-specific reflections. Without
+replacing the reflection calls with explicit object creation instructions,
+a call graph construction algorithm will
+conclude that no GUI object has been created, and thus miss many UI-related
+edges in the resulting graph.
 
@@
 
-\noindent \textbf{\textit{Summary.}} XX The 1-CFA call graph construction
-algorithm is more effective in finding errors. XXX. Our reflection-aware call
-graph construction algorithm is useful to find errors in
+\noindent \textbf{\textit{Summary.}} Using the 1-CFA call graph construction
+algorithm is more effective in finding errors, and our reflection-aware call
+graph construction algorithm is critical to find errors on
 Android applications.
 
-\subsubsection{Heuristic Filters}
+\subsubsection{Evaluating Heuristic Filters}
 \label{sec:filters}
@@
 We measure the effectiveness of the proposed heuristic filters of
-Section~\ref{} via the number of removed warnings.
+Section~\ref{sec:heuristic} via the number of removed false positives and
+redundant warnings.
 
-Table~\ref{table:filters} tabulates the results. The results show that
-our technique outputs thousnads of warnings for each subject, due to
-the conservative nature of static analysis.  However, the
-set of proposed heuristic filters are highly effectively. They
+Table~\ref{table:filters} tabulates the results. Although
+our static analysis outputs thousands of warnings for each
+subject, the proposed heuristic filters effectively reduces
+the number. On average, they
  reduce the false positive numbers and redundant warnings by up to a factor of
@@
 heuristics can still remove most of them.
-Heuristic filter, effective.
+%Heuristic filter, effective.
 
@@
  \fontsize{9pt}{\baselineskip}\selectfont
+\setlength{\tabcolsep}{.30\tabcolsep}
 \hspace*{-0.2cm}
-\begin{tabular}{|l||c|c|c|c|}
+\begin{tabular}{|l||c|c|c|c|c|c|}
 \hline
- Program  & \#Warning & \#Warning & \#Warning & \#Warning \\
- (version) & $F_1$ & $F_2$ & $F_3$&$F_4$ \\
+ Subject & Before & \#Warning & \#Warning & \#Warning & \#Warning& \#Warning \\
+ Program & Filtering & $F_1$ & $F_2$ & $F_3$&$F_4$ & $F_5$\\
 \hline \hline
-\multicolumn{5}{|l|}{SWT desktop applications}   \\
+\multicolumn{7}{|l|}{SWT desktop applications}   \\
  \hline
- xxx &  xxxx &  xx &  xxx & xx \\
+ xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
  \hline
- xxx &  xxxx &  xx &  xxx & xx \\
+ xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
  \hline
- xxx &  xxxx &  xx &  xxx & xx \\
+ xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
  \hline
  \hline
-\multicolumn{5}{|l|}{Eclipse plugins}   \\
+\multicolumn{7}{|l|}{Eclipse plugins}   \\
  \hline
- xxx &  xxxx &  xx &  xxx & xx \\
+ xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
  \hline
- xxx &  xxxx &  xx &  xxx & xx \\
+ xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
  \hline
- xxx &  xxxx &  xx &  xxx & xx \\
+ xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
  \hline
  \hline
-\multicolumn{5}{|l|}{Swing desktop applications}   \\
+\multicolumn{7}{|l|}{Swing desktop applications}   \\
  \hline
- xxx &  xxxx &  xx &  xxx & xx \\
+ xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
  \hline
- xxx &  xxxx &  xx &  xxx & xx \\
+ xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
  \hline
- xxx &  xxxx &  xx &  xxx & xx \\
+ xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
  \hline
  \hline
-\multicolumn{5}{|l|}{Android mobile applications}   \\
+\multicolumn{7}{|l|}{Android mobile applications}   \\
  \hline
- xxx &  xxxx &  xx &  xxx & xx \\
+ xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
  \hline
- xxx &  xxxx &  xx &  xxx & xx \\
+ xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
  \hline
- xxx &  xxxx &  xx &  xxx & xx \\
+ xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
 \hline
@@
 \Caption{{\label{table:filters}Number of warnings after applying a set of
-heuristic filters (Section~\ref{}). Column ``\#Warning $F_i$''
+heuristic filters (Section~\ref{sec:heuristic}). Column ``\#Warning $F_i$''
 represents the number of remaining warnings after applying
 filters 1 -- $i$, and the number of last column is taken
-from Table~\ref{} (Subcolumn ``\#Warning'' under column ``1-CFA / with taming reflection'').} }
+from Table~\ref{table:results} (Subcolumn ``\#Warning'' under column ``1-CFA / with taming reflection'').} }
 \end{table}
@@
 Our experiments also demonstrate that our approach has good scalability.
-Our tool has analyzed xxx LOC in total, and together with all dependent libraries,
-the largest subject our approach can analyze and detect errors has
-over XXX LOC, xx classes, and xxx methods.
+Together with all dependent library code, our tool has analyzed
+XXX LOC in total  XXX LOC in the largest program.
+%Our tool has analyzed xxx LOC in total, and together with all dependent libraries,
+%the largest subject our approach can analyze and detect errors has
+%over XXX LOC, xx classes, and xxx methods.
 
@@
 
-There are two major threats to validity in our evaluation. 
+There are two threats to validity in our evaluation. 
 The major threat is the degree to which the subject programs
@@
 in our implementation. It is still unknown whether using other 
-call graph construction algorithms such XFA~\cite{} may achieve better results.
+call graph construction algorithms such as XTA~\cite{xta} may achieve better results.
 
@@
 to remedy this limitation is to design an analysis to identify
-such threads. Second, our tool cannot compute call relationships
+those threads created before a GUI is launched.
+Second, our tool cannot compute call relationships
 for inter-process communication between components. It also
@@
 \subsubsection{Experimental Conclusions}
-Findings: programmers have noted this problem, but often overlook special cases like error handle, subtype
 
- Reporting on violations is fine but what is more important are the pracitces and patterns that need to be adopted to make it easier to avoid the issue in the first place.
+Invalid thread access errors significantly affect the usability of
+a GUI application, but can be subtle to find. In practice, programmers
+have designed practices and patterns to avoid such errors in the first
+place, but can easily overlook corner cases like exception-handling
+methods.
+
+The technique presented in this paper offers a promising solution.
+Compared with the straightforward approach to check every
+GUI accessing code isolatedly, our technique produces significantly
+less warniings. The reflection-aware call graph construction algorithm
+is critical in detecting errors for Android programs, and our
+proposed heuristic filtering rules are useful in reducing programmers'
+burden to inspect the output result.
+
+%Findings: programmers have noted this problem, but often overlook special cases like error handle, subtype
+
+% Reporting on violations is fine but what is more important are the pracitces and patterns that need to be adopted to make it easier to avoid the issue in the first place.
 That is why there is a Worker interface in this project

### 2012-01-23 GUIErrorDetector/paper/evaluation.tex
add refs and fix the typos

@@
 
-%Our experiment investigate the followinig four research questions:
+%Our experiment investigate the following four research questions:
 
@@
 We use a set of open-source projects from Sourceforge, Google code and Eclipse plugin
-market as evaluation subjects. We choose subjects for each supported GUI framework
-as follows. We search the framework keywords (e.g., ``Java Swing'' or ``Java SWT'')
-in the above three source repositories, and select subjects based on the following
-criterias: first, the subject must be a multithread GUI application, not
+market as evaluation subjects. To choose subjects for each supported GUI framework,
+we first search the framework keywords (e.g., ``Java Swing'' or ``Java SWT'')
+in the above three source repositories, and then select subjects based on the following
+criterias. First, the subject must be a multithreaded GUI application, not
 an open library. Second, the subject must undergone at least two years of active development,
 and is listed in the first 3 results pages based on popularity. This permits us
-to exclude all pre-mature subjects, which may contain obvious errors.
+to exclude many pre-mature subjects that may contain obvious errors.
 
 The subjects used in our experiment are shown in Table~\ref{table:subjects}. Our
-subjects range from end-user applications, programming tools, to games. Specifically:
+subjects include end-user applications, programming tools, and games. Specifically:
 
 \begin{itemize}
-\Item CelarFTP\footnote{\url{http://celerftp.sourceforge.net/}}
-and FileBunker\footnote{\url{http://filebunker.sourceforge.net/}} are two SWT desktop applications.
-CelarFTP implements a simple FTP client based on Java and SWT UI library, and
+\Item CelerFTP~\cite{celer} and FileBunker~\cite{filebunker} are two useful
+SWT desktop applications.
+CelerFTP implements a simple FTP client based on Java and SWT UI library, and
 FileBunker is a file backup application which uses one or more GMail accounts as its backup repository.
 
-\Item  AnyEdit\footnote{\url{http://andrei.gmxhome.de/anyedit/}}, FileSync4Eclipse\footnote{\url{andrei.gmxhome.de/filesync/}}, and
-EclipseRunner\footnote{\url{http://eclipserunnerplugin.googlecode.com/}} are three popular eclipse plugins.
+\Item  AnyEdit~\cite{anyedit}, FileSync~\cite{filesync}, and
+EclipseRunner~\cite{eclipserunner} are three popular eclipse plugins.
 AnyEdit adds several new tools to  Eclipse editors, output consoles, and main menu. 
-FileSync4Eclipse is a file synchronisation tool to keep files outside of Eclipse projects in synchronized
+FileSync is a file synchronisation tool to keep files outside of Eclipse projects in synchronized
 with Eclipse project files. EclipseRunner extends capability of running launch configurations in Eclipse IDE.
 
-\Item  S3dropbox\footnote{\url{http://s3dropbox.googlecode.com}} and SudokuPuzzleSolver\footnote{\url{http://sudokupuzzlesol.sourceforge.net/}}
+\Item  S3dropbox~\cite{s3dropbox} and SudokuPuzzleSolver~\cite{sudokusolver}
 are two Swing desktop applications. S3dropbox implements a client that allows users
@@
 We run our tool on each subject with three call graph construction
-algorithms: RTA~\cite{}, 0-CFA, and 1-CFA~\cite{}.  When running
+algorithms: RTA~\cite{rta}, 0-CFA, and 1-CFA~\cite{kcfa}.  When running
 each call graph construction algorithm on Android applications, we
-use two configurations: with and without taming reflection (Section~\ref{}).
-$k$-CFA ($k >$ 1) algorithm
-does not scale to large programs, and thus is not used in this experiment
+use two configurations: with and without the reflection-aware transformation
+(Section~\ref{sec:cg}).  We did not use more expensive algorithms like $k$-CFA ($k >$ 1),
+because they can not scale to large programs.
 
-SGTPuzzler is the only subject that uses native methods to interact with
+We inspect the source code of each subject to determine whether any
+native methods or project-specific GUI interaction patterns are implemented.
+We found SGTPuzzler is the only subject that uses native methods to interact with
 underlying operating systems. Thus, we manually added XXX \CodeIn{@CalledByNative}
-annotations after inspecting its source code. In addition, two subjects XXXX and XXX use a self-defined
-way to interact with the GUI framework. In this experiment, none of the paper
-authors was faimilar with the subjects; but we found it is quite easy
+annotations for it. Also two subjects XXXX and XXX employ a self-defined
+way to interact with the GUI framework. For example, the \CodeIn{safeInvokeXX}
+method in the XXX subject first checks whether the current thread is the UI-thread, and
+then determines whether to direct access a GUI object or wrap the code with
+message passing. We add XX heuristic filtering rules for those methods, to indicate
+that they are safe to be invoked from any thread. In this experiment, none of the paper
+authors was familar with the subjects; but we found it is quite easy
 to add extra those annotations and heuristic filters and finished these
@@
 \hspace*{-0.2cm}
-\setlength{\tabcolsep}{.75\tabcolsep}
+\setlength{\tabcolsep}{.65\tabcolsep}
 \begin{tabular}{|l||c|c|c||c|c|c||c|c|c||c|c|}
@@
  \hline
- xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx& xx & xx \\
+ S3dropbox &  xxxx &  xx &  xxx & xx & xx & xx& xx & 1 & 1 & 210 & xx \\
  \hline
- xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx& xx & xx \\
- \hline
- xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx& xx & xx \\
+  Sudoku Solver&  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx& 356 & xx \\
  \hline
@@
 
-Table~\ref{table:results} show our results in finding errors in
-multithreaded GUI applications, and Table~\ref{table:filters} show
-the results of applying each heuristic filter.
+%Table~\ref{table:results} show the errors in
+%our subject programs, and Table~\ref{table:filters} show
+%the effect of applying each heuristic filter.
 
-\subsubsection{Errors in Multithreaded GUI}
+\subsubsection{Errors in Multithreaded GUI Applications}
 \label{sec:errors}
 
-Swing is a single-threaded GUI toolkit, and is not thread-safe. 
-As the official documentation states, all Swing code must be executed in the UI-thread and
-invoking Swing code from multiple threads risks thread interference or memory-consistency errors.
+Table~\ref{table:results} tabulates the results of running our
+tool with three different call graph construction algorithms
+on the subject programs. From these results, we can see our
+tool found real errors from each subject on all the 
+supported GUI frameworks. The results vary slightly according
+to the specific call graph algorithm used. In general, using
+the 1-CFA algorithm finds most errors (XXX in total) with least
+warnings (XXX in total). The tradeoffs of using other
+algorithms will be explained in Section~\ref{sec:reflectionaware}.
 
-Since Swing does not provide any run-time checks for invalid thread access and, most of the time,
-programmers can get away with an apparently ``well behaved'' Swing GUI that actually breaks the
-single-thread rule.
+We further examined the detailed results for each subject.
+Among xxx warnings issued by using the 1-CFA algorithm, xxx
+are false positives, xxx are redundant:
+they have the same causes as the rest xxx warnings. (XXX why there
+are FP and redundant warnings?)
 
-Example in Swing
 \begin{figure}[t]
@@
 
+Figure~\ref{fig:pluginerror} shows an error found in the EclipseRunner
+plugin. This error is event-related. It happens when a 
+\CodeIn{ResourceChangeEvent} happen, which then invokes the \CodeIn{refresh}
+method at line 415 to update the user interface. In EclipseRunner
+, the \CodeIn{refresh} method has been
+called by XXX different methods in non-UI threads. Thus, our
+tool issues XXX separate warnings for each caller method to indicate
+different ways to trigger this error, despite that all these xxx warnings
+acutally have the same error cause.
+
+As reflected in our experiments, we found GUI developers have already
+used design patterns, runtime checks, and testing to avoid violating
+the single-thread rule. However, due to the huge space of
+possible UI interactions, potential
+invalid thread access errors still exist in many corner cases and
+can be hard to find. Thus, a static analysis as presented in this paper
+would be useful.
+
 \vspace{1mm}
 
-\noindent \textbf{\textit{Summary.}}
+\noindent \textbf{\textit{Summary.}}Our technique finds real errors
+in multithreaded GUI applications on four different frameworks with
+an acceptable false positive rate.
 
-\subsubsection{Comparison with a Straightforward Approach}
+\subsubsection{Comparing to a Straightforward Approach}
 \label{sec:straightforward}
@@
 straightforward way to detect potential invalid error
-is to check every method to determine whether all GUI-accessing
-are probably wrapping by safe methods. If not, this
-approach issues warnings.
+is to check every method to determine whether all GUI-accessing code
+is probably wrapping by safe methods. If not, this approach
+issues a warning for every violation. 
+%If not, this approach issues warnings.
 
-We implemented this naive approach and experimentally compared its
-results with the technique presented in Section~\ref{}.
-
-Algorithm:
-
-1. find all UI direct accessing methods
-
-2. to see is this methods called by non-safe
-
-The primary difference
+We implemented this straightforward approach and experimentally compared it
+with the technique presented in Section~\ref{sec:technique}.
+The far right column in Table~\ref{table:results} shows the results.
+The results show that this straightforward approach can identified every
+error as our technique does, but leads to a tremendous number of false
+positives and redundant warnings. The primary reason is that this simple approach
+does not globally reason about calling relationship between
+threads, UI-accessing methods, and safe methods, thus it often incorrectly
+classifies GUI accessing code which will never be executed
+in a non-UI thread as errenous. Furthermore, our technique
+outputs a method call chain in the error report, which can help
+developers understand how an invalid thread access error is triggered.
 
@@
 
-\noindent \textbf{\textit{Summary.}}
+\noindent \textbf{\textit{Summary.}} Our technique provides
+richer contextually information for a potential error, and 
+is significantly more precise than the straightforward approach.
 
-\subsubsection{Call Graph Construction Algorithms}
+\subsubsection{Comparing Call Graph Construction Algorithms}
 \label{sec:reflectionaware}
+
+We next compare three call graph construction algorithms (RTA, 0-CFA, and 1-CFA)
+used in our experiments. As shown in Table~\ref{table:results},  XXX found
+more errors with less warnings than the XXX and XXXX algorithms. This
+is because RTA and 0-CFA do not consider the context XXX, and it may
+mix the same methods called by different callers. Although the call graphs
+built by 1-CFA are significantly larger, XXX, the algorithm still runs
+in a practical amouont of time. For example,
+our tool finished building the call graph for the largest subject (xxx)
+within xxx minutes.
+
+The results in Table~\ref{table:results} also show that using a reflection-aware
+call graph construction algorithm is critical in finding errors in Android
+applications. None of the errors from the Android applications
+can be found by using normal call graph construction algorithms, due to
+their limitation in handling platform-specific reflections. Without
+replacing the reflection calls with explicit object creation instructions,
+a call graph construction algorithm will
+conclude that no GUI object has been created, and thus miss many UI-related
+edges in the resulting graph.
 
@@
 
-\noindent \textbf{\textit{Summary.}}
+\noindent \textbf{\textit{Summary.}} Using the 1-CFA call graph construction
+algorithm is more effective in finding errors, and our reflection-aware call
+graph construction algorithm is critical to find errors on
+Android applications.
 
-\subsubsection{Heuristic Filters}
+\subsubsection{Evaluating Heuristic Filters}
 \label{sec:filters}
+
+We measure the effectiveness of the proposed heuristic filters of
+Section~\ref{sec:heuristic} via the number of removed false positives and
+redundant warnings.
+
+Table~\ref{table:filters} tabulates the results. Although
+our static analysis outputs thousands of warnings for each
+subject, the proposed heuristic filters effectively reduces
+the number. On average, they
+ reduce the false positive numbers and redundant warnings by up to a factor of
+XXX. Specifically, filters $XX_i$ and $XX_j$  identified xx\% of
+the warnings as likely false positives, and filters $YY_i$
+and $YY_j$ identified YY\% of the warnings as redundant warnings.
+We further manually check each filtered warning, and found no
+real errors have been removed.
 
@@
 
-\noindent \textbf{\textit{Summary.}}
-Heuristic filter, effective.
+\noindent \textbf{\textit{Summary.}} Although a static analysis may
+issue false postivies or redundant reports, a set of well-designed
+heuristics can still remove most of them.
+%Heuristic filter, effective.
 
@@
 \Caption{{\label{table:filters}Number of warnings after applying a set of
-heuristic filters (Section~\ref{}). Column ``\#Warning $F_i$''
+heuristic filters (Section~\ref{sec:heuristic}). Column ``\#Warning $F_i$''
 represents the number of remaining warnings after applying
 filters 1 -- $i$, and the number of last column is taken
-from Table~\ref{} (Subcolumn ``\#Warning'' under column ``1-CFA / with taming reflection'').} }
+from Table~\ref{table:results} (Subcolumn ``\#Warning'' under column ``1-CFA / with taming reflection'').} }
 \end{table}
+
+\subsection{Discussions}
+
+We next discuss several important issues in our evaluation.
 
@@
 Our experiments also demonstrate that our approach has good scalability.
-Our tool has analyzed xxx LOC in total, and together with all dependent libraries,
-the largest subject our approach can analyze and detect errors has
-over XXX LOC, xx classes, and xxx methods.
-
-\subsection{Discussions}
+Together with all dependent library code, our tool has analyzed
+XXX LOC in total  XXX LOC in the largest program.
+%Our tool has analyzed xxx LOC in total, and together with all dependent libraries,
+%the largest subject our approach can analyze and detect errors has
+%over XXX LOC, xx classes, and xxx methods.
 
@@
 
-Our evaluation was limited in several ways. First, the studied
-subjects were selected with a bias towards popularity. Second,
-our tool cannot compute call relationships
-for inter-process communication between components. Missing
-Future work could evaluate our technique on more subjects, and
-investigate the false negative rate.
+There are two threats to validity in our evaluation. 
+The major threat is the degree to which the subject programs
+used in our experiment are representative of true practice.
+In our evaluation, the studied subjects were selected with a bias towards popularity from
+three open-source repositories. Another threat is that we only employed three
+well-known call graph construction algorithms (i.e., RTA, 0-CFA, and 1-CFA) 
+in our implementation. It is still unknown whether using other 
+call graph construction algorithms such as XTA~\cite{xta} may achieve better results.
+
+\subsubsection{Limitations}
+
+Our technique is limited in two aspects. First, it only considers
+non-UI threads that are spawned by the UI-thread after the GUI
+is initialized, and ignores other possible non-UI threads
+that are created during the pre-initialization GUI work. One way
+to remedy this limitation is to design an analysis to identify
+those threads created before a GUI is launched.
+Second, our tool cannot compute call relationships
+for inter-process communication between components. It also
+requires users to manually add annotations to characterize
+call relationships that involve native methods. This limitation
+may lead to false negatives. Investigating the false positive
+rate is ongoing work.
+
+%Future work could evaluate our technique on more subjects, and
+%investigate the false negative rate.
+
+%our technique requires developers to manually
+%add annotations to provide call relationships
+%Second,
+
+%Third, for subject program
+%that uses native methods,
 
 \subsubsection{Experimental Conclusions}
-Findings: programmers have noted this problem, but often overlook special cases like error handle, subtype
 
- Reporting on violations is fine but what is more important are the pracitces and patterns that need to be adopted to make it easier to avoid the issue in the first place.
+Invalid thread access errors significantly affect the usability of
+a GUI application, but can be subtle to find. In practice, programmers
+have designed practices and patterns to avoid such errors in the first
+place, but can easily overlook corner cases like exception-handling
+methods.
+
+The technique presented in this paper offers a promising solution.
+Compared with the straightforward approach to check every
+GUI accessing code isolatedly, our technique produces significantly
+less warnings. The reflection-aware call graph construction algorithm
+is critical in detecting errors for Android programs, and our
+proposed heuristic filtering rules are useful in reducing programmers'
+burden to inspect the output result.
+
+%Findings: programmers have noted this problem, but often overlook special cases like error handle, subtype
+
+% Reporting on violations is fine but what is more important are the practices and patterns that need to be adopted to make it easier to avoid the issue in the first place.
 That is why there is a Worker interface in this project

### 2012-01-23 GUIErrorDetector/paper/introduction.tex
add refs and fix the typos

@@
 
-%It may work during development, but like most concurrent bugs, you'll start to see weird exceptions come up that seem completely unrelated, and occur non-deterministly - usually spotted AFTER you've shipped by real users.
+%It may work during development, but like most concurrent bugs, you'll start to see weird exceptions come up that seem completely unrelated, and occur non-- usually spotted AFTER you've shipped by real users.
 Not good.
@@
 \vspace*{-2.0ex} \Caption{{\label{fig:report} A report
-generated by our tool to reveal the pontential error in
+generated by our tool to reveal the potential error in
 Figure~\ref{fig:androiderror}. This report indicates a 
@@
 two dominating GUI frameworks in developing desktop Java applications.
-Eclipse and its plugin development envrionment is the de-facto standard
+Eclipse and its plugin development environment is the de-facto standard
 IDE for Java. Android is the No. 1 platform for
@@
 and our proposed
-heuristics are useful (it signficantly reduces the number of
+heuristics are useful (it significantly reduces the number of
 false positives and redundant warnings).
@@
 from 4 different platforms over XXX LOC to show the usefulness
-of the proposed techinque (Section~\ref{sec:evaluation}).
+of the proposed technique (Section~\ref{sec:evaluation}).
 

### 2012-01-23 GUIErrorDetector/paper/technique.tex
add refs and fix the typos

@@
 from each \CodeIn{Thread.start()} node.
-Specifially, it uses a queue to keep track of all visited nodes, and
+Specifically, it uses a queue to keep track of all visited nodes, and
 then checks every successive node to be visited (line 12);
@@
 The basic idea to replace reflection calls with explicit object
-creation instructions, pretending the corresponding concreate object
+creation instructions, pretending the corresponding concrete object
 has been created.  The algorithm is shown in Figure~\ref{fig:cgalgorithm}.
@@
 returns a new object of the class set. The reflection-aware call graph
-construction algorithm is indepdent of the underlying call graph algorithm;
+construction algorithm is independent of the underlying call graph algorithm;
 any existing algorithm can be used to construct the resulting graph at line 8.
@@
 functionalities. When a plugin starts, Eclipse
-calls back the overrided extension points to handle the
+calls back the overridden extension points to handle the
 upcoming events. We customize our technique for Eclipse plugin as follows:
@@
 
-\item \textbf{Call graph entry nodes: } all overriden SWT
+\item \textbf{Call graph entry nodes: } all overridden SWT
 GUI event handling methods\footnote{Eclipse plugin is built
@@
 % a plugin's \CodeIn{ui} package.  Such methods are normally called by the eclipse framework
-%by the UI thread. XXX This rule, though quite heuristical, works quite well in practice.
+%by the UI thread. XXX This rule, though quite , works quite well in practice.
 
@@
 
-\item \textbf{Call graph entry nodes: } all overriden callback methods in 
-Swing's UI listerner classes are called from the UI thread. We treat those callback
+\item \textbf{Call graph entry nodes: } all overridden callback methods in 
+Swing's UI listener classes are called from the UI thread. We treat those callback
 methods as the entry nodes.
@@
 %Specifically, for each class, we check whether
-%it is a Swing listerner class. If so, we extract all its overriden callback methods as the call graph entry points.
+%it is a Swing listener class. If so, we extract all its overridden callback methods as the call graph entry points.
  %Such methods are normally called by the eclipse framework
@@
 all public methods from an \CodeIn{Activity} class as call graph entry nodes. Additionally,
-we also add all overriden callback methods in event listener classes as entry nodes.
+we also add all overridden callback methods in event listener classes as entry nodes.
 

### 2012-01-23 GUIErrorDetector/tests/edu/washington/cs/detector/util/TestJarViewer.java
some code for experiment

@@ -3,6 +3,7 @@ package edu.washington.cs.detector.util;
 import java.io.File;
 import java.io.IOException;
 import java.util.Collection;
+import java.util.zip.ZipEntry;
 import java.util.zip.ZipException;
 
 import junit.framework.TestCase;
@@ -42,5 +43,81 @@ public class TestJarViewer extends TestCase {
 		
 		System.out.println("Jar1 content: " + jar1Content.size());
 		System.out.println("Jar2 content: " + jar2Content.size());
+	}
+	
+	//=========== ignore the following, to measure the class/method number for experiment
+	public void testClassNumber() throws ZipException, IOException {
+		int i = 0;
+		int j = 0;
+		String[] files = EclipsePluginCommons.DEPENDENT_JARS.split(Globals.pathSep);
+		files = new String[] {
+				"D:\\research\\guierror\\eclipsews\\GUIErrorDetector\\exp-subjects\\original-android.jar"
+		};
+		for (String file : files) {
+			File jar2 = new File(file);
+			Collection<ZipEntry> entries = JarViewer.getContents(jar2);
+			for (ZipEntry entry : entries) {
+				if (entry.getName().endsWith(".class")) {
+					i++;
+					System.out.println(entry.getName());
+					String clazzName = Utils.translateSlashToDot(entry.getName());
+					clazzName = clazzName.substring(0, clazzName.length() - 6);
+					System.out.println(clazzName);
+					
+					try {
+						Class c = Class.forName(clazzName);
+						j = j + c.getDeclaredMethods().length;
+					} catch (Throwable e) {
+						continue;
+					}
+				}
+				
+			}
+		}
+		System.out.println("Number of class: " + i);
+		System.out.println("Number of method: " + j);
+	}
+	
+	public void testMeasureSwingMethodNumber() throws ZipException, IOException, ClassNotFoundException {
+		File jar2 = new File("D:\\Java\\jdk1.6.0_27\\src.zip");
+		int i = 0;
+		Collection<ZipEntry> entries = JarViewer.getContents(jar2);
+		for (ZipEntry entry : entries) {
+			if (entry.getName().endsWith(".java") && entry.getName().indexOf("swing") != -1) {
+				String name = entry.getName();
+				String clazzName = Utils.translateSlashToDot(name);
+				clazzName = clazzName.substring(0, clazzName.length() - 5);
+				try {
+				Class c = Class.forName(clazzName);
[…]

### 2012-01-23 GUIErrorDetector/src/edu/washington/cs/detector/guider/CGTraverseAndroidGuider.java
Add postDelay in Android's guider

@@ -21,7 +21,10 @@ public class CGTraverseAndroidGuider implements CGTraverseGuider {
 		"android.widget.Filter.filter(Ljava/lang/CharSequence;Landroid/widget/Filter$FilterListener;)V",
 		"android.net.http.IdleCache.cacheConnection(Lorg/apache/http/HttpHost;Landroid/net/http/Connection;)Z",
 		"android.net.http.RequestQueue$ActivePool.startup()V",
-		"android.webkit.CookieManager.removeExpiredCookie()V"
+		"android.webkit.CookieManager.removeExpiredCookie()V",
+		//two safe methods
+		"android.view.View.post(Ljava/lang/Runnable;)Z",
+		"android.view.View.postDelayed(Ljava/lang/Runnable;J)Z"
 	};
 	
 	@Override

### 2012-01-24 GUIErrorDetector/tests/edu/washington/cs/detector/experiments/straightforward/TestAndroids.java
Add code for the naive approach

@@ -1,0 +1,27 @@
+package edu.washington.cs.detector.experiments.straightforward;
+
+import java.util.Collection;
+
+import com.ibm.wala.classLoader.IMethod;
+import com.ibm.wala.ipa.callgraph.CGNode;
+import com.ibm.wala.ipa.cha.ClassHierarchy;
+import com.ibm.wala.util.graph.Graph;
+
+import edu.washington.cs.detector.experiments.straightforward.UnsafeUIAccessMethodFinder.GUI;
+import edu.washington.cs.detector.util.Utils;
+
+public class TestAndroids {
+
+	/**
+	 * modified the experiment driver to avoid repetition
+	 * */
+    public static void seeNaiveResult(Graph<CGNode> graph, ClassHierarchy cha, String[] packages) {
+    	UnsafeUIAccessMethodFinder finder = new UnsafeUIAccessMethodFinder(graph, packages);
+		finder.setClassHierarchy(cha);
+		finder.setUIAccessDecider(GUI.Android);
+		Collection<IMethod> unsafe = finder.finalAllUnsafeUIAccessMethods();
+		
+		System.out.println("No of unsafe: " + unsafe.size());
+		Utils.dumpCollection(unsafe, "./logs/eclipsepluginnaive.txt");
+	}
+}

### 2012-01-24 GUIErrorDetector/tests/edu/washington/cs/detector/experiments/straightforward/TestEclipsePlugins.java

@@ -1,0 +1,28 @@
+package edu.washington.cs.detector.experiments.straightforward;
+
+import java.util.Collection;
+
+import com.ibm.wala.classLoader.IMethod;
+import com.ibm.wala.ipa.callgraph.CGNode;
+import com.ibm.wala.ipa.cha.ClassHierarchy;
+import com.ibm.wala.util.graph.Graph;
+
+import edu.washington.cs.detector.experiments.straightforward.UnsafeUIAccessMethodFinder.GUI;
+import edu.washington.cs.detector.util.Utils;
+
+public class TestEclipsePlugins {
+
+	/**
+	 * Modified the driver to avoid repetition
+	 * */
+	public static void seeNaiveResult(Graph<CGNode> graph, ClassHierarchy cha, String[] packages) {
+		UnsafeUIAccessMethodFinder finder = new UnsafeUIAccessMethodFinder(graph, packages);
+		finder.setClassHierarchy(cha);
+		finder.setUIAccessDecider(GUI.SWT);
+		Collection<IMethod> unsafe = finder.finalAllUnsafeUIAccessMethods();
+		
+		System.out.println("No of unsafe: " + unsafe.size());
+		Utils.dumpCollection(unsafe, "./logs/eclipsepluginnaive.txt");
+	}
+	
+}

### 2012-01-24 GUIErrorDetector/tests/edu/washington/cs/detector/experiments/straightforward/TestSwtNaive.java

@@ -1,0 +1,64 @@
+package edu.washington.cs.detector.experiments.straightforward;
+
+import java.io.IOException;
+import java.util.Collection;
+
+import com.ibm.wala.classLoader.IMethod;
+
+import edu.washington.cs.detector.CGBuilder;
+import edu.washington.cs.detector.UIAnomalyDetector;
+import edu.washington.cs.detector.CGBuilder.CG;
+import edu.washington.cs.detector.experiments.straightforward.UnsafeUIAccessMethodFinder.GUI;
+import edu.washington.cs.detector.util.Globals;
+import edu.washington.cs.detector.util.Utils;
+import junit.framework.TestCase;
+
+public class TestSwtNaive extends TestCase {
+
+	public void testCelearFTP() throws IOException {
+		String path = "C:\\Users\\szhang\\Downloads\\celerftp0.0.1alpha.jar"
+			+ Globals.pathSep + "C:\\Users\\szhang\\Downloads\\celerftp0.0.1alpha\\celerftp0.0.1alpha\\lib\\swt-windows\\swt.jar";
+		
+		//initialize a UI anomaly detector
+        UIAnomalyDetector detector = new UIAnomalyDetector(path);
+		//configure the call graph builder, use 1-CFA as default
+		CGBuilder builder = new CGBuilder(path);
+		builder.setCGType(CG.RTA);
+		builder.buildCG();
+		
+		String[] packages = new String[]{"org.celerftp"};
+		
+		//check the straightforward approach result
+		UnsafeUIAccessMethodFinder finder = new UnsafeUIAccessMethodFinder(builder.getAppCallGraph(), packages);
+		finder.setClassHierarchy(builder.getClassHierarchy());
+		finder.setUIAccessDecider(GUI.SWT);
+		Collection<IMethod> unsafe = finder.finalAllUnsafeUIAccessMethods();
+		
+		System.out.println("No of unsafe: " + unsafe.size());
+		Utils.dumpCollection(unsafe, "./logs/celerftpnaive.txt");
+	}
+	
+	public void testFileBunker() throws IOException {
+		String path = Utils.conToPath(Utils.getJars("C:\\Users\\szhang\\Downloads\\FileBunker-1.1.2-win32\\FileBunker-1.1.2-win32\\Resources\\lib"))
[…]

### 2012-01-26 trunk/GUIErrorDetector/paper/evaluation.tex
revise

@@
 in the above three source repositories, and then select subjects based on the following
-criterias. First, the subject must be a multithread GUI application, not
+criterias. First, the subject must be a multithreaded GUI application, not
 an open library. Second, the subject must undergone at least two years of active development,
@@
 \begin{itemize}
-\Item CelerFTP~\cite{celer} and FileBunker~\cite{filebunker} are two useful
+\Item VirgoFTP~\cite{virgo} and FileBunker~\cite{filebunker} are two useful
 SWT desktop applications.
-CelerFTP implements a simple FTP client based on Java and SWT UI library, and
+VirgoFTP implements a simple FTP client based on Java and SWT UI library, and
 FileBunker is a file backup application which uses one or more GMail accounts as its backup repository.
 
-\Item  AnyEdit~\cite{anyedit}, FileSync~\cite{filesync}, and
-EclipseRunner~\cite{eclipserunner} are three popular eclipse plugins.
-AnyEdit adds several new tools to  Eclipse editors, output consoles, and main menu. 
-FileSync is a file synchronisation tool to keep files outside of Eclipse projects in synchronized
-with Eclipse project files. EclipseRunner extends capability of running launch configurations in Eclipse IDE.
+\Item  HudsonEclipse~\cite{hudson}, and
+EclipseRunner~\cite{eclipserunner} are two popular eclipse plugins.
+HudsonEclipse adds several new tools to  monitor Hudson build status from Eclipse.
+EclipseRunner extends capability of running launch configurations in Eclipse IDE.
 
-\Item  S3dropbox~\cite{s3dropbox} and SudokuPuzzleSolver~\cite{sudokusolver}
+\Item  S3dropbox~\cite{s3dropbox} and SudokuSolver~\cite{sudokusolver}
 are two Swing desktop applications. S3dropbox implements a client that allows users
-to drag and drop files, which are then uploaded to their Amazon S3 accounts. SodokuPuzzleSolver
+to drag and drop files, which are then uploaded to their Amazon S3 accounts. SodokuSolver
 computes Sodoku solutions efficiently using mutlithreading execution.
@@
 \hspace*{-0.2cm}
+\setlength{\tabcolsep}{.75\tabcolsep}
 \begin{tabular}{|p{4.4cm}||c|c|c|c|}
@@
  \hline
- CelerFTP (3.0 alpha) &  2293 &  20 &  165  \\
+ VirgoFTP (1.3.5) &  2293 &  20 &  165  \\
  \hline
@@
  \hline
- FileSync (1.4.0)&  7374 &  36 &  510 \\
- \hline
- AnyEdit (2.4.0)&  11077 &  74 &  649 \\
+ HudsonEclipse(1.0.9)&  11077 &  74 &  649 \\
  \hline
@@
  \hline
- Sudoku Solver (1.06)&  3555 &  10 &  62 \\
+ SudokuSolver (1.06)&  3555 &  10 &  62 \\
  \hline
@@
 \hline \hline
- SWT (3.6.2)&  xxxxx &  xxx &  xxxx  \\
+ SWT (3.6)&  129942 &  999 &  9643 \\
 \hline
- Eclipse plugin development (3.6.2)&  xxxxx &  xxx &  xxxx  \\
+ Eclipse plugin development (3.6.2)&  460830 &  6630 &  37183 \\
 \hline
-Swing (1.6)&  xxxxx &  xxx &  xxxx  \\
+Swing (1.6)&  167961 &  878 &  13159 \\
 \hline
- Android (3.6)&  xxxxx &  xxx &  xxxx  \\
+ Android (3.2)&  683289 &  5085 &  10584 \\
 \hline
@@
 \Caption{{\label{table:subjects} Open source programs
-used in our evaluation. Column ``LOC'' is the number of lines
+used in our evaluation. Column ``LOC'' is the number of non-blank, non-comment lines
 of code, as counted by LOCC~\cite{locc}.  Each program is analyzed
@@
 use two configurations: with and without the reflection-aware transformation
-(Section~\ref{sec:cg}).  We did not use more expensive algorithms like $k$-CFA ($k >$ 1),
+(Section~\ref{sec:cg}).  We did not use other more expensive algorithms like $k$-CFA ($k >$ 1),
 because they can not scale to large programs.
@@
 that they are safe to be invoked from any thread. In this experiment, none of the paper
-authors was faimilar with the subjects; but we found it is quite easy
+authors was familar with the subjects; but we found it is quite easy
 to add extra those annotations and heuristic filters and finished these
@@
 \hspace*{-0.2cm}
-\setlength{\tabcolsep}{.65\tabcolsep}
+\setlength{\tabcolsep}{.45\tabcolsep}
 \begin{tabular}{|l||c|c|c||c|c|c||c|c|c||c|c|}
@@
  \hline
- xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx& xx & xx \\
+ VirgoFTP&  12401 &  2 &  2 & 10858 & 2 & 2 & 43598 & 2 & 2& 149 & 2 \\
  \hline
- xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx& xx & xx \\
- \hline
- xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx& xx & xx \\
+ FileBunker &  18951 &  1 &  0 & 15743 & 0 & 0 & 76088 & 2 & 1& 693 & 1 \\
  \hline
@@
  \hline
- xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx& xx & xx \\
+ EclipseRunner&  11248&  6 &  1 & 7201 & 6 & 1 & 26911 & 6 & 1& 202 & 1 \\
+ %\hline
+ %FileSync&  12132 &  xx &  xxx &8235 & xx & xx& 32565 & 1 & 1 & 331 & 1 \\
  \hline
- xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx& xx & xx \\
- \hline
- xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx& xx & xx \\
+ HudsonEclipse& 18473 &  2 &  1 & 15814 & 2 & 1& 56645 & 3 & 1 & 182 & 1 \\
  \hline
@@
  \hline
- S3dropbox &  xxxx &  xx &  xxx & xx & xx & xx& xx & 1 & 1 & 210 & xx \\
+ S3dropbox & 37751 &  0 &  0 & 30609 & 0 & 0 & 115324 & 1 & 1 & 210 & 1 \\
  \hline
-  Sudoku Solver&  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx& 356 & xx \\
+  SudokuSolver&  27730&  3 &  2 & 20907 & 3 & 2 & 39299 & 2 & 2 & 356 & 2 \\
  \hline
@@
  \hline
- xxx &  xxxx / xxxx &  xx / xxxx &  xxx / xxxx & xx /xxx & xx / xxxx  & xx / xxxx& xx / xxx & xxxx / xxx  & xxxx / xxx& xx & xx \\
+ SGTPuzzler & 13631 / 13865&  12 / 16 &  0 / 0 & 9546 / 9682& 4 / 4& 1 / 1 & 35198 / 35756 & 1 / 1  & 1 / 1& 104 & 1 \\
  \hline
- xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx& xx & xx \\
+ Fennec & 14058 / 14387 &  55 / 54 &  0 / 0 & 8263 / 8898 & 0 / 0 & 0 / 0& 29125/ 31759 & xx / xxx & 0 / xxx& 433 & 1 \\
  \hline
- xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx& xx & xx \\
+ MyTracks & 24036 / 24036 &  161 / 220 & 0 / 0 & 10803 / 13645 & 119 / 119 & 0 / 0 & 39235 / 110977 & 61 / xxx & 0 / xxx& 1192 & 1 \\
 \hline
@@
 are FP and redundant warnings?)
+
+why finds a bug in SGTPuzzle, because the \CodeIn{SmallKeyBoard} has been
+explicitly created in this main class \CodeIn{SGTPuzzles} \CodeIn{setKeyboardVisibility},
+thus, even without reflection-aware
+
+Why RTA, 0-CFA finds few, because they do not distinguish different
+calling context.
 
@@
  \fontsize{9pt}{\baselineskip}\selectfont
-\setlength{\tabcolsep}{.30\tabcolsep}
+\setlength{\tabcolsep}{.01\tabcolsep}
 \hspace*{-0.2cm}
@@
  \hline
- xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
+ VirgoFTP &  21 &  21 &  3 & 3 &  2 & 2\\
  \hline
- xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
- \hline
- xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
+ FileBunker &  4494 &  3210 &  3210 &  642 &  2 & 2\\
  \hline
@@
 \multicolumn{7}{|l|}{Eclipse plugins}   \\
+ %\hline
+ %EclipseRunner &  xxxx &  xx &  xxx & xx &  xxx & xx\\
  \hline
- xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
+ EclipseRunner&  1621 &  1487 &  1487 & 1487 &  5 & 1\\
  \hline
- xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
- \hline
- xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
+ HundsonEclipse&  3192 &  2417 &  1696 & 9 &  3 & 3\\
  \hline
@@
  \hline
- xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
+ S3dropbox&  45528 &  31978 &  30975 & 9 &  1 & 1\\
  \hline
- xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
- \hline
- xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
+ SudokuSolver &  58 &  58 &  58 & 2 &  2 & 2\\
  \hline
@@
  \hline
- xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
+ SGTPuzzler&  2 &  1 &  1 & 1 &  1 & 1\\
  \hline
- xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
+ Fennec &  xxxx &  xx &  xxx & xx &  xxx & xx\\
  \hline
- xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
+ MyTracks &  xxxx &  xx &  xxx & xx &  xxx & xx\\
 \hline
@@
 \Caption{{\label{table:filters}Number of warnings after applying a set of
-heuristic filters (Section~\ref{sec:heuristic}). Column ``\#Warning $F_i$''
-represents the number of remaining warnings after applying
-filters 1 -- $i$, and the number of last column is taken
-from Table~\ref{table:results} (Subcolumn ``\#Warning'' under column ``1-CFA / with taming reflection'').} }
+heuristic filters (Section~\ref{sec:heuristic}). Column ``Before Filtering''
+shows the output warning number using the reflection-aware 1-CFA algorithm.
+Column ``\#Warning $F_i$'' represents the number of remaining warnings after applying
+filters 1 -- $i$, and the number in last column is taken
+from Table~\ref{table:results}.
+Results of using other algorithms show similar patterns, which are omitted for brevity.} }
 \end{table}
@@
 GUI accessing code isolatedly, our technique produces significantly
-less warniings. The reflection-aware call graph construction algorithm
+less warnings. The reflection-aware call graph construction algorithm
 is critical in detecting errors for Android programs, and our
@@
 
-% Reporting on violations is fine but what is more important are the pracitces and patterns that need to be adopted to make it easier to avoid the issue in the first place.
+% Reporting on violations is fine but what is more important are the practices and patterns that need to be adopted to make it easier to avoid the issue in the first place.
 That is why there is a Worker interface in this project

### 2012-01-26 trunk/GUIErrorDetector/paper/introduction.tex
revise implementation and evaluation sections
revise

@@
 \section{Introduction}
+\label{sec:introduction}
 
@@
 
-Many popular GUI frameworks such as Swing\footnote{\url{http://docs.oracle.com/javase/6/swing/}},
-SWT\footnote{\url{http://eclipse.org/swt/}}, Android\footnote{\url{http://www.android.com/}},
-Qt\footnote{\url{http://qt.nokia.com/products/}}, MacOS Cocoa\footnote{\url{http://developer.apple.com/cocoa.html}},
-and X Windows\footnote{\url{http://www.x.org/}}
+Many popular GUI frameworks such as Swing~\cite{swing},
+SWT~\cite{swt}, Android~\cite{android},
+Qt~\cite{qt}, MacOS Cocoa~\cite{macos},
+and X Windows~\cite{xwindow}
 adapt the \textit{single-thread rule}:
@@
 The invalid thread access error is one of the top 3 bugs in developing a SWT application, and is
-the source of many relevant concurrency bugs~\footnote{\url{http://www.slideshare.net/lakshmip/top-3-swt-exceptions-3951224}}.
+the source of many relevant concurrency bugs~\cite{top3bugs}.
 A Google search for ``SWTException:Invalid thread access''  returns over 11,800 entries,
@@
 \subsection{Finding Invalid Thread Access Errors}
+\label{sec:finding}
 
@@
 %is also inadequate to eliminate this error.
+
+%One way to find such invalid thread access error is to check every GUI object
+%accessing code to see whether
+
 A standard way to fix an
 invalid thread access error is to replace direct GUI object accessing code 
-with asynchronized message passing, to ensure a GUI object are accessed in
+with asynchronized message passing, to ensure a GUI object is accessed in
 the UI thread. For example, to fix the bug in Figure~\ref{fig:androiderror},
@@
 
-One may wonder that a straightforward program transformation to wrap
-every possible UI-accessing operation with asynchronized message passing
-may avoid the invalid thread error. However, such an approach is problematic,
-because using asynchronized message passing has no timing
+One may wonder that a simple analysis to check whether every GUI object
+accessing code has been wrapped by (a)synchronized message passing may
+be capable to find invalid thread errors. However, such an approach is problematic,
+because not every GUI object access needs to be wrapped by a message passing
+method, e.g., methods that are only called from UI-thread can safely
+access any GUI object. On the other hand, using asynchronized message passing has no timing
 guarantee. It is entirely possible that, in some cases, a GUI object has already been
-disposed before the message sent to arrives, causing other bugs. Thus, programmers can not use
-it everywhere; instead, they must choose carefully to put it in appropriate places
-with extreme caution. This makes invalid thread errors even harder to avoid,
-and demands a proactive technique to detect them.
+disposed before the message sent to arrives, causing other bugs. 
+Thus, programmers can not use it everywhere to wrap all GUI object accessing code.
+In our evaluation on real world programs, we found this simple analysis 
+can not be used in practice: it issued
+an unacceptable number of false positives and redundant warnings.
+
+%program transformation to wrap
+%every possible UI-accessing operation with asynchronized message passing
+%may avoid the invalid thread error. However, such an approach is problematic,
+%because using asynchronized message passing has no timing
+%guarantee. It is entirely possible that, in some cases, a GUI object has already been
+%disposed before the message sent to arrives, causing other bugs. Thus, programmers can not use
+%it everywhere; instead, they must choose carefully to put it in appropriate places
+%with extreme caution. This makes invalid thread errors even harder to avoid,
+%and demands a proactive technique to detect them.
 
@@
 is non-trivial.
-Existing call graph construction algorithms such as RTA~\cite{} and k-CFA~\cite{}
-either suffer from either imprecision or incompleteness .
-To alleviate this problem,
-we present a combined RTA and k-CFA call graph construction algorithm, and
-also compare its usefulness with other algorithms in  our experiments. We
-also note that static analysis may report false positives due to its
+Existing call graph construction algorithms such as RTA~\cite{rta}
+and k-CFA~\cite{kcfa}
+fails to build a sufficiently complete call graph, due to their limitations
+to reason about reflections.  To alleviate this problem,
+we present a method to build reflection-aware call graph, and
+also compare its usefulness with existing call graph construction algorithms in
+our experiments. We also note that static analysis may report false positives due to its
 conservative nature, or multiple warnings that actually correspond
@@
 
-We instantiated our technique for popular four GUI frameworks namely SWT,
+We instantiated our technique for four popular GUI frameworks namely SWT,
 eclipse plugin environment, Java Swing, and Android. 
@@
 two dominating GUI frameworks in developing desktop Java applications.
-Eclipse with its plugin development envrionment is the de-facto standard
+Eclipse and its plugin development environment is the de-facto standard
 IDE for Java. Android is the No. 1 platform for
@@
 push-button manner, and scales to realistic programs.
-We evaluate our implementation on XXX subjects from four different
-frameworks over XXX LOC. The experiment results demonstrate
-that: our technique is effective (it found XXX real-world errors
-on all supported frameworks); our combined RTA and k-CFA call
-graph construction algorithm is useful (XXX it improves both completeness
-and precision over the existing algorithms), and our proposed
-heuristics are useful (it signficantly reduces the number of
+We evaluate our implementation on 10 subjects from four different
+frameworks over 75000 LOC. The experiment results demonstrate
+that: our technique is effective (it found 12 real-world errors
+on all supported frameworks, and produced significantly less
+false positives and redundant warnings than the simple analysis);
+our reflection-aware call graph construction algorithm is
+critical in finding errors in Android applications,
+and our proposed
+heuristics are useful (it significantly reduces the number of
 false positives and redundant warnings).
@@
 
-\item \textbf{Evaluation.} We performed an experiment on XXX subjects
-from 4 different platforms over XXX LOC to show the usefulness
-of the proposed techinque (Section~\ref{sec:evaluation}).
+\item \textbf{Evaluation.} We performed an experiment on 10 subjects
+from 4 different platforms over 75000 LOC to show the usefulness
+of the proposed technique (Section~\ref{sec:evaluation}).
 

### 2012-01-26 trunk/GUIErrorDetector/paper/technique.tex
revise

@@
 indicates that a new, non-UI thread is spawned.  After that, 
-the algorithm uses a BFS to find reachable UI accessing methods (lines 9 -- 23)
+the algorithm uses a BFS to find reachable UI-accessing methods (lines 9 -- 23)
 from each \CodeIn{Thread.start()} node.
-Specifially, it uses a queue to keep track of all visited nodes, and
+Specifically, it uses a queue to keep track of all visited nodes, and
 then checks every successive node to be visited (line 12);
 it reports an error if that node
-is a UI accessing method (line 15), or skips it if it is
+is a UI-accessing method (line 15), or skips it if it is
 a safe method (line 17), or simply keeps traversing otherwise (line 19).
 
-If the algorithm determines that a UI accessing method may be invoked
+If the algorithm determines that a UI-accessing method may be invoked
 by a non-UI thread, it creates an error report containing the full
@@
 \begin{figure}[t]
+\textbf{\underline{TODO: reformat it using mathit}}\\
 \textbf{Input}: a Java program $P$\\
@@
 
-\subsubsection{Call Graph Construction}
+\subsubsection{Reflection-aware Call Graph Construction}
 \label{sec:cg}
@@
 program scale well but achieves relatively lower precision.  The
-k-CFA algorithms maintains one set per expression achieves better
-precision than RTA (\textit{k} is the context length, which is
-orthogonal to the number of maintained sets).
+k-CFA algorithms maintains one or several sets per expression achieves better
+precision than RTA (\textit{k} is length of calling context).
 
@@
 
-\textbf{need to describe why need to traverse from the UI entry, not just from the thread entry}
+%\textbf{need to describe why need to traverse from the UI entry, not just from the thread entry}
 
 \begin{figure}[t]
-\textbf{Input}: a Java program $P$, a list of classes $cls$\\
+\textbf{\underline{TODO: reformat it using mathit}}\\
+\textbf{Input}: a Java program $P$\\
 \textbf{Output}: a call graph $cg$\\
@@
 
-Unfortunately, GUI applications often use reflection, which makes either
-RTA or k-CFA insufficient to build a satisfactory call graph. 
-The example code in Figure~\ref{fig:sampleandroid}  illustrates their limitations.
-In Figure~\ref{fig:sampleandroid}, line 7 uses reflection to create a \CodeIn{Button}
+Unfortunately, GUI applications often use reflection extensively and make
+existing call graph construction algorithms fail to build a sufficiently complete
+call graph. The example code in Figure~\ref{fig:sampleandroid} from an Android application
+ illustrates the limitations.
+In Figure~\ref{fig:sampleandroid}, line 6 uses reflection to create a \CodeIn{Button}
 object by looking up its id declared in the XML file. When this button
-is clicked, its event handling code (line 10 -- 13) updates the text and caches
-the current view to a list declared at line 2.
+is clicked, its event handling code (line 9 -- 11) updates the text.
+%d caches
+%the current view to a list declared at line 2.
 
-Existing call graph algorithms either suffer from the problem of incompleteness
-or imprecision. The k-CFA algorithm performs points-to analysis with call
-graph construction interleavingly, and maintains a value set for every expression.
-For example, it concludes that variable \CodeIn{cachedViews} can only point
-to a \CodeIn{LinkedList} object and the method call \CodeIn{add} at line 12
-can only correspond to \CodeIn{LinkedList.add}. However, k-CFA fails to
-conclude that variable \CodeIn{button} declared at line 7 points to
-a \CodeIn{Button} object due to its limitation in dealing with reflection. Thus, k-CFA
-may miss the call graph edge corresponding to the method call \CodeIn{setText} at line 11. 
-On the other hand, using a coarse-grained algorithm like RTA~\cite{} can not still
-fully solve this problem. RTA adds an edge for a method invocation 
-to the call graph if an object of the receiver's type (or subtype)
-has been created.  By explicitly specifying that all GUI classes declared in the XML file will be created,
-RTA maintains a global value set for those GUI object type, and  adds a
-call edge \CodeIn{setText} to the call graph. However, RTA introduces 
-unnecessary precision loss: it may
-may conclude that the \CodeIn{cachedViews} variable at line 2
-point to any created \CodeIn{List} objects created somewhere else in the program, despite the
-fact that \CodeIn{cachedViews} can only be a \CodeIn{LinkedList} object.
+When using existing call graph algorithms to analyze the code in Figure~\ref{fig:sampleandroid},
+they fail to conclude that variable \CodeIn{button} declared at line 7
+point to a \CodeIn{Button} object due to its limitation in deal with the
+reflection call \CodeIn{findViewById}. Thus, the resulting
+call graph will miss the calling edge corresponding to the method
+call \CodeIn{setText} at line 10.
 
-To alleviate the above problems, we present a combined RTA and k-CFA
-call graph construction algorithm as shown in Figure~\ref{fig:cgalgorithm}.
-The algorithm shares the same spirit as k-CFA to maintain a value set
-for each expression. However, the only difference is that our
-algorithm uses a RTA-style treatment for constructing the value set for
-GUI classes: it parses the XML configuration file and explicitly
-adds a raw object to each declared GUI variable's value set. Thus,
-For the example in Figure~\ref{fig:sampleandroid}, this
-combined algorithm concludes that a \CodeIn{Button} object has been
-created at line 7 and then adds the call edge \CodeIn{setText} to the
-graph. It also concludes that the \CodeIn{cachedViews} variable can only
-point to a \CodeIn{LinkedList} object, avoiding unnecessary precision loss.
-%For desktop applications which have main method, it is straigtforward to apply
-%the above algorithm. However, for applications on platforms like eclipse plugin
-%and Android. presents new challenges. Two technical challenges must be solve.
-%First, use reflection extensively, Second, it is possible to interact with
-%native code.
+%Existing call graph algorithms failed either suffer from the problem of incompleteness
+%or imprecision. The k-CFA algorithm performs points-to analysis with call
+%graph construction interleavingly, and maintains a value set for every expression.
+%For example, it concludes that variable \CodeIn{cachedViews} can only point
+%to a \CodeIn{LinkedList} object and the method call \CodeIn{add} at line 12
+%can only correspond to \CodeIn{LinkedList.add}. However, k-CFA fails to
+%conclude that variable \CodeIn{button} declared at line 7 points to
+%a \CodeIn{Button} object due to its limitation in dealing with reflection. Thus, k-CFA
+%may miss the call graph edge corresponding to the method call \CodeIn{setText} at line 11. 
+%On the other hand, using a coarse-grained algorithm like RTA~\cite{} can not still
+%fully solve this problem. RTA adds an edge for a method invocation 
+%to the call graph if an object of the receiver's type (or subtype)
+%has been created.  By explicitly specifying that all GUI classes declared in the XML file will be created,
+%RTA maintains a global value set for those GUI object type, and  adds a
+%call edge \CodeIn{setText} to the call graph. However, RTA introduces 
+%unnecessary precision loss: it may
+%may conclude that the \CodeIn{cachedViews} variable at line 2
+%point to any created \CodeIn{List} objects created somewhere else in the program, despite the
+%fact that \CodeIn{cachedViews} can only be a \CodeIn{LinkedList} object.
 
-%Android features an extended event-based library and dynamic inflation of
-%graphical views from declarative XML layout files.
-%A static analyzer for Android programs must consider such features, for
-%correctness and precision.
+To alleviate this limitation, we present an algorithm to construct
+a reflection-aware call graph based on simple program transformation.
+The basic idea to replace reflection calls with explicit object
+creation instructions, pretending the corresponding concrete object
+has been created.  The algorithm is shown in Figure~\ref{fig:cgalgorithm}.
+It consists of two steps. The first step is a simple program
+transformation to replace reflection calls with object creations, and
+the second step is to use standard call graph construction algorithms
+to construct the graph on the transformed program. Lines 1 - 7 show
+the transformation step. The algorithm iterates through every statement
+in an analyzed program. When it sees a reflection call statement (e.g.,
+the \CodeIn{findViewById} method), the algorithm analyzes the
+program to determine a set of possible classes that may be created.
+After that, the algorithm creates a new instruction which non-deterministically
+returns a new object of the class set. The reflection-aware call graph
+construction algorithm is independent of the underlying call graph algorithm;
+any existing algorithm can be used to construct the resulting graph at line 8.
 
-%Give an example of how reflection affect call graph precision.
+For the example in Figure~\ref{fig:sampleandroid}, the algorithm
+first parses the XML configuration file to determine that the \CodeIn{button\_id}
+value is mapped to a \CodeIn{Button} instance declaration. Then it
+replaces the \CodeIn{findViewById(R.id.button\_id)} method call 
+with an explicit object creation instruction \CodeIn{new Button}.
+After that, the algorithm employs existing call graph construction
+algorithms to analyze the transformed program, and permits them
+to add the call edge \CodeIn{setText} to the resulting graph.
 
-%So, we present a new call graph construction algorithm
+Using this reflection-aware call graph construction algorithm is
+critical to detect bugs on realistic GUI applications.
+As demonstrated in our experiments, errors in all Android applications
+can only be detected using this algorithm.
 
-%reflected classes are known, use RTA.
+% combined RTA and k-CFA
+%call graph construction algorithm as shown in Figure~\ref{fig:cgalgorithm}.
+%The algorithm shares the same spirit as k-CFA to maintain a value set
+%for each expression. However, the only difference is that our
+%algorithm uses a RTA-style treatment for constructing the value set for
+%GUI classes: it parses the XML configuration file and explicitly
+%adds a raw object to each declared GUI variable's value set. Thus,
+%For the example in Figure~\ref{fig:sampleandroid}, this
+%combined algorithm concludes that a \CodeIn{Button} object has been
+%created at line 7 and then adds the call edge \CodeIn{setText} to the
+%graph. It also concludes that the \CodeIn{cachedViews} variable can only
+%point to a \CodeIn{LinkedList} object, avoiding unnecessary precision loss.
 
-%reflection code
-
-%native code
-
-\subsubsection{Heuristic Filtering and Annotation}
-\label{sec:heuristic}
-
-A static analysis can exhaustively check possible error path; but may report
-paths that do not actually exist (i.e., false positives) or different paths
- that correspond to the same error (i.e., redundant warnings). We devise
-a set of heuristics below to filter out likely false positives and redundant warnings.
-The first two heuristics are for reducing false positives, while the
-remaining ones are for removing redundant warnings.
-
-%To remove those 
-%The potentially huge volume of
-%reported warnings impose great burden for programmers to check
-%its validity.
-
-\begin{enumerate}
-
-\item \textbf{Filter Reports Containing Library Calls}. A
-reported method call chain involving common Library calls
-like \CodeIn{Object.toString} or \CodeIn{Runtime.shutDown} are unlikely to
-be buggy, and should be filtered. In addition, a method call chain that \textit{only}
-consists of library calls after the entry method is also unlikely
-to reveal a valid bug, since it has no interaction with the UI. 
-We encode a list of common library calls, and remove
-a report if it contaiins one of them.
-%Method call chain involves typical
-%system methods like \CodeIn{toString} are unlikely to reveal a real bug.
-
-\item \textbf{Filter Reports With User-Annotated Methods}. Besides general
-library calls, users are also permitted
-to explicitly annotate methods that will never trigger an error.
-For example, the Android GUI framework provides a utility method 
-\CodeIn{runOnUIThread} to check whether the current thread is the UI thread
-before executing the code; if
-not, it executes the code on the UI thread using message passing.
-A reported call chain containing a annotated 
-can be safely removed.
-%method will never cause an
-%invalid thread error and should be removed.
-
-\item \textbf{Filter Lexically Redundant Reports}. One reported method call
-chain can lexically subsume another one. For example, suppose that a reported method
-call chain \CodeIn{a()} $\rightarrow$ \CodeIn{b()} $\rightarrow$ \CodeIn{c()}
-leads to a potential error, and another entry method \CodeIn{d()} calls \CodeIn{a()}.
-Therefore, a static analysis might also report another method call chain
-\CodeIn{d()} $\rightarrow$ \CodeIn{a()} $\rightarrow$ \CodeIn{b()} $\rightarrow$ \CodeIn{c()}
-that actually corresponds to the same error root as the previous one. In this case, 
- removing the second call chain would not reduce the error detection capability:
-the first call chain already reveals the same error and is shorter 
-for programmers to interpret.
-
-\item \textbf{Filter Report With the Same $k$ Head Methods}. A method can call
-multiple methods that access GUI objects, such as:
-\begin{CodeOut}
-\begin{alltt}
-     public void m() \{
-         accessUIObject1();
-         accessUIObject2();
-     \}
-\end{alltt}
-\end{CodeOut}
-If method \CodeIn{m()} is invoked by a non-UI thread, two method call chains
-only different at last few method nodes will be reported:
-
-\CodeIn{a()} $\rightarrow$ ...\CodeIn{Thread.start()} ... $\rightarrow$ \CodeIn{m()} $\rightarrow$ \CodeIn{accessUIObject1()} ...
-
-\CodeIn{a()} $\rightarrow$ ...\CodeIn{Thread.start()} ... $\rightarrow$ \CodeIn{m()} $\rightarrow$ \CodeIn{accessUIObject2()} ...
-
-In fact, these two call chains correspond to the same error root: knowning
-method \CodeIn{m()} is called by a non-UI thread is sufficient to understand and fix this error.
-This filter compares every two reported method call chains that share the same
-$k$ ($k$ is user-settable with a default value 5) head nodes, and removes the longer one.
-
-\item \textbf{Filter Report With the Same $k$ Tail Methods}. A method
-can have multiple callers, so that method call chains with the same tail are likely
-to represent different ways to trigger the same error. This filter compares every
-two reported method call chains that share the same 
-$k$ ($k$ is user-settable with a default value 5) tail nodes, and removes the longer one.
-
-\end{enumerate}
-
-All above filters are based on heuristics, and thus not sound in
-that it may filter real bugs. However, as we will show in
-the next experiment section, all these filters work well, and significantly
-reduces the number of false positives and redundant reports in practice.
+\subsubsection{Annotation for Native Methods}
 
@@
 
-An eclipse plugin is an open program. Unlike a SWT desktop application, it does not
-have a main method as a single program entry point. Instead, it extends certain
-extension points provided by the eclispe framework. As a plugin starts, the eclipse
-framework will calls back the overrided extension points and intializes the plugin code.
-We customize our technique for eclipse plugin as follows:
+%An eclipse plugin is an open program. 
+Unlike a SWT desktop application, an Eclipse plugin does not
+have a main method as a single program entry point. Instead, it extends
+extension points provided by the Eclispe framework to implement
+functionalities. When a plugin starts, Eclipse
+calls back the overridden extension points to handle the
+upcoming events. We customize our technique for Eclipse plugin as follows:
 
@@
 
-\item \textbf{Call graph entry nodes: } due to the complexity of the eclipse architecture,
-there is no rigorous way in eclipse to identify a UI thread. Here, we use a heuristic to determine call graph
-entry nodes from the UI thread. As a naming convention, source code in a plugin's \CodeIn{ui}
-package deals with the creation and maintainance of a plugin's GUI, and is thus
-invoked by the UI thread. We conservatively treat all public methods in the \CodeIn{ui}
-as call graph entry nodes.
+\item \textbf{Call graph entry nodes: } all overridden SWT
+GUI event handling methods\footnote{Eclipse plugin is built
+on top of the SWT framework} are called from the UI thread.
+We treat these callback methods as the entry nodes.
+
+%due to the complexity of the eclipse
+%architecture,
+%there is no rigorous way in eclipse to identify a UI thread. Here, we use a heuristic to determine call graph
+%entry nodes from the UI thread. As a naming convention, source code in a plugin's \CodeIn{ui}
+%package deals with the creation and maintainance of a plugin's GUI, and is thus
+%invoked by the UI thread. We conservatively treat all public methods in the \CodeIn{ui}
+%as call graph entry nodes.
 
@@
 % a plugin's \CodeIn{ui} package.  Such methods are normally called by the eclipse framework
-%by the UI thread. XXX This rule, though quite heuristical, works quite well in practice.
+%by the UI thread. XXX This rule, though quite , works quite well in practice.
 
-\item \textbf{UI accessing nodes} and \textbf{Safe methods} are the same as SWT.
+\item \textbf{UI-accessing nodes} and \textbf{Safe methods} are the same as SWT.
 
@@
 
-\item \textbf{Call graph entry nodes: } all overriden callback methods in the
-listerner classes are called from the UI thread. We treat those callback
+\item \textbf{Call graph entry nodes: } all overridden callback methods in 
+Swing's UI listener classes are called from the UI thread. We treat those callback
 methods as the entry nodes.
@@
 
-\item \textbf{UI accessing nodes:} as stated in Swing's documentation, methods
+\item \textbf{UI-accessing nodes:} as stated in Swing's documentation, methods
 in Swing GUI classes are not thread safe with three exceptions (\CodeIn{repaint()},
 \CodeIn{revalidate()}, and \CodeIn{invalidate()}). Thus, we
-treat all methods as defined in each GUI class as UI accessing nodes.
+treat all methods defined in each GUI class as UI-accessing nodes.
 
@@
 all public methods from an \CodeIn{Activity} class as call graph entry nodes. Additionally,
-we also add all overriden callback methods in event listener classes as entry nodes.
+we also add all overridden callback methods in event listener classes as entry nodes.
 
-\item \textbf{UI accessing nodes: } like SWT, Android explicitly checks the current
-thread validity before accessing a GUI object using the \CodeIn{ViewRoot.checkThread} method.
-Thus, we treat every methods that calls \CodeIn{ViewRoot.checkThread} as a UI accessing node
+\item \textbf{UI-accessing nodes: } like SWT, Android explicitly checks whether
+the current thread is a UI thread or not before accessing a GUI object via
+the \CodeIn{ViewRoot.checkThread} method.
+Thus, we treat every methods calling \CodeIn{ViewRoot.checkThread} as a UI-accessing node
 in the call graph.

### 2012-01-26 GUIErrorDetector/paper/abstract.tex
revise

@@
 Heavy use of reflection in modern GUI applications makes existing
-call graph construction algorithms fail to build a sufficiently complete
-and precise call graph. Thus, we present a combined RTA and k-CFA
-call graph construction algorithm to overcome the limitations.% of analyzing GUI applications.
+call graph construction algorithms fail to build a good
+call graph. Thus, we present a method to overcome the limitations, and
+build reflection-aware call graphs.
+
+%call graph construction algorithm to overcome the limitations.% of analyzing GUI applications.
 
@@
 platforms: SWT, Eclipse plugin development framework, Java Swing, and
-Android. In an evaluation on XX subjects over XXX LOC, our technique
+Android. In an evaluation on 9 subjects over 75000 LOC, our technique
 found a number of real-world errors, suggesting its effectiveness

### 2012-01-26 GUIErrorDetector/paper/conclusion.tex
revise

--- 2011-12-25 trunk/GUIErrorDetector/paper/conclusion.tex
@@
 We have demonstrated that our technique can be both practical and useful
-by an evaluation on XXX subjects acrosss 4 popular GUI
+by an evaluation on 10 subjects acrosss 4 popular GUI
 frameworks. Our experiments have shown that we can find bugs
@@
 
-\begin{itemize}
-
-\item \textbf{Integration with dynamic and symbolic analyses.} The technique 
+%\begin{itemize}
+%\item
+\textbf{Integration with dynamic and symbolic analyses.} The technique 
 presented in this paper is a pure static analysis. It
@@
 
-\item \textbf{Unit testing multithreaded GUI programs.} Besides
+%\item
+\textbf{Unit testing multithreaded GUI programs.} Besides
 a static analysis,  software testing is another
@@
 
-\item \textbf{Fixing potential GUI errors.} After a potential error is revealed, fixing
+%\item
+\textbf{Fixing potential GUI errors.} After a potential error is revealed, fixing
 it and verifing the patch has often been another important and time-consuming process. Fixing concurrency
@@
 
-\end{itemize}
+%\end{itemize}

### 2012-01-26 GUIErrorDetector/paper/related.tex
revise

--- 2011-12-25 trunk/GUIErrorDetector/paper/related.tex
@@
 generation graph. 
-%Their approach targets Java desktop applications, which
-%are quite different from the Android mobile environment (XXXX).
 However, testing is often insufficient to ensure the correctness of a GUI program
@@
 each piece of code is tested. This makes it hard to determine
-the completeness of a test suite. %All of the (XXXXX, so that GUI is often not well tested)
+the completeness of a test suite. 
 In contrast, as advocated in this paper, the primary advantage of
 using a static analysis is that it can potentially explore
-all paths to find possible bugs without actually executing the tested code. % (XXX use heuristic filtering)
+all paths to find possible bugs without actually executing the tested code. 
 Compared with software testing, a static analysis tool may
@@
 a model checker to construct the witness for data races reported by the lockset algorithm.
-%(XXXX problem for applying to GUI).
 Unfortunately, due to the exponential size of the search space,

### 2012-01-28 trunk/GUIErrorDetector/tests/edu/washington/cs/detector/experiments/android/TestSGTPuzzle.java
test drivers for android programs

@@ -1,12 +1,20 @@
 package edu.washington.cs.detector.experiments.android;
 
 import java.io.IOException;
+import java.util.Collection;
+import java.util.Collections;
+import java.util.HashSet;
+import java.util.LinkedList;
 import java.util.List;
 import java.util.Set;
 
+import com.ibm.wala.ipa.callgraph.Entrypoint;
+import com.ibm.wala.ipa.cha.ClassHierarchy;
 import com.ibm.wala.ipa.cha.ClassHierarchyException;
 
 import edu.washington.cs.detector.AnomalyCallChain;
+import edu.washington.cs.detector.CGBuilder;
+import edu.washington.cs.detector.CGEntryManager;
 import edu.washington.cs.detector.CallChainFilter;
 import edu.washington.cs.detector.CGBuilder.CG;
 import edu.washington.cs.detector.NativeMethodConnector;
@@ -56,10 +64,28 @@ public class TestSGTPuzzle extends AbstractAndroidTest {
 		return "D:\\research\\guierror\\subjects\\android-programs\\extracted\\SGTPuzzles-9306-7.apk";
 	}
 	
+	@Override
+	protected Collection<Entrypoint> getExtraEntrypoints(CGBuilder builder) {
+		if(builder.getClassHierarchy() == null) {
+			throw new RuntimeException("Should can makeClassHiearchyAndScope first!");
+		}
+		ClassHierarchy cha = builder.getClassHierarchy();
+		List<String> otherClasses = new LinkedList<String>();
+	    otherClasses.add("android.view.ViewRoot");
+	    Iterable<Entrypoint> otherClassMethods = CGEntryManager.getAllPublicMethods(builder, otherClasses, false);
+	    //the extra entrypoint collection
+	    Collection<Entrypoint> extraEntrypoints = new HashSet<Entrypoint>();
+	    for(Entrypoint ep : otherClassMethods) {
+	    	extraEntrypoints.add(ep);
+	    }
+	    return extraEntrypoints;
+	}
+	
 	public void testFindErrors() throws ClassHierarchyException, IOException {
 		CGTraverseGuider ui2startGuider = new CGTraverseAndroidGuider();
 		CGTraverseExploreClientRunnableStrategy start2checkGuider = new  CGTraverseExploreClientRunnableStrategy(new String[]{"name.boyle.chris.sgtpuzzles"});
[…]

### 2012-01-28 GUIErrorDetector/tests/edu/washington/cs/detector/experiments/android/AbstractAndroidTest.java
test drivers for android programs

@@ -5,9 +5,12 @@ import java.io.FileNotFoundException;
 import java.io.IOException;
 import java.io.Reader;
 import java.util.Collection;
+import java.util.Collections;
+import java.util.HashSet;
 import java.util.LinkedHashSet;
 import java.util.LinkedList;
 import java.util.List;
+import java.util.Set;
 
 import com.ibm.wala.classLoader.IClass;
 import com.ibm.wala.classLoader.IMethod;
@@ -28,10 +31,16 @@ import edu.washington.cs.detector.NativeMethodConnector;
 import edu.washington.cs.detector.UIAnomalyDetector;
 import edu.washington.cs.detector.UIAnomalyMethodFinder;
 import edu.washington.cs.detector.CGBuilder.CG;
+import edu.washington.cs.detector.experiments.filters.MergeSameEntryToStartPathStrategy;
+import edu.washington.cs.detector.experiments.filters.MergeSamePrefixToLibCallStrategy;
+import edu.washington.cs.detector.experiments.filters.MergeSameTailStrategy;
 import edu.washington.cs.detector.experiments.filters.RemoveSubsumedChainStrategy;
+import edu.washington.cs.detector.experiments.filters.RemoveSystemCallStrategy;
+import edu.washington.cs.detector.experiments.straightforward.TestAndroids;
 import edu.washington.cs.detector.guider.CGTraverseGuider;
 import edu.washington.cs.detector.guider.CGTraverseNoSystemCalls;
 import edu.washington.cs.detector.guider.CGTraverseOnlyClientRunnableStrategy;
+import edu.washington.cs.detector.util.AndroidLogicByPassFileCreator;
 import edu.washington.cs.detector.util.AndroidUtils;
 import edu.washington.cs.detector.util.ApkUtils;
 import edu.washington.cs.detector.util.Files;
@@ -42,13 +51,53 @@ import junit.framework.TestCase;
 
 public abstract class AbstractAndroidTest extends TestCase {
 	
-	abstract protected String getAppPath();
+	public static String bypassfiledir = "dat";
 	
+	private boolean runnaiveapproach = false;
+	private String[] packageNames = null;
+	private String bypassFileName = null;
+	private String androidcheckingfile = null;
+	
+	public void setRunnaiveApproach(boolean app) {
+		this.runnaiveapproach = app;
+	}
+	public void setPackageNames(String[] packages) {
+		this.packageNames = packages;
[…]

### 2012-01-28 GUIErrorDetector/tests/edu/washington/cs/detector/experiments/android/TestMozillaFirefox.java

@@ -1,11 +1,19 @@
 package edu.washington.cs.detector.experiments.android;
 
+import java.util.Collection;
+import java.util.HashSet;
+import java.util.LinkedList;
 import java.util.List;
+import java.util.Set;
 
 import com.ibm.wala.ipa.callgraph.CGNode;
+import com.ibm.wala.ipa.callgraph.Entrypoint;
+import com.ibm.wala.ipa.cha.ClassHierarchy;
 import com.ibm.wala.util.graph.Graph;
 
 import edu.washington.cs.detector.AnomalyCallChain;
+import edu.washington.cs.detector.CGBuilder;
+import edu.washington.cs.detector.CGEntryManager;
 import edu.washington.cs.detector.CGBuilder.CG;
 import edu.washington.cs.detector.guider.CGTraverseAndroidGuider;
 import edu.washington.cs.detector.guider.CGTraverseExploreClientRunnableStrategy;
@@ -18,7 +26,9 @@ public class TestMozillaFirefox extends AbstractAndroidTest {
 
 	@Override
 	protected String getAppPath() {
-		String appPath = "D:\\research\\guierror\\subjects\\android-programs\\extracted\\mozilla-android-base\\classes\\org\\mozilla"
+		String appPath = 
+			//"D:\\research\\guierror\\subjects\\android-programs\\extracted\\mozilla-android-base\\classes\\org\\mozilla"
+			"D:\\research\\guierror\\subjects\\android-programs\\extracted\\mozilla-android-abstract-removed\\classes\\org\\mozilla"
 			+ Globals.pathSep
 			+ "D:\\research\\guierror\\eclipsews\\GUIErrorDetector\\exp-subjects\\original-android.jar";
 //		    + "D:\\Java\\android-sdk-windows\\platforms\\android-14\\android.jar";
@@ -30,21 +40,114 @@ public class TestMozillaFirefox extends AbstractAndroidTest {
 	protected String getDirPath() {
 		return "D:\\research\\guierror\\subjects\\android-programs\\extracted\\mozilla-android-base";
 	}
+	
+	@Override
+	protected Collection<Entrypoint> getExtraEntrypoints(CGBuilder builder) {
+		if(builder.getClassHierarchy() == null) {
+			throw new RuntimeException("Should can makeClassHiearchyAndScope first!");
+		}
+		ClassHierarchy cha = builder.getClassHierarchy();
[…]

### 2012-01-28 GUIErrorDetector/tests/edu/washington/cs/detector/experiments/android/TestMytracksAndroid.java

@@ -1,10 +1,19 @@
 package edu.washington.cs.detector.experiments.android;
 
 import java.io.IOException;
+import java.util.Collection;
+import java.util.HashSet;
+import java.util.LinkedList;
 import java.util.List;
 
+import com.ibm.wala.ipa.callgraph.Entrypoint;
+import com.ibm.wala.ipa.cha.ClassHierarchy;
+
 import edu.washington.cs.detector.AnomalyCallChain;
+import edu.washington.cs.detector.CGBuilder;
+import edu.washington.cs.detector.CGEntryManager;
 import edu.washington.cs.detector.CallChainFilter;
+import edu.washington.cs.detector.UIAnomalyMethodFinder;
 import edu.washington.cs.detector.CGBuilder.CG;
 import edu.washington.cs.detector.experiments.filters.MergeSameEntryToStartPathStrategy;
 import edu.washington.cs.detector.guider.CGTraverseAndroidGuider;
@@ -14,6 +23,9 @@ import edu.washington.cs.detector.guider.CGTraverseOnlyClientRunnableStrategy;
 import edu.washington.cs.detector.util.Globals;
 import edu.washington.cs.detector.util.Utils;
 
+/**
+ * the bug: http://code.google.com/p/mytracks/issues/detail?id=424
+ * */
 public class TestMytracksAndroid extends AbstractAndroidTest {
 
 	@Override
@@ -43,18 +55,74 @@ public class TestMytracksAndroid extends AbstractAndroidTest {
 		return "D:\\research\\guierror\\subjects\\android-programs\\sourcecode\\mytracks-april-29\\MyTracks";
 	}
 	
+	@Override
+	protected Collection<Entrypoint> getExtraEntrypoints(CGBuilder builder) {
+		if(builder.getClassHierarchy() == null) {
+			throw new RuntimeException("Should can makeClassHiearchyAndScope first!");
+		}
+		ClassHierarchy cha = builder.getClassHierarchy();
+		List<String> otherClasses = new LinkedList<String>();
+	    otherClasses.add("android.view.ViewRoot");
+	    Iterable<Entrypoint> otherClassMethods = CGEntryManager.getAllPublicMethods(builder, otherClasses, false);
+	    //the extra entrypoint collection
+	    Collection<Entrypoint> extraEntrypoints = new HashSet<Entrypoint>();
+	    for(Entrypoint ep : otherClassMethods) {
+	    	extraEntrypoints.add(ep);
+	    }
[…]

### 2012-01-28 trunk/GUIErrorDetector/src/edu/washington/cs/detector/AnomalyCallChain.java
edit source for doing experiments

@@ -89,6 +89,16 @@ public class AnomalyCallChain {
 		return sb.toString();
 	}
 	
+	public static String flatCGNodeListWithoutContext(List<CGNode> nodeList) {
+		assert nodeList != null;
+		StringBuilder sb = new StringBuilder();
+		for(CGNode node : nodeList) {
+			sb.append(node.getMethod().getSignature());
+			sb.append(Globals.lineSep);
+		}
+		return sb.toString();
+	}
+	
 	/**
 	 * A utility method to check whether there is a valid call chain from the
 	 * startNode to the endNode. return the path, else return an empty list.

### 2012-01-28 trunk/GUIErrorDetector/src/edu/washington/cs/detector/guider/CGTraverseAndroidSafeMethodGuider.java

@@ -9,15 +9,39 @@ public class CGTraverseAndroidSafeMethodGuider implements CGTraverseGuider {
 	String[] safeMethods = new String[] {
 			"android.app.Activity.runOnUiThread(Ljava/lang/Runnable;)V",
 			"android.widget.ProgressBar.refreshProgress(IIZ)V",
+			"android.view.View.performClick()Z",
+			"com.google.android.apps.mytracks.ChartActivity$",
+			"com.google.android.apps.mytracks.MyMapsList$",
+			"com.google.android.apps.mytracks.MyTracks$",
+			"com.google.android.apps.mytracks.MapActivity$",
+			"com.google.android.apps.mytracks.NavControls$",
+			"com.google.android.apps.mytracks.MyMapsList$",
+			"com.google.android.apps.mytracks.SensorStateActivity$",
+			"com.google.android.apps.mytracks.DialogManager4",
+			"com.google.android.apps.mytracks.StatsActivity$",
+			"com.google.android.apps.mytracks.io.ModernAuthManager$",
+			"com.google.android.apps.mytracks.ChartActivity.clearTrackPoints()V"
 		};
 	
 	@Override
 	public boolean traverse(CGNode src, CGNode dest) {
 		String destSig = dest.getMethod().getSignature();
-		if(Utils.includedIn(destSig, safeMethods)) {
+//		if(Utils.includedIn(destSig, safeMethods)) {
+//			return false;
+//		}
+		if(this.contains(destSig, safeMethods)) {
 			return false;
 		}
 		return true;
+	}
+	
+	private boolean contains(String dest, String[] strs) {
+		for(String str : strs) {
+			if(dest.indexOf(str) != -1) {
+				return true;
+			}
+		}
+		return false;
 	}
 
 }

### 2012-01-28 GUIErrorDetector/src/edu/washington/cs/detector/CGBuilder.java
edit source for doing experiments

@@ -28,7 +28,7 @@ import edu.washington.cs.detector.util.WALAUtils;
 
 public class CGBuilder {
 	
-	public enum CG {RTA, ZeroCFA, ZeroContainerCFA, ZeroOneCFA, ZeroOneContainerCFA, OneCFA, TwoCFA, CFA}
+	public enum CG {RTA, ZeroCFA, ZeroContainerCFA, ZeroOneCFA, ZeroOneContainerCFA, OneCFA, TwoCFA, CFA, FakeZeroCFA}
 	
 	public final String appPath;
 	public final File exclusionFile;
@@ -156,7 +156,10 @@ public class CGBuilder {
 			}
 			System.out.println("Use CFA with precision: " + this.cfaprecision);
 			builder = WALAUtils.makeCFABuilder(this.cfaprecision, options,  cache, cha, scope);
-		} else {
+		} else if (this.type == CG.FakeZeroCFA) {
+			System.out.println("Use Fake-0-CFA with precision: " + this.cfaprecision);
+			builder = WALAUtils.makeCFABuilder(0, options, cache, cha, scope);
+		}else {
 			throw new RuntimeException("The CG type: " + type + " is unknonw");
 		}
 		assert builder != null;

### 2012-01-28 GUIErrorDetector/src/edu/washington/cs/detector/UIAnomalyMethodFinder.java

@@ -189,7 +189,7 @@ public class UIAnomalyMethodFinder extends AbstractMethodFinder {
 				CGNode succNode = succIt.next();
 				
 				if(!super.guider.traverse(node, succNode)) {
-					//Log.logln("  skip by guider: " + succNode, DEBUG);
+					Log.logln("  skip by guider: " + succNode, DEBUG);
 					continue;
 				}
 				

### 2012-01-28 GUIErrorDetector/src/edu/washington/cs/detector/guider/CGTraverseExploreClientRunnableStrategy.java

@@ -28,8 +28,24 @@ public class CGTraverseExploreClientRunnableStrategy implements CGTraverseGuider
 
 	@Override
 	public boolean traverse(CGNode src, CGNode dest) {
+//		if(src.toString().indexOf("dispatchMessage") != -1) {
+//		    System.out.println("Checking traverse: src: " + src
+//		    		+ "\n    dest: " + dest);
+//		    IMethod srcMethod = src.getMethod();
+//			IClass srcClass = srcMethod.getDeclaringClass();
+//			String classFullName = WALAUtils.getJavaFullClassName(srcClass);
+//			//System.err.println(classFullName);
+//			String methodName = srcMethod.getName().toString();
+//		    String srcmethod = classFullName + "." + methodName;
+//		    System.out.println("  src method: " + srcmethod);
+//		}
+		
 		if(!safeGuier.traverse(src, dest)) {
 			return false;
+		}
+		
+		if(this.clientRunnablePackage.length == 0 && methodCallMapping.isEmpty()) {
+			return true;
 		}
 		
 		IMethod srcMethod = src.getMethod();
@@ -37,12 +53,19 @@ public class CGTraverseExploreClientRunnableStrategy implements CGTraverseGuider
 		String classFullName = WALAUtils.getJavaFullClassName(srcClass);
 		//System.err.println(classFullName);
 		String methodName = srcMethod.getName().toString();
-		if(classFullName.equals("java.lang.Thread") && (methodName.equals("start") || methodName.equals("run"))) {
-			IClass destClass = dest.getMethod().getDeclaringClass();
-			String destCode = WALAUtils.getJavaFullClassName(destClass);
-			if(!this.isInClientPackage(destCode)) {
-				//System.err.println("thread start: " + dest);
-				return false;
+		if (this.clientRunnablePackage.length > 0) {
+			if (classFullName.equals("java.lang.Thread") && (methodName.equals("start") /*|| methodName.equals("run")*/)) {
+				IClass destClass = dest.getMethod().getDeclaringClass();
+				String destCode = WALAUtils.getJavaFullClassName(destClass) + "." + dest.getMethod().getName().toString() ;
+//				System.out.println("source node: " + src);
+//				System.out.println("dest node: " + dest);
+				if (this.isInClientPackage(destCode.trim())) {
+					// System.err.println("thread start: " + dest);
+//					System.out.println(" XX  starting traverse! " + src + "  --> " + dest);
+					return true;
+				} else {
[…]

### 2012-01-28 GUIErrorDetector/src/edu/washington/cs/detector/util/EclipsePluginUtils.java

@@ -214,6 +214,9 @@ public class EclipsePluginUtils {
 	private static String jobChangeListener = "org.eclipse.core.runtime.jobs.IJobChangeListener";
 	private static IClass RESOURCE_CHANGE_LISTENER = null;
 	private static String resourceChangeListener = "org.eclipse.core.resources.IResourceChangeListener";
+	private static IClass LAUNCH_CONFIG_LISTENER = null;
+	private static String launchConfigListener = "org.eclipse.debug.core.ILaunchConfigurationListener";
+	
 	//public void resourceChanged(IResourceChangeEvent event); invoked by non-UI
 	private static IClass ACTION = null;
 	private static String action = "org.eclipse.jface.action.Action";  //run() invoked by non-UI
@@ -277,6 +280,16 @@ public class EclipsePluginUtils {
 			throw new RuntimeException("The class is not found: " + resourceChangeListener);
 		}
 		return RESOURCE_CHANGE_LISTENER;
+	}
+	
+	public static IClass getLaunchConfigListener(ClassHierarchy cha) {
+		if(LAUNCH_CONFIG_LISTENER == null) {
+			LAUNCH_CONFIG_LISTENER = WALAUtils.lookupClass(cha, launchConfigListener);
+		}
+		if(LAUNCH_CONFIG_LISTENER == null) {
+			throw new RuntimeException("The class is not found: " + launchConfigListener);
+		}
+		return LAUNCH_CONFIG_LISTENER;
 	}
 	
 	public static IClass getAction(ClassHierarchy cha) {
@@ -507,6 +520,42 @@ public class EclipsePluginUtils {
 		}
 		return entries;
 	}
+	
+	public static Collection<Entrypoint> getAllPublicProtectedResourceChangeListenerMethods(ClassHierarchy cha, String[] packages) {
+		Collection<IClass> allResourceChanges = EclipsePluginUtils.getAllAppSubClasses(cha, getResourceChangeListener(cha), packages);
+		Set<IMethod> methodSet = new HashSet<IMethod>();
+		for(IClass c : allResourceChanges) {
+			for(IMethod m : c.getDeclaredMethods()) {
+				if(m.isProtected() || m.isPublic()) {
+					methodSet.add(m);
+				}
+			}
+		}
+		Collection<Entrypoint> entries = new HashSet<Entrypoint>();
+		for(IMethod m : methodSet) {
+		    entries.add(new DefaultEntrypoint(m, cha));
+		}
[…]

### 2012-01-28 GUIErrorDetector/tests/edu/washington/cs/detector/experiments/search/AnomalyCallChainSearcher.java
a preliminary implementation of exhaustive search

@@ -1,0 +1,90 @@
+package edu.washington.cs.detector.experiments.search;
+
+import java.util.Collection;
+import java.util.LinkedHashSet;
+import java.util.LinkedList;
+import java.util.List;
+
+import com.ibm.wala.ipa.callgraph.CGNode;
+import com.ibm.wala.ipa.cha.ClassHierarchy;
+import com.ibm.wala.util.graph.Graph;
+
+import edu.washington.cs.detector.MethodEvaluator;
+import edu.washington.cs.detector.NativeMethodConnector;
+import edu.washington.cs.detector.guider.CGTraverseGuider;
+
+public class AnomalyCallChainSearcher {
+	public final CGNode startNode;
+	public final Graph<CGNode> graph;
+	
+	private CGTraverseGuider startGuider = null;
+	private CGTraverseGuider uiGuider = null;
+	private NativeMethodConnector connector = null;
+	private ClassHierarchy cha = null;
+	private String[] checkings = null;
+	private MethodEvaluator evaluator = null;
+	
+	public AnomalyCallChainSearcher(Graph<CGNode> graph, CGNode startNode) {
+		this.startNode = startNode;
+		this.graph = graph;
+	}
+	
+	public Collection<List<CGNode>> findAllAnomalyCallChains() {
+		Collection<List<CGNode>> result = new LinkedHashSet<List<CGNode>>();
+		
+		ThreadStartSearcher startSearcher = new ThreadStartSearcher(this.graph, this.startNode);
+		if(startGuider != null) {startSearcher.setTraverseGuider(startGuider); }
+		
+		LinkedList<CGNode> visited = new LinkedList<CGNode>();
+		Collection<List<CGNode>> list2starts = startSearcher.breadFirst(this.graph, visited);
+		
+		for(List<CGNode> list : list2starts) {
+			CGNode lastNode = list.get(list.size() - 1);
+			if(!startSearcher.isDestNode(lastNode)) {
+				throw new RuntimeException("lastnode is not destnode: " + lastNode);
+			}
+			
+			UIAnomalySearcher uiSearcher = new UIAnomalySearcher(this.graph, lastNode);
+			if(this.uiGuider != null) {uiSearcher.setTraverseGuider(uiGuider); }
+			if(this.connector != null) {uiSearcher.setNativeMethodConnector(connector); }
+			if(this.checkings != null) {uiSearcher.setCheckingMethods(checkings);}
[…]

### 2012-01-28 GUIErrorDetector/tests/edu/washington/cs/detector/experiments/search/ExhaustiveSearcher.java

@@ -1,0 +1,110 @@
+package edu.washington.cs.detector.experiments.search;
+
+import java.util.Collection;
+import java.util.Iterator;
+import java.util.LinkedHashSet;
+import java.util.LinkedList;
+import java.util.List;
+
+import com.ibm.wala.ipa.callgraph.CGNode;
+import com.ibm.wala.util.graph.Graph;
+
+import edu.washington.cs.detector.NativeMethodConnector;
+import edu.washington.cs.detector.guider.CGTraverseDefaultGuider;
+import edu.washington.cs.detector.guider.CGTraverseGuider;
+
+abstract public class ExhaustiveSearcher {
+	
+	public final Graph<CGNode> graph;
+	
+	public final CGNode startNode;
+	
+	CGTraverseGuider guider = new CGTraverseDefaultGuider();
+	
+	protected NativeMethodConnector connector = NativeMethodConnector.createEmptyConnector();
+	
+	public ExhaustiveSearcher(Graph<CGNode> graph, CGNode startNode) {
+		this.graph = graph;
+		this.startNode = startNode;
+	}
+	
+	public void setTraverseGuider(CGTraverseGuider guider) {
+		this.guider = guider;
+	}
+	
+	public void setNativeMethodConnector(NativeMethodConnector connector) {
+		if(connector == null) {
+			throw new RuntimeException("The native connector can not be null.");
+		}
+		this.connector = connector;
+	}
+	
+	public Collection<List<CGNode>> breadFirst(Graph<CGNode> graph, LinkedList<CGNode> visited) {
+		Collection<List<CGNode>> returnChains = new LinkedHashSet<List<CGNode>>();
+		
+		CGNode lastNode = visited.getLast();
+		LinkedList<CGNode> nodes = this.getAdjacentNodes(graph, lastNode);// graph.adjacentNodes(visited.getLast());
+		if(lastNode.getMethod().isNative()) {
+			if(!nodes.isEmpty()) {
+				throw new RuntimeException("Must be empty.");
+			}
+			if(!this.connector.isEmpty()) {
+				nodes.addAll(this.connector.getSucc(graph, lastNode));
+			}
+		}
+		
+        // examine adjacent nodes
+        for (CGNode node : nodes) {
+            if (visited.contains(node)) {
+                continue;
+            }
+            if(!this.shouldVisit(lastNode, node)) {
+            	continue;
+            }
+            if (this.isDestNode(node)) {
+                visited.add(node);
+//                printPath(visited);
[…]

### 2012-01-28 GUIErrorDetector/tests/edu/washington/cs/detector/experiments/search/Search.java

@@ -1,0 +1,65 @@
+package edu.washington.cs.detector.experiments.search;
+
+import java.util.LinkedList;
+
+public class Search {
+
+    private static final String START = "B";
+    private static final String END = "E";
+
+    public static void main(String[] args) {
+        // this graph is directional
+        ExampleGraph graph = new ExampleGraph();
+        graph.addEdge("A", "B");
+        graph.addEdge("A", "C");
+        graph.addEdge("B", "A");
+        graph.addEdge("B", "D");
+        graph.addEdge("B", "E"); // this is the only one-way connection
+        graph.addEdge("B", "F");
+        graph.addEdge("C", "A");
+        graph.addEdge("C", "E");
+        graph.addEdge("C", "F");
+        graph.addEdge("D", "B");
+        graph.addEdge("E", "C");
+        graph.addEdge("E", "F");
+        graph.addEdge("F", "B");
+        graph.addEdge("F", "C");
+        graph.addEdge("F", "E");
+        LinkedList<String> visited = new LinkedList();
+        visited.add(START);
+        new Search().breadthFirst(graph, visited);
+    }
+
+    private void breadthFirst(ExampleGraph graph, LinkedList<String> visited) {
+        LinkedList<String> nodes = graph.adjacentNodes(visited.getLast());
+        // examine adjacent nodes
+        for (String node : nodes) {
+            if (visited.contains(node)) {
+                continue;
+            }
+            if (node.equals(END)) {
+                visited.add(node);
+                printPath(visited);
+                visited.removeLast();
+                break;
+            }
+        }
+        // in breadth-first, recursion needs to come after visiting adjacent nodes
+        for (String node : nodes) {
+            if (visited.contains(node) || node.equals(END)) {
+                continue;
+            }
+            visited.addLast(node);
+            breadthFirst(graph, visited);
+            visited.removeLast();
+        }
+    }
+
+    private void printPath(LinkedList<String> visited) {
+        for (String node : visited) {
+            System.out.print(node);
+            System.out.print(" ");
+        }
+        System.out.println();
+    }
+}

### 2012-01-28 trunk/GUIErrorDetector/tests/edu/washington/cs/detector/experiments/search/ExampleGraph.java
a preliminary implementation of exhaustive search

@@ -1,0 +1,41 @@
+package edu.washington.cs.detector.experiments.search;
+
+import java.util.HashMap;
+import java.util.LinkedHashSet;
+import java.util.LinkedList;
+import java.util.Map;
+import java.util.Set;
+
+public class ExampleGraph {
+    private Map<String, LinkedHashSet<String>> map = new HashMap();
+
+    public void addEdge(String node1, String node2) {
+        LinkedHashSet<String> adjacent = map.get(node1);
+        if(adjacent==null) {
+            adjacent = new LinkedHashSet();
+            map.put(node1, adjacent);
+        }
+        adjacent.add(node2);
+    }
+
+    public void addTwoWayVertex(String node1, String node2) {
+        addEdge(node1, node2);
+        addEdge(node2, node1);
+    }
+
+    public boolean isConnected(String node1, String node2) {
+        Set adjacent = map.get(node1);
+        if(adjacent==null) {
+            return false;
+        }
+        return adjacent.contains(node2);
+    }
+
+    public LinkedList<String> adjacentNodes(String last) {
+        LinkedHashSet<String> adjacent = map.get(last);
+        if(adjacent==null) {
+            return new LinkedList();
+        }
+        return new LinkedList<String>(adjacent);
+    }
+}

### 2012-01-28 trunk/GUIErrorDetector/tests/edu/washington/cs/detector/experiments/search/ThreadStartSearcher.java

@@ -1,0 +1,19 @@
+package edu.washington.cs.detector.experiments.search;
+
+import com.ibm.wala.ipa.callgraph.CGNode;
+import com.ibm.wala.util.graph.Graph;
+
+import edu.washington.cs.detector.ThreadStartFinder;
+
+public class ThreadStartSearcher extends ExhaustiveSearcher {
+	
+	public ThreadStartSearcher(Graph<CGNode> graph, CGNode startNode) {
+		super(graph, startNode);
+	}
+
+	@Override
+	public boolean isDestNode(CGNode node) {
+		return ThreadStartFinder.isThreadStartNode(node);
+	}
+	
+}

### 2012-01-28 trunk/GUIErrorDetector/tests/edu/washington/cs/detector/experiments/search/UIAnomalySearcher.java

@@ -1,0 +1,55 @@
+package edu.washington.cs.detector.experiments.search;
+
+import com.ibm.wala.classLoader.IMethod;
+import com.ibm.wala.ipa.callgraph.CGNode;
+import com.ibm.wala.ipa.cha.ClassHierarchy;
+import com.ibm.wala.util.graph.Graph;
+
+import edu.washington.cs.detector.MethodEvaluator;
+import edu.washington.cs.detector.util.Files;
+import edu.washington.cs.detector.util.Utils;
+
+public class UIAnomalySearcher extends ExhaustiveSearcher {
+	
+	private MethodEvaluator evaluator = null;
+	
+	private ClassHierarchy cha;
+	
+	private String[] checking_methods
+    = Files.readWholeNoExp("./src/checking_methods.txt").toArray(new String[0]);
+
+	public UIAnomalySearcher(Graph<CGNode> graph, CGNode startNode) {
+		super(graph, startNode);
+	}
+	
+	public void setMethodEvaluator(MethodEvaluator evl) {
+		System.err.println("Use method evaluator to identify UI-accessing method: " + evl);
+		evaluator = evl;
+	}
+	
+	public void setClassHierarchy(ClassHierarchy cha) {
+		this.cha = cha;
+	}
+	
+	public void setCheckingMethods(String[] checkings) {
+		this.checking_methods = checkings;
+	}
+	
+	@Override
+	public boolean isDestNode(CGNode node) {
+		IMethod m = node.getMethod();
+		String methodSig = m.getSignature();
+		//System.out.println(methodSig);
+		if(Utils.<String>includedIn(methodSig, checking_methods) ) {
+			return true;
+		} else if(evaluator != null) {
+			if(this.cha == null) {
+				throw new RuntimeException("If the evaluator is set, ClassHierarchy can not be null.");
+			}
+			return evaluator.isThreadUnsafeMethod(this.cha, m);
+		} else {
+			return false;
+		}
+	}
+
+}

### 2012-01-28 trunk/GUIErrorDetector/tests/edu/washington/cs/detector/experiments/search/SimpleClock.java
a simple clock implementation

@@ -1,0 +1,35 @@
+package edu.washington.cs.detector.experiments.search;
+
+public class SimpleClock {
+	
+	static long startTime = -1;
+	
+	static long budget = -1;
+	
+	public static void start() {
+		if(startTime > 0) {
+			throw new RuntimeException();
+		}
+		System.err.println("Clock started...");
+		startTime = System.currentTimeMillis();
+	}
+	
+	public static void setBudget(long b) {
+		System.err.println(" budget set, max millis: " + b);
+		budget = b;
+	}
+	
+	public static void reset() {
+		System.err.println("Clock reset...");
+		startTime = -1;
+		budget = -1;
+	}
+	
+	public static boolean finish() {
+		if(startTime < 0) {
+			throw new RuntimeException();
+		}
+		return System.currentTimeMillis() - startTime > budget;
+	}
+	
+}

### 2012-01-29 trunk/GUIErrorDetector/sampleprogram/test/openparameter/B.java
revise for experiment

@@ -1,21 +1,38 @@
 package test.openparameter;
 
-class Entry {
-	public void callFoo2(B p) {
-		p.callFoo();
+
+
+abstract public class B {
+	public void foo()  {}
+	public static B b;
+	public void onCreate() {
+		b = this;
 	}
 }
 
-public class B {
-	private A a;
-	public B(Object o) {
-		a = new A(null);
+class A {
+	C c;
+	
+	public A() {
+		c = new C(this);
 	}
+	
 	public void callFoo() {
-		a.foo();
+		B.b.foo();
+	}
+	
+	public void callAnother() {
+		c.callback();
 	}
 }
-class A {
-	public A(Object o) {}
-	public void foo() {}
+
+class C {
+	A a;
+	public C(A a) {
+		this.a = a;
+	}
+	
+	public void callback() {
+		a.callFoo();
+	}
 }

### 2012-01-29 trunk/GUIErrorDetector/tests/edu/washington/cs/detector/experiments/android/TestMytracksAndroid.java
for supplementary experiments in evaluating various cg search strategies

@@ -13,6 +13,7 @@ import edu.washington.cs.detector.AnomalyCallChain;
 import edu.washington.cs.detector.CGBuilder;
 import edu.washington.cs.detector.CGEntryManager;
 import edu.washington.cs.detector.CallChainFilter;
+import edu.washington.cs.detector.UIAnomalyDetector;
 import edu.washington.cs.detector.UIAnomalyMethodFinder;
 import edu.washington.cs.detector.CGBuilder.CG;
 import edu.washington.cs.detector.experiments.filters.MergeSameEntryToStartPathStrategy;
@@ -112,7 +113,9 @@ public class TestMytracksAndroid extends AbstractAndroidTest {
 			CG type = CG.RTA;
 			type = CG.FakeZeroCFA;
 			type = CG.OneCFA;
-			//this finds bug
+			
+			UIAnomalyDetector.setToUseDFS();
+			
 		    List<AnomalyCallChain> chains = super.findErrorsInAndroidApp(type, ui2startGuider, start2checkGuider);
 //		    List<AnomalyCallChain> chains = super.findErrorsInAndroidApp(CG.OneCFA, ui2startGuider, start2checkGuider);
 //		    List<AnomalyCallChain> chains = super.findErrorsInAndroidApp(CG.FakeZeroCFA, ui2startGuider, start2checkGuider);

### 2012-01-29 trunk/GUIErrorDetector/tests/edu/washington/cs/detector/experiments/android/TestSGTPuzzle.java

@@ -18,6 +18,7 @@ import edu.washington.cs.detector.CGEntryManager;
 import edu.washington.cs.detector.CallChainFilter;
 import edu.washington.cs.detector.CGBuilder.CG;
 import edu.washington.cs.detector.NativeMethodConnector;
+import edu.washington.cs.detector.UIAnomalyDetector;
 import edu.washington.cs.detector.experiments.filters.RemoveNoClientClassStrategy;
 import edu.washington.cs.detector.experiments.filters.RemoveNonClientHeadStrategy;
 import edu.washington.cs.detector.guider.CGTraverseAndroidGuider;
@@ -101,6 +102,10 @@ public class TestSGTPuzzle extends AbstractAndroidTest {
 		  CG type = CG.FakeZeroCFA;
 		  type = CG.OneCFA;
 //		  type = CG.RTA;
+		  
+//		  super.setExhaustiveSearch(true);
+		  UIAnomalyDetector.setToUseDFS();
+		  
 		  super.setAndroidCheckingFile("./tests/edu/washington/cs/detector/checkingmethods_for_android_extra.txt");
 //		  super.setByfileName("sgtpuzzle.xml");
 		  List<AnomalyCallChain> chains = super.findErrorsInAndroidApp(type, ui2startGuider, start2checkGuider, connector);

### 2012-01-29 trunk/GUIErrorDetector/tests/edu/washington/cs/detector/experiments/eclipseplugin/AbstractEclipsePluginTest.java

@@ -2,6 +2,7 @@ package edu.washington.cs.detector.experiments.eclipseplugin;
 
 import java.io.IOException;
 import java.util.Collection;
+import java.util.LinkedHashSet;
 import java.util.LinkedList;
 import java.util.List;
 
@@ -26,6 +27,9 @@ import edu.washington.cs.detector.experiments.filters.RemoveNoClientClassStrateg
 import edu.washington.cs.detector.experiments.filters.RemoveSameEntryStrategy;
 import edu.washington.cs.detector.experiments.filters.RemoveSubsumedChainStrategy;
 import edu.washington.cs.detector.experiments.filters.RemoveSystemCallStrategy;
+import edu.washington.cs.detector.experiments.search.AnomalyCallChainSearcher;
+import edu.washington.cs.detector.experiments.search.ExhaustiveSearcher;
+import edu.washington.cs.detector.experiments.search.SimpleClock;
 import edu.washington.cs.detector.experiments.straightforward.TestEclipsePlugins;
 import edu.washington.cs.detector.guider.CGTraverseGuider;
 import edu.washington.cs.detector.guider.CGTraverseNoSystemCalls;
@@ -52,6 +56,7 @@ public abstract class AbstractEclipsePluginTest extends TestCase {
 	private boolean see_ui_access_runnable = false;
 	private boolean runnaiveapproach = false;
 	private boolean addrunnable = true;
+	private boolean useexhaustivesearch = false;
 	
 	//these four methods must be overriden
 	protected abstract Iterable<Entrypoint> getEntrypoints(ClassHierarchy cha);
@@ -92,6 +97,10 @@ public abstract class AbstractEclipsePluginTest extends TestCase {
 	
 	protected void setAddRunnable(boolean runnable) {
 		this.addrunnable = runnable;
+	}
+	
+	protected void setExhaustiveSearch(boolean exhaust) {
+		this.useexhaustivesearch = exhaust;
 	}
 	
 	public Collection<AnomalyCallChain> reportUIErrors() throws IOException, ClassHierarchyException {
@@ -159,10 +168,14 @@ public abstract class AbstractEclipsePluginTest extends TestCase {
 		//note that, the execution will return from here
 		List<AnomalyCallChain> chains  = new LinkedList<AnomalyCallChain>();
 		
+		Collection<CGNode> eventNodes = new LinkedHashSet<CGNode>();
+		
 		if(this.see_ui_access_runnable) {
 			
[…]

### 2012-01-29 trunk/GUIErrorDetector/tests/edu/washington/cs/detector/experiments/eclipseplugin/TestEclipseRunnerPlugin.java

@@ -122,10 +122,13 @@ public class TestEclipseRunnerPlugin extends AbstractEclipsePluginTest {
 		super.setSeeUIAccessRunnable(true);
 		
 //		super.setCGType(CG.ZeroCFA);
-//		super.setCGType(CG.OneCFA);
+		super.setCGType(CG.OneCFA);
 //		super.setCGType(CG.RTA);
-		super.setCGType(CG.ZeroCFA);
+//		super.setCGType(CG.ZeroCFA);
 //		super.setRunNaiveApproach(true);
+		
+//		super.setExhaustiveSearch(true);
+		UIAnomalyDetector.setToUseDFS();
 		
 		super.setThreadStartGuider(new CGTraverseSWTGuider());
 		super.setUIAnomalyGuider(new CGTraverseSWTGuider());

### 2012-01-29 trunk/GUIErrorDetector/tests/edu/washington/cs/detector/experiments/filters/RemoveSubsumedChainStrategy.java

@@ -32,7 +32,8 @@ public class RemoveSubsumedChainStrategy extends FilterStrategy {
 		
 		for(AnomalyCallChain chain : chains) {
 			//the flat string of the anomaly call chain
-			String chainStr = AnomalyCallChain.flatCGNodeList(chain.getFullCallChain());
+			String chainStr = //AnomalyCallChain.flatCGNodeList(chain.getFullCallChain());
+				AnomalyCallChain.flatCGNodeListWithoutContext(chain.getFullCallChain());
 			
 			boolean shouldAdd = true;
 			List<AnomalyCallChain> shouldRemoveList = new LinkedList<AnomalyCallChain>();

### 2012-01-29 trunk/GUIErrorDetector/tests/edu/washington/cs/detector/experiments/search/ExhaustiveSearcher.java

@@ -15,6 +15,8 @@ import edu.washington.cs.detector.guider.CGTraverseGuider;
 
 abstract public class ExhaustiveSearcher {
 	
+	public static boolean USE_CLOCK = false;
+	
 	public final Graph<CGNode> graph;
 	
 	public final CGNode startNode;
@@ -42,6 +44,12 @@ abstract public class ExhaustiveSearcher {
 	public Collection<List<CGNode>> breadFirst(Graph<CGNode> graph, LinkedList<CGNode> visited) {
 		Collection<List<CGNode>> returnChains = new LinkedHashSet<List<CGNode>>();
 		
+		if(USE_CLOCK) {
+        	if(SimpleClock.finish()) {
+        		return returnChains;
+        	}
+        }
+		
 		CGNode lastNode = visited.getLast();
 		LinkedList<CGNode> nodes = this.getAdjacentNodes(graph, lastNode);// graph.adjacentNodes(visited.getLast());
 		if(lastNode.getMethod().isNative()) {
@@ -67,6 +75,12 @@ abstract public class ExhaustiveSearcher {
                 List<CGNode> chain = this.generatePath(visited);
                 returnChains.add(chain);
                 
+                if(USE_CLOCK) {
+                	if(SimpleClock.finish()) {
+                		return returnChains;
+                	}
+                }
+                
                 visited.removeLast();
                 break;
             }
@@ -76,6 +90,12 @@ abstract public class ExhaustiveSearcher {
             if (visited.contains(node) || this.isDestNode(node)) {
                 continue;
             }
+            if(USE_CLOCK) {
+            	if(SimpleClock.finish()) {
+            		return returnChains;
+            	}
+            }
+            
             visited.addLast(node);
 //            breadthFirst(graph, visited);
             returnChains.addAll(breadFirst(graph, visited));
@@ -95,9 +115,9 @@ abstract public class ExhaustiveSearcher {
 		return l;
 	}
 	
-	abstract public boolean isDestNode(CGNode node);
+	abstract protected boolean isDestNode(CGNode node);
 	
-	public boolean shouldVisit(CGNode srcNode, CGNode destNode) {
+	private boolean shouldVisit(CGNode srcNode, CGNode destNode) {
 		return guider.traverse(srcNode, destNode);
 	}
 	

### 2012-01-29 trunk/GUIErrorDetector/tests/edu/washington/cs/detector/experiments/swing/AbstractSwingTest.java

@@ -17,6 +17,7 @@ import edu.washington.cs.detector.CGBuilder.CG;
 import edu.washington.cs.detector.CGEntryManager;
 import edu.washington.cs.detector.CallChainFilter;
 import edu.washington.cs.detector.SwingUIMethodEvaluator;
+import edu.washington.cs.detector.ThreadStartFinder;
 import edu.washington.cs.detector.UIAnomalyDetector;
 import edu.washington.cs.detector.UIAnomalyMethodFinder;
 import edu.washington.cs.detector.experiments.filters.MatchRunWithInvokeClassStrategy;
@@ -54,6 +55,8 @@ public abstract class AbstractSwingTest extends TestCase {
 	
 	private CGTraverseGuider uiAnomalyGuider = null;
 	
+	private boolean useexhaustivesearch = false;
+	
 	protected void setCGType(CG t) {
 		type = t;
 	}
@@ -80,6 +83,10 @@ public abstract class AbstractSwingTest extends TestCase {
 	
 	protected void setTweakStartnode(boolean tweak) {
 		this.tweak_startnode = tweak;
+	}
+	
+	protected void setExhaustiveSearch(boolean exhaust) {
+		this.useexhaustivesearch = exhaust;
 	}
 	
 	protected Iterable<Entrypoint> getAdditonalEntrypoints(ClassHierarchy cha) {
@@ -188,7 +195,9 @@ public abstract class AbstractSwingTest extends TestCase {
 		}
 
 		//start to detect errors
+		long start = System.currentTimeMillis();
 		chains = detector.detectUIAnomaly(builder, nodes);
+		
 		
 		System.out.println("size of chains before removing redundancy: " + chains.size());
 		chains = Utils.removeRedundantAnomalyCallChains(chains);
@@ -225,6 +234,10 @@ public abstract class AbstractSwingTest extends TestCase {
 		if(expectedNum != -1) {
 		    assertEquals("The number of expected call chain is wrong", expectedNum, chains.size());
 		}
+		
+		long end = System.currentTimeMillis();
+		
+		System.out.println("Total time cost: " + (start - end) + "-millis");
 		
 		//resort the state to move dependent tests
 		UIAnomalyMethodFinder.setMethodEvaluator(null);

### 2012-01-29 trunk/GUIErrorDetector/tests/edu/washington/cs/detector/experiments/swing/TestSudokuPuzzleSolver.java

@@ -42,6 +42,8 @@ public class TestSudokuPuzzleSolver extends AbstractSwingTest {
 		super.setCGType(CG.FakeZeroCFA);
 		super.setCGType(CG.OneCFA);
 		
+		UIAnomalyDetector.setToUseDFS(); //use DFS
+		
 		super.setNondefaultCG(true);
 		super.setAddExtraEntrypoints(true);
 		

### 2012-01-29 GUIErrorDetector/tests/edu/washington/cs/detector/TestBuildCGForOpenProgram.java
for supplementary experiments in evaluating various cg search strategies

@@ -27,7 +27,7 @@ public class TestBuildCGForOpenProgram extends TestCase {
 		CGBuilder builder = new CGBuilder(appPath);
 		
 		builder.makeScopeAndClassHierarchy();
-		Iterable<Entrypoint> entries = CGEntryManager.getAllPublicMethods(builder, "test.openparameter.Entry");
+		Iterable<Entrypoint> entries = CGEntryManager.getAllPublicMethods(builder,  "test.openparameter.A", "test.openparameter.B", "test.openparameter.C");
 		
 		System.out.println("Number of entries to build CG: " + Utils.countIterable(entries));
 		System.out.println("All iterables: " + Utils.iterableToCollection(entries));

### 2012-01-29 GUIErrorDetector/tests/edu/washington/cs/detector/experiments/android/AbstractAndroidTest.java

@@ -28,6 +28,7 @@ import edu.washington.cs.detector.CGBuilder;
 import edu.washington.cs.detector.CGEntryManager;
 import edu.washington.cs.detector.CallChainFilter;
 import edu.washington.cs.detector.NativeMethodConnector;
+import edu.washington.cs.detector.ThreadStartFinder;
 import edu.washington.cs.detector.UIAnomalyDetector;
 import edu.washington.cs.detector.UIAnomalyMethodFinder;
 import edu.washington.cs.detector.CGBuilder.CG;
@@ -36,6 +37,9 @@ import edu.washington.cs.detector.experiments.filters.MergeSamePrefixToLibCallSt
 import edu.washington.cs.detector.experiments.filters.MergeSameTailStrategy;
 import edu.washington.cs.detector.experiments.filters.RemoveSubsumedChainStrategy;
 import edu.washington.cs.detector.experiments.filters.RemoveSystemCallStrategy;
+import edu.washington.cs.detector.experiments.search.AnomalyCallChainSearcher;
+import edu.washington.cs.detector.experiments.search.ExhaustiveSearcher;
+import edu.washington.cs.detector.experiments.search.SimpleClock;
 import edu.washington.cs.detector.experiments.straightforward.TestAndroids;
 import edu.washington.cs.detector.guider.CGTraverseGuider;
 import edu.washington.cs.detector.guider.CGTraverseNoSystemCalls;
@@ -58,6 +62,8 @@ public abstract class AbstractAndroidTest extends TestCase {
 	private String bypassFileName = null;
 	private String androidcheckingfile = null;
 	
+	private boolean useexhaustivesearch = false;
+	
 	public void setRunnaiveApproach(boolean app) {
 		this.runnaiveapproach = app;
 	}
@@ -69,6 +75,10 @@ public abstract class AbstractAndroidTest extends TestCase {
 	}
 	public void setAndroidCheckingFile(String file) {
 		this.androidcheckingfile = file;
+	}
+	
+	protected void setExhaustiveSearch(boolean exhaust) {
+		this.useexhaustivesearch = exhaust;
 	}
 	
 	abstract protected String getAppPath();
@@ -254,7 +264,8 @@ public abstract class AbstractAndroidTest extends TestCase {
 		
 		//set up the anomaly detection
 		UIAnomalyDetector detector = new UIAnomalyDetector(getAppPath());
[…]

### 2012-01-29 GUIErrorDetector/tests/edu/washington/cs/detector/experiments/android/TestMozillaFirefox.java

@@ -15,6 +15,7 @@ import edu.washington.cs.detector.AnomalyCallChain;
 import edu.washington.cs.detector.CGBuilder;
 import edu.washington.cs.detector.CGEntryManager;
 import edu.washington.cs.detector.CGBuilder.CG;
+import edu.washington.cs.detector.UIAnomalyDetector;
 import edu.washington.cs.detector.guider.CGTraverseAndroidGuider;
 import edu.washington.cs.detector.guider.CGTraverseExploreClientRunnableStrategy;
 import edu.washington.cs.detector.guider.CGTraverseGuider;
@@ -133,8 +134,10 @@ public class TestMozillaFirefox extends AbstractAndroidTest {
 			
 			//this finds bugs
 			CG type = CG.FakeZeroCFA;
-//			type = CG.OneCFA;
+			type = CG.OneCFA;
 //			type = CG.RTA;
+			
+			UIAnomalyDetector.setToUseDFS();
 			
 		    List<AnomalyCallChain> chains = super.findErrorsInAndroidApp(type, ui2startGuider, start2checkGuider);
 //		    List<AnomalyCallChain> chains = super.findErrorsInAndroidApp(CG.ZeroCFA, ui2startGuider, start2checkGuider);

### 2012-01-29 GUIErrorDetector/tests/edu/washington/cs/detector/experiments/eclipseplugin/TestHundsonPlugin.java

@@ -114,11 +114,14 @@ public class TestHundsonPlugin extends AbstractEclipsePluginTest {
 		super.setAddRunnable(false);
 		
 //		super.setCGType(CG.ZeroCFA);
-//		super.setCGType(CG.OneCFA);
+		super.setCGType(CG.OneCFA);
 //		super.setCGType(CG.RTA);
-		super.setCGType(CG.FakeZeroCFA);
+//		super.setCGType(CG.FakeZeroCFA);
 		
 //		super.setRunNaiveApproach(true);
+		
+//		super.setExhaustiveSearch(true); //Experimentation on exhaustive search
+		UIAnomalyDetector.setToUseDFS(); //for experiment using DFS
 		
 		super.setThreadStartGuider(new CGTraverseSWTGuider());
 		super.setUIAnomalyGuider(new CGTraverseSWTGuider());

### 2012-01-29 GUIErrorDetector/tests/edu/washington/cs/detector/experiments/filters/MergeSameEntryToStartPathStrategy.java

@@ -18,7 +18,8 @@ public class MergeSameEntryToStartPathStrategy extends FilterStrategy {
 		Set<String> uniqueEntryToStartPath = new HashSet<String>();
 		
 		for(AnomalyCallChain chain : chains) {
-			String str = AnomalyCallChain.flatCGNodeList(chain.getUI2Start());
+//			String str = AnomalyCallChain.flatCGNodeList(chain.getUI2Start());
+			String str = AnomalyCallChain.flatCGNodeListWithoutContext(chain.getUI2Start());
 			if(!uniqueEntryToStartPath.contains(str)) {
 				uniqueEntryToStartPath.add(str);
 				result.add(chain);

### 2012-01-29 GUIErrorDetector/tests/edu/washington/cs/detector/experiments/filters/MergeSamePrefixToLibCallStrategy.java

@@ -39,7 +39,7 @@ public class MergeSamePrefixToLibCallStrategy extends FilterStrategy {
 //					continue;
 				}
 				List<CGNode> entryToNonLibCall = chain.getFullCallChain().subList(0, index + 1);
-				String chainStr = AnomalyCallChain.flatCGNodeList(entryToNonLibCall);
+				String chainStr = AnomalyCallChain.flatCGNodeListWithoutContext(entryToNonLibCall);
 				if(!chainMap.containsKey(chainStr)) {
 					chainMap.put(chainStr, chain);
 				}

### 2012-01-29 GUIErrorDetector/tests/edu/washington/cs/detector/experiments/search/AnomalyCallChainSearcher.java

@@ -14,7 +14,7 @@ import edu.washington.cs.detector.NativeMethodConnector;
 import edu.washington.cs.detector.guider.CGTraverseGuider;
 
 public class AnomalyCallChainSearcher {
-	public final CGNode startNode;
+	public final Collection<CGNode> startNodes;
 	public final Graph<CGNode> graph;
 	
 	private CGTraverseGuider startGuider = null;
@@ -24,18 +24,61 @@ public class AnomalyCallChainSearcher {
 	private String[] checkings = null;
 	private MethodEvaluator evaluator = null;
 	
-	public AnomalyCallChainSearcher(Graph<CGNode> graph, CGNode startNode) {
-		this.startNode = startNode;
+	public AnomalyCallChainSearcher(Graph<CGNode> graph, Collection<CGNode> startNodes) {
+		this.startNodes = startNodes;
 		this.graph = graph;
 	}
 	
-	public Collection<List<CGNode>> findAllAnomalyCallChains() {
+	/**
+	 * Find the full chain from entry node to thread.start to UI-accessing methods
+	 * */
+	public Collection<List<CGNode>> findFullAnomalyCallChains() {
+		Collection<List<CGNode>> all = new LinkedHashSet<List<CGNode>>();
+		for(CGNode startNode : this.startNodes) {
+			all.addAll(this.findFullAnomalyCallChains(startNode));
+		}
+		return all;
+	}
+	
+	/**
+	 * Find a method call chain from runnable or other  job methods to UI-accessing methods 
+	 * */
+	public Collection<List<CGNode>> findUIAnomalyCallChains() {
 		Collection<List<CGNode>> result = new LinkedHashSet<List<CGNode>>();
 		
-		ThreadStartSearcher startSearcher = new ThreadStartSearcher(this.graph, this.startNode);
+		for(CGNode startNode : this.startNodes) {
+			System.out.println("start from: " + startNode);
+			
+			UIAnomalySearcher uiSearcher = new UIAnomalySearcher(this.graph, startNode);
+			
+			//set all parts
+			if(this.uiGuider != null) {uiSearcher.setTraverseGuider(uiGuider); }
+			if(this.connector != null) {uiSearcher.setNativeMethodConnector(connector); }
+			if(this.checkings != null) {uiSearcher.setCheckingMethods(checkings);}
+			if(this.cha != null) {uiSearcher.setClassHierarchy(cha);}
[…]

### 2012-01-29 GUIErrorDetector/tests/edu/washington/cs/detector/experiments/search/UIAnomalySearcher.java

@@ -15,8 +15,7 @@ public class UIAnomalySearcher extends ExhaustiveSearcher {
 	
 	private ClassHierarchy cha;
 	
-	private String[] checking_methods
-    = Files.readWholeNoExp("./src/checking_methods.txt").toArray(new String[0]);
+	private String[] checking_methods = Files.readWholeNoExp("./src/checking_methods.txt").toArray(new String[0]);
 
 	public UIAnomalySearcher(Graph<CGNode> graph, CGNode startNode) {
 		super(graph, startNode);

### 2012-01-29 GUIErrorDetector/tests/edu/washington/cs/detector/experiments/swing/TestS3Dropbox.java

@@ -67,8 +67,10 @@ public class TestS3Dropbox extends AbstractSwingTest {
 		
 		UIAnomalyDetector.DEBUG = true;
 		super.setCGType(CG.OneCFA);
-		super.setCGType(CG.RTA);
-		super.setCGType(CG.ZeroCFA);
+//		super.setCGType(CG.RTA);
+//		super.setCGType(CG.ZeroCFA);
+		
+		UIAnomalyDetector.setToUseDFS(); //use DFS
 		
 		super.setNondefaultCG(true);
 //		super.setAddHandlers(true);

### 2012-01-29 GUIErrorDetector/tests/edu/washington/cs/detector/experiments/swt/TestFileBunker.java

@@ -49,10 +49,13 @@ public class TestFileBunker extends TestCase {
         
 		//configure the call graph builder, use 1-CFA as default
 		CGBuilder builder = new CGBuilder(path);
-//		builder.setCGType(CG.OneCFA);
+		builder.setCGType(CG.OneCFA);
 //		builder.setCGType(CG.RTA);
 //		builder.setCGType(CG.ZeroCFA);
-		builder.setCGType(CG.FakeZeroCFA);
+//		builder.setCGType(CG.FakeZeroCFA);
+		
+		UIAnomalyDetector.setToUseDFS();
+		
 		builder.buildCG();
 		//dump debugging information
 		WALAUtils.dumpClasses(builder.getClassHierarchy(), "./logs/loaded_classes.txt");

### 2012-01-29 GUIErrorDetector/tests/edu/washington/cs/detector/experiments/swt/TestVirgoFtp.java

@@ -37,9 +37,12 @@ public class TestVirgoFtp extends TestCase {
         detector.setUIAnomalyGuider(new CGTraverseSWTGuider());
 		
 		CGBuilder builder = new CGBuilder(path);
-//		builder.setCGType(CG.OneCFA);
-		builder.setCGType(CG.RTA);
-		builder.setCGType(CG.FakeZeroCFA);
+		builder.setCGType(CG.OneCFA);
+//		builder.setCGType(CG.RTA);
+//		builder.setCGType(CG.FakeZeroCFA);
+		
+		UIAnomalyDetector.setToUseDFS();
+		
 		builder.buildCG();
 		
 		WALAUtils.dumpClasses(builder.getClassHierarchy(), "./logs/loaded_classes.txt");

### 2012-01-29 GUIErrorDetector/src/edu/washington/cs/detector/ThreadStartFinder.java
revise for conducting supplementary experiments in evaluating cg

@@ -16,7 +16,13 @@ import edu.washington.cs.detector.guider.CGTraverseDefaultGuider;
 import edu.washington.cs.detector.guider.CGTraverseGuider;
 import edu.washington.cs.detector.util.Log;
 
+/**
+ * Another way for comparison is to find all paths between 2 nodes
+ * http://stackoverflow.com/questions/58306/graph-algorithm-to-find-all-connections-between-two-arbitrary-vertices
+ * */
 public class ThreadStartFinder {
+	
+	public static boolean USE_DEF = false;
 
 	public final Graph<CGNode> cg;
 
@@ -65,7 +71,11 @@ public class ThreadStartFinder {
 		while(!queue.isEmpty()) {
 			//System.out.println("visited node: ");
 			//System.out.println(visited);
-			CGNode node = queue.remove(0);
+			int removeIndex = 0;
+			if(USE_DEF) {
+				removeIndex = queue.size() - 1;
+			}
+			CGNode node = queue.remove(removeIndex); //queue.remove(0); //change to remove the last one for dfs
 			
 			assert cgNodeMap.containsKey(node);
 			CallChainNode chainNode = cgNodeMap.get(node);

### 2012-01-29 GUIErrorDetector/src/edu/washington/cs/detector/UIAnomalyDetector.java

@@ -27,6 +27,11 @@ public class UIAnomalyDetector {
 	
 	public static final String EXCLUSION_FILE_SWING = "Java60RegressionExclusionsWithoutGUI.txt";
 	public static final String EMPTY_FILE = "EmptyExclusion.txt";
+		
+	public static void setToUseDFS() {
+		ThreadStartFinder.USE_DEF = true;
+		UIAnomalyMethodFinder.USE_DEF = true;
+	}
 	
 	private final String appPath;
 	private String exclusion_file = CallGraphTestUtil.REGRESSION_EXCLUSIONS;

### 2012-01-29 GUIErrorDetector/src/edu/washington/cs/detector/UIAnomalyMethodFinder.java

@@ -22,6 +22,8 @@ import edu.washington.cs.detector.util.WALAUtils;
 
 public class UIAnomalyMethodFinder extends AbstractMethodFinder {
 	
+	public static boolean USE_DEF = false;
+	
 	public static boolean DEBUG = false;
 	
 	//some methods like Display#getBounds won't touch a UI element, but call checkDevice
@@ -143,7 +145,11 @@ public class UIAnomalyMethodFinder extends AbstractMethodFinder {
 		}
 		//perform BFS search here
 		while(!queue.isEmpty()) {
-			CGNode node = queue.remove(0);
+			int removeIndex = 0;
+			if(USE_DEF) {
+				removeIndex = queue.size() - 1;
+			}
+			CGNode node = queue.remove(removeIndex);//queue.remove(0); //remove the last for DFS
 			Log.logln("Visiting node: " + node, DEBUG);
 			
 			assert cgNodeMap.containsKey(node);

### 2012-01-29 trunk/GUIErrorDetector/paper/evaluation.tex
add more data

@@
  \hline
- Fennec & 14058 / 14387 &  55 / 54 &  0 / 0 & 8263 / 8898 & 0 / 0 & 0 / 0& 29125/ 31759 & xx / xxx & 0 / xxx& 433 & 1 \\
+ Fennec & 14058 / 14387 &  1 / 1 &  0 / 0 & 8263 / 8898 & 1 / 1 & 0 / 0& 29125/ 31759 & 3 / 3 & 1 / 1& 433 & 1 \\
  \hline
- MyTracks & 24036 / 24036 &  161 / 220 & 0 / 0 & 10803 / 13645 & 119 / 119 & 0 / 0 & 39235 / 110977 & 61 / xxx & 0 / xxx& 1192 & 1 \\
+ MyTracks & 24036 / 24036 &  161 / 220 & 0 / 0 & 10803 / 13645 & 119 / 119 & 0 / 0 & 39235 / 110977 & 61 / 1 & 0 / 1 & 1192 & 1 \\
 \hline
@@
  \fontsize{9pt}{\baselineskip}\selectfont
-\setlength{\tabcolsep}{.01\tabcolsep}
+\setlength{\tabcolsep}{.81\tabcolsep}
 \hspace*{-0.2cm}
@@
 \hline
- Subject & Before & \#Warning & \#Warning & \#Warning & \#Warning& \#Warning \\
+ Subject & Before & \#W & \#W & \#W & \#W& \#W \\
  Program & Filtering & $F_1$ & $F_2$ & $F_3$&$F_4$ & $F_5$\\
@@
  \hline
- Fennec &  xxxx &  xx &  xxx & xx &  xxx & xx\\
+ Fennec &  122 &  84 & 84 & 84 &  9 & 3\\
  \hline
- MyTracks &  xxxx &  xx &  xxx & xx &  xxx & xx\\
+ MyTracks &  1176 &  441 &  441 & 441 &  63 & 1 \\
 \hline
@@
 shows the output warning number using the reflection-aware 1-CFA algorithm.
-Column ``\#Warning $F_i$'' represents the number of remaining warnings after applying
+Column ``\#W $F_i$'' represents the number of remaining warnings after applying
 filters 1 -- $i$, and the number in last column is taken
@@
 
+\subsection{Comparing Graph Search Strategies}
+\label{sec:search}
+
+We next empirically compare different search strategies.
+
+Exhaustive search, and dfs, we found exhaustive search strategy
+can not terminte on any of the evaluated subject program, since the
+path is expoentially large to the graph node. For a realistic, program
+We implemented two alternative
+
+We check the path explored by the exhaustive algorithm
+
+Use DFS, avoid going too deep, under the setting of OneCFA. The time cost
+is almost identical
+
+The costs a tremedous more time than BFS, generates more warnings.
+
+Hundson: 3, 1
+
+EclipseRunner: 6, 1
+
+S3dropbox: ? , ?  too many warnings time: 31678 (45528 chains), running out of memory
+
+SudokuSolver:  2, 1 too many warnings: 1700, 2090
+
+VirgoFTP: 2, 2
+
+FileBunker:  2, 0  //very long method calls
+
+Fennec: 3, 1
+
+SGTPuzzler: 1, 1
+
+MyTracks: 1, 1
+
 \subsection{Discussions}
 
+\textbf{what about other graph traverse algorithms}
+
 We next discuss several important issues in our evaluation.
+
+excluding the call graph construction time.
 

### 2012-01-30 trunk/GUIErrorDetector/paper/implementation.tex
update

@@
 errors, and scales to realistic programs.  
-Optionally, the user may specify additional heuristics to guide call graph
-traverse, and annotate calling relations for native methods (Section~\ref{sec:heuristic}).
+Optionally, users may specify additional heuristic filters (Section~\ref{sec:heuristic}) %to guide call graph traverse
+, and annotate call relationships for native methods (Section~\ref{sec:annotation}).
 
 Our current implementation supports four widely-used GUI frameworks, namely
-SWT, Eclipse plugin development environment, Java Swing, and Android.
-Our implementation handles all of the Java language, and also takes
+SWT, Eclipse plugin development, Java Swing, and Android.
+Our implementation %handles all of the Java language, and
+also takes
 all dependent libraries (e.g., \CodeIn{rt.jar} and \CodeIn{android.jar})
-into analysis. Since Android applications are often fully encrypted and shipped in Dalvik
-bytecode as a single apk file, our implementation first uses
-android-apktool\footnote{\url{http://code.google.com/p/android-apktool/}} to
+into analysis. We implemented the reflection-aware call graph construction
+ algorithm (Section~\ref{sec:cg})
+using WALA's \textit{bypass logic}. Our tool parses the configuration file
+in an Android application and modifies the bytecode to replace all
+reflection calls with object creation instructions.
+Since Android applications are often fully encrypted and shipped in Dalvik
+bytecode as a single apk file, our tool first uses
+android-apktool~\cite{apktool} to
 decrypt the apk file, and then uses the 

### 2012-01-30 trunk/GUIErrorDetector/paper/introduction.tex
update

@@
 amount of time and space managing locks. Whenever the framework calls a method that might
-be implemented in client code (for example, any public or protected method in a public class),
+be implemented in client code (e.g., any public or protected method in a public class),
 the framework must save its state and release all locks so that the client code can grab locks
@@
 Our tool
-can find this error and generate a warning as shown in
+can find this error and generate a report as shown in
 Figure~\ref{fig:report}.
@@
 
-Invalid thread access errors have significantly affect the
+Invalid thread access errors have significantly affected the
 usability of GUIs, but they have not been thoroughly studied in
@@
 invalid thread access error is to replace direct GUI object accessing code 
-with asynchronized message passing, to ensure a GUI object is accessed in
+with (a)synchronized message passing, to ensure a GUI object is accessed in
 the UI thread. For example, to fix the bug in Figure~\ref{fig:androiderror},
@@
 \CodeIn{post} method in class \CodeIn{android.widget.View} is a
-a standard way to send messages to the UI-thread.}, as follows:
+a standard way to send asynchronized messages to the UI-thread.}, as follows:
 
@@
 be capable to find invalid thread errors. However, such an approach is problematic,
-because not every GUI object access needs to be wrapped by a message passing
-method, e.g., methods that are only called from UI-thread can safely
+because not every GUI object access needs to be wrapped by message passing
+method. For example, methods that are only called from UI-thread can safely
 access any GUI object. On the other hand, using asynchronized message passing has no timing
@@
 can not be used in practice: it issued
-an unacceptable number of false positives and redundant warnings.
+an unacceptable number of invalid warnings. %false positives and redundant warnings.
 
@@
 and k-CFA~\cite{kcfa}
-fails to build a sufficiently complete call graph, due to their limitations
+fails to build a good call graph, due to their limitations
 to reason about reflections.  To alleviate this problem,
-we present a method to build reflection-aware call graph, and
+we present an algorithm to build reflection-aware call graph, and
 also compare its usefulness with existing call graph construction algorithms in
@@
 conservative nature, or multiple warnings that actually correspond
-to the same error. To alleviate such limitations, we devise a set
+to the same error. To address such limitations, we devise a set
  of heuristics to filter likely false positives and redundant warnings.
@@
 We instantiated our technique for four popular GUI frameworks namely SWT,
-eclipse plugin environment, Java Swing, and Android. 
+Eclipse plugin environment, Java Swing, and Android. 
 Swing and SWT are unquestionably 
@@
 frameworks adapting the single-thread rule, a specific framework
-may have its own treatment of \textit{UI thread} and \textit{call graph
-entry nodes}. Thus, we must explicitly identify those framework-specific
+may have its own treatment of \textit{UI thread} and \textit{program 
+entry points}. Thus, we must explicitly identify those framework-specific
 parts in our prototype tool implementation.
@@
 We implement an invalid thread error detection tool that supports
-the above four GUI frameworks. Our tool works in a fully-automatic,
-push-button manner, and scales to realistic programs.
-We evaluate our implementation on 10 subjects from four different
-frameworks over 75000 LOC. The experiment results demonstrate
-that: our technique is effective (it found 12 real-world errors
-on all supported frameworks, and produced significantly less
-false positives and redundant warnings than the simple analysis);
+the above four GUI frameworks. Our tool works in a fully-automatic
+ manner, and scales to realistic programs.
+We evaluate our implementation on 9 subjects from four different
+frameworks over 67KLOC with 1.4MLOC of dependent library code.
+The experiment results demonstrate
+that: our technique is effective (it found 11 real-world errors
+from four supported frameworks
+%, and produced significantly less
+%false positives and redundant warnings than the simple analysis
+);
 our reflection-aware call graph construction algorithm is
@@
 multithreaded GUI programs, we propose a reflection-aware
-call graph construction method. (Section~\ref{sec:technique}).
+call graph construction algorithm. (Section~\ref{sec:technique}).
 
@@
 
-\item \textbf{Evaluation.} We performed an experiment on 10 subjects
-from 4 different platforms over 75000 LOC to show the usefulness
+\item \textbf{Evaluation.} We performed an experiment on 9 subjects
+from 4 different platforms over 67000 LOC to show the usefulness
 of the proposed technique (Section~\ref{sec:evaluation}).

### 2012-01-30 trunk/GUIErrorDetector/paper/technique.tex
update

@@
 GUI application. A Java call graph represents calling relationships
-between methods. Specially, each node represents a method and each
+between methods. Specifically, each node represents a method and each
 edge ($f$, $g$) indicates that method $f$ may call method $g$.
@@
 
+The algorithm in Figure~\ref{fig:detectalgorithm} uses BFS to search
+for potential error-revealing paths. Other graph search strategies
+such as Depath-First Search (DFS) or exhaustive path search can also be
+adapted. In our evaluation, we empirically show that BFS
+is more effective than DFS and exhaustive search in finding errors.
+
 Given a sound call graph, our algorithm is sound in that it does not
 miss true positives. We note, however, that computing a sound
-call graph for partial programs such as an Eclipse plugin,
-or in the presence of reflection, is non-trivial. 
-In particular, GUI applications built on some popular frameworks
-often use configuration files and reflection to specify GUI layout
-or extension points.
-Existing call graph construction algorithms suffer from incompleteness
-, imprecision, or both.  To alleviate this problem, 
-we proposed a combined RTA
-and k-CFA call graph construction algorithm in Section~\ref{sec:cg}.
-
-%we augument k-CFA with value set
+call graph 
+%for partial programs such as an Eclipse plugin, or
+in the presence of reflection is non-trivial. 
+In particular, GUI applications built on some popular frameworks like Android
+often use configuration files and reflection to specify GUI layout.
+%or extension points.
+%Existing call graph construction algorithms suffer from incompleteness
+%, imprecision, or both.  
+To alleviate this problem, we proposed a reflection-aware call graph
+construction algorithm in Section~\ref{sec:cg}.
 
@@
 above two limitations, we present a set of heuristics to filter
-highly likely false positives and remove redundant reports, and provide
-annotation support for programmers to specify call relationships for
+highly likely false positives and redundant reports, and provide
+annotation support for users to specify call relationships for
  native methods.
@@
 \STATE queue $\leftarrow$ an empty queue
-\STATE queue.enqueueAll(threadStart.$getAllSuccNodes$())
+\STATE queue.enqueue(threadStart.$getAllSuccNodes$())
 \WHILE{queue.isNotEmpty()}
@@
 \end{CodeOut}
-\label{fig:sampleandroid}
 \caption{Sample GUI application code on the Android platform. The layout
@@
 a Button object by its ID (line 7, the \CodeIn{findViewById} method).}
+\label{fig:sampleandroid}
 \end{figure}
 
-In the context of object-oriened languages wth dynamic dispatch, the
+In an object-oriened language wth dynamic dispatch, the
 crucial step in constructing a call graph is to compute a conservative
@@
 \end{algorithmic}
-\label{fig:cgalgorithm}
 \caption{A reflection-aware call graph construction algorithm. Lines 1
@@
 } 
+\label{fig:cgalgorithm}
 \end{figure}
@@
 
-When using existing call graph algorithms to analyze the code in Figure~\ref{fig:sampleandroid},
-they fail to conclude that variable \CodeIn{button} declared at line 7
+When analyzing the code in Figure~\ref{fig:sampleandroid}, existing call graph algorithms
+fail to conclude that variable \CodeIn{button} declared at line 7
 point to a \CodeIn{Button} object due to its limitation in deal with the
-reflection call \CodeIn{findViewById}. Thus, the resulting
+reflection call \CodeIn{findViewById}. As a result, the built 
 call graph will miss the calling edge corresponding to the method
@@
 
-To alleviate this limitation, we present an algorithm to construct
+To address this limitation, we present an algorithm to construct
 a reflection-aware call graph based on simple program transformation.
 The basic idea to replace reflection calls with explicit object
-creation instructions, pretending the corresponding concrete object
+creation instructions, pretending that the corresponding concrete object
 has been created.  The algorithm is shown in Figure~\ref{fig:cgalgorithm}.
@@
 to construct the graph on the transformed program. Lines 1 - 7 show
-the transformation step. The algorithm iterates through every statement
+the first step of program transformation. The algorithm iterates through every statement
 in an analyzed program. When it sees a reflection call statement (e.g.,
@@
 After that, the algorithm creates a new instruction which non-deterministically
-returns a new object of the class set. The reflection-aware call graph
-construction algorithm is independent of the underlying call graph algorithm;
-any existing algorithm can be used to construct the resulting graph at line 8.
+returns a new object from the class set. Line 8 is the second step
+to build a call graph on the transformed program.  In this step,
+any existing call graph construction algorithms can be used.
+%construction algorithm is independent of the underlying call graph algorithm;
+%any existing algorithm can be used to construct the resulting graph at line 8.
 
@@
 value is mapped to a \CodeIn{Button} instance declaration. Then it
-replaces the \CodeIn{findViewById(R.id.button\_id)} method call 
-with an explicit object creation instruction \CodeIn{new Button}.
+replaces the reflection call: \CodeIn{findViewById(R.id.button\_id)} 
+with an explicit object creation call: \CodeIn{new Button()}.
 After that, the algorithm employs existing call graph construction
@@
 critical to detect bugs on realistic GUI applications.
-As demonstrated in our experiments, errors in all Android applications
+As demonstrated in our experiments, errors in some Android applications
 can only be detected using this algorithm.
@@
 \subsubsection{Annotation for Native Methods}
+\label{sec:annotation}
 
@@
 
-Our static analysis will also take the call relationship as indicated by this
+Our static analysis  takes the call relationship specified by this
 annotation into consideration when traversing the call graph. In our experiment,
@@
  that have the same error cause (i.e., redundant warnings). We devise
-5 heuristics below to remove likely false positives and redundant warnings.
+5 heuristic filters below to remove likely false positives and redundant warnings.
 The first two are for eliminating false positives, while the
@@
 
-\begin{enumerate}
+%\begin{enumerate}
 
-\item \textbf{Filter Reports Containing Library Calls}. A
+%\item
+\textbf{1. Filter Reports Containing Library Calls}. A
 method call chain involving normal library calls
@@
 
-\item \textbf{Filter Reports With User-Annotated Methods}. Besides general
+%\item
+\textbf{2. Filter Reports With User-Annotated Methods}. Besides general
 library calls, users are also permitted
@@
 
-\item \textbf{Filter Lexically Redundant Reports}. One reported method call
+%\item
+\textbf{3. Filter Lexically Redundant Reports}. One reported method call
 chain can lexically subsume another one. For example, suppose that two
@@
 
-\item \textbf{Filter Report With the Same $k$ Head Methods}. A method can call
+%\item
+\textbf{4. Filter Report With the Same $k$ Head Methods}. A method can call
 multiple methods that access GUI objects, such as:
@@
 
-\item \textbf{Filter Report With the Same $k$ Tail Methods}. A method
+%\item
+\textbf{5. Filter Report With the Same $k$ Tail Methods}. A method
 can have multiple callers, so that method call chains with the same tail are likely
@@
 
-\end{enumerate}
+%\end{enumerate}
+\vspace{1mm}
 
@@
 that it may filter real bugs. However, as we will show in
-our experiments, these filters work remarkably well in
-reducing the number of false positives and redundant reports in practice.
+our experiments, these filters work remarkably well in practice.
 
@@
 %on which it is implemented.
-Like a normal Java application, a SWT desktop application
+Like a normal Java program, a SWT desktop application
 has a single main method as the entry point. By default,
-the main method launches the UI thread when initializing the GUI.
-We instantiate our technique for SWT applications as follows:
+the main method is executed in the UI thread after the GUI
+is initialized. We instantiate our technique for SWT applications as follows:
 
@@
 %An eclipse plugin is an open program. 
-Unlike a SWT desktop application, an Eclipse plugin does not
+An Eclipse plugin is built on top of the SWT framework.
+However, unlike a SWT desktop application, an Eclipse plugin does not
 have a main method as a single program entry point. Instead, it extends
@@
 \item \textbf{Call graph entry nodes: } all overridden SWT
-GUI event handling methods\footnote{Eclipse plugin is built
-on top of the SWT framework} are called from the UI thread.
+GUI event handling methods are called from the UI thread.
 We treat these callback methods as the entry nodes.
@@
 
-\item \textbf{UI-accessing nodes:} as stated in Swing's documentation, methods
-in Swing GUI classes are not thread safe with three exceptions (\CodeIn{repaint()},
+\item \textbf{UI-accessing nodes:} %as stated in Swing's documentation,
+methods in Swing GUI classes are not thread safe with three exceptions (\CodeIn{repaint()},
 \CodeIn{revalidate()}, and \CodeIn{invalidate()}). Thus, we
-treat all methods defined in each GUI class as UI-accessing nodes.
+treat nodes corresponding to those thread unsafe methods %in each GUI class
+as UI-accessing nodes.
 
 \item \textbf{Safe methods: }  Swing provides two helper methods
-(\CodeIn{SwingUti-\\lities.invokeLater} and \CodeIn{SwingUtilities.invokeAndWait}) to pass messages to the UI thread.
+(\CodeIn{SwingUti-\\lities.invokeLater} and \CodeIn{SwingUtilities.invokeAndWait}) to execute code in the UI thread.
 We treat these two methods as safe methods.
@@
 an \CodeIn{Activity} object is created and manipulated by the UI thread. We treat
-all public methods from an \CodeIn{Activity} class as call graph entry nodes. Additionally,
-we also add all overridden callback methods in event listener classes as entry nodes.
+all public methods from an \CodeIn{Activity} class as call graph entry nodes.
+We also add all overridden callback methods in event listener classes as entry nodes.
 
@@
 and \CodeIn{View.postDelay}) to execute code on the UI thread. Thus, we treat
-these two methods as safe methods, since invoking them on any thread
-would not cause an invalid thread access error.
+these two methods as safe methods.
+%, since invoking them on any thread
+%would not cause an invalid thread access error.
  %Invoking these two methods are generally considered to be safe, and would not

### 2012-01-30 GUIErrorDetector/paper/abstract.tex
update

@@
 platforms: SWT, Eclipse plugin development framework, Java Swing, and
-Android. In an evaluation on 9 subjects over 75000 LOC, our technique
+Android. In an evaluation on 9 subjects over 67000 LOC, our technique
 found a number of real-world errors, suggesting its effectiveness

### 2012-01-30 GUIErrorDetector/paper/conclusion.tex
update

@@
 whether a non-UI thread can access a GUI object.
-It uses a combined RTA and k-CFA algorithm to construct
-a good call graph, and employs a set of heuristics to
+It uses a reflection-aware call graph construction algorithm
+to build a good call graph, and employs a set of heuristics to
 filter likely false positives and redundant reports.
@@
 
-We have demonstrated that our technique can be both practical and useful
-by an evaluation on 10 subjects acrosss 4 popular GUI
-frameworks. Our experiments have shown that we can find bugs
-in real-world programs.
+We have demonstrated that our technique can be useful
+by an evaluation on 9 subjects acrosss 4 popular GUI
+frameworks. 
+%Our experiments have shown that we can find bugs
+%in real-world programs.
 
@@
 positives is to integrate the current static analysis with
-dynamic analyses~\cite{Jiang:2008:PPS:1453101.1453110, ZhangSBE2011}
+dynamic analyses~\cite{Jiang:2008:PPS:1453101.1453110}%, ZhangSBE2011}
 or symbolic analyses~\cite{xie05:symstra, Pasareanu:2011, halfond09issta, BMF97}
@@
 way to improve software quality.  Although many
-GUI testing techniques have been developed recently, few of them can be applied
+testing techniques have been developed recently, few of them can be applied
 to unit test multithreaded GUI programs to find potential errors \textit{earlier}. We
-are interested to investigate how to apply recent advance in automated
-software testing~\cite{Staats:2011:PTO:1985793.1985847, Jagannath:2011:IMU:2025113.2025145, Muccini_Bertolino_Inverardi_2004, Ricca:2001:ATW:381473.381476, Harman:2007}
+are interested in investigating how to apply recent advance in automated
+testing~\cite{Staats:2011:PTO:1985793.1985847, Jagannath:2011:IMU:2025113.2025145, Muccini_Bertolino_Inverardi_2004, Ricca:2001:ATW:381473.381476, Harman:2007}
 to the context of multithreaded GUI applications.
@@
 %\item
-\textbf{Fixing potential GUI errors.} After a potential error is revealed, fixing
+\textbf{Fixing potential GUI errors.} After an error is revealed, fixing
 it and verifing the patch has often been another important and time-consuming process. Fixing concurrency

### 2012-01-30 GUIErrorDetector/paper/evaluation.tex
update

@@
 four supported frameworks (Section~\ref{sec:errors}). We also compare our technique with
-a straightfoward approach in Section~\ref{sec:straightforward}. We further compare the reflection-aware call graph
-construction algorithms with existing algorithms, showing its usefulness (Section~\ref{sec:reflectionaware}).
+a straightfoward approach in Section~\ref{sec:straightforward},  compare the reflection-aware call graph
+construction algorithms with existing algorithms (Section~\ref{sec:reflectionaware}), and
+evaluate different graph search strategies in error detection (Section~\ref{sec:search}).
  Finally, we show that the set of proposed heuristics are effective
@@
 \label{sec:subjects}
+
+%library code: 1.4 million
 
@@
 \begin{itemize}
-\Item CelerFTP~\cite{celer} and FileBunker~\cite{filebunker} are two useful
-SWT desktop applications.
-CelerFTP implements a simple FTP client based on Java and SWT UI library, and
-FileBunker is a file backup application which uses one or more GMail accounts as its backup repository.
+\Item \textbf{SWT desktop applications.}
+%VirgoFTP~\cite{virgo} and FileBunker~\cite{filebunker} are two useful SWT desktop applications.
+VirgoFTP~\cite{virgo} implements a simple FTP client based on Java and SWT UI library, and
+FileBunker~\cite{filebunker} is a file backup application which uses one or more GMail accounts as its backup repository.
 
-\Item  AnyEdit~\cite{anyedit}, FileSync~\cite{filesync}, and
-EclipseRunner~\cite{eclipserunner} are three popular eclipse plugins.
-AnyEdit adds several new tools to  Eclipse editors, output consoles, and main menu. 
-FileSync is a file synchronisation tool to keep files outside of Eclipse projects in synchronized
-with Eclipse project files. EclipseRunner extends capability of running launch configurations in Eclipse IDE.
+\Item \textbf{Eclipse plugins.}
+HudsonEclipse~\cite{hudson} adds several new tools to  monitor Hudson build status from Eclipse.
+EclipseRunner~\cite{eclipserunner} extends capability of running launch configurations in Eclipse IDE.
 
-\Item  S3dropbox~\cite{s3dropbox} and SudokuPuzzleSolver~\cite{sudokusolver}
-are two Swing desktop applications. S3dropbox implements a client that allows users
-to drag and drop files, which are then uploaded to their Amazon S3 accounts. SodokuPuzzleSolver
+\Item \textbf{Swing applications.} %S3dropbox~\cite{s3dropbox} and SudokuSolver~\cite{sudokusolver} are two Swing desktop applications.
+S3dropbox~\cite{s3dropbox} implements a client that allows users
+to drag and drop files, which are then uploaded to their Amazon S3 accounts. SodokuSolver~\cite{sudokusolver}
 computes Sodoku solutions efficiently using mutlithreading execution.
 
-\Item  MyTracks~\cite{mytracks}, Fennec~\cite{fennec},
-and SGTPuzzles~\cite{sgtpuzzles} are three Android applications.
-MyTracks, developed by Google, records users' GPS tracks in outdoor activities, and provides
-interfaces to visualize them on Google Maps. Fennec, developed by Mozilla, is the Mozilla
-Firefox web browser for mobile devices. SGTPuzzles is a small logic single-player game.
+\Item  \textbf{Android applications.} %MyTracks~\cite{mytracks}, Fennec~\cite{fennec}, and SGTPuzzles~\cite{sgtpuzzles} are three Android applications.
+MyTracks~\cite{mytracks}, developed by Google, records users' GPS tracks in outdoor activities, and provides
+interfaces to visualize them on Google Maps. Fennec~\cite{fennec}, developed by Mozilla, is the Mozilla
+Firefox web browser for mobile devices. SGTPuzzles~\cite{sgtpuzzles} is a small logic single-player game.
 
@@
 \hspace*{-0.2cm}
+\setlength{\tabcolsep}{.70\tabcolsep}
 \begin{tabular}{|p{4.4cm}||c|c|c|c|}
@@
 \hline
+\hline
+ Total &  64215 &  554 &  4702 \\
+\hline
 \multicolumn{4}{l}{}   \\
@@
 \hline \hline
- SWT (3.6.2)&  xxxxx &  xxx &  xxxx  \\
+ SWT (3.6)&  129942 &  999 &  9643 \\
 \hline
- Eclipse plugin development (3.6.2)&  xxxxx &  xxx &  xxxx  \\
+ Eclipse plugin development (3.6.2)&  460830 &  6630 &  37183 \\
 \hline
-Swing (1.6)&  xxxxx &  xxx &  xxxx  \\
+Swing (1.6)&  167961 &  878 &  13159 \\
 \hline
- Android (3.6)&  xxxxx &  xxx &  xxxx  \\
+ Android (3.2)&  683289 &  5085 &  10584 \\
+\hline
+\hline
+ Total &  1442022 &  13592 &  70569\\
 \hline
@@
 algorithms: RTA~\cite{rta}, 0-CFA, and 1-CFA~\cite{kcfa}.  When running
-each call graph construction algorithm on Android applications, we
-use two configurations: with and without the reflection-aware transformation
-(Section~\ref{sec:cg}).  We did not use more expensive algorithms like $k$-CFA ($k >$ 1),
+each call graph construction algorithm on three Android applications, we
+use two configurations: with and without the reflection-aware algorithm 
+(Section~\ref{sec:cg}).  We did not use other expensive algorithms like $k$-CFA ($k >$ 1),
 because they can not scale to large programs.
@@
 We found SGTPuzzler is the only subject that uses native methods to interact with
-underlying operating systems. Thus, we manually added XXX \CodeIn{@CalledByNative}
-annotations for it. Also two subjects XXXX and XXX employ a self-defined
-way to interact with the GUI framework. For example, the \CodeIn{safeInvokeXX}
-method in the XXX subject first checks whether the current thread is the UI-thread, and
-then determines whether to direct access a GUI object or wrap the code with
-message passing. We add XX heuristic filtering rules for those methods, to indicate
-that they are safe to be invoked from any thread. In this experiment, none of the paper
+underlying operating systems. Thus, we manually added 3 \CodeIn{@CalledByNative}
+annotations for it. Also two subjects MyTracks and Fennec employ a self-defined
+way to interact with the GUI framework. For example, in MyTracks, all non-UI
+threads are initialized via using the library method \CodeIn{android.os.handler.handleCallback}.
+% the \CodeIn{safeInvokeXX}
+%method in the XXX subject first checks whether the current thread is the UI-thread, and
+%then determines whether to direct access a GUI object or wrap the code with
+%message passing. 
+Thus, we add 5 user-defined heuristic filters for these two subjects.%to indicate
+%that they are safe to be invoked from any thread. 
+In this experiment, none of the paper
 authors was familar with the subjects; but we found it is quite easy
-to add extra those annotations and heuristic filters and finished these
-manual parts in less than 20 minutes.
+to add extra annotations and heuristic filters. All these
+manual parts are finished in less than 60 minutes.
 
@@
 warning, we manually determine its validity by either searching the
-bug repository to check whether the same bug has been reported before,
+bug repository to check whether the same error has been reported before,
 or submitting a new bug report, or writing a test driver to reproduce
@@
 \hspace*{-0.2cm}
-\setlength{\tabcolsep}{.65\tabcolsep}
+\setlength{\tabcolsep}{.35\tabcolsep}
 \begin{tabular}{|l||c|c|c||c|c|c||c|c|c||c|c|}
@@
  \hline
- xxx &  xxxx / xxxx &  xx / xxxx &  xxx / xxxx & xx /xxx & xx / xxxx  & xx / xxxx& xx / xxx & xxxx / xxx  & xxxx / xxx& xx & xx \\
+ SGTPuzzler & 13631 / 13865&  12 / 16 &  0 / 0 & 9546 / 9682& 4 / 4& 1 / 1 & 35198 / 35756 & 1 / 1  & 1 / 1& 104 & 1 \\
  \hline
- xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx& xx & xx \\
+ Fennec & 14058 / 14387 &  1 / 1 &  0 / 0 & 8263 / 8898 & 1 / 1 & 0 / 0& 29125/ 31759 & 3 / 3 & 1 / 1& 433 & 1 \\
  \hline
- xxx &  xxxx &  xx &  xxx & xx & xx & xx& xx & xx & xx& xx & xx \\
+ MyTracks & 24036 / 24036 &  161 / 220 & 0 / 0 & 10803 / 13645 & 119 / 119 & 0 / 0 & 39235 / 110977 & 1 / 1 & 0 / 1 & 1192 & 1 \\
+\hline
+\hline
+ Total & 178279 / 178842 &  188 / 251 & 6 / 6 & 129744 / 133357 & 137 / 137& 7 / 7 & 461423 / 536358& 21 / 21 & 10 / 11 & 3521 & 11 \\
 \hline
@@
 \vspace{-15pt}
-\Caption{{\label{table:results}Experimental results in finding errors
+\Caption{{\label{table:results}Experimental results in finding invalid thread access errors
 in multithreaded GUI programs. Column ``CG Size'' shows the
@@
 call graph construction algorithms with (before ``/'') or without (after ``/'')
-taming the reflection on Android applications. In each cell of the table
+using the reflection-aware algorithm on Android applications. In each cell of the table
 for Android applications, a slash ``/'' separates the result of
 using normal call graph construction algorithm and the reflection-aware
-call graph construction algorithm. As a comparison, the
+call graph construction algorithm. The 6 errors found in VirgoFTP, FileBunker,
+S3dropbox, and SudokuSolver are previously  unknown. As a comparison, the
 results of a straightforward approach (Section~\ref{sec:straightforward}) are show at the far right.} }
@@
 on the subject programs. From these results, we can see our
-tool found real errors from each subject on all the 
+tool found real errors from each subject on  four
 supported GUI frameworks. The results vary slightly according
 to the specific call graph algorithm used. In general, using
-the 1-CFA algorithm finds most errors (XXX in total) with least
-warnings (XXX in total). The tradeoffs of using other
+the 1-CFA algorithm finds most errors (11 in total) and least
+warnings (21 in total). The tradeoffs of using other
 algorithms will be explained in Section~\ref{sec:reflectionaware}.
@@
 We further examined the detailed results for each subject.
-Among xxx warnings issued by using the 1-CFA algorithm, xxx
-are false positives, xxx are redundant:
-they have the same causes as the rest xxx warnings. (XXX why there
-are FP and redundant warnings?)
+Among the 21 warnings issued by using the 1-CFA algorithm, 2
+are false positives, and 8 are redundant:
+they have the same causes as the rest 11 warnings.
+
+%The primary
+%reason for the false positive is because the precision of call graph,
+%while the reason for redundant warnings is because multiple
+%methods ca
+%Even a context-sensitive call graph construction algorithm is used,
+
+%why finds a bug in SGTPuzzle, because the \CodeIn{SmallKeyBoard} has been
+%explicitly created in this main class \CodeIn{SGTPuzzles} \CodeIn{setKeyboardVisibility},
+%thus, even without reflection-aware
 
@@
 \end{CodeOut}
-\vspace*{-2.0ex} \Caption{{\label{fig:swingerror} A
-potential invalid thread access error reported by our tool
+\vspace*{-2.0ex} \Caption{{\label{fig:swingerror} An
+invalid thread access error reported by our tool
 in the S3dropbox Swing application. The error occurs when
 the method \CodeIn{deleteCurrentBucket} invoked at line 63 throws
-an exception, which leads method \CodeIn{deleteError} to
+an exception, which causes method \CodeIn{deleteError} to
 access a Swing GUI object \CodeIn{display} at line 79 from
@@
 two real errors our tool has found. Figure~\ref{fig:swingerror}
-shows a potential invalid thread access error in the S3dropbox
+shows an invalid thread access error in the S3dropbox
 program. This error happens when the \CodeIn{deterCurrentBucket}
@@
 Another reason of missing this violation is because some GUI frameworks like Swing
-do not provide any run-time checks for invalid thread access. Most
+do not provide any run-time checks for invalid thread accesses. Most
 of the time, programmers can get away with an apparently ``well behaved'' Swing
@@
 \end{CodeOut}
-\vspace*{-2.0ex} \Caption{{\label{fig:pluginerror} A
-potential invalid thread access error reported by our tool
+\vspace*{-2.0ex} \Caption{{\label{fig:pluginerror} An
+invalid thread access error reported by our tool
 for the EclipseRunner plugin. In Eclipse, the
@@
 happens. However, the \CodeIn{refresh} method directly accesses
-GUI objects (refresh the view at line 415) without any
+GUI objects (to refresh the view at line 415) without any
 protection and thus triggers the error.
@@
 , the \CodeIn{refresh} method has been
-called by XXX different methods in non-UI threads. Thus, our
-tool issues XXX separate warnings for each caller method to indicate
-different ways to trigger this error, despite that all these xxx warnings
+called by 6 different methods in non-UI threads. Thus, our
+tool issues 6 separate warnings for each caller method to indicate
+different ways to trigger this error, despite that all the 6 warnings
 acutally have the same error cause.
@@
 
-As we mentioned in Section~\ref{sec:finding}, a standard way to avoid
+As briefly mentioned in Section~\ref{sec:finding}, one way to avoid
 invalid thread access errors is to wrap every GUI access code
@@
 We implemented this straightforward approach and experimentally compared it
-with the technique presented in Section~\ref{sec:technique}.
+with our technique.% presented in Section~\ref{sec:technique}.
 The far right column in Table~\ref{table:results} shows the results.
-The results show that this straightforward approach can identified every
-error as our technique does, but leads to a tremendous number of false
+The results show that this straightforward approach can identify every
+error that our technique has found, but issue a huge number of false
 positives and redundant warnings. The primary reason is that this simple approach
@@
 classifies GUI accessing code which will never be executed
-in a non-UI thread as errenous. Furthermore, our technique
-outputs a method call chain in the error report, which can help
+in a non-UI thread as erroneous. Furthermore, our technique
+outputs a method call chain in each reported error, which can help
 developers understand how an invalid thread access error is triggered.
@@
 We next compare three call graph construction algorithms (RTA, 0-CFA, and 1-CFA)
-used in our experiments. As shown in Table~\ref{table:results},  XXX found
-more errors with less warnings than the XXX and XXXX algorithms. This
-is because RTA and 0-CFA do not consider the context XXX, and it may
-mix the same methods called by different callers. Although the call graphs
-built by 1-CFA are significantly larger, XXX, the algorithm still runs
-in a practical amouont of time. For example,
-our tool finished building the call graph for the largest subject (xxx)
-within xxx minutes.
+used in our experiments. As shown in Table~\ref{table:results},  1-CFA found
+more errors with less warnings than the other two algorithms. This
+is because RTA and 0-CFA do not consider the calling context when
+constructing a call graph, and it may
+mix the same method calls by different callers into a single node, and
+then introduce imprecision.
+
+%Although the call graphs
+%built by 1-CFA are significantly larger, XXX, the algorithm still runs
+%in a practical amouont of time. For example,
+%our tool finished building the call graph for the largest subject (xxx)
+%within xxx minutes.
 
 The results in Table~\ref{table:results} also show that using a reflection-aware
-call graph construction algorithm is critical in finding errors in Android
-applications. None of the errors from the Android applications
-can be found by using normal call graph construction algorithms, due to
-their limitation in handling platform-specific reflections. Without
-replacing the reflection calls with explicit object creation instructions,
-a call graph construction algorithm will
-conclude that no GUI object has been created, and thus miss many UI-related
-edges in the resulting graph.
+call graph construction algorithm is useful in finding errors in Android
+applications. One error from the MyTracks Android application
+can only be found by using the reflection-aware call graph construction algorithm.
+This is because the error-related GUI object (\CodeIn{msgTextView}) in MyTracks is created
+reflectively as follows.
+
+\begin{CodeOut}
+\begin{alltt}
+/*In class: com.google.android.apps.mytracks.StatsUtilities*/
+97.  public void setLatLong(int id, double d) \{
+98.     TextView msgTextView = (TextView) activity.\textbf{findViewById}(id);
+99.     msgTextView.setText(LAT\_LONG\_FORMAT.format(d));
+100.\}
+\end{alltt}
+\end{CodeOut}
+
+In constrast, the error-related GUI objects in the other two Android applications (Fennec
+and SGTPuzzler) are created explicitly, so that a normal call graph construction
+algorithm can create a sufficiently complete call graph.
+
+%Without
+%replacing the reflection calls with explicit object creation instructions,
+%a call graph construction algorithm will
+%conclude that no GUI object has been created, and thus miss many UI-related
+%edges in the resulting graph.
 
@@
 algorithm is more effective in finding errors, and our reflection-aware call
-graph construction algorithm is critical to find errors on
+graph construction algorithm is critical to find errors on some
 Android applications.
+
+\subsubsection{Comparing Graph Search Strategies}
+\label{sec:search}
+
+Our error detection algorithm in Figure~\ref{fig:detectalgorithm} uses BFS to search potential
+single-thread violations. However, other graph search strategies such as
+Depth-First Search (DFS) and exhaustive path search can also be employed. To
+understand trade-offs between using different search strategies, we 
+implemented two variants of the algorithm in Figure~\ref{fig:detectalgorithm}, and
+evaluated them on the same subjects with the identical environment settings.
+
+The first variant uses DFS by changing line 7 of Figure~\ref{fig:detectalgorithm}
+to \CodeIn{getReachableStartsByDFS(cg)}, changing line 9 of Figure~\ref{fig:detectalgorithm}
+to \CodeIn{queue} $\leftarrow$ \CodeIn{an empty stack}, and changing queue operations
+(\CodeIn{enqueue} and \CodeIn{dequeue}) to the corresponding stack operations (\CodeIn{push} and \CodeIn{pop}).
+This variant missed one error in the FileBunker subject, and found 8 errors
+in total.  That is because DFS searches deeper into the graph, and the path it finds
+may not be the shortest path.
+
+%Hundson: 3, 1
+%EclipseRunner: 6, 1
+%S3dropbox: ? , ?  too many warnings time: 31678 (45528 chains), running out of memory
+%SudokuSolver:  2, 1 too many warnings: 1700, 2090
+%VirgoFTP: 2, 2
+%FileBunker:  2, 0  //very long method calls
+%Fennec: 3, 1
+%SGTPuzzler: 1, 1
+%MyTracks: 1, 1
+
+The second variant uses exhaustive search to find potential errors. This variant
+enumerates all non-cyclic paths from the start nodes, and checks whether each
+path spawns a new thread and accesses GUI object without using safe methods. As
+a result, this variant run out of memory on all subjects. We further checked
+the traversed paths before the algorithm terminated, and found none of the explored
+path revealed a valid error. This is because the number of
+non-cyclic paths in a graph is exponetially large to the graph node number.
+For a realistic call graph which often contains thousands of nodes, it is impossible to enumerate all
+paths in practice.
+
+\vspace{1mm}
+
+\noindent \textbf{\textit{Summary.}} Using BFS finds more errors than DFS and
+exhaustive search in our error detection algorithm.
 
@@
 We measure the effectiveness of the proposed heuristic filters of
-Section~\ref{sec:heuristic} via the number of removed false positives and
+Section~\ref{sec:heuristic} in terms of the number of removed false positives and
 redundant warnings.
 
-Table~\ref{table:filters} tabulates the results. Although
-our static analysis outputs thousands of warnings for each
-subject, the proposed heuristic filters effectively reduces
-the number. On average, they
- reduce the false positive numbers and redundant warnings by up to a factor of
-XXX. Specifically, filters $XX_i$ and $XX_j$  identified xx\% of
-the warnings as likely false positives, and filters $YY_i$
-and $YY_j$ identified YY\% of the warnings as redundant warnings.
+Table~\ref{table:filters} tabulates the results.
+Our static analysis outputs thousands of warnings for the evaluated
+subjects, but the proposed heuristic filters effectively reduces
+the number of likely invalid warnings. On average, five heuristic
+filters remove 99.96\% of the reported warnings as false positives
+or redundant warnings. Specifically, heuristic filters 1 and 2 identified
+32.48\% of the warnings as likely false positives, and filters 3, 4,
+and 5 identified 67.48\% of the warnings as redundant warnings.
 We further manually check each filtered warning, and found no
@@
  \fontsize{9pt}{\baselineskip}\selectfont
-\setlength{\tabcolsep}{.30\tabcolsep}
+\setlength{\tabcolsep}{.81\tabcolsep}
 \hspace*{-0.2cm}
@@
 \multicolumn{7}{|l|}{Eclipse plugins}   \\
+ %\hline
+ %EclipseRunner &  xxxx &  xx &  xxx & xx &  xxx & xx\\
  \hline
- xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
+ EclipseRunner&  1621 &  1487 &  1487 & 1487 &  6 & 6\\
  \hline
- xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
- \hline
- xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
+ HundsonEclipse&  3192 &  2417 &  1696 & 9 &  3 & 3\\
  \hline
@@
  \hline
- xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
+ SGTPuzzler&  2 &  1 &  1 & 1 &  1 & 1\\
  \hline
- xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
+ Fennec &  122 &  84 & 84 & 84 &  9 & 3\\
  \hline
- xxx &  xxxx &  xx &  xxx & xx &  xxx & xx\\
+ MyTracks &  1176 &  441 &  441 & 441 &  63 & 1 \\
+\hline
+ \hline
+ Total &  56214 &  39708 &  37955 &  2678 &  89 & 21 \\
  \hline
@@
 \Caption{{\label{table:filters}Number of warnings after applying a set of
-heuristic filters (Section~\ref{sec:heuristic}). Column ``\#Warning $F_i$''
-represents the number of remaining warnings after applying
-filters 1 -- $i$, and the number of last column is taken
-from Table~\ref{table:results} (Subcolumn ``\#Warning'' under column ``1-CFA / with taming reflection'').} }
+heuristic filters (Section~\ref{sec:heuristic}). Column ``Before Filtering''
+shows the output warning number using the reflection-aware 1-CFA algorithm.
+Column ``\#W $F_i$'' represents the number of remaining warnings after applying
+filters 1 -- $i$. Numbers in last column are taken
+from Table~\ref{table:results}.
+Results of using other algorithms show similar patterns, which are omitted for brevity.} }
 \end{table}
@@
 
-We next discuss several important issues in our evaluation.
-
-\subsubsection{Performance and Scalability}
-
-Our tool runs in a practical amount of time. Our evaluations
+\noindent \textbf{\textit{Performance and scalability.}} Our tool
+has been evaluated on 9 subjects with over 67 KLOC and dependent
+libraries with over 1.4 MLOC, showing good scalability.
+For each subject program, it runs in a practical amount of time. Our evaluations
 were conducted on a 2.67GHz Intel Core PC with 4GB
 physical memory (1GB is allocated for JVM), running Fedora 16.
-For the largest subject, xxx, our tool finished the whole analysis
-within 286 seconds using the most expensive call graph construction
-algorithm (the reflection-aware 1-CFA analysis). Analyzing
+For the most time-consuming subject, MyTracks, our tool finished the whole analysis
+within 686 seconds using the most expensive call graph construction
+algorithm: the reflection-aware 1-CFA algorithm. Analyzing
 other subjects using different algorithms took less time.
@@
 
-Our experiments also demonstrate that our approach has good scalability.
-Together with all dependent library code, our tool has analyzed
-XXX LOC in total  XXX LOC in the largest program.
+%Our experiments also demonstrate that our approach has good scalability.
+%Together with all dependent library code, our tool has analyzed
+%XXX LOC in total  xxx the largest program.
 %Our tool has analyzed xxx LOC in total, and together with all dependent libraries,
@@
 
-\subsubsection{Threats to Validity}
+\vspace{1mm}
 
+\noindent \textbf{\textit{Threats to validity.}}
 There are two threats to validity in our evaluation. 
@@
 well-known call graph construction algorithms (i.e., RTA, 0-CFA, and 1-CFA) 
-in our implementation. It is still unknown whether using other 
-call graph construction algorithms such as XTA~\cite{xta} may achieve better results.
+in our evaluation. It is still unknown whether using other 
+call graph construction algorithms such as XTA~\cite{xta} or
+an incremental algorithm~\cite{inccg} may achieve better results.
 
-\subsubsection{Limitations}
+\vspace{1mm}
 
+\noindent \textbf{\textit{Limitations.}}
 Our technique is limited in two aspects. First, it only considers
@@
 to remedy this limitation is to design an analysis to identify
-those threads created before a GUI is launched.
+those non-UI threads created before a GUI is launched.
 Second, our tool cannot compute call relationships
@@
 
-\subsubsection{Experimental Conclusions}
+\vspace{1mm}
 
-Invalid thread access errors significantly affect the usability of
-a GUI application, but can be subtle to find. In practice, programmers
-have designed practices and patterns to avoid such errors in the first
-place, but can easily overlook corner cases like exception-handling
-methods.
+\noindent \textbf{\textit{Experimental Conclusions.}}
+Invalid thread access errors  can be subtle to detect in many cases.
+The technique presented in this paper offers a promising solution.
+Our technique finds real-world errors, and issues
+%Compared with the straightforward approach to check every
+%GUI accessing code isolatedly, our technique produces
+significantly less warnings when compared to a straightforward
+approach. In addition, the reflection-aware call graph construction algorithm
+is critical in detecting errors on Android applications, and our
+proposed heuristic filtering rules are useful to reduce invalid warnings.
 
-The technique presented in this paper offers a promising solution.
-Compared with the straightforward approach to check every
-GUI accessing code isolatedly, our technique produces significantly
-less warnings. The reflection-aware call graph construction algorithm
-is critical in detecting errors for Android programs, and our
-proposed heuristic filtering rules are useful in reducing programmers'
-burden to inspect the output result.
+%in reducing programmers'
+%burden to inspect the output result.
+
+%In practice, programmers
+%have designed practices and patterns to avoid such errors in the first
+%place, but can easily overlook corner cases like exception-handling
+%methods.
 

### 2012-01-30 GUIErrorDetector/paper/related.tex
update

@@
 some aspect(s) of GUI testing including model creation
-(for model-based testing)~\cite{androidtesting, Xie:2006:MTC:1172962.1172990},
+(for model-based testing)~\cite{androidtesting}, %, Xie:2006:MTC:1172962.1172990},
 test-case generation~\cite{YuanCohenMemonTSE2011, YuanMemonICSE2007},
@@
 For example,
-Kervinen et al.~\cite{Kervinen06model-basedtesting} present a formal model and architecture for testing
-concurrently running applications. The behavior of the system under test
-needs to be specified manually as a labeled transition system. 
-Guitar~\cite{YuanCohenMemonTSE2011, YuanMemonICSE2007, Xie:2006:MTC:1172962.1172990}
+%Kervinen et al.~\cite{Kervinen06model-basedtesting} present a formal model and architecture for testing
+%concurrently running applications. The behavior of the system under test
+%needs to be specified manually as a labeled transition system. 
+Guitar~\cite{YuanCohenMemonTSE2011, YuanMemonICSE2007}%, Xie:2006:MTC:1172962.1172990}
 is a GUI testing framework for Java and Microsoft Windows applications. 
@@
 result in a large number of
-test inputs requiring substantile human effort.
-The second
-problem is to determine the coverage of a set of test
-cases~\cite{MemonFSE2001}. For conventional software, coverage is measured
-using the amount and type of underlying code exercised.
-These measures do not work well for GUI testing, because
-what matters is not only how much of the code is tested,
-but in how many different possible states of the software
-each piece of code is tested. This makes it hard to determine
-the completeness of a test suite. 
+test inputs requiring substantile human effort, and then makes
+testing fail to detect many potential errors.
+%The second problem is to determine the coverage of a set of test
+%cases~\cite{MemonFSE2001}. For conventional software, coverage is measured
+%using the amount and type of underlying code exercised.
+%These measures do not work well for GUI testing, because
+%what matters is not only how much of the code is tested,
+%but in how many different possible states of the software
+%each piece of code is tested. This makes it hard to determine
+%the completeness of a test suite. 
 In contrast, as advocated in this paper, the primary advantage of
@@
 errors, and uses a quite different abstraction than ours.
-To the best of our knowledge, we are the first to identify the invalid
+To the best of our knowledge, we are the first to address the invalid
 thread access problem on multithreaded GUI applications, and
-our technique is a general one that is specifically designed to detect
-the invalid thread access errors.
+our technique is a general one that can be easily tailored for
+different GUI frameworks.
+
+%is specifically designed to detect
+%the invalid thread access errors.
 
@@
 A rich body of techniques have been developed to detect bugs in multithreaded programs~\cite{Huang:2011:PPC:2001420.2001438, Weeratunge:2010, Huang:2011:EST}.
-Active testing frameworks like AssertFuzzer~\cite{Sen:2008} uses the trace information to detect
-and create atomicity schedule violations. Static analysis tools such as Chord~\cite{Naik:2006}
+%Active testing frameworks like AssertFuzzer~\cite{Sen:2008} uses the trace information to detect
+%and create atomicity schedule violations.
+Static analysis tools such as Chord~\cite{Naik:2006}
  explore multithreaded bugs by statically analyzing the program. On the
 other hand, runtime analysis tools such as Eraser~\cite{Savage:1997}  dynamically detect concurrency bugs using the lockset
-algorithms or some criteria based automata. Bodden and Havelund~\cite{Bodden:2008} uses AOP for
-race detection by providing three novel pointcuts to the AspectJ language. More recently,
-Goldilock~\cite{Elmas:2007} uses the hybrid model that combines the happens-before and lock-based
+algorithms or some criteria based automata. 
+%Bodden and Havelund~\cite{Bodden:2008} uses AOP for
+%race detection by providing three novel pointcuts to the AspectJ language.
+More recently, Goldilock~\cite{Elmas:2007} uses the hybrid model that combines the happens-before and lock-based
 approaches to identify data races based on an execution. By exploiting the insight
@@
 CHESS~\cite{chess} dynamically explores the thread scheduling decisions to expose
-concurrency bugs using a context-bounded approach. Shacham et al~\cite{Shacham:2007} uses
-a model checker to construct the witness for data races reported by the lockset algorithm.
+concurrency bugs using a context-bounded approach. 
+%Shacham et al~\cite{Shacham:2007} uses
+%a model checker to construct the witness for data races reported by the lockset algorithm.
 Unfortunately, due to the exponential size of the search space,
@@
 we are not aware of any software model checking approach can scale to the subjects
-as large as those used in our experiments. Compared with model checking, the static analysis
+as large as those used in our experiments (including the dependent library code). Compared with model checking, the static analysis
 algorithm presented in this paper chooses call graph as the

### 2012-01-30 trunk/GUIErrorDetector/paper/abstract.tex
significant revise based on mike's comments

@@
 thread spawning as the sources and GUI object accessing as the sinks. 
-Heavy use of reflection in modern GUI applications makes existing
-call graph construction algorithms fail to build a good
-call graph. Thus, we present a method to overcome the limitations, and
-build reflection-aware call graphs.
+Existing call graph construction algorithms fail to build a good
+call graph for modern GUI applications, because of heavy use of reflection.
+Thus, we present a method to build reflection-aware call graphs.
 
@@
 
-We implemented our technique and instantiated it on four popular GUI
-platforms: SWT, Eclipse plugin development framework, Java Swing, and
-Android. In an evaluation on XX subjects over XXX LOC, our technique
-found a number of real-world errors, suggesting its effectiveness
-and showing good scalability.
+We implemented our technique and instantiated it for four popular GUI
+platforms: SWT, the Eclipse plugin development framework, Swing, and
+Android. In an evaluation on 9 programs comprising 67000 LOC, our technique
+found both previously-known and unknown errors.
+
+%a number of real-world errors, suggesting its effectiveness
+%and showing good scalability.
 

### 2012-01-30 trunk/GUIErrorDetector/paper/evaluation.tex
significant revise based on mike's comments

--- 2012-01-26 trunk/GUIErrorDetector/paper/evaluation.tex
@@
 \begin{itemize}
-\Item VirgoFTP~\cite{virgo} and FileBunker~\cite{filebunker} are two useful
-SWT desktop applications.
-VirgoFTP implements a simple FTP client based on Java and SWT UI library, and
-FileBunker is a file backup application which uses one or more GMail accounts as its backup repository.
+\Item \textbf{SWT desktop applications.}
+%VirgoFTP~\cite{virgo} and FileBunker~\cite{filebunker} are two useful SWT desktop applications.
+VirgoFTP~\cite{virgo} implements a simple FTP client based on Java and SWT UI library, and
+FileBunker~\cite{filebunker} is a file backup application which uses one or more GMail accounts as its backup repository.
 
-\Item  HudsonEclipse~\cite{hudson}, and
-EclipseRunner~\cite{eclipserunner} are two popular eclipse plugins.
-HudsonEclipse adds several new tools to  monitor Hudson build status from Eclipse.
-EclipseRunner extends capability of running launch configurations in Eclipse IDE.
+\Item \textbf{Eclipse plugins.}
+HudsonEclipse~\cite{hudson} adds several new tools to  monitor Hudson build status from Eclipse.
+EclipseRunner~\cite{eclipserunner} extends capability of running launch configurations in Eclipse IDE.
 
-\Item  S3dropbox~\cite{s3dropbox} and SudokuSolver~\cite{sudokusolver}
-are two Swing desktop applications. S3dropbox implements a client that allows users
-to drag and drop files, which are then uploaded to their Amazon S3 accounts. SodokuSolver
+\Item \textbf{Swing applications.} %S3dropbox~\cite{s3dropbox} and SudokuSolver~\cite{sudokusolver} are two Swing desktop applications.
+S3dropbox~\cite{s3dropbox} implements a client that allows users
+to drag and drop files, which are then uploaded to their Amazon S3 accounts. SodokuSolver~\cite{sudokusolver}
 computes Sodoku solutions efficiently using mutlithreading execution.
 
-\Item  MyTracks~\cite{mytracks}, Fennec~\cite{fennec},
-and SGTPuzzles~\cite{sgtpuzzles} are three Android applications.
-MyTracks, developed by Google, records users' GPS tracks in outdoor activities, and provides
-interfaces to visualize them on Google Maps. Fennec, developed by Mozilla, is the Mozilla
-Firefox web browser for mobile devices. SGTPuzzles is a small logic single-player game.
+\Item  \textbf{Android applications.} %MyTracks~\cite{mytracks}, Fennec~\cite{fennec}, and SGTPuzzles~\cite{sgtpuzzles} are three Android applications.
+MyTracks~\cite{mytracks}, developed by Google, records users' GPS tracks in outdoor activities, and provides
+interfaces to visualize them on Google Maps. Fennec~\cite{fennec}, developed by Mozilla, is the Mozilla
+Firefox web browser for mobile devices. SGTPuzzles~\cite{sgtpuzzles} is a small logic single-player game.
 
@@
 \hspace*{-0.2cm}
-\setlength{\tabcolsep}{.75\tabcolsep}
+\setlength{\tabcolsep}{.70\tabcolsep}
 \begin{tabular}{|p{4.4cm}||c|c|c|c|}
@@
  Android (3.2)&  683289 &  5085 &  10584 \\
+\hline
+\hline
+ Total &  1442022 &  13592 &  70569\\
 \hline
@@
 algorithms: RTA~\cite{rta}, 0-CFA, and 1-CFA~\cite{kcfa}.  When running
-each call graph construction algorithm on Android applications, we
-use two configurations: with and without the reflection-aware transformation
-(Section~\ref{sec:cg}).  We did not use other more expensive algorithms like $k$-CFA ($k >$ 1),
+each call graph construction algorithm on three Android applications, we
+use two configurations: with and without the reflection-aware algorithm 
+(Section~\ref{sec:cg}).  We did not use other expensive algorithms like $k$-CFA ($k >$ 1),
 because they can not scale to large programs.
@@
 \hspace*{-0.2cm}
-\setlength{\tabcolsep}{.45\tabcolsep}
+\setlength{\tabcolsep}{.35\tabcolsep}
 \begin{tabular}{|l||c|c|c||c|c|c||c|c|c||c|c|}
@@
  \hline
- Fennec & 14058 / 14387 &  55 / 54 &  0 / 0 & 8263 / 8898 & 0 / 0 & 0 / 0& 29125/ 31759 & xx / xxx & 0 / xxx& 433 & 1 \\
+ Fennec & 14058 / 14387 &  1 / 1 &  0 / 0 & 8263 / 8898 & 1 / 1 & 0 / 0& 29125/ 31759 & 3 / 3 & 1 / 1& 433 & 1 \\
  \hline
- MyTracks & 24036 / 24036 &  161 / 220 & 0 / 0 & 10803 / 13645 & 119 / 119 & 0 / 0 & 39235 / 110977 & 61 / xxx & 0 / xxx& 1192 & 1 \\
+ MyTracks & 24036 / 24036 &  161 / 220 & 0 / 0 & 10803 / 13645 & 119 / 119 & 0 / 0 & 39235 / 110977 & 1 / 1 & 0 / 1 & 1192 & 1 \\
+\hline
+\hline
+ Total & 178279 / 178842 &  188 / 251 & 6 / 6 & 129744 / 133357 & 137 / 137& 7 / 7 & 461423 / 536358& 21 / 21 & 10 / 11 & 3521 & 11 \\
 \hline
@@
 We further examined the detailed results for each subject.
-Among xxx warnings issued by using the 1-CFA algorithm, xxx
-are false positives, xxx are redundant:
-they have the same causes as the rest xxx warnings. (XXX why there
-are FP and redundant warnings?)
+Among the 21 warnings issued by using the 1-CFA algorithm, 2
+are false positives, and 8 are redundant:
+they have the same causes as the rest 11 warnings.
 
-why finds a bug in SGTPuzzle, because the \CodeIn{SmallKeyBoard} has been
-explicitly created in this main class \CodeIn{SGTPuzzles} \CodeIn{setKeyboardVisibility},
-thus, even without reflection-aware
+%The primary
+%reason for the false positive is because the precision of call graph,
+%while the reason for redundant warnings is because multiple
+%methods ca
+%Even a context-sensitive call graph construction algorithm is used,
 
-Why RTA, 0-CFA finds few, because they do not distinguish different
-calling context.
+%why finds a bug in SGTPuzzle, because the \CodeIn{SmallKeyBoard} has been
+%explicitly created in this main class \CodeIn{SGTPuzzles} \CodeIn{setKeyboardVisibility},
+%thus, even without reflection-aware
 
@@
 path. We reported this error to the S3dropbox developers. Tom Czarniecki,
-a key developer of S3dropbox confirmed this potential single-thread
+a key developer of S3dropbox confirmed this potential single-GUI-thread
 violation. He mentioned that the S3dropbox project has already
@@
 Another reason of missing this violation is because some GUI frameworks like Swing
-do not provide any run-time checks for invalid thread access. Most
+do not provide any run-time checks for invalid thread accesses. Most
 of the time, programmers can get away with an apparently ``well behaved'' Swing
-GUI that actually breaks the single-thread rule. However, As clearly
-indicated in the official documentation, Swing is a single-threaded GUI
+GUI that actually breaks the single-GUI-thread rule. However, As clearly
+indicated in the official documentation, Swing is a single-GUI-threaded GUI
 toolkit, and is not thread-safe. All Swing code must be executed in the UI-thread and
@@
 used design patterns, runtime checks, and testing to avoid violating
-the single-thread rule. However, due to the huge space of
+the single-GUI-thread rule. However, due to the huge space of
 possible UI interactions, potential
@@
 algorithm is more effective in finding errors, and our reflection-aware call
-graph construction algorithm is critical to find errors on
+graph construction algorithm is critical to find errors on some
 Android applications.
+
+\subsubsection{Comparing Graph Search Strategies}
+\label{sec:search}
+
+Our error detection algorithm in Figure~\ref{fig:detectalgorithm} uses BFS to search potential
+single-GUI-thread violations. However, other graph search strategies such as
+Depth-First Search (DFS) and exhaustive path search can also be employed. To
+understand trade-offs between using different search strategies, we 
+implemented two variants of the algorithm in Figure~\ref{fig:detectalgorithm}, and
+evaluated them on the same subjects with the identical environment settings.
+
+The first variant uses DFS by changing line 7 of Figure~\ref{fig:detectalgorithm}
+to \CodeIn{getReachableStartsByDFS(cg)}, changing line 9 of Figure~\ref{fig:detectalgorithm}
+to \CodeIn{queue} $\leftarrow$ \CodeIn{an empty stack}, and changing queue operations
+(\CodeIn{enqueue} and \CodeIn{dequeue}) to the corresponding stack operations (\CodeIn{push} and \CodeIn{pop}).
+This variant missed one error in the FileBunker subject, and found 8 errors
+in total.  That is because DFS searches deeper into the graph, and the path it finds
+may not be the shortest path.
+
+%Hundson: 3, 1
+%EclipseRunner: 6, 1
+%S3dropbox: ? , ?  too many warnings time: 31678 (45528 chains), running out of memory
+%SudokuSolver:  2, 1 too many warnings: 1700, 2090
+%VirgoFTP: 2, 2
+%FileBunker:  2, 0  //very long method calls
+%Fennec: 3, 1
+%SGTPuzzler: 1, 1
+%MyTracks: 1, 1
+
+The second variant uses exhaustive search to find potential errors. This variant
+enumerates all non-cyclic paths from the start nodes, and checks whether each
+path spawns a new thread and accesses GUI object without using safe methods. As
+a result, this variant run out of memory on all subjects. We further checked
+the traversed paths before the algorithm terminated, and found none of the explored
+path revealed a valid error. This is because the number of
+non-cyclic paths in a graph is exponetially large to the graph node number.
+For a realistic call graph which often contains thousands of nodes, it is impossible to enumerate all
+paths in practice.
+
+\vspace{1mm}
+
+\noindent \textbf{\textit{Summary.}} Using BFS finds more errors than DFS and
+exhaustive search in our error detection algorithm.
 
@@
  \hline
- EclipseRunner&  1621 &  1487 &  1487 & 1487 &  5 & 1\\
+ EclipseRunner&  1621 &  1487 &  1487 & 1487 &  6 & 6\\
  \hline
@@
  \hline
- Fennec &  xxxx &  xx &  xxx & xx &  xxx & xx\\
+ Fennec &  122 &  84 & 84 & 84 &  9 & 3\\
  \hline
- MyTracks &  xxxx &  xx &  xxx & xx &  xxx & xx\\
+ MyTracks &  1176 &  441 &  441 & 441 &  63 & 1 \\
+\hline
+ \hline
+ Total &  56214 &  39708 &  37955 &  2678 &  89 & 21 \\
  \hline
@@
 shows the output warning number using the reflection-aware 1-CFA algorithm.
-Column ``\#Warning $F_i$'' represents the number of remaining warnings after applying
-filters 1 -- $i$, and the number in last column is taken
+Column ``\#W $F_i$'' represents the number of remaining warnings after applying
+filters 1 -- $i$. Numbers in last column are taken
 from Table~\ref{table:results}.

### 2012-01-30 GUIErrorDetector/paper/introduction.tex
significant revise based on mike's comments

@@
 
-End-user satisfaction and retention of a software application
- are largely dependent on the usability and correctness of
-its GUIs.
+End-user satisfaction depends in part on the responsiveness and
+robustness of a software application's GUI.
 
-To make the GUI more responsive and utilize multi-core computation,
+To make the GUI more responsive, 
 GUI applications often spawn separate threads to handle time-consuming
@@
 and network requests. This permits the GUI to respond to new events
-even before the lengthy task completes.
+even before the lengthy task completes. However, the use of multiple threads
+makes new types of errors which may compromise robustness, possible.
+We now discuss a programming rule for multithreaded GUIs, the consequence
+of violating it, and a technique for statically detecting such violations.
 
-\subsection{The Single-thread Rule}
+%\subsection{The Single-thread Rule for GUI Object Access}
+%ugly hack
+\subsection{\hspace{-1.1ex}\mbox{The}~\mbox{Single-thread}~\mbox{Rule}~\mbox{for}~\mbox{GUI}~\mbox{Object}~\mbox{Access}}
 
-Many popular GUI frameworks such as Swing~\cite{swing},
-SWT~\cite{swt}, Android~\cite{android},
-Qt~\cite{qt}, MacOS Cocoa~\cite{macos},
+Many popular GUI frameworks such as Swing~\cite{swing}, SWT~\cite{swt}, Eclipse plugin~\cite{eclipse},
+Android~\cite{android}, Qt~\cite{qt}, MacOS Cocoa~\cite{macos},
 and X Windows~\cite{xwindow}
-adapt the \textit{single-thread rule}:
+adopt the \textit{single-GUI-thread rule}:
 
@@
 is executed. All code that interacts with GUI objects must also
-execute on that thread.  There are several advantages to the single-thread rule:
+execute on that thread.  There are several advantages to the single-GUI-thread rule:
 
@@
 
-\item GUI developers do not need an in-depth
-understanding of concurrent programming. A GUI framework in which all GUI objects
-fully support multithreaded access can be difficult to extend, particularly
-for developers who are not expert at threads programming.
+\item Concurrency errors, such as races and deadlocks, never occur on GUI objects, without
+requiring GUI developers to become experts at concurrent programming. Programming the
+(\textbf{hard-to-recognized words}) is also simpler and less error-prone.
 
-\item GUI events are dispatched in a predictable order from the same event queue.
-In contrast, in a GUI framework without adapting the single-thread rule where GUI objects 
-support multithreaded access, any component changes can be interleaved with event
-processing at the whim of the thread scheduler. This makes program behavior comprehension hard,
- and comprehensive testing difficult or impossible.
-
-\item The single-thread rule incurs less overhead.
-A GUI framework that attempts to carefully lock critical sections can spend a substantial
-amount of time and space managing locks. Whenever the framework calls a method that might
-be implemented in client code (for example, any public or protected method in a public class),
+\item The single-GUI-thread rule incurs less overhead.
+Otherwise, whenever the framework calls a method that might
+be implemented in client code (e.g., any public or protected method in a public class),
 the framework must save its state and release all locks so that the client code can grab locks
 if necessary. When GUI objects return from the method, the framework must re-grab their locks and
-restore states. Therefore, all applications using the framework will bear the cost of this, even though most
-applications do not require concurrent access to the GUI.
+restore states.  Even applications that do not require concurrent access to the GUI
+must bear this cost.
 
+\item GUI events are dispatched in a predictable order from a single event queue.
+If the thread scheduler could arbitrarily interleave, component changes, event processing,
+program comprehension and testing would be more difficult.
 \end{itemize}
@@
 %Single-threaded GUI frameworks are not unique to Java; ,
-%and many others are also single-threaded.
+%and many others are also single-GUI-threaded.
 
@@
 
-The single-thread rule pushes a burden back on GUI application developers,
-who must ensure all GUI objects are accessed by the UI thread.
+The single-GUI-thread rule requires GUI application developers to
+ ensure that all GUI objects are accessed only by the UI thread.
+If not, an \textit{invalid thread access error} will occur.
 
-In a multithreaded GUI application, the single-thread rule can be
-easily violated since a spawned non-UI thread often needs to update
+The single-GUI-thread rule can be easily violated since a spawned non-UI thread often needs to update
 the GUI  after its  task is finished.
-For example, a server program can get requests from other programs
-that might be running on different machines. These requests can come at any time,
-and they result in one of the server's methods being invoked in some thread.
-After handling the request, the GUI-update code that displays the response must be executed on the UI-thread.
-If not, an \textit{invalid thread access error} will occur. In practice, such
-invalid thread access error is \textit{frequent}, \textit{pervasive}, and \textit{severe}.
+In practice, invalid thread access errors are both \textit{frequent} and \textit{severe}.
 %and \textit{difficult to avoid}.
@@
 and discussion forum returns over 2732 bug reports and 351 distinct threads, respectively. 
-We manually studied all 156 \textit{confirmed} distinct bug reports, and 
-found this error has been reported in at least 20 distinct eclipse projects
-and 40 distinct eclipse components. Even after over 10 years of active development,
+We manually studied all 156 distinct \textit{confirmed} bug reports, and 
+found this error has been reported in at least 20 distinct Eclipse projects
+and 40 distinct Eclipse components. Even after over 10 years of active development,
 a recent release of Eclipse still contains this error (bug id: 333533, reported in 01/2011).
@@
 to fix them. Developers usually need non-local reasoning to find the specific
-UI interactions that can trigger the bug;  it even took developers 2 years
-to fix bug: 51757 and verify the patch. In addition, the invalid thread access error
-is UI-relevant and user-perceivable; it cannot be recovered by the program itself
-and often terminates the whole application. In many circumstances as described in the bug reports,
+UI interactions that can trigger the bug;  it took developers 2 years
+to fix bug 51757 and verify the patch. In addition, the invalid thread access error
+is severe. It is user-perceivable; it cannot be recovered by the program itself,
+and it often terminates the whole application. In many circumstances as described in the bug reports,
 users can only restart the application to recover from the error.
@@
 \begin{figure}[t]
+\hspace{6mm}\small{In class: org.mozilla.gecko.gfx.LayerView}
+\vspace{-2mm}
 \begin{CodeOut}
 \begin{alltt}
-
-     /* In class: org.mozilla.gecko.gfx.LayerView */
 68.  public LayerView(Context context, LayerController controller) \{
@@
      \}
-
-     /* In Android's lib class: android.opengl.GLSurfaceView */
+\end{alltt}
+\end{CodeOut}
+\hspace{6mm} \small{In Android library class: android.opengl.GLSurfaceView}
+\vspace{-2mm}
+\begin{CodeOut}
+\begin{alltt}
 272. public void setRenderer(Renderer renderer) \{
@@
      \}
-
-     /* In class: org.mozilla.gecko.gfx.LayerRenderer */
+\end{alltt}
+\end{CodeOut}
+ \hspace{6mm}\small{In class: org.mozilla.gecko.gfx.LayerRenderer}
+\vspace{-2mm}
+\begin{CodeOut}
+\begin{alltt}
 220. public void onSurfaceChanged(GL10 gl, int width, int height) \{
@@
 bug reported on 11/17/2011 in Mozilla firefox release 10.0.a.rc3
-for the Android platform (bugzilla ID: 703256). \CodeIn{LayerView}'s constructor
-calls method \CodeIn{setRender} that
-spawns a new thread at line 283. The new thread calls back method
-\CodeIn{onSurfaceChanged} that access GUI objects at line 222, and
-causes an invalid thread access error.
-Our tool
-can find this error and generate a warning as shown in
+for the Android platform (bugzilla ID: 703256). On line 74, \CodeIn{LayerView}'s constructor
+calls method \CodeIn{setRenderer} which 
+spawns a new thread on line 283. This newly created, non-UI thread calls back method
+\CodeIn{onSurfaceChanged} that accesses GUI objects on line 222,
+causing an invalid thread access error. Our tool
+finds this error and generate a report as shown in
 Figure~\ref{fig:report}.
@@
 like Android also suffer from similar problems. For example, 
-Figure~\ref{fig:androiderror} shows a recently reported bug on Android version of Mozilla Firefox.
-In Figure~\ref{fig:androiderror}, \CodeIn{LayViewer}'s constructor calls the
-\CodeIn{setRender} method (line 74), which spawns a new thread (line 283).
-This newly created, non-UI thread calls back the \CodeIn{onSurfaceChanged} method that
-accesses the GUI objects at line 222, causing an invalid thread access error.
-Compared to other reported errors, this bug is even more difficult to note, 
-since the code that spawns a new thread inside the \CodeIn{setRender} method is
+Figure~\ref{fig:androiderror} shows a recently-reported bug in the Android version of Mozilla Firefox.
+This bug is particularly difficult to diagnose, 
+since the code that spawns a new thread inside the \CodeIn{setRenderer} method is
 in an Android library whose source code may not be available to developers.
@@
 
-Invalid thread access errors have significantly affect the
-usability of GUIs, but they have not been thoroughly studied in
-the context of multithreaded GUI applications. To ensure GUIs
-behave correctly, effective techniques must be developed to alleviate this problem.
+To ensure GUIs behave correctly, developers must prevent or detect invalid thread
+access errors, and effective techniques must be developed.% to alleviate this problem.
 
-Software testing, the most widely used method to ensure program correctness,
-is insufficient to detect such errors. The space of possible interactions
-with a GUI is enormous, in that each sequence of GUI events can result in
+%Software testing, the most widely used method to ensure program correctness,
+%is insufficient to detect such errors. 
+It is infeasible for testing to cover the enormous space of possible interactions
+with a GUI, in that each sequence of GUI events can result in
 a difficult state, and each GUI event may need to be evaluated in all of
-these states. It is almost impossible for testing to cover every possible
-state. In fact, a widely-used software system like Eclipse
+these states. A well-developed software system like Eclipse
 often has a well-designed test suite that achieves fairly high statement coverage;
@@
 
-%Program refactoring~\cite{Mens:2004}, another popular way to improve software quality,
-%is also inadequate to eliminate this error.
-
-%One way to find such invalid thread access error is to check every GUI object
-%accessing code to see whether
-
-A standard way to fix an
-invalid thread access error is to replace direct GUI object accessing code 
-with asynchronized message passing, to ensure a GUI object is accessed in
-the UI thread. For example, to fix the bug in Figure~\ref{fig:androiderror},
-a developer would wrap line 222 inside a \CodeIn{post} message passing method\footnote{The
+Stylized coding patterns are also inadequate. One possible rule is to always
+access GUI objects via asynchronized message passing, to ensure a GUI object is accessed in
+the UI thread. For example, a developer could have prevented the bug in Figure~\ref{fig:androiderror},
+by wrapping line 222 inside a \CodeIn{post} message passing method\footnote{The
 \CodeIn{post} method in class \CodeIn{android.widget.View} is a
-a standard way to send messages to the UI-thread.}, as follows:
+a standard way to send asynchronized messages to the UI-thread.}, as follows:
 
@@
 
-One may wonder that a simple analysis to check whether every GUI object
-accessing code has been wrapped by (a)synchronized message passing may
-be capable to find invalid thread errors. However, such an approach is problematic,
-because not every GUI object access needs to be wrapped by a message passing
-method, e.g., methods that are only called from UI-thread can safely
-access any GUI object. On the other hand, using asynchronized message passing has no timing
-guarantee. It is entirely possible that, in some cases, a GUI object has already been
-disposed before the message sent to arrives, causing other bugs. 
-Thus, programmers can not use it everywhere to wrap all GUI object accessing code.
-In our evaluation on real world programs, we found this simple analysis 
-can not be used in practice: it issued
+Such an approach is desirable for accesses from non-UI threads, but it is unnecessary
+and dangerous fro accesses from the UI thread. Asynchronized message passing offers
+no timing guarantee, so that a GUI object may have already been
+disposed before the message sent to it arrives, causing other bugs. 
+In our evaluation on real-world programs, we found a simple analysis that
+requires GUI operations to be in a message issues
 an unacceptable number of false positives and redundant warnings.
@@
 
-This paper uses static analysis to find such potential errors.
-Static analysis has two advantages while compared to dynamic approaches such as
+This paper uses static analysis to find potential GUI errors.
+Static analysis has two advantages compared to dynamic approaches such as
  testing. First, a static analysis can explore every path of the program without
@@
 event dispatching thread before accessing a GUI object.
+\CodeIn{\small{...}} represents the other 9 method calls that are omitted for brevity.
 }} %\vspace{-5mm}
@@
 
-In our static analysis, we formulate finding invalid thread access as a call graph reachability
+Our static analysis formulates finding invalid thread access as a call graph reachability
 problem. Given a call graph, our technique traverses
-every possible paths from its entry nodes, checking whether
+every possible path from its entry nodes, checking whether
 there exists a path to access a GUI object from a non-UI thread. If 
@@
 This report clearly indicates how a new, non-UI thread is spawned and
-accesses GUI objects. 
-The generated report is a great starting point for the developers, who can
+accesses GUI objects. The generated report allows  developers to
 inspect the method call chain, understand how the error
-is triggered, and then determine if it is a real bug.
+is triggered, and fix it if it is a real bug.
 
-Our static analysis is independent of the call graph construction algorithms.
+Our static analysis is independent of the call graph construction algorithm.
 Given a sound call graph, our analysis is sound in that it does
-not miss true positives. We note, however, that computing a sound
-call graph with acceptable precision for GUI applications in the presence of reflection
-is non-trivial.
+not miss true positives. GUI applications tend to (\textbf{recognize}) use of reflection. And
+in the presence of reflection, however, it is
+non-trivial to compute a sound call graph with acceptable precision
 Existing call graph construction algorithms such as RTA~\cite{rta}
-and k-CFA~\cite{kcfa}
-fails to build a sufficiently complete call graph, due to their limitations
-to reason about reflections.  To alleviate this problem,
-we present a method to build reflection-aware call graph, and
+and k-CFA~\cite{kcfa} fail to build a good call graph.
+To alleviate this problem, we present an algorithm to build reflection-aware call graph, and
 also compare its usefulness with existing call graph construction algorithms in
@@
 
-We instantiated our technique for four popular GUI frameworks namely SWT,
-eclipse plugin environment, Java Swing, and Android. 
-Swing and SWT are unquestionably 
-two dominating GUI frameworks in developing desktop Java applications.
-Eclipse and its plugin development environment is the de-facto standard
-IDE for Java. Android is the No. 1 platform for
-developing mobile applications with market share 56\% as of Sep 2011.
-Although our technique is generally applicable for GUI
-frameworks adapting the single-thread rule, a specific framework
-may have its own treatment of \textit{UI thread} and \textit{call graph
-entry nodes}. Thus, we must explicitly identify those framework-specific
-parts in our prototype tool implementation.
+We implement an invalid thread error detection tool that supports
+four popular GUI frameworks namely SWT, Eclipse plugin environment,
+Swing, and Android. Swing and SWT are the
+two dominant GUI frameworks for desktop Java applications.
+Eclipse is the de-facto standard IDE for Java. Android is the No. 1 platform for
+mobile applications with market share 56\% as of Sep 2011.
+Although our technique is applicable to any GUI
+frameworks with the single-GUI-thread rule, a specific framework
+may have its own treatment of \textit{UI thread} and \textit{program 
+entry points}. Thus, our implementation is parameterized with respect to
+those those framework-specific parts.
 
@@
 
-We implement an invalid thread error detection tool that supports
-the above four GUI frameworks. Our tool works in a fully-automatic,
-push-button manner, and scales to realistic programs.
-We evaluate our implementation on XXX subjects from four different
-frameworks over XXX LOC. The experiment results demonstrate
-that: our technique is effective (it found XXX real-world errors
-on all supported frameworks, and produced significantly less
+Our tool works in a fully automatic, push-button manner, and scales to realistic programs.
+We evaluated our implementation on 9 subjects comprising over 67000 LOC.
+The experiment results demonstrate
+that: our technique is effective (it found 11 real-world errors
+from four supported frameworks, and produced significantly less
 false positives and redundant warnings than the simple analysis);
 our reflection-aware call graph construction algorithm is
-critical in finding errors in Android applications,
-%graph construction algorithm is useful (XXX it improves both completeness
-%and precision over the existing algorithms), 
+critical in finding errors in Android applications;
 and our proposed
@@
 \begin{itemize}
-\item \textbf{Problem.} We are the \textit{first} to address
-the invalid thread access error detection problem in the context of multithreaded GUI applications.
+\item \textbf{Problem.} To the best of our knowledge, we are the first to address
+the invalid thread access error detection problem for multithreaded GUI applications.
 %, and formulate it
@@
 and present a general error detection technique.
-In particular, to deal with the unique features in
+In addition, to deal with the unique features in
 multithreaded GUI programs, we propose a reflection-aware
-call graph construction method. (Section~\ref{sec:technique}).
+call graph construction algorithm. (Section~\ref{sec:technique}).
 
-\item \textbf{Implementation.} We implement our technique, and
-instantiate it for four
-popular GUI platforms: SWT, eclipse plugin, Swing, and Android (Section~\ref{sec:implementation}). Our
+\item \textbf{Implementation.} We implemented our technique, and
+instantiated it for four
+popular GUI platforms: SWT, Eclipse plugin, Swing, and Android (Section~\ref{sec:implementation}). Our
 tool implementation is publicly available at:
@@
 
-\item \textbf{Evaluation.} We performed an experiment on XXX subjects
-from 4 different platforms over XXX LOC to show the usefulness
-of the proposed technique (Section~\ref{sec:evaluation}).
+\item \textbf{Evaluation.} We performed an experiment on 9 subjects
+from 4 different frameworks, comprising over 67000 LOC. The results
+show the usefulness of the proposed technique (Section~\ref{sec:evaluation}).
 

### 2012-01-30 GUIErrorDetector/paper/technique.tex
significant revise based on mike's comments

@@
 GUI application has a single global UI thread. This is true for applications
-built on top of GUI frameworks adapting the single-thread rule. The
+built on top of GUI frameworks adapting the single-GUI-thread rule. The
 only exception is that 
@@
 \noindent  {\textsc{\textbf{Definition 4 (Safe Methods).}}} {GUI frameworks that
-adopt the single-thread rule must provide methods to permit non-UI threads
+adopt the single-GUI-thread rule must provide methods to permit non-UI threads
 to run code in the UI thread. We can such methods \textit{safe methods}, since

### 2012-01-31 trunk/GUIErrorDetector/paper/evaluation.tex
significant revise

@@
 compare the reflection-aware call graph construction algorithms
-with existing ones , and to evaluate the usefulness of the proposed 
+with existing ones, and to evaluate the usefulness of the proposed 
  heuristics.
 
-First, we describe our subject programs (Section~\ref{sec:subjects}) and the experimental procedural (Section~\ref{sec:procedural}).
-We then show that our technique detects bugs in real-world GUI applications on
-four supported frameworks (Section~\ref{sec:errors}). We also compare our technique with
+First, we describe our subject programs (Section~\ref{sec:subjects}) and the experimental procedure (Section~\ref{sec:procedural}).
+We then show that our technique detects bugs in real-world GUI applications (Section~\ref{sec:errors}).
+We also compare our technique with
 a straightfoward approach in Section~\ref{sec:straightforward},  compare the reflection-aware call graph
@@
  Finally, we show that the set of proposed heuristics are effective
-in removing redundant warnings and eliminate false positivies (Section~\ref{sec:filters}).
+in removing redundant warnings and eliminate false positives (Section~\ref{sec:filters}).
 
@@
 
-We use a set of open-source projects from Sourceforge, Google code and Eclipse plugin
+We use a set of open-source projects from Sourceforge, Google code, and the Eclipse plugin
 market as evaluation subjects. To choose subjects for each supported GUI framework,
-we first search the framework keywords (e.g., ``Java Swing'' or ``Java SWT'')
-in the above three source repositories, and then select subjects based on the following
-criterias. First, the subject must be a multithreaded GUI application, not
+we first searched for the framework keywords (e.g., ``Java Swing'' or ``Java SWT'')
+in the above three source repositories, and then selected subjects based on the following
+criteria. First, the subject must be a multithreaded GUI application, not
 an open library. Second, the subject must undergone at least two years of active development,
-and is listed in the first 3 results pages based on popularity. This permits us
-to exclude many pre-mature subjects that may contain obvious errors.
+and is listed in the first 3 result pages based on popularity. This permits us
+to exclude many immature subjects that may contain obvious errors.
 
 The subjects used in our experiment are shown in Table~\ref{table:subjects}. Our
-subjects include end-user applications, programming tools, and games. Specifically:
+subjects include end-user applications, programming tools, and games.
 
@@
 %VirgoFTP~\cite{virgo} and FileBunker~\cite{filebunker} are two useful SWT desktop applications.
-VirgoFTP~\cite{virgo} implements a simple FTP client based on Java and SWT UI library, and
+VirgoFTP~\cite{virgo} implements a simple FTP client based on Java and SWT UI library.
 FileBunker~\cite{filebunker} is a file backup application which uses one or more GMail accounts as its backup repository.
@@
 \Item \textbf{Eclipse plugins.}
-HudsonEclipse~\cite{hudson} adds several new tools to  monitor Hudson build status from Eclipse.
+HudsonEclipse~\cite{hudson} monitors Hudson build status from Eclipse.
 EclipseRunner~\cite{eclipserunner} extends capability of running launch configurations in Eclipse IDE.
@@
 \Item  \textbf{Android applications.} %MyTracks~\cite{mytracks}, Fennec~\cite{fennec}, and SGTPuzzles~\cite{sgtpuzzles} are three Android applications.
+SGTPuzzler~\cite{sgtpuzzles} is a single-player logic game.
+Fennec~\cite{fennec}, developed by Mozilla, is the Mozilla
+Firefox web browser for mobile devices. 
 MyTracks~\cite{mytracks}, developed by Google, records users' GPS tracks in outdoor activities, and provides
-interfaces to visualize them on Google Maps. Fennec~\cite{fennec}, developed by Mozilla, is the Mozilla
-Firefox web browser for mobile devices. SGTPuzzles~\cite{sgtpuzzles} is a small logic single-player game.
+interfaces to visualize them on Google Maps.
 
@@
 of code, as counted by LOCC~\cite{locc}.  Each program is analyzed
-together with its dependent GUI framework, as listed in
+together with its GUI framework, as listed in
 the bottom table.} }
@@
 
-\subsection{Procedural}
+\subsection{Experimental Procedure}
 \label{sec:procedural}
 
-We run our tool on each subject with three call graph construction
+We ran our tool on each subject with three call graph construction
 algorithms: RTA~\cite{rta}, 0-CFA, and 1-CFA~\cite{kcfa}.  When running
@@
 (Section~\ref{sec:cg}).  We did not use other expensive algorithms like $k$-CFA ($k >$ 1),
-because they can not scale to large programs.
+because they can not scale to our subject programs.
 
@@
 We found SGTPuzzler is the only subject that uses native methods to interact with
-underlying operating systems. Thus, we manually added 3 \CodeIn{@CalledByNative}
+underlying operating systems. Thus, we manually added 3 \CodeIn{@CalledByNativeMethods}
 annotations for it. Also two subjects MyTracks and Fennec employ a self-defined
@@
 After provided with necessary annotations and heuristic filters,
-our tool works in a fully-automatic, push-bottom manner. For each output
+our tool works in a fully-automatic, push-button manner. For each output
 warning, we manually determine its validity by either searching the
@@
 \cline{2-10}
- Program  &  \multicolumn{3}{|c|}{RTA / reflection aware}& \multicolumn{3}{|c|}{0-CFA / reflection aware} & \multicolumn{3}{|c||}{1-CFA / reflection aware} & \multicolumn{2}{|c|}{Section~\ref{sec:straightforward}}  \\
+ Program  &  \multicolumn{3}{|c|}{RTA }& \multicolumn{3}{|c|}{0-CFA } & \multicolumn{3}{|c||}{1-CFA } & \multicolumn{2}{|c|}{Section~\ref{sec:straightforward}}  \\
 \cline{2-12}
@@
 shows the number of warnings issued by our tool. Column ``\#Bug'' shows
-the actual bugs found. Columns ``RTA / reflection aware '', ``0-CFA / reflection aware'',
-and ``1-CFA / reflection aware'' show the results of using different
-call graph construction algorithms with (before ``/'') or without (after ``/'')
-using the reflection-aware algorithm on Android applications. In each cell of the table
+the actual bugs found. Columns ``RTA '', ``0-CFA'',
+and ``1-CFA'' show the results of using different
+call graph construction algorithms. In each cell of the table
 for Android applications, a slash ``/'' separates the result of
@@
 \begin{figure}[t]
+\hspace{4mm}\small{In class: com.tomczarniecki.s3.gui.DeleteBucketAction}
+\vspace{-2mm}
 \begin{CodeOut}
 \begin{alltt}
-/* In class: com.tomczarniecki.s3.gui.DeleteBucketAction */
 59.private void deleteBucket() \{
@@
 \begin{figure}[t]
+\hspace{4mm}\small{In class: com.eclipserunner.views.impl.RunnerView}
+\vspace{-2mm}
 \begin{CodeOut}
 \begin{alltt} 
-/* com.eclipserunner.views.impl.RunnerView */
 179.private void initializeResourceChangeListener() \{
@@
 
+\vspace{2mm}
+\hspace{3mm}\small{In class: com.google.android.apps.mytracks.StatsUtilities}
+\vspace{-2mm}
 \begin{CodeOut}
 \begin{alltt}
-/*In class: com.google.android.apps.mytracks.StatsUtilities*/
 97.  public void setLatLong(int id, double d) \{
@@
 99.     msgTextView.setText(LAT\_LONG\_FORMAT.format(d));
-100.\}
+100. \}
 \end{alltt}
@@
 call relationships that involve native methods. This limitation
-may lead to false negatives. Investigating the false positive
+may lead to false negatives. Investigating the false negative
 rate is ongoing work.

### 2012-01-31 trunk/GUIErrorDetector/paper/implementation.tex
significant revise

@@
 We implemented the proposed technique using the WALA framework~\cite{walatutorial}.
-Our prototype tool takes Java bytecode as inputs, works in a fully
+Our prototype tool takes Java bytecode as input, works in a fully
 automatic and push-button way to detect potential invalid thread access
@@
 Our current implementation supports four widely-used GUI frameworks, namely
-SWT, Eclipse plugin development, Java Swing, and Android.
-Our implementation %handles all of the Java language, and
-also takes
-all dependent libraries (e.g., \CodeIn{rt.jar} and \CodeIn{android.jar})
+SWT, Eclipse plugin development, Java Swing, and Android, including
+dependent libraries such as \CodeIn{rt.jar} and \CodeIn{android.jar}.
 into analysis. We implemented the reflection-aware call graph construction
@@
 library (i.e., \CodeIn{android.jar}) uses many ``stub'' classes as
-placeholder for the sake of efficiency. We manually re-compiled the whole
-\CodeIn{android.jar} from its source code by replacing all ``stub'' classes
+placeholders for the sake of efficiency. We manually re-compiled the whole
+\CodeIn{android.jar} from its source code and replaced all ``stub'' classes
 with real class files.

### 2012-01-31 trunk/GUIErrorDetector/paper/introduction.tex
significant revise

@@
 
-\item GUI developers do not need an in-depth
-understanding of concurrent programming. A GUI framework in which all GUI objects
-fully support multithreaded access can be difficult to extend, particularly
-for developers who are not expert at threads programming.
+\item Concurrency errors, such as races and deadlocks, never occur on GUI objects, without
+requiring GUI developers to become experts at concurrent programming. Programming the
+framework itself is also simpler and less error-prone.
 
-\item GUI events are dispatched in a predictable order from the same event queue.
-In contrast, in a GUI framework without adapting the single-thread rule where GUI objects 
-support multithreaded access, any component changes can be interleaved with event
-processing at the whim of the thread scheduler. This makes program behavior comprehension hard,
- and comprehensive testing difficult or impossible.
-
-\item The single-thread rule incurs less overhead.
-A GUI framework that attempts to carefully lock critical sections can spend a substantial
-amount of time and space managing locks. Whenever the framework calls a method that might
+\item The single-GUI-thread rule incurs less overhead.
+Otherwise, whenever the framework calls a method that might
 be implemented in client code (e.g., any public or protected method in a public class),
@@
 if necessary. When GUI objects return from the method, the framework must re-grab their locks and
-restore states. Therefore, all applications using the framework will bear the cost of this, even though most
-applications do not require concurrent access to the GUI.
+restore states.  Even applications that do not require concurrent access to the GUI
+must bear this cost.
 
+\item GUI events are dispatched in a predictable order from a single event queue.
+If the thread scheduler could arbitrarily interleave, component changes, event processing,
+program comprehension and testing would be more difficult.
 \end{itemize}
@@
 bug reported on 11/17/2011 in Mozilla firefox release 10.0.a.rc3
-for the Android platform (bugzilla ID: 703256). \CodeIn{LayerView}'s constructor
-calls method \CodeIn{setRender} that
-spawns a new thread at line 283. The new thread calls back method
-\CodeIn{onSurfaceChanged} that access GUI objects at line 222, and
-causes an invalid thread access error.
-Our tool
-can find this error and generate a report as shown in
+for the Android platform (bugzilla ID: 703256). On line 74, \CodeIn{LayerView}'s constructor
+calls method \CodeIn{setRenderer} which 
+spawns a new thread on line 283. This newly created, non-UI thread calls back method
+\CodeIn{onSurfaceChanged} that accesses GUI objects on line 222,
+causing an invalid thread access error. Our tool
+finds this error and generate a report as shown in
 Figure~\ref{fig:report}.
@@
 
-Invalid thread access errors have significantly affected the
-usability of GUIs, but they have not been thoroughly studied in
-the context of multithreaded GUI applications. To ensure GUIs
-behave correctly, effective techniques must be developed to alleviate this problem.
+To ensure GUIs behave correctly, developers must prevent or detect invalid thread
+access errors, and effective techniques must be developed.% to alleviate this problem.
 
-Software testing, the most widely used method to ensure program correctness,
-is insufficient to detect such errors. The space of possible interactions
-with a GUI is enormous, in that each sequence of GUI events can result in
+%Software testing, the most widely used method to ensure program correctness,
+%is insufficient to detect such errors. 
+It is infeasible for testing to cover the enormous space of possible interactions
+with a GUI, in that each sequence of GUI events can result in
 a difficult state, and each GUI event may need to be evaluated in all of
-these states. It is almost impossible for testing to cover every possible
-state. In fact, a widely-used software system like Eclipse
+these states. A well-developed software system like Eclipse
 often has a well-designed test suite that achieves fairly high statement coverage;
@@
 
-%Program refactoring~\cite{Mens:2004}, another popular way to improve software quality,
-%is also inadequate to eliminate this error.
-
-%One way to find such invalid thread access error is to check every GUI object
-%accessing code to see whether
-
-A standard way to fix an
-invalid thread access error is to replace direct GUI object accessing code 
-with (a)synchronized message passing, to ensure a GUI object is accessed in
-the UI thread. For example, to fix the bug in Figure~\ref{fig:androiderror},
-a developer would wrap line 222 inside a \CodeIn{post} message passing method\footnote{The
+Stylized coding patterns are also inadequate. One possible rule is to always
+access GUI objects via asynchronized message passing, to ensure a GUI object is accessed in
+the UI thread. For example, a developer could have prevented the bug in Figure~\ref{fig:androiderror},
+by wrapping line 222 inside a \CodeIn{post} message passing method\footnote{The
 \CodeIn{post} method in class \CodeIn{android.widget.View} is a
@@
 
-One may wonder that a simple analysis to check whether every GUI object
-accessing code has been wrapped by (a)synchronized message passing may
-be capable to find invalid thread errors. However, such an approach is problematic,
-because not every GUI object access needs to be wrapped by message passing
-method. For example, methods that are only called from UI-thread can safely
-access any GUI object. On the other hand, using asynchronized message passing has no timing
-guarantee. It is entirely possible that, in some cases, a GUI object has already been
-disposed before the message sent to arrives, causing other bugs. 
-Thus, programmers can not use it everywhere to wrap all GUI object accessing code.
-In our evaluation on real world programs, we found this simple analysis 
-can not be used in practice: it issued
-an unacceptable number of invalid warnings. %false positives and redundant warnings.
+Such an approach is desirable for accesses from non-UI threads, but it is unnecessary
+and dangerous for accesses from the UI thread. Asynchronized message passing offers
+no timing guarantee, so that a GUI object may have already been
+disposed before the message sent to it arrives, causing other bugs. 
+In our evaluation on real-world programs, we found a simple analysis that
+requires GUI operations to be in a message issues
+an unacceptable number of false positives and redundant warnings.
 
@@
 This report clearly indicates how a new, non-UI thread is spawned and
-accesses GUI objects. 
-The generated report is a great starting point for the developers, who can
+accesses GUI objects. The generated report allows  developers to
 inspect the method call chain, understand how the error
-is triggered, and then determine if it is a real bug.
+is triggered, and fix it if it is a real bug.
 
-Our static analysis is independent of the call graph construction algorithms.
+Our static analysis is independent of the call graph construction algorithm.
 Given a sound call graph, our analysis is sound in that it does
-not miss true positives. We note, however, that computing a sound
-call graph with acceptable precision for GUI applications in the presence of reflection
-is non-trivial.
+not miss true positives. GUI applications tend to use of reflection. And
+in the presence of reflection, however, it is
+non-trivial to compute a sound call graph with acceptable precision
 Existing call graph construction algorithms such as RTA~\cite{rta}
-and k-CFA~\cite{kcfa}
-fails to build a good call graph, due to their limitations
-to reason about reflections.  To alleviate this problem,
-we present an algorithm to build reflection-aware call graph, and
+and k-CFA~\cite{kcfa} fail to build a good call graph.
+To alleviate this problem, we present an algorithm to build reflection-aware call graph, and
 also compare its usefulness with existing call graph construction algorithms in
@@
 
-We instantiated our technique for four popular GUI frameworks namely SWT,
-Eclipse plugin environment, Java Swing, and Android. 
-Swing and SWT are unquestionably 
-two dominating GUI frameworks in developing desktop Java applications.
-Eclipse and its plugin development environment is the de-facto standard
-IDE for Java. Android is the No. 1 platform for
-developing mobile applications with market share 56\% as of Sep 2011.
-Although our technique is generally applicable for GUI
-frameworks adapting the single-thread rule, a specific framework
+We implement an invalid thread error detection tool that supports
+four popular GUI frameworks namely SWT, Eclipse plugin environment,
+Swing, and Android. Swing and SWT are the
+two dominant GUI frameworks for desktop Java applications.
+Eclipse is the de-facto standard IDE for Java. Android is the No. 1 platform for
+mobile applications with market share 56\% as of Sep 2011.
+Although our technique is applicable to any GUI
+frameworks with the single-GUI-thread rule, a specific framework
 may have its own treatment of \textit{UI thread} and \textit{program 
-entry points}. Thus, we must explicitly identify those framework-specific
-parts in our prototype tool implementation.
+entry points}. Thus, our implementation is parameterized with respect to
+those those framework-specific parts.
 
@@
 
-We implement an invalid thread error detection tool that supports
-the above four GUI frameworks. Our tool works in a fully-automatic
- manner, and scales to realistic programs.
-We evaluate our implementation on 9 subjects from four different
-frameworks over 67KLOC with 1.4MLOC of dependent library code.
+Our tool works in a fully automatic, push-button manner, and scales to realistic programs.
+We evaluated our implementation on 9 subjects comprising over 67000 LOC.
 The experiment results demonstrate
 that: our technique is effective (it found 11 real-world errors
-from four supported frameworks
-%, and produced significantly less
-%false positives and redundant warnings than the simple analysis
-);
+from four supported frameworks, and produced significantly less
+false positives and redundant warnings than the simple analysis);
 our reflection-aware call graph construction algorithm is
-critical in finding errors in Android applications,
+critical in finding errors in Android applications;
 and our proposed
@@
 and present a general error detection technique.
-In particular, to deal with the unique features in
+In addition, to deal with the unique features in
 multithreaded GUI programs, we propose a reflection-aware
@@
 
-\item \textbf{Implementation.} We implement our technique, and
-instantiate it for four
-popular GUI platforms: SWT, eclipse plugin, Swing, and Android (Section~\ref{sec:implementation}). Our
+\item \textbf{Implementation.} We implemented our technique, and
+instantiated it for four
+popular GUI platforms: SWT, Eclipse plugin, Swing, and Android (Section~\ref{sec:implementation}). Our
 tool implementation is publicly available at:
@@
 \item \textbf{Evaluation.} We performed an experiment on 9 subjects
-from 4 different platforms over 67000 LOC to show the usefulness
-of the proposed technique (Section~\ref{sec:evaluation}).
+from 4 different frameworks, comprising over 67000 LOC. The results
+show the usefulness of the proposed technique (Section~\ref{sec:evaluation}).
 

### 2012-01-31 GUIErrorDetector/paper/technique.tex
significant revise

@@
 
-We first give our high-level approach formulation, then present
-an error detection algorithm. Finally, we show how to instantiate
-the error algorithm to different GUI frameworks.
+We first give a high-level formulation of the problem, then present
+the error detection algorithm. Finally, we show how to instantiate
+the error algorithm for different GUI frameworks.
 
-\subsection{Approach Formulation}
+\subsection{Problem Formulation}
 
-This section formulates our high-level approach. We define the
+This section formulates the problem. We define the
 notations of \textit{UI thread}, \textit{non-UI threads},
@@
 dynamic call graphs over all possible executions of the program. 
-A conservative static call graph used in practice is a superset of
+A conservative, or sound, static call graph is a superset of
 the ideal call graph; it over-approximates the
@@
 
-Our algorithm in Figure~\ref{fig:detectalgorithm} works as follows. It
+Our algorithm in Figure~\ref{fig:detectalgorithm} %works as follows. It
 first constructs a static call graph for the tested program (line 2),
-then specifies entry nodes for it (line 3). The algorithm starts to traverse
-the call graph from every entry node (line 6). For every entry node,
-it first uses Breadth First Search (BFS) to find all reachable
-\CodeIn{Thread.start()} calls (line 7). Each \CodeIn{Thread.start()} call
-indicates that a new, non-UI thread is spawned.  After that, 
-the algorithm uses a BFS to find reachable UI-accessing methods (lines 9 -- 23)
-from each \CodeIn{Thread.start()} node.
-Specifically, it uses a queue to keep track of all visited nodes, and
-then checks every successive node to be visited (line 12);
-it reports an error if that node
-is a UI-accessing method (line 15), or skips it if it is
-a safe method (line 17), or simply keeps traversing otherwise (line 19).
+then specifies entry nodes, UI-accessing nodes, and safe nodes
+for it on line 3, 4, and 5, respectively. Lines 3--5 are GUI framework-specific.
+As an example, for a SWT desktop application, the entry nodes include
+the single main method, UI-accessing nodes include all methods that
+call method \CodeIn{Display.checkWidget} or \CodeIn{Display.checkDevice},
+and safe methods include two SWT helper methods \CodeIn{Display.asyncExec}  and
+\CodeIn{Display.syncExec} for message passing. The detailed instantiation
+for each supported framework is explained in Section~\ref{sec:platforms}.
 
-If the algorithm determines that a UI-accessing method may be invoked
-by a non-UI thread, it creates an error report containing the full
-method call chain from the entry node (line 15, the \CodeIn{createErrorReport}
-method). An example call chain for
-the motivating example in Figure~\ref{fig:androiderror} is shown
-in Figure~\ref{fig:report}.
+For each entry node, the algorithm uses standard Breadth First Search (BFS)
+to find all reachable \CodeIn{Thread.start()} nodes (line 7).
+Each \CodeIn{Thread.start()} node in a call graph indicates that a new,
+non-UI thread is spawned.  After that, from each \CodeIn{Thread.start()}
+node, the algorithm uses BFS again to find reachable UI-accessing methods (lines 9 -- 28).
+Specifically, it uses a queue to keep track of nodes to be visited (line 9),
+and also stores all visited nodes to avoid infinite loop (line 10).
+The algorithm checks every successive node to be visited (line 18);
+it reports an error if that node is a UI-accessing method (lines 20, 21), or skips
+it if it is a safe method (lines 22, 23), or simply keeps traversing otherwise (line 25).
 
-The algorithm in Figure~\ref{fig:detectalgorithm} uses BFS to search
-for potential error-revealing paths. Other graph search strategies
-such as Depath-First Search (DFS) or exhaustive path search can also be
-adapted. In our evaluation, we empirically show that BFS
-is more effective than DFS and exhaustive search in finding errors.
+Note that when the algorithm determines that a UI-accessing method may be invoked
+by a non-UI thread, it computes full method call chain from the entry node to
+the UI-accessing node as the error report.
+The method \CodeIn{createErrorReport} on line 20 does that. 
+As an example, the method call chain for the error in in Figure~\ref{fig:androiderror}
+is shown in Figure~\ref{fig:report}.
 
-Given a sound call graph, our algorithm is sound in that it does not
-miss true positives. We note, however, that computing a sound
-call graph 
-%for partial programs such as an Eclipse plugin, or
-in the presence of reflection is non-trivial. 
-In particular, GUI applications built on some popular frameworks like Android
-often use configuration files and reflection to specify GUI layout.
-%or extension points.
-%Existing call graph construction algorithms suffer from incompleteness
-%, imprecision, or both.  
-To alleviate this problem, we proposed a reflection-aware call graph
-construction algorithm in Section~\ref{sec:cg}.
-
-We also note that a static analysis may report false positives due
-to its conservative nature, or multiple warnings that actually correspond to
-the same error. In addition, some GUI applications may use
-Java native methods to interact with the underlying operating system.
-Native methods are often beyond the ability of a static analysis, but
-should be considered to construct a good call graph. To address the
-above two limitations, we present a set of heuristics to filter
-highly likely false positives and redundant reports, and provide
-annotation support for users to specify call relationships for
- native methods.
+Our algorithm in Figure~\ref{fig:detectalgorithm} uses BFS to search
+for potential error-revealing paths, since BFS permits to produce
+small error reports (i.e., shorter method call chains). However,
+other graph search strategies such as Depath-First Search (DFS) or
+exhaustive path search can also be employed. In our evaluation (Section~\ref{sec:search}),
+we empirically compared different graph search strategies, and demonstrate that
+using BFS allows the algorithm to find more errors than DFS and
+exhaustive path search.
 
 \begin{figure}[t]
-\textbf{\underline{TODO: reformat it using mathit}}\\
-\textbf{Input}: a Java program $P$\\
-\textbf{Output}: a set of potential $errors$\\
-\vspace{-5mm}
+\textbf{Input}: a Java program $\mathit{P}$\\
+\textbf{Output}: a set of potential invalid thread access $\mathit{errors}$\\
+%\textbf{Auxiliary Methods:}\\
+%getSuccNodes($\mathit{g}$, $\mathit{n}$): return node $\mathit{n}$'s successive
+%nodes in the graph $\mathit{g}$\\
+\vspace{-4mm}
 \begin{algorithmic}[1]
-\STATE errors $\leftarrow$ $\emptyset$
-\STATE cg $\leftarrow$ $constructCallGraph$($P$)
-\STATE entryNodes $\leftarrow$ $getEntryNodes$(cg)
-\STATE uiAccessNodes $\leftarrow$ $getUIAccessNodes$(cg)
-\STATE safeNodes $\leftarrow$ $getSafeNodes$(cg)
-\FOR{each entryNode in entryNodes}
-\STATE threadStartNodes $\leftarrow$ $getReachableStartsByBFS$(cg)
-\FOR{each threadStart in threadStartNodes}
-\STATE queue $\leftarrow$ an empty queue
-\STATE queue.enqueue(threadStart.$getAllSuccNodes$())
-\WHILE{queue.isNotEmpty()}
-\STATE nextNode $\leftarrow$ queue.dequeue()
-\FOR{each succNode in cg.$getSuccNodes$(nextNode)}
-\IF{succNode $\in$ uiAccessNodes}
-\STATE errors $\leftarrow$ errors $\cup$ $createErrorReport$(succNode)
-\ELSIF{succNode $\in$ safeNodes}
+\STATE $\mathit{errors}$ $\leftarrow$ $\emptyset$
+\STATE $\mathit{cg}$ $\leftarrow$ constructCallGraph($\mathit{P}$)
+\STATE $\mathit{entryNodes}$ $\leftarrow$ getEntryNodes($\mathit{cg}$)
+\STATE $\mathit{uiAccessNodes}$ $\leftarrow$ getUIAccessNodes($\mathit{cg}$)
+\STATE $\mathit{safeNodes}$ $\leftarrow$ getSafeNodes($\mathit{cg}$)
+\FOR{each $\mathit{entryNode}$ in $\mathit{entryNodes}$}
+\STATE $\mathit{threadStartNodes}$ $\leftarrow$ getReachableStartsByBFS($\mathit{cg}$)
+\FOR{each $\mathit{threadStart}$ in $\mathit{threadStartNodes}$}
+\STATE $\mathit{queue}$ $\leftarrow$ an empty queue\\
+\COMMENT{keep all visited nodes to avoid infinite loop}
+\STATE $\mathit{visited}$ $\leftarrow$ $\emptyset$
+\STATE $\mathit{queue}$.enqueue(getSuccNodes($\mathit{cg}$, $\mathit{threadStart}$))
+\WHILE{$\mathit{queue}$.isNotEmpty()}
+\STATE $\mathit{node}$ $\leftarrow$ $\mathit{queue}$.dequeue()
+\IF{$\mathit{node}$ $\in$ $\mathit{visited}$}
+\STATE continue
+\ENDIF
+\STATE $\mathit{visited}$ $\leftarrow$ $\mathit{visited}$ $\cup$ $\mathit{node}$
+\FOR{each $\mathit{succNode}$ in getSuccNodes($\mathit{cg}$, $\mathit{node}$)}
+\IF{$\mathit{succNode}$ $\in$ $\mathit{uiAccessNodes}$}
+\STATE $\mathit{newError}$ $\leftarrow$ createErrorReport($\mathit{entryNode, succNode}$)
+\STATE $\mathit{errors}$ $\leftarrow$ $\mathit{errors}$ $\cup$ $\mathit{newError}$
+\ELSIF{$\mathit{succNode}$ $\in$ $\mathit{safeNodes}$}
 \STATE continue
 \ELSE
-\STATE queue.enqueue(succNode)
+\STATE $\mathit{queue}$.enqueue($\mathit{succNode}$)
 \ENDIF 
@@
 \caption{Algorithm for detecting invalid thread access errors in multithreaded GUI programs. 
-Any call graph construction algorithm can be used (line 2).
-Three utility methods in lines 3 -- 5 are specific for each GUI framework
+Any call graph construction algorithm can be used (line 2). The algorithm
+is parameterized by the three methods in lines 3--5 which are specific to each GUI framework
  as described in Section~\ref{sec:platforms}.
@@
 \end{figure}
+
+Given a sound call graph, our algorithm is sound in that it does not
+miss true positives. We note, however, that computing a sound
+call graph in the presence of reflection is non-trivial. 
+In particular, GUI applications built on some popular frameworks like Android
+often use configuration files and reflection to specify GUI layout.
+To alleviate this problem, we next proposed a reflection-aware call graph
+construction algorithm in Section~\ref{sec:cg}.
 
@@
 \begin{figure}[t]
-\textbf{\underline{TODO: reformat it using mathit}}\\
-\textbf{Input}: a Java program $P$\\
-\textbf{Output}: a call graph $cg$\\
+\textbf{Input}: a Java program $\mathit{P}$\\
+\textbf{Output}: a call graph $\mathit{cg}$\\
 \vspace{-5mm}
 \begin{algorithmic}[1]
-\FOR{each $statement$ in $P$}
-\IF{$statement$ is a reflection call}
-\STATE objectSet $\leftarrow$ getAllObjectsToCreate($statement$)
-\STATE $newInstr$ $\leftarrow$ createObjectCreationStatement(objectSet)
-\STATE replace $statement$ with $newInstr$
+\FOR{each $\mathit{statement}$ in $\mathit{P}$}
+\IF{isReflectionCall($statement$)}
+\STATE $\mathit{objectSet}$ $\leftarrow$ getAllObjectsThatMaybeCreated($\mathit{statement}$)
+\STATE $\mathit{newStmt}$ $\leftarrow$ createObjectCreationStatement($\mathit{objectSet}$)
+\STATE replace $\mathit{statement}$ with $\mathit{newStmt}$
 \ENDIF
 \ENDFOR
-\STATE $cg$ $\leftarrow$ $constructCallGraph$($P$, callSiteMap)
-\RETURN $cg$
+\STATE $\mathit{cg}$ $\leftarrow$ constructCallGraph($\mathit{P}$)
+\RETURN $\mathit{cg}$
 %\ENDWHILE
@@
 \end{algorithmic}
-\caption{A reflection-aware call graph construction algorithm. Lines 1
-- 7 shows a simple program transformation to replace reflection calls
-with object creations, and line 8 constructs the call graph on
-the transformed program using the existing call graph algorithm. 
+\caption{A reflection-aware call graph construction algorithm. Lines
+1--7 show a simple program transformation to replace reflection calls
+with object creations, and line 8 builds the call graph using
+the existing call graph construction algorithms. This algorithm
+is parameterized by three methods on line 2, 3, and 8. How to
+instantiate it for Android applications is presented in Section~\ref{sec:cg}.
+%This algorithm is parameterized by the call graph construction
+%algorithm on line 8, in which any existing algorithm can be used.
 } 
@@
 Unfortunately, GUI applications often use reflection extensively and make
-existing call graph construction algorithms fail to build a sufficiently complete
-call graph. The example code in Figure~\ref{fig:sampleandroid} from an Android application
+existing call graph construction algorithms such as RTA and k-CFA
+fail to build a sufficiently complete call graph.
+The example code in Figure~\ref{fig:sampleandroid} from an Android application
  illustrates the limitations.
 In Figure~\ref{fig:sampleandroid}, line 6 uses reflection to create a \CodeIn{Button}
-object by looking up its id declared in the XML file. When this button
-is clicked, its event handling code (line 9 -- 11) updates the text.
+object by looking up its id declared in the associated XML file. When this button
+is clicked, its event handling code (lines 9--11) updates the text.
 %d caches
@@
 The basic idea to replace reflection calls with explicit object
-creation instructions, pretending that the corresponding concrete object
+creation statements, pretending that the corresponding concrete object
 has been created.  The algorithm is shown in Figure~\ref{fig:cgalgorithm}.
 It consists of two steps. The first step is a simple program
-transformation to replace reflection calls with object creations, and
-the second step is to use standard call graph construction algorithms
-to construct the graph on the transformed program. Lines 1 - 7 show
+transformation to replace reflection calls with object creation statements, and
+the second step is to use a standard call graph construction algorithm
+to construct the graph on the transformed program. The reflection call
+represents a method invocation that relies Java reflection to create
+objects, such as the \CodeIn{findViewById} method in Android applications.
+In Figure~\ref{fig:cgalgorithm}, lines 1--7 show
 the first step of program transformation. The algorithm iterates through every statement
-in an analyzed program. When it sees a reflection call statement (e.g.,
-the \CodeIn{findViewById} method), the algorithm analyzes the
-program to determine a set of possible classes that may be created.
-After that, the algorithm creates a new instruction which non-deterministically
-returns a new object from the class set. Line 8 is the second step
+in an analyzed program. When it sees a reflection call, the algorithm analyzes the
+program to determine a set of possible classes that might be created.
+After that, the algorithm creates a new statement which non-deterministically
+returns a new object from the object set. Line 8 is the second step
 to build a call graph on the transformed program.  In this step,
 any existing call graph construction algorithms can be used.
-%construction algorithm is independent of the underlying call graph algorithm;
-%any existing algorithm can be used to construct the resulting graph at line 8.
+
+The algorithm in Figure~\ref{fig:cgalgorithm} is parameterized in three places:
+line 2, line 3, and line 8. We instantiated it for Android applications as
+follows. On line 2, the predicate $isReflectionCall$ returns true
+if the $statement$ is a \CodeIn{findViewById(id)} method call. On line 3, method
+\CodeIn{getAllObjectsThatMaybeCreated} parses the associated XML configuration
+file in an Android application to extract the class declaration
+ correspondinig to the \CodeIn{id} value. If the \CodeIn{id}
+value is dynamically generated, the method will conservatively
+return all subclasses of the declared type. On line 8, any existing
+call graph construction algorithm can be used to build the call graph
+on top of the transformed program.
 
@@
 replaces the reflection call: \CodeIn{findViewById(R.id.button\_id)} 
-with an explicit object creation call: \CodeIn{new Button()}.
+with an explicit object creation call: \CodeIn{new Button(null)}.
 After that, the algorithm employs existing call graph construction
@@
 
-Using this reflection-aware call graph construction algorithm is
-critical to detect bugs on realistic GUI applications.
-As demonstrated in our experiments, errors in some Android applications
-can only be detected using this algorithm.
+As demonstrated in our experiments, using this reflection-aware call
+graph construction algorithm is critical to detect errors
+in Android applications.
 
@@
 beyond the ability of a static analysis but should be considered to make
-the call graph more complete. To do so, we provide an annotation \CodeIn{@CallByNativeMethods}
+the call graph more complete. To do so, we provide an annotation \CodeIn{@CalledByNativeMethods}
 for users to specify which native methods may call the current method. For example,
 the following code snippet indicates that native methods \CodeIn{native1()} and \CodeIn{native2()}
-will call method \CodeIn{javaMethod()}.
+may call method \CodeIn{javaMethod()}.
 
 %\noindent 
-\CodeIn{@CallByNativeMethods(callers=\{"native1", "native2"\})}
+\CodeIn{@CalledByNativeMethods(callers=\{"native1", "native2"\})}
 
@@
 Our static analysis takes the call relationship specified by this
-annotation into consideration when traversing the call graph. In our experiment,
-we found such an annotation was useful: one real-world bug can only be reported
-with the user-provided annotations.
+annotation into consideration when traversing the call graph. 
+Adding annotations for native methods is optional and requires manual effort.
+In our experiments, 1 out of 9 programs uses native methods to interact with
+the underlying operating system, and we added 3 annotations for it. We manually
+searched the source files, and inspected the code to determine target methods
+that a native method will call, if there are any. We found this annotation,
+although requires manual effort to add, was useful: one real-world bug
+can only be reported with using the user-provided annotations.
 
@@
 
-A static analysis can exhaustively check possible error path; but may report
-paths that do not actually exist (i.e., false positives) or multiple paths
- that have the same error cause (i.e., redundant warnings). We devise
+A static analysis can exhaustively check possible error paths; but may report
+paths that do not actually exist (false positives) or multiple paths
+ that have the same error cause (redundant warnings). We devise
 5 heuristic filters below to remove likely false positives and redundant warnings.
@@
 \textbf{1. Filter Reports Containing Library Calls}. A
-method call chain involving normal library calls
-like \CodeIn{Object.toString} or \CodeIn{Runtime.shutDown} are unlikely to
-be buggy. In addition, a method call chain that \textit{only}
-consists of library calls after the entry method is also unlikely
-to reveal a valid bug, since it has no UI interaction.
-We encode a list of common library calls, and remove
-a reported warning if it contains one of them.
+method call chain containing certain library calls
+like \CodeIn{Runtime.}\CodeIn{shutDown} are unlikely to
+be buggy. For example, the \CodeIn{Runtime.}\CodeIn{shutDown}
+method is called when JVM terminates, and uses multithreading
+to dispose all GUI objects after the program exits.
+We encoded a list of common library calls by proposing
+a basic set of library calls that seemed natural and
+generally applicable, based on our programming experience.
+We later added other calls we found helpful in analyzing
+programs and that we believed would be generally useful.
+%We encode a list of common library calls, and remove
+%a reported warning if it contains one of them.
 %Method call chain involves typical
@@
 \textbf{2. Filter Reports With User-Annotated Methods}. Besides general
-library calls, users are also permitted
-to explicitly annotate methods that will never trigger an error.
+library calls, users are also permitted to explicitly annotate methods
+that will never trigger an error.
 For example, the Android GUI framework provides a utility method 
@@
 Thus, a reported method call chain containing an annotated 
-can be safely removed.
-%method will never cause an
-%invalid thread error and should be removed.
+can be safely removed. We produced the list of annotated methods
+during analyzing programs on different GUI frameworks; we did this
+only between experiments rather than biasing experiments by tuning
+our tool to specific programs.
 
@@
 both lead to a potential error, since $\CodeIn{d()}$ and \CodeIn{a()}
-are two separated entry methods. The second call chain should
+are two distinct entry methods. The second call chain should
 be removed and would not reduce the error detection capability, since
@@
 This filter compares two reported chains that have the same
-$k$ ($k$ is user-settable with a default value 5) head nodes, and removes the longer one.
+$k$ ($k$ is user-settable with a default value 5 as used in our
+experiments) head nodes, and removes the longer one.
 
@@
 two reported method call chains that share the same 
-$k$ ($k$ is user-settable with a default value 5) tail nodes, and removes the longer one.
+$k$ ($k$ is user-settable with a default value 5 as used in our
+experiments) tail nodes, and removes the longer one.
 
@@
 
-We instantiate our error detection techniques for four popular GUI frameworks,
+We instantiated our error detection techniques for four popular GUI frameworks,
 namely SWT, Eclipse plugin environment, Swing, and Android.
 The major framework-specific parts, corresponding to
-lines 3 -- 5 in Figure~\ref{fig:detectalgorithm}, are to identify
-\textbf{call graph entry nodes}), \textbf{UI-accessing nodes},
+lines 3 -- 5 in Figure~\ref{fig:detectalgorithm}, are identifying
+\textbf{call graph entry nodes}, \textbf{UI-accessing nodes},
 and \textbf{safe methods} for each framework.
@@
 %on which it is implemented.
-Like a normal Java program, a SWT desktop application
-has a single main method as the entry point. By default,
-the main method is executed in the UI thread after the GUI
-is initialized. We instantiate our technique for SWT applications as follows:
+ We instantiate our technique for SWT applications as follows:
 
@@
 
-\item \textbf{Call graph entry nodes: } the main method
+\item \textbf{Call graph entry nodes: } the main method. Like a normal Java program,
+a SWT desktop application has a single main method as the entry point. By default,
+the main method is executed in the UI thread after the GUI
+is initialized.
 
@@
 thread is the UI thread or not.
-Thus, we treat nodes corresponding to the methods
+Thus, we treat nodes (in both user code and framework code) corresponding to the methods
 calling these two methods as UI-accessing nodes.
@@
 \item \textbf{Safe methods: } SWT provides two helper methods (\CodeIn{Display.\\asyncExec}
-and \CodeIn{Display.syncExec}) to execute code (a)synchronizedly on the UI thread.
+and \CodeIn{Display.syncExec}) to execute code (a)synchro-
+nizedly on the UI thread.
  We treat these two methods as safe methods, since invoking
@@
 %are generally considered to be safe and
-would not cause an invalid thread access error.
+will not cause an invalid thread access error.
 
@@
 
-%An eclipse plugin is an open program. 
-An Eclipse plugin is built on top of the SWT framework.
-However, unlike a SWT desktop application, an Eclipse plugin does not
-have a main method as a single program entry point. Instead, it extends
-extension points provided by the Eclispe framework to implement
-functionalities. When a plugin starts, Eclipse
-calls back the overridden extension points to handle the
-upcoming events. We customize our technique for Eclipse plugin as follows:
+We instantiated our technique for Eclipse plugin as follows:
 
@@
 \item \textbf{Call graph entry nodes: } all overridden SWT
-GUI event handling methods are called from the UI thread.
-We treat these callback methods as the entry nodes.
-
-%due to the complexity of the eclipse
-%architecture,
-%there is no rigorous way in eclipse to identify a UI thread. Here, we use a heuristic to determine call graph
-%entry nodes from the UI thread. As a naming convention, source code in a plugin's \CodeIn{ui}
-%package deals with the creation and maintainance of a plugin's GUI, and is thus
-%invoked by the UI thread. We conservatively treat all public methods in the \CodeIn{ui}
-%as call graph entry nodes.
-
-%entry nodesall overriden methods of the classes inside
-% a plugin's \CodeIn{ui} package.  Such methods are normally called by the eclipse framework
-%by the UI thread. XXX This rule, though quite , works quite well in practice.
+GUI event handling methods in user code. An Eclipse plugin is built
+on top of the SWT framework. However, unlike a SWT desktop application,
+an Eclipse plugin does not have a main method as a single program entry point.
+Instead, it extends extension points provided by the Eclispe framework to
+implement functionalities. When a plugin starts, Eclipse
+calls back the overridden extension points to handle the
+upcoming events. All SWT GUI event handling methods (i.e., the overriden
+methods in the class that implements \CodeIn{org.eclipse.swt.internal.\\SWTEventListener}) are
+called back from the UI thread, thus are used as call graph entry nodes.
 
@@
 
-%The collections classes from the original JDK (\CodeIn{Vector}
-%and \CodeIn{Hashtable}) and the AWT library are designed as
-%thread-safe. That is, two separate threads of execution can
-%access the UI element at the same time without the developer having
-%to worry about the threads interfering with one another. However, the
-%safety comes at a cost. Because there is a great deal of overhead
-%necessary to build thread-safe artifacts, the tend to be much slower
-%than nonthread-safe alternatives.
-
-%The design decisions for Swing changed. This does not mean the controls
-%can never be accessed from multiple threads, but the developer is now
-%responsible for adding code to ensure that no ill effects occur.
-
 A Swing application has a single main method, but contains three kinds of
@@
 of the application and starts to execute all event-handling code or spawns new worker threads. 
-We customized our technique for Swing as follows:
+We instantiated our technique for Swing as follows:
 %XXXX Therefore, we can not directly
@@
 
-\item \textbf{Call graph entry nodes: } all overridden callback methods in 
-Swing's UI listener classes are called from the UI thread. We treat those callback
-methods as the entry nodes.
-
-%Specifically, for each class, we check whether
-%it is a Swing listener class. If so, we extract all its overridden callback methods as the call graph entry points.
- %Such methods are normally called by the eclipse framework
-%by the UI thread. XXX This rule, though quite heuristical, works quite well in practice.
+\item \textbf{Call graph entry nodes:} all overridden Swing GUI event handling
+methods in user code. Those event handling methods are always
+called back from the UI thread, thus are used as call graph entry nodes.
 
 \item \textbf{UI-accessing nodes:} %as stated in Swing's documentation,
-methods in Swing GUI classes are not thread safe with three exceptions (\CodeIn{repaint()},
-\CodeIn{revalidate()}, and \CodeIn{invalidate()}). Thus, we
-treat nodes corresponding to those thread unsafe methods %in each GUI class
-as UI-accessing nodes.
+all methods defined in each Swing GUI class except for three thread-safe
+methods: \CodeIn{repaint()}, \CodeIn{revalidate()}, and \CodeIn{invalidate()}.
 
-\item \textbf{Safe methods: }  Swing provides two helper methods
-(\CodeIn{SwingUti-\\lities.invokeLater} and \CodeIn{SwingUtilities.invokeAndWait}) to execute code in the UI thread.
-We treat these two methods as safe methods.
+%methods in Swing GUI classes are not thread safe with three exceptions (\CodeIn{repaint()},
+%\CodeIn{revalidate()}, and \CodeIn{invalidate()}). Thus, we
+%treat nodes corresponding to those thread unsafe methods %in each GUI class
+%as UI-accessing nodes.
+
+\item \textbf{Safe methods: }  Swing's two helper methods
+(\CodeIn{SwingUtilities.} \CodeIn{invokeLater} and \CodeIn{SwingUtilities.invokeAndWait}) that execute code in the UI thread.
 
 \end{itemize}
-
-%A key tasks in instantiating
-%our technique to the Swing framework is to identify its event dispatch thread.
-%We use
 
@@
 Android is a Java-based platform for embedded or mobile devices. 
-%Android features an extended event-based library and dynamic inflation of
-%graphical views from declarative XML layout files.
-Android applications are written in Java, running in their own process within their own virtual machine.
 An Android program does not have a single entry point but can
@@
 as code interacting with the user through a visual interface. GUI event handlers
-are handled in an activity  in no particular ordering.
-We instantiate our technique for Android programs as follows:
+are handled in an activity.
+We instantiated our technique for Android programs as follows:
 %, with some notable exceptions such as the
@@
 
-\item \textbf{Call graph entry nodes: } in an Android application,
-an \CodeIn{Activity} object is created and manipulated by the UI thread. We treat
-all public methods from an \CodeIn{Activity} class as call graph entry nodes.
-We also add all overridden callback methods in event listener classes as entry nodes.
+\item \textbf{Call graph entry nodes: }in an Android application,
+an \CodeIn{Activity} object is created and manipulated by the UI thread. Thus, we treat
+all public methods defined in the \CodeIn{Activity} class 
+and any class in the user code that subclasses \CodeIn{Activity} as call graph entry nodes.
+We also add all overridden Android GUI event handling methods in user
+code as entry nodes, since they must be called back from the UI thread.
 
-\item \textbf{UI-accessing nodes: } like SWT, Android explicitly checks whether
+\item \textbf{UI-accessing nodes: }every method calling \CodeIn{ViewRoot.checkThread}.
+Like SWT, Android explicitly checks whether
 the current thread is a UI thread or not before accessing a GUI object via
 the \CodeIn{ViewRoot.checkThread} method.
-Thus, we treat every methods calling \CodeIn{ViewRoot.checkThread} as a UI-accessing node
-in the call graph.
+Thus, we treat 
 %method. This method is the only place where Android checks
@@
 
-\item \textbf{Safe methods: } Android provides two helper methods (\CodeIn{View.post}
-and \CodeIn{View.postDelay}) to execute code on the UI thread. Thus, we treat
-these two methods as safe methods.
-%, since invoking them on any thread
-%would not cause an invalid thread access error.
+\item \textbf{Safe methods: } two helper methods (\CodeIn{View.post}
+and \CodeIn{View.postDelay}) that execute code on the UI thread. 
+Invoking them on any thread will not cause an invalid thread access error.
 %Invoking these two methods are generally considered to be safe, and would not
@@
 
-In our experience, instantiating our general technique to  a specific framework
+Instantiating our general technique to  a specific framework
 requires moderate human effort. We wrote around 500 lines of Java code in total to achieve

### 2012-02-01 trunk/GUIErrorDetector/paper/conclusion.tex
significant revise

@@
 In this paper, we presented a general technique to find invalid
-thread access errors in multithreaded GUI applications. 
+thread access errors for multithreaded GUI applications. 
 Our technique statically explores paths in a call graph to check
 whether a non-UI thread can access a GUI object.
-It uses a combined RTA and k-CFA algorithm to construct
-a good call graph, and employs a set of heuristics to
-filter likely false positives and redundant reports.
+It uses a reflection-aware call graph construction algorithm
+to build a good call graph, and employs a set of heuristics to
+filter likely false positives and redundant warnings.
 Since graphical user interfaces are often inadequately tested due
@@
 more potential errors %before the application is released to customers (XXX),
-and thus encourage GUI developers to improve software reliability.
-
-We have demonstrated that our technique can be both practical and useful
-by an evaluation on XXX subjects acrosss 4 popular GUI
-frameworks. Our experiments have shown that we can find bugs
-in real-world programs.
+ to improve software reliability.
+We have also demonstrated that our technique can be useful
+by an evaluation on 9 subjects acrosss 4 popular GUI
+frameworks. 
+%Our experiments have shown that we can find bugs
+%in real-world programs.
 
@@
 
-\begin{itemize}
+%\begin{itemize}
+%\item
+\textbf{Integration with dynamic and symbolic analyses.} The technique 
+presented in this paper is a call graph-based, pure static analysis. 
+It may suffer from false positives for many GUI applications,
+due to the conservative nature of static analysis.
+A possible way to reduce the number of false
+positives is to integrate with
+dynamic analyses~\cite{Jiang:2008:PPS:1453101.1453110}%, ZhangSBE2011}
+or symbolic analyses~\cite{xie05:symstra, Pasareanu:2011, halfond09issta, BMF97}
+by using more accurate information to guide call graph exploration.
 
-\item \textbf{Integration with dynamic and symbolic analyses.} The technique 
-presented in this paper is a pure static analysis. It
-uses a combined RTA and k-CFA  algorithm to construct a relatively
-complete and precise call graph. However, our technique still suffers from
-a false positive rate for many GUI applications, due to the conservative
-nature of static analysis. A possible way to reduce such false
-positives is to integrate the current static analysis with
-dynamic analyses~\cite{Jiang:2008:PPS:1453101.1453110, ZhangSBE2011}
-or symbolic analyses~\cite{xie05:symstra, Pasareanu:2011, halfond09issta, BMF97}
-by employing more accurate information to guide call graph exploration.
-
-\item \textbf{Unit testing multithreaded GUI programs.} Besides
+%\item
+\textbf{Unit testing multithreaded GUI programs.} Besides
 a static analysis,  software testing is another
 way to improve software quality.  Although many
-GUI testing techniques have been developed recently, few of them can be applied
+testing techniques have been developed recently, few of them can be applied
 to unit test multithreaded GUI programs to find potential errors \textit{earlier}. We
-are interested to investigate how to apply recent advance in automated
-software testing~\cite{Staats:2011:PTO:1985793.1985847, Jagannath:2011:IMU:2025113.2025145, Muccini_Bertolino_Inverardi_2004, Ricca:2001:ATW:381473.381476, Harman:2007}
+plan to investigate how to apply recent advance in automated
+testing~\cite{Staats:2011:PTO:1985793.1985847, Jagannath:2011:IMU:2025113.2025145, Muccini_Bertolino_Inverardi_2004, Ricca:2001:ATW:381473.381476, Harman:2007}
 to the context of multithreaded GUI applications.
 
-\item \textbf{Fixing potential GUI errors.} After a potential error is revealed, fixing
+%\item
+\textbf{Fixing potential GUI errors.} After an error is revealed, fixing
 it and verifing the patch has often been another important and time-consuming process. Fixing concurrency
@@
 on automatically repairing test script for GUI applications~\cite{Daniel:2011:AGR:2002931.2002937, Huang:2010:RGT:1828417.1828465}. However, none of them focuses on repairing
-the GUI program to fix a revealed bug. Thus, we are interested in 
+the GUI program to patch a revealed error. Thus, we are interested in 
 developing automated error fixing techniques for

### 2012-02-01 trunk/GUIErrorDetector/paper/implementation.tex
significant revise

@@
 Our current implementation supports four widely-used GUI frameworks, namely
-SWT, Eclipse plugin development, Java Swing, and Android, including
-dependent libraries such as \CodeIn{rt.jar} and \CodeIn{android.jar}.
-into analysis. We implemented the reflection-aware call graph construction
- algorithm (Section~\ref{sec:cg})
-using WALA's \textit{bypass logic}. Our tool parses the configuration file
-in an Android application and modifies the bytecode to replace all
-reflection calls with object creation instructions.
+SWT, Eclipse plugin development, Swing, and Android.
+%, including dependent libraries such as \CodeIn{rt.jar} and \CodeIn{android.jar}.
+%into analysis. 
+We implemented the reflection-aware call graph construction
+ algorithm (Section~\ref{sec:cg}) using WALA's \textit{bypass logic}.
+Our tool does not requires a separated pass of program transformation; it
+first parses the configuration file in an Android application,
+and then intercepts the call graph construction
+process on-the-fly to replace all reflection calls with object creation statements.
 Since Android applications are often fully encrypted and shipped in Dalvik

### 2012-02-01 trunk/GUIErrorDetector/paper/introduction.tex
significant revise

@@
 \begin{alltt}
-
    org.mozilla.gecko.gfx.LayerView.<init>(Context;LayerController)
@@
    ... 
+-> android.view.ViewRoot.recomputeViewAttributes(View;)
 -> android.view.ViewRoot.checkThread()
@@
 \end{CodeOut}
+%\hspace{5mm}\CodeIn{\scriptsize{org.mozilla.gecko.gfx.LayerView.<init>(Context;LayerController)}}\\
+%$\rightarrow$\CodeIn{ \scriptsize{android.opengl.GLSurfaceView.setRenderer(GLSurfaceView\$Renderer;)}}\\
+%$\rightarrow$\CodeIn{ \scriptsize{java.lang.Thread.start()}}\\
+%$\rightarrow$\CodeIn{ \scriptsize{android.opengl.GLSurfaceView\$GLThread.run()}}\\
+%$\rightarrow$\CodeIn{ \scriptsize{android.opengl.GLSurfaceView\$GLThread.guardedRun()}}\\
+%$\rightarrow$\CodeIn{ \scriptsize{org.mozilla.gecko.gfx.LayerRenderer.onSurfaceChanged(GL10;II)}}\\
+%$\rightarrow$\CodeIn{ \scriptsize{org.mozilla.gecko.gfx.LayerView.setViewportSize(IntSize;)}}\\
+%\hspace{5mm}\CodeIn{...}\\
+%$\rightarrow$\CodeIn{ \scriptsize{android.view.ViewRoot.checkThread()}}
 \vspace*{-2.0ex} \Caption{{\label{fig:report} A report
@@
 event dispatching thread before accessing a GUI object.
-\CodeIn{\small{...}} represents the other 9 method calls that are omitted for brevity.
+8 more methods in the call chain, shown as
+\CodeIn{\small{...}} above, are omitted for brevity.
 }} %\vspace{-5mm}
@@
 Our tool works in a fully automatic, push-button manner, and scales to realistic programs.
-We evaluated our implementation on 9 subjects comprising over 67000 LOC.
+We evaluated our implementation on 9 subjects comprising over 76000 LOC.
 The experiment results demonstrate
@@
 \item \textbf{Evaluation.} We performed an experiment on 9 subjects
-from 4 different frameworks, comprising over 67000 LOC. The results
+from 4 different frameworks, comprising over 76000 LOC. The results
 show the usefulness of the proposed technique (Section~\ref{sec:evaluation}).

### 2012-02-01 trunk/GUIErrorDetector/paper/related.tex
significant revise

@@
 
-Work related to this paper falls into two main categories; (1)
-techniques and tools to analyze and test GUI programs; and (2)
-bug finding techniques for general multithreaded programs.
+Work related to this paper falls into three main categories; (1)
+techniques and tools to analyze and test GUI programs; (2)
+bug finding techniques for general multithreaded programs; and (3)
+call graph construction algorithms.
 
@@
 some aspect(s) of GUI testing including model creation
-(for model-based testing)~\cite{androidtesting, Xie:2006:MTC:1172962.1172990},
-test-case generation~\cite{YuanCohenMemonTSE2011, YuanMemonICSE2007},
+(for model-based testing)~\cite{androidtesting}, %, Xie:2006:MTC:1172962.1172990},
+test generation~\cite{YuanCohenMemonTSE2011, YuanMemonICSE2007},
 test oracle creation~\cite{MemonFSE2000}, test execution~\cite{MemonFSE2001},
@@
 For example,
-Kervinen et al.~\cite{Kervinen06model-basedtesting} present a formal model and architecture for testing
-concurrently running applications. The behavior of the system under test
-needs to be specified manually as a labeled transition system. 
-Guitar~\cite{YuanCohenMemonTSE2011, YuanMemonICSE2007, Xie:2006:MTC:1172962.1172990}
+%Kervinen et al.~\cite{Kervinen06model-basedtesting} present a formal model and architecture for testing
+%concurrently running applications. The behavior of the system under test
+%needs to be specified manually as a labeled transition system. 
+Guitar~\cite{YuanCohenMemonTSE2011, YuanMemonICSE2007}%, Xie:2006:MTC:1172962.1172990}
 is a GUI testing framework for Java and Microsoft Windows applications. 
 Yuan and Memon~\cite{YuanMemonICSE2007} generate event-sequence based test cases for GUI
-programs. They proposed a model-based approach for testing GUI-based applications.
-Their technique can generate test cases automatically using a structural event
+programs. Their model-based approach can generate test cases automatically using a structural event
 generation graph. 
-%Their approach targets Java desktop applications, which
-%are quite different from the Android mobile environment (XXXX).
-However, testing is often insufficient to ensure the correctness of a GUI program
+However, testing is often insufficient to detect many potential
+errors in a GUI application
 due to the huge space of possible interactions
 with a GUI. The large number of possible interactions
-result in a large number of
-test inputs requiring substantile human effort.
-The second
-problem is to determine the coverage of a set of test
-cases~\cite{MemonFSE2001}. For conventional software, coverage is measured
-using the amount and type of underlying code exercised.
-These measures do not work well for GUI testing, because
-what matters is not only how much of the code is tested,
-but in how many different possible states of the software
-each piece of code is tested. This makes it hard to determine
-the completeness of a test suite. %All of the (XXXXX, so that GUI is often not well tested)
-In contrast, as advocated in this paper, the primary advantage of
-using a static analysis is that it can potentially explore
-all paths to find possible bugs without actually executing the tested code. % (XXX use heuristic filtering)
+need a large number of test inputs that require substantile human effort.
+%The second problem is to determine the coverage of a set of test
+%cases~\cite{MemonFSE2001}. For conventional software, coverage is measured
+%using the amount and type of underlying code exercised.
+%These measures do not work well for GUI testing, because
+%what matters is not only how much of the code is tested,
+%but in how many different possible states of the software
+%each piece of code is tested. This makes it hard to determine
+%the completeness of a test suite. 
+In contrast, as suggested in this paper,
+using a static analysis can potentially explore
+all paths to find potential errors without actually executing the tested code. 
 Compared with software testing, a static analysis tool may
-report false positives due to its conservative nature.
+report false positives and redundant warnings due to its conservative nature.
 Nevertheless, as we demonstrated in our experiments, using a few simple heuristics
-can dramatically reduce the number of false positives  to
+can dramatically reduce the number of false positives and redundant warnings to
 an acceptable level.
@@
 a user attempts an action that has led to problems in the past. 
-As a comparison, our work aims to find unknown errors in a multithreaded
+As a comparison, our work aims to find unknown errors in multithreaded
 GUI applications, while their work aims to prevent an existing bug
@@
 errors, and uses a quite different abstraction than ours.
-To the best of our knowledge, we are the first to identify the invalid
-thread access problem on multithreaded GUI applications, and
-our technique is a general one that is specifically designed to detect
-the invalid thread access errors.
+To the best of our knowledge, we are the first to address the invalid
+thread access error detection problem for multithreaded GUI applications, and
+our core technique is a general one that can be tailored for
+various GUI frameworks.
+
+%is specifically designed to detect
+%the invalid thread access errors.
 
@@
 A rich body of techniques have been developed to detect bugs in multithreaded programs~\cite{Huang:2011:PPC:2001420.2001438, Weeratunge:2010, Huang:2011:EST}.
-Active testing frameworks like AssertFuzzer~\cite{Sen:2008} uses the trace information to detect
-and create atomicity schedule violations. Static analysis tools such as Chord~\cite{Naik:2006}
- explore multithreaded bugs by statically analyzing the program. On the
-other hand, runtime analysis tools such as Eraser~\cite{Savage:1997}  dynamically detect concurrency bugs using the lockset
-algorithms or some criteria based automata. Bodden and Havelund~\cite{Bodden:2008} uses AOP for
-race detection by providing three novel pointcuts to the AspectJ language. More recently,
-Goldilock~\cite{Elmas:2007} uses the hybrid model that combines the happens-before and lock-based
+%Active testing frameworks like AssertFuzzer~\cite{Sen:2008} uses the trace information to detect
+%and create atomicity schedule violations.
+Static analysis tools such as Chord~\cite{Naik:2006}
+ explore multithreaded bugs by statically analyzing the program. Runtime
+analysis tools such as Eraser~\cite{Savage:1997}  dynamically detect concurrency bugs using the lockset
+algorithms or some criteria based automata. 
+%Bodden and Havelund~\cite{Bodden:2008} uses AOP for
+%race detection by providing three novel pointcuts to the AspectJ language.
+More recently, Goldilock~\cite{Elmas:2007} uses the hybrid model that combines the happens-before and lock-based
 approaches to identify data races based on an execution. By exploiting the insight
@@
 relation to efficiently and precisely detect races at runtime. However, finding
-invalid thread errors is quite different than detecting data races in
+invalid thread access errors is quite different than detecting data races in
 a multithreaded program. A data race occurs when two concurrent threads access
@@
 reference and verify that consistent locking behavior is observed among different threads. Instead,
-our technique only needs to track whether a non-UI thread can reach a GUI object or not.
-How to adapt existing data race detection approaches to 
+our technique only needs to track whether a non-UI thread can reach a GUI object or not,
+and is much cheaper.
+How to leverage the recent advance in data race detection to 
 improve our technique is one of our future work.
@@
 CHESS~\cite{chess} dynamically explores the thread scheduling decisions to expose
-concurrency bugs using a context-bounded approach. Shacham et al~\cite{Shacham:2007} uses
-a model checker to construct the witness for data races reported by the lockset algorithm.
-%(XXXX problem for applying to GUI).
+concurrency bugs using a context-bounded approach. 
+%Shacham et al~\cite{Shacham:2007} uses
+%a model checker to construct the witness for data races reported by the lockset algorithm.
 Unfortunately, due to the exponential size of the search space,
@@
 we are not aware of any software model checking approach can scale to the subjects
-as large as those used in our experiments. Compared with model checking, the static analysis
+as large as those used in our experiments (including the library code). Compared with model checking, the static analysis
 algorithm presented in this paper chooses call graph as the
-abstraction level with a set of heuristics, and thus is much lightweighted. It is highly tailored to find the invalid thread
-access errors instead of being a general property checking tool. For this reason,
-our technique achieves good scalability with reasonable precision.
+abstraction level with a set of heuristics, and thus achieves good
+scalability with reasonable precision. It is specifically designed to find invalid thread
+access errors instead of being a general property checking tool.
+
+%For this reason,
+%our technique achieves good scalability with reasonable precision.
+
+\subsection{Call Graph Construction Algorithms}
+
+A lot of effort has been spent on analyzing function pointers in C
+as well as virtual method calls in C++ and Java ~\cite{rta, kcfa,
+xta, inccg, Sundaresan:2000, Might:2010}.
+We briefly mention some of the highlights of call graph construction
+algorithms for Java here. Grove et al~\cite{kcfa} described a unified
+framework for expressing call graph construction algorithms, and
+performed a quantitative study comparing different instantiations
+of the framework. Tip and Palsberg~\cite{xta} quantitatively compared
+several low-cost call graph construction algorithms for Java.
+Sundaresan et al.~\cite{Sundaresan:2000} went beyond the tranditional
+CHA and RTA~\cite{rta} approaches in Java and and used type propagation
+for the purpose of obtaining a more precise call graph.
+However, the heavy use of reflection in some GUI applications make
+those algorithms insufficient to build a good call graph.
+As reflected in our experiments, using standard call graph algorithms
+such as RTA, 0-CFA, and 1-CFA fails to find UI-specific errors in
+Android applications, due to the incompleteness of the resulting graph.
+
+To enable call graph conostruction in the presence of  reflection,
+Livshits et al.~\cite{Livshits:2005} presented a static analysis
+that attempts to infer additional information about
+reflective call sites directly from program code. The analysis
+attempts to use information stored in string constants to resolve
+reflective calls statically. Their approach focuses on standard Java
+reflection library calls (e.g., \CodeIn{java.lang.Class.forName}) but not on
+framework-specific ones (e.g., \CodeIn{android.view.View.findViewById}).
+The WALA framework implements a similar approach to handle Java
+reflections, but still fails to build a sufficiently complete call graph for
+Android applications. TamiFlex~\cite{Bodden:2011}, a pure dynamic
+approach, dumps all reflectively-created class instances to a file
+by intercepting JVM system calls, and re-inserts those recorded 
+class into a program. However, TamiFlex requires a set of representative
+program executions which may not be available in practice,
+ and is only sound with respect to the recorded executions.
+Perphas the most close work to our reflection-aware call graph
+construction algorithm is Payet and Spoto's Julia
+system~\cite{Payet:2011:SAA:2032266.2032299}, which is independently
+proposed with our algorithm. One difference is that the Julia system
+requires to instrument the code of Android's library class
+\CodeIn{android.view.LayoutInflater} that performs the XML inflation ahead of time,
+then replaces the \CodeIn{findViewById} call with with a
+non-deterministic execution of new statements.
+In constrast, our algorithm leverages the powerful \textit{Bypass logic}
+in the WALA framework to transform the program on-the-fly when
+constructing the call graph, without requiring a separate pass of
+off-line instrumentation.
+
+%There are few algorithms have been studied to construct call
+%A recent paper by Hirzel, Diwan, and Hind addresses the issues of dynamic
+%class loading, native methods, and reflection in order to deal with the full complexity
+%of Java in the implementation of a common pointer analysis [5]. Their
+%approach involves converting the pointer analysis [6] into an online algorithm:
+%they add constraints between analysis nodes as they are discovered at runtime.
+%Newly generated constraints cause re-computation and the results are propagated
+%to analysis clients such as a method inliner and a garbage collector at
+%runtime. Their approach leverages the class hierarchy analysis (CHA) to update
+%the call graph. Our technique uses a more precise pointer analysis-based
+%approach to call graph construction.

### 2012-02-01 trunk/GUIErrorDetector/paper/technique.tex
significant revise

@@
 
-Our algorithm in Figure~\ref{fig:detectalgorithm} works as follows. It
+Our algorithm in Figure~\ref{fig:detectalgorithm} %works as follows. It
 first constructs a static call graph for the tested program (line 2),
-then specifies entry nodes for it (line 3). The algorithm starts to traverse
-the call graph from every entry node (line 6). For every entry node,
-it first uses Breadth First Search (BFS) to find all reachable
-\CodeIn{Thread.start()} calls (line 7). Each \CodeIn{Thread.start()} call
-indicates that a new, non-UI thread is spawned.  After that, 
-the algorithm uses a BFS to find reachable UI-accessing methods (lines 9 -- 23)
-from each \CodeIn{Thread.start()} node.
-Specifically, it uses a queue to keep track of all visited nodes, and
-then checks every successive node to be visited (line 12);
-it reports an error if that node
-is a UI-accessing method (line 15), or skips it if it is
-a safe method (line 17), or simply keeps traversing otherwise (line 19).
+then specifies entry nodes, UI-accessing nodes, and safe nodes
+for it on line 3, 4, and 5, respectively. Lines 3--5 are GUI framework-specific.
+As an example, for a SWT desktop application, the entry nodes include
+the single main method, UI-accessing nodes include all methods that
+call method \CodeIn{Display.checkWidget} or \CodeIn{Display.checkDevice},
+and safe methods include two SWT helper methods \CodeIn{Display.asyncExec}  and
+\CodeIn{Display.syncExec} for message passing. The detailed instantiation
+for each supported framework is explained in Section~\ref{sec:platforms}.
 
-If the algorithm determines that a UI-accessing method may be invoked
-by a non-UI thread, it creates an error report containing the full
-method call chain from the entry node (line 15, the \CodeIn{createErrorReport}
-method). An example call chain for
-the motivating example in Figure~\ref{fig:androiderror} is shown
-in Figure~\ref{fig:report}.
+For each entry node, the algorithm uses standard Breadth First Search (BFS)
+to find all reachable \CodeIn{Thread.start()} nodes (line 7).
+Each \CodeIn{Thread.start()} node in a call graph indicates that a new,
+non-UI thread is spawned.  After that, from each \CodeIn{Thread.start()}
+node, the algorithm uses BFS again to find reachable UI-accessing methods (lines 9 -- 28).
+Specifically, it uses a queue to keep track of nodes to be visited (line 9),
+and stores all visited nodes to avoid infinite loop (line 10).
+The algorithm checks every successive node to be visited (line 18);
+it reports an error if that node is a UI-accessing method (lines 20, 21), or skips
+it if it is a safe method (lines 22, 23), or simply keeps traversing otherwise (line 25).
 
-The algorithm in Figure~\ref{fig:detectalgorithm} uses BFS to search
-for potential error-revealing paths. Other graph search strategies
-such as Depath-First Search (DFS) or exhaustive path search can also be
-adapted. In our evaluation, we empirically show that BFS
-is more effective than DFS and exhaustive search in finding errors.
-
-Given a sound call graph, our algorithm is sound in that it does not
-miss true positives. We note, however, that computing a sound
-call graph 
-%for partial programs such as an Eclipse plugin, or
-in the presence of reflection is non-trivial. 
-In particular, GUI applications built on some popular frameworks like Android
-often use configuration files and reflection to specify GUI layout.
-%or extension points.
-%Existing call graph construction algorithms suffer from incompleteness
-%, imprecision, or both.  
-To alleviate this problem, we proposed a reflection-aware call graph
-construction algorithm in Section~\ref{sec:cg}.
-
-We also note that a static analysis may report false positives due
-to its conservative nature, or multiple warnings that actually correspond to
-the same error. In addition, some GUI applications may use
-Java native methods to interact with the underlying operating system.
-Native methods are often beyond the ability of a static analysis, but
-should be considered to construct a good call graph. To address the
-above two limitations, we present a set of heuristics to filter
-highly likely false positives and redundant reports, and provide
-annotation support for users to specify call relationships for
- native methods.
+Note that when the algorithm determines that a UI-accessing method may be invoked
+by a non-UI thread, it computes a method call chain from the entry node to
+the UI-accessing node as the error report.
+The method \CodeIn{createErrorReport} on line 20 does that. 
+Figure~\ref{fig:androiderror} shows a method call chain from the entry
+node \CodeIn{LayerView.<init>} to the UI-accessing node \CodeIn{ViewRoot}.\CodeIn{recomputeViewAttributes}
+(for the sake of clarification, we also show the checking method \CodeIn{checkThread} in the reported warning).
 
 \begin{figure}[t]
-\textbf{\underline{TODO: reformat it using mathit}}\\
-\textbf{Input}: a Java program $P$\\
-\textbf{Output}: a set of potential $errors$\\
-\vspace{-5mm}
+\textbf{Input}: a Java program $\mathit{P}$\\
+\textbf{Output}: a set of potential invalid thread access $\mathit{errors}$\\
+%\textbf{Auxiliary Methods:}\\
+%getSuccNodes($\mathit{g}$, $\mathit{n}$): return node $\mathit{n}$'s successive
+%nodes in the graph $\mathit{g}$\\
+\vspace{-4mm}
 \begin{algorithmic}[1]
-\STATE errors $\leftarrow$ $\emptyset$
-\STATE cg $\leftarrow$ $constructCallGraph$($P$)
-\STATE entryNodes $\leftarrow$ $getEntryNodes$(cg)
-\STATE uiAccessNodes $\leftarrow$ $getUIAccessNodes$(cg)
-\STATE safeNodes $\leftarrow$ $getSafeNodes$(cg)
-\FOR{each entryNode in entryNodes}
-\STATE threadStartNodes $\leftarrow$ $getReachableStartsByBFS$(cg)
-\FOR{each threadStart in threadStartNodes}
-\STATE queue $\leftarrow$ an empty queue
-\STATE queue.enqueue(threadStart.$getAllSuccNodes$())
-\WHILE{queue.isNotEmpty()}
-\STATE nextNode $\leftarrow$ queue.dequeue()
-\FOR{each succNode in cg.$getSuccNodes$(nextNode)}
-\IF{succNode $\in$ uiAccessNodes}
-\STATE errors $\leftarrow$ errors $\cup$ $createErrorReport$(succNode)
-\ELSIF{succNode $\in$ safeNodes}
+\STATE $\mathit{errors}$ $\leftarrow$ $\emptyset$
+\STATE $\mathit{cg}$ $\leftarrow$ constructCallGraph($\mathit{P}$)
+\STATE $\mathit{entryNodes}$ $\leftarrow$ getEntryNodes($\mathit{cg}$)
+\STATE $\mathit{uiAccessNodes}$ $\leftarrow$ getUIAccessNodes($\mathit{cg}$)
+\STATE $\mathit{safeNodes}$ $\leftarrow$ getSafeNodes($\mathit{cg}$)
+\FOR{each $\mathit{entryNode}$ in $\mathit{entryNodes}$}
+\STATE $\mathit{threadStartNodes}$ $\leftarrow$ getReachableStartsByBFS($\mathit{cg}$)
+\FOR{each $\mathit{threadStart}$ in $\mathit{threadStartNodes}$}
+\STATE $\mathit{fringe}$ $\leftarrow$ an empty queue\\
+\COMMENT{keep all visited nodes to avoid infinite loop}
+\STATE $\mathit{visited}$ $\leftarrow$ $\emptyset$
+\STATE $\mathit{fringe}$.enqueue(getSuccNodes($\mathit{cg}$, $\mathit{threadStart}$))
+\WHILE{$\mathit{fringe}$.isNotEmpty()}
+\STATE $\mathit{node}$ $\leftarrow$ $\mathit{fringe}$.dequeue()
+\IF{$\mathit{node}$ $\in$ $\mathit{visited}$}
+\STATE continue
+\ENDIF
+\STATE $\mathit{visited}$ $\leftarrow$ $\mathit{visited}$ $\cup$ $\mathit{node}$
+\FOR{each $\mathit{succNode}$ in getSuccNodes($\mathit{cg}$, $\mathit{node}$)}
+\IF{$\mathit{succNode}$ $\in$ $\mathit{uiAccessNodes}$}
+\STATE $\mathit{newError}$ $\leftarrow$ createErrorReport($\mathit{entryNode, succNode}$)
+\STATE $\mathit{errors}$ $\leftarrow$ $\mathit{errors}$ $\cup$ $\mathit{newError}$
+\ELSIF{$\mathit{succNode}$ $\in$ $\mathit{safeNodes}$}
 \STATE continue
 \ELSE
-\STATE queue.enqueue(succNode)
+\STATE $\mathit{fringe}$.enqueue($\mathit{succNode}$)
 \ENDIF 
@@
 \end{figure}
+
+The algorithm in Figure~\ref{fig:detectalgorithm} uses BFS to search
+for potential error-revealing paths, since BFS always returns the
+shortest path from the entry node to the UI-accessing node, and thus
+permits to produce small error reports. However,
+other graph search strategies such as Depath-First Search (DFS) or
+exhaustive path search can also be employed. In our evaluation (Section~\ref{sec:search}),
+we empirically compared three different graph search strategies, and demonstrate that
+using BFS allows the algorithm to find more errors than DFS and
+exhaustive path search.
+Given a sound call graph, our algorithm is sound in that it does not
+miss true positives. We note, however, that computing a sound
+call graph in the presence of reflection is non-trivial. 
+To alleviate this problem, we next proposed a reflection-aware call graph
+construction algorithm in Section~\ref{sec:cg}.
 
@@
 
-In an object-oriened language wth dynamic dispatch, the
-crucial step in constructing a call graph is to compute a conservative
-approximation of the set of methods that can be invoked by a given
-virtual method call. Call graph construction algorithms have been
-studied intensively in the 1990s. While their original formulations
-use a variety of formalisms, most of them can be recast as set-based
-analyses. Various algorithms differ primarily in the number of sets
-that are used to approximate run-time values of expressions. 
-In practice, algorithms such as RTA that use a single set for the whole
-program scale well but achieves relatively lower precision.  The
-k-CFA algorithms maintains one or several sets per expression achieves better
-precision than RTA (\textit{k} is length of calling context).
-
-%this is wrong for k-CFA, k-CFA maintains several sets per expression, which k > 0
-%should cite Ben Livshit's paper on "Reflection analysis for Java"
-%Donot overclaim "say propose a new technique", instead, say "refine the technique"
-%also need to cite Yannis's paper on solving k-CFA paradox
-
-%\textbf{need to describe why need to traverse from the UI entry, not just from the thread entry}
-
 \begin{figure}[t]
-\textbf{\underline{TODO: reformat it using mathit}}\\
-\textbf{Input}: a Java program $P$\\
-\textbf{Output}: a call graph $cg$\\
+\textbf{Input}: a Java program $\mathit{P}$\\
+\textbf{Output}: a call graph $\mathit{cg}$\\
 \vspace{-5mm}
 \begin{algorithmic}[1]
-\FOR{each $statement$ in $P$}
-\IF{$statement$ is a reflection call}
-\STATE objectSet $\leftarrow$ getAllObjectsToCreate($statement$)
-\STATE $newInstr$ $\leftarrow$ createObjectCreationStatement(objectSet)
-\STATE replace $statement$ with $newInstr$
+\FOR{each $\mathit{statement}$ in $\mathit{P}$}
+\IF{isReflectionCall($statement$)}
+\STATE $\mathit{objectSet}$ $\leftarrow$ getAllObjectsThatMaybeCreated($\mathit{statement}$)
+\STATE $\mathit{newStmt}$ $\leftarrow$ createObjectCreationStatement($\mathit{objectSet}$)
+\STATE replace $\mathit{statement}$ with $\mathit{newStmt}$
 \ENDIF
 \ENDFOR
-\STATE $cg$ $\leftarrow$ $constructCallGraph$($P$, callSiteMap)
-\RETURN $cg$
+\STATE $\mathit{cg}$ $\leftarrow$ constructCallGraph($\mathit{P}$)
+\RETURN $\mathit{cg}$
 %\ENDWHILE
@@
 
-Unfortunately, GUI applications often use reflection extensively and make
-existing call graph construction algorithms fail to build a sufficiently complete
-call graph. The example code in Figure~\ref{fig:sampleandroid} from an Android application
+GUI applications tend to use reflection intensively. In particular, GUI applications built on 
+top of the Android framework often use configuration files and reflection to specify GUI layout.
+The heavy use of reflection makes many existing call graph construction algorithms such as RTA~\cite{rta}
+and k-CFA~\cite{kcfa} fail to build a sufficiently complete call graph.
+The example code in Figure~\ref{fig:sampleandroid} from an Android application
  illustrates the limitations.
 In Figure~\ref{fig:sampleandroid}, line 6 uses reflection to create a \CodeIn{Button}
-object by looking up its id declared in the XML file. When this button
-is clicked, its event handling code (line 9 -- 11) updates the text.
+object by looking up its id declared in the associated XML file. When this button
+is clicked, its event handling code (lines 9--11) updates the text.
 %d caches
@@
 The basic idea to replace reflection calls with explicit object
-creation instructions, pretending that the corresponding concrete object
+creation statements, pretending that the corresponding concrete object
 has been created.  The algorithm is shown in Figure~\ref{fig:cgalgorithm}.
 It consists of two steps. The first step is a simple program
-transformation to replace reflection calls with object creations, and
-the second step is to use standard call graph construction algorithms
-to construct the graph on the transformed program. Lines 1 - 7 show
+transformation to replace reflection calls with object creation statements, and
+the second step is to use an existing call graph construction algorithm
+to build the graph on the transformed program. In our context,
+a reflection call represents a framework-specific helper method invocation
+that uses Java reflection to create desirable objects, such as
+the \CodeIn{findViewById} method in Android applications, instead
+of the methods in the \CodeIn{java.lang.reflection} package.
+In Figure~\ref{fig:cgalgorithm}, lines 1--7 show
 the first step of program transformation. The algorithm iterates through every statement
-in an analyzed program. When it sees a reflection call statement (e.g.,
-the \CodeIn{findViewById} method), the algorithm analyzes the
-program to determine a set of possible classes that may be created.
-After that, the algorithm creates a new instruction which non-deterministically
-returns a new object from the class set. Line 8 is the second step
-to build a call graph on the transformed program.  In this step,
-any existing call graph construction algorithms can be used.
-%construction algorithm is independent of the underlying call graph algorithm;
-%any existing algorithm can be used to construct the resulting graph at line 8.
+in an analyzed program. When it sees a reflection call, the algorithm
+determines a set of possible objects that might be created.
+After that, the algorithm creates a statement which non-deterministically
+returns a new object from the object set. Line 8 is the second step
+to build a call graph on the transformed program.
 
-For the example in Figure~\ref{fig:sampleandroid}, the algorithm
-first parses the XML configuration file to determine that the \CodeIn{button\_id}
-value is mapped to a \CodeIn{Button} instance declaration. Then it
-replaces the reflection call: \CodeIn{findViewById(R.id.button\_id)} 
-with an explicit object creation call: \CodeIn{new Button()}.
+This algorithm is parameterized in three places:
+line 2, line 3, and line 8. Currently, we instantiated it
+for Android applications as follows. On line 2,
+the predicate isReflectionCall returns true
+if the $statement$ is a \CodeIn{findViewById(id)} method call. On line 3, method
+\CodeIn{getAllObjectsThatMaybeCreated} parses the associated XML configuration
+file in an Android application to extract the class declaration
+ correspondinig to the given \CodeIn{id} value. If the \CodeIn{id}
+value is dynamically generated, the method will conservatively
+return instances of all subclasses of the declared type.
+On line 8, any existing call graph construction algorithm can be directly
+used.
+
+Take the code in Figure~\ref{fig:sampleandroid} as an example.
+When the algorithm sees the reflection call
+\CodeIn{findViewById(R.id.button\_id)}, it
+parses the XML configuration file to determine that the \CodeIn{button\_id}
+value is mapped to a \CodeIn{Button} instance. Then, it
+replaces the reflection call
+with an explicit object creation statement: \CodeIn{new Button(null)}.
 After that, the algorithm employs existing call graph construction

### 2012-02-01 GUIErrorDetector/paper/evaluation.tex
significant revise

@@
 
-%Our experiment investigate the following four research questions:
-
-%\begin{itemize}
-%\Item can our approach detect real bugs in multithreaded GUI applications?
-
-%\Item is the reflection-aware call graph construction algorithm useful?
-
-%\Item how effective is the proposed heuristic? is the reflection-aware call graph construction algorithm useful?
-%\end{itemize}
-
 Our experiment objective is three-fold: to demonstrate the effectiveness
 of our approach in detecting real bugs in multithreaded GUI applications, to 
-compare the reflection-aware call graph construction algorithms
-with existing ones , and to evaluate the usefulness of the proposed 
+compare the reflection-aware call graph construction algorithm
+with existing ones, and to evaluate the usefulness of the proposed 
  heuristics.
 
-First, we describe our subject programs (Section~\ref{sec:subjects}) and the experimental procedural (Section~\ref{sec:procedural}).
-We then show that our technique detects bugs in real-world GUI applications on
-four supported frameworks (Section~\ref{sec:errors}). We also compare our technique with
-a straightfoward approach in Section~\ref{sec:straightforward},  compare the reflection-aware call graph
+First, we describe our subject programs (Section~\ref{sec:subjects}) and the experimental procedure (Section~\ref{sec:procedural}).
+We then show that our technique detects bugs in real-world GUI applications (Section~\ref{sec:errors}).
+We also compare our technique with
+a straightfoward approach (Section~\ref{sec:straightforward}),  compare the reflection-aware call graph
 construction algorithms with existing algorithms (Section~\ref{sec:reflectionaware}), and
@@
 
-We use a set of open-source projects from Sourceforge, Google code and Eclipse plugin
+We use a set of open-source projects from Sourceforge, Google code, and the Eclipse plugin
 market as evaluation subjects. To choose subjects for each supported GUI framework,
-we first search the framework keywords (e.g., ``Java Swing'' or ``Java SWT'')
-in the above three source repositories, and then select subjects based on the following
-criterias. First, the subject must be a multithreaded GUI application, not
-an open library. Second, the subject must undergone at least two years of active development,
-and is listed in the first 3 results pages based on popularity. This permits us
-to exclude many pre-mature subjects that may contain obvious errors.
+we first searched for the framework keywords (e.g., ``Java Swing'' or ``Java SWT'')
+in the above three source repositories, and then selected subjects based on the following
+criteria. First, the subject must be a Java application, not
+an open library. Second, the subject must use multithreading in its implementation.
+Third, the subject must undergone at least two years of active development,
+and is listed in the first 3 result pages based on popularity. This permits us
+to exclude many immature subjects that may contain obvious errors.
 
-The subjects used in our experiment are shown in Table~\ref{table:subjects}. Our
-subjects include end-user applications, programming tools, and games. Specifically:
+We chose subjects belonging to various categories from all subjects satisfying
+the above criteria. The subjects used in our experiment are shown in Table~\ref{table:subjects},
+which include end-user applications, programming tools, and games.
 
@@
 \Item  \textbf{Android applications.} %MyTracks~\cite{mytracks}, Fennec~\cite{fennec}, and SGTPuzzles~\cite{sgtpuzzles} are three Android applications.
-MyTracks~\cite{mytracks}, developed by Google, records users' GPS tracks in outdoor activities, and provides
-interfaces to visualize them on Google Maps. Fennec~\cite{fennec}, developed by Mozilla, is the Mozilla
-Firefox web browser for mobile devices. SGTPuzzles~\cite{sgtpuzzles} is a small logic single-player game.
+SGTPuzzler~\cite{sgtpuzzles} is a single-player logic game.
+Fennec~\cite{fennec}, developed by Mozilla, is the Mozilla
+Firefox web browser for mobile devices. 
+MyTracks~\cite{mytracks}, developed by Google, records users' GPS tracks, and provides
+interfaces to visualize them on Google Maps.
 
@@
  \hline
- VirgoFTP (1.3.5) &  2293 &  20 &  165  \\
+ VirgoFTP (1.3.5) &  10815 &  116 &  1955\\
  \hline
@@
 \hline
- Total &  64215 &  554 &  4702 \\
+ Total &  76232 &  650 &  6492\\
 \hline
@@
 
-\subsection{Procedural}
+\subsection{Experimental Procedure}
 \label{sec:procedural}
 
-We run our tool on each subject with three call graph construction
+We ran our tool on each subject with three call graph construction
 algorithms: RTA~\cite{rta}, 0-CFA, and 1-CFA~\cite{kcfa}.  When running
 each call graph construction algorithm on three Android applications, we
-use two configurations: with and without the reflection-aware algorithm 
+used two configurations: with and without the reflection-aware algorithm 
 (Section~\ref{sec:cg}).  We did not use other expensive algorithms like $k$-CFA ($k >$ 1),
-because they can not scale to large programs.
+because they can not scale to our subject programs.
 
-We inspect the source code of each subject to determine whether any
+We first inspect the source code of each subject to determine whether any
 native methods or project-specific GUI interaction patterns are implemented.
-We found SGTPuzzler is the only subject that uses native methods to interact with
-underlying operating systems. Thus, we manually added 3 \CodeIn{@CalledByNative}
-annotations for it. Also two subjects MyTracks and Fennec employ a self-defined
-way to interact with the GUI framework. For example, in MyTracks, all non-UI
+Among all evaluated subjects, we found SGTPuzzler is the only program that
+uses native methods to interact with
+the underlying operating system. Thus, we checked the native code carefully,
+and manually added 3 \CodeIn{@CalledByNativeMethods}
+annotations for it. Two subjects MyTracks and Fennec employ a customized pattern
+to interact with the GUI framework. For example, in MyTracks, all non-UI
 threads are initialized via using the library method \CodeIn{android.os.handler.handleCallback}.
@@
 supported GUI frameworks. The results vary slightly according
-to the specific call graph algorithm used. In general, using
-the 1-CFA algorithm finds most errors (11 in total) and least
-warnings (21 in total). The tradeoffs of using other
-algorithms will be explained in Section~\ref{sec:reflectionaware}.
+to the call graph algorithm used. In general, using
+the 1-CFA algorithm found most errors (11 in total) and least
+warnings (21 in total). The trade-offs of using other call graph
+construction algorithms will be explained in Section~\ref{sec:reflectionaware}.
 
 We further examined the detailed results for each subject.
-Among the 21 warnings issued by using the 1-CFA algorithm, 2
-are false positives, and 8 are redundant:
-they have the same causes as the rest 11 warnings.
+Among the 21 warnings issued by using the 1-CFA algorithm, 11
+warnings reveals 11 distinct errors, in which 6 are previously-unknwon.
+2 warnings are false positive, and the remaining 8 warnings
+are redundant.
 
@@
 
-Figures~\ref{fig:swingerror} amd~\ref{fig:pluginerror} show
-two real errors our tool has found. Figure~\ref{fig:swingerror}
-shows an invalid thread access error in the S3dropbox
-program. This error happens when the \CodeIn{deterCurrentBucket}
-method at line 63 throws an exception. This error can be hard to
+%Figures~\ref{fig:swingerror} amd~\ref{fig:pluginerror} show
+%two real errors our tool has found. 
+Figure~\ref{fig:swingerror}
+shows an invalid thread access error our tool found in the S3dropbox
+program. This error only happens when the \CodeIn{deterCurrentBucket}
+method at line 63 throws an exception, and can be hard to
 detect by testing, since the test must  execute that specific exception-handling
 path. We reported this error to the S3dropbox developers. Tom Czarniecki,
-a key developer of S3dropbox confirmed this potential single-thread
+a key developer of S3dropbox confirmed this potential single-GUI-thread
 violation. He mentioned that the S3dropbox project has already
@@
 of the time, programmers can get away with an apparently ``well behaved'' Swing
-GUI that actually breaks the single-thread rule. However, As clearly
-indicated in the official documentation, Swing is a single-threaded GUI
+GUI that actually breaks the single-GUI-thread rule. However, As clearly
+indicated in the official documentation, Swing is a single-GUI-threaded GUI
 toolkit, and is not thread-safe. All Swing code must be executed in the UI-thread and
@@
 method at line 415 to update the user interface. In EclipseRunner
-, the \CodeIn{refresh} method has been
-called by 6 different methods in non-UI threads. Thus, our
+, the \CodeIn{refresh} method is
+called by 6 different methods from the same non-UI thread. Thus, our
 tool issues 6 separate warnings for each caller method to indicate
-different ways to trigger this error, despite that all the 6 warnings
-acutally have the same error cause.
+6 different ways to trigger this error, despite that all the 6 warnings
+acutally have the same error cause and are redundant with one another.
 
@@
 
-\noindent \textbf{\textit{Summary.}}Our technique finds real errors
+\noindent \textbf{\textit{Summary.}} Our technique can find real errors
 in multithreaded GUI applications on four different frameworks with
-an acceptable false positive rate.
+acceptable accuracy.
 
@@
 
-As briefly mentioned in Section~\ref{sec:finding}, one way to avoid
-invalid thread access errors is to wrap every GUI access code
-with message passing methods (i.e., the safe methods). Thus, a
+As briefly mentioned in Section~\ref{sec:finding}, one way to prevent
+invalid thread access errors is to wrap every GUI accessing operation
+with message passing (i.e., via the safe methods). Thus, a
 straightforward way to detect potential invalid error
-is to check every method to determine whether all GUI-accessing code
-is probably wrapping by safe methods. If not, this approach
-issues a warning for every violation. 
+is to check every method in the user code to determine whether all GUI-accessing operation
+is probably wrapped. If not, this approach issues a warning.% for every violation. 
 %If not, this approach issues warnings.
@@
 threads, UI-accessing methods, and safe methods, thus it often incorrectly
-classifies GUI accessing code which will never be executed
+classifies GUI accessing operations which will never be executed
 in a non-UI thread as erroneous. Furthermore, our technique
-outputs a method call chain in each reported error, which can help
+outputs a method call chain with each reported error, which can help
 developers understand how an invalid thread access error is triggered.
@@
 \noindent \textbf{\textit{Summary.}} Our technique provides
-richer contextually information for a potential error, and 
+richer contextually information for the reported error, and 
 is significantly more precise than the straightforward approach.
@@
 
-We next compare three call graph construction algorithms (RTA, 0-CFA, and 1-CFA)
+We next compare the three call graph construction algorithms (RTA, 0-CFA, and 1-CFA)
 used in our experiments. As shown in Table~\ref{table:results},  1-CFA found
@@
 is because RTA and 0-CFA do not consider the calling context when
-constructing a call graph, and it may
-mix the same method calls by different callers into a single node, and
-then introduce imprecision.
+constructing a call graph, and may
+mix the same method calls by different callers into a single node, thus
+introducing imprecision.
 
@@
 99.     msgTextView.setText(LAT\_LONG\_FORMAT.format(d));
-100.\}
+100. \}
 \end{alltt}
 \end{CodeOut}
+
+\normalsize
 
@@
 
-\noindent \textbf{\textit{Summary.}} Using the 1-CFA call graph construction
-algorithm is more effective in finding errors, and our reflection-aware call
-graph construction algorithm is critical to find errors on some
+\noindent \textbf{\textit{Summary.}} Using the 1-CFA 
+algorithm finds more errors than 0-CFA and RTA, and our reflection-aware call
+graph construction algorithm is useful to find errors on some
 Android applications.
@@
 
-Our error detection algorithm in Figure~\ref{fig:detectalgorithm} uses BFS to search potential
-single-thread violations. However, other graph search strategies such as
+Our error detection algorithm in Figure~\ref{fig:detectalgorithm} uses BFS to search for
+potential single-GUI-thread violations. However, other graph search strategies such as
 Depth-First Search (DFS) and exhaustive path search can also be employed. To
@@
 
-The first variant uses DFS by changing line 7 of Figure~\ref{fig:detectalgorithm}
-to \CodeIn{getReachableStartsByDFS(cg)}, changing line 9 of Figure~\ref{fig:detectalgorithm}
-to \CodeIn{queue} $\leftarrow$ \CodeIn{an empty stack}, and changing queue operations
-(\CodeIn{enqueue} and \CodeIn{dequeue}) to the corresponding stack operations (\CodeIn{push} and \CodeIn{pop}).
-This variant missed one error in the FileBunker subject, and found 8 errors
-in total.  That is because DFS searches deeper into the graph, and the path it finds
-may not be the shortest path.
+The first variant uses DFS for graph traverse by changing method \CodeIn{getReachableStartsByBFS(cg)}
+to \CodeIn{getReachableStartsByDFS(cg)} on line 7, changing line 9 to
+$\mathit{fringe}$ $\leftarrow$ $\mathit{an}$ $\mathit{empty}$ $\mathit{stack}$,
+and changing queue operations (\CodeIn{enqueue} and \CodeIn{dequeue} on lines 11, 13, and 25 of Figure~\ref{fig:androiderror})
+to the correspondiing statck operations (\CodeIn{push} and \CodeIn{pop}).
+
+As a result, this variant found 8 errors in total and missed 1 error in the FileBunker subject.
+The reason is that DFS tends to search deeper into the graph, and the path it returns
+is more likely not to be the shortest one. In the FileBunker subject, the path
+returned by DFS is much longer, and does not actually exist.
 
@@
 The second variant uses exhaustive search to find potential errors. This variant
-enumerates all non-cyclic paths from the start nodes, and checks whether each
+enumerates all non-cyclic paths from the start nodes, and then checks whether each
 path spawns a new thread and accesses GUI object without using safe methods. As
-a result, this variant run out of memory on all subjects. We further checked
-the traversed paths before the algorithm terminated, and found none of the explored
+a result, this variant run out of memory on all subjects. We checked
+the output paths before the algorithm terminated, and found none of the explored
 path revealed a valid error. This is because the number of
 non-cyclic paths in a graph is exponetially large to the graph node number.
-For a realistic call graph which often contains thousands of nodes, it is impossible to enumerate all
-paths in practice.
+For a realistic call graph which often contains thousands of nodes, for which
+it is impossible to enumerate all paths in practice.
 
@@
 Table~\ref{table:filters} tabulates the results.
-Our static analysis outputs thousands of warnings for the evaluated
-subjects, but the proposed heuristic filters effectively reduces
+Our static analysis output thousands of warnings for the evaluated
+subjects, but the proposed heuristic filters effectively reduced
 the number of likely invalid warnings. On average, five heuristic
-filters remove 99.96\% of the reported warnings as false positives
+filters removed 99.96\% of the reported warnings as false positives
 or redundant warnings. Specifically, heuristic filters 1 and 2 identified
@@
 and 5 identified 67.48\% of the warnings as redundant warnings.
-We further manually check each filtered warning, and found no
-real errors have been removed.
+Remarkably, the 3rd heuristic filter for removing lexically redundant
+reports is the most effective one on the evaluated subjects: it removes 35277 redundant warnings.
+
+%We further manually check each filtered warning, and found no
+%real errors have been removed.
 
@@
 \noindent \textbf{\textit{Performance and scalability.}} Our tool
-has been evaluated on 9 subjects with over 67 KLOC and dependent
+has been evaluated on 9 subjects with over 76 KLOC and dependent
 libraries with over 1.4 MLOC, showing good scalability.
@@
 non-UI threads that are spawned by the UI-thread after the GUI
-is initialized, and ignores other possible non-UI threads
+is initialized, and ignores other possible non-UI threads (quite unusual)
 that are created during the pre-initialization GUI work. One way

### 2012-02-01 GUIErrorDetector/paper/evaluation.tex
fix typos and bibtex

@@
 We also compare our technique with
-a straightfoward approach (Section~\ref{sec:straightforward}),  compare the reflection-aware call graph
+a straightforward approach (Section~\ref{sec:straightforward}),  compare the reflection-aware call graph
 construction algorithms with existing algorithms (Section~\ref{sec:reflectionaware}), and
@@
 In this experiment, none of the paper
-authors was familar with the subjects; but we found it is quite easy
+authors was familiar with the subjects; but we found it is quite easy
 to add extra annotations and heuristic filters. All these
@@
 Among the 21 warnings issued by using the 1-CFA algorithm, 11
-warnings reveals 11 distinct errors, in which 6 are previously-unknwon.
-2 warnings are false positive, and the remaining 8 warnings
-are redundant.
+warnings reveals 11 distinct errors, in which 6 are previously-unknown,
+2 warnings are false positive, and the remaining 8 
+are redundant warnings.
 
@@
 6 different ways to trigger this error, despite that all the 6 warnings
-acutally have the same error cause and are redundant with one another.
+actually have the same error cause and are redundant with one another.
 
@@
 
-In constrast, the error-related GUI objects in the other two Android applications (Fennec
+In contrast, the error-related GUI objects in the other two Android applications (Fennec
 and SGTPuzzler) are created explicitly, so that a normal call graph construction
@@
 path revealed a valid error. This is because the number of
-non-cyclic paths in a graph is exponetially large to the graph node number.
+non-cyclic paths in a graph is exponentially large to the graph node number.
 For a realistic call graph which often contains thousands of nodes, for which
@@
 \noindent \textbf{\textit{Summary.}} Although a static analysis may
-issue false postivies or redundant reports, a set of well-designed
+issue false positives or redundant reports, a set of well-designed
 heuristics can still remove most of them.

### 2012-02-01 GUIErrorDetector/paper/introduction.tex
fix typos and bibtex

@@
 requiring GUI developers to become experts at concurrent programming. Programming the
-(\textbf{hard-to-recognized words}) is also simpler and less error-prone.
+framework itself is also simpler and less error-prone.
 
@@
 causing an invalid thread access error. Our tool
-finds this error and generate a report as shown in
+finds this error and generates a report as shown in
 Figure~\ref{fig:report}.
@@
 Such an approach is desirable for accesses from non-UI threads, but it is unnecessary
-and dangerous fro accesses from the UI thread. Asynchronized message passing offers
+and dangerous for accesses from the UI thread. Asynchronized message passing offers
 no timing guarantee, so that a GUI object may have already been
@@
 Given a sound call graph, our analysis is sound in that it does
-not miss true positives. GUI applications tend to (\textbf{recognize}) use of reflection. And
+not miss true positives. GUI applications tend to use of reflection. And
 in the presence of reflection, however, it is
@@
 entry points}. Thus, our implementation is parameterized with respect to
-those those framework-specific parts.
+those framework-specific parts.
 

### 2012-02-01 trunk/GUIErrorDetector/paper/related.tex
fix typos and bibtex

@@
 (for model-based testing)~\cite{androidtesting}, %, Xie:2006:MTC:1172962.1172990},
-test generation~\cite{YuanCohenMemonTSE2011, YuanMemonICSE2007},
-test oracle creation~\cite{MemonFSE2000}, test execution~\cite{MemonFSE2001},
+test generation~\cite{YuanMemonICSE2007},
+test oracle creation~\cite{MemonFSE2000}, test execution~\cite{YuanCohenMemonTSE2011},
 and test script repairing~\cite{Huang:2010:RGT:1828417.1828465, Daniel:2011:AGR:2002931.2002937}.
@@
 with a GUI. The large number of possible interactions
-need a large number of test inputs that require substantile human effort.
+need a large number of test inputs that require substantial human effort.
 %The second problem is to determine the coverage of a set of test
@@
 several low-cost call graph construction algorithms for Java.
-Sundaresan et al.~\cite{Sundaresan:2000} went beyond the tranditional
-CHA and RTA~\cite{rta} approaches in Java and and used type propagation
+Sundaresan et al.~\cite{Sundaresan:2000} went beyond the traditional
+CHA and RTA~\cite{rta} approaches in Java and used type propagation
 for the purpose of obtaining a more precise call graph.
@@
 
-To enable call graph conostruction in the presence of  reflection,
+To enable call graph construction in the presence of  reflection,
 Livshits et al.~\cite{Livshits:2005} presented a static analysis
@@
  and is only sound with respect to the recorded executions.
-Perphas the most close work to our reflection-aware call graph
+Perhaps the most close work to our reflection-aware call graph
 construction algorithm is Payet and Spoto's Julia
@@
 non-deterministic execution of new statements.
-In constrast, our algorithm leverages the powerful \textit{Bypass logic}
+In contrast, our algorithm leverages the powerful \textit{Bypass logic}
 in the WALA framework to transform the program on-the-fly when

### 2012-02-01 trunk/GUIErrorDetector/paper/evaluation.tex
Restrict \small to just the code block to which it applies

@@
 
-%Our experiment investigate the following four research questions:
-
-%\begin{itemize}
-%\Item can our approach detect real bugs in multithreaded GUI applications?
-
-%\Item is the reflection-aware call graph construction algorithm useful?
-
-%\Item how effective is the proposed heuristic? is the reflection-aware call graph construction algorithm useful?
-%\end{itemize}
-
 Our experiment objective is three-fold: to demonstrate the effectiveness
 of our approach in detecting real bugs in multithreaded GUI applications, to 
-compare the reflection-aware call graph construction algorithms
+compare the reflection-aware call graph construction algorithm
 with existing ones, and to evaluate the usefulness of the proposed 
@@
 We also compare our technique with
-a straightfoward approach in Section~\ref{sec:straightforward},  compare the reflection-aware call graph
+a straightforward approach (Section~\ref{sec:straightforward}),  compare the reflection-aware call graph
 construction algorithms with existing algorithms (Section~\ref{sec:reflectionaware}), and
@@
 in the above three source repositories, and then selected subjects based on the following
-criteria. First, the subject must be a multithreaded GUI application, not
-an open library. Second, the subject must undergone at least two years of active development,
+criteria. First, the subject must be a Java application, not
+an open library. Second, the subject must use multithreading in its implementation.
+Third, the subject must undergone at least two years of active development,
 and is listed in the first 3 result pages based on popularity. This permits us
@@
 
-The subjects used in our experiment are shown in Table~\ref{table:subjects}. Our
-subjects include end-user applications, programming tools, and games.
+We chose subjects belonging to various categories from all subjects satisfying
+the above criteria. The subjects used in our experiment are shown in Table~\ref{table:subjects},
+which include end-user applications, programming tools, and games.
 
@@
 Firefox web browser for mobile devices. 
-MyTracks~\cite{mytracks}, developed by Google, records users' GPS tracks in outdoor activities, and provides
+MyTracks~\cite{mytracks}, developed by Google, records users' GPS tracks, and provides
 interfaces to visualize them on Google Maps.
@@
 each call graph construction algorithm on three Android applications, we
-use two configurations: with and without the reflection-aware algorithm 
+used two configurations: with and without the reflection-aware algorithm 
 (Section~\ref{sec:cg}).  We did not use other expensive algorithms like $k$-CFA ($k >$ 1),
@@
 
-We inspect the source code of each subject to determine whether any
+We first inspect the source code of each subject to determine whether any
 native methods or project-specific GUI interaction patterns are implemented.
-We found SGTPuzzler is the only subject that uses native methods to interact with
-underlying operating systems. Thus, we manually added 3 \CodeIn{@CalledByNativeMethods}
-annotations for it. Also two subjects MyTracks and Fennec employ a self-defined
-way to interact with the GUI framework. For example, in MyTracks, all non-UI
+Among all evaluated subjects, we found SGTPuzzler is the only program that
+uses native methods to interact with
+the underlying operating system. Thus, we checked the native code carefully,
+and manually added 3 \CodeIn{@CalledByNativeMethods}
+annotations for it. Two subjects MyTracks and Fennec employ a customized pattern
+to interact with the GUI framework. For example, in MyTracks, all non-UI
 threads are initialized via using the library method \CodeIn{android.os.handler.handleCallback}.
@@
 supported GUI frameworks. The results vary slightly according
-to the specific call graph algorithm used. In general, using
-the 1-CFA algorithm finds most errors (11 in total) and least
-warnings (21 in total). The tradeoffs of using other
-algorithms will be explained in Section~\ref{sec:reflectionaware}.
+to the call graph algorithm used. In general, using
+the 1-CFA algorithm found most errors (11 in total) and least
+warnings (21 in total). The trade-offs of using other call graph
+construction algorithms will be explained in Section~\ref{sec:reflectionaware}.
 
 We further examined the detailed results for each subject.
-Among the 21 warnings issued by using the 1-CFA algorithm, 2
-are false positives, and 8 are redundant:
-they have the same causes as the rest 11 warnings.
+Among the 21 warnings issued by using the 1-CFA algorithm, 11
+warnings reveals 11 distinct errors, in which 6 are previously-unknown,
+2 warnings are false positive, and the remaining 8 
+are redundant warnings.
 
@@
 
-Figures~\ref{fig:swingerror} amd~\ref{fig:pluginerror} show
-two real errors our tool has found. Figure~\ref{fig:swingerror}
-shows an invalid thread access error in the S3dropbox
-program. This error happens when the \CodeIn{deterCurrentBucket}
-method at line 63 throws an exception. This error can be hard to
+%Figures~\ref{fig:swingerror} amd~\ref{fig:pluginerror} show
+%two real errors our tool has found. 
+Figure~\ref{fig:swingerror}
+shows an invalid thread access error our tool found in the S3dropbox
+program. This error only happens when the \CodeIn{deterCurrentBucket}
+method at line 63 throws an exception, and can be hard to
 detect by testing, since the test must  execute that specific exception-handling
@@
 method at line 415 to update the user interface. In EclipseRunner
-, the \CodeIn{refresh} method has been
-called by 6 different methods in non-UI threads. Thus, our
+, the \CodeIn{refresh} method is
+called by 6 different methods from the same non-UI thread. Thus, our
 tool issues 6 separate warnings for each caller method to indicate
-different ways to trigger this error, despite that all the 6 warnings
-acutally have the same error cause.
+6 different ways to trigger this error, despite that all the 6 warnings
+actually have the same error cause and are redundant with one another.
 
@@
 
-\vspace{2mm}
+{\vspace{2mm}
 \hspace{3mm}\small{In class: com.google.android.apps.mytracks.StatsUtilities}
@@
 \end{alltt}
-\end{CodeOut}
+\end{CodeOut}}
 
-In constrast, the error-related GUI objects in the other two Android applications (Fennec
+In contrast, the error-related GUI objects in the other two Android applications (Fennec
 and SGTPuzzler) are created explicitly, so that a normal call graph construction
@@
 
-Our error detection algorithm in Figure~\ref{fig:detectalgorithm} uses BFS to search potential
-single-GUI-thread violations. However, other graph search strategies such as
+Our error detection algorithm in Figure~\ref{fig:detectalgorithm} uses BFS to search for
+potential single-GUI-thread violations. However, other graph search strategies such as
 Depth-First Search (DFS) and exhaustive path search can also be employed. To
@@
 The second variant uses exhaustive search to find potential errors. This variant
-enumerates all non-cyclic paths from the start nodes, and checks whether each
+enumerates all non-cyclic paths from the start nodes, and then checks whether each
 path spawns a new thread and accesses GUI object without using safe methods. As
-a result, this variant run out of memory on all subjects. We further checked
-the traversed paths before the algorithm terminated, and found none of the explored
+a result, this variant run out of memory on all subjects. We checked
+the output paths before the algorithm terminated, and found none of the explored
 path revealed a valid error. This is because the number of
-non-cyclic paths in a graph is exponetially large to the graph node number.
-For a realistic call graph which often contains thousands of nodes, it is impossible to enumerate all
-paths in practice.
+non-cyclic paths in a graph is exponentially large to the graph node number.
+For a realistic call graph which often contains thousands of nodes, for which
+it is impossible to enumerate all paths in practice.
 

### 2012-02-02 trunk/GUIErrorDetector/src/edu/washington/cs/detector/util/CalledByNativeMethods.java
rename to CalledByNativeMethods

@@ -16,6 +16,6 @@ import java.lang.annotation.ElementType;
 
 @Retention(RetentionPolicy.RUNTIME)
 @Target({ElementType.METHOD})
-public @interface CallByNativeMethods {
+public @interface CalledByNativeMethods {
 	String[] callers();
 }

### 2012-02-02 GUIErrorDetector/src/edu/washington/cs/detector/util/NativeAnnotationProcessor.java
create the native annotation processor

@@ -1,8 +1,19 @@
 package edu.washington.cs.detector.util;
 
+import java.io.File;
+import java.io.IOException;
+import java.lang.annotation.Annotation;
+import java.lang.reflect.Method;
+import java.net.MalformedURLException;
+import java.net.URL;
+import java.net.URLClassLoader;
 import java.util.Collection;
 import java.util.LinkedHashMap;
+import java.util.LinkedHashSet;
+import java.util.LinkedList;
 import java.util.Map;
+import java.util.Set;
+import java.util.zip.ZipException;
 
 import com.ibm.wala.classLoader.IClass;
 import com.ibm.wala.classLoader.IMethod;
@@ -11,20 +22,106 @@ import com.ibm.wala.ipa.cha.ClassHierarchy;
 import com.ibm.wala.shrikeCT.AnnotationsReader.UnimplementedException;
 import com.ibm.wala.shrikeCT.InvalidClassFileException;
 import com.ibm.wala.types.TypeName;
-import com.ibm.wala.types.annotations.Annotation;
-import com.ibm.wala.util.debug.Assertions;
 
 public class NativeAnnotationProcessor {
+	
+	public static Collection<String[]> getAllCallingPairsByNativeAnnotations(String jarFile, String lib) {
+		Collection<String[]> pairs = new LinkedList<String[]>();
+		try {
+		    Map<String, Collection<String>> relations = findCalledByNativesAnntationFromJarFile(jarFile, lib);
+		    for(String key : relations.keySet()) {
+		    	Collection<String> values = relations.get(key);
+		    	for(String value : values) {
+		    		String[] pair = new String[]{value, key};
+		    		pairs.add(pair);
+		    	}
+		    }
+		    return pairs;
+		} catch (Exception e) {
+			throw new RuntimeException(e);
+		}
+	}
 
+	//java method  ->  a collection native method callers
+	public static Map<String, Collection<String>> findCalledByNativesAnntationFromJarFile(String jarFile, String lib) {
+		if(!jarFile.endsWith(".jar")) {
+			throw new RuntimeException("The file provided: " + jarFile + " is not a jar file.");
+		}
+		Map<String, Collection<String>> callRelations = new LinkedHashMap<String, Collection<String>>();
+		
+		try {
+			Set<Class<?>> classes = loadAllClasses(jarFile, lib);
+			for(Class<?> clz : classes) {
+				Method[] methods = clz.getDeclaredMethods();
+				for(Method m : methods) {
[…]

### 2012-02-02 GUIErrorDetector/tests/edu/washington/cs/detector/util/TestNativeAnnotationProcessor.java

@@ -1,6 +1,10 @@
 package edu.washington.cs.detector.util;
 
 import java.io.IOException;
+import java.util.Collection;
+import java.util.Map;
+import java.util.Set;
+import java.util.zip.ZipException;
 
 import com.ibm.wala.core.tests.callGraph.CallGraphTestUtil;
 import com.ibm.wala.ipa.cha.ClassHierarchy;
@@ -25,4 +29,38 @@ public class TestNativeAnnotationProcessor extends TestCase {
 		NativeAnnotationProcessor.getNativeCallRelations(cha);
 	}
 	
+
+	//using the Java reflection approach
+	public void testNativeAnnotation() {
+		String jarFileName = //"D:\\research\\guierror\\subjects\\android-programs\\extracted\\sgtpuzzles.jar";
+		    "D:\\research\\guierror\\subjects\\android-programs\\extracted\\sgtpuzzles-annotation.jar";
+		
+		String lib = "D:\\research\\guierror\\eclipsews\\GUIErrorDetector\\exp-subjects\\original-android.jar";
+		try {
+			Set<Class<?>> loadedClasses = NativeAnnotationProcessor.loadAllClasses(jarFileName, lib);
+			System.out.println("Number of loaded class: " + loadedClasses.size());
+			
+			//get the relations
+			Map<String, Collection<String>> relations
+			    = NativeAnnotationProcessor.findCalledByNativesAnntationFromJarFile(jarFileName, lib);
+			System.out.println(relations);
+		} catch (Exception e) {
+			e.printStackTrace();
+		}
+	}
+	
+	public void testNativeMethodPairs() {
+		String jarFileName = //"D:\\research\\guierror\\subjects\\android-programs\\extracted\\sgtpuzzles.jar";
+		    "D:\\research\\guierror\\subjects\\android-programs\\extracted\\sgtpuzzles-annotation.jar";
+		
+		String lib = "D:\\research\\guierror\\eclipsews\\GUIErrorDetector\\exp-subjects\\original-android.jar";
+		try {
+			Collection<String[]> pairs = NativeAnnotationProcessor.getAllCallingPairsByNativeAnnotations(jarFileName, lib);
+			for(String[] pair : pairs) {
+				System.out.println(pair[0] + "  -> " + pair[1]);
+			}
+		} catch (Exception e) {
+			e.printStackTrace();
+		}
+	}
 }

### 2012-02-02 GUIErrorDetector/src/edu/washington/cs/detector/CGBuilder.java
improve the name of the 0-CFA enum

@@ -28,7 +28,7 @@ import edu.washington.cs.detector.util.WALAUtils;
 
 public class CGBuilder {
 	
-	public enum CG {RTA, ZeroCFA, ZeroContainerCFA, ZeroOneCFA, ZeroOneContainerCFA, OneCFA, TwoCFA, CFA, FakeZeroCFA}
+	public enum CG {RTA, ZeroCFA, ZeroContainerCFA, ZeroOneCFA, ZeroOneContainerCFA, OneCFA, TwoCFA, CFA, TempZeroCFA}
 	
 	public final String appPath;
 	public final File exclusionFile;
@@ -156,7 +156,7 @@ public class CGBuilder {
 			}
 			System.out.println("Use CFA with precision: " + this.cfaprecision);
 			builder = WALAUtils.makeCFABuilder(this.cfaprecision, options,  cache, cha, scope);
-		} else if (this.type == CG.FakeZeroCFA) {
+		} else if (this.type == CG.TempZeroCFA) {
 			System.out.println("Use Fake-0-CFA with precision: " + this.cfaprecision);
 			builder = WALAUtils.makeCFABuilder(0, options, cache, cha, scope);
 		}else {

### 2012-02-02 GUIErrorDetector/paper/evaluation.tex
correct two data and add more explanation

@@
 
-We first inspect the source code of each subject to determine whether any
-native methods or project-specific GUI interaction patterns are implemented.
-Among all evaluated subjects, we found SGTPuzzler is the only program that
+We first inspected the source code of each subject to determine whether any
+native methods or project-specific GUI interaction patterns were implemented.
+Among all evaluated subjects, SGTPuzzler is the only program that
 uses native methods to interact with
-the underlying operating system. Thus, we checked the native code carefully,
-and manually added 3 \CodeIn{@CalledByNativeMethods}
+the underlying operating system. Thus, we manually checked the possible
+Java methods that a native method may call, and then added 7 \CodeIn{@CalledByNativeMethods}
 annotations for it. Two subjects MyTracks and Fennec employ a customized pattern
@@
 %message passing. 
-Thus, we add 5 user-defined heuristic filters for these two subjects.%to indicate
+Thus, we add 11 user-defined heuristic filters for these two subjects.
+%to indicate
 %that they are safe to be invoked from any thread. 
@@
 After provided with necessary annotations and heuristic filters,
-our tool works in a fully-automatic, push-button manner. For each output
-warning, we manually determine its validity by either searching the
+our tool worked in a fully-automatic, push-button manner. For each output
+warning, we manually determined its validity by either searching the
 bug repository to check whether the same error has been reported before,
@@
 a key developer of S3dropbox confirmed this potential single-GUI-thread
-violation. He mentioned that the S3dropbox project has already
+violation. He mentioned that the S3dropbox project had already
 used certain design patterns and practice to avoid such violations (e.g.,
@@
 \end{alltt}
-\end{CodeOut}
-
-\normalsize
+\end{CodeOut}}
 
@@
 in our evaluation. It is still unknown whether using other 
-call graph construction algorithms such as XTA~\cite{xta} or
+call graph construction algorithms such as XTA~\cite{xta}, VTA~\cite{Sundaresan:2000} or
 an incremental algorithm~\cite{inccg} may achieve better results.

### 2012-02-02 GUIErrorDetector/tests/edu/washington/cs/detector/experiments/android/TestMozillaFirefox.java
refactoring for renaming

@@ -133,7 +133,7 @@ public class TestMozillaFirefox extends AbstractAndroidTest {
 //			super.setByfileName("fennec.xml");
 			
 			//this finds bugs
-			CG type = CG.FakeZeroCFA;
+			CG type = CG.TempZeroCFA;
 			type = CG.OneCFA;
 //			type = CG.RTA;
 			

### 2012-02-02 GUIErrorDetector/tests/edu/washington/cs/detector/experiments/android/TestSGTPuzzle.java

@@ -26,6 +26,7 @@ import edu.washington.cs.detector.guider.CGTraverseAndroidSafeMethodGuider;
 import edu.washington.cs.detector.guider.CGTraverseExploreClientRunnableStrategy;
 import edu.washington.cs.detector.guider.CGTraverseGuider;
 import edu.washington.cs.detector.util.Globals;
+import edu.washington.cs.detector.util.NativeAnnotationProcessor;
 import edu.washington.cs.detector.util.WALAUtils;
 
 /**
@@ -87,19 +88,43 @@ public class TestSGTPuzzle extends AbstractAndroidTest {
 		CGTraverseExploreClientRunnableStrategy start2checkGuider = new  CGTraverseExploreClientRunnableStrategy(new String[]{"name.boyle.chris.sgtpuzzles"});
 //		start2checkGuider.addMethodGuidance("java.lang.Thread.start", "name.boyle.chris.sgtpuzzles.SGTPuzzles$9");
 		
-			//new CGTraverseAndroidSafeMethodGuider();
-//		    new CGTraverseOnlyClientRunnableStrategy();
-		
+		//parse the native annotation
 		NativeMethodConnector connector = new NativeMethodConnector();
-		connector.addNativeMethodMapping("name.boyle.chris.sgtpuzzles.SGTPuzzles.init",
-				"name.boyle.chris.sgtpuzzles.SGTPuzzles.changedState");
+		Collection<String[]> pairs = getAllPairs();
+		for(String[] pair : pairs) {
+			connector.addNativeMethodMapping(pair[0], pair[1]);
+		}
+		//only this rule is useful, the remaining is for completeness
+		//the following annotation information is actually read from the @CalledByNativeMethods
+		//for debugging purpose in this experiment, I hard code these parts, 7 annotations in total
+//		connector.addNativeMethodMapping(
+//				"name.boyle.chris.sgtpuzzles.SGTPuzzles.init",
+//				"name.boyle.chris.sgtpuzzles.SGTPuzzles.changedState");
+//		connector.addNativeMethodMapping(
+//				"name.boyle.chris.sgtpuzzles.SGTPuzzles.init",
+//				"name.boyle.chris.sgtpuzzles.SGTPuzzles.gameStarted");
+//		connector.addNativeMethodMapping(
[…]

### 2012-02-02 trunk/GUIErrorDetector/tests/edu/washington/cs/detector/experiments/android/TestMytracksAndroid.java
refactoring for renaming

@@ -88,7 +88,6 @@ public class TestMytracksAndroid extends AbstractAndroidTest {
 //		
 //		return result;
 //	}
-	
 	public void testFindErrors() {
 		CGTraverseGuider ui2startGuider = new CGTraverseAndroidGuider();
 		String[] guiderArray = 
@@ -111,7 +110,7 @@ public class TestMytracksAndroid extends AbstractAndroidTest {
 			super.setByfileName("mytracks.xml");
 			
 			CG type = CG.RTA;
-			type = CG.FakeZeroCFA;
+			type = CG.TempZeroCFA;
 			type = CG.OneCFA;
 			
 			UIAnomalyDetector.setToUseDFS();
@@ -137,7 +136,7 @@ public class TestMytracksAndroid extends AbstractAndroidTest {
 		String extractDir = "D:\\research\\guierror\\subjects\\android-programs\\extracted\\MyTracks-1.1.11.rc1.apk";
 		super.decryptXML(apkToolDir, apkFile, extractDir);
 	}
-	
+
 //	Node: < Application, Lcom/google/android/apps/mytracks/StatsActivity, onSelectedTrackChanged(Lcom/google/android/apps/mytracks/content/Track;Z)V > Context: CallStringContext: [ fakeRootMethod@357 ], line: 244
 //	 -> Node: synthetic < Primordial, Ljava/lang/Thread, start()V > Context: CallStringContext: [ onSelectedTrackChanged@55 ], line: -1
 //	 -> Node: < Application, Landroid/os/HandlerThread, run()V > Context: CallStringContext: [ start@1 ], line: -1

### 2012-02-02 trunk/GUIErrorDetector/tests/edu/washington/cs/detector/experiments/swing/TestSudokuPuzzleSolver.java

@@ -39,7 +39,7 @@ public class TestSudokuPuzzleSolver extends AbstractSwingTest {
 		super.setCGType(CG.RTA);
 //		super.setCGType(CG.ZeroCFA);
 //		super.setCGType(CG.OneCFA);
-		super.setCGType(CG.FakeZeroCFA);
+		super.setCGType(CG.TempZeroCFA);
 		super.setCGType(CG.OneCFA);
 		
 		UIAnomalyDetector.setToUseDFS(); //use DFS

### 2012-02-02 GUIErrorDetector/paper/abstract.tex
improve introduction / abstract, and correct the wordings

--- 2012-01-04 GUIErrorDetector/paper/abstract.tex
@@
 thread spawning as the sources and GUI object accessing as the sinks. 
-Heavy use of reflection in modern GUI applications makes existing
-call graph construction algorithms fail to build a sufficiently complete
-and precise call graph. Thus, we present a combined RTA and k-CFA
-call graph construction algorithm to overcome the limitations.% of analyzing GUI applications.
+Standard call graph construction algorithms fail to build a good
+call graph for some modern GUI applications, because of heavy use of reflection.
+Thus, we present a method to build reflection-aware call graphs.
 
-We implemented our technique and instantiated it on four popular GUI
-platforms: SWT, Eclipse plugin development framework, Java Swing, and
-Android. In an evaluation on XX subjects over XXX LOC, our technique
-found a number of real-world errors, suggesting its effectiveness
-and showing good scalability.
+We implemented our technique and instantiated it for four popular Java GUI
+platforms: SWT, the Eclipse plugin development framework, Swing, and
+Android. In an evaluation on 9 programs comprising 67000 LOC, our technique
+found both previously-known and unknown errors.
 

### 2012-02-02 GUIErrorDetector/paper/technique.tex
improve introduction / abstract, and correct the wordings

@@
 
-This section formulates the problem. We define the
+This section formulates the problem. We first define the
 notations of \textit{UI thread}, \textit{non-UI threads},
 \textit{UI-accessing methods},
- \textit{safe methods}, and \textit{invalid thread access error}, and
-two assumptions we make with regard to error detection.
+ \textit{safe UI methods}, and \textit{invalid thread access error}, and
+state two assumptions we make with regard to error detection.
 
@@
 GUI application has a single global UI thread. This is true for applications
-built on top of GUI frameworks adapting the single-GUI-thread rule. The
+built on top of GUI frameworks adopting the single-GUI-thread rule. The
 only exception is that 
  an application may fork a new process to launch another
-application with its own UI thread. In that case, we require the new
+application with its own UI thread. In that case, we require the
 launched application to be analyzed separately.}\vspace{1mm}
@@
 
-\noindent  {\textsc{\textbf{Definition 4 (Safe Methods).}}} {GUI frameworks that
+\noindent  {\textsc{\textbf{Definition 4 (Safe UI Methods).}}} {GUI frameworks that
 adopt the single-GUI-thread rule must provide methods to permit non-UI threads
-to run code in the UI thread. We can such methods \textit{safe methods}, since
+to run code in the UI thread. We call such methods \textit{safe UI methods}, since
 they can be invoked safely by any thread.}\vspace{1mm}
@@
 \noindent  {\textsc{\textbf{Definition 5 (Invalid Thread Access).}}} {An invalid
-thread access error occurs when the UI thread spawns a non-UI thread, and there
+thread access error occurs when the UI thread may spawn a non-UI thread, and there
 exists a path from the non-UI thread's \CodeIn{start} method to any UI-accessing method
-without going through any safe method. }\vspace{2mm}
+without going through any safe UI method. }\vspace{2mm}
 
@@
 call method \CodeIn{Display.checkWidget} or \CodeIn{Display.checkDevice},
-and safe methods include two SWT helper methods \CodeIn{Display.asyncExec}  and
+and safe UI methods include two SWT helper methods \CodeIn{Display.asyncExec}  and
 \CodeIn{Display.syncExec} for message passing. The detailed instantiation
@@
 Specifically, it uses a queue to keep track of nodes to be visited (line 9),
-and also stores all visited nodes to avoid infinite loop (line 10).
+and stores all visited nodes to avoid infinite loop (line 10).
 The algorithm checks every successive node to be visited (line 18);
 it reports an error if that node is a UI-accessing method (lines 20, 21), or skips
-it if it is a safe method (lines 22, 23), or simply keeps traversing otherwise (line 25).
+it if it is a safe UI method (lines 22, 23), or simply keeps traversing otherwise (line 25).
 
 Note that when the algorithm determines that a UI-accessing method may be invoked
-by a non-UI thread, it computes full method call chain from the entry node to
+by a non-UI thread, it computes a method call chain from the entry node to
 the UI-accessing node as the error report.
 The method \CodeIn{createErrorReport} on line 20 does that. 
-As an example, the method call chain for the error in in Figure~\ref{fig:androiderror}
-is shown in Figure~\ref{fig:report}.
-
-Our algorithm in Figure~\ref{fig:detectalgorithm} uses BFS to search
-for potential error-revealing paths, since BFS permits to produce
-small error reports (i.e., shorter method call chains). However,
-other graph search strategies such as Depath-First Search (DFS) or
-exhaustive path search can also be employed. In our evaluation (Section~\ref{sec:search}),
-we empirically compared different graph search strategies, and demonstrate that
-using BFS allows the algorithm to find more errors than DFS and
-exhaustive path search.
+Figure~\ref{fig:androiderror} shows a method call chain from the entry
+node \CodeIn{LayerView.<init>} to the UI-accessing node \CodeIn{ViewRoot}.\CodeIn{recomputeViewAttributes}
+(for the sake of clarification, we also show the checking method \CodeIn{checkThread} in the reported warning).
 
@@
 \FOR{each $\mathit{threadStart}$ in $\mathit{threadStartNodes}$}
-\STATE $\mathit{queue}$ $\leftarrow$ an empty queue\\
+\STATE $\mathit{fringe}$ $\leftarrow$ an empty queue\\
 \COMMENT{keep all visited nodes to avoid infinite loop}
 \STATE $\mathit{visited}$ $\leftarrow$ $\emptyset$
-\STATE $\mathit{queue}$.enqueue(getSuccNodes($\mathit{cg}$, $\mathit{threadStart}$))
-\WHILE{$\mathit{queue}$.isNotEmpty()}
-\STATE $\mathit{node}$ $\leftarrow$ $\mathit{queue}$.dequeue()
+\STATE $\mathit{fringe}$.enqueue(getSuccNodes($\mathit{cg}$, $\mathit{threadStart}$))
+\WHILE{$\mathit{fringe}$.isNotEmpty()}
+\STATE $\mathit{node}$ $\leftarrow$ $\mathit{fringe}$.dequeue()
 \IF{$\mathit{node}$ $\in$ $\mathit{visited}$}
@@
 \ELSE
-\STATE $\mathit{queue}$.enqueue($\mathit{succNode}$)
+\STATE $\mathit{fringe}$.enqueue($\mathit{succNode}$)
 \ENDIF 
@@
 
+The algorithm in Figure~\ref{fig:detectalgorithm} uses BFS to search
+for potential error-revealing paths, since BFS always returns the
+shortest path from the entry node to the UI-accessing node, and thus
+permits to produce small error reports. However,
+other graph search strategies such as Depath-First Search (DFS) or
+exhaustive path search can also be employed. In our evaluation (Section~\ref{sec:search}),
+we empirically compared three different graph search strategies, and demonstrate that
+using BFS allows the algorithm to find more errors than DFS and
+exhaustive path search.
 Given a sound call graph, our algorithm is sound in that it does not
@@
 call graph in the presence of reflection is non-trivial. 
-In particular, GUI applications built on some popular frameworks like Android
-often use configuration files and reflection to specify GUI layout.
 To alleviate this problem, we next proposed a reflection-aware call graph
@@
 
-In an object-oriened language wth dynamic dispatch, the
-crucial step in constructing a call graph is to compute a conservative
-approximation of the set of methods that can be invoked by a given
-virtual method call. Call graph construction algorithms have been
-studied intensively in the 1990s. While their original formulations
-use a variety of formalisms, most of them can be recast as set-based
-analyses. Various algorithms differ primarily in the number of sets
-that are used to approximate run-time values of expressions. 
-In practice, algorithms such as RTA that use a single set for the whole
-program scale well but achieves relatively lower precision.  The
-k-CFA algorithms maintains one or several sets per expression achieves better
-precision than RTA (\textit{k} is length of calling context).
-
-%this is wrong for k-CFA, k-CFA maintains several sets per expression, which k > 0
-%should cite Ben Livshit's paper on "Reflection analysis for Java"
-%Donot overclaim "say propose a new technique", instead, say "refine the technique"
-%also need to cite Yannis's paper on solving k-CFA paradox
-
-%\textbf{need to describe why need to traverse from the UI entry, not just from the thread entry}
-
 \begin{figure}[t]
@@
 
-Unfortunately, GUI applications often use reflection extensively and make
-existing call graph construction algorithms such as RTA and k-CFA
-fail to build a sufficiently complete call graph.
+GUI applications tend to use reflection intensively. In particular, GUI applications built on 
+top of the Android framework often use configuration files and reflection to specify GUI layout.
+The heavy use of reflection makes many existing call graph construction algorithms such as RTA~\cite{rta}
+and k-CFA~\cite{kcfa} fail to build a sufficiently complete call graph.
 The example code in Figure~\ref{fig:sampleandroid} from an Android application
@@
 transformation to replace reflection calls with object creation statements, and
-the second step is to use a standard call graph construction algorithm
-to construct the graph on the transformed program. The reflection call
-represents a method invocation that relies Java reflection to create
-objects, such as the \CodeIn{findViewById} method in Android applications.
+the second step is to use an existing call graph construction algorithm
+to build the graph on the transformed program. In our context,
+a reflection call represents a framework-specific helper method invocation
+that uses Java reflection to create desirable objects, such as
+the \CodeIn{findViewById} method in Android applications, instead
+of the methods in the \CodeIn{java.lang.reflection} package.
 In Figure~\ref{fig:cgalgorithm}, lines 1--7 show
 the first step of program transformation. The algorithm iterates through every statement
-in an analyzed program. When it sees a reflection call, the algorithm analyzes the
-program to determine a set of possible classes that might be created.
-After that, the algorithm creates a new statement which non-deterministically
+in an analyzed program. When it sees a reflection call, the algorithm
+determines a set of possible objects that might be created.
+After that, the algorithm creates a statement which non-deterministically
 returns a new object from the object set. Line 8 is the second step
-to build a call graph on the transformed program.  In this step,
-any existing call graph construction algorithms can be used.
+to build a call graph on the transformed program.
 
-The algorithm in Figure~\ref{fig:cgalgorithm} is parameterized in three places:
-line 2, line 3, and line 8. We instantiated it for Android applications as
-follows. On line 2, the predicate $isReflectionCall$ returns true
+This algorithm is parameterized in three places:
+line 2, line 3, and line 8. Currently, we instantiated it
+for Android applications as follows. On line 2,
+the predicate isReflectionCall returns true
 if the $statement$ is a \CodeIn{findViewById(id)} method call. On line 3, method
@@
 file in an Android application to extract the class declaration
- correspondinig to the \CodeIn{id} value. If the \CodeIn{id}
+ correspondinig to the given \CodeIn{id} value. If the \CodeIn{id}
 value is dynamically generated, the method will conservatively
-return all subclasses of the declared type. On line 8, any existing
-call graph construction algorithm can be used to build the call graph
-on top of the transformed program.
+return instances of all subclasses of the declared type.
+On line 8, any existing call graph construction algorithm can be directly
+used.
 
-For the example in Figure~\ref{fig:sampleandroid}, the algorithm
-first parses the XML configuration file to determine that the \CodeIn{button\_id}
-value is mapped to a \CodeIn{Button} instance declaration. Then it
-replaces the reflection call: \CodeIn{findViewById(R.id.button\_id)} 
-with an explicit object creation call: \CodeIn{new Button(null)}.
+Take the code in Figure~\ref{fig:sampleandroid} as an example.
+When the algorithm sees the reflection call
+\CodeIn{findViewById(R.id.button\_id)}, it
+parses the XML configuration file to determine that the \CodeIn{button\_id}
+value is mapped to a \CodeIn{Button} instance. Then, it
+replaces the reflection call
+with an explicit object creation statement: \CodeIn{new Button(null)}.
 After that, the algorithm employs existing call graph construction
@@
 multiple methods that access GUI objects, such as:
+
 \begin{CodeOut}
@@
 \textbf{call graph entry nodes}, \textbf{UI-accessing nodes},
-and \textbf{safe methods} for each framework.
+and \textbf{safe UI methods} for each framework.
 
 %For each framework, we customize the \textit{call graph entry nodes},
-%\textit{UI-accessing nodes}, and \textit{safe methods} on lines 3 -- 5 of the
+%\textit{UI-accessing nodes}, and \textit{safe UI methods} on lines 3 -- 5 of the
 %algorithm in
@@
 %customizing for: entry points, starting points, error checking, thread
-%safe methods, what is the event dispatching thread?
+%safe UI methods, what is the event dispatching thread?
 
@@
 
-\item \textbf{Safe methods: } SWT provides two helper methods (\CodeIn{Display.\\asyncExec}
+\item \textbf{Safe UI methods: } SWT provides two helper methods (\CodeIn{Display.\\asyncExec}
 and \CodeIn{Display.syncExec}) to execute code (a)synchro-
 nizedly on the UI thread.
- We treat these two methods as safe methods, since invoking
+ We treat these two methods as safe UI methods, since invoking
 them from any thread 
@@
 
-\item \textbf{UI-accessing nodes} and \textbf{Safe methods} are the same as SWT.
+\item \textbf{UI-accessing nodes} and \textbf{Safe UI methods} are the same as SWT.
 
@@
 
-\item \textbf{Safe methods: }  Swing's two helper methods
+\item \textbf{Safe UI methods: }  Swing's two helper methods
 (\CodeIn{SwingUtilities.} \CodeIn{invokeLater} and \CodeIn{SwingUtilities.invokeAndWait}) that execute code in the UI thread.
@@
 
-\item \textbf{Safe methods: } two helper methods (\CodeIn{View.post}
+\item \textbf{Safe UI methods: } two helper methods (\CodeIn{View.post}
 and \CodeIn{View.postDelay}) that execute code on the UI thread. 

### 2012-02-02 trunk/GUIErrorDetector/paper/introduction.tex
improve introduction / abstract, and correct the wordings

@@
 even before the lengthy task completes. However, the use of multiple threads
-makes new types of errors which may compromise robustness, possible.
+enables new types of errors which may compromise robustness, possible.
 We now discuss a programming rule for multithreaded GUIs, the consequence
@@
 
-\item Concurrency errors, such as races and deadlocks, never occur on GUI objects, without
-requiring GUI developers to become experts at concurrent programming. Programming the
+\item Concurrency errors, such as races and deadlocks, never occur on GUI objects. 
+GUI developers need not become experts at concurrent programming. Programming the
 framework itself is also simpler and less error-prone.
@@
 Otherwise, whenever the framework calls a method that might
-be implemented in client code (e.g., any public or protected method in a public class),
+be implemented in client code (e.g., any non-final public or protected method in a public class),
 the framework must save its state and release all locks so that the client code can grab locks
@@
 \item GUI events are dispatched in a predictable order from a single event queue.
-If the thread scheduler could arbitrarily interleave, component changes, event processing,
+If the thread scheduler could arbitrarily interleave component changes, then event processing,
 program comprehension and testing would be more difficult.
@@
  ensure that all GUI objects are accessed only by the UI thread.
-If not, an \textit{invalid thread access error} will occur.
+If not, an \textit{invalid thread access error} will occur. This may
+terminate the application, but it is considered \textbf{hard-to-recognize? probabably?} to nondeterministic concurrency errors.
 
@@
 the GUI  after its  task is finished.
-In practice, invalid thread access errors are both \textit{frequent} and \textit{severe}.
+In practice, invalid thread access errors are \textit{frequent}, \textit{severe}, and \textit{hard} to debug.
 %and \textit{difficult to avoid}.
@@
 a recent release of Eclipse still contains this error (bug id: 333533, reported in 01/2011).
- Furthermore, many reported  errors are non-trivial, and it is unintuitive
-to fix them. Developers usually need non-local reasoning to find the specific
-UI interactions that can trigger the bug;  it took developers 2 years
-to fix bug 51757 and verify the patch. In addition, the invalid thread access error
+ In addition, the invalid thread access error
 is severe. It is user-perceivable; it cannot be recovered by the program itself,
@@
 users can only restart the application to recover from the error.
+Furthermore, many reported  errors are non-trivial to diagnose and fix.
+Developers usually need non-local reasoning to find the specific
+UI interactions that can trigger the bug;  it took developers 2 years
+to fix bug 51757 and verify the patch.
 
@@
 \end{CodeOut}
-\vspace*{-2.0ex} \Caption{{\label{fig:androiderror} A real
-bug reported on 11/17/2011 in Mozilla firefox release 10.0.a.rc3
-for the Android platform (bugzilla ID: 703256). On line 74, \CodeIn{LayerView}'s constructor
+\vspace*{-2.0ex} \Caption{{\label{fig:androiderror} 
+Bug 703256 reported on 11/17/2011 in Mozilla Firefox release 10.0.a.rc3
+for Android. On line 74, \CodeIn{LayerView}'s constructor
 calls method \CodeIn{setRenderer} which 
@@
 The invalid thread access error is not unique to the SWT framework. Other recent GUI frameworks
-like Android also suffer from similar problems. For example, 
+like Android suffer from similar problems. For example, 
 Figure~\ref{fig:androiderror} shows a recently-reported bug in the Android version of Mozilla Firefox.
@@
 since the code that spawns a new thread inside the \CodeIn{setRenderer} method is
-in an Android library whose source code may not be available to developers.
+in an Android library.
 
@@
 
-To ensure GUIs behave correctly, developers must prevent or detect invalid thread
-access errors, and effective techniques must be developed.% to alleviate this problem.
+To ensure that GUIs behave correctly, developers must prevent or detect invalid thread
+access errors. Currently, no effective techniques exist. %must be developed.% to alleviate this problem.
 
@@
 It is infeasible for testing to cover the enormous space of possible interactions
-with a GUI, in that each sequence of GUI events can result in
+with a GUI. Each sequence of GUI events can result in
 a difficult state, and each GUI event may need to be evaluated in all of
@@
 access GUI objects via asynchronized message passing, to ensure a GUI object is accessed in
-the UI thread. For example, a developer could have prevented the bug in Figure~\ref{fig:androiderror},
+the UI thread. For example, a developer could have prevented the bug in Figure~\ref{fig:androiderror}
 by wrapping line 222 inside a \CodeIn{post} message passing method\footnote{The
@@
 221.     gl.glViewport(0, 0, width, height);
-         \textbf{mView.post(new Runnable() \{}
-             \textbf{public void run() \{}
+         \textbf{mView.post(new Runnable() \ttlcb}
+             \textbf{public void run() \ttlcb}
 222.             mView.setViewportSize(new IntSize(width, height));
-             \textbf{\}}
-         \textbf{\});}
+             \textbf{\ttrcb}
+         \textbf{\ttrcb);}
      \}
@@
 and dangerous for accesses from the UI thread. Asynchronized message passing offers
-no timing guarantee, so that a GUI object may have already been
+no timing guarantee, so a GUI object may have already been
 disposed before the message sent to it arrives, causing other bugs. 
@@
 %$\rightarrow$\CodeIn{ \scriptsize{android.view.ViewRoot.checkThread()}}
-\vspace*{-2.0ex} \Caption{{\label{fig:report} A report
-generated by our tool to reveal the potential error in
-Figure~\ref{fig:androiderror}. This report indicates a 
-full method call chain that causes the error. $\rightarrow$ represents
+\vspace*{-2.0ex} \Caption{{\label{fig:report} Our tool reports
+a method call chain that reveals the potential error in
+Figure~\ref{fig:androiderror}. $\rightarrow$ represents
 the call relationship
@@
 every possible path from its entry nodes, checking whether
-there exists a path to access a GUI object from a non-UI thread. If 
-a suspicious path is found,
-the static analysis issues a potential warning in the form of a method
-call chain from the starting point, serving as the contextual information
-for developers to understand the error.
+any path accesses a GUI object from a non-UI thread. If 
+a suspicious path is found, the static analysis warns of a potential error.
+The warning is in the form of a method
+call chain from the starting point.
 As an example, Figure~\ref{fig:report} shows a report produced
@@
 inspect the method call chain, understand how the error
-is triggered, and fix it if it is a real bug.
+could be triggered, and fix it if it is a real bug.
 
@@
 Given a sound call graph, our analysis is sound in that it does
-not miss true positives. GUI applications tend to use of reflection. And
-in the presence of reflection, however, it is
-non-trivial to compute a sound call graph with acceptable precision
-Existing call graph construction algorithms such as RTA~\cite{rta}
+not miss true positives. GUI applications tend to use reflection, and
+in the presence of reflection, existing call graph construction algorithms such as RTA~\cite{rta}
 and k-CFA~\cite{kcfa} fail to build a good call graph.
@@
 also compare its usefulness with existing call graph construction algorithms in
-our experiments. We also note that static analysis may report false positives due to its
+our experiments. Static analysis may report false positives due to its
 conservative nature, or multiple warnings that actually correspond
@@
 
-We implement an invalid thread error detection tool that supports
-four popular GUI frameworks namely SWT, Eclipse plugin environment,
+We implemented an invalid-thread-error detection tool that supports
+four popular GUI frameworks: SWT, Eclipse plugin environment,
 Swing, and Android. Swing and SWT are the
 two dominant GUI frameworks for desktop Java applications.
-Eclipse is the de-facto standard IDE for Java. Android is the No. 1 platform for
+Eclipse is the de-facto standard IDE for Java. Android is the \#1 platform for
 mobile applications with market share 56\% as of Sep 2011.
 Although our technique is applicable to any GUI
-frameworks with the single-GUI-thread rule, a specific framework
-may have its own treatment of \textit{UI thread} and \textit{program 
+framework with the single-GUI-thread rule. Each framework
+has its own definition of \textit{UI thread} and \textit{program 
 entry points}. Thus, our implementation is parameterized with respect to
-those those framework-specific parts.
-
-%Applications built on top of different GUI frameworks have different
-%treatment of \textit{UI thread} and \textit{call graph entry nodes}.
-%Instantiating the general technique for each framework only requires few
-%human effort. The primary framework-specific part is to specify
-%the \textit{UI thread} and \textit{call graph entry nodes}.
+those framework-specific parts.
 
 Our tool works in a fully automatic, push-button manner, and scales to realistic programs.
-We evaluated our implementation on 9 subjects comprising over 76000 LOC.
+We evaluated our implementation on 9 programs comprising over 76000 LOC.
 The experiment results demonstrate
 that: our technique is effective (it found 11 real-world errors
-from four supported frameworks, and produced significantly less
-false positives and redundant warnings than the simple analysis);
+from four supported frameworks and produced 10 false positive warnings);
 our reflection-aware call graph construction algorithm is
@@
 and our proposed
-heuristics are useful (it significantly reduces the number of
-false positives and redundant warnings).
+heuristics significantly reduce the number of
+false positives and redundant warnings.
 
@@
 the invalid thread access error detection problem for multithreaded GUI applications.
-%, and formulate it
-%as a call graph reachability problem.
 
@@
 and present a general error detection technique.
-In addition, to deal with the unique features in
-multithreaded GUI programs, we propose a reflection-aware
+In addition, we use a reflection-aware
 call graph construction algorithm. (Section~\ref{sec:technique}).
 
-\item \textbf{Implementation.} We implemented our technique, and
+\item \textbf{Implementation.} We implemented our technique and
 instantiated it for four
 popular GUI platforms: SWT, Eclipse plugin, Swing, and Android (Section~\ref{sec:implementation}). Our
-tool implementation is publicly available at:
-\url{http://guierrordetector.googlecode.com}
+tool implementation is publicly available at
+\url{http://guierrordetector.googlecode.com}.
 
-\item \textbf{Evaluation.} We performed an experiment on 9 subjects
+\item \textbf{Evaluation.} We applied our tool to 9 programs 
 from 4 different frameworks, comprising over 76000 LOC. The results

### 2012-02-03 GUIErrorDetector/paper/evaluation.tex
improve introduction / abstract, and correct the wordings
changes based on new comments

@@
 Our experiment objective is three-fold: to demonstrate the effectiveness
-of our approach in detecting real bugs in multithreaded GUI applications, to 
+of our approach in detecting real errors in multithreaded GUI applications, to 
 compare the reflection-aware call graph construction algorithm
@@
 We also compare our technique with
-a straightforward approach (Section~\ref{sec:straightforward}),  compare the reflection-aware call graph
-construction algorithms with existing algorithms (Section~\ref{sec:reflectionaware}), and
-evaluate different graph search strategies in error detection (Section~\ref{sec:search}).
+a straightforward approach (Section~\ref{sec:straightforward}),  compare
+different call graph construction algorithms (Section~\ref{sec:reflectionaware}), and
+evaluate various graph search strategies in error detection (Section~\ref{sec:search}).
  Finally, we show that the set of proposed heuristics are effective
@@
 
-We chose subjects belonging to various categories from all subjects satisfying
+We randomly chose subjects belonging to various categories from subjects satisfying
 the above criteria. The subjects used in our experiment are shown in Table~\ref{table:subjects},
@@
 S3dropbox~\cite{s3dropbox} implements a client that allows users
-to drag and drop files, which are then uploaded to their Amazon S3 accounts. SodokuSolver~\cite{sudokusolver}
-computes Sodoku solutions efficiently using mutlithreading execution.
+to drag and drop files, which are then uploaded to their Amazon S3 accounts. SudokuSolver~\cite{sudokusolver}
+computes Sudoku solutions efficiently using mutlithreading execution.
 
@@
 used two configurations: with and without the reflection-aware algorithm 
-(Section~\ref{sec:cg}).  We did not use other expensive algorithms like $k$-CFA ($k >$ 1),
+(Section~\ref{sec:cg}).  We did not use more expensive algorithms like $k$-CFA ($k >$ 1),
 because they can not scale to our subject programs.
@@
 S3dropbox, and SudokuSolver are previously  unknown. As a comparison, the
-results of a straightforward approach (Section~\ref{sec:straightforward}) are show at the far right.} }
+results of a straightforward approach (Section~\ref{sec:straightforward}) are shown at the far right.} }
 \end{table*}
@@
 the 1-CFA algorithm found most errors (11 in total) and least
-warnings (21 in total). The trade-offs of using other call graph
+false positive warnings (10 in total). A comparison of using other call graph
 construction algorithms will be explained in Section~\ref{sec:reflectionaware}.
@@
 Among the 21 warnings issued by using the 1-CFA algorithm, 11
-warnings reveals 11 distinct errors, in which 6 are previously-unknown,
-2 warnings are false positive, and the remaining 8 
-are redundant warnings.
+warnings reveals 11 distinct errors (6 are previously-unknown),
+2 warnings are false positive, and the remaining 8 warnings
+are redundant.
 
@@
 invalid thread access errors is to wrap every GUI accessing operation
-with message passing (i.e., via the safe methods). Thus, a
+with message passing (i.e., via the safe UI methods). Thus, a
 straightforward way to detect potential invalid error
@@
 The far right column in Table~\ref{table:results} shows the results.
-The results show that this straightforward approach can identify every
-error that our technique has found, but issue a huge number of false
-positives and redundant warnings. The primary reason is that this simple approach
+The results show that this straightforward approach could identify every
+error that our technique found, but issue a huge number of warnings.
+The primary reason is that this simple approach
 does not globally reason about calling relationship between
-threads, UI-accessing methods, and safe methods, thus it often incorrectly
+threads, UI-accessing methods, and safe UI methods, thus it often incorrectly
 classifies GUI accessing operations which will never be executed
@@
 used in our experiments. As shown in Table~\ref{table:results},  1-CFA found
-more errors with less warnings than the other two algorithms. This
+more errors with less false positive warnings than the other two algorithms. This
 is because RTA and 0-CFA do not consider the calling context when
@@
 mix the same method calls by different callers into a single node, thus
-introducing imprecision.
+introduce imprecision.
 
@@
 
-In contrast, the error-related GUI objects in the other two Android applications (Fennec
-and SGTPuzzler) are created explicitly, so that a normal call graph construction
-algorithm can create a sufficiently complete call graph.
+For other two Android applications (Fennec and SGTPuzzler), the errors
+can be found by using a standard call graph construction algorithm. This
+is because the error-related GUI objects are created explicitly, so that
+the standard call graph construction algorithm is sufficient.
 
@@
 
-The first variant uses DFS for graph traverse by changing method \CodeIn{getReachableStartsByBFS(cg)}
-to \CodeIn{getReachableStartsByDFS(cg)} on line 7, changing line 9 to
+The first variant uses DFS for graph traverse by changing
+line 7 in Figure~\ref{fig:androiderror} to:
 $\mathit{fringe}$ $\leftarrow$ $\mathit{an}$ $\mathit{empty}$ $\mathit{stack}$,
-and changing queue operations (\CodeIn{enqueue} and \CodeIn{dequeue} on lines 11, 13, and 25 of Figure~\ref{fig:androiderror})
-to the correspondiing statck operations (\CodeIn{push} and \CodeIn{pop}).
+and changing queue operations (\CodeIn{enqueueAll}, \CodeIn{dequeue}, and \CodeIn{enqueue} on lines 9,
+11, and 23 in Figure~\ref{fig:androiderror}, respectively)
+to the corresponding statck operations (\CodeIn{pushAll}, \CodeIn{pop} and \CodeIn{push}).
 
@@
 The reason is that DFS tends to search deeper into the graph, and the path it returns
-is more likely not to be the shortest one. In the FileBunker subject, the path
-returned by DFS is much longer, and does not actually exist.
+may not be the shortest one and are more likely to be an infeasible path in practice.
+For the FileBunker subject, paths
+returned by DFS are much longer than BFS, and do not actually exist.
 
@@
 The second variant uses exhaustive search to find potential errors. This variant
-enumerates all non-cyclic paths from the start nodes, and then checks whether each
-path spawns a new thread and accesses GUI object without using safe methods. As
+enumerates all non-cyclic paths from all reachable \CodeIn{Thread.start()} nodes
+to each UI-accessing node, and then checks whether each
+path spawns a new thread and accesses GUI object without using safe UI methods. As
 a result, this variant run out of memory on all subjects. We checked
 the output paths before the algorithm terminated, and found none of the explored
-path revealed a valid error. This is because the number of
+path revealed a real error. This is because the number of
 non-cyclic paths in a graph is exponentially large to the graph node number.
-For a realistic call graph which often contains thousands of nodes, for which
+For a realistic call graph which often contains thousands of nodes,
 it is impossible to enumerate all paths in practice.
@@
 or redundant warnings. Specifically, heuristic filters 1 and 2 identified
-32.48\% of the warnings as likely false positives, and filters 3, 4,
-and 5 identified 67.48\% of the warnings as redundant warnings.
+29.38\% of the warnings as likely false positives, and filters 3, 4,
+and 5 identified 70.58\% of the warnings as redundant warnings.
 Remarkably, the 3rd heuristic filter for removing lexically redundant
-reports is the most effective one on the evaluated subjects: it removes 35277 redundant warnings.
+reports is the most effective one on the evaluated subjects: it removes 37019 redundant warnings.
 
@@
  \fontsize{9pt}{\baselineskip}\selectfont
-\setlength{\tabcolsep}{.81\tabcolsep}
+\setlength{\tabcolsep}{.46\tabcolsep}
 \hspace*{-0.2cm}
@@
  Subject & Before & \#W & \#W & \#W & \#W& \#W \\
- Program & Filtering & $F_1$ & $F_2$ & $F_3$&$F_4$ & $F_5$\\
+ Program & Filtering & $F_1$ & $F_{1,2}$ & $F_{1,2,3}$&$F_{1,2,3,4}$ & $F_{1,2,3,4,5}$\\
 \hline \hline
@@
  \hline
- HundsonEclipse&  3192 &  2417 &  1696 & 9 &  3 & 3\\
+ HundsonEclipse&  3192 &  2417 &  2417 & 9 &  3 & 3\\
  \hline
@@
  \hline
- S3dropbox&  45528 &  31978 &  30975 & 9 &  1 & 1\\
+ S3dropbox&  45528 &  31978 &  31978 & 9 &  1 & 1\\
  \hline
@@
  \hline
- Fennec &  122 &  84 & 84 & 84 &  9 & 3\\
+ Fennec &  122 &  122 & 84 & 84 &  9 & 3\\
  \hline
- MyTracks &  1176 &  441 &  441 & 441 &  63 & 1 \\
+ MyTracks &  1176 &  1176 &  441 & 441 &  63 & 1 \\
 \hline
  \hline
- Total &  56214 &  39708 &  37955 &  2678 &  89 & 21 \\
+ Total &  56214 &  40470 &  39697 &  2678 &  89 & 21 \\
  \hline
@@
 \Caption{{\label{table:filters}Number of warnings after applying a set of
-heuristic filters (Section~\ref{sec:heuristic}). Column ``Before Filtering''
-shows the output warning number using the reflection-aware 1-CFA algorithm.
-Column ``\#W $F_i$'' represents the number of remaining warnings after applying
-filters 1 -- $i$. Numbers in last column are taken
-from Table~\ref{table:results}.
-Results of using other algorithms show similar patterns, which are omitted for brevity.} }
+heuristic filters. Column ``Before Filtering''
+shows the output warning number by the reflection-aware 1-CFA algorithm.
+Results of using other algorithms show similar patterns, which are omitted for brevity.
+Column ``\#W $F_{i,...,j}$'' represents the number of remaining warnings after applying
+the $i$th to $j$th filters as defined in Section~\ref{sec:heuristic}.
+Numbers in last column are taken from the subcolumn ``\#Warnings"
+under column ``1-CFA'' in Table~\ref{table:results}.
+} }
 \end{table}

### 2012-02-03 GUIErrorDetector/paper/implementation.tex
changes based on new comments

@@
 We implemented the proposed technique using the WALA framework~\cite{walatutorial}.
-Our prototype tool takes Java bytecode as inputs, works in a fully
+Our prototype tool takes Java bytecode as input, works in a fully
 automatic and push-button way to detect potential invalid thread access
 errors, and scales to realistic programs.
-Optionally, users may specify additional heuristics to guide call graph
-traverse, and annotate call relationships for native methods (Section~\ref{sec:heuristic}).
+
+%Optionally, users may specify additional heuristic filters (Section~\ref{sec:heuristic}) %to guide call graph traverse
+%, and annotate call relationships for native methods (Section~\ref{sec:annotation}).
 
 Our current implementation supports four widely-used GUI frameworks, namely
-SWT, Eclipse plugin development, Java Swing, and Android.
-Our implementation %handles all of the Java language, and
-also takes
-all dependent libraries (e.g., \CodeIn{rt.jar} and \CodeIn{android.jar})
-into analysis. We implemented the reflection-aware call graph construction
- algorithm (Section~\ref{sec:cg})
-using WALA's \textit{bypass logic}. Our tool parses the configuration file
-in an Android application and modifies the bytecode to replace all
-reflection calls with object creation instructions.
+SWT, Eclipse plugin development, Swing, and Android.
+%, including dependent libraries such as \CodeIn{rt.jar} and \CodeIn{android.jar}.
+%into analysis. 
+We implemented the reflection-aware call graph construction
+ algorithm (Section~\ref{sec:cg}) using WALA's \textit{bypass logic}.
+Unlike similar tools~\cite{Payet:2011:SAA:2032266.2032299}, our tool
+does not require a separated
+pass of program instrumentation; instead, it
+parses the configuration file in an Android application,
+and then intercepts the call graph construction
+process on-the-fly to replace all reflection calls with object creation statements.
 Since Android applications are often fully encrypted and shipped in Dalvik

### 2012-02-03 GUIErrorDetector/paper/introduction.tex
Use correct font for curly braces in code listings
changes based on new comments

@@
 Many popular GUI frameworks such as Swing~\cite{swing}, SWT~\cite{swt}, Eclipse plugin~\cite{eclipse},
-Android~\cite{android}, Qt~\cite{qt}, MacOS Cocoa~\cite{macos},
-and X Windows~\cite{xwindow}
+Android~\cite{android}, Qt~\cite{qt}, and MacOS Cocoa~\cite{macos}
 adopt the \textit{single-GUI-thread rule}:
@@
  ensure that all GUI objects are accessed only by the UI thread.
-If not, an \textit{invalid thread access error} will occur.
+If not, an \textit{invalid thread access error} will occur. This may
+terminate the application, but it is considered preferable
+to nondeterministic concurrency errors.
 
@@
      \}
-
 \end{alltt}
 \end{CodeOut}
-\vspace*{-2.0ex} \Caption{{\label{fig:androiderror} A real
-bug reported on 11/17/2011 in Mozilla firefox release 10.0.a.rc3
-for the Android platform (bugzilla ID: 703256). On line 74, \CodeIn{LayerView}'s constructor
+\vspace*{-3.0ex} \Caption{{\label{fig:androiderror} 
+Bug 703256 reported on 11/17/2011 in Fennec (Mozilla Firefox for Android)
+release 10.0.a.rc3. On line 74, \CodeIn{LayerView}'s constructor
 calls method \CodeIn{setRenderer} which 
@@
 It is infeasible for testing to cover the enormous space of possible interactions
-with a GUI, in that each sequence of GUI events can result in
-a difficult state, and each GUI event may need to be evaluated in all of
+with a GUI. Each sequence of GUI events can result in
+a different state, and each GUI event may need to be evaluated in all of
 these states. A well-developed software system like Eclipse
@@
 
+{\vspace{2mm}
+\hspace{3mm}\small{In class: org.mozilla.gecko.gfx.LayerRenderer}
+\vspace{-2mm}
 \begin{CodeOut}
 \begin{alltt}
-     /* In class: org.mozilla.gecko.gfx.LayerRenderer */
 220. public void onSurfaceChanged(GL10 gl, int width, int height) \{
 221.     gl.glViewport(0, 0, width, height);
-         \textbf{mView.post(new Runnable() \{}
-             \textbf{public void run() \{}
+         \textbf{mView.post(new Runnable() \ttlcb}
+             \textbf{public void run() \ttlcb}
 222.             mView.setViewportSize(new IntSize(width, height));
-             \textbf{\}}
-         \textbf{\});}
+             \textbf{\ttrcb}
+         \textbf{\ttrcb);}
      \}
 \end{alltt}
-\end{CodeOut}
+\end{CodeOut}}
 
@@
 %$\rightarrow$\CodeIn{ \scriptsize{android.view.ViewRoot.checkThread()}}
-\vspace*{-2.0ex} \Caption{{\label{fig:report} A report
-generated by our tool to reveal the potential error in
-Figure~\ref{fig:androiderror}. This report indicates a 
-full method call chain that causes the error. $\rightarrow$ represents
+\vspace*{-3.0ex} \Caption{{\label{fig:report} Our tool reports
+a method call chain that reveals the potential error in
+Figure~\ref{fig:androiderror}. $\rightarrow$ represents
 the call relationship
@@
 
-We implement an invalid thread error detection tool that supports
-four popular GUI frameworks namely SWT, Eclipse plugin environment,
+We implemented an invalid-thread-error detection tool that supports
+four popular GUI frameworks: SWT, Eclipse plugin environment,
 Swing, and Android. Swing and SWT are the
 two dominant GUI frameworks for desktop Java applications.
-Eclipse is the de-facto standard IDE for Java. Android is the No. 1 platform for
+Eclipse is the de-facto standard IDE for Java. Android is the \#1 platform for
 mobile applications with market share 56\% as of Sep 2011.
 Although our technique is applicable to any GUI
-frameworks with the single-GUI-thread rule, a specific framework
-may have its own treatment of \textit{UI thread} and \textit{program 
+framework with the single-GUI-thread rule, each framework
+has its own definition of \textit{UI thread} and \textit{program 
 entry points}. Thus, our implementation is parameterized with respect to
@@
 
-%Applications built on top of different GUI frameworks have different
-%treatment of \textit{UI thread} and \textit{call graph entry nodes}.
-%Instantiating the general technique for each framework only requires few
-%human effort. The primary framework-specific part is to specify
-%the \textit{UI thread} and \textit{call graph entry nodes}.
-
-Our tool works in a fully automatic, push-button manner, and scales to realistic programs.
-We evaluated our implementation on 9 subjects comprising over 76000 LOC.
+Our tool works in a fully automatic, push-button manner,
+and scales to realistic programs.
+We evaluated our implementation on 9 programs comprising over 76000 LOC.
 The experiment results demonstrate
 that: our technique is effective (it found 11 real-world errors
-from four supported frameworks, and produced significantly less
-false positives and redundant warnings than the simple analysis);
-our reflection-aware call graph construction algorithm is
-critical in finding errors in Android applications;
-and our proposed
-heuristics are useful (it significantly reduces the number of
-false positives and redundant warnings).
+from four supported frameworks and produced only 10 false positive warnings);
+our reflection-aware call graph construction algorithm helps in
+finding errors in Android applications;
+and our proposed heuristics significantly reduce the number of
+false positives and redundant warnings.
 

### 2012-02-03 GUIErrorDetector/paper/technique.tex
changes based on new comments

@@
 first constructs a static call graph for the tested program (line 2),
-then specifies entry nodes, UI-accessing nodes, and safe nodes
+then specifies entry nodes, UI-accessing nodes, and safe UI nodes
 for it on line 3, 4, and 5, respectively. Lines 3--5 are GUI framework-specific.
@@
 
-For each entry node, the algorithm uses standard Breadth First Search (BFS)
-to find all reachable \CodeIn{Thread.start()} nodes (line 7).
+The algorithm first finds all reachable \CodeIn{Thread.start()}
+nodes from the entry nodes (line 6).
+%For each entry node, the algorithm uses standard Breadth First Search (BFS)
+%to find all reachable \CodeIn{Thread.start()} nodes (line 7).
 Each \CodeIn{Thread.start()} node in a call graph indicates that a new,
 non-UI thread is spawned.  After that, from each \CodeIn{Thread.start()}
-node, the algorithm uses BFS again to find reachable UI-accessing methods (lines 9 -- 28).
-Specifically, it uses a queue to keep track of nodes to be visited (line 9),
-and stores all visited nodes to avoid infinite loop (line 10).
-The algorithm checks every successive node to be visited (line 18);
-it reports an error if that node is a UI-accessing method (lines 20, 21), or skips
-it if it is a safe UI method (lines 22, 23), or simply keeps traversing otherwise (line 25).
+node, the algorithm uses BFS to search for reachable UI-accessing
+methods (lines 9 -- 26).
+Specifically, it uses a queue to keep track of the nodes to be visited (line 7),
+and stores all visited nodes to avoid infinite loop (line 8).
+The algorithm checks every successive node to be visited (line 16):
+it reports an error if that node is a UI-accessing method (lines 18, 19), or skips
+it if it is a safe UI method (lines 20, 21), or simply keeps traversing otherwise (line 23).
 
@@
 the UI-accessing node as the error report.
-The method \CodeIn{createErrorReport} on line 20 does that. 
+The method \CodeIn{createErrorReport} on line 18 does that. 
 Figure~\ref{fig:androiderror} shows a method call chain from the entry
@@
 \textbf{Input}: a Java program $\mathit{P}$\\
-\textbf{Output}: a set of potential invalid thread access $\mathit{errors}$\\
+\textbf{Output}: a set of potential invalid thread access errors\\
 %\textbf{Auxiliary Methods:}\\
@@
 \STATE $\mathit{entryNodes}$ $\leftarrow$ getEntryNodes($\mathit{cg}$)
-\STATE $\mathit{uiAccessNodes}$ $\leftarrow$ getUIAccessNodes($\mathit{cg}$)
-\STATE $\mathit{safeNodes}$ $\leftarrow$ getSafeNodes($\mathit{cg}$)
-\FOR{each $\mathit{entryNode}$ in $\mathit{entryNodes}$}
-\STATE $\mathit{threadStartNodes}$ $\leftarrow$ getReachableStartsByBFS($\mathit{cg}$)
-\FOR{each $\mathit{threadStart}$ in $\mathit{threadStartNodes}$}
+\STATE $\mathit{uiAccessingNodes}$ $\leftarrow$ getUIAccessNodes($\mathit{cg}$)
+\STATE $\mathit{safeUINodes}$ $\leftarrow$ getSafeNodes($\mathit{cg}$)\\
+\COMMENT{get all reachable \CodeIn{thread.start()} nodes from entry nodes}
+\STATE $\mathit{threadStarts}$ $\leftarrow$ $\bigcup_{entry \in entryNodes}$ getReachableStarts($\mathit{entry}$)
+\COMMENT{keep the nodes to be visited next in a fringe}
 \STATE $\mathit{fringe}$ $\leftarrow$ an empty queue\\
@@
 \STATE $\mathit{visited}$ $\leftarrow$ $\emptyset$
-\STATE $\mathit{fringe}$.enqueue(getSuccNodes($\mathit{cg}$, $\mathit{threadStart}$))
+\STATE $\mathit{fringe}$.enqueueAll($\mathit{threadStarts}$)
 \WHILE{$\mathit{fringe}$.isNotEmpty()}
@@
 \FOR{each $\mathit{succNode}$ in getSuccNodes($\mathit{cg}$, $\mathit{node}$)}
-\IF{$\mathit{succNode}$ $\in$ $\mathit{uiAccessNodes}$}
+\IF{$\mathit{succNode}$ $\in$ $\mathit{uiAccessingNodes}$}
 \STATE $\mathit{newError}$ $\leftarrow$ createErrorReport($\mathit{entryNode, succNode}$)
 \STATE $\mathit{errors}$ $\leftarrow$ $\mathit{errors}$ $\cup$ $\mathit{newError}$
-\ELSIF{$\mathit{succNode}$ $\in$ $\mathit{safeNodes}$}
+\ELSIF{$\mathit{succNode}$ $\in$ $\mathit{safeUINodes}$}
 \STATE continue
@@
 \ENDWHILE
-\ENDFOR
-\ENDFOR
 \RETURN $errors$
@@
 for potential error-revealing paths, since BFS always returns the
-shortest path from the entry node to the UI-accessing node, and thus
-permits to produce small error reports. However,
+shortest path to the UI-accessing node, permitting
+to produce smaller error reports. However,
 other graph search strategies such as Depath-First Search (DFS) or
-exhaustive path search can also be employed. In our evaluation (Section~\ref{sec:search}),
-we empirically compared three different graph search strategies, and demonstrate that
-using BFS allows the algorithm to find more errors than DFS and
+exhaustive path search can also be employed. In our experiment (Section~\ref{sec:search}),
+we empirically compared three different graph search strategies, and demonstrated that
+using BFS, algorithm found more errors than DFS and
 exhaustive path search.
+
 Given a sound call graph, our algorithm is sound in that it does not
@@
 is parameterized by three methods on line 2, 3, and 8. How to
-instantiate it for Android applications is presented in Section~\ref{sec:cg}.
+instantiate it for the Android framework is presented in Section~\ref{sec:cg}.
 %This algorithm is parameterized by the call graph construction
@@
 reflection call \CodeIn{findViewById}. As a result, the built 
-call graph will miss the calling edge corresponding to the method
-call \CodeIn{setText} at line 10.
+call graph will miss the calling edge corresponding to the
+\CodeIn{setText} method call on line 10.
 
@@
 return instances of all subclasses of the declared type.
-On line 8, any existing call graph construction algorithm can be directly
-used.
+On line 8, any existing call graph construction algorithm can be applied.
 
@@
 As demonstrated in our experiments, using this reflection-aware call
-graph construction algorithm is critical to detect errors
+graph construction algorithm helps in detecting errors
 in Android applications.
@@
 In our experiments, 1 out of 9 programs uses native methods to interact with
-the underlying operating system, and we added 3 annotations for it. We manually
-searched the source files, and inspected the code to determine target methods
-that a native method will call, if there are any. We found this annotation,
-although requires manual effort to add, was useful: one real-world bug
+the underlying operating system. We manually
+searched the source files, inspected the code to determine possible target methods
+that may be called by a native method, and added 7 annotations for this program.
+We found such an annotation, was useful: one real-world bug
 can only be reported with using the user-provided annotations.
@@
 method is called when JVM terminates, and uses multithreading
-to dispose all GUI objects after the program exits.
+to dispose all GUI objects when the program exits.
 We encoded a list of common library calls by proposing
@@
 %\item
-\textbf{4. Filter Report With the Same $k$ Head Methods}. A method can call
+\textbf{4. Filter Report With the Same Head Methods from The Entry Node to \CodeIn{Thread.start()}}. A method can call
 multiple methods that access GUI objects, such as:
-
+\vspace{-1mm}
 \begin{CodeOut}
@@
 This filter compares two reported chains that have the same
-$k$ ($k$ is user-settable with a default value 5 as used in our
-experiments) head nodes, and removes the longer one.
+head nodes from the entry node to \CodeIn{Thread}.\CodeIn{start()},
+and removes the longer one.
+%$k$ ($k$ is user-settable with a default value 5 as used in our
+%experiments) head nodes, and removes the longer one.
 
 %\item
-\textbf{5. Filter Report With the Same $k$ Tail Methods}. A method
+\textbf{5. Filter Report With the Same Tail Methods from \CodeIn{Thread}.
+\CodeIn{start()}
+to the UI-accessing node}. A method
 can have multiple callers, so that method call chains with the same tail are likely
@@
 two reported method call chains that share the same 
-$k$ ($k$ is user-settable with a default value 5 as used in our
-experiments) tail nodes, and removes the longer one.
+tail nodes from \CodeIn{Thread.start()} to the UI-accessing node, and
+removes the longer one.
 
@@
 
-All above 5 filters are based on heuristics, and thus are not sound in
-that it may filter real bugs. However, as we will show in
+Among the above 5 filters, filters 2 and 3 are sound
+in that they will not filter real bugs, and other 3 filters
+are based on heuristics. However, as we will show in
 our experiments, these filters work remarkably well in practice.
@@
 \item \textbf{UI-accessing nodes: } SWT provides explicit
-runtime checking for illegal thread access. Any methods for manipulating
+runtime checking for illegal thread accesses. Any methods for manipulating
 GUI object must call methods \CodeIn{Display.checkWidget}
@@
 methods in the class that implements \CodeIn{org.eclipse.swt.internal.\\SWTEventListener}) are
-called back from the UI thread, thus are used as call graph entry nodes.
+always called back from the UI thread, thus are used as call graph entry nodes.
 
@@
 the \CodeIn{ViewRoot.checkThread} method.
-Thus, we treat 
 %method. This method is the only place where Android checks

### 2012-02-03 GUIErrorDetector/paper/evaluation.tex
revise the algorithm and UI-accessing methods

@@
 line 7 in Figure~\ref{fig:androiderror} to:
-$\mathit{fringe}$ $\leftarrow$ $\mathit{an}$ $\mathit{empty}$ $\mathit{stack}$,
+$\mathit{worklist}$ $\leftarrow$ $\mathit{an}$ $\mathit{empty}$ $\mathit{stack}$,
 and changing queue operations (\CodeIn{enqueueAll}, \CodeIn{dequeue}, and \CodeIn{enqueue} on lines 9,

### 2012-02-03 trunk/GUIErrorDetector/paper/technique.tex
Fix paragraph spacing
revise the algorithm and UI-accessing methods

@@
 potential errors at the method level can be sufficient in most cases.
-Thus, we believe using the call graph is well suited for this problem while
-compared with other program representations like control flow graph or
-program dependence graph.
+%Thus, we believe using the call graph is well suited for this problem while
+%compared with other program representations like control flow graph or
+%program dependence graph.
 
@@
 first constructs a static call graph for the tested program (line 2),
-then specifies entry nodes, UI-accessing nodes, and safe nodes
+then specifies entry nodes, UI-accessing nodes, and safe UI nodes
 for it on line 3, 4, and 5, respectively. Lines 3--5 are GUI framework-specific.
 As an example, for a SWT desktop application, the entry nodes include
-the single main method, UI-accessing nodes include all methods that
-call method \CodeIn{Display.checkWidget} or \CodeIn{Display.checkDevice},
-and safe methods include two SWT helper methods \CodeIn{Display.asyncExec}  and
+the single main method, UI-accessing nodes include 
+\CodeIn{Display.checkWidget} and \CodeIn{Display.checkDevice},
+and safe UI methods include two SWT helper methods \CodeIn{Display.asyncExec}  and
 \CodeIn{Display.syncExec} for message passing. The detailed instantiation
@@
 
-For each entry node, the algorithm uses standard Breadth First Search (BFS)
-to find all reachable \CodeIn{Thread.start()} nodes (line 7).
+The algorithm first performs graph traversal to find all reachable \CodeIn{Thread.start()}
+nodes from the entry nodes (line 6).
+%For each entry node, the algorithm uses standard Breadth First Search (BFS)
+%to find all reachable \CodeIn{Thread.start()} nodes (line 7).
 Each \CodeIn{Thread.start()} node in a call graph indicates that a new,
-non-UI thread is spawned.  After that, from each \CodeIn{Thread.start()}
-node, the algorithm uses BFS again to find reachable UI-accessing methods (lines 9 -- 28).
-Specifically, it uses a queue to keep track of nodes to be visited (line 9),
-and stores all visited nodes to avoid infinite loop (line 10).
-The algorithm checks every successive node to be visited (line 18);
-it reports an error if that node is a UI-accessing method (lines 20, 21), or skips
-it if it is a safe method (lines 22, 23), or simply keeps traversing otherwise (line 25).
+non-UI thread is spawned.  The \CodeIn{Thread.start()}
+nodes act as the sources in the main graph traversal.
+The algorithm uses BFS to search for reachable UI-accessing
+methods (lines 10 -- 25).
+The algorithm stops the traversal if it reaches a UI-accessing
+method (lines 16 -- 18) or a safe UI method (lines 19, 20).
+%Specifically, it uses a queue to keep track of the nodes to be visited (line 7),
+%and stores all visited nodes to avoid infinite loop (line 8).
+%The algorithm checks every successive node to be visited (line 16):
+%it reports an error if that node is a UI-accessing method (lines 18, 19), or skips
+%it if it is a safe UI method (lines 20, 21), or simply keeps traversing otherwise (line 23).
 
-Note that when the algorithm determines that a UI-accessing method may be invoked
-by a non-UI thread, it computes a method call chain from the entry node to
-the UI-accessing node as the error report.
-The method \CodeIn{createErrorReport} on line 20 does that. 
-Figure~\ref{fig:androiderror} shows a method call chain from the entry
-node \CodeIn{LayerView.<init>} to the UI-accessing node \CodeIn{ViewRoot}.\CodeIn{recomputeViewAttributes}
-(for the sake of clarification, we also show the checking method \CodeIn{checkThread} in the reported warning).
+The error message created by the method \CodeIn{createErrorReport} on line 17
+includes the method call chain from the entry node to the UI-accessing node
+as the error report. For brevity, we do not show the data structures that store
+the current call chain.
+Figure~\ref{fig:report} shows a method call chain from the entry
+node \CodeIn{LayerView.<init>} to the UI-accessing node \CodeIn{ViewRoot}.\CodeIn{checkThread}.
+%Note that when the algorithm determines that a UI-accessing method may be invoked
+%by a non-UI thread, it computes a method call chain from the entry node to
+%the UI-accessing node as the error report.
+% does that.
 
@@
 \STATE $\mathit{entryNodes}$ $\leftarrow$ getEntryNodes($\mathit{cg}$)
-\STATE $\mathit{uiAccessNodes}$ $\leftarrow$ getUIAccessNodes($\mathit{cg}$)
-\STATE $\mathit{safeNodes}$ $\leftarrow$ getSafeNodes($\mathit{cg}$)
-\FOR{each $\mathit{entryNode}$ in $\mathit{entryNodes}$}
-\STATE $\mathit{threadStartNodes}$ $\leftarrow$ getReachableStartsByBFS($\mathit{cg}$)
-\FOR{each $\mathit{threadStart}$ in $\mathit{threadStartNodes}$}
-\STATE $\mathit{fringe}$ $\leftarrow$ an empty queue\\
-\COMMENT{keep all visited nodes to avoid infinite loop}
+\STATE $\mathit{uiAccessingNodes}$ $\leftarrow$ getUIAccessNodes($\mathit{cg}$)
+\STATE $\mathit{safeUINodes}$ $\leftarrow$ getSafeNodes($\mathit{cg}$)\\
+\COMMENT{get all reachable \CodeIn{thread.start()} nodes from entry nodes}
+\STATE $\mathit{threadStarts}$ $\leftarrow$ $\bigcup_{entry \in entryNodes}$ getReachableStarts($\mathit{entry}$)
+\COMMENT{keep the nodes to be visited next in a worklist}
+\STATE $\mathit{worklist}$ $\leftarrow$ an empty queue\\
+\STATE $\mathit{worklist}$.enqueueAll($\mathit{threadStarts}$)
 \STATE $\mathit{visited}$ $\leftarrow$ $\emptyset$
-\STATE $\mathit{fringe}$.enqueue(getSuccNodes($\mathit{cg}$, $\mathit{threadStart}$))
-\WHILE{$\mathit{fringe}$.isNotEmpty()}
-\STATE $\mathit{node}$ $\leftarrow$ $\mathit{fringe}$.dequeue()
+\WHILE{$\mathit{worklist}$.isNotEmpty()}
+\STATE $\mathit{node}$ $\leftarrow$ $\mathit{worklist}$.dequeue()
 \IF{$\mathit{node}$ $\in$ $\mathit{visited}$}
@@
 \STATE $\mathit{visited}$ $\leftarrow$ $\mathit{visited}$ $\cup$ $\mathit{node}$
-\FOR{each $\mathit{succNode}$ in getSuccNodes($\mathit{cg}$, $\mathit{node}$)}
-\IF{$\mathit{succNode}$ $\in$ $\mathit{uiAccessNodes}$}
-\STATE $\mathit{newError}$ $\leftarrow$ createErrorReport($\mathit{entryNode, succNode}$)
+\IF{$\mathit{node}$ $\in$ $\mathit{uiAccessingNodes}$}
+\STATE $\mathit{newError}$ $\leftarrow$ createErrorReport($\mathit{node}$)
 \STATE $\mathit{errors}$ $\leftarrow$ $\mathit{errors}$ $\cup$ $\mathit{newError}$
-\ELSIF{$\mathit{succNode}$ $\in$ $\mathit{safeNodes}$}
+\ELSIF{$\mathit{node}$ $\in$ $\mathit{safeUINodes}$}
 \STATE continue
 \ELSE
-\STATE $\mathit{fringe}$.enqueue($\mathit{succNode}$)
+\STATE $\mathit{worklist}$.enqueueAll(getSuccNodes($\mathit{cg}$, $\mathit{node}$))
 \ENDIF 
-\ENDFOR
 \ENDWHILE
-\ENDFOR
-\ENDFOR
 \RETURN $errors$
@@
 for potential error-revealing paths, since BFS always returns the
-shortest path from the entry node to the UI-accessing node, and thus
-permits to produce small error reports. However,
+shortest path to the UI-accessing node, permitting
+smaller error reports. However,
 other graph search strategies such as Depath-First Search (DFS) or
-exhaustive path search can also be employed. In our evaluation (Section~\ref{sec:search}),
-we empirically compared three different graph search strategies, and demonstrate that
-using BFS allows the algorithm to find more errors than DFS and
+exhaustive path search can also be employed. In our experiment (Section~\ref{sec:search}),
+we empirically compared three different graph search strategies, and demonstrated that
+using BFS, algorithm found more errors than DFS and
 exhaustive path search.
+
 Given a sound call graph, our algorithm is sound in that it does not
@@
 \begin{alltt}
-
 <LinearLayout>
@@
 \end{CodeOut}
-\caption{Sample GUI application code on the Android platform. The layout
+\vspace*{-3.0ex} \caption{Sample GUI application code on the Android platform. The layout
 XML file (the top) specifies a Button object declaratively, 
@@
 %\ENDWHILE
-\vspace{-2mm}
 \end{algorithmic}
+\vspace{-3mm}
 \caption{A reflection-aware call graph construction algorithm. Lines
-1--7 show a simple program transformation to replace reflection calls
+1--7 are a simple program transformation to replace reflection calls
 with object creations, and line 8 builds the call graph using
-the existing call graph construction algorithms. This algorithm
-is parameterized by three methods on line 2, 3, and 8. How to
-instantiate it for Android applications is presented in Section~\ref{sec:cg}.
+an existing call graph construction algorithm. This algorithm
+is parameterized by two methods on lines 2 and 3. 
+How to instantiate it for the Android framework is presented in Section~\ref{sec:cg}.
 %This algorithm is parameterized by the call graph construction
@@
 
-GUI applications tend to use reflection intensively. In particular, GUI applications built on 
-top of the Android framework often use configuration files and reflection to specify GUI layout.
-The heavy use of reflection makes many existing call graph construction algorithms such as RTA~\cite{rta}
+%GUI applications tend to use reflection intensively. In particular,
+GUI applications built on top of the Android framework
+use configuration files and reflection to specify GUI layout.
+As a result, call graph construction algorithms such as RTA~\cite{rta}
 and k-CFA~\cite{kcfa} fail to build a sufficiently complete call graph.
@@
 When analyzing the code in Figure~\ref{fig:sampleandroid}, existing call graph algorithms
-fail to conclude that variable \CodeIn{button} declared at line 7
-point to a \CodeIn{Button} object due to its limitation in deal with the
+fail to conclude that the variable \CodeIn{button} declared at line 7
+points to a \textit{non-null} \CodeIn{Button} object due to its limitation in deal with the
 reflection call \CodeIn{findViewById}. As a result, the built 
-call graph will miss the calling edge corresponding to the method
-call \CodeIn{setText} at line 10.
+call graph will exclude the calling edge corresponding to the
+\CodeIn{setText} method call on line 10.
 
@@
 To address this limitation, we present an algorithm to construct
-a reflection-aware call graph based on simple program transformation.
-The basic idea to replace reflection calls with explicit object
+a reflection-aware call graph based on a simple program transformation.
+The basic idea is to replace reflection calls with explicit object
 creation statements, pretending that the corresponding concrete object
 has been created.  The algorithm is shown in Figure~\ref{fig:cgalgorithm}.
-It consists of two steps. The first step is a simple program
+It consists of two steps. The first step (lines 1 -- 7) is a simple program
 transformation to replace reflection calls with object creation statements, and
-the second step is to use an existing call graph construction algorithm
+the second step (line 8) uses an existing call graph construction algorithm
 to build the graph on the transformed program. In our context,
@@
 of the methods in the \CodeIn{java.lang.reflection} package.
-In Figure~\ref{fig:cgalgorithm}, lines 1--7 show
-the first step of program transformation. The algorithm iterates through every statement
-in an analyzed program. When it sees a reflection call, the algorithm
+%In Figure~\ref{fig:cgalgorithm}, lines 1--7 show
+%the first step of program transformation. The algorithm iterates through every statement
+%in an analyzed program.
+When it sees a reflection call, the algorithm
 determines a set of possible objects that might be created.
-After that, the algorithm creates a statement which non-deterministically
-returns a new object from the object set. Line 8 is the second step
-to build a call graph on the transformed program.
+After that, the algorithm creates a statement that non-deterministically
+returns a new object from the object set.
+%Line 8 is the second step
+%to build a call graph on the transformed program.
 
-This algorithm is parameterized in three places:
-line 2, line 3, and line 8. Currently, we instantiated it
-for Android applications as follows. On line 2,
-the predicate isReflectionCall returns true
-if the $statement$ is a \CodeIn{findViewById(id)} method call. On line 3, method
-\CodeIn{getAllObjectsThatMaybeCreated} parses the associated XML configuration
+This algorithm is parameterized by two methods on
+lines 2 and 3. When instantiated for the Android framework,
+the predicate isReflectionCall on line 2 returns true
+if the $statement$ is a \CodeIn{findViewById(id)} method call, and the method
+getAllObjectsThatMaybeCreated on line 3 parses the associated XML configuration
 file in an Android application to extract the class declaration
  correspondinig to the given \CodeIn{id} value. If the \CodeIn{id}
-value is dynamically generated, the method will conservatively
+value is dynamically generated, this method will conservatively
 return instances of all subclasses of the declared type.
-On line 8, any existing call graph construction algorithm can be directly
-used.
+%On line 8, any existing call graph construction algorithm can be applied.
 
@@
 As demonstrated in our experiments, using this reflection-aware call
-graph construction algorithm is critical to detect errors
-in Android applications.
+graph construction algorithm helps in detecting errors
+in Android applications (Section~\ref{sec:evaluation}).
 
@@
 %\item
-\textbf{4. Filter Report With the Same $k$ Head Methods}. A method can call
+\textbf{4. Filter Report With the Same Head Methods from The Entry Node to \CodeIn{Thread.start()}}. A method can call
 multiple methods that access GUI objects, such as:
+\vspace{-1mm}
 \begin{CodeOut}
@@
 
-\item \textbf{UI-accessing nodes: } SWT provides explicit
-runtime checking for illegal thread access. Any methods for manipulating
-GUI object must call methods \CodeIn{Display.checkWidget}
-or \CodeIn{Display.checkDevice} to check whether the current
-thread is the UI thread or not.
-Thus, we treat nodes (in both user code and framework code) corresponding to the methods
-calling these two methods as UI-accessing nodes.
+\item \textbf{UI-accessing nodes: } the \CodeIn{Display.checkWidget}
+and \CodeIn{Display.} \CodeIn{checkDevice} methods. SWT uses the above
+two methods to explicitly check illegal thread accesses at runtime.
+Any methods for manipulating GUI object must call (one of) these two methods
+ to determine whether the current thread is the UI thread or not.
+%Thus, we treat nodes (in both user code and framework code) corresponding to the methods
+%calling these two methods as UI-accessing nodes.
 %must be invoked
@@
 methods in the class that implements \CodeIn{org.eclipse.swt.internal.\\SWTEventListener}) are
-called back from the UI thread, thus are used as call graph entry nodes.
+always called back from the UI thread, thus are used as call graph entry nodes.
 
-\item \textbf{UI-accessing nodes} and \textbf{Safe methods} are the same as SWT.
+\item \textbf{UI-accessing nodes} and \textbf{Safe UI methods} are the same as SWT.
 
@@
 
-\item \textbf{UI-accessing nodes: }every method calling \CodeIn{ViewRoot.checkThread}.
+\item \textbf{UI-accessing nodes: }the \CodeIn{ViewRoot.checkThread} method.
 Like SWT, Android explicitly checks whether

### 2012-02-04 GUIErrorDetector/paper/evaluation.tex
fix inconsistent places

--- 2012-02-03 GUIErrorDetector/paper/evaluation.tex
@@
 The first variant uses DFS for graph traverse by changing
-line 7 in Figure~\ref{fig:androiderror} to:
-$\mathit{fringe}$ $\leftarrow$ $\mathit{an}$ $\mathit{empty}$ $\mathit{stack}$,
-and changing queue operations (\CodeIn{enqueueAll}, \CodeIn{dequeue}, and \CodeIn{enqueue} on lines 9,
-11, and 23 in Figure~\ref{fig:androiderror}, respectively)
-to the corresponding statck operations (\CodeIn{pushAll}, \CodeIn{pop} and \CodeIn{push}).
-
+line 7 in Figure~\ref{fig:detectalgorithm} to:
+$\mathit{worklist}$ $\leftarrow$ $\mathit{an}$ $\mathit{empty}$ $\mathit{stack}$,
+and changing queue operations (\CodeIn{dequeue}, and \CodeIn{enqueueAll} on lines 11, and
+22 in Figure~\ref{fig:androiderror}, respectively)
+to the corresponding statck operations (\CodeIn{pop}, and \CodeIn{pushAll}).
 As a result, this variant found 8 errors in total and missed 1 error in the FileBunker subject.

### 2012-02-04 GUIErrorDetector/paper/technique.tex
fix inconsistent places

@@
 As an example, for a SWT desktop application, the entry nodes include
-the single main method, UI-accessing nodes include all methods that
-call method \CodeIn{Display.checkWidget} or \CodeIn{Display.checkDevice},
+the single main method, UI-accessing nodes include methods
+\CodeIn{Display.checkWidget} and \CodeIn{Display.checkDevice},
 and safe UI methods include two SWT helper methods \CodeIn{Display.asyncExec}  and
@@
 
-The algorithm first finds all reachable \CodeIn{Thread.start()}
+The algorithm first performs graph traversal to find all reachable \CodeIn{Thread.start()}
 nodes from the entry nodes (line 6).
@@
 Each \CodeIn{Thread.start()} node in a call graph indicates that a new,
-non-UI thread is spawned.  After that, from each \CodeIn{Thread.start()}
-node, the algorithm uses BFS to search for reachable UI-accessing
-methods (lines 9 -- 26).
-Specifically, it uses a queue to keep track of the nodes to be visited (line 7),
-and stores all visited nodes to avoid infinite loop (line 8).
-The algorithm checks every successive node to be visited (line 16):
-it reports an error if that node is a UI-accessing method (lines 18, 19), or skips
-it if it is a safe UI method (lines 20, 21), or simply keeps traversing otherwise (line 23).
+non-UI thread is spawned.  The \CodeIn{Thread.start()}
+nodes act as the sources in the main graph traversal.
+The algorithm uses BFS to search for reachable UI-accessing
+methods (lines 10 -- 24).
+The algorithm stops the traversal if it reaches a UI-accessing
+method (lines 16 -- 18) or a safe UI method (lines 19, 20).
+%Specifically, it uses a queue to keep track of the nodes to be visited (line 7),
+%and stores all visited nodes to avoid infinite loop (line 8).
+%The algorithm checks every successive node to be visited (line 16):
+%it reports an error if that node is a UI-accessing method (lines 18, 19), or skips
+%it if it is a safe UI method (lines 20, 21), or simply keeps traversing otherwise (line 23).
 
-Note that when the algorithm determines that a UI-accessing method may be invoked
-by a non-UI thread, it computes a method call chain from the entry node to
-the UI-accessing node as the error report.
-The method \CodeIn{createErrorReport} on line 18 does that. 
-Figure~\ref{fig:androiderror} shows a method call chain from the entry
-node \CodeIn{LayerView.<init>} to the UI-accessing node \CodeIn{ViewRoot}.\CodeIn{recomputeViewAttributes}
-(for the sake of clarification, we also show the checking method \CodeIn{checkThread} in the reported warning).
+The error message created by the method \CodeIn{createErrorReport} on line 17
+includes the method call chain from the entry node to the UI-accessing node
+as the error report. For brevity, we do not show the data structures that store
+the current call chain.
+Figure~\ref{fig:report} shows a method call chain from the entry
+node \CodeIn{LayerView.<init>} to the UI-accessing node \CodeIn{ViewRoot}.\CodeIn{checkThread}.
+%Note that when the algorithm determines that a UI-accessing method may be invoked
+%by a non-UI thread, it computes a method call chain from the entry node to
+%the UI-accessing node as the error report.
+% does that.
 
@@
 \STATE $\mathit{threadStarts}$ $\leftarrow$ $\bigcup_{entry \in entryNodes}$ getReachableStarts($\mathit{entry}$)
-\COMMENT{keep the nodes to be visited next in a fringe}
-\STATE $\mathit{fringe}$ $\leftarrow$ an empty queue\\
-\COMMENT{keep all visited nodes to avoid infinite loop}
+\COMMENT{keep the nodes to be visited next in a worklist}
+\STATE $\mathit{worklist}$ $\leftarrow$ an empty queue\\
+\STATE $\mathit{worklist}$.enqueueAll($\mathit{threadStarts}$)
 \STATE $\mathit{visited}$ $\leftarrow$ $\emptyset$
-\STATE $\mathit{fringe}$.enqueueAll($\mathit{threadStarts}$)
-\WHILE{$\mathit{fringe}$.isNotEmpty()}
-\STATE $\mathit{node}$ $\leftarrow$ $\mathit{fringe}$.dequeue()
+\WHILE{$\mathit{worklist}$.isNotEmpty()}
+\STATE $\mathit{node}$ $\leftarrow$ $\mathit{worklist}$.dequeue()
 \IF{$\mathit{node}$ $\in$ $\mathit{visited}$}
@@
 \STATE $\mathit{visited}$ $\leftarrow$ $\mathit{visited}$ $\cup$ $\mathit{node}$
-\FOR{each $\mathit{succNode}$ in getSuccNodes($\mathit{cg}$, $\mathit{node}$)}
-\IF{$\mathit{succNode}$ $\in$ $\mathit{uiAccessingNodes}$}
-\STATE $\mathit{newError}$ $\leftarrow$ createErrorReport($\mathit{entryNode, succNode}$)
+\IF{$\mathit{node}$ $\in$ $\mathit{uiAccessingNodes}$}
+\STATE $\mathit{newError}$ $\leftarrow$ createErrorReport($\mathit{node}$)
 \STATE $\mathit{errors}$ $\leftarrow$ $\mathit{errors}$ $\cup$ $\mathit{newError}$
-\ELSIF{$\mathit{succNode}$ $\in$ $\mathit{safeUINodes}$}
+\ELSIF{$\mathit{node}$ $\in$ $\mathit{safeUINodes}$}
 \STATE continue
 \ELSE
-\STATE $\mathit{fringe}$.enqueue($\mathit{succNode}$)
+\STATE $\mathit{worklist}$.enqueueAll(getSuccNodes($\mathit{cg}$, $\mathit{node}$))
 \ENDIF 
-\ENDFOR
 \ENDWHILE
@@
 shortest path to the UI-accessing node, permitting
-to produce smaller error reports. However,
+smaller error reports. However,
 other graph search strategies such as Depath-First Search (DFS) or
@@
 we empirically compared three different graph search strategies, and demonstrated that
-using BFS, algorithm found more errors than DFS and
+using BFS, the algorithm found more errors than DFS and
 exhaustive path search.
@@
 \end{CodeOut}
-\caption{Sample GUI application code on the Android platform. The layout
+\vspace*{-3.0ex} \caption{Sample GUI application code on the Android platform. The layout
 XML file (the top) specifies a Button object declaratively, 
 and the Java code (the bottom)
-first loads the XML file (line 6) and then uses reflection to create
-a Button object by its ID (line 7, the \CodeIn{findViewById} method).}
+first loads the XML file (line 5) and then uses reflection to create
+a Button object by its ID (line 6, the \CodeIn{findViewById} method).}
 \label{fig:sampleandroid}
@@
 %\ENDWHILE
-\vspace{-2mm}
 \end{algorithmic}
+\vspace{-3mm}
 \caption{A reflection-aware call graph construction algorithm. Lines
-1--7 show a simple program transformation to replace reflection calls
+1--7 are a simple program transformation to replace reflection calls
 with object creations, and line 8 builds the call graph using
-the existing call graph construction algorithms. This algorithm
-is parameterized by three methods on line 2, 3, and 8. How to
-instantiate it for the Android framework is presented in Section~\ref{sec:cg}.
+an existing call graph construction algorithm. This algorithm
+is parameterized by two methods on lines 2 and 3. 
+How to instantiate it for the Android framework is presented in Section~\ref{sec:cg}.
 %This algorithm is parameterized by the call graph construction
@@
 When analyzing the code in Figure~\ref{fig:sampleandroid}, existing call graph algorithms
-fail to conclude that variable \CodeIn{button} declared at line 7
-point to a \CodeIn{Button} object due to its limitation in deal with the
+fail to conclude that the variable \CodeIn{button} declared at line 6
+points to a \textit{non-null} \CodeIn{Button} object due to its limitation in deal with the
 reflection call \CodeIn{findViewById}. As a result, the built 
-call graph will miss the calling edge corresponding to the
+call graph will exclude the calling edge corresponding to the
 \CodeIn{setText} method call on line 10.
@@
 of the methods in the \CodeIn{java.lang.reflection} package.
-In Figure~\ref{fig:cgalgorithm}, lines 1--7 show
-the first step of program transformation. The algorithm iterates through every statement
-in an analyzed program. When it sees a reflection call, the algorithm
+%In Figure~\ref{fig:cgalgorithm}, lines 1--7 show
+%the first step of program transformation. The algorithm iterates through every statement
+%in an analyzed program.
+When it sees a reflection call, the algorithm
 determines a set of possible objects that might be created.
-After that, the algorithm creates a statement which non-deterministically
-returns a new object from the object set. Line 8 is the second step
-to build a call graph on the transformed program.
+After that, the algorithm creates a statement that non-deterministically
+returns a new object from the object set.
+%Line 8 is the second step
+%to build a call graph on the transformed program.
 
-This algorithm is parameterized in three places:
-line 2, line 3, and line 8. Currently, we instantiated it
-for Android applications as follows. On line 2,
-the predicate isReflectionCall returns true
-if the $statement$ is a \CodeIn{findViewById(id)} method call. On line 3, method
-\CodeIn{getAllObjectsThatMaybeCreated} parses the associated XML configuration
+This algorithm is parameterized by two methods on
+lines 2 and 3. When instantiated for the Android framework,
+the predicate isReflectionCall on line 2 returns true
+if the $statement$ is a \CodeIn{findViewById(id)} method call, and the method
+getAllObjectsThatMaybeCreated on line 3 parses the associated XML configuration
 file in an Android application to extract the class declaration
- correspondinig to the given \CodeIn{id} value. If the \CodeIn{id}
-value is dynamically generated, the method will conservatively
+ corresponding to the given \CodeIn{id} value. If the \CodeIn{id}
+value is dynamically generated, this method will conservatively
 return instances of all subclasses of the declared type.
-On line 8, any existing call graph construction algorithm can be applied.
+%On line 8, any existing call graph construction algorithm can be applied.
 
@@
 graph construction algorithm helps in detecting errors
-in Android applications.
+in Android applications (Section~\ref{sec:evaluation}).
 
@@
 Adding annotations for native methods is optional and requires manual effort.
-In our experiments, 1 out of 9 programs uses native methods to interact with
-the underlying operating system. We manually
+In our experiments, 1 out of 9 programs uses native methods. We manually
 searched the source files, inspected the code to determine possible target methods
 that may be called by a native method, and added 7 annotations for this program.
-We found such an annotation, was useful: one real-world bug
+We found such an annotation was useful: one error
 can only be reported with using the user-provided annotations.
@@
 %\item
-\textbf{4. Filter Report With the Same Head Methods from The Entry Node to \CodeIn{Thread.start()}}. A method can call
+\textbf{4. Filter Report With the Same Head Methods from the Entry Node to \CodeIn{Thread.start()}}. A method can call
 multiple methods that access GUI objects, such as:
@@
 This filter compares two reported chains that have the same
-head nodes from the entry node to \CodeIn{Thread}.\CodeIn{start()},
+head methods from the entry node to \CodeIn{Thread}.\CodeIn{start()},
 and removes the longer one.
@@
 \CodeIn{start()}
-to the UI-accessing node}. A method
+to the UI-accessing Method}. A method
 can have multiple callers, so that method call chains with the same tail are likely
@@
 two reported method call chains that share the same 
-tail nodes from \CodeIn{Thread.start()} to the UI-accessing node, and
+tail from \CodeIn{Thread.start()} to the UI-accessing methods, and
 removes the longer one.
@@
 are based on heuristics. However, as we will show in
-our experiments, these filters work remarkably well in practice.
+our experiments, these filters work remarkably well in practice (Section~\ref{sec:filters}).
 
@@
 
-We instantiated our error detection techniques for four popular GUI frameworks,
-namely SWT, Eclipse plugin environment, Swing, and Android.
+We instantiated our error detection technique for four popular GUI frameworks:
+SWT, Eclipse plugin, Swing, and Android.
 The major framework-specific parts, corresponding to
@@
 %on which it is implemented.
- We instantiate our technique for SWT applications as follows:
+ We instantiated our technique for SWT applications as follows:
 
@@
 
-\item \textbf{UI-accessing nodes: } SWT provides explicit
-runtime checking for illegal thread accesses. Any methods for manipulating
-GUI object must call methods \CodeIn{Display.checkWidget}
-or \CodeIn{Display.checkDevice} to check whether the current
-thread is the UI thread or not.
-Thus, we treat nodes (in both user code and framework code) corresponding to the methods
-calling these two methods as UI-accessing nodes.
+\item \textbf{UI-accessing nodes: } the \CodeIn{Display.checkWidget}
+and \CodeIn{Display.} \CodeIn{checkDevice} methods. SWT uses the above
+two methods to explicitly check thread accesses at runtime.
+Any methods for manipulating GUIs object must call (one of) these two methods
+ to determine whether the current thread is the UI thread or not.
+%Thus, we treat nodes (in both user code and framework code) corresponding to the methods
+%calling these two methods as UI-accessing nodes.
 %must be invoked
@@
 implement functionalities. When a plugin starts, Eclipse
-calls back the overridden extension points to handle the
+calls back the overridden methods to handle the
 upcoming events. All SWT GUI event handling methods (i.e., the overriden
-methods in the class that implements \CodeIn{org.eclipse.swt.internal.\\SWTEventListener}) are
+methods in the class that implements \CodeIn{org.eclipse.swt.internal.SWTEvent-\\Listener}) are
 always called back from the UI thread, thus are used as call graph entry nodes.
@@
 \item \textbf{Safe UI methods: }  Swing's two helper methods
-(\CodeIn{SwingUtilities.} \CodeIn{invokeLater} and \CodeIn{SwingUtilities.invokeAndWait}) that execute code in the UI thread.
+(\CodeIn{SwingUtilities.} \CodeIn{invokeLater} and \CodeIn{SwingUtilities.invokeAndWait}) that execute code on the UI thread.
 
@@
 We also add all overridden Android GUI event handling methods in user
-code as entry nodes, since they must be called back from the UI thread.
+code as entry nodes, since they are also called back from the UI thread.
 
-\item \textbf{UI-accessing nodes: }every method calling \CodeIn{ViewRoot.checkThread}.
+\item \textbf{UI-accessing nodes: }the \CodeIn{ViewRoot.checkThread} method.
 Like SWT, Android explicitly checks whether

### 2012-02-04 trunk/GUIErrorDetector/paper/implementation.tex
fix inconsistent places

@@
 errors, and scales to realistic programs.
-Optionally, users may specify additional heuristic filters (Section~\ref{sec:heuristic}) %to guide call graph traverse
-, and annotate call relationships for native methods (Section~\ref{sec:annotation}).
+
+%Optionally, users may specify additional heuristic filters (Section~\ref{sec:heuristic}) %to guide call graph traverse
+%, and annotate call relationships for native methods (Section~\ref{sec:annotation}).
 
@@
  algorithm (Section~\ref{sec:cg}) using WALA's \textit{bypass logic}.
-Our tool does not requires a separated pass of program transformation; it
-first parses the configuration file in an Android application,
+Unlike similar tools~\cite{Payet:2011:SAA:2032266.2032299}, our tool
+does not require a separated
+pass of program instrumentation; instead, it
+parses the configuration file in an Android application,
 and then intercepts the call graph construction
@@
 decrypt the apk file, and then uses the 
-ded translator~\cite{Enck:2011:SAA:2028067.2028088} to convert
+ded translator~\cite{ded} to convert
 Dalvik bytecode to Java bytecode before feeding to WALA.  The Android system

### 2012-02-06 trunk/GUIErrorDetector/src/edu/washington/cs/detector/experimental/InvalidThreadAccessDetector.java
Add the experimental implementation

@@ -1,0 +1,249 @@
+package edu.washington.cs.detector.experimental;
+
+import java.io.File;
+import java.io.IOException;
+import java.util.Collection;
+import java.util.LinkedHashMap;
+import java.util.LinkedHashSet;
+import java.util.LinkedList;
+import java.util.List;
+import java.util.Map;
+
+import com.ibm.wala.core.tests.callGraph.CallGraphTestUtil;
+import com.ibm.wala.ipa.callgraph.CGNode;
+import com.ibm.wala.ipa.callgraph.CallGraph;
+import com.ibm.wala.util.graph.Graph;
+import com.ibm.wala.util.io.FileProvider;
+
+import edu.washington.cs.detector.AnomalyCallChain;
+import edu.washington.cs.detector.AnomalyFinder;
+import edu.washington.cs.detector.CGBuilder;
+import edu.washington.cs.detector.CGBuilder.CG;
+import edu.washington.cs.detector.CallChainFilter;
+import edu.washington.cs.detector.CallChainNode;
+import edu.washington.cs.detector.FilterStrategy;
+import edu.washington.cs.detector.MethodEvaluator;
+import edu.washington.cs.detector.NativeMethodConnector;
+import edu.washington.cs.detector.ThreadStartFinder;
+import edu.washington.cs.detector.guider.CGTraverseGuider;
+import edu.washington.cs.detector.util.Log;
+import edu.washington.cs.detector.util.Utils;
+import edu.washington.cs.detector.util.WALAUtils;
+
+//implements the algorithm
+public class InvalidThreadAccessDetector {
+	
+	public static boolean DEBUG = false;
+	
+	public static boolean LOG_RESULT = false;
+	
+	public static final String EXCLUSION_FILE_SWING = "Java60RegressionExclusionsWithoutGUI.txt";
+	public static final String EMPTY_FILE = "EmptyExclusion.txt";
+		
+	public static void setToUseDFS() {
+		ThreadStartFinder.USE_DEF = true;
+		UIAccessingMethodFinder.USE_DEF = true;
+	}
+	
+	private final String appPath;
+	private String exclusion_file = CallGraphTestUtil.REGRESSION_EXCLUSIONS;
+	private List<FilterStrategy> filters = new LinkedList<FilterStrategy>();
+	private CGTraverseGuider threadStartGuider = null;
+	private CGTraverseGuider uiAnomalyGuider = null;
+	private NativeMethodConnector nativeConnector = null;
+	private CG cgOpt = null;
+	
[…]

### 2012-02-06 GUIErrorDetector/src/edu/washington/cs/detector/experimental/UIAccessingMethodFinder.java
Add the experimental implementation

@@ -1,0 +1,211 @@
+package edu.washington.cs.detector.experimental;
+
+import java.util.Collection;
+import java.util.HashSet;
+import java.util.Iterator;
+import java.util.LinkedHashMap;
+import java.util.LinkedHashSet;
+import java.util.LinkedList;
+import java.util.List;
+import java.util.Map;
+import java.util.Set;
+
+import com.ibm.wala.classLoader.IMethod;
+import com.ibm.wala.ipa.callgraph.CGNode;
+import com.ibm.wala.ipa.cha.ClassHierarchy;
+import com.ibm.wala.util.graph.Graph;
+
+import edu.washington.cs.detector.AbstractMethodFinder;
+import edu.washington.cs.detector.CallChainNode;
+import edu.washington.cs.detector.MethodEvaluator;
+import edu.washington.cs.detector.NativeMethodConnector;
+import edu.washington.cs.detector.guider.CGTraverseGuider;
+import edu.washington.cs.detector.util.Files;
+import edu.washington.cs.detector.util.Log;
+import edu.washington.cs.detector.util.Utils;
+import edu.washington.cs.detector.util.WALAUtils;
+
+public class UIAccessingMethodFinder extends AbstractMethodFinder {
+	
+	public static boolean USE_DEF = false;
+	public static boolean DEBUG = false;
+	private static String[] checking_methods
+	    = Files.readWholeNoExp("./src/checking_methods.txt").toArray(new String[0]);
+	
+	private static Map<CGNode, List<CallChainNode>> cachedResult = new LinkedHashMap<CGNode, List<CallChainNode>>();	
+	//bad design here, cha needs to be set when evaluator is set
+	private static MethodEvaluator evaluator = null;
+	/** reload all checking method for customization */
+	public static String[] getCheckingMethods() {
+		return checking_methods;
+	}
+	public static void setCheckingMethods(String fileName) {
+		assert fileName != null;
+		checking_methods = Files.readWholeNoExp(fileName).toArray(new String[0]);
+		for(String method : checking_methods) {
+			System.err.println("error checking method as sink: " + method);
+		}
+	}
+	public static Map<CGNode, List<CallChainNode>> getCachedResult() {
+		return cachedResult;
+	}
+	/** clear the cache*/
+	public static void clearCachedResult() {
+		cachedResult.clear();
+	}
[…]

### 2012-02-06 GUIErrorDetector/src/edu/washington/cs/detector/guider/CGTraverseSWTGuider.java
small tweak of the guider

@@ -35,7 +35,7 @@ public class CGTraverseSWTGuider implements CGTraverseGuider {
 		return true;
 	}
 	
-	private boolean matchExcludedSWTCalls(CGNode dest) {
+	protected boolean matchExcludedSWTCalls(CGNode dest) {
 		String destStr = dest.toString();
 		for(String str : swtCalls) {
 			if(destStr.indexOf(str) != -1) {

### 2012-02-06 trunk/GUIErrorDetector/sampleprogram/test/nativeannotation/NormalClass.java
small change of the sampel programs

@@ -1,6 +1,6 @@
 package test.nativeannotation;
 
-import edu.washington.cs.detector.util.CallByNativeMethods;
+import edu.washington.cs.detector.util.CalledByNativeMethods;
 
 public class NormalClass {
 	
@@ -8,12 +8,12 @@ public class NormalClass {
 	 * should fetch calling relations for the following 2
 	 * */
 	
-	@CallByNativeMethods(callers={"test.nativeannotation.NativeClass.nativeMethod1"})
+	@CalledByNativeMethods(callers={"test.nativeannotation.NativeClass.nativeMethod1"})
 	public void javaMethod1() {
 		
 	}
 	
-	@CallByNativeMethods(callers={"test.nativeannotation.NativeClass.nativeMethod1",
+	@CalledByNativeMethods(callers={"test.nativeannotation.NativeClass.nativeMethod1",
 			"test.nativeannotation.NativeClass.nativeMethod2"})
 	public void javaMethod2() {
 		
@@ -23,12 +23,12 @@ public class NormalClass {
 	 * should report errors below
 	 * */
 	
-	@CallByNativeMethods(callers={"test.nativeannotation.NativeClass.nonNativeMethod"})
+	@CalledByNativeMethods(callers={"test.nativeannotation.NativeClass.nonNativeMethod"})
 	public void incorrectAnnotationMethod() {
 		
 	}
 	
-	@CallByNativeMethods(callers={"test.nativeannotation.NativeClass.notexistmethod"})
+	@CalledByNativeMethods(callers={"test.nativeannotation.NativeClass.notexistmethod"})
 	public void notExistAnnotationMethod() {
 		
 	}

### 2012-02-06 trunk/GUIErrorDetector/sampleprogram/test/threaderror/ThreadError.java

@@ -48,6 +48,7 @@ public class ThreadError {
 			final Runnable r = new Runnable() {
 				@Override
 				public void run() {
+					System.out.println(Display.getCurrent());
 					helloWorldTest.setText("I want to change the text.");
 				}
 

### 2012-02-06 GUIErrorDetector/tests/edu/washington/cs/detector/experiments/android/AbstractAndroidTest.java
experiment setting for using the "incorrect" algorithmn

@@ -32,6 +32,7 @@ import edu.washington.cs.detector.ThreadStartFinder;
 import edu.washington.cs.detector.UIAnomalyDetector;
 import edu.washington.cs.detector.UIAnomalyMethodFinder;
 import edu.washington.cs.detector.CGBuilder.CG;
+import edu.washington.cs.detector.experimental.InvalidThreadAccessDetector;
 import edu.washington.cs.detector.experiments.filters.MergeSameEntryToStartPathStrategy;
 import edu.washington.cs.detector.experiments.filters.MergeSamePrefixToLibCallStrategy;
 import edu.washington.cs.detector.experiments.filters.MergeSameTailStrategy;
@@ -263,7 +264,11 @@ public abstract class AbstractAndroidTest extends TestCase {
 		
 		
 		//set up the anomaly detection
-		UIAnomalyDetector detector = new UIAnomalyDetector(getAppPath());
+//		UIAnomalyDetector detector = new UIAnomalyDetector(getAppPath());
+		
+		InvalidThreadAccessDetector detector = new InvalidThreadAccessDetector(getAppPath());
+		
+		
 		String defaultcheckingfile = "./tests/edu/washington/cs/detector/checkingmethods_for_android.txt";
 		detector.configureCheckingMethods(defaultcheckingfile);
 		if(this.androidcheckingfile != null) {

### 2012-02-06 GUIErrorDetector/tests/edu/washington/cs/detector/experiments/android/TestMozillaFirefox.java

@@ -137,7 +137,7 @@ public class TestMozillaFirefox extends AbstractAndroidTest {
 			type = CG.OneCFA;
 //			type = CG.RTA;
 			
-			UIAnomalyDetector.setToUseDFS();
+//			UIAnomalyDetector.setToUseDFS();
 			
 		    List<AnomalyCallChain> chains = super.findErrorsInAndroidApp(type, ui2startGuider, start2checkGuider);
 //		    List<AnomalyCallChain> chains = super.findErrorsInAndroidApp(CG.ZeroCFA, ui2startGuider, start2checkGuider);

### 2012-02-06 GUIErrorDetector/tests/edu/washington/cs/detector/experiments/swing/AbstractSwingTest.java

@@ -20,6 +20,7 @@ import edu.washington.cs.detector.SwingUIMethodEvaluator;
 import edu.washington.cs.detector.ThreadStartFinder;
 import edu.washington.cs.detector.UIAnomalyDetector;
 import edu.washington.cs.detector.UIAnomalyMethodFinder;
+import edu.washington.cs.detector.experimental.InvalidThreadAccessDetector;
 import edu.washington.cs.detector.experiments.filters.MatchRunWithInvokeClassStrategy;
 import edu.washington.cs.detector.experiments.filters.MergeSamePrefixToLibCallStrategy;
 import edu.washington.cs.detector.experiments.filters.RemoveNoClientClassStrategy;
@@ -57,6 +58,8 @@ public abstract class AbstractSwingTest extends TestCase {
 	
 	private boolean useexhaustivesearch = false;
 	
+	private boolean useworklist = false;
+	
 	protected void setCGType(CG t) {
 		type = t;
 	}
@@ -89,6 +92,10 @@ public abstract class AbstractSwingTest extends TestCase {
 		this.useexhaustivesearch = exhaust;
 	}
 	
+	protected void setUseWorklist(boolean worklist) {
+		this.useworklist = worklist;
+	}
+	
 	protected Iterable<Entrypoint> getAdditonalEntrypoints(ClassHierarchy cha) {
 		return Collections.emptySet();
 	}
@@ -113,6 +120,8 @@ public abstract class AbstractSwingTest extends TestCase {
 	    ClassHierarchyException {
 		
 		UIAnomalyDetector detector = new UIAnomalyDetector(appPath);
+		
+//		InvalidThreadAccessDetector detector = new InvalidThreadAccessDetector(appPath);
 		
 		/** a few configurations to configure the tool for swing*/
 		if(type != null) {

### 2012-02-06 GUIErrorDetector/tests/edu/washington/cs/detector/experiments/swt/TestFileBunker.java

@@ -9,6 +9,7 @@ import edu.washington.cs.detector.CallChainFilter;
 import edu.washington.cs.detector.TestCommons;
 import edu.washington.cs.detector.UIAnomalyDetector;
 import edu.washington.cs.detector.CGBuilder.CG;
+import edu.washington.cs.detector.experimental.InvalidThreadAccessDetector;
 import edu.washington.cs.detector.experiments.filters.MergeSameEntryToStartPathStrategy;
 import edu.washington.cs.detector.experiments.filters.MergeSameTailStrategy;
 import edu.washington.cs.detector.experiments.filters.RemoveContainingNodeStrategy;
@@ -42,7 +43,9 @@ public class TestFileBunker extends TestCase {
 		UIAnomalyDetector.DEBUG = true;
 		
 		//initialize a UI anomaly detector
-        UIAnomalyDetector detector = new UIAnomalyDetector(path);
+//        UIAnomalyDetector detector = new UIAnomalyDetector(path);
+		
+		InvalidThreadAccessDetector detector = new InvalidThreadAccessDetector(path);
         
         detector.setThreadStartGuider(new CGTraverseSWTGuider());
         detector.setUIAnomalyGuider(new CGTraverseSWTGuider());
@@ -54,7 +57,7 @@ public class TestFileBunker extends TestCase {
 //		builder.setCGType(CG.ZeroCFA);
 //		builder.setCGType(CG.FakeZeroCFA);
 		
-		UIAnomalyDetector.setToUseDFS();
+//		UIAnomalyDetector.setToUseDFS();
 		
 		builder.buildCG();
 		//dump debugging information

### 2012-02-06 GUIErrorDetector/tests/edu/washington/cs/detector/experiments/swt/TestJvimf.java

@@ -1,0 +1,115 @@
+package edu.washington.cs.detector.experiments.swt;
+
+import java.io.IOException;
+import java.util.List;
+
+import com.ibm.wala.ipa.callgraph.CGNode;
+
+import junit.framework.TestCase;
+
+import edu.washington.cs.detector.AnomalyCallChain;
+import edu.washington.cs.detector.CGBuilder;
+import edu.washington.cs.detector.CallChainFilter;
+import edu.washington.cs.detector.TestCommons;
+import edu.washington.cs.detector.UIAnomalyDetector;
+import edu.washington.cs.detector.CGBuilder.CG;
+import edu.washington.cs.detector.experiments.filters.MergeSamePrefixStrategy;
+import edu.washington.cs.detector.experiments.filters.MergeSamePrefixToLibCallStrategy;
+import edu.washington.cs.detector.experiments.filters.MergeSameTailStrategy;
+import edu.washington.cs.detector.experiments.filters.RemoveSameEntryStrategy;
+import edu.washington.cs.detector.experiments.filters.RemoveSystemCallStrategy;
+import edu.washington.cs.detector.guider.CGTraverseSWTGuider;
+import edu.washington.cs.detector.util.Globals;
+import edu.washington.cs.detector.util.Utils;
+import edu.washington.cs.detector.util.WALAUtils;
+
+public class TestJvimf extends TestCase {
+public String dir = "D:\\research\\guierror\\subjects\\swt-subjects\\jvifm-src-0.12b\\";
+	
+    public String appPath = dir + "jvifm.jar";
+    
+	public String libJar =  dir + "apache-tool.jar"
+	     + Globals.pathSep + dir + "swt.jar"
+	     + Globals.pathSep + dir + "commons-cli-1.1.jar"
+	     + Globals.pathSep + dir + "commons-io-1.4.jar"
+	     + Globals.pathSep + dir + "commons-logging.jar"
+	     + Globals.pathSep + dir + "commons-vfs-20070730.jar"
+	     + Globals.pathSep + dir + "dom4j.jar"
+	     + Globals.pathSep + dir + "jaxen-1.1-beta-9.jar"
+	     + Globals.pathSep + dir + "jintellitype-1.3.1.jar"
+	     + Globals.pathSep + dir + "jxgrabkey.jar";
+
+	String[] packages = new String[]{"net.sf.jvifm"};
+	
+	String logFile = "./logs/jvimf-anomalies.txt";
+	
+	public void testJvimf() throws IOException {
[…]

### 2012-02-06 GUIErrorDetector/tests/edu/washington/cs/detector/experiments/swt/TestVirgoFtp.java

@@ -7,13 +7,16 @@ import edu.washington.cs.detector.AnomalyCallChain;
 import edu.washington.cs.detector.CGBuilder;
 import edu.washington.cs.detector.CallChainFilter;
 import edu.washington.cs.detector.TestCommons;
+import edu.washington.cs.detector.ThreadStartFinder;
 import edu.washington.cs.detector.UIAnomalyDetector;
 import edu.washington.cs.detector.CGBuilder.CG;
+import edu.washington.cs.detector.experimental.InvalidThreadAccessDetector;
 import edu.washington.cs.detector.experiments.filters.MergeSamePrefixToLibCallStrategy;
 import edu.washington.cs.detector.experiments.filters.MergeSameTailStrategy;
 import edu.washington.cs.detector.experiments.filters.RemoveSystemCallStrategy;
 import edu.washington.cs.detector.guider.CGTraverseSWTGuider;
 import edu.washington.cs.detector.util.Globals;
+import edu.washington.cs.detector.util.Log;
 import edu.washington.cs.detector.util.Utils;
 import edu.washington.cs.detector.util.WALAUtils;
 import junit.framework.TestCase;
@@ -31,7 +34,13 @@ public class TestVirgoFtp extends TestCase {
 	
 	public void testRunVirgoFtp() throws IOException {
 		String path = appPath + Globals.pathSep + libJar;
-        UIAnomalyDetector detector = new UIAnomalyDetector(path);
+		
+		Log.logConfig("./log.txt");
+		
+//        UIAnomalyDetector detector = new UIAnomalyDetector(path);
+		
+		//the worklist based
+        InvalidThreadAccessDetector detector = new InvalidThreadAccessDetector(path);
         
         detector.setThreadStartGuider(new CGTraverseSWTGuider());
         detector.setUIAnomalyGuider(new CGTraverseSWTGuider());
@@ -41,7 +50,9 @@ public class TestVirgoFtp extends TestCase {
 //		builder.setCGType(CG.RTA);
 //		builder.setCGType(CG.FakeZeroCFA);
 		
-		UIAnomalyDetector.setToUseDFS();
+		ThreadStartFinder.check_find_all_starts = true;
+		
+		//UIAnomalyDetector.setToUseDFS();
 		
 		builder.buildCG();
 		

### 2012-02-06 GUIErrorDetector/tests/edu/washington/cs/detector/experiments/swt/TestVuze.java

@@ -9,7 +9,6 @@ import edu.washington.cs.detector.CallChainFilter;
 import edu.washington.cs.detector.TestCommons;
 import edu.washington.cs.detector.UIAnomalyDetector;
 import edu.washington.cs.detector.CGBuilder.CG;
-import edu.washington.cs.detector.experimental.InvalidThreadAccessDetector;
 import edu.washington.cs.detector.experiments.filters.MergeSamePrefixToLibCallStrategy;
 import edu.washington.cs.detector.experiments.filters.MergeSameTailStrategy;
 import edu.washington.cs.detector.experiments.filters.RemoveSystemCallStrategy;
@@ -19,32 +18,19 @@ import edu.washington.cs.detector.util.Utils;
 import edu.washington.cs.detector.util.WALAUtils;
 import junit.framework.TestCase;
 
-public class TestArecaBackup extends TestCase {
-	public String dir = "D:\\research\\guierror\\subjects\\swt-subjects\\areca-latest\\";
-		
+public class TestVuze extends TestCase {
+   public String dir = "D:\\research\\guierror\\subjects\\swt-subjects\\vuze-4.7\\";
 	
-    public String appPath = dir + "areca-latest.jar";
-	
+    public String appPath = dir + "vuze-4.7.jar";
     
-    
-	public String libJar = dir + "activation.jar"
-	    + Globals.pathSep + dir + "commons-net-1.4.1.jar"
-	    + Globals.pathSep + dir +  "jakarta-oro-2.0.8.jar"
-	    + Globals.pathSep + dir + "jsch.jar"
-	    + Globals.pathSep + dir +  "local_policy.jar"
-	    + Globals.pathSep + dir +  "mail.jar"
-	    + Globals.pathSep + dir +  "org.eclipse.core.commands_3.2.0.I20060605-1400.jar"
-	    + Globals.pathSep + dir +  "org.eclipse.equinox.common_3.2.0.v20060603.jar"
-	    + Globals.pathSep + dir +  "org.eclipse.jface_3.2.0.I20060605-1400.jar"
+	public String libJar = dir + "apache-log4j.jar"
+	    + Globals.pathSep + dir + "commons-cli-1.2.jar"
         + Globals.pathSep + "D:\\develop-tools\\eclipse\\eclipse\\plugins\\org.eclipse.swt.win32.win32.x86_64_3.6.2.v3659c.jar";
 	    
 	
-	public void testArecaBackup() throws IOException {
+	public void testVuze() throws IOException {
[…]

### 2012-02-06 GUIErrorDetector/tests/edu/washington/cs/detector/experiments/swt/TestZekr.java

@@ -9,7 +9,6 @@ import edu.washington.cs.detector.CallChainFilter;
 import edu.washington.cs.detector.TestCommons;
 import edu.washington.cs.detector.UIAnomalyDetector;
 import edu.washington.cs.detector.CGBuilder.CG;
-import edu.washington.cs.detector.experimental.InvalidThreadAccessDetector;
 import edu.washington.cs.detector.experiments.filters.MergeSamePrefixToLibCallStrategy;
 import edu.washington.cs.detector.experiments.filters.MergeSameTailStrategy;
 import edu.washington.cs.detector.experiments.filters.RemoveSystemCallStrategy;
@@ -19,32 +18,38 @@ import edu.washington.cs.detector.util.Utils;
 import edu.washington.cs.detector.util.WALAUtils;
 import junit.framework.TestCase;
 
-public class TestArecaBackup extends TestCase {
-	public String dir = "D:\\research\\guierror\\subjects\\swt-subjects\\areca-latest\\";
-		
+public class TestZekr extends TestCase {
+    public String dir = "D:\\research\\guierror\\subjects\\swt-subjects\\zekr-exp\\";
 	
-    public String appPath = dir + "areca-latest.jar";
-	
+    public String appPath = dir + "zekr.jar";
     
-    
-	public String libJar = dir + "activation.jar"
-	    + Globals.pathSep + dir + "commons-net-1.4.1.jar"
-	    + Globals.pathSep + dir +  "jakarta-oro-2.0.8.jar"
-	    + Globals.pathSep + dir + "jsch.jar"
-	    + Globals.pathSep + dir +  "local_policy.jar"
-	    + Globals.pathSep + dir +  "mail.jar"
-	    + Globals.pathSep + dir +  "org.eclipse.core.commands_3.2.0.I20060605-1400.jar"
-	    + Globals.pathSep + dir +  "org.eclipse.equinox.common_3.2.0.v20060603.jar"
-	    + Globals.pathSep + dir +  "org.eclipse.jface_3.2.0.I20060605-1400.jar"
-        + Globals.pathSep + "D:\\develop-tools\\eclipse\\eclipse\\plugins\\org.eclipse.swt.win32.win32.x86_64_3.6.2.v3659c.jar";
+	public String libJar = dir + "basicplayer-3.0.jar"
+	   + Globals.pathSep + dir + "commons-codec-1.3.jar"
[…]

### 2012-02-06 trunk/GUIErrorDetector/tests/edu/washington/cs/detector/experiments/swing/TestS3Dropbox.java
experiment setting for using the "incorrect" algorithmn

@@ -70,7 +70,7 @@ public class TestS3Dropbox extends AbstractSwingTest {
 //		super.setCGType(CG.RTA);
 //		super.setCGType(CG.ZeroCFA);
 		
-		UIAnomalyDetector.setToUseDFS(); //use DFS
+//		UIAnomalyDetector.setToUseDFS(); //use DFS
 		
 		super.setNondefaultCG(true);
 //		super.setAddHandlers(true);

### 2012-02-06 trunk/GUIErrorDetector/tests/edu/washington/cs/detector/experiments/swt/TestIpScan.java

@@ -9,7 +9,6 @@ import edu.washington.cs.detector.CallChainFilter;
 import edu.washington.cs.detector.TestCommons;
 import edu.washington.cs.detector.UIAnomalyDetector;
 import edu.washington.cs.detector.CGBuilder.CG;
-import edu.washington.cs.detector.experimental.InvalidThreadAccessDetector;
 import edu.washington.cs.detector.experiments.filters.MergeSamePrefixToLibCallStrategy;
 import edu.washington.cs.detector.experiments.filters.MergeSameTailStrategy;
 import edu.washington.cs.detector.experiments.filters.RemoveSystemCallStrategy;
@@ -19,32 +18,21 @@ import edu.washington.cs.detector.util.Utils;
 import edu.washington.cs.detector.util.WALAUtils;
 import junit.framework.TestCase;
 
-public class TestArecaBackup extends TestCase {
-	public String dir = "D:\\research\\guierror\\subjects\\swt-subjects\\areca-latest\\";
-		
+public class TestIpScan extends TestCase {
+    public String dir = "D:\\research\\guierror\\subjects\\swt-subjects\\ipscan\\ipscan-exp\\";
 	
-    public String appPath = dir + "areca-latest.jar";
-	
+    public String appPath = dir + "ipscan-exp.jar";
     
-    
-	public String libJar = dir + "activation.jar"
-	    + Globals.pathSep + dir + "commons-net-1.4.1.jar"
-	    + Globals.pathSep + dir +  "jakarta-oro-2.0.8.jar"
-	    + Globals.pathSep + dir + "jsch.jar"
-	    + Globals.pathSep + dir +  "local_policy.jar"
-	    + Globals.pathSep + dir +  "mail.jar"
-	    + Globals.pathSep + dir +  "org.eclipse.core.commands_3.2.0.I20060605-1400.jar"
-	    + Globals.pathSep + dir +  "org.eclipse.equinox.common_3.2.0.v20060603.jar"
-	    + Globals.pathSep + dir +  "org.eclipse.jface_3.2.0.I20060605-1400.jar"
-        + Globals.pathSep + "D:\\develop-tools\\eclipse\\eclipse\\plugins\\org.eclipse.swt.win32.win32.x86_64_3.6.2.v3659c.jar";
-	    
+	public String libJar =  dir + "swt-win64.jar"
+	     + Globals.pathSep + dir + "picocontainer-1.0.jar";
+
[…]

### 2012-02-06 trunk/GUIErrorDetector/tests/edu/washington/cs/detector/experiments/swt/TestJanos.java

@@ -3,48 +3,48 @@ package edu.washington.cs.detector.experiments.swt;
 import java.io.IOException;
 import java.util.List;
 
+import junit.framework.TestCase;
 import edu.washington.cs.detector.AnomalyCallChain;
 import edu.washington.cs.detector.CGBuilder;
 import edu.washington.cs.detector.CallChainFilter;
 import edu.washington.cs.detector.TestCommons;
 import edu.washington.cs.detector.UIAnomalyDetector;
 import edu.washington.cs.detector.CGBuilder.CG;
-import edu.washington.cs.detector.experimental.InvalidThreadAccessDetector;
 import edu.washington.cs.detector.experiments.filters.MergeSamePrefixToLibCallStrategy;
 import edu.washington.cs.detector.experiments.filters.MergeSameTailStrategy;
+import edu.washington.cs.detector.experiments.filters.RemoveSameEntryStrategy;
 import edu.washington.cs.detector.experiments.filters.RemoveSystemCallStrategy;
 import edu.washington.cs.detector.guider.CGTraverseSWTGuider;
 import edu.washington.cs.detector.util.Globals;
 import edu.washington.cs.detector.util.Utils;
 import edu.washington.cs.detector.util.WALAUtils;
-import junit.framework.TestCase;
 
-public class TestArecaBackup extends TestCase {
-	public String dir = "D:\\research\\guierror\\subjects\\swt-subjects\\areca-latest\\";
-		
+public class TestJanos extends TestCase {
+    public String dir = "D:\\research\\guierror\\subjects\\swt-subjects\\janos\\janos-exp\\";
 	
-    public String appPath = dir + "areca-latest.jar";
-	
+    public String appPath = dir + "janos.jar";
     
-    
-	public String libJar = dir + "activation.jar"
-	    + Globals.pathSep + dir + "commons-net-1.4.1.jar"
-	    + Globals.pathSep + dir +  "jakarta-oro-2.0.8.jar"
-	    + Globals.pathSep + dir + "jsch.jar"
-	    + Globals.pathSep + dir +  "local_policy.jar"
-	    + Globals.pathSep + dir +  "mail.jar"
-	    + Globals.pathSep + dir +  "org.eclipse.core.commands_3.2.0.I20060605-1400.jar"
-	    + Globals.pathSep + dir +  "org.eclipse.equinox.common_3.2.0.v20060603.jar"
[…]

### 2012-02-06 trunk/GUIErrorDetector/tests/edu/washington/cs/detector/experiments/swt/TestPajp.java

@@ -9,7 +9,6 @@ import edu.washington.cs.detector.CallChainFilter;
 import edu.washington.cs.detector.TestCommons;
 import edu.washington.cs.detector.UIAnomalyDetector;
 import edu.washington.cs.detector.CGBuilder.CG;
-import edu.washington.cs.detector.experimental.InvalidThreadAccessDetector;
 import edu.washington.cs.detector.experiments.filters.MergeSamePrefixToLibCallStrategy;
 import edu.washington.cs.detector.experiments.filters.MergeSameTailStrategy;
 import edu.washington.cs.detector.experiments.filters.RemoveSystemCallStrategy;
@@ -19,32 +18,18 @@ import edu.washington.cs.detector.util.Utils;
 import edu.washington.cs.detector.util.WALAUtils;
 import junit.framework.TestCase;
 
-public class TestArecaBackup extends TestCase {
-	public String dir = "D:\\research\\guierror\\subjects\\swt-subjects\\areca-latest\\";
-		
+public class TestPajp extends TestCase {
+    public String dir = "D:\\research\\guierror\\subjects\\swt-subjects\\pajp-duper-c76c595\\";
 	
-    public String appPath = dir + "areca-latest.jar";
-	
+    public String appPath = dir + "pajp.jar";
     
-    
-	public String libJar = dir + "activation.jar"
-	    + Globals.pathSep + dir + "commons-net-1.4.1.jar"
-	    + Globals.pathSep + dir +  "jakarta-oro-2.0.8.jar"
-	    + Globals.pathSep + dir + "jsch.jar"
-	    + Globals.pathSep + dir +  "local_policy.jar"
-	    + Globals.pathSep + dir +  "mail.jar"
-	    + Globals.pathSep + dir +  "org.eclipse.core.commands_3.2.0.I20060605-1400.jar"
-	    + Globals.pathSep + dir +  "org.eclipse.equinox.common_3.2.0.v20060603.jar"
-	    + Globals.pathSep + dir +  "org.eclipse.jface_3.2.0.I20060605-1400.jar"
-        + Globals.pathSep + "D:\\develop-tools\\eclipse\\eclipse\\plugins\\org.eclipse.swt.win32.win32.x86_64_3.6.2.v3659c.jar";
+	public String libJar =  dir + "fast-md5.jar"
+	     + Globals.pathSep + dir + "swt.jar";
 	    
 	
-	public void testArecaBackup() throws IOException {
+	public void testPajp() throws IOException {
[…]

### 2012-02-06 trunk/GUIErrorDetector/paper/abstract.tex
significant revise

@@
 thread spawning as the sources and GUI object accessing as the sinks. 
-Existing call graph construction algorithms fail to build a good
-call graph for modern GUI applications, because of heavy use of reflection.
+Standard call graph construction algorithms fail to build a good
+call graph for some modern GUI applications, because of heavy use of reflection.
 Thus, we present a method to build reflection-aware call graphs.
 
-%call graph construction algorithm to overcome the limitations.% of analyzing GUI applications.
-
-We implemented our technique and instantiated it for four popular GUI
+We implemented our technique and instantiated it for four popular Java GUI
 platforms: SWT, the Eclipse plugin development framework, Swing, and
-Android. In an evaluation on 9 programs comprising 67000 LOC, our technique
+Android. In an evaluation on \subnum programs comprising \totaloc LOC, our technique
 found both previously-known and unknown errors.
 
-%a number of real-world errors, suggesting its effectiveness
-%and showing good scalability.
-
 \end{abstract}

### 2012-02-06 trunk/GUIErrorDetector/paper/evaluation.tex
significant revise

@@
 
-Our experiment objective is three-fold: to demonstrate the effectiveness
-of our approach in detecting real bugs in multithreaded GUI applications, to 
+Our experimental objective is three-fold: to demonstrate the effectiveness
+of our approach in detecting real errors in multithreaded GUI applications, to 
 compare the reflection-aware call graph construction algorithm
 with existing ones, and to evaluate the usefulness of the proposed 
- heuristics.
+ filters.
+
+\textbf{This part needs to re-write, talk sound/heuristic filters separately}
 
@@
 We also compare our technique with
-a straightforward approach (Section~\ref{sec:straightforward}),  compare the reflection-aware call graph
-construction algorithms with existing algorithms (Section~\ref{sec:reflectionaware}), and
-evaluate different graph search strategies in error detection (Section~\ref{sec:search}).
- Finally, we show that the set of proposed heuristics are effective
-in removing redundant warnings and eliminate false positives (Section~\ref{sec:filters}).
+a straightforward approach (Section~\ref{sec:straightforward}),  compare
+different call graph construction algorithms (Section~\ref{sec:reflectionaware}), and
+evaluate various graph search strategies in error detection (Section~\ref{sec:search}).
+ Finally, we show that the proposed filters are effective
+in removing redundant warnings and eliminating
+false positives (Section~\ref{sec:filters}).
 
@@
 
-We use a set of open-source projects from Sourceforge, Google code, and the Eclipse plugin
+We use a set of open-source projects from Sourceforge, Google code,
+and the Eclipse plugin
 market as evaluation subjects. To choose subjects for each supported GUI framework,
@@
 an open library. Second, the subject must use multithreading in its implementation.
-Third, the subject must undergone at least two years of active development,
+Third, the subject must have undergone at least two years of active development,
 and is listed in the first 3 result pages based on popularity. This permits us
-to exclude many immature subjects that may contain obvious errors.
+to exclude immature subjects that may contain obvious errors.
 
-We chose subjects belonging to various categories from all subjects satisfying
+We chose subjects belonging to various categories from those subjects satisfying
 the above criteria. The subjects used in our experiment are shown in Table~\ref{table:subjects},
@@
 HudsonEclipse~\cite{hudson} monitors Hudson build status from Eclipse.
-EclipseRunner~\cite{eclipserunner} extends capability of running launch configurations in Eclipse IDE.
+EclipseRunner~\cite{eclipserunner} extends Eclipse's capability to run launch configurations.
 
 \Item \textbf{Swing applications.} %S3dropbox~\cite{s3dropbox} and SudokuSolver~\cite{sudokusolver} are two Swing desktop applications.
-S3dropbox~\cite{s3dropbox} implements a client that allows users
-to drag and drop files, which are then uploaded to their Amazon S3 accounts. SodokuSolver~\cite{sudokusolver}
-computes Sodoku solutions efficiently using mutlithreading execution.
+S3dropbox~\cite{s3dropbox}  allows users
+to drag and drop files to their Amazon S3 accounts. SudokuSolver~\cite{sudokusolver}
+computes Sudoku solutions efficiently using mutlithreading execution.
 
@@
 used two configurations: with and without the reflection-aware algorithm 
-(Section~\ref{sec:cg}).  We did not use other expensive algorithms like $k$-CFA ($k >$ 1),
+(Section~\ref{sec:cg}).  We did not use more expensive algorithms like $k$-CFA ($k >$ 1),
 because they can not scale to our subject programs.
 
-We first inspect the source code of each subject to determine whether any
-native methods or project-specific GUI interaction patterns are implemented.
-Among all evaluated subjects, we found SGTPuzzler is the only program that
-uses native methods to interact with
-the underlying operating system. Thus, we checked the native code carefully,
-and manually added 3 \CodeIn{@CalledByNativeMethods}
+We first inspected the source code of each subject to determine whether any
+native methods or project-specific GUI interaction patterns were implemented.
+Only SGTPuzzler uses native methods to interact with
+the underlying operating system. Thus, we manually checked the possible
+Java methods that a native method may call, and then added \annotationnum \CodeIn{@CalledByNativeMethods}
 annotations for it. Two subjects MyTracks and Fennec employ a customized pattern
@@
 %message passing. 
-Thus, we add 5 user-defined heuristic filters for these two subjects.%to indicate
+Thus, we add 11 user-defined filters for these two subjects.
+%to indicate
 %that they are safe to be invoked from any thread. 
@@
 authors was familiar with the subjects; but we found it is quite easy
-to add extra annotations and heuristic filters. All these
-manual parts are finished in less than 60 minutes.
+to add extra annotations and user-defined filters. All these
+manual parts took less than a total of 60 minutes.
 
-After provided with necessary annotations and heuristic filters,
-our tool works in a fully-automatic, push-button manner. For each output
-warning, we manually determine its validity by either searching the
+For each output
+warning, we manually determined its validity by either searching the
 bug repository to check whether the same error has been reported before,
@@
 \hspace*{-0.2cm}
-\setlength{\tabcolsep}{.35\tabcolsep}
-\begin{tabular}{|l||c|c|c||c|c|c||c|c|c||c|c|}
+\setlength{\tabcolsep}{.15\tabcolsep}
+\begin{tabular}{|l||c|c|c||c|c|c||c|c|c||c|}
 \hline
- Subject&  \multicolumn{9}{|c||}{Our Technique} & \multicolumn{2}{|c|}{The Approach in}  \\
+ Subject&  \multicolumn{9}{|c||}{Our Technique} & Requiring Wrappers  \\
 \cline{2-10}
- Program  &  \multicolumn{3}{|c|}{RTA }& \multicolumn{3}{|c|}{0-CFA } & \multicolumn{3}{|c||}{1-CFA } & \multicolumn{2}{|c|}{Section~\ref{sec:straightforward}}  \\
-\cline{2-12}
- & CG Size & \#Warning & \#Bug & CG Size & \#Warning & \#Bug & CG Size & \#Warning & \#Bug & \#Warning & \#Bug\\
+ Program  &  \multicolumn{3}{|c|}{RTA }& \multicolumn{3}{|c|}{0-CFA } & \multicolumn{3}{|c||}{1-CFA } & (Section~\ref{sec:straightforward})  \\
+\cline{2-11}
+ & CG Size & \#Warning & \#Bug & CG Size & \#Warning & \#Bug & CG Size & \#Warning & \#Bug & \#Warning \\
 \hline \hline
-\multicolumn{12}{|l|}{SWT desktop applications}   \\
+\multicolumn{11}{|l|}{SWT desktop applications}   \\
  \hline
- VirgoFTP&  12401 &  2 &  2 & 10858 & 2 & 2 & 43598 & 2 & 2& 149 & 2 \\
+ VirgoFTP&  12401 &  2 &  2 & 10858 & 2 & 2 & 43598 & 2 & 2& 149  \\
  \hline
- FileBunker &  18951 &  1 &  0 & 15743 & 0 & 0 & 76088 & 2 & 1& 693 & 1 \\
+ FileBunker &  18951 &  1 &  0 & 15743 & 0 & 0 & 76088 & 2 & 1& 693  \\
  \hline
  \hline
-\multicolumn{12}{|l|}{Eclipse plugins}   \\
+\multicolumn{11}{|l|}{Eclipse plugins}   \\
  \hline
- EclipseRunner&  11248&  6 &  1 & 7201 & 6 & 1 & 26911 & 6 & 1& 202 & 1 \\
+ EclipseRunner&  11248&  6 &  1 & 7201 & 6 & 1 & 26911 & 6 & 1& 202  \\
  %\hline
@@
  \hline
- HudsonEclipse& 18473 &  2 &  1 & 15814 & 2 & 1& 56645 & 3 & 1 & 182 & 1 \\
+ HudsonEclipse& 18473 &  2 &  1 & 15814 & 2 & 1& 56645 & 3 & 1 & 182 \\
  \hline
  \hline
-\multicolumn{12}{|l|}{Swing desktop applications}   \\
+\multicolumn{11}{|l|}{Swing desktop applications}   \\
  \hline
- S3dropbox & 37751 &  0 &  0 & 30609 & 0 & 0 & 115324 & 1 & 1 & 210 & 1 \\
+ S3dropbox & 37751 &  0 &  0 & 30609 & 0 & 0 & 115324 & 1 & 1 & 210  \\
  \hline
-  SudokuSolver&  27730&  3 &  2 & 20907 & 3 & 2 & 39299 & 2 & 2 & 356 & 2 \\
+  SudokuSolver&  27730&  3 &  2 & 20907 & 3 & 2 & 39299 & 2 & 2 & 356  \\
  \hline
  \hline
-\multicolumn{12}{|l|}{Android mobile applications}   \\
+\multicolumn{11}{|l|}{Android mobile applications}   \\
  \hline
- SGTPuzzler & 13631 / 13865&  12 / 16 &  0 / 0 & 9546 / 9682& 4 / 4& 1 / 1 & 35198 / 35756 & 1 / 1  & 1 / 1& 104 & 1 \\
+ SGTPuzzler & 13631 / 13865&  12 / 16 &  0 / 0 & 9546 / 9682& 4 / 4& 1 / 1 & 35198 / 35756 & 1 / 1  & 1 / 1& 104 \\
  \hline
- Fennec & 14058 / 14387 &  1 / 1 &  0 / 0 & 8263 / 8898 & 1 / 1 & 0 / 0& 29125/ 31759 & 3 / 3 & 1 / 1& 433 & 1 \\
+ Fennec & 14058 / 14387 &  1 / 1 &  0 / 0 & 8263 / 8898 & 1 / 1 & 0 / 0& 29125/ 31759 & 3 / 3 & 1 / 1& 433 \\
  \hline
- MyTracks & 24036 / 24036 &  161 / 220 & 0 / 0 & 10803 / 13645 & 119 / 119 & 0 / 0 & 39235 / 110977 & 1 / 1 & 0 / 1 & 1192 & 1 \\
+ MyTracks & 24036 / 24036 &  161 / 220 & 0 / 0 & 10803 / 13645 & 119 / 119 & 0 / 0 & 39235 / 110977 & 1 / 1 & 0 / 1 & 1192 \\
 \hline
 \hline
- Total & 178279 / 178842 &  188 / 251 & 6 / 6 & 129744 / 133357 & 137 / 137& 7 / 7 & 461423 / 536358& 21 / 21 & 10 / 11 & 3521 & 11 \\
+ Total & 178279 / 178842 &  188 / 251 & 6 / 6 & 129744 / 133357 & 137 / 137& 7 / 7 & 461423 / 536358& 21 / 21 & 10 / 11 & 3521 \\
 \hline
@@
 using normal call graph construction algorithm and the reflection-aware
-call graph construction algorithm. The 6 errors found in VirgoFTP, FileBunker,
+call graph construction algorithm. The \bugs errors found in VirgoFTP, FileBunker,
 S3dropbox, and SudokuSolver are previously  unknown. As a comparison, the
-results of a straightforward approach (Section~\ref{sec:straightforward}) are show at the far right.} }
+results of a straightforward approach (Section~\ref{sec:straightforward}) are shown at the far right.} }
 \end{table*}
@@
 
-Table~\ref{table:results} tabulates the results of running our
-tool with three different call graph construction algorithms
-on the subject programs. From these results, we can see our
-tool found real errors from each subject on  four
-supported GUI frameworks. The results vary slightly according
-to the call graph algorithm used. In general, using
-the 1-CFA algorithm found most errors (11 in total) and least
-warnings (21 in total). The trade-offs of using other call graph
-construction algorithms will be explained in Section~\ref{sec:reflectionaware}.
+Table~\ref{table:results} tabulates the experimental results.
+Our tool found real errors in each subject programs.
 
-We further examined the detailed results for each subject.
-Among the 21 warnings issued by using the 1-CFA algorithm, 11
-warnings reveals 11 distinct errors, in which 6 are previously-unknown,
-2 warnings are false positive, and the remaining 8 
-are redundant warnings.
+%of running our
+%tool with three different call graph construction algorithms
+%on the subject programs. From these results, we can see our
+%tool found real errors from each subject on  four
+%supported GUI frameworks. The results vary slightly according
+%to the call graph algorithm used. In general, using
+%the 1-CFA algorithm found most errors (\bugs in total) and least
+%false positive warnings (\falses in total).
 
-%The primary
-%reason for the false positive is because the precision of call graph,
-%while the reason for redundant warnings is because multiple
-%methods ca
-%Even a context-sensitive call graph construction algorithm is used,
+%We further examined the detailed results for each subject.
+Among the \warnings warnings issued when using the 1-CFA call graph algorithm, \bugs
+warnings reveal \bugs distinct errors (\newbugs are previously unknown),
+2 warnings are false positives, and the remaining 8 warnings
+are redundant. Section~\ref{sec:reflectionaware} compares with other call graph
+construction algorithms.
 
-%why finds a bug in SGTPuzzle, because the \CodeIn{SmallKeyBoard} has been
-%explicitly created in this main class \CodeIn{SGTPuzzles} \CodeIn{setKeyboardVisibility},
-%thus, even without reflection-aware
+We have submitted all of the newly-found errors
+to the developers. As of Feb 2012, 1 error in S3dropbox has been confirmed.
+4 errors can be reproduced and validated in our own experimental environment, and
+1 error from FileBunker was submitted but has not been verified
+by its developers yet.
 
@@
 shows an invalid thread access error our tool found in the S3dropbox
-program. This error only happens when the \CodeIn{deterCurrentBucket}
-method at line 63 throws an exception, and can be hard to
-detect by testing, since the test must  execute that specific exception-handling
-path. We reported this error to the S3dropbox developers. Tom Czarniecki,
-a key developer of S3dropbox confirmed this potential single-GUI-thread
-violation. He mentioned that the S3dropbox project has already
-used certain design patterns and practice to avoid such violations (e.g.,
+program. This error only happens when the \CodeIn{deleteCurrentBucket}
+call on line 63 throws an exception, making it hard to
+detect by testing. We reported this error to the S3dropbox developers. Tom Czarniecki,
+a key developer of S3dropbox, confirmed this single-GUI-thread
+violation. He mentioned that the S3dropbox project uses
+certain design patterns to avoid such violations (e.g.,
 actions for UI interaction are encapsulated into a \CodeIn{Worker} interface),
-but they still overlooked  the reported code snippet.
+but they still overlooked  the error our tool found.
 
-Another reason of missing this violation is because some GUI frameworks like Swing
-do not provide any run-time checks for invalid thread accesses. Most
-of the time, programmers can get away with an apparently ``well behaved'' Swing
-GUI that actually breaks the single-GUI-thread rule. However, As clearly
-indicated in the official documentation, Swing is a single-GUI-threaded GUI
-toolkit, and is not thread-safe. All Swing code must be executed in the UI-thread and
-invoking Swing code from multiple threads risks thread interference
-or memory-consistency errors, particularly in the multi-core era.
+Another reason they overlooked this violation is because some GUI frameworks like Swing
+do not provide any run-time checks for invalid thread accesses. Swing
+GUI might not exhibit user-visible faults on many erreoneous executions.
+However, as clearly stated in the official documentation~\cite{swing}, Swing is a single-GUI-threaded GUI
+toolkit and invoking Swing code from multiple threads risks thread interference
+or memory-consistency errors.
 
@@
 \CodeIn{ResourceChangeEvent} happen, which then invokes the \CodeIn{refresh}
-method at line 415 to update the user interface. In EclipseRunner
-, the \CodeIn{refresh} method is
+method at line 415 to update the user interface. In EclipseRunner,
+the \CodeIn{refresh} method is
 called by 6 different methods from the same non-UI thread. Thus, our
-tool issues 6 separate warnings for each caller method to indicate
-6 different ways to trigger this error, despite that all the 6 warnings
-actually have the same error cause and are redundant with one another.
+tool issues 6 separate warnings to indicate
+6 different ways to trigger this error. 5 of the warnings are redundant.
+
+Besides the above two examples, other errors our tool reported were also
+subtle to find. Take the two newly-found errors in SudokuSolver
+as an example. One error happens when
+the given Sudoku is unsolvable; and the other one happens
+when the program fails to launch the mail composing window of the
+user default mail client (after clicking "eMail Me" button).
 
@@
 invalid thread access errors still exist in many corner cases and
-can be hard to find. Thus, a static analysis as presented in this paper
-would be useful.
+can be hard to find. 
+%Thus, a static analysis as presented in this paper
+%would be useful.
 
@@
 \noindent \textbf{\textit{Summary.}} Our technique can find real errors
-in multithreaded GUI applications on four different frameworks with
+in multithreaded GUI applications with
 acceptable accuracy.
 
-\subsubsection{Comparing to a Straightforward Approach}
+\subsubsection{Comparison to Requiring Wrappers}
 \label{sec:straightforward}
@@
 invalid thread access errors is to wrap every GUI accessing operation
-with message passing (i.e., via the safe methods). Thus, a
-straightforward way to detect potential invalid error
-is to check every method in the user code to determine whether all GUI-accessing operation
-is probably wrapped. If not, this approach issues a warning.% for every violation. 
-%If not, this approach issues warnings.
+with message passing (i.e., via the safe UI methods). Although
+this approach can give rise to other types of errors, a
+straightforward way to detect potential invalid thread access errors
+is to issue a warning whenever a GUI-accessing operation
+is not wrapped.
 
-We implemented this straightforward approach and experimentally compared it
-with our technique.% presented in Section~\ref{sec:technique}.
-The far right column in Table~\ref{table:results} shows the results.
-The results show that this straightforward approach can identify every
-error that our technique has found, but issue a huge number of false
-positives and redundant warnings. The primary reason is that this simple approach
-does not globally reason about calling relationship between
-threads, UI-accessing methods, and safe methods, thus it often incorrectly
+As shown in the far right column of ``Requiring Wrappers'' in
+Table~\ref{table:results}, Requiring Wrappers could identify every
+error that our technique found, but it issues a huge number of warnings,
+most of which are probably false positives.
+The primary reason is that this simple approach
+does not globally reason about the calling relationship between
+threads, UI-accessing methods, and safe UI methods, and thus it often incorrectly
 classifies GUI accessing operations which will never be executed
@@
 \noindent \textbf{\textit{Summary.}} Our technique provides
-richer contextually information for the reported error, and 
-is significantly more precise than the straightforward approach.
+richer contextual information for the reported error, and 
+is significantly more precise than requiring each GUI
+access to be wrapped.
 
@@
 used in our experiments. As shown in Table~\ref{table:results},  1-CFA found
-more errors with less warnings than the other two algorithms. This
+more errors with fewer false positive warnings than the other two algorithms. This
 is because RTA and 0-CFA do not consider the calling context when
@@
 The results in Table~\ref{table:results} also show that using a reflection-aware
-call graph construction algorithm is useful in finding errors in Android
+call graph construction algorithm helps in finding errors in Android
 applications. One error from the MyTracks Android application
@@
 
-In contrast, the error-related GUI objects in the other two Android applications (Fennec
-and SGTPuzzler) are created explicitly, so that a normal call graph construction
-algorithm can create a sufficiently complete call graph.
+Errors in the other two Android applications (Fennec and SGTPuzzler)
+can be found by using a standard call graph construction algorithm.
+This is because the error-related GUI objects are created explicitly,
+so the standard call graph construction algorithm is sufficient.
 
@@
 algorithm finds more errors than 0-CFA and RTA, and our reflection-aware call
-graph construction algorithm is useful to find errors on some
+graph construction algorithm helps to find errors on some
 Android applications.
@@
 
-The first variant uses DFS for graph traverse by changing method \CodeIn{getReachableStartsByBFS(cg)}
-to \CodeIn{getReachableStartsByDFS(cg)} on line 7, changing line 9 to
-$\mathit{fringe}$ $\leftarrow$ $\mathit{an}$ $\mathit{empty}$ $\mathit{stack}$,
-and changing queue operations (\CodeIn{enqueue} and \CodeIn{dequeue} on lines 11, 13, and 25 of Figure~\ref{fig:androiderror})
-to the correspondiing statck operations (\CodeIn{push} and \CodeIn{pop}).
-
-As a result, this variant found 8 errors in total and missed 1 error in the FileBunker subject.
+The first variant uses DFS for graph traversal by changing
+line 8 in Figure~\ref{fig:detectalgorithm} to:
+$\mathit{worklist}$ $\leftarrow$ $\mathit{an}$ $\mathit{empty}$ $\mathit{stack}$,
+and changing queue operations (\CodeIn{enqueueAll}, and \CodeIn{dequeue}
+on lines 9, 12, and
+23 in Figure~\ref{fig:androiderror}, respectively)
+to the corresponding statck operations (\CodeIn{pushAll}, and \CodeIn{pop}).
+This variant found 10 errors in total and missed 1 error in the FileBunker subject.
 The reason is that DFS tends to search deeper into the graph, and the path it returns
-is more likely not to be the shortest one. In the FileBunker subject, the path
-returned by DFS is much longer, and does not actually exist.
+may not be the shortest one and is more likely to be an infeasible path in practice.
+%For the FileBunker subject, paths
+%returned by DFS are much longer than BFS, and do not actually exist.
 
@@
 The second variant uses exhaustive search to find potential errors. This variant
-enumerates all non-cyclic paths from the start nodes, and then checks whether each
-path spawns a new thread and accesses GUI object without using safe methods. As
-a result, this variant run out of memory on all subjects. We checked
+enumerates all non-cyclic paths from all reachable \CodeIn{Thread.start()} nodes
+to each UI-accessing node, and then checks whether each
+path spawns a new thread and accesses GUI objects without using safe UI methods.
+This variant ran out of memory on all subjects. We checked
 the output paths before the algorithm terminated, and found none of the explored
-path revealed a valid error. This is because the number of
-non-cyclic paths in a graph is exponentially large to the graph node number.
-For a realistic call graph which often contains thousands of nodes, for which
-it is impossible to enumerate all paths in practice.
+path revealed a real error. This is because the number of
+non-cyclic paths in a graph is exponential in the graph node number.
+For a realistic call graph which often contains thousands of nodes,
+it is infeasible to enumerate all paths.
+%only a very few amount of paths can be enumerated within a practical amount of time.
 
@@
 
-\subsubsection{Evaluating Heuristic Filters}
+\subsubsection{Evaluating Error Filters}
 \label{sec:filters}
 
-We measure the effectiveness of the proposed heuristic filters of
-Section~\ref{sec:heuristic} in terms of the number of removed false positives and
-redundant warnings.
+Table~\ref{table:filters} measures the effectiveness of the proposed 
+error filters of Section~\ref{sec:heuristic}
 
-Table~\ref{table:filters} tabulates the results.
-Our static analysis output thousands of warnings for the evaluated
-subjects, but the proposed heuristic filters effectively reduced
-the number of likely invalid warnings. On average, five heuristic
-filters removed 99.96\% of the reported warnings as false positives
+The five error filters removed 99.96\% of the reported warnings as false positives
 or redundant warnings. Specifically, heuristic filters 1 and 2 identified
-32.48\% of the warnings as likely false positives, and filters 3, 4,
-and 5 identified 67.48\% of the warnings as redundant warnings.
-Remarkably, the 3rd heuristic filter for removing lexically redundant
-reports is the most effective one on the evaluated subjects: it removes 35277 redundant warnings.
+29.38\% of the warnings as likely false positives, and filters 3, 4,
+and 5 identified 70.58\% of the warnings as redundant warnings.
+The 3rd filter for removing lexically redundant
+reports is the most effective one.
+% on the evaluated subjects: it removes 37019 redundant warnings.
 
@@
 issue false positives or redundant reports, a set of well-designed
-heuristics can still remove most of them.
+sound and heuristic filters can still remove most of them.
 %Heuristic filter, effective.
@@
 \hline
- Subject & Before & \#W & \#W & \#W & \#W& \#W \\
- Program & Filtering & $F_1$ & $F_2$ & $F_3$&$F_4$ & $F_5$\\
+ & \multicolumn{6}{|c|}{Number of Warnings}  \\
+\cline{2-7}
+ Subject & Before & \multicolumn{2}{|c|}{Sound Filters}  &  \multicolumn{3}{|c|}{Heuristic Filters}  \\
+\cline{3-7}
+ Program &Filtering  & $F_1$ & $F_{1,2}$ & $F_{1,2,3}$&$F_{1,2,3,4}$ & $F_{1,2,3,4,5}$\\
 \hline \hline
@@
 \Caption{{\label{table:filters}Number of warnings after applying a set of
-heuristic filters (Section~\ref{sec:heuristic}). Column ``Before Filtering''
-shows the output warning number using the reflection-aware 1-CFA algorithm.
-Column ``\#W $F_i$'' represents the number of remaining warnings after applying
-filters 1 -- $i$. Numbers in last column are taken
-from Table~\ref{table:results}.
-Results of using other algorithms show similar patterns, which are omitted for brevity.} }
+sound and heuristic filters. Column ``Before Filtering''
+shows the number of warnings by the reflection-aware 1-CFA algorithm.
+Other algorithms show similar patterns, which are omitted for brevity.
+Column ``$F_{i,...,j}$'' represents the number of remaining warnings after applying
+the $i$th to $j$th filters as defined in Section~\ref{sec:heuristic}.
+The numbers in the last column are the same as the subcolumn ``\#Warnings"
+under column ``1-CFA'' in Table~\ref{table:results}.
+} }
 \end{table}
@@
 \noindent \textbf{\textit{Performance and scalability.}} Our tool
-has been evaluated on 9 subjects with over 76 KLOC and dependent
-libraries with over 1.4 MLOC, showing good scalability.
-For each subject program, it runs in a practical amount of time. Our evaluations
+has been evaluated on \subnum subjects with over \totaloc LOC and frameworks
+with over 1.4 MLOC, showing good scalability. Our evaluations
 were conducted on a 2.67GHz Intel Core PC with 4GB
@@
 
-%Our experiments also demonstrate that our approach has good scalability.
-%Together with all dependent library code, our tool has analyzed
-%XXX LOC in total  xxx the largest program.
-%Our tool has analyzed xxx LOC in total, and together with all dependent libraries,
-%the largest subject our approach can analyze and detect errors has
-%over XXX LOC, xx classes, and xxx methods.
-
 \vspace{1mm}
@@
 \noindent \textbf{\textit{Threats to validity.}}
-There are two threats to validity in our evaluation. 
-The major threat is the degree to which the subject programs
+There are two major threats to validity in our evaluation. 
+One threat is the degree to which the subject programs
 used in our experiment are representative of true practice.
@@
 
-%Future work could evaluate our technique on more subjects, and
-%investigate the false negative rate.
-
-%our technique requires developers to manually
-%add annotations to provide call relationships
-%Second,
-
-%Third, for subject program
-%that uses native methods,
-
 \vspace{1mm}
@@
 The technique presented in this paper offers a promising solution.
-Our technique finds real-world errors, and issues
-%Compared with the straightforward approach to check every
-%GUI accessing code isolatedly, our technique produces
-significantly less warnings when compared to a straightforward
-approach. In addition, the reflection-aware call graph construction algorithm
-is critical in detecting errors on Android applications, and our
-proposed heuristic filtering rules are useful to reduce invalid warnings.
-
-%in reducing programmers'
-%burden to inspect the output result.
-
-%In practice, programmers
-%have designed practices and patterns to avoid such errors in the first
-%place, but can easily overlook corner cases like exception-handling
-%methods.
-
-%Findings: programmers have noted this problem, but often overlook special cases like error handle, subtype
-
-% Reporting on violations is fine but what is more important are the practices and patterns that need to be adopted to make it easier to avoid the issue in the first place.
-That is why there is a Worker interface in this project
+Our technique finds real-world errors and issues
+few false positive warnings. Our
+proposed filters are useful to reduce the number of warnings.

### 2012-02-06 trunk/GUIErrorDetector/paper/introduction.tex
significant revise

@@
 If not, an \textit{invalid thread access error} will occur. This may
-terminate the application, but it is considered \textbf{hard-to-recognize? probabably?} to nondeterministic concurrency errors.
+terminate the application, but it is considered preferable
+to nondeterministic concurrency errors.
 
@@
      \}
-
 \end{alltt}
 \end{CodeOut}
-\vspace*{-2.0ex} \Caption{{\label{fig:androiderror} 
-Bug 703256 reported on 11/17/2011 in Mozilla Firefox release 10.0.a.rc3
-for Android. On line 74, \CodeIn{LayerView}'s constructor
+\vspace*{-3.0ex} \Caption{{\label{fig:androiderror} 
+Bug 703256 reported on 11/17/2011 in Fennec (Mozilla Firefox for Android)
+release 10.0.a.rc3. On line 74, \CodeIn{LayerView}'s constructor
 calls method \CodeIn{setRenderer} which 
@@
 with a GUI. Each sequence of GUI events can result in
-a difficult state, and each GUI event may need to be evaluated in all of
+a different state, and each GUI event may need to be evaluated in all of
 these states. A well-developed software system like Eclipse
@@
 
+{\vspace{2mm}
+\hspace{3mm}\small{In class: org.mozilla.gecko.gfx.LayerRenderer}
+\vspace{-2mm}
 \begin{CodeOut}
 \begin{alltt}
-     /* In class: org.mozilla.gecko.gfx.LayerRenderer */
 220. public void onSurfaceChanged(GL10 gl, int width, int height) \{
@@
 \end{alltt}
-\end{CodeOut}
+\end{CodeOut}}
 
@@
 %$\rightarrow$\CodeIn{ \scriptsize{android.view.ViewRoot.checkThread()}}
-\vspace*{-2.0ex} \Caption{{\label{fig:report} Our tool reports
+\vspace*{-3.0ex} \Caption{{\label{fig:report} Our tool reports
 a method call chain that reveals the potential error in
@@
 to the same error. To address such limitations, we devise a set
- of heuristics to filter likely false positives and redundant warnings.
+ of sound and heuristic filters to remove likely false positives and redundant warnings.
 
@@
 Although our technique is applicable to any GUI
-framework with the single-GUI-thread rule. Each framework
+framework with the single-GUI-thread rule, each framework
 has its own definition of \textit{UI thread} and \textit{program 
@@
 
-Our tool works in a fully automatic, push-button manner, and scales to realistic programs.
-We evaluated our implementation on 9 programs comprising over 76000 LOC.
+Our tool works in a fully automatic, push-button manner,
+and scales to realistic programs.
+We evaluated our implementation on \subnum programs comprising over \totaloc LOC.
 The experiment results demonstrate
-that: our technique is effective (it found 11 real-world errors
-from four supported frameworks and produced 10 false positive warnings);
-our reflection-aware call graph construction algorithm is
-critical in finding errors in Android applications;
-and our proposed
-heuristics significantly reduce the number of
+that: our technique is effective (it found \bugs real-world errors
+from four supported frameworks and produced only \falses false positive warnings);
+our reflection-aware call graph construction algorithm helps in
+finding errors in Android applications;
+and our proposed filters significantly reduce the number of
 false positives and redundant warnings.
@@
 
-\item \textbf{Evaluation.} We applied our tool to 9 programs 
-from 4 different frameworks, comprising over 76000 LOC. The results
+\item \textbf{Evaluation.} We applied our tool to \subnum programs 
+from 4 different frameworks, comprising over \totaloc LOC. The results
 show the usefulness of the proposed technique (Section~\ref{sec:evaluation}).

### 2012-02-06 trunk/GUIErrorDetector/paper/technique.tex
significant revise

@@
 As an example, for a SWT desktop application, the entry nodes include
-the single main method, UI-accessing nodes include 
+the single main method, UI-accessing nodes include methods
 \CodeIn{Display.checkWidget} and \CodeIn{Display.checkDevice},
@@
 
-The algorithm first performs graph traversal to find all reachable \CodeIn{Thread.start()}
-nodes from the entry nodes (line 6).
+The algorithm first performs graph traversal to find
+all reachable \CodeIn{Thread.start()}
+nodes from each entry node (line 7).
 %For each entry node, the algorithm uses standard Breadth First Search (BFS)
@@
 The algorithm uses BFS to search for reachable UI-accessing
-methods (lines 10 -- 25).
+methods (lines 11 -- 25).
 The algorithm stops the traversal if it reaches a UI-accessing
-method (lines 16 -- 18) or a safe UI method (lines 19, 20).
+method (lines 17 -- 19) or a safe UI method (lines 20, 21).
 %Specifically, it uses a queue to keep track of the nodes to be visited (line 7),
@@
 
-The error message created by the method \CodeIn{createErrorReport} on line 17
+The error message created by the method \CodeIn{createErrorReport} on line 18
 includes the method call chain from the entry node to the UI-accessing node
@@
 \STATE $\mathit{entryNodes}$ $\leftarrow$ getEntryNodes($\mathit{cg}$)
-\STATE $\mathit{uiAccessingNodes}$ $\leftarrow$ getUIAccessNodes($\mathit{cg}$)
-\STATE $\mathit{safeUINodes}$ $\leftarrow$ getSafeNodes($\mathit{cg}$)\\
-\COMMENT{get all reachable \CodeIn{thread.start()} nodes from entry nodes}
-\STATE $\mathit{threadStarts}$ $\leftarrow$ $\bigcup_{entry \in entryNodes}$ getReachableStarts($\mathit{entry}$)
+\STATE $\mathit{uiAccessingNodes}$ $\leftarrow$ getUIAccessingNodes($\mathit{cg}$)
+\STATE $\mathit{safeUINodes}$ $\leftarrow$ getSafeUINodes($\mathit{cg}$)\\
+\FOR{each $\mathit{entryNode}$ in $\mathit{entryNodes}$}
+\STATE $\mathit{threadStarts}$ $\leftarrow$ getReachableStarts($\mathit{entryNode}$)\\
 \COMMENT{keep the nodes to be visited next in a worklist}
@@
 \ENDWHILE
+\ENDFOR
 \RETURN $errors$
@@
 we empirically compared three different graph search strategies, and demonstrated that
-using BFS, algorithm found more errors than DFS and
+using BFS, the algorithm found more errors than DFS and
 exhaustive path search.
+
+\subsection{Call Graph Construction}
 
@@
 
-\subsubsection{Reflection-aware Call Graph Construction}
+\subsubsection{Reflection}
 \label{sec:cg}
@@
 and the Java code (the bottom)
-first loads the XML file (line 6) and then uses reflection to create
-a Button object by its ID (line 7, the \CodeIn{findViewById} method).}
+first loads the XML file (line 5) and then uses reflection to create
+a Button object by its ID (line 6, the \CodeIn{findViewById} method).}
 \label{fig:sampleandroid}
@@
 When analyzing the code in Figure~\ref{fig:sampleandroid}, existing call graph algorithms
-fail to conclude that the variable \CodeIn{button} declared at line 7
+fail to conclude that the variable \CodeIn{button} declared at line 6
 points to a \textit{non-null} \CodeIn{Button} object due to its limitation in deal with the
@@
 file in an Android application to extract the class declaration
- correspondinig to the given \CodeIn{id} value. If the \CodeIn{id}
+ corresponding to the given \CodeIn{id} value. If the \CodeIn{id}
 value is dynamically generated, this method will conservatively
@@
 
-\subsubsection{Annotation for Native Methods}
+\subsubsection{Native Methods}
 \label{sec:annotation}
 
-A GUI application may also use native methods to interact with the underlying
-operating system or platforms. However, native methods are often
+A GUI application may use native methods to interact with the underlying
+operating system or platform. Native methods are often
 beyond the ability of a static analysis but should be considered to make
@@
 
-Our static analysis takes the call relationship specified by this
+\noindent Our static analysis takes the call relationship specified by this
 annotation into consideration when traversing the call graph. 
 Adding annotations for native methods is optional and requires manual effort.
-In our experiments, 1 out of 9 programs uses native methods to interact with
-the underlying operating system. We manually
+In our experiments, 1 out of \subnum programs uses native methods. We manually
 searched the source files, inspected the code to determine possible target methods
-that may be called by a native method, and added 7 annotations for this program.
-We found such an annotation, was useful: one real-world bug
-can only be reported with using the user-provided annotations.
+that may be called by a native method, and added \annotationnum annotations for this program.
+We found such an annotation was useful: one error
+is only reported when using the user-provided annotations.
 
-\subsubsection{Heuristic Filtering}
+\subsection{Filtering the Error Reports}
 \label{sec:heuristic}
@@
  that have the same error cause (redundant warnings). We devise
-5 heuristic filters below to remove likely false positives and redundant warnings.
-The first two are for eliminating false positives, while the
-other three are for reducing redundant warnings.
+5 filters below to remove likely false positives and redundant warnings.
+The first 2 filters are sound in that they will not filter real bugs, and
+other 3 filters are based on heuristics. Orthogonally, filters 2
+and 3 are for eliminating false positives, and filters 1, 4, and 5
+are for reducing redundant warnings.
+
+%1 - subsumed, 2 - user annotated, 3 - sysem call, 4 heand  5,  tail
 
@@
 %\item
-\textbf{1. Filter Reports Containing Library Calls}. A
-method call chain containing certain library calls
-like \CodeIn{Runtime.}\CodeIn{shutDown} are unlikely to
-be buggy. For example, the \CodeIn{Runtime.}\CodeIn{shutDown}
-method is called when JVM terminates, and uses multithreading
-to dispose all GUI objects when the program exits.
-We encoded a list of common library calls by proposing
-a basic set of library calls that seemed natural and
-generally applicable, based on our programming experience.
-We later added other calls we found helpful in analyzing
-programs and that we believed would be generally useful.
-%We encode a list of common library calls, and remove
-%a reported warning if it contains one of them.
-%Method call chain involves typical
-%system methods like \CodeIn{toString} are unlikely to reveal a real bug.
+
+\subsubsection{Sound Filters}
+
+\textbf{1. Filter Lexically Redundant Reports}. One reported method call
+chain can lexically subsume another one. For example, suppose that two
+reported method call chains: \CodeIn{a()} $\rightarrow$ \CodeIn{b()}
+$\rightarrow$ \CodeIn{c()} and 
+\CodeIn{d()} $\rightarrow$ \CodeIn{a()} $\rightarrow$ \CodeIn{b()} $\rightarrow$ \CodeIn{c()}
+both lead to a potential error, since $\CodeIn{d()}$ and \CodeIn{a()}
+are two distinct entry methods. The second call chain should
+be removed and would not reduce the error detection capability, since
+the first chain reveals the same error and is shorter 
+for programmers to interpret.
 
@@
 
+\subsubsection{Heuristic Filters}
 %\item
-\textbf{3. Filter Lexically Redundant Reports}. One reported method call
-chain can lexically subsume another one. For example, suppose that two
-reported method call chains: \CodeIn{a()} $\rightarrow$ \CodeIn{b()}
-$\rightarrow$ \CodeIn{c()} and 
-\CodeIn{d()} $\rightarrow$ \CodeIn{a()} $\rightarrow$ \CodeIn{b()} $\rightarrow$ \CodeIn{c()}
-both lead to a potential error, since $\CodeIn{d()}$ and \CodeIn{a()}
-are two distinct entry methods. The second call chain should
-be removed and would not reduce the error detection capability, since
-the first chain reveals the same error and is shorter 
-for programmers to interpret.
 
-%\item
-\textbf{4. Filter Report With the Same Head Methods from The Entry Node to \CodeIn{Thread.start()}}. A method can call
+\textbf{3. Filter Reports Containing Library Calls}. A
+method call chain containing certain library calls
+like \CodeIn{Runtime.}\CodeIn{shutDown} are unlikely to
+be buggy. For example, the \CodeIn{Runtime.}\CodeIn{shutDown}
+method is called when JVM terminates, and uses multithreading
+to dispose all GUI objects when the program exits.
+We encoded a list of common library calls by proposing
+a basic set of library calls that seemed natural and
+generally applicable, based on our programming experience.
+We later added other calls we found helpful in analyzing
+programs and that we believed would be generally useful.
+
+\textbf{4. Filter Report With the Same Head Methods from the Entry Node to \CodeIn{Thread.start()}}. A method can call
 multiple methods that access GUI objects, such as:
-\vspace{-1mm}
+\vspace{-2mm}
 \begin{CodeOut}
@@
 \end{CodeOut}
-If method \CodeIn{m()} is invoked by a non-UI thread, method call chains
-only different at the last few method nodes may be reported separately, such as:
+\vspace{-2mm}
+If method \CodeIn{m()} is invoked by a non-UI thread, method call chains that
+only differ in the last few method nodes may be reported separately, such as:
 
-\CodeIn{a()} $\rightarrow$ ...\CodeIn{Thread.start()} ... $\rightarrow$ \CodeIn{m()} $\rightarrow$ \CodeIn{accessUIObject1()} ...
+\CodeIn{a()} $\rightarrow$ ...\CodeIn{Thread.start()} $\rightarrow$ \CodeIn{m()} $\rightarrow$ \CodeIn{accessUIObject1()} ...
 
-\CodeIn{a()} $\rightarrow$ ...\CodeIn{Thread.start()} ... $\rightarrow$ \CodeIn{m()} $\rightarrow$ \CodeIn{accessUIObject2()} ...
+\CodeIn{a()} $\rightarrow$ ...\CodeIn{Thread.start()} $\rightarrow$ \CodeIn{m()} $\rightarrow$ \CodeIn{accessUIObject2()} ...
 
@@
 
-Among the above 5 filters, filters 2 and 3 are sound
-in that they will not filter real bugs, and other 3 filters
-are based on heuristics. However, as we will show in
-our experiments, these filters work remarkably well in practice.
-
-\subsection{Instantiation for Different Frameworks}
-\label{sec:platforms}
-
-We instantiated our error detection techniques for four popular GUI frameworks,
-namely SWT, Eclipse plugin environment, Swing, and Android.
-The major framework-specific parts, corresponding to
-lines 3 -- 5 in Figure~\ref{fig:detectalgorithm}, are identifying
-\textbf{call graph entry nodes}, \textbf{UI-accessing nodes},
-and \textbf{safe UI methods} for each framework.
-
-%For each framework, we customize the \textit{call graph entry nodes},
-%\textit{UI-accessing nodes}, and \textit{safe UI methods} on lines 3 -- 5 of the
-%algorithm in
-
-%For the sake of efficiency, they are all using the single thread model.
-
-%Why these platforms? popularity? account for xxx\% of the GUI.
-
-%customizing for: entry points, starting points, error checking, thread
-%safe UI methods, what is the event dispatching thread?
-
-\subsubsection{SWT}
-
-%SWT is an open source widget toolkit for Java designed to provide efficient,
-%portable access to the GUI facilities of the operating systems
-%on which it is implemented.
- We instantiate our technique for SWT applications as follows:
-
-%starts from its main method.
-%By default, the thread that the main method executes is the UI thread. Thus, we instantiate
-%our technique as follows:
-
-\begin{itemize}
-
-\item \textbf{Call graph entry nodes: } the main method. Like a normal Java program,
-a SWT desktop application has a single main method as the entry point. By default,
-the main method is executed in the UI thread after the GUI
-is initialized.
-
-\item \textbf{UI-accessing nodes: } the \CodeIn{Display.checkWidget}
-and \CodeIn{Display.} \CodeIn{checkDevice} methods. SWT uses the above
-two methods to explicitly check illegal thread accesses at runtime.
-Any methods for manipulating GUI object must call (one of) these two methods
- to determine whether the current thread is the UI thread or not.
-%Thus, we treat nodes (in both user code and framework code) corresponding to the methods
-%calling these two methods as UI-accessing nodes.
-%must be invoked
-%in the UI thread and as
-%UI-accessing nodes.
- %methods to check whether the current thread is the UI thread or not. Thus,
-%we treat all such methods that must be accessed in UI thread as the UI-accessing nodes.
-% any
-%methods that calls the checking method must be invoked in the UI thread.
-
-\item \textbf{Safe UI methods: } SWT provides two helper methods (\CodeIn{Display.\\asyncExec}
-and \CodeIn{Display.syncExec}) to execute code (a)synchro-
-nizedly on the UI thread.
- We treat these two methods as safe UI methods, since invoking
-them from any thread 
-%are generally considered to be safe and
-will not cause an invalid thread access error.
-
-\end{itemize}
-
-\subsubsection{Eclipse plugin}
-
-We instantiated our technique for Eclipse plugin as follows:
-
-%Unlike a SWT desktop application, an eclipse plugin, though is developed in SWT,
-%has no single main method. Instead, (XXX) it extends certain extension points
-%exposed by the eclipse framework, and eclipse will XXX. To instantiate our
-%technique for the Eclipse plugin environment, we need to redefine the
-%call graph entry points.
-
-\begin{itemize}
-
-\item \textbf{Call graph entry nodes: } all overridden SWT
-GUI event handling methods in user code. An Eclipse plugin is built
-on top of the SWT framework. However, unlike a SWT desktop application,
-an Eclipse plugin does not have a main method as a single program entry point.
-Instead, it extends extension points provided by the Eclispe framework to
-implement functionalities. When a plugin starts, Eclipse
-calls back the overridden extension points to handle the
-upcoming events. All SWT GUI event handling methods (i.e., the overriden
-methods in the class that implements \CodeIn{org.eclipse.swt.internal.\\SWTEventListener}) are
-always called back from the UI thread, thus are used as call graph entry nodes.
-
-\item \textbf{UI-accessing nodes} and \textbf{Safe UI methods} are the same as SWT.
-
-\end{itemize}
-
-\subsubsection{Swing}
-
-A Swing application has a single main method, but contains three kinds of
-threads: \textit{initial thread} that executes initial application code from the main method,
-the \textit{UI thread}, where all GUI manipulation code is executed,
-and the \textit{worker thread} where time-consuming background tasks are executed.
-After a Swing program starts, its initial thread exits and the UI thread takes charge
-of the application and starts to execute all event-handling code or spawns new worker threads. 
-We instantiated our technique for Swing as follows:
-%XXXX Therefore, we can not directly
-%use the main method as the call graph entry point, since it is not invoked
-%by the UI thread. We customize our technique for Swing as follows:
-
-\begin{itemize}
-
-\item \textbf{Call graph entry nodes:} all overridden Swing GUI event handling
-methods in user code. Those event handling methods are always
-called back from the UI thread, thus are used as call graph entry nodes.
-
-\item \textbf{UI-accessing nodes:} %as stated in Swing's documentation,
-all methods defined in each Swing GUI class except for three thread-safe
-methods: \CodeIn{repaint()}, \CodeIn{revalidate()}, and \CodeIn{invalidate()}.
-
-%methods in Swing GUI classes are not thread safe with three exceptions (\CodeIn{repaint()},
-%\CodeIn{revalidate()}, and \CodeIn{invalidate()}). Thus, we
-%treat nodes corresponding to those thread unsafe methods %in each GUI class
-%as UI-accessing nodes.
-
-\item \textbf{Safe UI methods: }  Swing's two helper methods
-(\CodeIn{SwingUtilities.} \CodeIn{invokeLater} and \CodeIn{SwingUtilities.invokeAndWait}) that execute code in the UI thread.
-
-\end{itemize}
-
-\subsubsection{Android}
-
-Android is a Java-based platform for embedded or mobile devices. 
-An Android program does not have a single entry point but can
-rather use parts of other Android applications on-demand and can require their
-services by calling corresponding event handlers, directly or through the
-operating system. In particular, Android applications use \textit{activities}
-as code interacting with the user through a visual interface. GUI event handlers
-are handled in an activity.
-We instantiated our technique for Android programs as follows:
-%, with some notable exceptions such as the
-%lifecycle of activities.
-
-%An XML \textit{manifest file} registers the components of an application. Other XML
-%fies describe the visual layout of the activities. Activities \textit{inflate}
-%layout files into
-%visual objects (a hierarchy of views), through an \textit{inflater} provided by the An-
-%droid library. This means that library or user-defined views are not explicitly
-%created by new statements but rather inflated through \textit{reflection}. Library meth-
-%ods such as \CodeIn{findViewById} access the inflated views.
-
-\begin{itemize}
-
-\item \textbf{Call graph entry nodes: }in an Android application,
-an \CodeIn{Activity} object is created and manipulated by the UI thread. Thus, we treat
-all public methods defined in the \CodeIn{Activity} class 
-and any class in the user code that subclasses \CodeIn{Activity} as call graph entry nodes.
-We also add all overridden Android GUI event handling methods in user
-code as entry nodes, since they must be called back from the UI thread.
-
-\item \textbf{UI-accessing nodes: }the \CodeIn{ViewRoot.checkThread} method.
-Like SWT, Android explicitly checks whether
-the current thread is a UI thread or not before accessing a GUI object via
-the \CodeIn{ViewRoot.checkThread} method.
-%method. This method is the only place where Android checks
-%whether the current thread is the UI thread or not. Thus, any
-%methods that calls the checking method must be invoked in the UI thread.
-
-\item \textbf{Safe UI methods: } two helper methods (\CodeIn{View.post}
-and \CodeIn{View.postDelay}) that execute code on the UI thread. 
-Invoking them on any thread will not cause an invalid thread access error.
-%Invoking these two methods are generally considered to be safe, and would not
-%cause an invalid thread access error.
-
-\end{itemize}
-
-Instantiating our general technique to  a specific framework
-requires moderate human effort. We wrote around 500 lines of Java code in total to achieve
-the above four instantiations.
+As we will show in our experiments (Section~\ref{sec:filters}), these filters
+work remarkably well by reducing over 99\% of the reported warnings. In addition,
+we also found that only using sound filters was not sufficient. The overwhelming
+number of warnings after applied sound filters motivated the use
+of heuristic filters.

### 2012-02-06 GUIErrorDetector/paper/conclusion.tex
significant revise

@@
 In this paper, we presented a general technique to find invalid
-thread access errors in multithreaded GUI applications. 
+thread access errors for multithreaded GUI applications. 
 Our technique statically explores paths in a call graph to check
@@
 It uses a reflection-aware call graph construction algorithm
-to build a good call graph, and employs a set of heuristics to
-filter likely false positives and redundant reports.
+to build a good call graph, and employs a set of sound and heuristic
+filters to filter likely false positives and redundant warnings.
 Since graphical user interfaces are often inadequately tested due
@@
 more potential errors %before the application is released to customers (XXX),
-and thus encourage GUI developers to improve software reliability.
-
-We have demonstrated that our technique can be useful
+ to improve software reliability.
+We have also demonstrated that our technique can be useful
 by an evaluation on 9 subjects acrosss 4 popular GUI
@@
 \textbf{Integration with dynamic and symbolic analyses.} The technique 
-presented in this paper is a pure static analysis. It
-uses a combined RTA and k-CFA  algorithm to construct a relatively
-complete and precise call graph. However, our technique still suffers from
-a false positive rate for many GUI applications, due to the conservative
-nature of static analysis. A possible way to reduce such false
-positives is to integrate the current static analysis with
+presented in this paper is a call graph-based, pure static analysis. 
+It may suffer from false positives for many GUI applications,
+due to the conservative nature of static analysis.
+A possible way to reduce the number of false
+positives is to integrate with
 dynamic analyses~\cite{Jiang:2008:PPS:1453101.1453110}%, ZhangSBE2011}
 or symbolic analyses~\cite{xie05:symstra, Pasareanu:2011, halfond09issta, BMF97}
-by employing more accurate information to guide call graph exploration.
+by using more accurate information to guide call graph exploration.
 
@@
 to unit test multithreaded GUI programs to find potential errors \textit{earlier}. We
-are interested in investigating how to apply recent advance in automated
+plan to investigate how to apply recent advance in automated
 testing~\cite{Staats:2011:PTO:1985793.1985847, Jagannath:2011:IMU:2025113.2025145, Muccini_Bertolino_Inverardi_2004, Ricca:2001:ATW:381473.381476, Harman:2007}

### 2012-02-06 GUIErrorDetector/paper/implementation.tex
significant revise

@@
 
-We implemented the proposed technique using the WALA framework~\cite{walatutorial}.
-Our prototype tool takes Java bytecode as input, works in a fully
-automatic and push-button way to detect potential invalid thread access
+We instantiated the proposed technique for four widely-used
+GUI frameworks, namely SWT, Eclipse plugin development, Swing, and Android;
+and implemented a prototype tool.
+Our tool is built on top of the WALA framework~\cite{walatutorial}.
+It takes Java bytecode as input, 
+automatically detects potential invalid thread access
 errors, and scales to realistic programs.
 
-%Optionally, users may specify additional heuristic filters (Section~\ref{sec:heuristic}) %to guide call graph traverse
-%, and annotate call relationships for native methods (Section~\ref{sec:annotation}).
+%We implemented the proposed technique using the WALA framework~\cite{walatutorial}.
+%Our prototype tool takes Java bytecode as input, 
+%automatically detects potential invalid thread access
+%errors, and scales to realistic programs.
 
-Our current implementation supports four widely-used GUI frameworks, namely
-SWT, Eclipse plugin development, Swing, and Android.
-%, including dependent libraries such as \CodeIn{rt.jar} and \CodeIn{android.jar}.
-%into analysis. 
+%Static Single Assignment (SSA) transformation to get limited flow sensitivity
+\subsection{Instantiation for Different Frameworks}
+\label{sec:platforms}
+
+%We instantiated our error detection technique for four popular GUI frameworks:
+%SWT, Eclipse plugin, Swing, and Android.
+When instantiating our error detection technique for different
+frameworks, the major framework-specific parts, corresponding to
+lines 3 -- 5 in Figure~\ref{fig:detectalgorithm}, are identifying
+\textbf{call graph entry nodes}, \textbf{UI-accessing nodes},
+and \textbf{safe UI methods} for each framework.
+
+%For each framework, we customize the \textit{call graph entry nodes},
+%\textit{UI-accessing nodes}, and \textit{safe UI methods} on lines 3 -- 5 of the
+%algorithm in
+
+%For the sake of efficiency, they are all using the single thread model.
+
+%Why these platforms? popularity? account for xxx\% of the GUI.
+
+%customizing for: entry points, starting points, error checking, thread
+%safe UI methods, what is the event dispatching thread?
+
+\newcommand{\smallstep}{\vspace{-2mm}}
+\subsubsection{SWT}
+
+ We instantiated our technique for SWT applications as follows:
+
+\begin{itemize}
+\smallstep
+
+\item \textbf{Call graph entry nodes: } the main method. Like a normal Java program,
+a SWT desktop application has a single main method as the entry point. By default,
+the main method is executed in the UI thread after the GUI
+is initialized.
+
+\smallstep
+
+\item \textbf{UI-accessing nodes: } the \CodeIn{Display.checkWidget}
+and \CodeIn{Display.} \CodeIn{checkDevice} methods. SWT uses the above
+two methods to explicitly check thread accesses at runtime.
+%Any methods for manipulating GUIs object must call (one of) these two methods
+% to determine whether the current thread is the UI thread or not.
+\smallstep
+
+\item \textbf{Safe UI methods: } \CodeIn{Display.asyncExec}
+and \CodeIn{Display.syncExec}. SWT provides these two methods
+to execute code (a)synchro- nizedly on the UI thread.
+%We treat these two methods as safe UI methods, since invoking
+%them from any thread 
+%will not cause an invalid thread access error.
+
+\end{itemize}
+
+\subsubsection{Eclipse plugin}
+
+We instantiated our technique for the Eclipse plugin development framework as follows:
+
+\smallstep
+
+%Unlike a SWT desktop application, an eclipse plugin, though is developed in SWT,
+%has no single main method. Instead, (XXX) it extends certain extension points
+%exposed by the eclipse framework, and eclipse will XXX. To instantiate our
+%technique for the Eclipse plugin environment, we need to redefine the
+%call graph entry points.
+
+\begin{itemize}
+
+\item \textbf{Call graph entry nodes: } all user code methods that override
+ SWT GUI event handling methods. Eclipse
+calls back the overridden methods to handle the
+events. All SWT GUI event handling methods (i.e., the overriden
+methods in the class that implements \CodeIn{org.eclipse.swt.internal.SWTEventListener}) are
+always called back from the UI thread, thus are used as call graph entry nodes.
+
+\smallstep
+
+\item \textbf{UI-accessing nodes} and \textbf{Safe UI methods} are the same as SWT.
+
+\end{itemize}
+
+\subsubsection{Swing}
+
+A Swing application has a single main method, but contains three kinds of
+threads: \textit{initial thread} that executes initial application code from the main method,
+the \textit{UI thread}, where all GUI manipulation code is executed,
+and the \textit{worker thread} where time-consuming background tasks are executed.
+After a Swing program starts, its initial thread exits and the UI thread takes charge
+of the application and starts to execute all event-handling code or spawns new worker threads. 
+We instantiated our technique for Swing as follows:
+%XXXX Therefore, we can not directly
+%use the main method as the call graph entry point, since it is not invoked
+%by the UI thread. We customize our technique for Swing as follows:
+
+\begin{itemize}
+
+\item \textbf{Call graph entry nodes:} all overridden Swing GUI event handling
+methods in user code. Those event handling methods are always
+called back from the UI thread.
+
+\smallstep
+
+\item \textbf{UI-accessing nodes:} %as stated in Swing's documentation,
+all methods defined in each Swing GUI class except for three thread-safe
+methods: \CodeIn{repaint()}, \CodeIn{revalidate()}, and \CodeIn{invalidate()}.
+
+\smallstep
+
+\item \textbf{Safe UI methods: } 
+\CodeIn{SwingUtilities.}\CodeIn{invokeLater} and \CodeIn{Swing-\\Utilities.invokeAndWait} that execute code on the UI thread.
+
+\end{itemize}
+
+\smallstep
+
+\subsubsection{Android}
+
+Android is a Java-based platform for embedded or mobile devices. 
+An Android program does not have a single entry point but can
+rather use parts of other Android applications on-demand and can require their
+services by calling corresponding event handlers, directly or through the
+operating system. In particular, Android applications use \textit{activities}
+(i.e., instances of the \CodeIn{Activity} class)
+to interact with users through a visual interface and handle GUI events.
+We instantiated our technique for Android programs as follows:
+%, with some notable exceptions such as the
+%lifecycle of activities.
+
+%An XML \textit{manifest file} registers the components of an application. Other XML
+%fies describe the visual layout of the activities. Activities \textit{inflate}
+%layout files into
+%visual objects (a hierarchy of views), through an \textit{inflater} provided by the An-
+%droid library. This means that library or user-defined views are not explicitly
+%created by new statements but rather inflated through \textit{reflection}. Library meth-
+%ods such as \CodeIn{findViewById} access the inflated views.
+
+\begin{itemize}
+
+\item \textbf{Call graph entry nodes: }in an Android application,
+an \CodeIn{Activity} object is created and manipulated by the UI thread. Thus, we treat
+all public methods defined in the \CodeIn{Activity} class 
+and any overriding definitions in its subclasses as call graph entry nodes.
+We also add all overridden Android GUI event handling methods in user
+code as entry nodes, since they are also called back from the UI thread.
+
+\smallstep
+
+\item \textbf{UI-accessing nodes: }the \CodeIn{ViewRoot.checkThread} method.
+Like SWT, Android explicitly checks whether
+the current thread is a UI thread or not before accessing a GUI object via
+the \CodeIn{ViewRoot.checkThread} method.
+
+\smallstep
+
+\item \textbf{Safe UI methods: } \CodeIn{View.post}
+and \CodeIn{View.postDelay} that execute code on the UI thread. 
+%Invoking them on any thread will not cause an invalid thread access error.
+%Invoking these two methods are generally considered to be safe, and would not
+%cause an invalid thread access error.
+
+\end{itemize}
+
+Instantiating our general technique to  a specific framework
+requires moderate human effort. We wrote around 500 lines of Java code in total to achieve
+the above four instantiations.
+
+\subsection{Implementation Details}
+
+%Our current implementation supports four widely-used GUI frameworks:
+%SWT, Eclipse plugin development, Swing, and Android.
 We implemented the reflection-aware call graph construction
@@
 Unlike similar tools~\cite{Payet:2011:SAA:2032266.2032299}, our tool
-does not require a separated
-pass of program instrumentation; instead, it
+does not require a separate
+pass for program instrumentation; instead, it
 parses the configuration file in an Android application,
@@
 decrypt the apk file, and then uses the 
-ded translator~\cite{Enck:2011:SAA:2028067.2028088} to convert
+ded translator~\cite{ded} to convert
 Dalvik bytecode to Java bytecode before feeding to WALA.  The Android system
 library (i.e., \CodeIn{android.jar}) uses many ``stub'' classes as
-placeholders for the sake of efficiency. We manually re-compiled the whole
-\CodeIn{android.jar} from its source code and replaced all ``stub'' classes
-with real class files.
-
-%Static Single Assignment (SSA) transformation to get limited flow sensitivity
+placeholders for the sake of efficiency. We manually re-compiled 
+\CodeIn{android.jar} from its source code, so it contains real
+class files rather than stubs.

### 2012-02-07 GUIErrorDetector/src/edu/washington/cs/detector/CGBuilder.java
improve the naming

@@ -157,7 +157,7 @@ public class CGBuilder {
 			System.out.println("Use CFA with precision: " + this.cfaprecision);
 			builder = WALAUtils.makeCFABuilder(this.cfaprecision, options,  cache, cha, scope);
 		} else if (this.type == CG.TempZeroCFA) {
-			System.out.println("Use Fake-0-CFA with precision: " + this.cfaprecision);
+			System.out.println("Use Temp-0-CFA with 0 context precision ");
 			builder = WALAUtils.makeCFABuilder(0, options, cache, cha, scope);
 		}else {
 			throw new RuntimeException("The CG type: " + type + " is unknonw");

### 2012-02-07 trunk/GUIErrorDetector/tests/edu/washington/cs/detector/experiments/straightforward/TestSwtNaive.java
Running requiring wrappers for ArecaBackup

@@ -61,4 +61,39 @@ public class TestSwtNaive extends TestCase {
 		Utils.dumpCollection(unsafe, "./logs/filebunkernaive.txt");
 	}
 	
+	public void testArecaBackup() throws IOException {
+		String dir = "D:\\research\\guierror\\subjects\\swt-subjects\\areca-latest\\";
+		
+	    String appPath = dir + "areca-latest.jar";
+	    
+		String libJar = dir + "activation.jar"
+		    + Globals.pathSep + dir + "commons-net-1.4.1.jar"
+		    + Globals.pathSep + dir +  "jakarta-oro-2.0.8.jar"
+		    + Globals.pathSep + dir + "jsch.jar"
+		    + Globals.pathSep + dir +  "local_policy.jar"
+		    + Globals.pathSep + dir +  "mail.jar"
+		    + Globals.pathSep + dir +  "org.eclipse.core.commands_3.2.0.I20060605-1400.jar"
+		    + Globals.pathSep + dir +  "org.eclipse.equinox.common_3.2.0.v20060603.jar"
+		    + Globals.pathSep + dir +  "org.eclipse.jface_3.2.0.I20060605-1400.jar"
+	        + Globals.pathSep + "D:\\develop-tools\\eclipse\\eclipse\\plugins\\org.eclipse.swt.win32.win32.x86_64_3.6.2.v3659c.jar";
+
+		String path = appPath + Globals.pathSep + libJar;
+		
+		// configure the call graph builder, use 1-CFA as default
+		CGBuilder builder = new CGBuilder(path);
+		builder.setCGType(CG.RTA);
+		builder.buildCG();
+		
+        String[] packages = new String[]{"com.application.areca", "com.jcraft.jsch", "com.myJava"};
+		
+		//check the straightforward approach result
+		UnsafeUIAccessMethodFinder finder = new UnsafeUIAccessMethodFinder(builder.getAppCallGraph(), packages);
+		finder.setClassHierarchy(builder.getClassHierarchy());
+		finder.setUIAccessDecider(GUI.SWT);
+		Collection<IMethod> unsafe = finder.finalAllUnsafeUIAccessMethods();
+		
+		System.out.println("No of unsafe: " + unsafe.size());
+		Utils.dumpCollection(unsafe, "./logs/arecabackupnaive.txt");
+	}
+	
 }

### 2012-02-07 GUIErrorDetector/paper/evaluation.tex
update the experimental data

@@
 
-Our experiment objective is three-fold: to demonstrate the effectiveness
+Our experimental objective is three-fold: to demonstrate the effectiveness
 of our approach in detecting real errors in multithreaded GUI applications, to 
@@
 with existing ones, and to evaluate the usefulness of the proposed 
- heuristics.
+error filters.
 
@@
 evaluate various graph search strategies in error detection (Section~\ref{sec:search}).
- Finally, we show that the set of proposed heuristics are effective
-in removing redundant warnings and eliminate false positives (Section~\ref{sec:filters}).
+ Finally, we show that the proposed filters are effective
+in removing redundant warnings and eliminating
+false positives (Section~\ref{sec:filters}).
 
@@
 an open library. Second, the subject must use multithreading in its implementation.
-Third, the subject must undergone at least two years of active development,
+Third, the subject must have undergone at least two years of active development,
 and is listed in the first 3 result pages based on popularity. This permits us
-to exclude many immature subjects that may contain obvious errors.
+to exclude immature subjects that may contain obvious errors.
 
-We randomly chose subjects belonging to various categories from subjects satisfying
+We chose subjects belonging to various categories from those subjects satisfying
 the above criteria. The subjects used in our experiment are shown in Table~\ref{table:subjects},
@@
 VirgoFTP~\cite{virgo} implements a simple FTP client based on Java and SWT UI library.
-FileBunker~\cite{filebunker} is a file backup application which uses one or more GMail accounts as its backup repository.
+FileBunker~\cite{filebunker} is a file backup application which uses one or more GMail
+accounts as its backup repository. ArecaBackup~\cite{areca} offers a personal
+file backup solution for Linux and Windows.
 
@@
 HudsonEclipse~\cite{hudson} monitors Hudson build status from Eclipse.
-EclipseRunner~\cite{eclipserunner} extends capability of running launch configurations in Eclipse IDE.
+EclipseRunner~\cite{eclipserunner} extends Eclipse's capability to run launch configurations.
 
 \Item \textbf{Swing applications.} %S3dropbox~\cite{s3dropbox} and SudokuSolver~\cite{sudokusolver} are two Swing desktop applications.
-S3dropbox~\cite{s3dropbox} implements a client that allows users
-to drag and drop files, which are then uploaded to their Amazon S3 accounts. SudokuSolver~\cite{sudokusolver}
+S3dropbox~\cite{s3dropbox}  allows users
+to drag and drop files to their Amazon S3 accounts. SudokuSolver~\cite{sudokusolver}
 computes Sudoku solutions efficiently using mutlithreading execution.
+
+\smallstep
 
@@
  \hline
+ ArecaBackup (7.2)&   23226 &  444 &  4729 \\
+ \hline
  \hline
@@
 \hline
- Total &  76232 &  650 &  6492\\
+ Total &  99458 &  1094 &  11221 \\
 \hline
@@
 native methods or project-specific GUI interaction patterns were implemented.
-Among all evaluated subjects, SGTPuzzler is the only program that
-uses native methods to interact with
+Only SGTPuzzler uses native methods to interact with
 the underlying operating system. Thus, we manually checked the possible
-Java methods that a native method may call, and then added 7 \CodeIn{@CalledByNativeMethods}
+Java methods that a native method may call, and then added \annotationnum \CodeIn{@CalledByNativeMethods}
 annotations for it. Two subjects MyTracks and Fennec employ a customized pattern
@@
 %message passing. 
-Thus, we add 11 user-defined heuristic filters for these two subjects.
+Thus, we add 11 user-defined filters for these two subjects.
 %to indicate
@@
 authors was familiar with the subjects; but we found it is quite easy
-to add extra annotations and heuristic filters. All these
-manual parts are finished in less than 60 minutes.
+to add extra annotations and user-defined filters. All these
+manual parts took less than a total of 60 minutes.
 
-After provided with necessary annotations and heuristic filters,
-our tool worked in a fully-automatic, push-button manner. For each output
+For each output
 warning, we manually determined its validity by either searching the
@@
 \hspace*{-0.2cm}
-\setlength{\tabcolsep}{.35\tabcolsep}
-\begin{tabular}{|l||c|c|c||c|c|c||c|c|c||c|c|}
+\setlength{\tabcolsep}{.15\tabcolsep}
+\begin{tabular}{|l||c|c|c||c|c|c||c|c|c||c|}
 \hline
- Subject&  \multicolumn{9}{|c||}{Our Technique} & \multicolumn{2}{|c|}{The Approach in}  \\
+ Subject&  \multicolumn{9}{|c||}{Our Technique} & Requiring Wrappers  \\
 \cline{2-10}
- Program  &  \multicolumn{3}{|c|}{RTA }& \multicolumn{3}{|c|}{0-CFA } & \multicolumn{3}{|c||}{1-CFA } & \multicolumn{2}{|c|}{Section~\ref{sec:straightforward}}  \\
-\cline{2-12}
- & CG Size & \#Warning & \#Bug & CG Size & \#Warning & \#Bug & CG Size & \#Warning & \#Bug & \#Warning & \#Bug\\
+ Program  &  \multicolumn{3}{|c||}{RTA }& \multicolumn{3}{|c||}{0-CFA } & \multicolumn{3}{|c||}{1-CFA } & (Section~\ref{sec:straightforward})  \\
+\cline{2-11}
+ & CG Size & \#Warning & \#Bug & CG Size & \#Warning & \#Bug & CG Size & \#Warning & \#Bug & \#Warning \\
 \hline \hline
-\multicolumn{12}{|l|}{SWT desktop applications}   \\
+\multicolumn{11}{|l|}{SWT desktop applications}   \\
  \hline
- VirgoFTP&  12401 &  2 &  2 & 10858 & 2 & 2 & 43598 & 2 & 2& 149 & 2 \\
+ VirgoFTP&  12401 &  2 &  2 & 10858 & 2 & 2 & 43598 & 2 & 2& 149  \\
  \hline
- FileBunker &  18951 &  1 &  0 & 15743 & 0 & 0 & 76088 & 2 & 1& 693 & 1 \\
+ FileBunker &  18951 &  1 &  0 & 15743 & 0 & 0 & 76088 & 2 & 1& 693  \\
+ \hline
+ ArecaBackup&  20882 &  1  &  0 & 19697 & 1 & 1  & 116398 & 1 & 1 & 3021\\
  \hline
  \hline
-\multicolumn{12}{|l|}{Eclipse plugins}   \\
+\multicolumn{11}{|l|}{Eclipse plugins}   \\
  \hline
- EclipseRunner&  11248&  6 &  1 & 7201 & 6 & 1 & 26911 & 6 & 1& 202 & 1 \\
+ EclipseRunner&  11248&  6 &  1 & 7201 & 6 & 1 & 26911 & 6 & 1& 202  \\
  %\hline
@@
  \hline
- HudsonEclipse& 18473 &  2 &  1 & 15814 & 2 & 1& 56645 & 3 & 1 & 182 & 1 \\
+ HudsonEclipse& 18473 &  2 &  1 & 15814 & 2 & 1& 56645 & 3 & 1 & 182 \\
  \hline
  \hline
-\multicolumn{12}{|l|}{Swing desktop applications}   \\
+\multicolumn{11}{|l|}{Swing desktop applications}   \\
  \hline
- S3dropbox & 37751 &  0 &  0 & 30609 & 0 & 0 & 115324 & 1 & 1 & 210 & 1 \\
+ S3dropbox & 37751 &  0 &  0 & 30609 & 0 & 0 & 115324 & 1 & 1 & 210  \\
  \hline
-  SudokuSolver&  27730&  3 &  2 & 20907 & 3 & 2 & 39299 & 2 & 2 & 356 & 2 \\
+  SudokuSolver&  27730&  3 &  2 & 20907 & 3 & 2 & 39299 & 2 & 2 & 356  \\
  \hline
  \hline
-\multicolumn{12}{|l|}{Android mobile applications}   \\
+\multicolumn{11}{|l|}{Android mobile applications}   \\
  \hline
- SGTPuzzler & 13631 / 13865&  12 / 16 &  0 / 0 & 9546 / 9682& 4 / 4& 1 / 1 & 35198 / 35756 & 1 / 1  & 1 / 1& 104 & 1 \\
+ SGTPuzzler & 13631 / 13865&  12 / 16 &  0 / 0 & 9546 / 9682& 4 / 4& 1 / 1 & 35198 / 35756 & 1 / 1  & 1 / 1& 104 \\
  \hline
- Fennec & 14058 / 14387 &  1 / 1 &  0 / 0 & 8263 / 8898 & 1 / 1 & 0 / 0& 29125/ 31759 & 3 / 3 & 1 / 1& 433 & 1 \\
+ Fennec & 14058 / 14387 &  1 / 1 &  0 / 0 & 8263 / 8898 & 1 / 1 & 0 / 0& 29125/ 31759 & 3 / 3 & 1 / 1& 433 \\
  \hline
- MyTracks & 24036 / 24036 &  161 / 220 & 0 / 0 & 10803 / 13645 & 119 / 119 & 0 / 0 & 39235 / 110977 & 1 / 1 & 0 / 1 & 1192 & 1 \\
+ MyTracks & 24036 / 24036 &  161 / 220 & 0 / 0 & 10803 / 13645 & 119 / 119 & 0 / 0 & 39235 / 110977 & 1 / 1 & 0 / 1 & 1192 \\
 \hline
 \hline
- Total & 178279 / 178842 &  188 / 251 & 6 / 6 & 129744 / 133357 & 137 / 137& 7 / 7 & 461423 / 536358& 21 / 21 & 10 / 11 & 3521 & 11 \\
+ Total & 199161 / 199724 &  189 / 252 & 7 / 7 & 149441 / 153054& 138 / 138& 8 / 8 & 577821 / 652756& 22 / 22 & 11 / 12 & 6542\\
 \hline
@@
 using normal call graph construction algorithm and the reflection-aware
-call graph construction algorithm. The 6 errors found in VirgoFTP, FileBunker,
+call graph construction algorithm. The \newbugs errors found in VirgoFTP, FileBunker, ArecaBackup
 S3dropbox, and SudokuSolver are previously  unknown. As a comparison, the
@@
 
-Table~\ref{table:results} tabulates the results of running our
-tool with three different call graph construction algorithms
-on the subject programs. From these results, we can see our
-tool found real errors from each subject on  four
-supported GUI frameworks. The results vary slightly according
-to the call graph algorithm used. In general, using
-the 1-CFA algorithm found most errors (11 in total) and least
-false positive warnings (10 in total). A comparison of using other call graph
-construction algorithms will be explained in Section~\ref{sec:reflectionaware}.
+Table~\ref{table:results} tabulates the experimental results.
+Our tool found real errors in each subject programs.
 
-We further examined the detailed results for each subject.
-Among the 21 warnings issued by using the 1-CFA algorithm, 11
-warnings reveals 11 distinct errors (6 are previously-unknown),
-2 warnings are false positive, and the remaining 8 warnings
-are redundant.
+%of running our
+%tool with three different call graph construction algorithms
+%on the subject programs. From these results, we can see our
+%tool found real errors from each subject on  four
+%supported GUI frameworks. The results vary slightly according
+%to the call graph algorithm used. In general, using
+%the 1-CFA algorithm found most errors (\bugs in total) and least
+%false positive warnings (\falses in total).
 
-%The primary
-%reason for the false positive is because the precision of call graph,
-%while the reason for redundant warnings is because multiple
-%methods ca
-%Even a context-sensitive call graph construction algorithm is used,
+%We further examined the detailed results for each subject.
+Among the \warnings warnings issued when using the 1-CFA call graph algorithm, \bugs
+warnings reveal \bugs distinct errors (\newbugs are previously unknown),
+2 warnings are false positives, and the remaining 8 warnings
+are redundant. Section~\ref{sec:reflectionaware} compares with other call graph
+construction algorithms.
 
-%why finds a bug in SGTPuzzle, because the \CodeIn{SmallKeyBoard} has been
-%explicitly created in this main class \CodeIn{SGTPuzzles} \CodeIn{setKeyboardVisibility},
-%thus, even without reflection-aware
+We have submitted all of the newly-found errors
+to the developers. As of Feb 2012, 1 error in S3dropbox has been confirmed.
+4 errors can be reproduced and validated in our own experimental environment, and
+1 error from FileBunker was submitted but has not been verified
+by its developers yet.
 
@@
 shows an invalid thread access error our tool found in the S3dropbox
-program. This error only happens when the \CodeIn{deterCurrentBucket}
-method at line 63 throws an exception, and can be hard to
-detect by testing, since the test must  execute that specific exception-handling
-path. We reported this error to the S3dropbox developers. Tom Czarniecki,
-a key developer of S3dropbox confirmed this potential single-GUI-thread
-violation. He mentioned that the S3dropbox project had already
-used certain design patterns and practice to avoid such violations (e.g.,
+program. This error only happens when the \CodeIn{deleteCurrentBucket}
+call on line 63 throws an exception, making it hard to
+detect by testing. We reported this error to the S3dropbox developers. Tom Czarniecki,
+a key developer of S3dropbox, confirmed this single-GUI-thread
+violation. He mentioned that the S3dropbox project uses
+certain design patterns to avoid such violations (e.g.,
 actions for UI interaction are encapsulated into a \CodeIn{Worker} interface),
-but they still overlooked  the reported code snippet.
+but they still overlooked  the error our tool found.
 
-Another reason of missing this violation is because some GUI frameworks like Swing
-do not provide any run-time checks for invalid thread accesses. Most
-of the time, programmers can get away with an apparently ``well behaved'' Swing
-GUI that actually breaks the single-GUI-thread rule. However, As clearly
-indicated in the official documentation, Swing is a single-GUI-threaded GUI
-toolkit, and is not thread-safe. All Swing code must be executed in the UI-thread and
-invoking Swing code from multiple threads risks thread interference
-or memory-consistency errors, particularly in the multi-core era.
+Another reason they overlooked this violation is because some GUI frameworks like Swing
+do not provide any run-time checks for invalid thread accesses. Swing
+GUI might not exhibit user-visible faults on many erreoneous executions.
+However, as clearly stated in the official documentation~\cite{swing}, Swing is a single-GUI-threaded GUI
+toolkit and invoking Swing code from multiple threads risks thread interference
+or memory-consistency errors.
 
@@
 invalid thread access errors is to wrap every GUI accessing operation
-with message passing (i.e., via the safe UI methods). Thus, a
-straightforward way to detect potential invalid error
-is to check every method in the user code to determine whether all GUI-accessing operation
-is probably wrapped. If not, this approach issues a warning.% for every violation. 
-%If not, this approach issues warnings.
+with message passing (i.e., via the safe UI methods). Although
+this approach can give rise to other types of errors, a
+straightforward way to detect potential invalid thread access errors
+is to issue a warning whenever a GUI-accessing operation
+is not wrapped.
 
-We implemented this straightforward approach and experimentally compared it
-with our technique.% presented in Section~\ref{sec:technique}.
-The far right column in Table~\ref{table:results} shows the results.
-The results show that this straightforward approach could identify every
-error that our technique found, but issue a huge number of warnings.
+As shown in the far right column of ``Requiring Wrappers'' in
+Table~\ref{table:results}, Requiring Wrappers could identify every
+error that our technique found, but it issues a huge number of warnings,
+most of which are probably false positives.
 The primary reason is that this simple approach
-does not globally reason about calling relationship between
-threads, UI-accessing methods, and safe UI methods, thus it often incorrectly
+does not globally reason about the calling relationship between
+threads, UI-accessing methods, and safe UI methods, and thus it often incorrectly
 classifies GUI accessing operations which will never be executed
@@
 used in our experiments. As shown in Table~\ref{table:results},  1-CFA found
-more errors with less false positive warnings than the other two algorithms. This
+more errors with fewer false positive warnings than the other two algorithms. This
 is because RTA and 0-CFA do not consider the calling context when
@@
 mix the same method calls by different callers into a single node, thus
-introduce imprecision.
+introducing imprecision.
 
@@
 
-For other two Android applications (Fennec and SGTPuzzler), the errors
-can be found by using a standard call graph construction algorithm. This
-is because the error-related GUI objects are created explicitly, so that
-the standard call graph construction algorithm is sufficient.
+Errors in the other two Android applications (Fennec and SGTPuzzler)
+can be found by using a standard call graph construction algorithm.
+This is because the error-related GUI objects are created explicitly,
+so the standard call graph construction algorithm is sufficient.
 
@@
 
-The first variant uses DFS for graph traverse by changing
-line 7 in Figure~\ref{fig:detectalgorithm} to:
+The first variant uses DFS for graph traversal by changing
+line 8 in Figure~\ref{fig:detectalgorithm} to:
 $\mathit{worklist}$ $\leftarrow$ $\mathit{an}$ $\mathit{empty}$ $\mathit{stack}$,
-and changing queue operations (\CodeIn{dequeue}, and \CodeIn{enqueueAll} on lines 11, and
-22 in Figure~\ref{fig:androiderror}, respectively)
-to the corresponding statck operations (\CodeIn{pop}, and \CodeIn{pushAll}).
-As a result, this variant found 8 errors in total and missed 1 error in the FileBunker subject.
+and changing queue operations (\CodeIn{enqueueAll}, and \CodeIn{dequeue}
+on lines 9, 12, and
+23 in Figure~\ref{fig:androiderror}, respectively)
+to the corresponding statck operations (\CodeIn{pushAll}, and \CodeIn{pop}).
+This variant found 10 errors in total and missed 1 error in the FileBunker subject.
 The reason is that DFS tends to search deeper into the graph, and the path it returns
-may not be the shortest one and are more likely to be an infeasible path in practice.
-For the FileBunker subject, paths
-returned by DFS are much longer than BFS, and do not actually exist.
+may not be the shortest one and is more likely to be an infeasible path in practice.
+%For the FileBunker subject, paths
+%returned by DFS are much longer than BFS, and do not actually exist.
 
@@
 to each UI-accessing node, and then checks whether each
-path spawns a new thread and accesses GUI object without using safe UI methods. As
-a result, this variant run out of memory on all subjects. We checked
+path spawns a new thread and accesses GUI objects without using safe UI methods.
+This variant ran out of memory on all subjects. We checked
 the output paths before the algorithm terminated, and found none of the explored
 path revealed a real error. This is because the number of
-non-cyclic paths in a graph is exponentially large to the graph node number.
+non-cyclic paths in a graph is exponential in the graph node number.
 For a realistic call graph which often contains thousands of nodes,
-it is impossible to enumerate all paths in practice.
+it is infeasible to enumerate all paths.
+%only a very few amount of paths can be enumerated within a practical amount of time.
 
@@
 
-\subsubsection{Evaluating Heuristic Filters}
+\subsubsection{Evaluating Error Filters}
 \label{sec:filters}
 
-We measure the effectiveness of the proposed heuristic filters of
-Section~\ref{sec:heuristic} in terms of the number of removed false positives and
-redundant warnings.
-
-Table~\ref{table:filters} tabulates the results.
-Our static analysis output thousands of warnings for the evaluated
-subjects, but the proposed heuristic filters effectively reduced
-the number of likely invalid warnings. On average, five heuristic
-filters removed 99.96\% of the reported warnings as false positives
-or redundant warnings. Specifically, heuristic filters 1 and 2 identified
-29.38\% of the warnings as likely false positives, and filters 3, 4,
-and 5 identified 70.58\% of the warnings as redundant warnings.
-Remarkably, the 3rd heuristic filter for removing lexically redundant
-reports is the most effective one on the evaluated subjects: it removes 37019 redundant warnings.
-
-%We further manually check each filtered warning, and found no
-%real errors have been removed.
+Table~\ref{table:filters} measures the effectiveness of the proposed 
+error filters of Section~\ref{sec:heuristic}.
+The five error filters removed 99.96\% of the reported warnings as false positives
+or redundant warnings. Specifically, two sound filters 1 and 2 identified
+removed 36.52\% of the warnings, and three heuristic filters 3, 4, and 5
+removed 63.44\% of the warnings. Among them, the 1st filter for removing
+lexically redundant reports is the most effective one.
 
@@
 \hline
- Subject & Before & \#W & \#W & \#W & \#W& \#W \\
- Program & Filtering & $F_1$ & $F_{1,2}$ & $F_{1,2,3}$&$F_{1,2,3,4}$ & $F_{1,2,3,4,5}$\\
+ & \multicolumn{6}{|c|}{Number of Warnings}  \\
+\cline{2-7}
+ Subject & Before & \multicolumn{2}{|c|}{Sound Filters}  &  \multicolumn{3}{|c|}{Heuristic Filters}  \\
+\cline{3-7}
+ Program &Filtering  & $F_1$ & $F_{1,2}$ & $F_{1,2,3}$&$F_{1,2,3,4}$ & $F_{1,2,3,4,5}$\\
 \hline \hline
@@
  \hline
- VirgoFTP &  21 &  21 &  3 & 3 &  2 & 2\\
+ VirgoFTP &  21 &  21 &  21 & 7 &  2 & 2\\
  \hline
- FileBunker &  4494 &  3210 &  3210 &  642 &  2 & 2\\
+ FileBunker &  4494 &  4494 &  3210 &  3210 &  10  & 2\\
+ \hline
+ ArecaBackup &  6219 &  438 & 438 &  438  &  1 & 1\\
  \hline
@@
  \hline
- EclipseRunner&  1621 &  1487 &  1487 & 1487 &  6 & 6\\
+ EclipseRunner&  1644 &  1644 &  1644 & 1644 &  6 & 6\\
  \hline
- HundsonEclipse&  3192 &  2417 &  2417 & 9 &  3 & 3\\
+ HundsonEclipse&  1367 &  567 &  567 & 567 &  3 & 3\\
  \hline
@@
  \hline
- S3dropbox&  45528 &  31978 &  31978 & 9 &  1 & 1\\
+ S3dropbox&  45528 &  31978 &  31978 & 30975 &  9 & 1\\
  \hline
- SudokuSolver &  58 &  58 &  58 & 2 &  2 & 2\\
+ SudokuSolver &  58 &  58 &  58 & 58  &  2 & 2\\
  \hline
@@
  \hline
- Fennec &  122 &  122 & 84 & 84 &  9 & 3\\
+ Fennec &  122 &  84 & 84 & 84 &  9 & 3\\
  \hline
- MyTracks &  1176 &  1176 &  441 & 441 &  63 & 1 \\
+ MyTracks &  1176 &  1176 &  483 & 441 &  69 & 1 \\
 \hline
  \hline
- Total &  56214 &  40470 &  39697 &  2678 &  89 & 21 \\
+ Total &  60631 &  40461 &  38484 &  37425 &  112 & 22 \\
  \hline
@@
 \Caption{{\label{table:filters}Number of warnings after applying a set of
-heuristic filters. Column ``Before Filtering''
-shows the output warning number by the reflection-aware 1-CFA algorithm.
-Results of using other algorithms show similar patterns, which are omitted for brevity.
-Column ``\#W $F_{i,...,j}$'' represents the number of remaining warnings after applying
+sound and heuristic filters. Column ``Before Filtering''
+shows the number of warnings by the reflection-aware 1-CFA algorithm.
+Other algorithms show similar patterns, which are omitted for brevity.
+Column ``$F_{i,...,j}$'' represents the number of remaining warnings after applying
 the $i$th to $j$th filters as defined in Section~\ref{sec:heuristic}.
-Numbers in last column are taken from the subcolumn ``\#Warnings"
+The numbers in the last column are the same as the subcolumn ``\#Warnings"
 under column ``1-CFA'' in Table~\ref{table:results}.

### 2012-02-07 trunk/GUIErrorDetector/paper/related.tex
update the experimental data

@@
 report false positives and redundant warnings due to its conservative nature.
-Nevertheless, as we demonstrated in our experiments, using a few simple heuristics
-can dramatically reduce the number of false positives and redundant warnings to
+Nevertheless, as we demonstrated in our experiments, using a few simple error
+filters can dramatically reduce the number of false positives and redundant warnings to
 an acceptable level.
@@
 we are not aware of any software model checking approach can scale to the subjects
-as large as those used in our experiments (including the library code). Compared with model checking, the static analysis
-algorithm presented in this paper chooses call graph as the
-abstraction level with a set of heuristics, and thus achieves good
-scalability with reasonable precision. It is specifically designed to find invalid thread
-access errors instead of being a general property checking tool.
+as large as those used in our experiments (including the library code).
+The technique presented in this paper is specifically designed to find invalid thread
+errors instead of being a general property checking tool. 
+It chooses call graph as a coarse-grained program representation with a
+set of error filters, achieving good scalability with reasonable accuracy.
 
@@
 as well as virtual method calls in C++ and Java ~\cite{rta, kcfa,
-xta, inccg, Sundaresan:2000, Might:2010}.
+xta, inccg, Sundaresan:2000}.
 We briefly mention some of the highlights of call graph construction
@@
 As reflected in our experiments, using standard call graph algorithms
-such as RTA, 0-CFA, and 1-CFA fails to find UI-specific errors in
-Android applications, due to the incompleteness of the resulting graph.
+fails to find errors in some
+Android applications. %, due to the incompleteness of the resulting graph.
 

### 2012-02-07 trunk/GUIErrorDetector/paper/evaluation.tex
check the number to make it consistent

@@
 with existing ones, and to evaluate the usefulness of the proposed 
- filters.
-
-\textbf{This part needs to re-write, talk sound/heuristic filters separately}
+error filters.
 
@@
  Finally, we show that the proposed filters are effective
-in removing redundant warnings and eliminating
-false positives (Section~\ref{sec:filters}).
+in removing warnings (Section~\ref{sec:filters}).
 
@@
 VirgoFTP~\cite{virgo} implements a simple FTP client based on Java and SWT UI library.
-FileBunker~\cite{filebunker} is a file backup application which uses one or more GMail accounts as its backup repository.
+FileBunker~\cite{filebunker} is a file backup application which uses one or more GMail
+accounts as its backup repository. ArecaBackup~\cite{areca} offers a local
+file backup solution for Linux and Windows.
 
@@
 computes Sudoku solutions efficiently using mutlithreading execution.
+
+\smallstep
 
@@
 %message passing. 
-Thus, we add 11 user-defined filters for these two subjects.
+Thus, we add \filternum user-defined filters for these two subjects.
 %to indicate
@@
 \cline{2-10}
- Program  &  \multicolumn{3}{|c|}{RTA }& \multicolumn{3}{|c|}{0-CFA } & \multicolumn{3}{|c||}{1-CFA } & (Section~\ref{sec:straightforward})  \\
+ Program  &  \multicolumn{3}{|c||}{RTA }& \multicolumn{3}{|c||}{0-CFA } & \multicolumn{3}{|c||}{1-CFA } & (Section~\ref{sec:straightforward})  \\
 \cline{2-11}
@@
  FileBunker &  18951 &  1 &  0 & 15743 & 0 & 0 & 76088 & 2 & 1& 693  \\
+ \hline
+ ArecaBackup&  20882 &  1  &  0 & 19697 & 1 & 1  & 116398 & 1 & 1 & 3021\\
  \hline
@@
 \hline
- Total & 178279 / 178842 &  188 / 251 & 6 / 6 & 129744 / 133357 & 137 / 137& 7 / 7 & 461423 / 536358& 21 / 21 & 10 / 11 & 3521 \\
+ Total & 199161 / 199724 &  189 / 252 & 7 / 7 & 149441 / 153054& 138 / 138& 8 / 8 & 577821 / 652756& 22 / 22 & 11 / 12 & 6542\\
 \hline
@@
 using normal call graph construction algorithm and the reflection-aware
-call graph construction algorithm. The \bugs errors found in VirgoFTP, FileBunker,
+call graph construction algorithm. The \newbugs errors found in VirgoFTP, FileBunker, ArecaBackup
 S3dropbox, and SudokuSolver are previously  unknown. As a comparison, the
-results of a straightforward approach (Section~\ref{sec:straightforward}) are shown at the far right.} }
+results of a straightforward approach, called ``Requiring Wrappers'' (Section~\ref{sec:straightforward}),
+are shown at the far right.} }
 \end{table*}
@@
 
-Table~\ref{table:results} tabulates the experimental results.
-Our tool found real errors in each subject programs.
-
-%of running our
-%tool with three different call graph construction algorithms
-%on the subject programs. From these results, we can see our
-%tool found real errors from each subject on  four
-%supported GUI frameworks. The results vary slightly according
-%to the call graph algorithm used. In general, using
-%the 1-CFA algorithm found most errors (\bugs in total) and least
-%false positive warnings (\falses in total).
-
-%We further examined the detailed results for each subject.
-Among the \warnings warnings issued when using the 1-CFA call graph algorithm, \bugs
-warnings reveal \bugs distinct errors (\newbugs are previously unknown),
+As shown Table~\ref{table:results},  our tool found
+real errors in each subject program. Using the 1-CFA
+call graph algorithm, our tool issued 22 warnings, among
+which \bugs warnings reveal \bugs distinct errors (\newbugs are previously unknown),
 2 warnings are false positives, and the remaining 8 warnings
@@
 
-We have submitted all of the newly-found errors
-to the developers. As of Feb 2012, 1 error in S3dropbox has been confirmed.
-4 errors can be reproduced and validated in our own experimental environment, and
-1 error from FileBunker was submitted but has not been verified
-by its developers yet.
+We have submitted all \newbugs new errors
+to the subject developers. As of Feb 2012, 1 error in S3dropbox has been confirmed,
+4 errors have been reproduced and validated in our own experimental environment, and
+2 errors in FileBunker and ArecaBackup had not been verified by developers yet.
 
@@
 but they still overlooked  the error our tool found.
-
 Another reason they overlooked this violation is because some GUI frameworks like Swing
@@
 GUI might not exhibit user-visible faults on many erreoneous executions.
-However, as clearly stated in the official documentation~\cite{swing}, Swing is a single-GUI-threaded GUI
-toolkit and invoking Swing code from multiple threads risks thread interference
+However, as clearly stated in the official documentation~\cite{swing}, %Swing is a single-GUI-threaded GUI toolkit and
+accessing Swing GUI objects from non-UI threads risks thread interference
 or memory-consistency errors.
@@
 Besides the above two examples, other errors our tool reported were also
-subtle to find. Take the two newly-found errors in SudokuSolver
-as an example. One error happens when
-the given Sudoku is unsolvable; and the other one happens
-when the program fails to launch the mail composing window of the
-user default mail client (after clicking "eMail Me" button).
+subtle to find. For example, our tool found two new errors in SudokuSolver.
+One error only happens when
+the given sudoku is unsolvable; and the other one happens
+when the JVM fails to launch the mail composing window of the
+user default mail client (after a user clicks "eMail Me" button).
 
@@
 to the corresponding statck operations (\CodeIn{pushAll}, and \CodeIn{pop}).
-This variant found 10 errors in total and missed 1 error in the FileBunker subject.
+This variant found 11 errors in total and missed 1 error in the FileBunker subject.
 The reason is that DFS tends to search deeper into the graph, and the path it returns
@@
 Table~\ref{table:filters} measures the effectiveness of the proposed 
-error filters of Section~\ref{sec:heuristic}
-
+error filters of Section~\ref{sec:heuristic}.
 The five error filters removed 99.96\% of the reported warnings as false positives
-or redundant warnings. Specifically, heuristic filters 1 and 2 identified
-29.38\% of the warnings as likely false positives, and filters 3, 4,
-and 5 identified 70.58\% of the warnings as redundant warnings.
-The 3rd filter for removing lexically redundant
-reports is the most effective one.
-% on the evaluated subjects: it removes 37019 redundant warnings.
-
-%We further manually check each filtered warning, and found no
-%real errors have been removed.
+or redundant warnings. Specifically, two sound filters 1 and 2 
+removed 34.44\% of the warnings, and three heuristic filters 3, 4, and 5
+removed 65.52\% of the warnings. Among them, the 4th filter for removing
+reports with the same head methods from the entry node to \CodeIn{Thread.start()}
+is the most effective one.
 
@@
  \hline
- VirgoFTP &  21 &  21 &  3 & 3 &  2 & 2\\
+ VirgoFTP &  21 &  21 &  21 & 7 &  2 & 2\\
  \hline
- FileBunker &  4494 &  3210 &  3210 &  642 &  2 & 2\\
+ FileBunker &  4494 &  4494 &  4494 &  3210 &  10  & 2\\
+ \hline
+ ArecaBackup &  6219 &  438 & 438 &  438  &  1 & 1\\
  \hline
@@
  \hline
- Fennec &  122 &  122 & 84 & 84 &  9 & 3\\
+ Fennec &  122 &  84 & 80 & 80 &  9 & 3\\
  \hline
- MyTracks &  1176 &  1176 &  441 & 441 &  63 & 1 \\
+ MyTracks &  1176 &  1176 &  483 & 441 &  69 & 1 \\
 \hline
  \hline
- Total &  56214 &  40470 &  39697 &  2678 &  89 & 21 \\
+ Total &  60631 &  40461 &  39764 &  37421 &  112 & 22 \\
  \hline
@@
 In our evaluation, the studied subjects were selected with a bias towards popularity from
-three open-source repositories. Another threat is that we only employed three
-well-known call graph construction algorithms (i.e., RTA, 0-CFA, and 1-CFA) 
+well-known open-source repositories. Another threat is that we only employed three
+widely-used call graph construction algorithms (i.e., RTA, 0-CFA, and 1-CFA) 
 in our evaluation. It is still unknown whether using other 

### 2012-02-07 trunk/GUIErrorDetector/paper/technique.tex
update the experimental data
check the number to make it consistent

@@
 the single main method, UI-accessing nodes include methods
-\CodeIn{Display.checkWidget} and \CodeIn{Display.checkDevice},
+\CodeIn{Widget.checkWidget} and \CodeIn{Display.checkDevice},
 and safe UI methods include two SWT helper methods \CodeIn{Display.asyncExec}  and
@@
 \textbf{2. Filter Reports With User-Annotated Methods}. Besides general
-library calls, users are also permitted to explicitly annotate methods
+library calls, users are also permitted to explicitly annotate project-specific methods
 that will never trigger an error.
-For example, the Android GUI framework provides a utility method 
-\CodeIn{runOnUIThread} to check whether the current thread is the UI thread
-before executing the code. If the current thread is not the UI thread,
-this method will be executed on the UI thread via message passing.
-Thus, a reported method call chain containing an annotated 
-can be safely removed. We produced the list of annotated methods
-during analyzing programs on different GUI frameworks; we did this
-only between experiments rather than biasing experiments by tuning
-our tool to specific programs.
+%For example, the Android GUI framework provides a utility method 
+%\CodeIn{runOnUIThread} to check whether the current thread is the UI thread
+%before executing the code. If the current thread is not the UI thread,
+%this method will be executed on the UI thread via message passing.
+%Thus,
+A reported method call chain containing an annotated 
+can be safely removed. In our experiments, we produced a list of \filternum
+annotated methods for two subjects because they are using a customized
+pattern to interact with the GUI framework.
+
+%during analyzing programs on different GUI frameworks; we did this
+%only between experiments rather than biasing experiments by tuning
+%our tool to specific programs.
 

### 2012-02-07 GUIErrorDetector/paper/introduction.tex
small revise

@@
 
+\smallstep
+
 \item The single-GUI-thread rule incurs less overhead.
@@
 must bear this cost.
+
+\smallstep
 
@@
 to the same error. To address such limitations, we devise a set
- of heuristics to filter likely false positives and redundant warnings.
+ of error filters to remove likely false positives and redundant warnings.
 
@@
 and scales to realistic programs.
-We evaluated our implementation on 9 programs comprising over 76000 LOC.
+We evaluated our implementation on \subnum programs comprising \totaloc LOC.
 The experiment results demonstrate
-that: our technique is effective (it found 11 real-world errors
-from four supported frameworks and produced only 10 false positive warnings);
+that: our technique is effective (it found \bugs real-world errors
+from four supported frameworks and produced only \falses false positive warnings);
 our reflection-aware call graph construction algorithm helps in
 finding errors in Android applications;
-and our proposed heuristics significantly reduce the number of
+and our proposed filters significantly reduce the number of
 false positives and redundant warnings.
@@
 
+\smallstep
+
 \item \textbf{Technique.} We formulate finding
@@
 call graph construction algorithm. (Section~\ref{sec:technique}).
+
+\smallstep
 
@@
 
-\item \textbf{Evaluation.} We applied our tool to 9 programs 
-from 4 different frameworks, comprising over 76000 LOC. The results
+\smallstep
+
+\item \textbf{Evaluation.} We applied our tool to \subnum programs 
+from 4 different frameworks, comprising \totaloc LOC. The results
 show the usefulness of the proposed technique (Section~\ref{sec:evaluation}).

### 2012-02-07 GUIErrorDetector/paper/technique.tex
small revise

@@
 We first give a high-level formulation of the problem, then present
-the error detection algorithm. Finally, we show how to instantiate
-the error algorithm for different GUI frameworks.
+the error detection algorithm. Finally, we present how to 
+construct a reflection-aware call graph and filter the error reports.
 
@@
 The algorithm uses BFS to search for reachable UI-accessing
-methods (lines 10 -- 24).
+methods (lines 11 -- 25).
 The algorithm stops the traversal if it reaches a UI-accessing
-method (lines 16 -- 18) or a safe UI method (lines 19, 20).
+method (lines 17 -- 19) or a safe UI method (lines 20, 21).
 %Specifically, it uses a queue to keep track of the nodes to be visited (line 7),
@@
 
+\subsection{Call Graph Construction}
+
 Given a sound call graph, our algorithm is sound in that it does not
 miss true positives. We note, however, that computing a sound
-call graph in the presence of reflection is non-trivial. 
+call graph in the presence of reflection and native methods is non-trivial. 
 To alleviate this problem, we next proposed a reflection-aware call graph
-construction algorithm in Section~\ref{sec:cg}.
+construction algorithm in Section~\ref{sec:cg} and annotation support
+for native methods in Section~\ref{sec:annotation}.
 
-\subsubsection{Reflection-aware Call Graph Construction}
+\subsubsection{Reflection}
 \label{sec:cg}
@@
 points to a \textit{non-null} \CodeIn{Button} object due to its limitation in deal with the
-reflection call \CodeIn{findViewById}. As a result, the built 
-call graph will exclude the calling edge corresponding to the
-\CodeIn{setText} method call on line 10.
+reflection call \CodeIn{findViewById}, and exclude the calling edge
+corresponding to the \CodeIn{setText} method call on line 10 in the resulting call graph.
+
+%. As a result, the built 
+%call graph will exclude the calling edge corresponding to the
+%\CodeIn{setText} method call on line 10.
 
@@
 graph construction algorithm helps in detecting errors
-in Android applications (Section~\ref{sec:evaluation}).
+in Android applications (Section~\ref{sec:reflectionaware}).
 
@@
 
-Our static analysis takes the call relationship specified by this
+\noindent Our static analysis takes the call relationship specified by this
 annotation into consideration when traversing the call graph. 
 Adding annotations for native methods is optional and requires manual effort.
-In our experiments, 1 out of 9 programs uses native methods. We manually
+In our experiments, 1 out of \subnum programs uses native methods. We manually
 searched the source files, inspected the code to determine possible target methods
-that may be called by a native method, and added 7 annotations for this program.
+that may be called by a native method, and added \annotationnum annotations for this program.
 We found such an annotation was useful: one error
-can only be reported with using the user-provided annotations.
+is only reported when using the user-provided annotations.
 
-\subsubsection{Heuristic Filtering}
+\subsection{Filtering the Error Reports}
 \label{sec:heuristic}
@@
  that have the same error cause (redundant warnings). We devise
-5 heuristic filters below to remove likely false positives and redundant warnings.
-The first two are for eliminating false positives, while the
-other three are for reducing redundant warnings.
+5 error filters below to remove likely false positives and redundant warnings.
+The first 2 filters are sound in that they will not filter real bugs, and
+other 3 filters are based on heuristics. Orthogonally, filters 2
+and 3 are for eliminating false positives, and filters 1, 4, and 5
+are for reducing redundant warnings.
+
+%1 - subsumed, 2 - user annotated, 3 - sysem call, 4 heand  5,  tail
 
@@
 %\item
-\textbf{1. Filter Reports Containing Library Calls}. A
-method call chain containing certain library calls
-like \CodeIn{Runtime.}\CodeIn{shutDown} are unlikely to
-be buggy. For example, the \CodeIn{Runtime.}\CodeIn{shutDown}
-method is called when JVM terminates, and uses multithreading
-to dispose all GUI objects when the program exits.
-We encoded a list of common library calls by proposing
-a basic set of library calls that seemed natural and
-generally applicable, based on our programming experience.
-We later added other calls we found helpful in analyzing
-programs and that we believed would be generally useful.
-%We encode a list of common library calls, and remove
-%a reported warning if it contains one of them.
-%Method call chain involves typical
-%system methods like \CodeIn{toString} are unlikely to reveal a real bug.
 
-%\item
-\textbf{2. Filter Reports With User-Annotated Methods}. Besides general
-library calls, users are also permitted to explicitly annotate methods
-that will never trigger an error.
-For example, the Android GUI framework provides a utility method 
-\CodeIn{runOnUIThread} to check whether the current thread is the UI thread
-before executing the code. If the current thread is not the UI thread,
-this method will be executed on the UI thread via message passing.
-Thus, a reported method call chain containing an annotated 
-can be safely removed. We produced the list of annotated methods
-during analyzing programs on different GUI frameworks; we did this
-only between experiments rather than biasing experiments by tuning
-our tool to specific programs.
+\subsubsection{Sound Filters}
 
-%\item
-\textbf{3. Filter Lexically Redundant Reports}. One reported method call
+\textbf{1. Filter Lexically Redundant Reports}. One reported method call
 chain can lexically subsume another one. For example, suppose that two
@@
 %\item
+\textbf{2. Filter Reports With User-Annotated Methods}. Besides general
+library calls, users are also permitted to explicitly annotate project-specific methods
+that will never trigger an error.
+%For example, the Android GUI framework provides a utility method 
+%\CodeIn{runOnUIThread} to check whether the current thread is the UI thread
+%before executing the code. If the current thread is not the UI thread,
+%this method will be executed on the UI thread via message passing.
+%Thus,
+A reported method call chain containing an annotated  method
+can be safely removed. In our experiments, we produced a list of \filternum
+annotated methods for two subjects because they are using a customized
+pattern to interact with the GUI framework.
+
+%during analyzing programs on different GUI frameworks; we did this
+%only between experiments rather than biasing experiments by tuning
+%our tool to specific programs.
+
+\subsubsection{Heuristic Filters}
+%\item
+
+\textbf{3. Filter Reports Containing Library Calls}. A
+method call chain containing certain library calls
+like \CodeIn{Runtime.}\CodeIn{shutDown} are unlikely to
+be buggy. For example, the \CodeIn{Runtime.}\CodeIn{shutDown}
+method is called when JVM terminates, and uses multithreading
+to dispose all GUI objects when the program exits.
+We encoded a list of 25 common library calls by proposing
+a basic set of library calls that seemed natural and
+generally applicable, based on our programming experience.
+We later added other calls we found helpful in analyzing
+programs and that we believed would be generally useful.
+
 \textbf{4. Filter Report With the Same Head Methods from the Entry Node to \CodeIn{Thread.start()}}. A method can call
 multiple methods that access GUI objects, such as:
-\vspace{-1mm}
+\vspace{-2mm}
 \begin{CodeOut}
@@
 \end{CodeOut}
-If method \CodeIn{m()} is invoked by a non-UI thread, method call chains
-only different at the last few method nodes may be reported separately, such as:
+\vspace{-2mm}
+If method \CodeIn{m()} is invoked by a non-UI thread, method call chains that
+only differ in the last few method nodes may be reported separately, such as:
 
@@
 
-Among the above 5 filters, filters 2 and 3 are sound
-in that they will not filter real bugs, and other 3 filters
-are based on heuristics. However, as we will show in
-our experiments, these filters work remarkably well in practice (Section~\ref{sec:filters}).
-
-\subsection{Instantiation for Different Frameworks}
-\label{sec:platforms}
-
-We instantiated our error detection technique for four popular GUI frameworks:
-SWT, Eclipse plugin, Swing, and Android.
-The major framework-specific parts, corresponding to
-lines 3 -- 5 in Figure~\ref{fig:detectalgorithm}, are identifying
-\textbf{call graph entry nodes}, \textbf{UI-accessing nodes},
-and \textbf{safe UI methods} for each framework.
-
-%For each framework, we customize the \textit{call graph entry nodes},
-%\textit{UI-accessing nodes}, and \textit{safe UI methods} on lines 3 -- 5 of the
-%algorithm in
-
-%For the sake of efficiency, they are all using the single thread model.
-
-%Why these platforms? popularity? account for xxx\% of the GUI.
-
-%customizing for: entry points, starting points, error checking, thread
-%safe UI methods, what is the event dispatching thread?
-
-\subsubsection{SWT}
-
-%SWT is an open source widget toolkit for Java designed to provide efficient,
-%portable access to the GUI facilities of the operating systems
-%on which it is implemented.
- We instantiated our technique for SWT applications as follows:
-
-%starts from its main method.
-%By default, the thread that the main method executes is the UI thread. Thus, we instantiate
-%our technique as follows:
-
-\begin{itemize}
-
-\item \textbf{Call graph entry nodes: } the main method. Like a normal Java program,
-a SWT desktop application has a single main method as the entry point. By default,
-the main method is executed in the UI thread after the GUI
-is initialized.
-
-\item \textbf{UI-accessing nodes: } the \CodeIn{Display.checkWidget}
-and \CodeIn{Display.} \CodeIn{checkDevice} methods. SWT uses the above
-two methods to explicitly check thread accesses at runtime.
-Any methods for manipulating GUIs object must call (one of) these two methods
- to determine whether the current thread is the UI thread or not.
-%Thus, we treat nodes (in both user code and framework code) corresponding to the methods
-%calling these two methods as UI-accessing nodes.
-%must be invoked
-%in the UI thread and as
-%UI-accessing nodes.
- %methods to check whether the current thread is the UI thread or not. Thus,
-%we treat all such methods that must be accessed in UI thread as the UI-accessing nodes.
-% any
-%methods that calls the checking method must be invoked in the UI thread.
-
-\item \textbf{Safe UI methods: } SWT provides two helper methods (\CodeIn{Display.\\asyncExec}
-and \CodeIn{Display.syncExec}) to execute code (a)synchro-
-nizedly on the UI thread.
- We treat these two methods as safe UI methods, since invoking
-them from any thread 
-%are generally considered to be safe and
-will not cause an invalid thread access error.
-
-\end{itemize}
-
-\subsubsection{Eclipse plugin}
-
-We instantiated our technique for Eclipse plugin as follows:
-
-%Unlike a SWT desktop application, an eclipse plugin, though is developed in SWT,
-%has no single main method. Instead, (XXX) it extends certain extension points
-%exposed by the eclipse framework, and eclipse will XXX. To instantiate our
-%technique for the Eclipse plugin environment, we need to redefine the
-%call graph entry points.
-
-\begin{itemize}
-
-\item \textbf{Call graph entry nodes: } all overridden SWT
-GUI event handling methods in user code. An Eclipse plugin is built
-on top of the SWT framework. However, unlike a SWT desktop application,
-an Eclipse plugin does not have a main method as a single program entry point.
-Instead, it extends extension points provided by the Eclispe framework to
-implement functionalities. When a plugin starts, Eclipse
-calls back the overridden methods to handle the
-upcoming events. All SWT GUI event handling methods (i.e., the overriden
-methods in the class that implements \CodeIn{org.eclipse.swt.internal.SWTEvent-\\Listener}) are
-always called back from the UI thread, thus are used as call graph entry nodes.
-
-\item \textbf{UI-accessing nodes} and \textbf{Safe UI methods} are the same as SWT.
-
-\end{itemize}
-
-\subsubsection{Swing}
-
-A Swing application has a single main method, but contains three kinds of
-threads: \textit{initial thread} that executes initial application code from the main method,
-the \textit{UI thread}, where all GUI manipulation code is executed,
-and the \textit{worker thread} where time-consuming background tasks are executed.
-After a Swing program starts, its initial thread exits and the UI thread takes charge
-of the application and starts to execute all event-handling code or spawns new worker threads. 
-We instantiated our technique for Swing as follows:
-%XXXX Therefore, we can not directly
-%use the main method as the call graph entry point, since it is not invoked
-%by the UI thread. We customize our technique for Swing as follows:
-
-\begin{itemize}
-
-\item \textbf{Call graph entry nodes:} all overridden Swing GUI event handling
-methods in user code. Those event handling methods are always
-called back from the UI thread, thus are used as call graph entry nodes.
-
-\item \textbf{UI-accessing nodes:} %as stated in Swing's documentation,
-all methods defined in each Swing GUI class except for three thread-safe
-methods: \CodeIn{repaint()}, \CodeIn{revalidate()}, and \CodeIn{invalidate()}.
-
-%methods in Swing GUI classes are not thread safe with three exceptions (\CodeIn{repaint()},
-%\CodeIn{revalidate()}, and \CodeIn{invalidate()}). Thus, we
-%treat nodes corresponding to those thread unsafe methods %in each GUI class
-%as UI-accessing nodes.
-
-\item \textbf{Safe UI methods: }  Swing's two helper methods
-(\CodeIn{SwingUtilities.} \CodeIn{invokeLater} and \CodeIn{SwingUtilities.invokeAndWait}) that execute code on the UI thread.
-
-\end{itemize}
-
-\subsubsection{Android}
-
-Android is a Java-based platform for embedded or mobile devices. 
-An Android program does not have a single entry point but can
-rather use parts of other Android applications on-demand and can require their
-services by calling corresponding event handlers, directly or through the
-operating system. In particular, Android applications use \textit{activities}
-as code interacting with the user through a visual interface. GUI event handlers
-are handled in an activity.
-We instantiated our technique for Android programs as follows:
-%, with some notable exceptions such as the
-%lifecycle of activities.
-
-%An XML \textit{manifest file} registers the components of an application. Other XML
-%fies describe the visual layout of the activities. Activities \textit{inflate}
-%layout files into
-%visual objects (a hierarchy of views), through an \textit{inflater} provided by the An-
-%droid library. This means that library or user-defined views are not explicitly
-%created by new statements but rather inflated through \textit{reflection}. Library meth-
-%ods such as \CodeIn{findViewById} access the inflated views.
-
-\begin{itemize}
-
-\item \textbf{Call graph entry nodes: }in an Android application,
-an \CodeIn{Activity} object is created and manipulated by the UI thread. Thus, we treat
-all public methods defined in the \CodeIn{Activity} class 
-and any class in the user code that subclasses \CodeIn{Activity} as call graph entry nodes.
-We also add all overridden Android GUI event handling methods in user
-code as entry nodes, since they are also called back from the UI thread.
-
-\item \textbf{UI-accessing nodes: }the \CodeIn{ViewRoot.checkThread} method.
-Like SWT, Android explicitly checks whether
-the current thread is a UI thread or not before accessing a GUI object via
-the \CodeIn{ViewRoot.checkThread} method.
-%method. This method is the only place where Android checks
-%whether the current thread is the UI thread or not. Thus, any
-%methods that calls the checking method must be invoked in the UI thread.
-
-\item \textbf{Safe UI methods: } two helper methods (\CodeIn{View.post}
-and \CodeIn{View.postDelay}) that execute code on the UI thread. 
-Invoking them on any thread will not cause an invalid thread access error.
-%Invoking these two methods are generally considered to be safe, and would not
-%cause an invalid thread access error.
-
-\end{itemize}
-
-Instantiating our general technique to  a specific framework
-requires moderate human effort. We wrote around 500 lines of Java code in total to achieve
-the above four instantiations.
+As we will show in our experiments (Section~\ref{sec:filters}), these filters
+work remarkably well by reducing over 99\% of the reported warnings. In addition,
+we also found that only using sound filters was not sufficient. The overwhelming
+number of warnings after applied sound filters motivated the use
+of heuristic filters.

### 2012-02-07 trunk/GUIErrorDetector/paper/conclusion.tex
small revise

@@
 It uses a reflection-aware call graph construction algorithm
-to build a good call graph, and employs a set of heuristics to
-filter likely false positives and redundant warnings.
+to build a good call graph, and employs a set of error
+filters to filter likely false positives and redundant warnings.
 Since graphical user interfaces are often inadequately tested due
@@
 We have also demonstrated that our technique can be useful
-by an evaluation on 9 subjects acrosss 4 popular GUI
+by an evaluation on \subnum subjects acrosss 4 popular GUI
 frameworks. 
@@
 presented in this paper is a call graph-based, pure static analysis. 
-It may suffer from false positives for many GUI applications,
+It suffers from false positives for many GUI applications,
 due to the conservative nature of static analysis.

### 2012-02-07 trunk/GUIErrorDetector/paper/evaluation.tex
small revise

@@
 
-We have submitted all \newbugs new errors
+We submitted all \newbugs new errors
 to the subject developers. As of Feb 2012, 1 error in S3dropbox has been confirmed,
@@
 in the S3dropbox Swing application. The error occurs when
-the method \CodeIn{deleteCurrentBucket} invoked at line 63 throws
+the method \CodeIn{deleteCurrentBucket} invoked on line 63 throws
 an exception, which causes method \CodeIn{deleteError} to
-access a Swing GUI object \CodeIn{display} at line 79 from
-a non-UI thread. This error is previously-unknown, and has been confirmed by the S3dropbox developers.
+access a Swing GUI object \CodeIn{display} on line 79 from
+a non-UI thread. This error is previously unknown, and has been confirmed by the S3dropbox developers.
 }} %\vspace{-5mm}
@@
 for the EclipseRunner plugin. In Eclipse, the
-callback method \CodeIn{resourceChanged} at line 181
+callback method \CodeIn{resourceChanged} on line 181
 is invoked by non-UI threads when a \CodeIn{ResourceChangeEvent}
 happens. However, the \CodeIn{refresh} method directly accesses
-GUI objects (to refresh the view at line 415) without any
+GUI objects (to refresh the view on line 415) without any
 protection and thus triggers the error.
@@
 \CodeIn{ResourceChangeEvent} happen, which then invokes the \CodeIn{refresh}
-method at line 415 to update the user interface. In EclipseRunner,
+method on line 415 to update the user interface. In EclipseRunner,
 the \CodeIn{refresh} method is
@@
 One error only happens when
-the given sudoku is unsolvable; and the other one happens
-when the JVM fails to launch the mail composing window of the
+the given Sudoku is unsolvable; and the other one happens
+when  JVM fails to launch the mail composing window of the
 user default mail client (after a user clicks "eMail Me" button).

### 2012-02-07 trunk/GUIErrorDetector/paper/implementation.tex
Add a figure, and clarify a few points. the make file should be modified.

@@
 
-We implemented the proposed technique using the WALA framework~\cite{walatutorial}.
-Our prototype tool takes Java bytecode as input, works in a fully
-automatic and push-button way to detect potential invalid thread access
+We instantiated the proposed technique for four widely-used
+GUI frameworks, namely SWT, Eclipse plugin development, Swing, and Android;
+and implemented a prototype tool.
+Our tool is built on top of the WALA framework~\cite{walatutorial}.
+It takes Java bytecode as input, 
+automatically detects potential invalid thread access
 errors, and scales to realistic programs.
 
-%Optionally, users may specify additional heuristic filters (Section~\ref{sec:heuristic}) %to guide call graph traverse
-%, and annotate call relationships for native methods (Section~\ref{sec:annotation}).
+%We implemented the proposed technique using the WALA framework~\cite{walatutorial}.
+%Our prototype tool takes Java bytecode as input, 
+%automatically detects potential invalid thread access
+%errors, and scales to realistic programs.
 
-Our current implementation supports four widely-used GUI frameworks, namely
-SWT, Eclipse plugin development, Swing, and Android.
-%, including dependent libraries such as \CodeIn{rt.jar} and \CodeIn{android.jar}.
-%into analysis. 
+%Static Single Assignment (SSA) transformation to get limited flow sensitivity
+\subsection{Instantiation for Different Frameworks}
+\label{sec:platforms}
+
+%We instantiated our error detection technique for four popular GUI frameworks:
+%SWT, Eclipse plugin, Swing, and Android.
+When instantiating our error detection technique for different
+frameworks, the major framework-specific parts, corresponding to
+lines 3 -- 5 in Figure~\ref{fig:detectalgorithm}, are identifying
+\textbf{call graph entry nodes}, \textbf{UI-accessing nodes},
+and \textbf{safe UI methods} for each framework.
+
+%For each framework, we customize the \textit{call graph entry nodes},
+%\textit{UI-accessing nodes}, and \textit{safe UI methods} on lines 3 -- 5 of the
+%algorithm in
+
+%For the sake of efficiency, they are all using the single thread model.
+
+%Why these platforms? popularity? account for xxx\% of the GUI.
+
+%customizing for: entry points, starting points, error checking, thread
+%safe UI methods, what is the event dispatching thread?
+
+\subsubsection{SWT}
+
+ We instantiated our technique for SWT applications as follows:
+
+\begin{itemize}
+\smallstep
+
+\item \textbf{Call graph entry nodes: } the main method. Like a normal Java program,
+a SWT desktop application has a single main method as the entry point. By default,
+the main method is executed in the UI thread after the GUI
+is initialized.
+
+\smallstep
+
+\item \textbf{UI-accessing nodes: } the \CodeIn{Widget.checkWidget}
+and \CodeIn{Display.} \CodeIn{checkDevice} methods. SWT uses the above
+two methods to explicitly check whether the current thread is a UI thread
+or not, and throw a \CodeIn{RuntimeException} if the checking fails.
+%thread accesses at runtime.
+%Any methods for manipulating GUIs object must call (one of) these two methods
+% to determine whether the current thread is the UI thread or not.
+\smallstep
+
+\item \textbf{Safe UI methods: } \CodeIn{Display.asyncExec}
+and \CodeIn{Display.syncExec}. SWT provides these two methods
+to execute code (a)synchro- nizedly on the UI thread.
+%We treat these two methods as safe UI methods, since invoking
+%them from any thread 
+%will not cause an invalid thread access error.
+
+\end{itemize}
+
+\subsubsection{Eclipse plugin}
+
+We instantiated our technique for the Eclipse plugin development framework as follows:
+
+\smallstep
+
+%Unlike a SWT desktop application, an eclipse plugin, though is developed in SWT,
+%has no single main method. Instead, (XXX) it extends certain extension points
+%exposed by the eclipse framework, and eclipse will XXX. To instantiate our
+%technique for the Eclipse plugin environment, we need to redefine the
+%call graph entry points.
+
+\begin{itemize}
+
+\item \textbf{Call graph entry nodes: } all user code methods that override
+ SWT GUI event handling methods. Eclipse
+calls back the overridden methods to handle the
+events. All SWT GUI event handling methods (i.e., the overriden
+methods in the class that implements \CodeIn{org.eclipse.swt.internal.SWTEventListener}) are
+always called back from the UI thread, thus are used as call graph entry nodes.
+
+\smallstep
+
+\item \textbf{UI-accessing nodes} and \textbf{Safe UI methods} are the same as SWT.
+
+\end{itemize}
+
+\subsubsection{Swing}
+
+A Swing application has a single main method, but contains three kinds of
+threads: \textit{initial thread} that executes initial application code from the main method,
+the \textit{UI thread}, where all GUI manipulation code is executed,
+and the \textit{worker thread} where time-consuming background tasks are executed.
+After a Swing program starts, its initial thread exits and the UI thread takes charge
+of the application and starts to execute all event-handling code or spawns new worker threads. 
+We instantiated our technique for Swing as follows:
+%XXXX Therefore, we can not directly
+%use the main method as the call graph entry point, since it is not invoked
+%by the UI thread. We customize our technique for Swing as follows:
+
+\begin{itemize}
+
+\item \textbf{Call graph entry nodes:} all overridden Swing GUI event handling
+methods in user code. Those event handling methods are always
+called back from the UI thread.
+
+\smallstep
+
+\item \textbf{UI-accessing nodes:} %as stated in Swing's documentation,
+all methods defined in each Swing GUI class except for three thread-safe
+methods: \CodeIn{repaint()}, \CodeIn{revalidate()}, and \CodeIn{invalidate()}.
+
+\smallstep
+
+\item \textbf{Safe UI methods: } 
+\CodeIn{SwingUtilities.}\CodeIn{invokeLater} and \CodeIn{Swing-\\Utilities.invokeAndWait} that execute code on the UI thread.
+
+\end{itemize}
+
+\smallstep
+
+\subsubsection{Android}
+
+Android is a Java-based platform for embedded or mobile devices. 
+An Android program does not have a single entry point but can
+rather use parts of other Android applications on-demand and can require their
+services by calling corresponding event handlers, directly or through the
+operating system. In particular, Android applications use \textit{activities}
+(i.e., instances of the \CodeIn{Activity} class)
+to interact with users through a visual interface and handle GUI events.
+We instantiated our technique for Android programs as follows:
+
+\begin{itemize}
+
+\item \textbf{Call graph entry nodes: }in an Android application,
+an \CodeIn{Activity} object is created and manipulated by the UI thread. Thus, we treat
+all public methods defined in the \CodeIn{Activity} class 
+and any overriding definitions in its subclasses as call graph entry nodes.
+We also add all overridden Android GUI event handling methods in user
+code as entry nodes, since they are also called back from the UI thread.
+
+\smallstep
+
+\item \textbf{UI-accessing nodes: }the \CodeIn{ViewRoot.checkThread} method.
+Like SWT, Android explicitly performs runtim checking before accessing
+a GUI object via the \CodeIn{ViewRoot.checkThread} method. If the current
+thread is a non-UI thread, the \CodeIn{ViewRoot.checkThread} method throws
+a \CodeIn{RuntimeException}.
+
+\smallstep
+
+\item \textbf{Safe UI methods: } \CodeIn{View.post}
+and \CodeIn{View.postDelay} that execute code on the UI thread. 
+%Invoking them on any thread will not cause an invalid thread access error.
+%Invoking these two methods are generally considered to be safe, and would not
+%cause an invalid thread access error.
+
+\end{itemize}
+
+Instantiating our general technique to  a specific framework
+requires moderate human effort. We wrote around 500 lines of Java code in total to achieve
+the above four instantiations.
+
+\subsection{Implementation Details}
+
+%Our current implementation supports four widely-used GUI frameworks:
+%SWT, Eclipse plugin development, Swing, and Android.
 We implemented the reflection-aware call graph construction
@@
 Unlike similar tools~\cite{Payet:2011:SAA:2032266.2032299}, our tool
-does not require a separated
-pass of program instrumentation; instead, it
+does not require a separate pass for program instrumentation; instead, it
 parses the configuration file in an Android application,
@@
 library (i.e., \CodeIn{android.jar}) uses many ``stub'' classes as
-placeholders for the sake of efficiency. We manually re-compiled the whole
-\CodeIn{android.jar} from its source code and replaced all ``stub'' classes
-with real class files.
-
-%Static Single Assignment (SSA) transformation to get limited flow sensitivity
+placeholders for the sake of efficiency. We manually re-compiled 
+\CodeIn{android.jar} from its source code, so it contains real
+class files rather than stubs.

### 2012-02-07 trunk/GUIErrorDetector/paper/technique.tex
Add a figure, and clarify a few points. the make file should be modified.

@@
 miss true positives. We note, however, that computing a sound
-call graph in the presence of reflection is non-trivial. 
+call graph in the presence of reflection and native methods is non-trivial. 
 To alleviate this problem, we next proposed a reflection-aware call graph
-construction algorithm in Section~\ref{sec:cg}.
+construction algorithm in Section~\ref{sec:cg} and annotation support
+for native methods in Section~\ref{sec:annotation}.
 
@@
 annotation into consideration when traversing the call graph.
+
 Adding annotations for native methods is optional and requires manual effort.
 In our experiments, 1 out of \subnum programs uses native methods. We manually
-searched the source files, inspected the code to determine possible target methods
+searched the Java source files to find all native methods,
+inspected the C code to determine possible target methods
 that may be called by a native method, and added \annotationnum annotations for this program.
@@
  that have the same error cause (redundant warnings). We devise
-5 filters below to remove likely false positives and redundant warnings.
+5 error filters below to remove likely false positives and redundant warnings.
 The first 2 filters are sound in that they will not filter real bugs, and
@@
 %Thus,
-A reported method call chain containing an annotated 
+A reported method call chain containing an annotated  method
 can be safely removed. In our experiments, we produced a list of \filternum
@@
 to dispose all GUI objects when the program exits.
-We encoded a list of common library calls by proposing
+We encoded a list of 25 common library calls by proposing
 a basic set of library calls that seemed natural and
@@
 
-\CodeIn{a()} $\rightarrow$ ...\CodeIn{Thread.start()} $\rightarrow$ \CodeIn{m()} $\rightarrow$ \CodeIn{accessUIObject1()} ...
+\CodeIn{a()} $\rightarrow$ ...\CodeIn{Thread.start()} ... $\rightarrow$ \CodeIn{m()} $\rightarrow$ \CodeIn{accessUIObject1()} ...
 
-\CodeIn{a()} $\rightarrow$ ...\CodeIn{Thread.start()} $\rightarrow$ \CodeIn{m()} $\rightarrow$ \CodeIn{accessUIObject2()} ...
+\CodeIn{a()} $\rightarrow$ ...\CodeIn{Thread.start()} ... $\rightarrow$ \CodeIn{m()} $\rightarrow$ \CodeIn{accessUIObject2()} ...
 
@@
 tail from \CodeIn{Thread.start()} to the UI-accessing methods, and
-removes the longer one.
+removes the longer one. Using filters 4 and 5 together results in
+only one error per \CodeIn{Thread.start()}.
 

### 2012-02-07 GUIErrorDetector/paper/evaluation.tex
Add a figure, and clarify a few points. the make file should be modified.

@@
 FileBunker~\cite{filebunker} is a file backup application which uses one or more GMail
-accounts as its backup repository. ArecaBackup~\cite{areca} offers a personal
+accounts as its backup repository. ArecaBackup~\cite{areca} offers a local
 file backup solution for Linux and Windows.
@@
  \hline
- VirgoFTP&  12401 &  2 &  2 & 10858 & 2 & 2 & 43598 & 2 & 2& 149  \\
+ VirgoFTP&  12401 &  1 &  1 & 10858 & 1 & 1 & 43598 & 2 & 2& 149  \\
  \hline
@@
 \hline
- Total & 199161 / 199724 &  189 / 252 & 7 / 7 & 149441 / 153054& 138 / 138& 8 / 8 & 577821 / 652756& 22 / 22 & 11 / 12 & 6542\\
+ Total & 199161 / 199724 &  188 / 251 & 6 / 6 & 149441 / 153054& 137 / 137& 7 / 7 & 577821 / 652756& 22 / 22 & 11 / 12 & 6542\\
 \hline
@@
 S3dropbox, and SudokuSolver are previously  unknown. As a comparison, the
-results of a straightforward approach (Section~\ref{sec:straightforward}) are shown at the far right.} }
+results of a straightforward approach, called ``Requiring Wrappers'' (Section~\ref{sec:straightforward}),
+are shown at the far right.} }
 \end{table*}
@@
 
-We have submitted all of the newly-found errors
-to the developers. As of Feb 2012, 1 error in S3dropbox has been confirmed.
-4 errors can be reproduced and validated in our own experimental environment, and
-1 error from FileBunker was submitted but has not been verified
-by its developers yet.
+We submitted all \newbugs new errors
+to the subject developers. As of Feb 2012, 1 error in S3dropbox has been confirmed,
+4 errors have been reproduced and validated in our own experimental environment, and
+2 errors in FileBunker and ArecaBackup had not been verified by developers yet.
 
@@
 Besides the above two examples, other errors our tool reported were also
-subtle to find. Take the two newly-found errors in SudokuSolver
-as an example. One error happens when
+subtle to find. For example, our tool found two new errors in SudokuSolver.
+One error only happens when
 the given Sudoku is unsolvable; and the other one happens
-when the program fails to launch the mail composing window of the
-user default mail client (after clicking "eMail Me" button).
+when  JVM fails to launch the mail composing window of the
+user default mail client (after a user clicks the "eMail Me" button).
 
@@
 mix the same method calls by different callers into a single node, thus
-introducing imprecision.
+introducing imprecision. Although the error-revealing path exists in
+the less precise graphs, it presents the error detection algorithm finding it.
+Figure~\ref{fig:ex} illustrates this limitation.
 
-%Although the call graphs
-%built by 1-CFA are significantly larger, XXX, the algorithm still runs
-%in a practical amouont of time. For example,
-%our tool finished building the call graph for the largest subject (xxx)
-%within xxx minutes.
+\begin{figure}[t]
+  \centering
+  \includegraphics[scale=0.33]{cgexample}
+  \vspace*{-5.0ex}\caption {{\label{fig:ex} (a) shows an example code, in which
+\CodeIn{safeMtd} is a Safe UI method, and \CodeIn{uiAcc} is a UI-Accessing method.
+(b) shows a less precise call graph built by RTA or 0-CFA, and (c) shows a more
+precise call graph built by 1-CFA. The node for \CodeIn{Thread.run()}
+method is omitted for brevity. Using the less precise call graph, the error
+detection algorithm will report an invalid method call chain: \CodeIn{entry()}
+$\rightarrow$ \CodeIn{f()} $\rightarrow$ \CodeIn{start()} $\rightarrow$ \CodeIn{uiAcc()},
+but miss the actual error path: \CodeIn{entry()} $\rightarrow$ \CodeIn{g1()} $\rightarrow$
+\CodeIn{g2()} $\rightarrow$ \CodeIn{start()} $\rightarrow$ \CodeIn{uiAcc()}. The
+actual error path can only be found when using the more precise call graph.
+}}
+\end{figure}
 
@@
 The five error filters removed 99.96\% of the reported warnings as false positives
-or redundant warnings. Specifically, two sound filters 1 and 2 identified
-removed 36.52\% of the warnings, and three heuristic filters 3, 4, and 5
-removed 63.44\% of the warnings. Among them, the 1st filter for removing
-lexically redundant reports is the most effective one.
+or redundant warnings. Specifically, two sound filters 1 and 2 
+removed 34.44\% of the warnings, and three heuristic filters 3, 4, and 5
+removed a further 65.52\% of the warnings. Among them, the 4th filter for removing
+reports with the same head methods from the entry node to \CodeIn{Thread.start()}
+is the most effective one.
 
@@
  \hline
- FileBunker &  4494 &  4494 &  3210 &  3210 &  10  & 2\\
+ FileBunker &  4494 &  4494 &  4494 &  3210 &  10  & 2\\
  \hline
@@
  \hline
- Fennec &  122 &  84 & 84 & 84 &  9 & 3\\
+ Fennec &  122 &  84 & 80 & 80 &  9 & 3\\
  \hline
@@
  \hline
- Total &  60631 &  40461 &  38484 &  37425 &  112 & 22 \\
+ Total &  60631 &  40461 &  39764 &  37421 &  112 & 22 \\
  \hline
@@
 the $i$th to $j$th filters as defined in Section~\ref{sec:heuristic}.
-The numbers in the last column are the same as the subcolumn ``\#Warnings"
+The numbers in the last column are the same as the subcolumn ``\#Warning"
 under column ``1-CFA'' in Table~\ref{table:results}.
@@
 For the most time-consuming subject, MyTracks, our tool finished the whole analysis
-within 686 seconds using the most expensive call graph construction
+within 209 seconds using the most expensive call graph construction
 algorithm: the reflection-aware 1-CFA algorithm. Analyzing

### 2012-02-07 GUIErrorDetector/paper/related.tex
Add a figure, and clarify a few points. the make file should be modified.

@@
 (for model-based testing)~\cite{androidtesting}, %, Xie:2006:MTC:1172962.1172990},
-test-case generation~\cite{YuanCohenMemonTSE2011, YuanMemonICSE2007},
-test oracle creation~\cite{MemonFSE2000}, test execution~\cite{MemonFSE2001},
+test generation~\cite{YuanMemonICSE2007},
+test oracle creation~\cite{MemonFSE2000}, test execution~\cite{YuanCohenMemonTSE2011},
 and test script repairing~\cite{Huang:2010:RGT:1828417.1828465, Daniel:2011:AGR:2002931.2002937}.
@@
 Yuan and Memon~\cite{YuanMemonICSE2007} generate event-sequence based test cases for GUI
-programs. They proposed a model-based approach for testing GUI-based applications.
-Their technique can generate test cases automatically using a structural event
+programs. Their model-based approach can generate test cases automatically using a structural event
 generation graph. 
-However, testing is often insufficient to ensure the correctness of a GUI program
+However, testing is often insufficient to detect many potential
+errors in a GUI application
 due to the huge space of possible interactions
 with a GUI. The large number of possible interactions
-result in a large number of
-test inputs requiring substantile human effort, and then makes
-testing fail to detect many potential errors.
+need a large number of test inputs that require substantial human effort.
 %The second problem is to determine the coverage of a set of test
@@
 %the completeness of a test suite. 
-In contrast, as advocated in this paper, the primary advantage of
-using a static analysis is that it can potentially explore
-all paths to find possible bugs without actually executing the tested code. 
+In contrast, as suggested in this paper,
+using a static analysis can potentially explore
+all paths to find potential errors without actually executing the tested code. 
 Compared with software testing, a static analysis tool may
-report false positives due to its conservative nature.
-Nevertheless, as we demonstrated in our experiments, using a few simple heuristics
-can dramatically reduce the number of false positives  to
+report false positives and redundant warnings due to its conservative nature.
+Nevertheless, as we demonstrated in our experiments, using a few simple error
+filters can dramatically reduce the number of false positives and redundant warnings to
 an acceptable level.
@@
 To the best of our knowledge, we are the first to address the invalid
-thread access problem on multithreaded GUI applications, and
-our technique is a general one that can be easily tailored for
-different GUI frameworks.
+thread access error detection problem for multithreaded GUI applications, and
+our core technique is a general one that can be tailored for
+various GUI frameworks.
 
@@
 Static analysis tools such as Chord~\cite{Naik:2006}
- explore multithreaded bugs by statically analyzing the program. On the
-other hand, runtime analysis tools such as Eraser~\cite{Savage:1997}  dynamically detect concurrency bugs using the lockset
+ explore multithreaded bugs by statically analyzing the program. Runtime
+analysis tools such as Eraser~\cite{Savage:1997}  dynamically detect concurrency bugs using the lockset
 algorithms or some criteria based automata. 
@@
 we are not aware of any software model checking approach can scale to the subjects
-as large as those used in our experiments (including the dependent library code). Compared with model checking, the static analysis
-algorithm presented in this paper chooses call graph as the
-abstraction level with a set of heuristics, and thus is much lightweighted. It is highly tailored to find the invalid thread
-access errors instead of being a general property checking tool. For this reason,
-our technique achieves good scalability with reasonable precision.
+as large as those used in our experiments (including the library code).
+The technique presented in this paper is specifically designed to find invalid thread
+errors instead of being a general property checking tool. 
+It chooses call graph as a coarse-grained program representation with a
+set of error filters, achieving good scalability with reasonable accuracy.
+
+%For this reason,
+%our technique achieves good scalability with reasonable precision.
+
+\subsection{Call Graph Construction Algorithms}
+
+A lot of effort has been spent on analyzing function pointers in C
+as well as virtual method calls in C++ and Java ~\cite{rta, kcfa,
+xta, inccg, Sundaresan:2000}.
+We briefly mention some of the highlights of call graph construction
+algorithms for Java here. Grove et al~\cite{kcfa} described a unified
+framework for expressing call graph construction algorithms, and
+performed a quantitative study comparing different instantiations
+of the framework. Tip and Palsberg~\cite{xta} quantitatively compared
+several low-cost call graph construction algorithms for Java.
+Sundaresan et al.~\cite{Sundaresan:2000} went beyond the traditional
+CHA and RTA~\cite{rta} approaches in Java and used type propagation
+for the purpose of obtaining a more precise call graph.
+However, the heavy use of reflection in some GUI applications make
+those algorithms insufficient to build a good call graph.
+As reflected in our experiments, using standard call graph algorithms
+fails to find errors in some
+Android applications. %, due to the incompleteness of the resulting graph.
+
+To enable call graph construction in the presence of  reflection,
+Livshits et al.~\cite{Livshits:2005} presented a static analysis
+that attempts to infer additional information about
+reflective call sites directly from program code. The analysis
+attempts to use information stored in string constants to resolve
+reflective calls statically. Their approach focuses on standard Java
+reflection library calls (e.g., \CodeIn{java.lang.Class.forName}) but not on
+framework-specific ones (e.g., \CodeIn{android.view.View.findViewById}).
+The WALA framework implements a similar approach to handle Java
+reflections, but still fails to build a sufficiently complete call graph for
+Android applications. TamiFlex~\cite{Bodden:2011}, a pure dynamic
+approach, dumps all reflectively-created class instances to a file
+by intercepting JVM system calls, and re-inserts those recorded 
+class into a program. However, TamiFlex requires a set of representative
+program executions which may not be available in practice,
+ and is only sound with respect to the recorded executions.
+Perhaps the most close work to our reflection-aware call graph
+construction algorithm is Payet and Spoto's Julia
+system~\cite{Payet:2011:SAA:2032266.2032299}, which is independently
+proposed with our algorithm. One difference is that the Julia system
+requires to instrument the code of Android's library class
+\CodeIn{android.view.LayoutInflater} that performs the XML inflation ahead of time,
+then replaces the \CodeIn{findViewById} call with with a
+non-deterministic execution of new statements.
+In contrast, our algorithm leverages WALA's \textit{bypass logic}
+to transform the program on-the-fly when
+constructing the call graph, without requiring a separate pass of
+off-line instrumentation.
+
+%There are few algorithms have been studied to construct call
+%A recent paper by Hirzel, Diwan, and Hind addresses the issues of dynamic
+%class loading, native methods, and reflection in order to deal with the full complexity
+%of Java in the implementation of a common pointer analysis [5]. Their
+%approach involves converting the pointer analysis [6] into an online algorithm:
+%they add constraints between analysis nodes as they are discovered at runtime.
+%Newly generated constraints cause re-computation and the results are propagated
+%to analysis clients such as a method inliner and a garbage collector at
+%runtime. Their approach leverages the class hierarchy analysis (CHA) to update
+%the call graph. Our technique uses a more precise pointer analysis-based
+%approach to call graph construction.

### 2012-02-07 GUIErrorDetector/paper/conclusion.tex
substantile changes

@@
 It uses a reflection-aware call graph construction algorithm
-to build a good call graph, and employs a set of sound and heuristic
+to build a good call graph, and employs a set of error
 filters to filter likely false positives and redundant warnings.
-Since graphical user interfaces are often inadequately tested due
-to the enormously large space of UI interactions and
-extreme resource constraints during their development, we
-believe that providing a static analysis can allow developers to find
-more potential errors %before the application is released to customers (XXX),
- to improve software reliability.
-We have also demonstrated that our technique can be useful
-by an evaluation on 9 subjects acrosss 4 popular GUI
+%Since graphical user interfaces are often inadequately tested due
+%to the enormously large space of UI interactions and
+%extreme resource constraints during their development, we
+%believe that providing a static analysis can allow developers to find
+%more potential errors %before the application is released to customers (XXX),
+% to improve software reliability.
+We demonstrated the usefulness of our technique
+by an evaluation on \subnum subjects on 4 popular GUI
 frameworks. 

### 2012-02-07 GUIErrorDetector/paper/related.tex
substantile changes

@@
 reflective calls statically. Their approach focuses on standard Java
-reflection library calls (e.g., \CodeIn{java.lang.Class.forName}) but not on
-framework-specific ones (e.g., \CodeIn{android.view.View.findViewById}).
+reflection calls (e.g., \CodeIn{java.lang.Class.forName}) but not on
+framework-specific ones (e.g., \CodeIn{android.view.View.find-\\ViewById}).
 The WALA framework implements a similar approach to handle Java

### 2012-02-07 trunk/GUIErrorDetector/paper/evaluation.tex
substantile changes

@@
 \section{Empirical Evaluation}
+\smallstep
 \label{sec:evaluation}
@@
 
+\smallstep
+\tinystep
+
 \subsection{Experimental Procedure}
@@
 to interact with the GUI framework. For example, in MyTracks, all non-UI
-threads are initialized via using the library method \CodeIn{android.os.handler.handleCallback}.
+threads are initialized via using the library method \CodeIn{android.os.} \CodeIn{handler.handleCallback}.
 % the \CodeIn{safeInvokeXX}
@@
 for Android applications, a slash ``/'' separates the result of
-using normal call graph construction algorithm and the reflection-aware
+using standard call graph construction algorithm and the reflection-aware
 call graph construction algorithm. The \newbugs errors found in VirgoFTP, FileBunker, ArecaBackup
 S3dropbox, and SudokuSolver are previously  unknown. As a comparison, the
-results of a straightforward approach, called ``Requiring Wrappers'' (Section~\ref{sec:straightforward}),
+results of the ``Requiring Wrappers'' approach (Section~\ref{sec:straightforward}),
 are shown at the far right.} }
@@
 
+\tinystep
 \subsection{Results}
@@
 %the effect of applying each heuristic filter.
+\smallstep
 
@@
 80.\}
+\smallstep
 \end{alltt}
 \end{CodeOut}
+\smallstep
 \vspace*{-2.0ex} \Caption{{\label{fig:swingerror} An
@@
 Figure~\ref{fig:swingerror}
-shows an invalid thread access error our tool found in the S3dropbox
-program. This error only happens when the \CodeIn{deleteCurrentBucket}
+shows an invalid thread access error our tool found in S3dropbox.
+This error happens when the \CodeIn{deleteCurrentBucket}
 call on line 63 throws an exception, making it hard to
@@
 \end{CodeOut}
+\smallstep
 \vspace*{-2.0ex} \Caption{{\label{fig:pluginerror} An
@@
 when  JVM fails to launch the mail composing window of the
-user default mail client (after a user clicks "eMail Me" button).
+user default mail client (after a user clicks the "eMail Me" button).
 
@@
 mix the same method calls by different callers into a single node, thus
-introducing imprecision.
+introducing imprecision. Although the error-revealing paths exist in
+less precise graphs, the impreicison prevents our algorithm finding them.
+Figure~\ref{fig:ex} illustrates this limitation.
 
-%Although the call graphs
-%built by 1-CFA are significantly larger, XXX, the algorithm still runs
-%in a practical amouont of time. For example,
-%our tool finished building the call graph for the largest subject (xxx)
-%within xxx minutes.
+\begin{figure}[t]
+  \centering
+  \includegraphics[scale=0.33]{cgexample}
+  \vspace*{-3.0ex}\caption {{\label{fig:ex} (a) shows an example code, in which
+\CodeIn{safeMtd()} is a Safe UI method, and \CodeIn{uiAcc()} is a UI-Accessing method.
+(b) shows a less precise call graph built by RTA or 0-CFA, and (c) shows a more
+precise call graph built by 1-CFA. Nodes for constructors and \CodeIn{Thread.run()}
+are omitted for brevity. Using the less precise call graph, the error
+detection algorithm will report an invalid method call chain: \CodeIn{entry()}
+$\rightarrow$ \CodeIn{f()} $\rightarrow$ \CodeIn{start()} $\rightarrow$ \CodeIn{uiAcc()},
+but miss the actual error path: \CodeIn{entry()} $\rightarrow$ \CodeIn{g1()} $\rightarrow$
+\CodeIn{g2()} $\rightarrow$ \CodeIn{start()} $\rightarrow$ \CodeIn{uiAcc()}. The
+actual error path can only be found when using the more precise call graph.
+}}
+\end{figure}
 
@@
 removed 34.44\% of the warnings, and three heuristic filters 3, 4, and 5
-removed 65.52\% of the warnings. Among them, the 4th filter for removing
+removed a further 65.52\% of the warnings. Among them, the 4th filter for removing
 reports with the same head methods from the entry node to \CodeIn{Thread.start()}
@@
 \Caption{{\label{table:filters}Number of warnings after applying a set of
-sound and heuristic filters. Column ``Before Filtering''
+sound and heuristic error filters. Column ``Before Filtering''
 shows the number of warnings by the reflection-aware 1-CFA algorithm.

### 2012-02-07 trunk/GUIErrorDetector/paper/implementation.tex
substantile changes

@@
+\tinystep
+\tinystep
 \section{Implementation}
@@
 GUI frameworks, namely SWT, Eclipse plugin development, Swing, and Android;
-and implemented a prototype tool.
-Our tool is built on top of the WALA framework~\cite{walatutorial}.
-It takes Java bytecode as input, 
-automatically detects potential invalid thread access
-errors, and scales to realistic programs.
+and implemented an error detection tool.
 
@@
 
-%Static Single Assignment (SSA) transformation to get limited flow sensitivity
+\tinystep
+
 \subsection{Instantiation for Different Frameworks}
@@
 
-%We instantiated our error detection technique for four popular GUI frameworks:
-%SWT, Eclipse plugin, Swing, and Android.
 When instantiating our error detection technique for different
@@
 
-%For each framework, we customize the \textit{call graph entry nodes},
-%\textit{UI-accessing nodes}, and \textit{safe UI methods} on lines 3 -- 5 of the
-%algorithm in
-
-%For the sake of efficiency, they are all using the single thread model.
-
-%Why these platforms? popularity? account for xxx\% of the GUI.
-
-%customizing for: entry points, starting points, error checking, thread
-%safe UI methods, what is the event dispatching thread?
-
+\tinystep
 \subsubsection{SWT}
@@
 to execute code (a)synchro- nizedly on the UI thread.
-%We treat these two methods as safe UI methods, since invoking
-%them from any thread 
-%will not cause an invalid thread access error.
 
@@
 
+\tinystep
 \subsubsection{Eclipse plugin}
@@
 \smallstep
-
-%Unlike a SWT desktop application, an eclipse plugin, though is developed in SWT,
-%has no single main method. Instead, (XXX) it extends certain extension points
-%exposed by the eclipse framework, and eclipse will XXX. To instantiate our
-%technique for the Eclipse plugin environment, we need to redefine the
-%call graph entry points.
 
@@
 events. All SWT GUI event handling methods (i.e., the overriden
-methods in the class that implements \CodeIn{org.eclipse.swt.internal.SWTEventListener}) are
+methods in the class that implements \CodeIn{org.eclipse.swt.internal.SWTEvent-\\Listener}) are
 always called back from the UI thread, thus are used as call graph entry nodes.
@@
 
+\tinystep
 \subsubsection{Swing}
@@
 We instantiated our technique for Swing as follows:
-%XXXX Therefore, we can not directly
-%use the main method as the call graph entry point, since it is not invoked
-%by the UI thread. We customize our technique for Swing as follows:
 
@@
 all methods defined in each Swing GUI class except for three thread-safe
-methods: \CodeIn{repaint()}, \CodeIn{revalidate()}, and \CodeIn{invalidate()}.
+methods: \CodeIn{repaint()}, \CodeIn{revali-\\date()}, and \CodeIn{invalidate()}.
 
@@
 and \CodeIn{View.postDelay} that execute code on the UI thread.
-%Invoking them on any thread will not cause an invalid thread access error.
-%Invoking these two methods are generally considered to be safe, and would not
-%cause an invalid thread access error.
 
 \end{itemize}
+
+\tinystep
 
@@
 
-%Our current implementation supports four widely-used GUI frameworks:
-%SWT, Eclipse plugin development, Swing, and Android.
+We implemented our error detection tool using
+the WALA framework~\cite{walatutorial}.
+Our tool takes Java bytecode as input, 
+automatically detects potential invalid thread access
+errors, and scales to realistic programs.
+
 We implemented the reflection-aware call graph construction

### 2012-02-07 trunk/GUIErrorDetector/paper/technique.tex
substantile changes

@@
 the single main method, UI-accessing nodes include methods
-\CodeIn{Widget.checkWidget} and \CodeIn{Display.checkDevice},
+\CodeIn{Widget.checkWidget} and \CodeIn{Display.} \CodeIn{checkDevice},
 and safe UI methods include two SWT helper methods \CodeIn{Display.asyncExec}  and
@@
 How to instantiate it for the Android framework is presented in Section~\ref{sec:cg}.
-%This algorithm is parameterized by the call graph construction
-%algorithm on line 8, in which any existing algorithm can be used.
 } 
@@
 is clicked, its event handling code (lines 9--11) updates the text.
-%d caches
-%the current view to a list declared at line 2.
 
@@
 corresponding to the \CodeIn{setText} method call on line 10 in the resulting call graph.
-
-%. As a result, the built 
-%call graph will exclude the calling edge corresponding to the
-%\CodeIn{setText} method call on line 10.
-
-%Existing call graph algorithms failed either suffer from the problem of incompleteness
-%or imprecision. The k-CFA algorithm performs points-to analysis with call
-%graph construction interleavingly, and maintains a value set for every expression.
-%For example, it concludes that variable \CodeIn{cachedViews} can only point
-%to a \CodeIn{LinkedList} object and the method call \CodeIn{add} at line 12
-%can only correspond to \CodeIn{LinkedList.add}. However, k-CFA fails to
-%conclude that variable \CodeIn{button} declared at line 7 points to
-%a \CodeIn{Button} object due to its limitation in dealing with reflection. Thus, k-CFA
-%may miss the call graph edge corresponding to the method call \CodeIn{setText} at line 11. 
-%On the other hand, using a coarse-grained algorithm like RTA~\cite{} can not still
-%fully solve this problem. RTA adds an edge for a method invocation 
-%to the call graph if an object of the receiver's type (or subtype)
-%has been created.  By explicitly specifying that all GUI classes declared in the XML file will be created,
-%RTA maintains a global value set for those GUI object type, and  adds a
-%call edge \CodeIn{setText} to the call graph. However, RTA introduces 
-%unnecessary precision loss: it may
-%may conclude that the \CodeIn{cachedViews} variable at line 2
-%point to any created \CodeIn{List} objects created somewhere else in the program, despite the
-%fact that \CodeIn{cachedViews} can only be a \CodeIn{LinkedList} object.
 
@@
 of the methods in the \CodeIn{java.lang.reflection} package.
-%In Figure~\ref{fig:cgalgorithm}, lines 1--7 show
-%the first step of program transformation. The algorithm iterates through every statement
-%in an analyzed program.
 When it sees a reflection call, the algorithm
@@
 returns a new object from the object set.
-%Line 8 is the second step
-%to build a call graph on the transformed program.
 
@@
 algorithms to analyze the transformed program, and permits them
-to add the call edge \CodeIn{setText} to the resulting graph.
+to include the call edge \CodeIn{setText} in the resulting graph.
 
@@
 in Android applications (Section~\ref{sec:reflectionaware}).
-
-% combined RTA and k-CFA
-%call graph construction algorithm as shown in Figure~\ref{fig:cgalgorithm}.
-%The algorithm shares the same spirit as k-CFA to maintain a value set
-%for each expression. However, the only difference is that our
-%algorithm uses a RTA-style treatment for constructing the value set for
-%GUI classes: it parses the XML configuration file and explicitly
-%adds a raw object to each declared GUI variable's value set. Thus,
-%For the example in Figure~\ref{fig:sampleandroid}, this
-%combined algorithm concludes that a \CodeIn{Button} object has been
-%created at line 7 and then adds the call edge \CodeIn{setText} to the
-%graph. It also concludes that the \CodeIn{cachedViews} variable can only
-%point to a \CodeIn{LinkedList} object, avoiding unnecessary precision loss.
 

### 2012-02-07 trunk/GUIErrorDetector/paper/technique.tex
tweak

@@
 
-%during analyzing programs on different GUI frameworks; we did this
-%only between experiments rather than biasing experiments by tuning
-%our tool to specific programs.
-
 \subsubsection{Heuristic Filters}
@@
 We later added other calls we found helpful in analyzing
-programs and that we believed would be generally useful.
+programs on different GUI frameworks and that we believed would be generally useful.
+We did this only between experiments rather than biasing experiments by tuning
+our tool to specific programs.
 

### 2012-02-08 GUIErrorDetector/src/edu/washington/cs/detector/util/AndroidUtils.java
small code tweak

@@ -204,7 +204,7 @@ public class AndroidUtils {
 		return declaredUIComponents;
 	}
 	
-	private static Set<String> getLibWidgets() {
+	public static Set<String> getLibWidgets() {
 		Set<String> widgetSet = new HashSet<String>();
 		for(String widgetName : widgetShortNames) {
 			widgetSet.add(widgetName);
@@ -269,7 +269,7 @@ public class AndroidUtils {
 		return ACTIVITY;
 	}
 	
-	private static String WIDGET_PACKAGE = "android.widget";
+	static String WIDGET_PACKAGE = "android.widget";
 	
 	private static IClass VIEW = null;
 	
@@ -397,7 +397,7 @@ public class AndroidUtils {
 		"ZoomControls"
 	};
 	
-	private static Set<String> getOtherUIs() {
+	public static Set<String> getOtherUIs() {
 		Set<String> uiSet = new HashSet<String>();
 		for(String uiName : otherUIs) {
 			uiSet.add(uiName);

### 2012-02-08 GUIErrorDetector/src/edu/washington/cs/detector/util/Utils.java

@@ -33,6 +33,16 @@ import edu.washington.cs.detector.CallChainNode;
 
 public class Utils {
 	
+	public static void checkTrue(boolean cond) {
+		checkTrue(cond, "");
+	}
+	
+	public static void checkTrue(boolean cond, String msg) {
+		if(!cond) {
+			throw new RuntimeException(msg);
+		}
+	}
+	
 	public static String translateSlashToDot(String str) {
 		assert str != null;
 		return str.replace('/', '.');

### 2012-02-08 GUIErrorDetector/src/edu/washington/cs/detector/util/AndroidLayoutParser.java
Add a fine-grained layout parser

@@ -1,0 +1,123 @@
+package edu.washington.cs.detector.util;
+
+import java.io.ByteArrayInputStream;
+import java.io.File;
+import java.io.IOException;
+import java.io.InputStream;
+import java.io.Reader;
+import java.util.Collection;
+import java.util.LinkedHashMap;
+import java.util.LinkedHashSet;
+import java.util.List;
+import java.util.Map;
+import java.util.Set;
+
+import javax.xml.parsers.ParserConfigurationException;
+import javax.xml.parsers.SAXParser;
+import javax.xml.parsers.SAXParserFactory;
+
+import org.xml.sax.Attributes;
+import org.xml.sax.InputSource;
+import org.xml.sax.SAXException;
+import org.xml.sax.helpers.DefaultHandler;
+
+import com.ibm.wala.classLoader.IClass;
+import com.ibm.wala.ipa.cha.ClassHierarchy;
+
+public class AndroidLayoutParser {
+
+	static String id_prefix = "@+id/";
+	
+	static Set<String> androidWidgetShortName = AndroidUtils.getLibWidgets();
+	static Set<String> otherAndroidUIFullName = AndroidUtils.getOtherUIs();
+
+	public static Map<String, String> extractAndroidUIMapping(ClassHierarchy cha, String dir) {
+		try {
+		    List<Reader> xmlFileReaders = AndroidUtils.getAllLayoutXMLFromDir(new File(dir));
+		    return extractAndroidUIMapping(cha, xmlFileReaders);
+		} catch (Throwable e) {
+			throw new RuntimeException(e);
+		}
+	}
+	
+	public static Map<String, String> extractAndroidUIMapping(ClassHierarchy cha, List<Reader> readers) throws IOException {
+		Map<String, String> map = new LinkedHashMap<String, String>();
+		for(Reader reader : readers) {
+			String xmlContent = Files.getFileContents(reader);
+			map.putAll(extractAndroidUIMapping(xmlContent, cha));
+		}
+		return map;
+	}
+	
+	// mapping from id => full class names
+	public static Map<String, String> extractAndroidUIMapping(String xmlContent, ClassHierarchy cha) {
+		Map<String, String> extractedMap = new LinkedHashMap<String, String>();
+		try {
+			SAXParserFactory factory = SAXParserFactory.newInstance();
+			SAXParser saxParser = factory.newSAXParser();
[…]

### 2012-02-08 GUIErrorDetector/src/edu/washington/cs/detector/util/AndroidLayoutParser.java
LayoutParser tested

@@ -81,6 +81,8 @@ public class AndroidLayoutParser {
 				validatedMap.put(idKey, value);
 			} else if (otherAndroidUIFullName.contains(value)) {
 				validatedMap.put(idKey, value);
+			} else if (value.equals("WebView")) {
+				validatedMap.put(idKey, "android.webkit.WebView");
 			} else {
 				Utils.checkTrue(cha != null);
 				IClass VIEW = AndroidUtils.getWidgetView(cha);
@@ -111,8 +113,10 @@ public class AndroidLayoutParser {
 				for (int i = 0; i < attributes.getLength(); i++) {
 					if (attributes.getQName(i).equals("android:id")) {
 						String idValue = attributes.getValue(i);
-						Utils.checkTrue(idValue.startsWith(id_prefix));
-						String id = idValue.substring(id_prefix.length());
+						Utils.checkTrue(idValue.indexOf("/") != -1);
+//						Utils.checkTrue(idValue.startsWith(id_prefix), "ID: " + idValue + ", qname: " + qName);
+//						String id = idValue.substring(id_prefix.length());
+						String id = idValue.substring(idValue.indexOf("/") + 1);
 						Utils.checkTrue(!idMap.containsKey(id));
 						idMap.put(id, qName);
 					}

### 2012-02-08 trunk/GUIErrorDetector/tests/edu/washington/cs/detector/util/LayoutParserTest.java
LayoutParser tested

@@ -1,0 +1,80 @@
+package edu.washington.cs.detector.util;
+
+import java.io.IOException;
+import java.util.Map;
+
+import com.ibm.wala.core.tests.callGraph.CallGraphTestUtil;
+import com.ibm.wala.ipa.cha.ClassHierarchy;
+import com.ibm.wala.ipa.cha.ClassHierarchyException;
+
+import edu.washington.cs.detector.CGBuilder;
+import junit.framework.TestCase;
+
+public class LayoutParserTest extends TestCase {
+	
+	public void testSGTPuzzlers() throws IOException, ClassHierarchyException {
+		String path = 
+			"D:\\research\\guierror\\subjects\\android-programs\\extracted\\sgtpuzzles.jar"
+			+ Globals.pathSep +	"D:\\research\\guierror\\eclipsews\\GUIErrorDetector\\exp-subjects\\original-android.jar";
+		String dir = "D:\\research\\guierror\\subjects\\android-programs\\extracted\\SGTPuzzles-9306-7.apk";
+		
+		CGBuilder builder = new CGBuilder(path,CallGraphTestUtil.REGRESSION_EXCLUSIONS);
+	    builder.makeScopeAndClassHierarchy();
+	    ClassHierarchy cha = builder.getClassHierarchy();
+	    
+	    Map<String, String> uiMap = AndroidLayoutParser.extractAndroidUIMapping(cha, dir);
+	    for(String key : uiMap.keySet()) {
+	    	System.out.println(key + ": --- " + uiMap.get(key));
+	    }
+	}
+	
+    public void testMytracks() throws IOException, ClassHierarchyException {
+    	String path = 
+    		"D:\\research\\guierror\\subjects\\android-programs\\sourcecode\\mytracks-april-29\\mytracks-april-29.jar"
+			+ Globals.pathSep +
+			"D:\\research\\guierror\\subjects\\android-programs\\sourcecode\\mytracks-april-29\\mytrackslib-april-29.jar"
+			+ Globals.pathSep +
+			"D:\\research\\guierror\\subjects\\android-programs\\sourcecode\\mytracks-april-29\\MyTracks\\libs\\accounts.jar"
+		    + Globals.pathSep +
+		    "D:\\research\\guierror\\subjects\\android-programs\\sourcecode\\mytracks-april-29\\MyTracks\\libs\\google-api-client-1.2.2-alpha.jar"
+		    + Globals.pathSep +
[…]

### 2012-02-08 trunk/GUIErrorDetector/paper/evaluation.tex
tweak and make the cg larger

@@
 less precise graphs, the impreicison prevents our algorithm finding them.
-Figure~\ref{fig:ex} illustrates this limitation.
+Figure~\ref{fig:ex} illustrates this point.
 
@@
   \centering
-  \includegraphics[scale=0.33]{cgexample}
-  \vspace*{-3.0ex}\caption {{\label{fig:ex} (a) shows an example code, in which
-\CodeIn{safeMtd()} is a Safe UI method, and \CodeIn{uiAcc()} is a UI-Accessing method.
+  \includegraphics[scale=0.45]{cgexample}
+  \vspace*{-5.0ex}\caption {{\label{fig:ex} (a) shows an example code, in which
+\CodeIn{safe()} is a Safe UI method, and \CodeIn{uiAcc()} is a UI-Accessing method.
 (b) shows a less precise call graph built by RTA or 0-CFA, and (c) shows a more
-precise call graph built by 1-CFA. Nodes for constructors and \CodeIn{Thread.run()}
-are omitted for brevity. Using the less precise call graph, the error
+precise call graph built by 1-CFA. Nodes for constructors are omitted for brevity.
+Using the less precise call graph, the error
 detection algorithm will report an invalid method call chain: \CodeIn{entry()}
-$\rightarrow$ \CodeIn{f()} $\rightarrow$ \CodeIn{start()} $\rightarrow$ \CodeIn{uiAcc()},
+$\rightarrow$ \CodeIn{f()} $\rightarrow$ \CodeIn{start()} $\rightarrow$ \CodeIn{run()}
+$\rightarrow$ \CodeIn{uiAcc()},
 but miss the actual error path: \CodeIn{entry()} $\rightarrow$ \CodeIn{g1()} $\rightarrow$
-\CodeIn{g2()} $\rightarrow$ \CodeIn{start()} $\rightarrow$ \CodeIn{uiAcc()}. The
+\CodeIn{g2()} $\rightarrow$ \CodeIn{start()} $\rightarrow$ \CodeIn{run()} $\rightarrow$ \CodeIn{uiAcc()}. The
 actual error path can only be found when using the more precise call graph.
@@
 on lines 9, 12, and
-23 in Figure~\ref{fig:androiderror}, respectively)
+23 in Figure~\ref{fig:detectalgorithm}, respectively)
 to the corresponding statck operations (\CodeIn{pushAll}, and \CodeIn{pop}).

### 2012-02-08 trunk/GUIErrorDetector/paper/introduction.tex
update the experimental data
tweak and make the cg larger

@@
 \end{CodeOut}
+\tinystep
 \vspace*{-3.0ex} \Caption{{\label{fig:androiderror} 
@@
 %$\rightarrow$\CodeIn{ \scriptsize{android.view.ViewRoot.checkThread()}}
+\tinystep
 \vspace*{-3.0ex} \Caption{{\label{fig:report} Our tool reports
@@
 problem. Given a call graph, our technique traverses
-every possible path from its entry nodes, checking whether
+paths from its entry nodes, checking whether
 any path accesses a GUI object from a non-UI thread. If 
@@
 to the same error. To address such limitations, we devise a set
- of sound and heuristic filters to remove likely false positives and redundant warnings.
+ of error filters to remove likely false positives and redundant warnings.
 
@@
 and scales to realistic programs.
-We evaluated our implementation on \subnum programs comprising over \totaloc LOC.
+We evaluated our implementation on \subnum programs comprising \totaloc LOC.
 The experiment results demonstrate
@@
 
+\smallstep
+
 \item \textbf{Evaluation.} We applied our tool to \subnum programs 
-from 4 different frameworks, comprising over \totaloc LOC. The results
+from 4 different frameworks, comprising \totaloc LOC. The results
 show the usefulness of the proposed technique (Section~\ref{sec:evaluation}).

### 2012-02-09 GUIErrorDetector/paper/implementation.tex
update the experimental data
small tweak

@@
 
-%For each framework, we customize the \textit{call graph entry nodes},
-%\textit{UI-accessing nodes}, and \textit{safe UI methods} on lines 3 -- 5 of the
-%algorithm in
-
-%For the sake of efficiency, they are all using the single thread model.
-
-%Why these platforms? popularity? account for xxx\% of the GUI.
-
-%customizing for: entry points, starting points, error checking, thread
-%safe UI methods, what is the event dispatching thread?
-
-\newcommand{\smallstep}{\vspace{-2mm}}
+\tinystep
 \subsubsection{SWT}
@@
 
-\item \textbf{UI-accessing nodes: } the \CodeIn{Display.checkWidget}
+\item \textbf{UI-accessing nodes: } the \CodeIn{Widget.checkWidget}
 and \CodeIn{Display.} \CodeIn{checkDevice} methods. SWT uses the above
-two methods to explicitly check thread accesses at runtime.
+two methods to explicitly check whether the current thread is a UI thread,
+and throw a \CodeIn{RuntimeException} if the checking fails.
+%thread accesses at runtime.
 %Any methods for manipulating GUIs object must call (one of) these two methods
@@
 events. All SWT GUI event handling methods (i.e., the overriden
-methods in the class that implements \CodeIn{org.eclipse.swt.internal.SWTEventListener}) are
-always called back from the UI thread, thus are used as call graph entry nodes.
+methods in the class that implements \CodeIn{org.eclipse.swt.internal.SWTEvent-\\Listener}) are
+always called back from the UI thread.
+%, thus are used as call graph entry nodes.
 
@@
 
+\tinystep
+\tinystep
 \subsubsection{Swing}
@@
 
-\item \textbf{Call graph entry nodes:} all overridden Swing GUI event handling
-methods in user code. Those event handling methods are always
+\item \textbf{Call graph entry nodes:} all user code methods that override
+Swing GUI event handling methods. Those event handling methods are always
 called back from the UI thread.
@@
 Android is a Java-based platform for embedded or mobile devices. 
-An Android program does not have a single entry point but can
-rather use parts of other Android applications on-demand and can require their
-services by calling corresponding event handlers, directly or through the
-operating system. In particular, Android applications use \textit{activities}
+An Android program does not have a single entry point.
+%but can
+%rather use parts of other Android applications on-demand and can require their
+%services by calling corresponding event handlers, directly or through the
+%operating system. In particular,
+%Android applications 
+It uses \textit{activities}
 (i.e., instances of the \CodeIn{Activity} class)
@@
 We instantiated our technique for Android programs as follows:
-%, with some notable exceptions such as the
-%lifecycle of activities.
-
-%An XML \textit{manifest file} registers the components of an application. Other XML
-%fies describe the visual layout of the activities. Activities \textit{inflate}
-%layout files into
-%visual objects (a hierarchy of views), through an \textit{inflater} provided by the An-
-%droid library. This means that library or user-defined views are not explicitly
-%created by new statements but rather inflated through \textit{reflection}. Library meth-
-%ods such as \CodeIn{findViewById} access the inflated views.
 
@@
 and any overriding definitions in its subclasses as call graph entry nodes.
-We also add all overridden Android GUI event handling methods in user
-code as entry nodes, since they are also called back from the UI thread.
+We also add all user code methods that override Android GUI event handling methods
+as entry nodes, since they are called back from the UI thread.
 
@@
 \item \textbf{UI-accessing nodes: }the \CodeIn{ViewRoot.checkThread} method.
-Like SWT, Android explicitly checks whether
-the current thread is a UI thread or not before accessing a GUI object via
-the \CodeIn{ViewRoot.checkThread} method.
+Like SWT, Android explicitly performs runtime checking before accessing
+a GUI object via the \CodeIn{ViewRoot.checkThread} method. If the current
+thread is a non-UI thread, the \CodeIn{ViewRoot.checkThread} method throws
+a \CodeIn{RuntimeException}.
 
@@
 
-%Our current implementation supports four widely-used GUI frameworks:
-%SWT, Eclipse plugin development, Swing, and Android.
+We implemented our error detection tool using
+the WALA framework~\cite{walatutorial}.
+Our tool takes Java bytecode as input, 
+automatically detects potential invalid thread access
+errors, and scales to realistic programs.  
 We implemented the reflection-aware call graph construction
  algorithm (Section~\ref{sec:cg}) using WALA's \textit{bypass logic}.
-Unlike similar tools~\cite{Payet:2011:SAA:2032266.2032299}, our tool
-does not require a separate
-pass for program instrumentation; instead, it
+Unlike existing tools~\cite{Payet:2011:SAA:2032266.2032299}, our tool
+does not require a separate pass for program instrumentation; instead, it
 parses the configuration file in an Android application,

### 2012-02-09 trunk/GUIErrorDetector/paper/evaluation.tex
small tweak

@@
+\tinystep
 \section{Empirical Evaluation}
-\smallstep
 \label{sec:evaluation}
@@
 \hline
- Total & 199161 / 199724 &  188 / 251 & 6 / 6 & 149441 / 153054& 137 / 137& 7 / 7 & 577821 / 652756& 22 / 22 & 11 / 12 & 6542\\
+ Total & 199161 / 199724 &  188 / 251 & 5 / 5 & 149441 / 153054& 137 / 137& 6 / 6 & 577821 / 652756& 22 / 22 & 11 / 12 & 6542\\
 \hline
@@
 
-Besides the above two examples, other errors our tool reported were also
+Besides the above two examples, other errors our tool reported are also
 subtle to find. For example, our tool found two new errors in SudokuSolver.
@@
 As briefly mentioned in Section~\ref{sec:finding}, one way to prevent
-invalid thread access errors is to wrap every GUI accessing operation
+invalid thread access errors is to wrap every GUI-accessing operation
 with message passing (i.e., via the safe UI methods). Although
@@
 Table~\ref{table:results}, Requiring Wrappers could identify every
-error that our technique found, but it issues a huge number of warnings,
+error that our technique found, but it issued a huge number of warnings,
 most of which are probably false positives.
@@
 Using the less precise call graph, the error
-detection algorithm will report an invalid method call chain: \CodeIn{entry()}
+detection algorithm in Figure~\ref{fig:detectalgorithm} will report an invalid method call chain: \CodeIn{entry()}
 $\rightarrow$ \CodeIn{f()} $\rightarrow$ \CodeIn{start()} $\rightarrow$ \CodeIn{run()}
@@
 This variant ran out of memory on all subjects. We checked
-the output paths before the algorithm terminated, and found none of the explored
-path revealed a real error. This is because the number of
-non-cyclic paths in a graph is exponential in the graph node number.
+the explored paths before the algorithm terminated, and found none of them
+revealed a real error. This is because the number of
+non-cyclic paths in a graph is exponential in the graph size.%node number.
 For a realistic call graph which often contains thousands of nodes,
@@
 issue false positives or redundant reports, a set of well-designed
-sound and heuristic filters can still remove most of them.
+error filters can remove most of them.
 %Heuristic filter, effective.

### 2012-02-09 trunk/GUIErrorDetector/paper/introduction.tex
small tweak

@@
 If the thread scheduler could arbitrarily interleave component changes, then event processing,
-program comprehension and testing would be more difficult.
+program comprehension, and testing would be more difficult.
 \end{itemize}
@@
 requires GUI operations to be in a message issues
-an unacceptable number of false positives and redundant warnings.
+an unacceptable number of warnings. %false positives and redundant warnings.
 
@@
 Static analysis has two advantages compared to dynamic approaches such as
- testing. First, a static analysis can explore every path of the program without
+ testing. First, a static analysis can explore paths of the program without
 executing the code, and without the need for a test suite.
@@
 We evaluated our implementation on \subnum programs comprising \totaloc LOC.
-The experiment results demonstrate
+The experimental results demonstrate
 that: our technique is effective (it found \bugs real-world errors
@@
 finding errors in Android applications;
-and our proposed filters significantly reduce the number of
-false positives and redundant warnings.
+and our proposed filters significantly reduce the number of warnings.
+%false positives and redundant warnings.
 
@@
 This paper makes the following contributions:
+
+\tinystep
 

### 2012-02-09 trunk/GUIErrorDetector/paper/related.tex
small tweak

@@
 
+\tinystep
 \subsection{Analysis and Testing for GUI Applications}
+%\vspace{1mm}
 
+%\noindent \textit{\textbf{Analysis and Testing for GUI Applications}}
 Automated GUI testing is a challenging tasks~\cite{Bertolino:2007:STR:1253532.1254712,
@@
 
-%is specifically designed to detect
-%the invalid thread access errors.
-
-%To the best of our knowledge, there is no prior work to tackle this invalid thread access problem
-% on multithreaded GUI applications.
-
+\tinystep
 \subsection{Finding Bugs in Multithreaded Programs}
 
+%\vspace{1mm}
+
+%\noindent \textit{\textbf{Finding Bugs in Multithreaded Programs}}
 A rich body of techniques have been developed to detect bugs in multithreaded programs~\cite{Huang:2011:PPC:2001420.2001438, Weeratunge:2010, Huang:2011:EST}.
@@
 
+\tinystep
+
 \subsection{Call Graph Construction Algorithms}
+%\vspace{1mm}
 
+%\noindent \textit{\textbf{Call Graph Construction Algorithms}}
 A lot of effort has been spent on analyzing function pointers in C
@@
 non-deterministic execution of new statements.
-In contrast, our algorithm leverages the powerful \textit{Bypass logic}
-in the WALA framework to transform the program on-the-fly when
+In contrast, our algorithm leverages WALA's \textit{bypass logic}
+to transform the program on-the-fly when
 constructing the call graph, without requiring a separate pass of

### 2012-02-09 trunk/GUIErrorDetector/paper/technique.tex
small tweak

@@
 We first give a high-level formulation of the problem, then present
-the error detection algorithm. Finally, we present how to 
+the error detection algorithm. Finally, we show how to 
 construct a reflection-aware call graph and filter the error reports.
@@
 When analyzing the code in Figure~\ref{fig:sampleandroid}, existing call graph algorithms
-fail to conclude that the variable \CodeIn{button} declared at line 6
-points to a \textit{non-null} \CodeIn{Button} object due to its limitation in deal with the
-reflection call \CodeIn{findViewById}, and exclude the calling edge
+fail to conclude that the variable \CodeIn{button} declared on line 6
+points to a \textit{non-null} \CodeIn{Button} object due to its limitation in handling the
+reflection call \CodeIn{findViewById}, and exclude the edge
 corresponding to the \CodeIn{setText} method call on line 10 in the resulting call graph.
@@
 getAllObjectsThatMaybeCreated on line 3 parses the associated XML configuration
-file in an Android application to extract the class declaration
+file to extract the class declaration
  corresponding to the given \CodeIn{id} value. If the \CodeIn{id}
@@
 %\item
-\textbf{2. Filter Reports With User-Annotated Methods}. Besides general
-library calls, users are also permitted to explicitly annotate project-specific methods
+\textbf{2. Filter Reports With User-Annotated Methods}. Users are
+permitted to explicitly annotate project-specific methods
 that will never trigger an error.
@@
 We encoded a list of 25 common library calls by proposing
-a basic set of library calls that seemed natural and
+a basic set of library calls that seemed %natural and
 generally applicable, based on our programming experience.

### 2012-02-09 GUIErrorDetector/paper/evaluation.tex
many tweaks

@@
+\tinystep
 \section{Empirical Evaluation}
@@
 
-\begin{itemize}
+\begin{itemize}%\addtolength{\itemsep}{-0.5\baselineskip}
 \Item \textbf{SWT desktop applications.}
@@
 mix the same method calls by different callers into a single node, thus
-introducing imprecision. Although the error-revealing path exists in
-the less precise graphs, it presents the error detection algorithm finding it.
-Figure~\ref{fig:ex} illustrates this limitation.
+introducing imprecision. Although the error-revealing paths exist in
+less precise graphs, the impreicison prevents our algorithm finding them.
+Figure~\ref{fig:ex} illustrates this point.
 
@@
   \centering
-  \includegraphics[scale=0.33]{cgexample}
+  \includegraphics[scale=0.45]{cgexample}
   \vspace*{-5.0ex}\caption {{\label{fig:ex} (a) shows an example code, in which
-\CodeIn{safeMtd} is a Safe UI method, and \CodeIn{uiAcc} is a UI-Accessing method.
+\CodeIn{safe()} is a Safe UI method, and \CodeIn{uiAcc()} is a UI-Accessing method.
 (b) shows a less precise call graph built by RTA or 0-CFA, and (c) shows a more
-precise call graph built by 1-CFA. The node for \CodeIn{Thread.run()}
-method is omitted for brevity. Using the less precise call graph, the error
-detection algorithm will report an invalid method call chain: \CodeIn{entry()}
-$\rightarrow$ \CodeIn{f()} $\rightarrow$ \CodeIn{start()} $\rightarrow$ \CodeIn{uiAcc()},
+precise call graph built by 1-CFA. Nodes for constructors are omitted for brevity.
+Using the less precise call graph, the error
+detection algorithm in Figure~\ref{fig:detectalgorithm} will report an invalid method call chain: \CodeIn{entry()}
+$\rightarrow$ \CodeIn{f()} $\rightarrow$ \CodeIn{start()} $\rightarrow$ \CodeIn{run()}
+$\rightarrow$ \CodeIn{uiAcc()},
 but miss the actual error path: \CodeIn{entry()} $\rightarrow$ \CodeIn{g1()} $\rightarrow$
-\CodeIn{g2()} $\rightarrow$ \CodeIn{start()} $\rightarrow$ \CodeIn{uiAcc()}. The
+\CodeIn{g2()} $\rightarrow$ \CodeIn{start()} $\rightarrow$ \CodeIn{run()} $\rightarrow$ \CodeIn{uiAcc()}. The
 actual error path can only be found when using the more precise call graph.
@@
 \noindent \textbf{\textit{Limitations.}}
-Our technique is limited in two aspects. First, it only considers
+Our technique is limited in three aspects. First, it only considers
 non-UI threads that are spawned by the UI-thread after the GUI
@@
 those non-UI threads created before a GUI is launched.
-Second, our tool cannot compute call relationships
+Second, like many bug-finding techniques, our technique
+is neither sound nor complete. It may miss true positives due
+to the graph search strategy the algorithm employs, or
+issue false positives because the conservative nature of
+a static analysis. Designing better call graph construction
+and search algorithm may alleviate this limitation.
+Third, our tool cannot compute call relationships
 for inter-process communication between components. It also

### 2012-02-09 GUIErrorDetector/paper/technique.tex
many tweaks

@@
 
-Given a sound call graph, our algorithm is sound in that it does not
-miss true positives. We note, however, that computing a sound
+%Given a sound call graph, our algorithm is sound in that it does not
+%miss true positives. We note, however, 
+For some modern GUI applications, computing a good
 call graph in the presence of reflection and native methods is non-trivial. 
-To alleviate this problem, we next proposed a reflection-aware call graph
+To alleviate this problem, we next present a reflection-aware call graph
 construction algorithm in Section~\ref{sec:cg} and annotation support
@@
 is clicked, its event handling code (lines 9--11) updates the text.
-%d caches
-%the current view to a list declared at line 2.
 
 When analyzing the code in Figure~\ref{fig:sampleandroid}, existing call graph algorithms
-fail to conclude that the variable \CodeIn{button} declared at line 6
-points to a \textit{non-null} \CodeIn{Button} object due to its limitation in deal with the
-reflection call \CodeIn{findViewById}, and exclude the calling edge
+fail to conclude that the variable \CodeIn{button} declared on line 6
+points to a \textit{non-null} \CodeIn{Button} object due to its limitation in handling the
+reflection call \CodeIn{findViewById}, and exclude the edge
 corresponding to the \CodeIn{setText} method call on line 10 in the resulting call graph.
-
-%. As a result, the built 
-%call graph will exclude the calling edge corresponding to the
-%\CodeIn{setText} method call on line 10.
-
-%Existing call graph algorithms failed either suffer from the problem of incompleteness
-%or imprecision. The k-CFA algorithm performs points-to analysis with call
-%graph construction interleavingly, and maintains a value set for every expression.
-%For example, it concludes that variable \CodeIn{cachedViews} can only point
-%to a \CodeIn{LinkedList} object and the method call \CodeIn{add} at line 12
-%can only correspond to \CodeIn{LinkedList.add}. However, k-CFA fails to
-%conclude that variable \CodeIn{button} declared at line 7 points to
-%a \CodeIn{Button} object due to its limitation in dealing with reflection. Thus, k-CFA
-%may miss the call graph edge corresponding to the method call \CodeIn{setText} at line 11. 
-%On the other hand, using a coarse-grained algorithm like RTA~\cite{} can not still
-%fully solve this problem. RTA adds an edge for a method invocation 
-%to the call graph if an object of the receiver's type (or subtype)
-%has been created.  By explicitly specifying that all GUI classes declared in the XML file will be created,
-%RTA maintains a global value set for those GUI object type, and  adds a
-%call edge \CodeIn{setText} to the call graph. However, RTA introduces 
-%unnecessary precision loss: it may
-%may conclude that the \CodeIn{cachedViews} variable at line 2
-%point to any created \CodeIn{List} objects created somewhere else in the program, despite the
-%fact that \CodeIn{cachedViews} can only be a \CodeIn{LinkedList} object.
 
@@
 We encoded a list of 25 common library calls by proposing
-a basic set of library calls that seemed natural and
+a basic set of library calls that seemed %natural and
 generally applicable, based on our programming experience.
 We later added other calls we found helpful in analyzing
-programs and that we believed would be generally useful.
+programs on different GUI frameworks and that we believed would be generally useful.
+We did this only between experiments rather than biasing experiments by tuning
+our tool to specific programs.
 

### 2012-02-09 trunk/GUIErrorDetector/paper/introduction.tex
many tweaks

@@
 and k-CFA~\cite{kcfa} fail to build a good call graph.
-To alleviate this problem, we present an algorithm to build reflection-aware call graph, and
+To alleviate this problem, we use an algorithm to build reflection-aware call graph, and
 also compare its usefulness with existing call graph construction algorithms in

### 2012-02-09 trunk/GUIErrorDetector/paper/evaluation.tex
some tweak on space

@@
 
-\begin{itemize}
+\begin{myindentpar}{-2mm}
+\begin{itemize}%\addtolength{\itemsep}{-0.5\baselineskip}
 \Item \textbf{SWT desktop applications.}
@@
 
+\vspace{0.5mm}
+\vspace{0.5mm}
+
 \Item \textbf{Eclipse plugins.}
@@
 EclipseRunner~\cite{eclipserunner} extends Eclipse's capability to run launch configurations.
+
+\vspace{0.5mm}
 
@@
 
-\smallstep
+\vspace{0.5mm}
 
@@
 \end{itemize}
+\end{myindentpar}
 
@@
 when  JVM fails to launch the mail composing window of the
-user default mail client (after a user clicks the "eMail Me" button).
+user default mail client.% (after a user clicks the "eMail Me" button).
 
@@
 those non-UI threads created before a GUI is launched.
-Second, our tool cannot compute call relationships
+Second, like many bug-finding techniques, our technique
+is neither sound nor complete. It may miss true positives due
+to the used graph search strategy, or
+issue false positives due to the conservative nature of
+a static analysis. Designing better call graph construction algorithms
+and graph search strategies may alleviate this limitation.
+Third, our tool cannot compute call relationships
 for inter-process communication between components. It also

### 2012-02-09 trunk/GUIErrorDetector/paper/evaluation.tex
Fix fonts on curly braces in tt font.

@@
 \begin{alltt}
-59.private void deleteBucket() \{
-60.    executor.execute(new Runnable() \{
-61.        public void run() \{
-62.            try \{
+59.private void deleteBucket() \ttlcb
+60.    executor.execute(new Runnable() \ttlcb
+61.        public void run() \ttlcb
+62.            try \ttlcb
 63.                controller.deleteCurrentBucket();
-64.            \} catch (Exception e) \{
+64.            {\ttrcb} catch (Exception e) \ttlcb
 65.                logger.info("Delete failed", e);
 66.                deleteError(); 
-67.            \}
-68.       \}
-69.    \});
-70.\}
+67.            \ttrcb
+68.       \ttrcb
+69.    \ttrcb);
+70.\ttrcb
 
-77.private void deleteError() \{
+77.private void deleteError() \ttlcb
 78.    String text = "Cannot delete folder .....";
@@
         String.format(text, controller.getSelectedBucketName())); 
-80.\}
+80.\ttrcb
 \smallstep
@@
 \begin{alltt} 
-179.private void initializeResourceChangeListener() \{
+179.private void initializeResourceChangeListener() \ttlcb
 180.  ResourcesPlugin.getWorkspace().addResourceChangeListener(
-        new IResourceChangeListener() \{
-181.      public void resourceChanged(IResourceChangeEvent event) \{
+        new IResourceChangeListener() \ttlcb
+181.      public void resourceChanged(IResourceChangeEvent event) \ttlcb
 182.        refresh();
-183.      \}
-184.  \}, IResourceChangeEvent.POST\_CHANGE);
-185.\}
+183.      \ttrcb
+184.  \ttrcb, IResourceChangeEvent.POST\_CHANGE);
+185.\ttrcb
 
-414.public void refresh() \{
+414.public void refresh() \ttlcb
 415.  getViewer().refresh();
-416.\}
+416.\ttrcb
 \end{alltt}
@@
 \begin{alltt}
-97.  public void setLatLong(int id, double d) \{
+97.  public void setLatLong(int id, double d) \ttlcb
 98.     TextView msgTextView = (TextView) activity.\textbf{findViewById}(id);
 99.     msgTextView.setText(LAT\_LONG\_FORMAT.format(d));
-100. \}
+100. \ttrcb
 \end{alltt}

### 2012-02-09 trunk/GUIErrorDetector/paper/introduction.tex
some tweak on space
Fix fonts on curly braces in tt font.

@@
 
-\smallstep
+\tinystep
 
@@
 consisting of numerous bug reports, forum posts, and mailing list threads on
-this problem. Eclipse, the IDE for Java development, is built on top of SWT.
+this problem. Eclipse, the IDE for Java development, is built on top of SWT\@.
 Searching for ``SWTException:Invalid thread access'' in Eclipse's bug repository
@@
 \begin{alltt}
-68.  public LayerView(Context context, LayerController controller) \{
+68.  public LayerView(Context context, LayerController controller) \ttlcb
 69.     super(context);
@@
         ...
-     \}
+     \ttrcb
 \end{alltt}
@@
 \begin{alltt}
-272. public void setRenderer(Renderer renderer) \{
+272. public void setRenderer(Renderer renderer) \ttlcb
         ...
@@
 283.    mGLThread.start();   
-     \}
+     \ttrcb
 \end{alltt}
@@
 \begin{alltt}
-220. public void onSurfaceChanged(GL10 gl, int width, int height) \{
+220. public void onSurfaceChanged(GL10 gl, int width, int height) \ttlcb
 221.    gl.glViewport(0, 0, width, height);
 222.    mView.setViewportSize(new IntSize(width, height));
-     \}
+     \ttrcb
 \end{alltt}
@@
 \begin{alltt}
-220. public void onSurfaceChanged(GL10 gl, int width, int height) \{
+220. public void onSurfaceChanged(GL10 gl, int width, int height) \ttlcb
 221.     gl.glViewport(0, 0, width, height);
@@
          \textbf{\ttrcb);}
-     \}
+     \ttrcb
 \end{alltt}

### 2012-02-09 GUIErrorDetector/paper/evaluation.tex
many small tweaks based on Hao Lu's comments

@@
 
+\begin{myindentpar}{-2mm}
 \begin{itemize}%\addtolength{\itemsep}{-0.5\baselineskip}
@@
 the given Sudoku is unsolvable; and the other one happens
-when  JVM fails to launch the mail composing window of the
-user default mail client (after a user clicks the "eMail Me" button).
+when  JVM fails to launch the %mail composing window of the
+user default mail client.% (after a user clicks the "eMail Me" button).
 
@@
 introducing imprecision. Although the error-revealing paths exist in
-less precise graphs, the impreicison prevents our algorithm finding them.
+less precise graphs, the impreicison prevents our algorithm from finding them.
 Figure~\ref{fig:ex} illustrates this point.
@@
 potential single-GUI-thread violations. However, other graph search strategies such as
-Depth-First Search (DFS) and exhaustive path search can also be employed. To
+DFS and exhaustive path search can also be employed. To
 understand trade-offs between using different search strategies, we 
@@
 is neither sound nor complete. It may miss true positives due
-to the graph search strategy the algorithm employs, or
-issue false positives because the conservative nature of
-a static analysis. Designing better call graph construction
-and search algorithm may alleviate this limitation.
+to the used graph search strategy, or
+issue false positives due to the conservative nature of
+a static analysis. Designing better call graph construction algorithms
+and graph search strategies may alleviate this limitation.
 Third, our tool cannot compute call relationships

### 2012-02-09 GUIErrorDetector/paper/implementation.tex
some tweak on space
many small tweaks based on Hao Lu's comments

@@
 \tinystep
+\tinystep
 \subsubsection{Eclipse plugin}
@@
 \smallstep
+\begin{myindentpar}{-2mm}
 
@@
 \end{itemize}
+\end{myindentpar}
 
+\tinystep
 \tinystep
@@
 A Swing application has a single main method, but contains three kinds of
-threads: \textit{initial thread} that executes initial application code from the main method,
+threads: the \textit{initial thread} that executes initial application code from the main method,
 the \textit{UI thread}, where all GUI manipulation code is executed,
@@
 
+\begin{myindentpar}{-2mm}
 \begin{itemize}
+\tinystep
 
@@
 
+\tinystep
 \subsubsection{Android}

### 2012-02-09 GUIErrorDetector/paper/technique.tex
some tweak on space
Fix fonts on curly braces in tt font.
many small tweaks based on Hao Lu's comments

@@
 exists a path from the non-UI thread's \CodeIn{start} method to any UI-accessing method
-without going through any safe UI method. }\vspace{2mm}
+without going through any safe UI method. }\vspace{1mm}
 
@@
 may invoke a UI-accessing method.
+
+\tinystep
 
@@
 nodes act as the sources in the main graph traversal.
-The algorithm uses BFS to search for reachable UI-accessing
+The algorithm uses Breadth-First Search (BFS) to search for reachable UI-accessing
 methods (lines 11 -- 25).
@@
 smaller error reports. However,
-other graph search strategies such as Depath-First Search (DFS) or
+other graph search strategies such as Depth-First Search (DFS) or
 exhaustive path search can also be employed. In our experiment (Section~\ref{sec:search}),
@@
 exhaustive path search.
+
+\tinystep
 
@@
 
-1. public class MyActivity extends Activity \{
+1. public class MyActivity extends Activity \ttlcb
 2.    @Override
-3.    public void onCreate(Bundle savedInstanceState) \{
+3.    public void onCreate(Bundle savedInstanceState) \ttlcb
 4.        super.onCreate(savedInstanceState);
@@
 6.        Button button = (Button) findViewById(R.id.\textbf{button\_id});
-7.        button.setOnClickListener(new Button.OnClickListener() \{
+7.        button.setOnClickListener(new Button.OnClickListener() \ttlcb
 8.            @Override
-9.            public void onClick(View v) \{
+9.            public void onClick(View v) \ttlcb
 10.               button.setText("Button Clicked.");
-11.           \}
-12.       \});
-13.   \}
-14. \}
+11.           \ttrcb
+12.       \ttrcb);
+13.   \ttrcb
+14. \ttrcb
 \end{alltt}
@@
 %\noindent 
-\CodeIn{@CalledByNativeMethods(callers=\{"native1", "native2"\})}
+\CodeIn{@CalledByNativeMethods(callers=\ttlcb"native1", "native2"\ttrcb)}
 
 %\noindent
-\CodeIn{public void javaMethod() \{ ... \}}
+\CodeIn{public void javaMethod() \ttlcb\ ... \ttrcb}
 
@@
 %\item
-\textbf{2. Filter Reports With User-Annotated Methods}. Users are
+\textbf{2. Filter Reports with User-Annotated Methods}. Users are
 permitted to explicitly annotate project-specific methods
@@
 can be safely removed. In our experiments, we produced a list of \filternum
-annotated methods for two subjects because they are using a customized
+annotated methods for two subjects because they use a customized
 pattern to interact with the GUI framework.
@@
 
-\textbf{4. Filter Report With the Same Head Methods from the Entry Node to \CodeIn{Thread.start()}}. A method can call
+\textbf{4. Filter Report with the Same Head Methods from the Entry Node to \CodeIn{Thread.start()}}. A method can call
 multiple methods that access GUI objects, such as:
@@
 \begin{alltt}
-     public void m() \{
+     public void m() \ttlcb
          accessUIObject1();
          accessUIObject2();
-     \}
+     \ttrcb
 \end{alltt}
@@
 %\item
-\textbf{5. Filter Report With the Same Tail Methods from \CodeIn{Thread}.
+\textbf{5. Filter Report with the Same Tail Methods from \CodeIn{Thread}.
 \CodeIn{start()}
@@
 work remarkably well by reducing over 99\% of the reported warnings. In addition,
-we also found that only using sound filters was not sufficient. The overwhelming
-number of warnings after applied sound filters motivated the use
+we also found that using sound filters alone was insufficient. The overwhelming
+number of warnings after sound filters were applied motivated the use
 of heuristic filters.

### 2012-02-09 trunk/GUIErrorDetector/paper/introduction.tex
many small tweaks based on Hao Lu's comments

@@
 Our static analysis is independent of the call graph construction algorithm.
-Given a sound call graph, our analysis is sound in that it does
-not miss true positives. GUI applications tend to use reflection, and
+%Given a sound call graph, our analysis is sound in that it does
+%not miss true positives.
+However, modern GUI applications tend to use reflection, and
 in the presence of reflection, existing call graph construction algorithms such as RTA~\cite{rta}

### 2012-02-09 GUIErrorDetector/paper/abstract.tex
revise abstract, and introduction

@@
 call graph for some modern GUI applications, because of heavy use of reflection.
-Thus, we present a method to build reflection-aware call graphs.
+Thus, our technique builds reflection-aware call graphs.
 
@@
 platforms: SWT, the Eclipse plugin development framework, Swing, and
-Android. In an evaluation on 9 programs comprising 67000 LOC, our technique
-found both previously-known and unknown errors.
+Android. In an evaluation on \subnum programs comprising \totaloc LOC, our technique
+found 5 previously-known errors and 7 new ones.
 

### 2012-02-09 GUIErrorDetector/paper/introduction.tex
substantile changes
revise abstract, and introduction

@@
 even before the lengthy task completes. However, the use of multiple threads
-enables new types of errors which may compromise robustness, possible.
-We now discuss a programming rule for multithreaded GUIs, the consequence
+enables new types of errors that may compromise robustness.
+We now discuss a standard programming rule for multithreaded GUIs, the consequences
 of violating it, and a technique for statically detecting such violations.
@@
 
-The single-GUI-thread rule can be easily violated since a spawned non-UI thread often needs to update
+The single-GUI-thread rule can be easily violated; since a spawned non-UI thread often needs to update
 the GUI  after its  task is finished.
-In practice, invalid thread access errors are \textit{frequent}, \textit{severe}, and \textit{hard} to debug.
+In practice, invalid thread access errors are \textit{frequent}, \textit{severe}, and \textit{hard to debug}.
 %and \textit{difficult to avoid}.
@@
 Take the popular Standard Widget Toolkit (SWT) GUI framework as an example. 
-The invalid thread access error is one of the top 3 bugs in developing a SWT application, and is
-the source of many relevant concurrency bugs~\cite{top3bugs}.
+Invalid thread access is one of the top 3 bugs in developing a SWT application, and is
+the source of many concurrency bugs~\cite{top3bugs}.
 A Google search for ``SWTException:Invalid thread access''  returns over 11,800 entries,
 consisting of numerous bug reports, forum posts, and mailing list threads on
-this problem. Eclipse, the IDE for Java development, is built on top of SWT.
+this problem. Eclipse, the IDE for Java development, is built on top of SWT\@.
 Searching for ``SWTException:Invalid thread access'' in Eclipse's bug repository
@@
 We manually studied all 156 distinct \textit{confirmed} bug reports, and 
-found this error has been reported in at least 20 distinct Eclipse projects
+found this error has been confirmed in at least 20 distinct Eclipse projects
 and 40 distinct Eclipse components. Even after over 10 years of active development,
-a recent release of Eclipse still contains this error (bug id: 333533, reported in 01/2011).
+a recent release of Eclipse still contains this error (bug id: 333533, reported in January 2011).
  In addition, the invalid thread access error
-is severe. It is user-perceivable; it cannot be recovered by the program itself,
+is severe. It is user-perceivable, it cannot be recovered by the program itself,
 and it often terminates the whole application. In many circumstances as described in the bug reports,
-users can only restart the application to recover from the error.
+users must restart the application to recover from the error.
 Furthermore, many reported  errors are non-trivial to diagnose and fix.
@@
 UI interactions that can trigger the bug;  it took developers 2 years
-to fix bug 51757 and verify the patch.
+to fix Eclipse bug 51757 and verify the patch.
 
@@
 \begin{alltt}
-220. public void onSurfaceChanged(GL10 gl, int width, int height) \{
+220. public void onSurfaceChanged(GL10 gl, int width, int height) \ttlcb
 221.    gl.glViewport(0, 0, width, height);
 222.    mView.setViewportSize(new IntSize(width, height));
-     \}
+     \ttrcb
 \end{alltt}
 \end{CodeOut}
+\tinystep
 \vspace*{-3.0ex} \Caption{{\label{fig:androiderror} 
@@
 To ensure that GUIs behave correctly, developers must prevent or detect invalid thread
-access errors. Currently, no effective techniques exist. %must be developed.% to alleviate this problem.
+access errors. Current techniques are not effective. %must be developed.% to alleviate this problem.
 
@@
 a different state, and each GUI event may need to be evaluated in all of
-these states. A well-developed software system like Eclipse
-often has a well-designed test suite that achieves fairly high statement coverage;
+these states. A  software system like Eclipse
+often has a test suite that achieves fairly high statement coverage,
 but many paths executed by bug-triggering UI sequences are still not covered.
@@
 Stylized coding patterns are also inadequate. One possible rule is to always
-access GUI objects via asynchronized message passing, to ensure a GUI object is accessed in
+access GUI objects via asynchronous message passing, to ensure a GUI object is accessed in
 the UI thread. For example, a developer could have prevented the bug in Figure~\ref{fig:androiderror}
-by wrapping line 222 inside a \CodeIn{post} message passing method\footnote{The
+by wrapping line 222 inside a \CodeIn{post} message-passing method\footnote{The
 \CodeIn{post} method in class \CodeIn{android.widget.View} is a
@@
 8 more methods in the call chain, shown as
-\CodeIn{\small{...}} above, are omitted for brevity.
+``\CodeIn{\small{...}}" above, are omitted for brevity.
 }} %\vspace{-5mm}
@@
 Our static analysis is independent of the call graph construction algorithm.
-Given a sound call graph, our analysis is sound in that it does
-not miss true positives. GUI applications tend to use reflection, and
+%Given a sound call graph, our analysis is sound in that it does
+%not miss true positives.
+However, modern GUI applications tend to use reflection, and
 in the presence of reflection, existing call graph construction algorithms such as RTA~\cite{rta}
 and k-CFA~\cite{kcfa} fail to build a good call graph.
-To alleviate this problem, we present an algorithm to build reflection-aware call graph, and
+To alleviate this problem, we use an algorithm to build reflection-aware call graph, and
 also compare its usefulness with existing call graph construction algorithms in
@@
 
+\tinystep
+
 \begin{itemize}

### 2012-02-09 GUIErrorDetector/paper/technique.tex
Small changes: add headings

@@
 
+\noindent  {\textsc{\textbf{Problem.}}}
 At a high level, to detect an invalid thread access error, an analysis needs to track all

### 2012-02-10 trunk/GUIErrorDetector/paper/introduction.tex
address the first round of comments

@@
 Take the popular Standard Widget Toolkit (SWT) GUI framework as an example. 
-The invalid thread access error is one of the top 3 bugs in developing a SWT application, and is
-the source of many relevant concurrency bugs~\cite{top3bugs}.
+Invalid thread access is one of the top 3 bugs in developing a SWT application, and is
+the source of many concurrency bugs~\cite{top3bugs}.
 A Google search for ``SWTException:Invalid thread access''  returns over 11,800 entries,
@@
 
-Such an approach is desirable for accesses from non-UI threads, but it is unnecessary
-and dangerous for accesses from the UI thread. Asynchronized message passing offers
-no timing guarantee, so a GUI object may have already been
-disposed before the message sent to it arrives, causing other bugs. 
+Such an approach is desirable for accesses from non-UI threads, but it is unnecessary.
 In our evaluation on real-world programs, we found a simple analysis that
@@
 an unacceptable number of warnings. %false positives and redundant warnings.
+Furthermore, this approach is dangerous for accesses from the UI thread. Asynchronized message passing offers
+no timing guarantee, so a GUI object may have already been
+disposed before the message sent to it arrives, causing other bugs.
 
@@
 
+\smallskip
+
+\textbf{Our approach: static analysis.}
 This paper uses static analysis to find potential GUI errors.
@@
 executing the code, and without the need for a test suite.
-Second, a static analysis can verify the code: if it
+Second, a static analysis can verify the code: if a sound static analysis
 reports no warnings, the code is guaranteed to be bug-free.
@@
 in the presence of reflection, existing call graph construction algorithms such as RTA~\cite{rta}
-and k-CFA~\cite{kcfa} fail to build a good call graph.
-To alleviate this problem, we use an algorithm to build reflection-aware call graph, and
+and k-CFA~\cite{kcfa} fail to build a complete call graph.
+To alleviate this problem, we present an algorithm to build a reflection-aware call graph, and
 also compare its usefulness with existing call graph construction algorithms in
-our experiments. Static analysis may report false positives due to its
+our experiments.
+
+Static analysis may report false positives due to its
 conservative nature, or multiple warnings that actually correspond
@@
  of error filters to remove likely false positives and redundant warnings.
+The filters introduce potential unsoundness to our algorithm, but in practice
+they work well and make our technique usable.
 
@@
 entry points}. Thus, our implementation is parameterized with respect to
-those framework-specific parts.
+those framework-specific parts (see Section~\ref{sec:platforms}).
 
-Our tool works in a fully automatic, push-button manner,
+Our tool works in an automatic manner,
 and scales to realistic programs.
@@
 that: our technique is effective (it found \bugs real-world errors
-from four supported frameworks and produced only \falses false positive warnings);
+ and produced only \falses false positive warnings);
 our reflection-aware call graph construction algorithm helps in
@@
 In addition, we use a reflection-aware
-call graph construction algorithm. (Section~\ref{sec:technique}).
+call graph construction algorithm (Section~\ref{sec:technique}).
 

### 2012-02-10 trunk/GUIErrorDetector/paper/technique.tex
address the first round of comments

@@
 
-We first give a high-level formulation of the problem, then present
-the error detection algorithm. Finally, we show how to 
-construct a reflection-aware call graph and filter the error reports.
+We first give a high-level formulation of the problem (Section~\ref{sec:probl}), then present
+the error detection algorithm (Section~\ref{sec:algorithm}). Finally, we show how to 
+construct a reflection-aware call graph (Section~\ref{sec:cgcon}) and filter the error reports (Section~\ref{sec:heuristic}).
 
 \subsection{Problem Formulation}
+\label{sec:probl}
 
-This section formulates the problem. We first define the
-notations of \textit{UI thread}, \textit{non-UI threads},
+This section formulates the problem. We first define 
+\textit{UI thread}, \textit{non-UI threads},
 \textit{UI-accessing methods},
@@
 GUI initialization. After the GUI becomes visible, the UI thread
-takes charge of the application to handle events from the GUI,
-and spawns new threads to process lengthy operations in the background. }\vspace{1mm}
+takes charge of the application to handle events from the GUI.
+It spawns new threads to process lengthy operations in the background. }\vspace{1mm}
 
@@
 before the UI thread has been initialized. That is, all post-initialization
-GUI work naturally occurs in the UI thread. Once the GUI is visible, the
+GUI work occurs in the UI thread. Once the GUI is visible, the
 application is driven by events, which are always handled in the UI thread.
@@
 immediately apparent and the whole application may abort even before the
-GUI is visible. This is highly unlikely for realistic GUI
+GUI is visible. This is highly unlikely for fielded GUI
 applications.
@@
 
-\noindent {\textsc{\textbf{Definition 3 (UI-Accessing Methods).}}} { A method
+\noindent {\textsc{\textbf{Definition 3 (UI-Accessing Method).}}} { A method
 whose execution may read or write a UI object is called a UI-accessing method.}\vspace{1mm}
 
-\noindent  {\textsc{\textbf{Definition 4 (Safe UI Methods).}}} {GUI frameworks that
+\noindent  {\textsc{\textbf{Definition 4 (Safe UI Method).}}} {GUI frameworks that
 adopt the single-GUI-thread rule must provide methods to permit non-UI threads
@@
 
-\noindent  {\textsc{\textbf{Definition 5 (Invalid Thread Access).}}} {An invalid
-thread access error occurs when the UI thread may spawn a non-UI thread, and there
+\noindent  {\textsc{\textbf{Definition 5 (Invalid Thread Access).}}} {An invalid-thread-access error occurs when the UI thread may spawn a non-UI thread, and there
 exists a path from the non-UI thread's \CodeIn{start} method to any UI-accessing method
-without going through any safe UI method. }\vspace{2mm}
+without going through any safe UI method. }\vspace{1mm}
 
+\noindent  {\textsc{\textbf{Problem.}}}
 At a high level, to detect an invalid thread access error, an analysis needs to track all
@@
 
+\tinystep
+
 \subsection{Error Detection Algorithm}
+\label{sec:algorithm}
 
-The algorithm for detecting potential invalid thread access errors
-is shown in Figure~\ref{fig:detectalgorithm}. Our algorithm uses a
+Figure~\ref{fig:detectalgorithm} shows the algorithm for detecting
+potential invalid thread access errors. Our algorithm uses a
 static call graph as the program representation for a multithreaded
@@
 dynamic call graph of every possible execution. 
-In an object-oriented programming language like
-Java, a method is the basic logic unit in a program. Reporting
-potential errors at the method level can be sufficient in most cases.
+Our algorithm's reports are in terms of methods, as shown in Figure~\ref{fig:report}.
+
+%In an object-oriented programming language like
+%Java, a method is the basic logic unit in a program. Reporting
+%potential errors at the method level can be sufficient in most cases.
 %Thus, we believe using the call graph is well suited for this problem while
@@
 then specifies entry nodes, UI-accessing nodes, and safe UI nodes
-for it on line 3, 4, and 5, respectively. Lines 3--5 are GUI framework-specific.
+for it on lines 3, 4, and 5, respectively. Lines 3 -- 5 are GUI framework-specific.
 As an example, for a SWT desktop application, the entry nodes include
@@
 and safe UI methods include two SWT helper methods \CodeIn{Display.asyncExec}  and
-\CodeIn{Display.syncExec} for message passing. The detailed instantiation
-for each supported framework is explained in Section~\ref{sec:platforms}.
+\CodeIn{Display.syncExec} for message passing. Section~\ref{sec:platforms}
+explains the detailed instantiation for each supported framework.
 
@@
 nodes act as the sources in the main graph traversal.
-The algorithm uses BFS to search for reachable UI-accessing
-methods (lines 11 -- 25).
+The algorithm uses Breadth-First Search (BFS) to search for reachable UI-accessing
+methods (lines 9 -- 23).
 The algorithm stops the traversal if it reaches a UI-accessing
-method (lines 17 -- 19) or a safe UI method (lines 20, 21).
+method (lines 15 -- 17) or a safe UI method (lines 18, 19).
 %Specifically, it uses a queue to keep track of the nodes to be visited (line 7),
@@
 includes the method call chain from the entry node to the UI-accessing node
-as the error report. For brevity, we do not show the data structures that store
+as the error report. For brevity, the algorithm does not show the data structures that store
 the current call chain.
-Figure~\ref{fig:report} shows a method call chain from the entry
+The error report in Figure~\ref{fig:report} displays a method call chain from the entry
 node \CodeIn{LayerView.<init>} to the UI-accessing node \CodeIn{ViewRoot}.\CodeIn{checkThread}.
@@
 \FOR{each $\mathit{entryNode}$ in $\mathit{entryNodes}$}
-\STATE $\mathit{threadStarts}$ $\leftarrow$ getReachableStarts($\mathit{entryNode}$)\\
-\COMMENT{keep the nodes to be visited next in a worklist}
-\STATE $\mathit{worklist}$ $\leftarrow$ an empty queue\\
-\STATE $\mathit{worklist}$.enqueueAll($\mathit{threadStarts}$)
+\STATE $\mathit{worklist}$ $\leftarrow$ getReachableStarts($\mathit{entryNode}$)
 \STATE $\mathit{visited}$ $\leftarrow$ $\emptyset$
-\WHILE{$\mathit{worklist}$.isNotEmpty()}
+\WHILE{$\mathit{worklist}$ $\neq$ $\emptyset$}
 \STATE $\mathit{node}$ $\leftarrow$ $\mathit{worklist}$.dequeue()
@@
 Any call graph construction algorithm can be used (line 2). The algorithm
-is parameterized by the three methods in lines 3--5 which are specific to each GUI framework
+is parameterized by the three methods in lines 3 -- 5 which are specific to each GUI framework
  as described in Section~\ref{sec:platforms}.
@@
 
+\tinystep
+
 \subsection{Call Graph Construction}
+\label{sec:cgcon}
 
-Given a sound call graph, our algorithm is sound in that it does not
-miss true positives. We note, however, that computing a sound
+%Given a sound call graph, our algorithm is sound in that it does not
+%miss true positives. We note, however, 
+For some modern GUI applications, computing a good
 call graph in the presence of reflection and native methods is non-trivial. 
-To alleviate this problem, we next proposed a reflection-aware call graph
+To alleviate this problem, we next present a reflection-aware call graph
 construction algorithm in Section~\ref{sec:cg} and annotation support
@@
 \begin{algorithmic}[1]
-\FOR{each $\mathit{statement}$ in $\mathit{P}$}
-\IF{isReflectionCall($statement$)}
-\STATE $\mathit{objectSet}$ $\leftarrow$ getAllObjectsThatMaybeCreated($\mathit{statement}$)
-\STATE $\mathit{newStmt}$ $\leftarrow$ createObjectCreationStatement($\mathit{objectSet}$)
-\STATE replace $\mathit{statement}$ with $\mathit{newStmt}$
+\FOR{each $\mathit{expression}$ in $\mathit{P}$}
+\IF{isReflectionCall($expression$)}
+\STATE $\mathit{objectSet}$ $\leftarrow$ getAllObjectsThatMaybeCreated($\mathit{expression}$)
+\STATE $\mathit{newExpr}$ $\leftarrow$ createObjectCreationExpression($\mathit{objectSet}$)
+\STATE replace $\mathit{expression}$ with $\mathit{newExpr}$
 \ENDIF
@@
 \caption{A reflection-aware call graph construction algorithm. Lines
-1--7 are a simple program transformation to replace reflection calls
+1 -- 7 are a simple program transformation to replace reflection calls
 with object creations, and line 8 builds the call graph using
@@
 object by looking up its id declared in the associated XML file. When this button
-is clicked, its event handling code (lines 9--11) updates the text.
+is clicked, its event handling code (lines 9 -- 11) updates the text.
 
@@
 fail to conclude that the variable \CodeIn{button} declared on line 6
-points to a \textit{non-null} \CodeIn{Button} object due to its limitation in handling the
-reflection call \CodeIn{findViewById}, and exclude the edge
-corresponding to the \CodeIn{setText} method call on line 10 in the resulting call graph.
+points to a \textit{non-null} \CodeIn{Button} object due to their limitations in handling the
+reflection call \CodeIn{findViewById}. The resulting call graph
+omits the edge corresponding to the \CodeIn{setText} method call on line 10.
 
@@
 The basic idea is to replace reflection calls with explicit object
-creation statements, pretending that the corresponding concrete object
+creation expressions, pretending that the corresponding concrete object
 has been created.  The algorithm is shown in Figure~\ref{fig:cgalgorithm}.
 It consists of two steps. The first step (lines 1 -- 7) is a simple program
-transformation to replace reflection calls with object creation statements, and
+transformation to replace reflection calls with object creation expressions, and
 the second step (line 8) uses an existing call graph construction algorithm
@@
 determines a set of possible objects that might be created.
-After that, the algorithm creates a statement that non-deterministically
+After that, the algorithm creates an expression that non-deterministically
 returns a new object from the object set.
@@
 the predicate isReflectionCall on line 2 returns true
-if the $statement$ is a \CodeIn{findViewById(id)} method call, and the method
+if the $expression$ is a \CodeIn{findViewById(id)} method call, and the method
 getAllObjectsThatMaybeCreated on line 3 parses the associated XML configuration
@@
 replaces the reflection call
-with an explicit object creation statement: \CodeIn{new Button(null)}.
+with an explicit object creation expression: \CodeIn{new Button(null)}.
 After that, the algorithm employs existing call graph construction

### 2012-02-10 GUIErrorDetector/paper/abstract.tex
address the first round of comments

@@
 We implemented our technique and instantiated it for four popular Java GUI
-platforms: SWT, the Eclipse plugin development framework, Swing, and
+frameworks: SWT, the Eclipse plugin development framework, Swing, and
 Android. In an evaluation on \subnum programs comprising \totaloc LOC, our technique

### 2012-02-10 GUIErrorDetector/paper/evaluation.tex
address the first round of comments

@@
  \hline
- SGTPuzzler & 13631 / 13865&  12 / 16 &  0 / 0 & 9546 / 9682& 4 / 4& 1 / 1 & 35198 / 35756 & 1 / 1  & 1 / 1& 104 \\
+ SGTPuzzler & 13631 / 13865&  1 / 16 &  0 / 0 & 9546 / 9682& 0 / 4& 0 / 1 & 35198 / 35756 & 0 / 1  & 0 / 1& 104 \\
  \hline
@@
 \hline
- Total & 199161 / 199724 &  188 / 251 & 5 / 5 & 149441 / 153054& 137 / 137& 6 / 6 & 577821 / 652756& 22 / 22 & 11 / 12 & 6542\\
+ Total & 199161 / 199724 &  177 / 251 & 5 / 5 & 149441 / 153054& 133 / 137& 6 / 7 & 577821 / 652756& 21 / 22 & 10 / 12 & 6542\\
 \hline
@@
 using standard call graph construction algorithm and the reflection-aware
-call graph construction algorithm. The \newbugs errors found in VirgoFTP, FileBunker, ArecaBackup
+call graph construction algorithm (with \annotationnum native method annotations
+for SGTPuzzler). The \newbugs errors found in VirgoFTP, FileBunker, ArecaBackup
 S3dropbox, and SudokuSolver are previously  unknown. As a comparison, the
@@
 We submitted all \newbugs new errors
-to the subject developers. As of Feb 2012, 1 error in S3dropbox has been confirmed,
+to the subject developers. As of February 2012, 1 error in S3dropbox has been confirmed,
 4 errors have been reproduced and validated in our own experimental environment, and
@@
 used in our experiments. As shown in Table~\ref{table:results},  1-CFA found
-more errors with fewer false positive warnings than the other two algorithms. This
+more errors than the other two algorithms. This
 is because RTA and 0-CFA do not consider the calling context when
@@
 
-The results in Table~\ref{table:results} also show that using a reflection-aware
-call graph construction algorithm helps in finding errors in Android
-applications. One error from the MyTracks Android application
-can only be found by using the reflection-aware call graph construction algorithm.
+The results in Table~\ref{table:results} also show that using the
+call graph construction algorithm in Section~\ref{sec:cgcon}
+helps in finding errors in Android applications. One error from the MyTracks Android application
+can only be found by using the reflection-aware call graph construction algorithm (Section~\ref{sec:cg}).
 This is because the error-related GUI object (\CodeIn{msgTextView}) in MyTracks is created
@@
 
-Errors in the other two Android applications (Fennec and SGTPuzzler)
+Another error in SGTPuzzler is only reported when adding \annotationnum native method
+annotations (Section~\ref{sec:annotation}). The error in Fennec
 can be found by using a standard call graph construction algorithm.
@@
 The first variant uses DFS for graph traversal by changing
-line 8 in Figure~\ref{fig:detectalgorithm} to:
-$\mathit{worklist}$ $\leftarrow$ $\mathit{an}$ $\mathit{empty}$ $\mathit{stack}$,
-and changing queue operations (\CodeIn{enqueueAll}, and \CodeIn{dequeue}
-on lines 9, 12, and
-23 in Figure~\ref{fig:detectalgorithm}, respectively)
-to the corresponding statck operations (\CodeIn{pushAll}, and \CodeIn{pop}).
+the data structure of $\mathit{worklist}$ on line 7 in Figure~\ref{fig:detectalgorithm} to
+a stack, and changing queue operations (\CodeIn{dequeue}, and \CodeIn{enqueueAll}
+on lines 10, and 21 in Figure~\ref{fig:detectalgorithm}, respectively)
+to the corresponding statck operations (\CodeIn{pop}, and \CodeIn{pushAll}).
 This variant found 11 errors in total and missed 1 error in the FileBunker subject.

### 2012-02-10 GUIErrorDetector/paper/evaluation.tex
Address the second round of comments

@@
 of our approach in detecting real errors in multithreaded GUI applications, to 
-compare the reflection-aware call graph construction algorithm
+compare our call graph construction algorithm
 with existing ones, and to evaluate the usefulness of the proposed 
@@
 
-We use a set of open-source projects from Sourceforge, Google code,
+We used a set of open-source projects from Sourceforge, Google code,
 and the Eclipse plugin
@@
 Third, the subject must have undergone at least two years of active development,
-and is listed in the first 3 result pages based on popularity. This permits us
+and it is listed in the first 3 result pages based on popularity. This permits us
 to exclude immature subjects that may contain obvious errors.
 
-We chose subjects belonging to various categories from those subjects satisfying
-the above criteria. The subjects used in our experiment are shown in Table~\ref{table:subjects},
-which include end-user applications, programming tools, and games.
+The subjects used in our experiment (Table~\ref{table:subjects})
+include end-user applications, programming tools, and games.
 
@@
 %VirgoFTP~\cite{virgo} and FileBunker~\cite{filebunker} are two useful SWT desktop applications.
-VirgoFTP~\cite{virgo} implements a simple FTP client based on Java and SWT UI library.
-FileBunker~\cite{filebunker} is a file backup application which uses one or more GMail
+VirgoFTP~\cite{virgo} implements a simple FTP client based on Java and the SWT UI library.
+FileBunker~\cite{filebunker} is a file backup application that uses one or more GMail
 accounts as its backup repository. ArecaBackup~\cite{areca} offers a local
@@
 HudsonEclipse~\cite{hudson} monitors Hudson build status from Eclipse.
-EclipseRunner~\cite{eclipserunner} extends Eclipse's capability to run launch configurations.
+EclipseRunner~\cite{eclipserunner} extends Eclipse's capability of running launch configurations.
 
@@
 to drag and drop files to their Amazon S3 accounts. SudokuSolver~\cite{sudokusolver}
-computes Sudoku solutions efficiently using mutlithreading execution.
+computes Sudoku solutions efficiently using mutlithreaded execution.
 
@@
 each call graph construction algorithm on three Android applications, we
-used two configurations: with and without the reflection-aware algorithm 
-(Section~\ref{sec:cg}).  We did not use more expensive algorithms like $k$-CFA ($k >$ 1),
-because they can not scale to our subject programs.
+used two configurations: with and without our enhancements
+(Section~\ref{sec:cgcon}).  We did not use more expensive algorithms like $k$-CFA ($k >$ 1),
+because they do not scale to our subject programs.
 
@@
 Only SGTPuzzler uses native methods to interact with
-the underlying operating system. Thus, we manually checked the possible
+the underlying operating system. For it, we manually checked the possible
 Java methods that a native method may call, and then added \annotationnum \CodeIn{@CalledByNativeMethods}
@@
 %message passing. 
-Thus, we add \filternum user-defined filters for these two subjects.
+We added \filternum user-defined filters for these two subjects.
 %to indicate
@@
 
-For each output
-warning, we manually determined its validity by either searching the
+For all \subnum programs, we manually determined validity of each output warning
+by either searching the
 bug repository to check whether the same error has been reported before,
@@
 call graph algorithm, our tool issued 22 warnings, among
-which \bugs warnings reveal \bugs distinct errors (\newbugs are previously unknown),
+which \bugs warnings reveal \bugs distinct errors (\newbugs were previously unknown),
 2 warnings are false positives, and the remaining 8 warnings
@@
 4 errors have been reproduced and validated in our own experimental environment, and
-2 errors in FileBunker and ArecaBackup had not been verified by developers yet.
+2 errors in FileBunker and ArecaBackup had not yet been verified by developers.
 
@@
 actions for UI interaction are encapsulated into a \CodeIn{Worker} interface),
-but they still overlooked  the error our tool found.
+but the developers still overlooked  the error our tool found.
 Another reason they overlooked this violation is because some GUI frameworks like Swing
-do not provide any run-time checks for invalid thread accesses. Swing
-GUI might not exhibit user-visible faults on many erreoneous executions.
+do not provide any run-time checks for invalid thread accesses. The Swing
+GUI does not exhibit user-visible faults on some erreoneous executions.
 However, as clearly stated in the official documentation~\cite{swing}, %Swing is a single-GUI-threaded GUI toolkit and

### 2012-02-10 GUIErrorDetector/paper/implementation.tex
Address the second round of comments

@@
 \item \textbf{UI-accessing nodes: } the \CodeIn{Widget.checkWidget}
-and \CodeIn{Display.} \CodeIn{checkDevice} methods. SWT uses the above
-two methods to explicitly check whether the current thread is a UI thread,
-and throw a \CodeIn{RuntimeException} if the checking fails.
-%thread accesses at runtime.
-%Any methods for manipulating GUIs object must call (one of) these two methods
-% to determine whether the current thread is the UI thread or not.
+and \CodeIn{Display.} \CodeIn{checkDevice} methods. SWT performs
+runtime checking before accessing a GUI object via these methods.
+If the current thread is a non-UI thread, the \CodeIn{Widget.checkWidget}
+and \CodeIn{Display.checkDevice} methods throw a \CodeIn{RuntimeException}.
+
 \smallstep
@@
 After a Swing program starts, its initial thread exits and the UI thread takes charge
-of the application and starts to execute all event-handling code or spawns new worker threads. 
+of the application and starts to execute event-handling code or spawn new worker threads. 
 We instantiated our technique for Swing as follows:
@@
 \item \textbf{Safe UI methods: } 
-\CodeIn{SwingUtilities.}\CodeIn{invokeLater} and \CodeIn{Swing-\\Utilities.invokeAndWait} that execute code on the UI thread.
+\CodeIn{SwingUtilities.}\CodeIn{invokeLater} and \CodeIn{Swing-\\Utilities.invokeAndWait}, which execute code on the UI thread.
 
@@
 \item \textbf{Safe UI methods: } \CodeIn{View.post}
-and \CodeIn{View.postDelay} that execute code on the UI thread.
+and \CodeIn{View.postDelay}, which execute code on the UI thread.
 
@@
  algorithm (Section~\ref{sec:cg}) using WALA's \textit{bypass logic}.
-Unlike existing tools~\cite{Payet:2011:SAA:2032266.2032299}, our tool
+Unlike other tools~\cite{Payet:2011:SAA:2032266.2032299}, our tool
 does not require a separate pass for program instrumentation; instead, it

### 2012-02-10 GUIErrorDetector/paper/technique.tex
Address the second round of comments

@@
 
-\noindent  {\textsc{\textbf{Definition 5 (Invalid Thread Access).}}} {An invalid
-thread access error occurs when the UI thread may spawn a non-UI thread, and there
+\noindent  {\textsc{\textbf{Definition 5 (Invalid Thread Access).}}} {An invalid-thread-access error occurs when the UI thread may spawn a non-UI thread, and there
 exists a path from the non-UI thread's \CodeIn{start} method to any UI-accessing method
@@
 \subsection{Error Detection Algorithm}
+\label{sec:algorithm}
 
-The algorithm for detecting potential invalid thread access errors
-is shown in Figure~\ref{fig:detectalgorithm}. Our algorithm uses a
+Figure~\ref{fig:detectalgorithm} shows the algorithm for detecting
+potential invalid thread access errors. Our algorithm uses a
 static call graph as the program representation for a multithreaded
@@
 The algorithm uses Breadth-First Search (BFS) to search for reachable UI-accessing
-methods (lines 11 -- 25).
+methods (lines 9 -- 23).
 The algorithm stops the traversal if it reaches a UI-accessing
-method (lines 17 -- 19) or a safe UI method (lines 20, 21).
+method (lines 15 -- 17) or a safe UI method (lines 18, 19).
 %Specifically, it uses a queue to keep track of the nodes to be visited (line 7),
@@
 \subsection{Call Graph Construction}
+\label{sec:cgcon}
 
@@
 to include the call edge \CodeIn{setText} in the resulting graph.
-
-As demonstrated in our experiments, using this reflection-aware call
-graph construction algorithm helps in detecting errors
-in Android applications (Section~\ref{sec:reflectionaware}).
 
@@
 Adding annotations for native methods is optional and requires manual effort.
-In our experiments, 1 out of \subnum programs uses native methods. We manually
+In our experiments, 1 out of \subnum programs (SGTPuzzler) uses native methods. We manually
 searched the Java source files to find all native methods,
@@
 is only reported when using the user-provided annotations.
+
+As demonstrated in our experiments, using our call
+graph construction algorithm helps in detecting errors
+in Android applications (Section~\ref{sec:reflectionaware}).
 
@@
 The first 2 filters are sound in that they will not filter real bugs, and
-other 3 filters are based on heuristics. Orthogonally, filters 2
+the other 3 filters are based on heuristics. Orthogonally, filters 2
 and 3 are for eliminating false positives, and filters 1, 4, and 5
@@
 chain can lexically subsume another one. For example, suppose that two
-reported method call chains: \CodeIn{a()} $\rightarrow$ \CodeIn{b()}
+reported method call chains; \CodeIn{a()} $\rightarrow$ \CodeIn{b()}
 $\rightarrow$ \CodeIn{c()} and 
-\CodeIn{d()} $\rightarrow$ \CodeIn{a()} $\rightarrow$ \CodeIn{b()} $\rightarrow$ \CodeIn{c()}
+\CodeIn{d()} $\rightarrow$ \CodeIn{a()} $\rightarrow$ \CodeIn{b()} $\rightarrow$ \CodeIn{c()},
 both lead to a potential error, since $\CodeIn{d()}$ and \CodeIn{a()}
-are two distinct entry methods. The second call chain should
-be removed and would not reduce the error detection capability, since
+are two distinct entry methods. The second call chain can
+be removed without reducing the error detection capability, since
 the first chain reveals the same error and is shorter 
@@
 can be safely removed. In our experiments, we produced a list of \filternum
-annotated methods for two subjects because they use a customized
+annotated methods for two subjects (Fennec and MyTracks) because they use a customized
 pattern to interact with the GUI framework.
@@
 programs on different GUI frameworks and that we believed would be generally useful.
-We did this only between experiments rather than biasing experiments by tuning
-our tool to specific programs.
+%We did this only between experiments rather than biasing experiments by tuning
+%our tool to specific programs.
 
@@
 multiple methods that access GUI objects, such as:
-\vspace{-2mm}
+\vspace{-1mm}
 \begin{CodeOut}
@@
 
-In fact, these two chains may have the same error root: knowning that
+In fact, these two chains may have the same error root cause: knowing that
 method \CodeIn{m()} is called by a non-UI thread is sufficient to understand
@@
 to the UI-accessing Method}. A method
-can have multiple callers, so that method call chains with the same tail are likely
+can have multiple callers, so method call chains with the same tail are likely
 to just represent different ways to trigger the same error. This filter compares 

### 2012-02-10 GUIErrorDetector/paper/related.tex
more tweaks

@@
 
+\tinystep
 \subsection{Analysis and Testing for GUI Applications}
+%\vspace{1mm}
 
+%\noindent \textit{\textbf{Analysis and Testing for GUI Applications}}
 Automated GUI testing is a challenging tasks~\cite{Bertolino:2007:STR:1253532.1254712,
 Harrold:2000:TR:336512.336532}.
- Many GUI analysis and testing techniques have been proposed in the past decade; some have been
-implemented as tools and adopted by practitioners. Existing techniques automate
+ Many GUI analysis and testing techniques have been proposed in the past decade.
+Existing techniques automate
 some aspect(s) of GUI testing including model creation
@@
 %needs to be specified manually as a labeled transition system. 
-Guitar~\cite{YuanCohenMemonTSE2011, YuanMemonICSE2007}%, Xie:2006:MTC:1172962.1172990}
+Guitar~\cite{YuanCohenMemonTSE2011, YuanMemonICSE2007}
 is a GUI testing framework for Java and Microsoft Windows applications. 
 Yuan and Memon~\cite{YuanMemonICSE2007} generate event-sequence based test cases for GUI
-programs. Their model-based approach can generate test cases automatically using a structural event
-generation graph. 
+programs using a structural event generation graph. 
 However, testing is often insufficient to detect many potential
-errors in a GUI application
-due to the huge space of possible interactions
-with a GUI. The large number of possible interactions
-need a large number of test inputs that require substantial human effort.
-%The second problem is to determine the coverage of a set of test
-%cases~\cite{MemonFSE2001}. For conventional software, coverage is measured
-%using the amount and type of underlying code exercised.
-%These measures do not work well for GUI testing, because
-%what matters is not only how much of the code is tested,
-%but in how many different possible states of the software
-%each piece of code is tested. This makes it hard to determine
-%the completeness of a test suite. 
+errors in a GUI application due to the huge space of possible UI interactions.
+%The large number of possible interactions
+%requires a large number of test inputs that require substantial human effort.
 In contrast, as suggested in this paper,
-using a static analysis can potentially explore
-all paths to find potential errors without actually executing the tested code. 
-Compared with software testing, a static analysis tool may
+using a static analysis can explore paths to find potential errors without actually executing the tested code,
+and find potential errors missed by testing.
+Compared to software testing, a static analysis tool may
 report false positives and redundant warnings due to its conservative nature.
-Nevertheless, as we demonstrated in our experiments, using a few simple error
-filters can dramatically reduce the number of false positives and redundant warnings to
+However, as we demonstrated in our experiments, using a few simple error
+filters can dramatically reduce the number of warnings to
 an acceptable level.
@@
 More recently, Goldilock~\cite{Elmas:2007} uses the hybrid model that combines the happens-before and lock-based
-approaches to identify data races based on an execution. By exploiting the insight
-that a full generality of the happens-before is unnecessary in most data accesses,
-FastTrack~\cite{Flanagan:2009} proposes an adaptive representation for the happen-before
-relation to efficiently and precisely detect races at runtime. However, finding
-invalid thread access errors is quite different than detecting data races in
-a multithreaded program. A data race occurs when two concurrent threads access
+approaches to identify data races based on an execution.
+%By exploiting the insight
+%that a full generality of the happens-before is unnecessary in most data accesses,
+%FastTrack~\cite{Flanagan:2009} proposes an adaptive representation for the happen-before
+%relation to efficiently and precisely detect races at runtime.
+However, finding
+invalid thread access errors is quite different than detecting data races.
+A data race occurs when two concurrent threads access
 a shared variable and when at least one access is a write and the threads
@@
 an invalid thread access error occurs when a non-UI thread accesses (reads or writes) a GUI object.
-Unlike detecting potential data races, finding invalid thread access error does not require monitoring every shared-memory
-reference and verify that consistent locking behavior is observed among different threads. Instead,
-our technique only needs to track whether a non-UI thread can reach a GUI object or not,
+Unlike detecting data races, finding invalid thread access error does not require monitoring every shared-memory
+reference and verify that consistent locking behavior is observed among different threads.
+A technique only needs to track whether a non-UI thread can accesses a GUI object or not,
 and is much cheaper.
 How to leverage the recent advance in data race detection to 
-improve our technique is one of our future work.
+improve our technique is our future work.
 
@@
 By exhaustively exploring the thread scheduling space, a model checker can
-report counter examples for the potential bugs with a counter example. For example,
-CHESS~\cite{chess} dynamically explores the thread scheduling decisions to expose
-concurrency bugs using a context-bounded approach. 
+report counter examples for the potential bugs with a counter example.
+%For example,
+%CHESS~\cite{chess} dynamically explores the thread scheduling decisions to expose
+%concurrency bugs using a context-bounded approach. 
 %Shacham et al~\cite{Shacham:2007} uses
@@
 It chooses call graph as a coarse-grained program representation with a
-set of error filters, achieving good scalability with reasonable accuracy.
+set of error filters, to achieve good scalability with reasonable accuracy.
 
@@
 
+\tinystep
+
 \subsection{Call Graph Construction Algorithms}
+%\vspace{1mm}
 
-A lot of effort has been spent on analyzing function pointers in C
-as well as virtual method calls in C++ and Java ~\cite{rta, kcfa,
-xta, inccg, Sundaresan:2000}.
+%\noindent \textit{\textbf{Call Graph Construction Algorithms}}
+A lot of effort has been spent on building call graphs for
+Object-oriented programs~\cite{rta, kcfa, xta, inccg, Sundaresan:2000}.
 We briefly mention some of the highlights of call graph construction
@@
 framework for expressing call graph construction algorithms, and
-performed a quantitative study comparing different instantiations
-of the framework. Tip and Palsberg~\cite{xta} quantitatively compared
+studied different instantiations of the framework.
+Tip and Palsberg~\cite{xta} quantitatively compared
 several low-cost call graph construction algorithms for Java.
-Sundaresan et al.~\cite{Sundaresan:2000} went beyond the traditional
-CHA and RTA~\cite{rta} approaches in Java and used type propagation
-for the purpose of obtaining a more precise call graph.
-However, the heavy use of reflection in some GUI applications make
-those algorithms insufficient to build a good call graph.
+Sundaresan et al.~\cite{Sundaresan:2000} went beyond the% traditional
+CHA and RTA~\cite{rta} approaches and used type propagation
+to build a more precise call graph.
+However, the use of reflection makes
+those algorithms insufficient to build a complete call graph.
 As reflected in our experiments, using standard call graph algorithms
-fails to find errors in some
-Android applications. %, due to the incompleteness of the resulting graph.
+misses errors in some Android applications. %, due to the incompleteness of the resulting graph.
 
@@
 Livshits et al.~\cite{Livshits:2005} presented a static analysis
-that attempts to infer additional information about
-reflective call sites directly from program code. The analysis
-attempts to use information stored in string constants to resolve
+to reason about reflective calls. The analysis
+attempts to infer additional information stored in string constants to resolve
 reflective calls statically. Their approach focuses on standard Java
-reflection calls (e.g., \CodeIn{java.lang.Class.forName}) but not on
-framework-specific ones (e.g., \CodeIn{android.view.View.find-\\ViewById}).
-The WALA framework implements a similar approach to handle Java
-reflections, but still fails to build a sufficiently complete call graph for
+reflection calls (e.g., \CodeIn{Class.forName}) instead of the
+framework-specific ones (e.g., \CodeIn{View.findViewById}).
+The standard call graph algorithms we used from WALA handles standard Java
+reflection calls as~\cite{Livshits:2005} does, but still fails to build
+a sufficiently complete call graph for
 Android applications. TamiFlex~\cite{Bodden:2011}, a pure dynamic
-approach, dumps all reflectively-created class instances to a file
+approach, records all reflectively-created class instances
 by intercepting JVM system calls, and re-inserts those recorded 
 class into a program. However, TamiFlex requires a set of representative
-program executions which may not be available in practice,
- and is only sound with respect to the recorded executions.
-Perhaps the most close work to our reflection-aware call graph
+program executions and is only sound with respect to the given executions.
+Perhaps the closest work to our call graph
 construction algorithm is Payet and Spoto's Julia
-system~\cite{Payet:2011:SAA:2032266.2032299}, which is independently
-proposed with our algorithm. One difference is that the Julia system
-requires to instrument the code of Android's library class
-\CodeIn{android.view.LayoutInflater} that performs the XML inflation ahead of time,
-then replaces the \CodeIn{findViewById} call with with a
-non-deterministic execution of new statements.
-In contrast, our algorithm leverages WALA's \textit{bypass logic}
-to transform the program on-the-fly when
-constructing the call graph, without requiring a separate pass of
-off-line instrumentation.
+system~\cite{Payet:2011:SAA:2032266.2032299}. The Julia system
+needs to first instrument Android's library code that performs the XML inflation,
+and then replaces the \CodeIn{findViewById} call with the corresponding
+object creation expressions. In additiona, the Julia system does not handle
+native methods when building call graphs. In contrast, our technique provides
+annotation support for native methods, and our tool does not need a separate
+pass of off-line instrumentation. The reflection-aware call graph is created
+online by incerpting the standard call graph construction process.
 

### 2012-02-10 trunk/GUIErrorDetector/paper/evaluation.tex
more tweaks

@@
 for Android applications, a slash ``/'' separates the result of
-using standard call graph construction algorithm and the reflection-aware
-call graph construction algorithm. The \newbugs errors found in VirgoFTP, FileBunker, ArecaBackup
+using standard call graph construction algorithm and our call
+graph construction algorithm in Section~\ref{sec:cgcon} (dealing
+with reflection calls and adding \annotationnum native method annotations
+for SGTPuzzler). The \newbugs errors found in VirgoFTP, FileBunker, ArecaBackup
 S3dropbox, and SudokuSolver are previously  unknown. As a comparison, the
@@
 We submitted all \newbugs new errors
-to the subject developers. As of Feb 2012, 1 error in S3dropbox has been confirmed,
+to the subject developers. As of February 2012, 1 error in S3dropbox has been confirmed,
 4 errors have been reproduced and validated in our own experimental environment, and
-2 errors in FileBunker and ArecaBackup had not been verified by developers yet.
+2 errors in FileBunker and ArecaBackup had not yet been verified by developers.
 
@@
 the given Sudoku is unsolvable; and the other one happens
-when  JVM fails to launch the mail composing window of the
+when  JVM fails to launch the %mail composing window of the
 user default mail client.% (after a user clicks the "eMail Me" button).
@@
 
-We next compare the three call graph construction algorithms (RTA, 0-CFA, and 1-CFA)
+We next compare the 3 call graph construction algorithms (RTA, 0-CFA, and 1-CFA)
 used in our experiments. As shown in Table~\ref{table:results},  1-CFA found
-more errors with fewer false positive warnings than the other two algorithms. This
+more errors than the other two algorithms. This
 is because RTA and 0-CFA do not consider the calling context when
-constructing a call graph, and may
+constructing a call graph, and 
 mix the same method calls by different callers into a single node, thus
-introducing imprecision. Although the error-revealing paths exist in
-less precise graphs, the impreicison prevents our algorithm finding them.
+introducing imprecision. Although the error paths exist in
+less precise graphs, the impreicison prevents our algorithm from finding them.
 Figure~\ref{fig:ex} illustrates this point.
@@
 \noindent \textbf{\textit{Summary.}} Using the 1-CFA 
-algorithm finds more errors than 0-CFA and RTA, and our reflection-aware call
+algorithm finds more errors than 0-CFA and RTA, and our call
 graph construction algorithm helps to find errors on some
@@
  \fontsize{9pt}{\baselineskip}\selectfont
-\setlength{\tabcolsep}{.46\tabcolsep}
+\setlength{\tabcolsep}{.40\tabcolsep}
 \hspace*{-0.2cm}

### 2012-02-10 trunk/GUIErrorDetector/paper/implementation.tex
more tweaks

@@
 \item \textbf{UI-accessing nodes: } the \CodeIn{Widget.checkWidget}
-and \CodeIn{Display.} \CodeIn{checkDevice} methods. SWT uses the above
-two methods to explicitly check whether the current thread is a UI thread
-or not, and throw a \CodeIn{RuntimeException} if the checking fails.
-%thread accesses at runtime.
-%Any methods for manipulating GUIs object must call (one of) these two methods
-% to determine whether the current thread is the UI thread or not.
+and \CodeIn{Display.} \CodeIn{checkDevice} methods. SWT performs
+runtime checking before accessing a GUI object via these methods.
+If the current thread is a non-UI thread, the \CodeIn{Widget.checkWidget}
+and \CodeIn{Display.checkDevice} methods throw a \CodeIn{RuntimeException}.
+
 \smallstep
@@
 events. All SWT GUI event handling methods (i.e., the overriden
-methods in the class that implements \CodeIn{org.eclipse.swt.internal.SWTEvent-\\Listener}) are
-always called back from the UI thread, thus are used as call graph entry nodes.
+methods in the class that implements \CodeIn{org.eclipse.swt.internal.SWTEventListener}) are
+always called back from the UI thread.
+%, thus are used as call graph entry nodes.
 
-\smallstep
+\tinystep
 
@@
 \end{itemize}
+\end{myindentpar}
 
+\tinystep
+\tinystep
 \tinystep
@@
 After a Swing program starts, its initial thread exits and the UI thread takes charge
-of the application and starts to execute all event-handling code or spawns new worker threads. 
+of the application and starts to execute event-handling code or spawn new worker threads. 
 We instantiated our technique for Swing as follows:
 
+\begin{myindentpar}{-2mm}
 \begin{itemize}
+\tinystep
 
-\item \textbf{Call graph entry nodes:} all overridden Swing GUI event handling
-methods in user code. Those event handling methods are always
+\item \textbf{Call graph entry nodes:} all user code methods that override
+Swing GUI event handling methods. Those event handling methods are always
 called back from the UI thread.
 
-\smallstep
+\tinystep
 
@@
 
-\smallstep
+\tinystep
 
 \item \textbf{Safe UI methods: } 
-\CodeIn{SwingUtilities.}\CodeIn{invokeLater} and \CodeIn{Swing-\\Utilities.invokeAndWait} that execute code on the UI thread.
+\CodeIn{SwingUtilities.}\CodeIn{invokeLater} and \CodeIn{SwingUti-\\lities.invokeAndWait}, which execute code on the UI thread.
 
 \end{itemize}
+\end{myindentpar}
 
@@
 and any overriding definitions in its subclasses as call graph entry nodes.
-We also add all overridden Android GUI event handling methods in user
-code as entry nodes, since they are also called back from the UI thread.
+We also add all user code methods that override Android GUI event handling methods
+as entry nodes, since they are called back from the UI thread.
 
-\smallstep
+\tinystep
 
 \item \textbf{UI-accessing nodes: }the \CodeIn{ViewRoot.checkThread} method.
-Like SWT, Android explicitly performs runtim checking before accessing
+Like SWT, Android explicitly performs runtime checking before accessing
 a GUI object via the \CodeIn{ViewRoot.checkThread} method. If the current
@@
 
-\smallstep
+\tinystep
 
 \item \textbf{Safe UI methods: } \CodeIn{View.post}
-and \CodeIn{View.postDelay} that execute code on the UI thread.
+and \CodeIn{View.postDelay}, which execute code on the UI thread.
 
 \end{itemize}
+\end{myindentpar}
 
@@
 errors, and scales to realistic programs.  
-
 We implemented the reflection-aware call graph construction
  algorithm (Section~\ref{sec:cg}) using WALA's \textit{bypass logic}.
-Unlike similar tools~\cite{Payet:2011:SAA:2032266.2032299}, our tool
+Unlike other tools~\cite{Payet:2011:SAA:2032266.2032299}, our tool
 does not require a separate pass for program instrumentation; instead, it

### 2012-02-10 trunk/GUIErrorDetector/paper/introduction.tex
more small edits

@@
 In our evaluation on real-world programs, we found a simple analysis that
-requires GUI operations to be in a message issues
+requires GUI operations to be in a message issued
 an unacceptable number of warnings. %false positives and redundant warnings.
@@
 two dominant GUI frameworks for desktop Java applications.
-Eclipse is the de-facto standard IDE for Java. Android is the \#1 platform for
-mobile applications with market share 56\% as of Sep 2011.
+Eclipse is a widely-used IDE for Java. Android is the \#1 platform for
+mobile applications with market share 56\% as of September 2011.
 Although our technique is applicable to any GUI
@@
 finding errors in Android applications;
-and our proposed filters significantly reduce the number of warnings.
+and our proposed error filters significantly reduce the number of warnings.
 %false positives and redundant warnings.

### 2012-02-10 trunk/GUIErrorDetector/paper/related.tex
more small edits

@@
 Harrold:2000:TR:336512.336532}.
- Many GUI analysis and testing techniques have been proposed in the past decade; some have been
-implemented as tools and adopted by practitioners. Existing techniques automate
+ Many GUI analysis and testing techniques have been proposed in the past decade.
+Existing techniques automate
 some aspect(s) of GUI testing including model creation
@@
  without compromising the detection capability. To our best knowledge,
-we are not aware of any software model checking approach can scale to the subjects
+we are not aware of any software model checking approach can scale to subjects
 as large as those used in our experiments (including the library code).
@@
 %\noindent \textit{\textbf{Call Graph Construction Algorithms}}
-A lot of effort has been spent on analyzing function pointers in C
-as well as virtual method calls in C++ and Java ~\cite{rta, kcfa,
-xta, inccg, Sundaresan:2000}.
+A lot of effort has been spent on building call graphs for
+Object-oriented programs~\cite{rta, kcfa, xta, inccg, Sundaresan:2000}.
 We briefly mention some of the highlights of call graph construction
@@
 framework for expressing call graph construction algorithms, and
-performed a quantitative study comparing different instantiations
-of the framework. Tip and Palsberg~\cite{xta} quantitatively compared
+studied different instantiations of the framework.
+Tip and Palsberg~\cite{xta} quantitatively compared
 several low-cost call graph construction algorithms for Java.
-Sundaresan et al.~\cite{Sundaresan:2000} went beyond the traditional
-CHA and RTA~\cite{rta} approaches in Java and used type propagation
-for the purpose of obtaining a more precise call graph.
-However, the heavy use of reflection in some GUI applications make
-those algorithms insufficient to build a good call graph.
+Sundaresan et al.~\cite{Sundaresan:2000} went beyond the
+CHA and RTA~\cite{rta} approaches and used type propagation
+to build a more precise call graph.
+However, the use of reflection makes
+those algorithms insufficient to build a complete call graph.
 As reflected in our experiments, using standard call graph algorithms
-fails to find errors in some
-Android applications. %, due to the incompleteness of the resulting graph.
+misses errors in some Android applications. %, due to the incompleteness of the resulting graph.
 
@@
 Livshits et al.~\cite{Livshits:2005} presented a static analysis
-that attempts to infer additional information about
-reflective call sites directly from program code. The analysis
-attempts to use information stored in string constants to resolve
+to reason about reflective calls. The analysis
+attempts to infer additional information stored in string constants to resolve
 reflective calls statically. Their approach focuses on standard Java
-reflection calls (e.g., \CodeIn{java.lang.Class.forName}) but not on
-framework-specific ones (e.g., \CodeIn{android.view.View.find-\\ViewById}).
-The WALA framework implements a similar approach to handle Java
-reflections, but still fails to build a sufficiently complete call graph for
+reflection calls (e.g., \CodeIn{Class.forName}) instead of the
+framework-specific ones (e.g., \CodeIn{View.findViewById}).
+The standard call graph algorithms implemented in WALA, which we used
+in our experiments, actually handle standard Java
+reflection calls as~\cite{Livshits:2005} does, but still fails to build
+a sufficiently complete call graph for
 Android applications. TamiFlex~\cite{Bodden:2011}, a pure dynamic
-approach, dumps all reflectively-created class instances to a file
+approach, records all reflectively-created class instances
 by intercepting JVM system calls, and re-inserts those recorded 
 class into a program. However, TamiFlex requires a set of representative
-program executions which may not be available in practice,
- and is only sound with respect to the recorded executions.
-Perhaps the most close work to our reflection-aware call graph
+program executions and is only sound with respect to the given executions.
+Perhaps the closest work to our call graph
 construction algorithm is Payet and Spoto's Julia
-system~\cite{Payet:2011:SAA:2032266.2032299}, which is independently
-proposed with our algorithm. One difference is that the Julia system
-requires to instrument the code of Android's library class
-\CodeIn{android.view.LayoutInflater} that performs the XML inflation ahead of time,
-then replaces the \CodeIn{findViewById} call with with a
-non-deterministic execution of new statements.
-In contrast, our algorithm leverages WALA's \textit{bypass logic}
-to transform the program on-the-fly when
-constructing the call graph, without requiring a separate pass of
-off-line instrumentation.
+system~\cite{Payet:2011:SAA:2032266.2032299}. The Julia system
+needs to first instrument Android's library code that performs the XML inflation,
+and then replaces the \CodeIn{findViewById} call with the corresponding
+object creation expressions. In additiona, the Julia system does not handle
+native methods when building call graphs. In contrast, our technique provides
+annotation support for native methods, and our tool does not need a separate
+pass of off-line instrumentation. The reflection-aware call graph is created
+online by incerpting the standard call graph construction process.
 

### 2012-02-10 trunk/GUIErrorDetector/paper/technique.tex
more small edits

@@
 
-The error message created by the method \CodeIn{createErrorReport} on line 18
+The error message created by the method \CodeIn{createErrorReport} on line 16
 includes the method call chain from the entry node to the UI-accessing node
@@
 
-As demonstrated in our experiments, using this reflection-aware call
+As demonstrated in our experiments, this reflection-aware call
 graph construction algorithm helps in detecting errors
@@
 
-A static analysis can exhaustively check possible error paths; but may report
+A static analysis can check possible error paths without executing the code; but may report
 paths that do not actually exist (false positives) or multiple paths

### 2012-02-10 GUIErrorDetector/paper/evaluation.tex
more small edits

@@
 
-For all \subnum programs, we manually determined validity of each output warning
+For all \subnum programs, we manually determined the validity of each output warning
 by either searching the
@@
 for Android applications, a slash ``/'' separates the result of
-using standard call graph construction algorithm and the reflection-aware
-call graph construction algorithm (with \annotationnum native method annotations
+using standard call graph construction algorithm and our call
+graph construction algorithm in Section~\ref{sec:cgcon} (dealing
+with reflection calls and adding \annotationnum native method annotations
 for SGTPuzzler). The \newbugs errors found in VirgoFTP, FileBunker, ArecaBackup
@@
 to the subject developers. As of February 2012, 1 error in S3dropbox has been confirmed,
-4 errors have been reproduced and validated in our own experimental environment, and
-2 errors in FileBunker and ArecaBackup had not yet been verified by developers.
+we have reproduced 4 errors, and 2 errors in FileBunker and ArecaBackup
+had not yet been verified by the developers.
 
@@
 Another reason they overlooked this violation is because some GUI frameworks like Swing
-do not provide any run-time checks for invalid thread accesses. The Swing
+do not provide any runtime checks for invalid thread accesses. The Swing
 GUI does not exhibit user-visible faults on some erreoneous executions.
@@
 plugin. This error is event-related. It happens when a 
-\CodeIn{ResourceChangeEvent} happen, which then invokes the \CodeIn{refresh}
+\CodeIn{ResourceChangeEvent} happens, which then invokes the \CodeIn{refresh}
 method on line 415 to update the user interface. In EclipseRunner,
@@
 when  JVM fails to launch the %mail composing window of the
-user default mail client.% (after a user clicks the "eMail Me" button).
+user's default mail client.% (after a user clicks the "eMail Me" button).
 
-As reflected in our experiments, we found GUI developers have already
+We found GUI developers have already
 used design patterns, runtime checks, and testing to avoid violating
@@
 
-We next compare the three call graph construction algorithms (RTA, 0-CFA, and 1-CFA)
+We next compare the 3 call graph construction algorithms (RTA, 0-CFA, and 1-CFA)
 used in our experiments. As shown in Table~\ref{table:results},  1-CFA found
@@
 is because RTA and 0-CFA do not consider the calling context when
-constructing a call graph, and may
+constructing a call graph, and 
 mix the same method calls by different callers into a single node, thus
-introducing imprecision. Although the error-revealing paths exist in
+introducing imprecision. Although the error paths exist in
 less precise graphs, the impreicison prevents our algorithm from finding them.
@@
   \vspace*{-5.0ex}\caption {{\label{fig:ex} (a) shows an example code, in which
-\CodeIn{safe()} is a Safe UI method, and \CodeIn{uiAcc()} is a UI-Accessing method.
+\CodeIn{safe()} is a Safe UI method, and \CodeIn{uiAcc()} is a UI-accessing method.
 (b) shows a less precise call graph built by RTA or 0-CFA, and (c) shows a more
@@
 the data structure of $\mathit{worklist}$ on line 7 in Figure~\ref{fig:detectalgorithm} to
-a stack, and changing queue operations (\CodeIn{dequeue}, and \CodeIn{enqueueAll}
-on lines 10, and 21 in Figure~\ref{fig:detectalgorithm}, respectively)
-to the corresponding statck operations (\CodeIn{pop}, and \CodeIn{pushAll}).
+a stack, and changing queue operations (\CodeIn{dequeue} and \CodeIn{enqueueAll}
+on lines 10 and 21 in Figure~\ref{fig:detectalgorithm}, respectively)
+to the corresponding statck operations (\CodeIn{pop} and \CodeIn{pushAll}).
 This variant found 11 errors in total and missed 1 error in the FileBunker subject.
@@
 revealed a real error. This is because the number of
-non-cyclic paths in a graph is exponential in the graph size.%node number.
+non-cyclic paths in a graph is exponential in the graph size.
 For a realistic call graph which often contains thousands of nodes,
@@
 is neither sound nor complete. It may miss true positives due
-to the used graph search strategy, or
+to the graph search strategy, or
 issue false positives due to the conservative nature of

### 2012-02-10 GUIErrorDetector/paper/evaluation.tex
more edits

@@
 \vspace{-15pt}
-\Caption{{\label{table:results}Experimental results in finding invalid thread access errors
+\Caption{{\label{table:results}Experimental results in finding invalid-thread-access errors
 in multithreaded GUI programs. Column ``CG Size'' shows the
@@
 with reflection calls and adding \annotationnum native method annotations
-for SGTPuzzler). The \newbugs errors found in VirgoFTP, FileBunker, ArecaBackup
+for SGTPuzzler). The \newbugs errors found in VirgoFTP, FileBunker, ArecaBackup,
 S3dropbox, and SudokuSolver are previously  unknown. As a comparison, the
@@
 
-As briefly mentioned in Section~\ref{sec:finding}, one way to prevent
+As mentioned in Section~\ref{sec:finding}, one way to prevent
 invalid thread access errors is to wrap every GUI-accessing operation
@@
 constructing a call graph, and 
-mix the same method calls by different callers into a single node, thus
+mix calls to the same method from different callers into a single node, thus
 introducing imprecision. Although the error paths exist in
-less precise graphs, the impreicison prevents our algorithm from finding them.
-Figure~\ref{fig:ex} illustrates this point.
+the less precise graphs, our algorithm does not report them because of its heuristics
+for outputting the shortest possible call chain. Figure~\ref{fig:ex} illustrates this point.
 
@@
   \includegraphics[scale=0.45]{cgexample}
-  \vspace*{-5.0ex}\caption {{\label{fig:ex} (a) shows an example code, in which
+  \vspace*{-5.0ex}\caption {{\label{fig:ex} (a) shows example code, in which
 \CodeIn{safe()} is a Safe UI method, and \CodeIn{uiAcc()} is a UI-accessing method.
@@
 precise call graph built by 1-CFA. Nodes for constructors are omitted for brevity.
-Using the less precise call graph, the error
-detection algorithm in Figure~\ref{fig:detectalgorithm} will report an invalid method call chain: \CodeIn{entry()}
+Using the less precise call graph, our error
+detection algorithm (Figure~\ref{fig:detectalgorithm}) reports an invalid method
+call chain: \CodeIn{entry()}
 $\rightarrow$ \CodeIn{f()} $\rightarrow$ \CodeIn{start()} $\rightarrow$ \CodeIn{run()}
-$\rightarrow$ \CodeIn{uiAcc()},
-but miss the actual error path: \CodeIn{entry()} $\rightarrow$ \CodeIn{g1()} $\rightarrow$
-\CodeIn{g2()} $\rightarrow$ \CodeIn{start()} $\rightarrow$ \CodeIn{run()} $\rightarrow$ \CodeIn{uiAcc()}. The
-actual error path can only be found when using the more precise call graph.
+$\rightarrow$ \CodeIn{uiAcc()}. It does not report
+the actual error path because it is longer: \CodeIn{entry()} $\rightarrow$ \CodeIn{g1()} $\rightarrow$
+\CodeIn{g2()} $\rightarrow$ \CodeIn{start()} $\rightarrow$ \CodeIn{run()} $\rightarrow$ \CodeIn{uiAcc()}.
+The algorithm outputs the actual error path when using the more precise call graph.
 }}
@@
 Another error in SGTPuzzler is only reported when adding \annotationnum native method
-annotations (Section~\ref{sec:annotation}). The error in Fennec
-can be found by using a standard call graph construction algorithm.
-This is because the error-related GUI objects are created explicitly,
-so the standard call graph construction algorithm is sufficient.
+annotations (Section~\ref{sec:annotation}).
+
+%The error in Fennec
+%can be found by using a standard call graph construction algorithm.
+%This is because the error-related GUI objects are created explicitly,
+%so the standard call graph construction algorithm is sufficient.
 
@@
 algorithm finds more errors than 0-CFA and RTA, and our call
-graph construction algorithm helps to find errors on some
+graph construction algorithm helps to find errors in some
 Android applications.
@@
 
-Our error detection algorithm in Figure~\ref{fig:detectalgorithm} uses BFS to search for
-potential single-GUI-thread violations. However, other graph search strategies such as
+Our error detection algorithm in Figure~\ref{fig:detectalgorithm} uses a
+slightly modified BFS to search for
+potential single-GUI-thread violations. However, standard BFS
+and other graph search strategies such as
 DFS and exhaustive path search can also be employed. To
 understand trade-offs between using different search strategies, we 
-implemented two variants of the algorithm in Figure~\ref{fig:detectalgorithm}, and
+implemented three variants of the algorithm in Figure~\ref{fig:detectalgorithm}, and
 evaluated them on the same subjects with the identical environment settings.
 
-The first variant uses DFS for graph traversal by changing
+The first variant uses standard BFS for graph traversal by deleting
+lines 6 and 23 in Figure~\ref{fig:detectalgorithm}, and changing
+7 in Figure~\ref{fig:detectalgorithm} to:
+
+\vspace{0.2mm}
+$\mathit{worklist}$ $\leftarrow$ $\bigcup_{entry \in entryNodes}$ getReachableStarts($\mathit{entry}$)
+\vspace{0.2mm}
+
+\noindent This variant returns the shortest path from \textit{any} \CodeIn{Thread.start()} node
+to \textit{any} UI-accessing node, rather than the shortest path from \textit{a given}
+\CodeIn{Thread.start()} node to \textit{any} UI-accessing node as the algorithm in
+Figure~\ref{fig:detectalgorithm} does.
+This variant found 10 errors in total and missed 1 error in S3dropbox and 1 error in
+SudokuSolver. This is because in BFS (either the standard BFS or our algorithm), each
+node will \textit{only} be visited once; but in the standard BFS, if a node has been covered
+in an error path from a \CodeIn{Thread.start()} node, that node will not be visited again
+even when the standard BFS traverses from another \CodeIn{Thread.start()} node, thus
+missing potential errors.
+
+The second variant uses DFS for graph traversal by changing
 the data structure of $\mathit{worklist}$ on line 7 in Figure~\ref{fig:detectalgorithm} to
@@
 
-%Hundson: 3, 1
-%EclipseRunner: 6, 1
-%S3dropbox: ? , ?  too many warnings time: 31678 (45528 chains), running out of memory
-%SudokuSolver:  2, 1 too many warnings: 1700, 2090
-%VirgoFTP: 2, 2
-%FileBunker:  2, 0  //very long method calls
-%Fennec: 3, 1
-%SGTPuzzler: 1, 1
-%MyTracks: 1, 1
-
-The second variant uses exhaustive search to find potential errors. This variant
+The third variant uses exhaustive search to find potential errors. This variant
 enumerates all non-cyclic paths from all reachable \CodeIn{Thread.start()} nodes
@@
 
-\noindent \textbf{\textit{Summary.}} Using BFS finds more errors than DFS and
-exhaustive search in our error detection algorithm.
+\noindent \textbf{\textit{Summary.}} Our algorithm finds more errors than
+using standard BFS, DFS and exhaustive search in error detection.
 
@@
 
-Table~\ref{table:filters} measures the effectiveness of the proposed 
+Table~\ref{table:filters} measures the effectiveness of the
 error filters of Section~\ref{sec:heuristic}.
-The five error filters removed 99.96\% of the reported warnings as false positives
+The five error filters removed 99.96\% of the reported warnings as likely false positives
 or redundant warnings. Specifically, two sound filters 1 and 2 
 removed 34.44\% of the warnings, and three heuristic filters 3, 4, and 5
-removed a further 65.52\% of the warnings. Among them, the 4th filter for removing
-reports with the same head methods from the entry node to \CodeIn{Thread.start()}
-is the most effective one.
+removed a further 65.52\% of the warnings. The most effective filter is
+\#4, for removing reports with the same head methods from the entry node to \CodeIn{Thread.start()}.
 
@@
 
-\subsection{Discussions}
+\subsection{Discussion}
 
@@
 has been evaluated on \subnum subjects with over \totaloc LOC and frameworks
-with over 1.4 MLOC, showing good scalability. Our evaluations
+with 1.4 MLOC, showing good scalability. Our evaluations
 were conducted on a 2.67GHz Intel Core PC with 4GB
@@
 widely-used call graph construction algorithms (i.e., RTA, 0-CFA, and 1-CFA) 
-in our evaluation. It is still unknown whether using other 
+in our evaluation. Using other 
 call graph construction algorithms such as XTA~\cite{xta}, VTA~\cite{Sundaresan:2000} or
-an incremental algorithm~\cite{inccg} may achieve better results.
+an incremental algorithm~\cite{inccg} might achieve divergent results.
 
@@
 issue false positives due to the conservative nature of
-a static analysis. Designing better call graph construction algorithms
-and graph search strategies may alleviate this limitation.
+a static analysis. Designing better call graph construction algorithms,
+graph search strategies, and filtering heuristics may alleviate this limitation.
 Third, our tool cannot compute call relationships
@@
 few false positive warnings. Our
-proposed filters are useful to reduce the number of warnings.
+proposed filters are useful in reducing the number of warnings.

### 2012-02-10 GUIErrorDetector/paper/technique.tex
more edits

@@
 the single main method, UI-accessing nodes include methods
-\CodeIn{Widget.checkWidget} and \CodeIn{Display.} \CodeIn{checkDevice},
+\CodeIn{Widget.checkWidget} and \CodeIn{Display.}\CodeIn{checkDevice},
 and safe UI methods include two SWT helper methods \CodeIn{Display.asyncExec}  and
@@
 
+As demonstrated in our experiments, this reflection-aware call
+graph construction algorithm helps in detecting errors
+in Android applications (Section~\ref{sec:reflectionaware}).
+
 \subsubsection{Native Methods}
@@
 
-As demonstrated in our experiments, using our call
-graph construction algorithm helps in detecting errors
-in Android applications (Section~\ref{sec:reflectionaware}).
-
 \subsection{Filtering the Error Reports}
@@
 the other 3 filters are based on heuristics. Orthogonally, filters 2
-and 3 are for eliminating false positives, and filters 1, 4, and 5
+and 3 are for reducing false positives, and filters 1, 4, and 5
 are for reducing redundant warnings.

### 2012-02-10 trunk/GUIErrorDetector/paper/conclusion.tex
revise related work, and conclusion

@@
 
-In this paper, we presented a general technique to find invalid
-thread access errors for multithreaded GUI applications. 
+This paper presented a general technique to find invalid
+thread access errors in multithreaded GUI applications. 
 Our technique statically explores paths in a call graph to check
@@
 filters to filter likely false positives and redundant warnings.
-Since graphical user interfaces are often inadequately tested due
-to the enormously large space of UI interactions and
-extreme resource constraints during their development, we
-believe that providing a static analysis can allow developers to find
-more potential errors %before the application is released to customers (XXX),
- to improve software reliability.
-We have also demonstrated that our technique can be useful
-by an evaluation on \subnum subjects acrosss 4 popular GUI
+%Since graphical user interfaces are often inadequately tested due
+%to the enormously large space of UI interactions and
+%extreme resource constraints during their development, we
+%believe that providing a static analysis can allow developers to find
+%more potential errors %before the application is released to customers (XXX),
+% to improve software reliability.
+We demonstrated the usefulness of our technique
+by an evaluation on \subnum programs built on 4 popular GUI
 frameworks.
-%Our experiments have shown that we can find bugs
-%in real-world programs.
 
-Besides general issues such as performance or ease of use, our future
+The source code of our tool implementation is available at:
+
+\noindent \url{http://guierrordetector.googlecode.com}
+
+\vspace{1mm}
+
+Besides general issues such as performance and ease of use, our future
 work will concentrate on the following topics:
@@
 positives is to integrate with
-dynamic analyses~\cite{Jiang:2008:PPS:1453101.1453110}%, ZhangSBE2011}
+dynamic analyses~\cite{Jiang:2008:PPS:1453101.1453110}
 or symbolic analyses~\cite{xie05:symstra, Pasareanu:2011, halfond09issta, BMF97}
@@
 \textbf{Fixing potential GUI errors.} After an error is revealed, fixing
-it and verifing the patch has often been another important and time-consuming process. Fixing concurrency
+it and verifying the patch is often time-consuming. Fixing concurrency
 bugs has become especially critical in the multicore era.
-Recently, a few work has been done
-on automatically repairing test script for GUI applications~\cite{Daniel:2011:AGR:2002931.2002937, Huang:2010:RGT:1828417.1828465}. However, none of them focuses on repairing
+Recently, work has been done
+on automatically repairing test scripts for GUI applications~\cite{Daniel:2011:AGR:2002931.2002937, Huang:2010:RGT:1828417.1828465}. However, none of them focuses on repairing
 the GUI program to patch a revealed error. Thus, we are interested in 

### 2012-02-10 trunk/GUIErrorDetector/paper/evaluation.tex
revise related work, and conclusion

@@
   \includegraphics[scale=0.45]{cgexample}
-  \vspace*{-5.0ex}\caption {{\label{fig:ex} (a) shows an example code, in which
-\CodeIn{safe()} is a Safe UI method, and \CodeIn{uiAcc()} is a UI-Accessing method.
+  \vspace*{-5.0ex}\caption {{\label{fig:ex} (a) shows example code, in which
+\CodeIn{safe()} is a Safe UI method, and \CodeIn{uiAcc()} is a UI-accessing method.
 (b) shows a less precise call graph built by RTA or 0-CFA, and (c) shows a more
 precise call graph built by 1-CFA. Nodes for constructors are omitted for brevity.
-Using the less precise call graph, the error
-detection algorithm in Figure~\ref{fig:detectalgorithm} will report an invalid method call chain: \CodeIn{entry()}
+Using the less precise call graph, our error
+detection algorithm (Figure~\ref{fig:detectalgorithm}) reports an invalid method
+call chain: \CodeIn{entry()}
 $\rightarrow$ \CodeIn{f()} $\rightarrow$ \CodeIn{start()} $\rightarrow$ \CodeIn{run()}
-$\rightarrow$ \CodeIn{uiAcc()},
-but miss the actual error path: \CodeIn{entry()} $\rightarrow$ \CodeIn{g1()} $\rightarrow$
-\CodeIn{g2()} $\rightarrow$ \CodeIn{start()} $\rightarrow$ \CodeIn{run()} $\rightarrow$ \CodeIn{uiAcc()}. The
-actual error path can only be found when using the more precise call graph.
+$\rightarrow$ \CodeIn{uiAcc()}. It does not report
+the actual error path because it is longer: \CodeIn{entry()} $\rightarrow$ \CodeIn{g1()} $\rightarrow$
+\CodeIn{g2()} $\rightarrow$ \CodeIn{start()} $\rightarrow$ \CodeIn{run()} $\rightarrow$ \CodeIn{uiAcc()}.
+The algorithm outputs the actual error path when using the more precise call graph.
 }}
@@
 
-Our error detection algorithm in Figure~\ref{fig:detectalgorithm} uses BFS to search for
-potential single-GUI-thread violations. However, other graph search strategies such as
+Our error detection algorithm in Figure~\ref{fig:detectalgorithm} uses a
+slightly modified BFS to search for
+potential single-GUI-thread violations. However, standard BFS
+and other graph search strategies such as
 DFS and exhaustive path search can also be employed. To
 understand trade-offs between using different search strategies, we 
-implemented two variants of the algorithm in Figure~\ref{fig:detectalgorithm}, and
+implemented three variants of the algorithm in Figure~\ref{fig:detectalgorithm}, and
 evaluated them on the same subjects with the identical environment settings.
 
-The first variant uses DFS for graph traversal by changing
+The first variant uses standard BFS for graph traversal by deleting
+lines 6 and 24 in Figure~\ref{fig:detectalgorithm}, and changing
+7 in Figure~\ref{fig:detectalgorithm} to:
+
+\vspace{0.2mm}
+$\mathit{worklist}$ $\leftarrow$ $\bigcup_{entry \in entryNodes}$ getReachableStarts($\mathit{entry}$)
+\vspace{0.2mm}
+
+\noindent This variant returns the shortest path from \textit{any} \CodeIn{Thread.start()} node
+to \textit{any} UI-accessing node, rather than the shortest path from \textit{a given}
+\CodeIn{Thread.start()} node to \textit{any} UI-accessing node as the algorithm in
+Figure~\ref{fig:detectalgorithm} does.
+This variant found 10 errors in total and missed 1 error in S3dropbox and 1 error in
+SudokuSolver. This is because in BFS (either the standard BFS or our algorithm), each
+node will \textit{only} be visited once; but in the standard BFS, if a node has been covered
+in an error path from a \CodeIn{Thread.start()} node, that node will not be visited again
+even when the standard BFS traverses from another \CodeIn{Thread.start()} node, thus
+missing potential errors.
+
+The second variant uses DFS for graph traversal by changing
 the data structure of $\mathit{worklist}$ on line 7 in Figure~\ref{fig:detectalgorithm} to
-a stack, and changing queue operations (\CodeIn{dequeue}, and \CodeIn{enqueueAll}
-on lines 10, and 21 in Figure~\ref{fig:detectalgorithm}, respectively)
-to the corresponding statck operations (\CodeIn{pop}, and \CodeIn{pushAll}).
+a stack, and changing queue operations (\CodeIn{dequeue} and \CodeIn{enqueueAll}
+on lines 10 and 21 in Figure~\ref{fig:detectalgorithm}, respectively)
+to the corresponding statck operations (\CodeIn{pop} and \CodeIn{pushAll}).
 This variant found 11 errors in total and missed 1 error in the FileBunker subject.
@@
 In our evaluation, the studied subjects were selected with a bias towards popularity from
-well-known open-source repositories. Another threat is that we only employed three
+open-source repositories. Another threat is that we only employed three
 widely-used call graph construction algorithms (i.e., RTA, 0-CFA, and 1-CFA) 
-in our evaluation. It is still unknown whether using other 
+in our evaluation. Using other 
 call graph construction algorithms such as XTA~\cite{xta}, VTA~\cite{Sundaresan:2000} or
-an incremental algorithm~\cite{inccg} may achieve better results.
+an incremental algorithm~\cite{inccg} might achieve divergent results.
 
@@
 is neither sound nor complete. It may miss true positives due
-to the used graph search strategy, or
+to the graph search strategy, or
 issue false positives due to the conservative nature of
-a static analysis. Designing better call graph construction algorithms
-and graph search strategies may alleviate this limitation.
+a static analysis. Designing better call graph construction algorithms,
+graph search strategies, and filtering heuristics may alleviate this limitation.
 Third, our tool cannot compute call relationships

### 2012-02-10 GUIErrorDetector/paper/related.tex
revise related work, and conclusion

@@
 Work related to this paper falls into three main categories; (1)
-techniques and tools to analyze and test GUI programs; (2)
-bug finding techniques for general multithreaded programs; and (3)
+analyzing and testing GUI applications; (2)
+bug finding techniques for multithreaded programs; and (3)
 call graph construction algorithms.
@@
 \tinystep
-\subsection{Analysis and Testing for GUI Applications}
+\subsection{Analyzing and Testing GUI Applications}
 %\vspace{1mm}
@@
 %\noindent \textit{\textbf{Analysis and Testing for GUI Applications}}
-Automated GUI testing is a challenging tasks~\cite{Bertolino:2007:STR:1253532.1254712,
+Automated GUI testing is a challenging task~\cite{Bertolino:2007:STR:1253532.1254712,
 Harrold:2000:TR:336512.336532}.
- Many GUI analysis and testing techniques have been proposed in the past decade.
-Existing techniques automate
-some aspect(s) of GUI testing including model creation
+Various techniques automate GUI testing including model creation
 (for model-based testing)~\cite{androidtesting}, %, Xie:2006:MTC:1172962.1172990},
@@
 For example,
-%Kervinen et al.~\cite{Kervinen06model-basedtesting} present a formal model and architecture for testing
-%concurrently running applications. The behavior of the system under test
-%needs to be specified manually as a labeled transition system. 
 Guitar~\cite{YuanCohenMemonTSE2011, YuanMemonICSE2007}
 is a GUI testing framework for Java and Microsoft Windows applications. 
-Yuan and Memon~\cite{YuanMemonICSE2007} generate event-sequence based test cases for GUI
+Yuan and Memon~\cite{YuanMemonICSE2007} generate event-sequence-based test cases for GUI
 programs using a structural event generation graph. 
@@
 %requires a large number of test inputs that require substantial human effort.
-In contrast, as suggested in this paper,
-using a static analysis can explore paths to find potential errors without actually executing the tested code,
-and find potential errors missed by testing.
-Compared to software testing, a static analysis tool may
+In contrast, a static analysis can explore all paths to find potential errors missed by testing.
+Compared to software testing, a static analysis tool such as ours may
 report false positives and redundant warnings due to its conservative nature.
-However, as we demonstrated in our experiments, using a few simple error
-filters can dramatically reduce the number of warnings to
+In our experiments, simple error filters reduced the number of warnings to
 an acceptable level.
@@
 Michail and Xie~\cite{michail05:helping} proposed a tool-based approach to help users avoid bugs
-in GUI applications. Their approach monitors user's action in the background,
-and gives a user a warning as well as the opportunity to abort the action, when
+in GUI applications. Their approach monitors a user's action in the background,
+and gives a warning as well as the opportunity to abort the action, when
 a user attempts an action that has led to problems in the past. 
-As a comparison, our work aims to find unknown errors in multithreaded
-GUI applications, while their work aims to prevent an existing bug
-from happening again.
-%is significantly different than their
+Their work aims to prevent an existing bug from happening again.
+By contrast, our work aims to find unknown errors.
 
@@
 nullness analysis, class analysis, and termination analysis.  However,
-their framework does not support detecting the invalid thread access
+their framework does not support detecting invalid-thread-access
 errors, and uses a quite different abstraction than ours.
@@
 thread access error detection problem for multithreaded GUI applications, and
-our core technique is a general one that can be tailored for
-various GUI frameworks.
+our core technique has been tailored for four GUI frameworks.
 
@@
 A rich body of techniques have been developed to detect bugs in multithreaded programs~\cite{Huang:2011:PPC:2001420.2001438, Weeratunge:2010, Huang:2011:EST}.
-%Active testing frameworks like AssertFuzzer~\cite{Sen:2008} uses the trace information to detect
-%and create atomicity schedule violations.
 Static analysis tools such as Chord~\cite{Naik:2006}
- explore multithreaded bugs by statically analyzing the program. Runtime
-analysis tools such as Eraser~\cite{Savage:1997}  dynamically detect concurrency bugs using the lockset
-algorithms or some criteria based automata. 
-%Bodden and Havelund~\cite{Bodden:2008} uses AOP for
-%race detection by providing three novel pointcuts to the AspectJ language.
-More recently, Goldilock~\cite{Elmas:2007} uses the hybrid model that combines the happens-before and lock-based
+explore multithreaded programs. Runtime
+analysis tools such as Eraser~\cite{Savage:1997}  dynamically detect concurrency bugs using lockset
+algorithms or some criteria-based automata. 
+More recently, Goldilocks~\cite{Elmas:2007} uses a
+hybrid model that combines the happens-before and lock-based
 approaches to identify data races based on an execution.
-%By exploiting the insight
-%that a full generality of the happens-before is unnecessary in most data accesses,
-%FastTrack~\cite{Flanagan:2009} proposes an adaptive representation for the happen-before
-%relation to efficiently and precisely detect races at runtime.
-However, finding
-invalid thread access errors is quite different than detecting data races.
+However, finding invalid-thread-access errors is quite different than detecting data races.
 A data race occurs when two concurrent threads access
@@
 an invalid thread access error occurs when a non-UI thread accesses (reads or writes) a GUI object.
-Unlike detecting data races, finding invalid thread access error does not require monitoring every shared-memory
-reference and verify that consistent locking behavior is observed among different threads.
+Unlike detecting data races, finding an invalid-thread-access error does not require monitoring every shared-memory
+reference to verify that consistent locking behavior is observed among different threads.
 A technique only needs to track whether a non-UI thread can accesses a GUI object or not,
-and is much cheaper.
-How to leverage the recent advance in data race detection to 
-improve our technique is our future work.
-
-%Significantly different from the concurrency bug finding work....
-
-%They are often limited to detect errors manifested in a specific concrete execution.
+and is much cheaper. Leveraging data race detection to 
+improve our technique is future work.
 
@@
 By exhaustively exploring the thread scheduling space, a model checker can
-report counter examples for the potential bugs with a counter example.
-%For example,
-%CHESS~\cite{chess} dynamically explores the thread scheduling decisions to expose
-%concurrency bugs using a context-bounded approach. 
-%Shacham et al~\cite{Shacham:2007} uses
-%a model checker to construct the witness for data races reported by the lockset algorithm.
+report counterexamples as bug reports.
 Unfortunately, due to the exponential size of the search space,
 it is hard for model checking approaches to scale to a realistic multithreaded GUI application
- without compromising the detection capability. To our best knowledge,
-we are not aware of any software model checking approach can scale to the subjects
+ without compromising the error detection capability. 
+We are not aware of any software model checking approach that scales to programs
 as large as those used in our experiments (including the library code).
@@
 errors instead of being a general property checking tool. 
-It chooses call graph as a coarse-grained program representation with a
+It chooses the call graph as a coarse-grained program representation with a
 set of error filters, to achieve good scalability with reasonable accuracy.
@@
 %\noindent \textit{\textbf{Call Graph Construction Algorithms}}
-A lot of effort has been spent on building call graphs for
-Object-oriented programs~\cite{rta, kcfa, xta, inccg, Sundaresan:2000}.
-We briefly mention some of the highlights of call graph construction
-algorithms for Java here. Grove et al~\cite{kcfa} described a unified
+We briefly mention some call graph construction
+algorithms for Java. Grove et al.~\cite{kcfa} described a unified
 framework for expressing call graph construction algorithms, and
@@
 several low-cost call graph construction algorithms for Java.
-Sundaresan et al.~\cite{Sundaresan:2000} went beyond the% traditional
-CHA and RTA~\cite{rta} approaches and used type propagation
-to build a more precise call graph.
-However, the use of reflection makes
-those algorithms insufficient to build a complete call graph.
+Sundaresan et al.~\cite{Sundaresan:2000} went beyond the
+RTA~\cite{rta} approach and used type propagation
+to build a more precise call graph.  However,
+those algorithms do not build a complete call graph in the presence of reflection.
 As reflected in our experiments, using standard call graph algorithms
-misses errors in some Android applications. %, due to the incompleteness of the resulting graph.
+misses errors in some Android applications.
 
-To enable call graph construction in the presence of  reflection,
 Livshits et al.~\cite{Livshits:2005} presented a static analysis
@@
 reflective calls statically. Their approach focuses on standard Java
-reflection calls (e.g., \CodeIn{Class.forName}) instead of the
-framework-specific ones (e.g., \CodeIn{View.findViewById}).
-The standard call graph algorithms we used from WALA handles standard Java
+reflection calls (e.g., \CodeIn{Class.forName}) instead of
+framework-specific ones (e.g., \CodeIn{View.find-\\ViewById}).
+The standard call graph algorithms implemented in WALA, which we used
+in our experiments, actually handles standard Java
 reflection calls as~\cite{Livshits:2005} does, but still fails to build
@@
 and then replaces the \CodeIn{findViewById} call with the corresponding
-object creation expressions. In additiona, the Julia system does not handle
+object creation expressions. In addition, the Julia system does not handle
 native methods when building call graphs. In contrast, our technique provides
@@
 pass of off-line instrumentation. The reflection-aware call graph is created
-online by incerpting the standard call graph construction process.
+online by intercepting the standard call graph construction process.
 

### 2012-02-11 GUIErrorDetector/paper/introduction.tex
Small changes: add headings
tweak

@@
 
-The single-GUI-thread rule can be easily violated; since a spawned non-UI thread often needs to update
+The single-GUI-thread rule can be easily violated, since a spawned non-UI thread often needs to update
 the GUI  after its  task is finished.
@@
 Searching for ``SWTException:Invalid thread access'' in Eclipse's bug repository
-and discussion forum returns over 2732 bug reports and 351 distinct threads, respectively. 
+and discussion forum returns over 2732 bug reports and 351 distinct discussion threads, respectively. 
 We manually studied all 156 distinct \textit{confirmed} bug reports, and 
@@
 spawns a new thread on line 283. This newly created, non-UI thread calls back method
-\CodeIn{onSurfaceChanged} that accesses GUI objects on line 222,
+\CodeIn{onSurfaceChanged} that accesses GUI objects on line 222 of \CodeIn{LayerRenderer},
 causing an invalid thread access error. Our tool
@@
 by wrapping line 222 inside a \CodeIn{post} message-passing method\footnote{The
-\CodeIn{post} method in class \CodeIn{android.widget.View} is a
+\CodeIn{post} method in class \CodeIn{android.widget.View} is
 a standard way to send asynchronized messages to the UI-thread.}, as follows:
@@
 
-Such an approach is desirable for accesses from non-UI threads, but it is unnecessary
-and dangerous for accesses from the UI thread. Asynchronized message passing offers
+Such an approach is desirable for accesses from non-UI threads, but it is unnecessary.
+In our evaluation on real-world programs, we found that a simple analysis that
+requires GUI operations to be in a message issued
+an unacceptable number of warnings. %false positives and redundant warnings.
+Furthermore, this approach is dangerous for accesses from the UI thread. Asynchronized message passing offers
 no timing guarantee, so a GUI object may have already been
 disposed before the message sent to it arrives, causing other bugs.
-In our evaluation on real-world programs, we found a simple analysis that
-requires GUI operations to be in a message issues
-an unacceptable number of warnings. %false positives and redundant warnings.
 
@@
 that: our technique is effective (it found \bugs real-world errors
-from four supported frameworks and produced only \falses false positive warnings);
+ and produced only \falses false positive warnings);
 our reflection-aware call graph construction algorithm helps in
 finding errors in Android applications;
-and our proposed filters significantly reduce the number of warnings.
+and our proposed error filters significantly reduce the number of warnings.
 %false positives and redundant warnings.

### 2012-02-11 trunk/GUIErrorDetector/paper/related.tex
tweak

@@
+\tinystep
 \section{Related Work}
@@
 %\noindent \textit{\textbf{Analysis and Testing for GUI Applications}}
-Automated GUI testing is a challenging tasks~\cite{Bertolino:2007:STR:1253532.1254712,
+Automated GUI testing is a challenging task~\cite{Bertolino:2007:STR:1253532.1254712,
 Harrold:2000:TR:336512.336532}.
- Many GUI analysis and testing techniques have been proposed in the past decade.
-Existing techniques automate
-some aspect(s) of GUI testing including model creation
-(for model-based testing)~\cite{androidtesting}, %, Xie:2006:MTC:1172962.1172990},
+Various techniques automate GUI testing including
+%model creation
+%(for model-based testing)~\cite{androidtesting}, %, Xie:2006:MTC:1172962.1172990},
 test generation~\cite{YuanMemonICSE2007},
@@
 By exhaustively exploring the thread scheduling space, a model checker can
-report counter examples for the potential bugs with a counter example.
-%For example,
-%CHESS~\cite{chess} dynamically explores the thread scheduling decisions to expose
-%concurrency bugs using a context-bounded approach. 
-%Shacham et al~\cite{Shacham:2007} uses
-%a model checker to construct the witness for data races reported by the lockset algorithm.
+report counterexamples as bug reports.
 Unfortunately, due to the exponential size of the search space,
 it is hard for model checking approaches to scale to a realistic multithreaded GUI application
- without compromising the detection capability. To our best knowledge,
-we are not aware of any software model checking approach can scale to subjects
+ without compromising the error detection capability. 
+We are not aware of any software model checking approach that scales to programs
 as large as those used in our experiments (including the library code).
@@
 Sundaresan et al.~\cite{Sundaresan:2000} went beyond the
-CHA and RTA~\cite{rta} approaches and used type propagation
-to build a more precise call graph.
-However, the use of reflection makes
-those algorithms insufficient to build a complete call graph.
+RTA~\cite{rta} approach and used type propagation
+to build a more precise call graph.  However,
+those algorithms do not build a complete call graph in the presence of reflection.
 As reflected in our experiments, using standard call graph algorithms
-misses errors in some Android applications. %, due to the incompleteness of the resulting graph.
+misses errors in some Android applications.
 
-To enable call graph construction in the presence of  reflection,
 Livshits et al.~\cite{Livshits:2005} presented a static analysis
@@
 reflective calls statically. Their approach focuses on standard Java
-reflection calls (e.g., \CodeIn{Class.forName}) instead of the
-framework-specific ones (e.g., \CodeIn{View.findViewById}).
+reflection calls (e.g., \CodeIn{Class.forName}) instead of
+framework-specific ones (e.g., \CodeIn{View.find-\\ViewById}).
 The standard call graph algorithms implemented in WALA, which we used
-in our experiments, actually handle standard Java
+in our experiments, actually handles standard Java
 reflection calls as~\cite{Livshits:2005} does, but still fails to build

### 2012-02-11 trunk/GUIErrorDetector/paper/evaluation.tex
spell checks

@@
 to drag and drop files to their Amazon S3 accounts. SudokuSolver~\cite{sudokusolver}
-computes Sudoku solutions efficiently using mutlithreaded execution.
+computes Sudoku solutions using mutlithreaded execution.
 
@@
 on lines 10 and 21 in Figure~\ref{fig:detectalgorithm}, respectively)
-to the corresponding statck operations (\CodeIn{pop} and \CodeIn{pushAll}).
+to the corresponding stack operations (\CodeIn{pop} and \CodeIn{pushAll}).
 This variant found 11 errors in total and missed 1 error in the FileBunker subject.
@@
 physical memory (1GB is allocated for JVM), running Fedora 16.
-For the most time-consuming subject, MyTracks, our tool finished the whole analysis
-within 209 seconds using the most expensive call graph construction
-algorithm: the reflection-aware 1-CFA algorithm. Analyzing
-other subjects using different algorithms took less time.
-The performance has not been tuned, and we believe
-that it could be improved further.
+For the most time-consuming subject, S3dropbox, our tool finished the whole analysis
+within 252 seconds using the most expensive 1-CFA call graph construction
+algorithm. Analyzing other subjects using different algorithms took less time.
+The percentage of call graph construction cost ranges
+from 33.4\% (Fennec) to 91.1\% (VirgoFTP) out of
+the total analysis time among all evaluated programs.
+%The performance has not been tuned, and we believe
+%that it could be improved further.
 

### 2012-02-11 trunk/GUIErrorDetector/paper/introduction.tex
spell checks

@@
 by wrapping line 222 inside a \CodeIn{post} message-passing method\footnote{The
-\CodeIn{post} method in class \CodeIn{android.widget.View} is a
-a standard way to send asynchronized messages to the UI-thread.}, as follows:
+\CodeIn{post} method in class \CodeIn{android.widget.View} is
+a standard way to send asynchronous messages to the UI-thread.}, as follows:
 
@@
 Such an approach is desirable for accesses from non-UI threads, but it is unnecessary.
-In our evaluation on real-world programs, we found a simple analysis that
+In our evaluation on real-world programs, we found that a simple analysis that
 requires GUI operations to be in a message issued

### 2012-02-11 trunk/GUIErrorDetector/paper/evaluation.tex
address the comments by jamie

@@
 Java methods that a native method may call, and then added \annotationnum \CodeIn{@CalledByNativeMethods}
-annotations for it. Two subjects MyTracks and Fennec employ a customized pattern
+annotations for it. Two subjects, MyTracks and Fennec, employ a customized pattern
 to interact with the GUI framework. For example, in MyTracks, all non-UI
@@
 In this experiment, none of the paper
-authors was familiar with the subjects; but we found it is quite easy
+authors was familiar with the subjects, but we found it was quite easy
 to add extra annotations and user-defined filters. All these
@@
 
-As shown Table~\ref{table:results},  our tool found
+As shown in Table~\ref{table:results},  our tool found
 real errors in each subject program. Using the 1-CFA
@@
 protection and thus triggers the error.
-This error has been reported by other users 13 months after the
+This error was reported by other users 13 months after the
 buggy code was checked in, and fixed by developers.
@@
 
-\noindent \textbf{\textit{Summary.}} Although a static analysis may
-issue false positives or redundant reports, a set of well-designed
-error filters can remove most of them.
+\noindent \textbf{\textit{Summary.}} Our proposed error filters are 
+effective in reducing the number of warnings.
+%Although a static analysis may
+%issue false positives or redundant reports, a set of well-designed
+%error filters can remove most of them.
 %Heuristic filter, effective.

### 2012-02-11 GUIErrorDetector/paper/evaluation.tex
Edits to search strategy evaluation.  Also formatting tweaks

@@
 
-We used a set of open-source projects from Sourceforge, Google code,
+We used a set of open-source projects from SourceForge, Google Code,
 and the Eclipse plugin
-market as evaluation subjects. To choose subjects for each supported GUI framework,
+marketplace as evaluation subjects. To choose subjects for each supported GUI framework,
 we first searched for the framework keywords (e.g., ``Java Swing'' or ``Java SWT'')
@@
 Java methods that a native method may call, and then added \annotationnum \CodeIn{@CalledByNativeMethods}
-annotations for it. Two subjects MyTracks and Fennec employ a customized pattern
+annotations for it. Two subjects, MyTracks and Fennec, employ a customized pattern
 to interact with the GUI framework. For example, in MyTracks, all non-UI
-threads are initialized via using the library method \CodeIn{android.os.} \CodeIn{handler.handleCallback}.
+threads are initialized via using the library method \CodeIn{android.os.}\discretionary{}{}{}\CodeIn{handler.handleCallback}.
 % the \CodeIn{safeInvokeXX}
@@
 
-Our error detection algorithm in Figure~\ref{fig:detectalgorithm} uses a
-slightly modified BFS to search for
-potential single-GUI-thread violations. However, standard BFS
-and other graph search strategies such as
-DFS and exhaustive path search can also be employed. To
-understand trade-offs between using different search strategies, we 
-implemented three variants of the algorithm in Figure~\ref{fig:detectalgorithm}, and
-evaluated them on the same subjects with the identical environment settings.
+The error detection algorithm in Figure~\ref{fig:detectalgorithm} uses a
+separate BFS for each entry node.  This section evaluates three variants:
+a multiple-source BFS; a separate DFS for each entry node; and exhaustive
+search.
 
-The first variant uses standard BFS for graph traversal by deleting
-lines 6 and 23 in Figure~\ref{fig:detectalgorithm}, and changing
-7 in Figure~\ref{fig:detectalgorithm} to:
+The first variant uses a single BFS, but starting at multiple sources.  It deletes
+lines 6 and 24 in Figure~\ref{fig:detectalgorithm} and changes line
+7 to:
 
 \vspace{0.2mm}
-$\mathit{worklist}$ $\leftarrow$ $\bigcup_{entry \in entryNodes}$ getReachableStarts($\mathit{entry}$)
+$\mathit{worklist}$ $\leftarrow$ $\bigcup_{\mathit{entry} \in \mathit{entryNodes}}$ getReachableStarts($\mathit{entry}$)
 \vspace{0.2mm}
 
-\noindent This variant returns the shortest path from \textit{any} \CodeIn{Thread.start()} node
-to \textit{any} UI-accessing node, rather than the shortest path from \textit{a given}
-\CodeIn{Thread.start()} node to \textit{any} UI-accessing node as the algorithm in
+\noindent This variant returns the shortest path from any \CodeIn{Thread.start()} node
+to any UI-accessing node, rather than the shortest path from each
+\CodeIn{Thread.start()} node to any UI-accessing node as the algorithm in
 Figure~\ref{fig:detectalgorithm} does.
-This variant found 10 errors in total and missed 1 error in S3dropbox and 1 error in
-SudokuSolver. This is because in BFS (either the standard BFS or our algorithm), each
-node will \textit{only} be visited once; but in the standard BFS, if a node has been covered
-in an error path from a \CodeIn{Thread.start()} node, that node will not be visited again
-even when the standard BFS traverses from another \CodeIn{Thread.start()} node, thus
-missing potential errors.
+This variant reported 10 errors and 12 false positives.   It missed 1 error in S3dropbox and 1 error in
+SudokuSolver.
+It visits every node in the call graph only once, rather than potentially
+once per entry node, but in so doing prunes out real error paths.
 
-The second variant uses DFS for graph traversal by changing
-the data structure of $\mathit{worklist}$ on line 7 in Figure~\ref{fig:detectalgorithm} to
-a stack, and changing queue operations (\CodeIn{dequeue} and \CodeIn{enqueueAll}
-on lines 10 and 21 in Figure~\ref{fig:detectalgorithm}, respectively)
-to the corresponding statck operations (\CodeIn{pop} and \CodeIn{pushAll}).
-This variant found 11 errors in total and missed 1 error in the FileBunker subject.
-The reason is that DFS tends to search deeper into the graph, and the path it returns
-may not be the shortest one and is more likely to be an infeasible path in practice.
+The second variant one DFS per entry node, by changing
+the $\mathit{worklist}$ on line 7 of Figure~\ref{fig:detectalgorithm} to
+a stack, and changing queue operations dequeue and enqueueAll
+on lines 10 and 21
+to pop and pushAll.
+This variant reported 11 errors and 10 false positives.  It missed 1 error in FileBunker.
+DFS tends to search deeper into the graph and return longer paths that are
+more likely to be infeasible.
 %For the FileBunker subject, paths
@@
 path spawns a new thread and accesses GUI objects without using safe UI methods.
-This variant ran out of memory on all subjects. We checked
-the explored paths before the algorithm terminated, and found none of them
-revealed a real error. This is because the number of
-non-cyclic paths in a graph is exponential in the graph size.
-For a realistic call graph which often contains thousands of nodes,
+This variant ran out of memory on all subjects, and did not output any real
+errors before it terminated.  The number of
+non-cyclic paths in a graph is exponential in the graph size, and it 
 it is infeasible to enumerate all paths.
+for a realistic call graph, which often contains thousands of nodes.
 %only a very few amount of paths can be enumerated within a practical amount of time.
+
+Given a sound call graph, exhaustive search is sound because it does not
+miss any possible errors.  However, it is impractical.  Compared to
+exhaustive search, using BFS or DFS can be viewed as a heuristic filtering
+step, akin to the filters of Section~\ref{sec:heuristic}.
+%   The algorithm of
+% Figure~\ref{fig:detectalgorithm}, which does multiple BFS traversals, does
+% less pruning, and runs more slowly, than the variant that does one
+% multi-source BFS, but
+ The heuristics of Section~\ref{sec:heuristic} are
+more effective at retaining real errors than the search variants.
 
@@
 \noindent \textbf{\textit{Summary.}} Our algorithm finds more errors than
-using standard BFS, DFS and exhaustive search in error detection.
+using multi-source BFS, DFS, or exhaustive search.
 
@@
 In our evaluation, the studied subjects were selected with a bias towards popularity from
-well-known open-source repositories. Another threat is that we only employed three
+open-source repositories. Another threat is that we only employed three
 widely-used call graph construction algorithms (i.e., RTA, 0-CFA, and 1-CFA) 
@@
 proposed filters are useful in reducing the number of warnings.
+
+%%% Local Variables: 
+%%% mode: latex
+%%% TeX-master: "guierror"
+%%% TeX-command-default: "PDF"
+%%% End:
+
+%  LocalWords:  multithreaded SWT multithreading 2mm VirgoFTP UI GMail S3
+%  LocalWords:  FileBunker ArecaBackup plugins HudsonEclipse EclipseRunner
+%  LocalWords:  S3dropbox SudokuSolver Sudoku mutlithreaded SGTPuzzler 9pt
+%  LocalWords:  Fennec MyTracks LOC v9306 plugin LOCC RTA CFA
+%  LocalWords:  CalledByNativeMethods

### 2012-02-11 trunk/GUIErrorDetector/paper/implementation.tex
Edits to search strategy evaluation.  Also formatting tweaks

@@
 
-\item \textbf{Call graph entry nodes: } the main method. Like a normal Java program,
+\item \textbf{Call graph entry nodes:}  the main method. Like a normal Java program,
 a SWT desktop application has a single main method as the entry point. By default,
@@
 
-\item \textbf{UI-accessing nodes: } the \CodeIn{Widget.checkWidget}
-and \CodeIn{Display.} \CodeIn{checkDevice} methods. SWT performs
+\item \textbf{UI-accessing nodes:}  the \CodeIn{Widget.checkWidget}
+and \CodeIn{Display.}\discretionary{}{}{}\CodeIn{checkDevice} methods. SWT performs
 runtime checking before accessing a GUI object via these methods.
@@
 
-\item \textbf{Safe UI methods: } \CodeIn{Display.asyncExec}
+\item \textbf{Safe UI methods:}  \CodeIn{Display.asyncExec}
 and \CodeIn{Display.syncExec}. SWT provides these two methods
@@
 
-\item \textbf{Call graph entry nodes: } all user code methods that override
+\item \textbf{Call graph entry nodes:}  all user code methods that override
  SWT GUI event handling methods. Eclipse
@@
 
-\item \textbf{Safe UI methods: } 
+\item \textbf{Safe UI methods:}  
 \CodeIn{SwingUtilities.}\CodeIn{invokeLater} and \CodeIn{SwingUti-\\lities.invokeAndWait}, which execute code on the UI thread.
@@
 
-\item \textbf{Call graph entry nodes: }in an Android application,
+\item \textbf{Call graph entry nodes:} in an Android application,
 an \CodeIn{Activity} object is created and manipulated by the UI thread. Thus, we treat
@@
 
-\item \textbf{UI-accessing nodes: }the \CodeIn{ViewRoot.checkThread} method.
+\item \textbf{UI-accessing nodes:} the \CodeIn{ViewRoot.checkThread} method.
 Like SWT, Android explicitly performs runtime checking before accessing
@@
 
-\item \textbf{Safe UI methods: } \CodeIn{View.post}
+\item \textbf{Safe UI methods:}  \CodeIn{View.post}
 and \CodeIn{View.postDelay}, which execute code on the UI thread.

### 2012-02-11 trunk/GUIErrorDetector/paper/technique.tex
Undo many spacing hacks, use uniform spacing throughout the paper

@@
 multiple methods that access GUI objects, such as:
-\vspace{-1mm}
+
+\pagebreak[3]
+\vspace{-2mm}                   %
 \begin{CodeOut}
@@
 of heuristic filters.
+
+%%% Local Variables: 
+%%% mode: latex
+%%% TeX-master: "guierror"
+%%% TeX-command-default: "PDF"
+%%% End:

### 2012-02-11 GUIErrorDetector/paper/evaluation.tex
Undo many spacing hacks, use uniform spacing throughout the paper

@@
 
-\begin{myindentpar}{-2mm}
+% \begin{myindentpar}{-2mm}
 \begin{itemize}%\addtolength{\itemsep}{-0.5\baselineskip}
-\Item \textbf{SWT desktop applications.}
+\item \textbf{SWT desktop applications.}
 %VirgoFTP~\cite{virgo} and FileBunker~\cite{filebunker} are two useful SWT desktop applications.
@@
 
-\vspace{0.5mm}
-\vspace{0.5mm}
+% \vspace{0.5mm}
+% \vspace{0.5mm}
 
-\Item \textbf{Eclipse plugins.}
+\item \textbf{Eclipse plugins.}
 HudsonEclipse~\cite{hudson} monitors Hudson build status from Eclipse.
@@
 
-\vspace{0.5mm}
+% \vspace{0.5mm}
 
-\Item \textbf{Swing applications.} %S3dropbox~\cite{s3dropbox} and SudokuSolver~\cite{sudokusolver} are two Swing desktop applications.
+\item \textbf{Swing applications.} %S3dropbox~\cite{s3dropbox} and SudokuSolver~\cite{sudokusolver} are two Swing desktop applications.
 S3dropbox~\cite{s3dropbox}  allows users
@@
 
-\vspace{0.5mm}
+% \vspace{0.5mm}
 
-\Item  \textbf{Android applications.} %MyTracks~\cite{mytracks}, Fennec~\cite{fennec}, and SGTPuzzles~\cite{sgtpuzzles} are three Android applications.
+\item  \textbf{Android applications.} %MyTracks~\cite{mytracks}, Fennec~\cite{fennec}, and SGTPuzzles~\cite{sgtpuzzles} are three Android applications.
 SGTPuzzler~\cite{sgtpuzzles} is a single-player logic game.
@@
 \end{itemize}
-\end{myindentpar}
+% \end{myindentpar}
 
@@
 80.\ttrcb
-\smallstep
 \end{alltt}
 \end{CodeOut}
-\smallstep
-\vspace*{-2.0ex} \Caption{{\label{fig:swingerror} An
+\vspace*{-15pt}
+\Caption{{\label{fig:swingerror} An
 invalid thread access error reported by our tool
@@
 \end{CodeOut}
-\smallstep
-\vspace*{-2.0ex} \Caption{{\label{fig:pluginerror} An
+\vspace*{-15pt}
+\Caption{{\label{fig:pluginerror} An
 invalid thread access error reported by our tool
@@
 call graph construction algorithms such as XTA~\cite{xta}, VTA~\cite{Sundaresan:2000} or
-an incremental algorithm~\cite{inccg} might achieve divergent results.
+an incremental algorithm~\cite{inccg} might achieve different results.
 

### 2012-02-11 GUIErrorDetector/paper/introduction.tex
Undo many spacing hacks, use uniform spacing throughout the paper

@@
 \CodeIn{post} method in class \CodeIn{android.widget.View} is
-a standard way to send asynchronized messages to the UI-thread.}, as follows:
+a standard way to send asynchronous messages to the UI-thread.}, as follows:
 
@@
 %$\rightarrow$\CodeIn{ \scriptsize{android.view.ViewRoot.checkThread()}}
-\tinystep
-\vspace*{-3.0ex} \Caption{{\label{fig:report} Our tool reports
+\vspace*{-15pt}
+\Caption{{\label{fig:report} Our tool reports
 a method call chain that reveals the potential error in
@@
 tool implementation is publicly available at
-\url{http://guierrordetector.googlecode.com}.
+{\smaller\url{http://guierrordetector.googlecode.com}}.
 
@@
 \end{itemize}
+
+%%% Local Variables: 
+%%% mode: latex
+%%% TeX-master: "guierror"
+%%% TeX-command-default: "PDF"
+%%% End:

### 2012-02-11 trunk/GUIErrorDetector/paper/evaluation.tex
Spacing hacks

@@
 
-\begin{myindentpar}{-2mm}
+\vspace{-5pt}
+
+% \begin{myindentpar}{-2mm}
 \begin{itemize}%\addtolength{\itemsep}{-0.5\baselineskip}
-\Item \textbf{SWT desktop applications.}
+\item \textbf{SWT desktop applications.}
 %VirgoFTP~\cite{virgo} and FileBunker~\cite{filebunker} are two useful SWT desktop applications.
@@
 to interact with the GUI framework. For example, in MyTracks, all non-UI
-threads are initialized via using the library method \CodeIn{android.os.} \CodeIn{handler.handleCallback}.
+threads are initialized via using the library method \CodeIn{android.os.}\discretionary{}{}{}\CodeIn{handler.handleCallback}.
 % the \CodeIn{safeInvokeXX}
@@
 
-Our error detection algorithm in Figure~\ref{fig:detectalgorithm} uses a
-slightly modified BFS to search for
-potential single-GUI-thread violations. However, standard BFS
-and other graph search strategies such as
-DFS and exhaustive path search can also be employed. To
-understand trade-offs between using different search strategies, we 
-implemented three variants of the algorithm in Figure~\ref{fig:detectalgorithm}, and
-evaluated them on the same subjects with the identical environment settings.
+The error detection algorithm in Figure~\ref{fig:detectalgorithm} uses a
+separate BFS for each entry node.  This section evaluates three variants:
+a multiple-source BFS; a separate DFS for each entry node; and exhaustive
+search.
 
-The first variant uses standard BFS for graph traversal by deleting
-lines 6 and 24 in Figure~\ref{fig:detectalgorithm}, and changing
-7 in Figure~\ref{fig:detectalgorithm} to:
+The first variant uses a single BFS, but starting at multiple sources.  It deletes
+lines 6 and 24 in Figure~\ref{fig:detectalgorithm} and changes line
+7 to:
 
 \vspace{0.2mm}
-$\mathit{worklist}$ $\leftarrow$ $\bigcup_{entry \in entryNodes}$ getReachableStarts($\mathit{entry}$)
+$\mathit{worklist}$ $\leftarrow$ $\bigcup_{\mathit{entry} \in \mathit{entryNodes}}$ getReachableStarts($\mathit{entry}$)
 \vspace{0.2mm}
 
-\noindent This variant returns the shortest path from \textit{any} \CodeIn{Thread.start()} node
-to \textit{any} UI-accessing node, rather than the shortest path from \textit{a given}
-\CodeIn{Thread.start()} node to \textit{any} UI-accessing node as the algorithm in
+\noindent This variant returns the shortest path from any \CodeIn{Thread.start()} node
+to any UI-accessing node, rather than the shortest path from each
+\CodeIn{Thread.start()} node to any UI-accessing node as the algorithm in
 Figure~\ref{fig:detectalgorithm} does.
-This variant found 10 errors in total and missed 1 error in S3dropbox and 1 error in
-SudokuSolver. This is because in BFS (either the standard BFS or our algorithm), each
-node will \textit{only} be visited once; but in the standard BFS, if a node has been covered
-in an error path from a \CodeIn{Thread.start()} node, that node will not be visited again
-even when the standard BFS traverses from another \CodeIn{Thread.start()} node, thus
-missing potential errors.
+This variant reported 10 errors and 12 false positives.   It missed 1 error in S3dropbox and 1 error in
+SudokuSolver.
+It visits every node in the call graph only once, rather than potentially
+once per entry node, but in so doing prunes out real error paths.
 
-The second variant uses DFS for graph traversal by changing
-the data structure of $\mathit{worklist}$ on line 7 in Figure~\ref{fig:detectalgorithm} to
-a stack, and changing queue operations (\CodeIn{dequeue} and \CodeIn{enqueueAll}
-on lines 10 and 21 in Figure~\ref{fig:detectalgorithm}, respectively)
-to the corresponding stack operations (\CodeIn{pop} and \CodeIn{pushAll}).
-This variant found 11 errors in total and missed 1 error in the FileBunker subject.
-The reason is that DFS tends to search deeper into the graph, and the path it returns
-may not be the shortest one and is more likely to be an infeasible path in practice.
+The second variant one DFS per entry node, by changing
+the $\mathit{worklist}$ on line 7 of Figure~\ref{fig:detectalgorithm} to
+a stack, and changing queue operations dequeue and enqueueAll
+on lines 10 and 21
+to pop and pushAll.
+This variant reported 11 errors and 10 false positives.  It missed 1 error in FileBunker.
+DFS tends to search deeper into the graph and return longer paths that are
+more likely to be infeasible or to be removed by the filters.
 %For the FileBunker subject, paths

### 2012-02-11 GUIErrorDetector/paper/introduction.tex
Spacing hacks

@@
 
-\vspace{-2mm}
+\makeatletter
+\newenvironment{myquotation}
+               {\list{}{\listparindent=0pt%whatever you need
+                        \itemindent    \listparindent
+                        \leftmargin=10pt%  whatever you need
+                        \rightmargin=0pt%whatever you need
+                        \topsep=0pt%%%%%  whatever you need
+                        \parsep        \z@ \@plus\p@}%
+                \item\relax}
+               {\endlist}
+\makeatother
 
-\begin{quote}
+\begin{myquotation}
 All GUI objects, including visual components and data models, must be
  accessed exclusively from the \textit{event dispatching thread}.
-\end{quote}
-
-\vspace{-2mm}
+\end{myquotation}
 
@@
 
+\vspace{-5pt}
+
 \tinystep

### 2012-02-11 GUIErrorDetector/paper/evaluation.tex
Clarify "infeasible" claim about DFS.
fixing typos

@@
 include end-user applications, programming tools, and games.
+
+\vspace{-5pt}
 
@@
 It visits every node in the call graph only once, rather than potentially
-once per entry node, but in so doing prunes out real error paths.
+once per entry node, but doing so prunes out real error paths.
 
-The second variant one DFS per entry node, by changing
+The second variant uses one DFS per entry node, by changing
 the $\mathit{worklist}$ on line 7 of Figure~\ref{fig:detectalgorithm} to
@@
 DFS tends to search deeper into the graph and return longer paths that are
-more likely to be infeasible.
+more likely to be infeasible or to be removed by the filters.
 %For the FileBunker subject, paths

### 2012-02-11 trunk/GUIErrorDetector/paper/evaluation.tex
Shorten a sentence

@@
 
+\label{sec:performance}
+
 \noindent \textbf{\textit{Performance and scalability.}} Our tool
@@
 algorithm. Analyzing other subjects using different algorithms took less time.
-The percentage of call graph construction cost ranges
-from 33.4\% (Fennec) to 91.1\% (VirgoFTP) out of
-the total analysis time among all evaluated programs.
+Call graph construction took 33--91\% of
+the total analysis time.
 %The performance has not been tuned, and we believe

### 2012-02-11 trunk/GUIErrorDetector/paper/implementation.tex
fix typoes, inconsistency

@@
 We instantiated the proposed technique for four widely-used
-GUI frameworks, namely SWT, Eclipse plugin development, Swing, and Android;
+GUI frameworks, namely SWT, Eclipse plugin framework, Swing, and Android;
 and implemented an error detection tool.
@@
 
-We instantiated our technique for the Eclipse plugin development framework as follows:
+We instantiated our technique for the Eclipse plugin framework as follows:
 

### 2012-02-11 trunk/GUIErrorDetector/paper/introduction.tex
fix typoes, inconsistency

@@
 enables new types of errors that may compromise robustness.
-We now discuss a standard programming rule for multithreaded GUIs, the consequences
+We now discuss a standard programming rule for multithreaded GUI applications, the consequences
 of violating it, and a technique for statically detecting such violations.
@@
 The filters introduce potential unsoundness to our algorithm, but in practice
-they work well and make our technique usable.
+they work well and make our technique more usable.
 
@@
 We implemented an invalid-thread-error detection tool that supports
-four popular GUI frameworks: SWT, Eclipse plugin environment,
+four popular GUI frameworks: SWT, Eclipse plugin framework,
 Swing, and Android. Swing and SWT are the
@@
 instantiated it for four
-popular GUI platforms: SWT, Eclipse plugin, Swing, and Android (Section~\ref{sec:implementation}). Our
+popular GUI frameworks: SWT, Eclipse plugin, Swing, and Android (Section~\ref{sec:implementation}). Our
 tool implementation is publicly available at
-\url{http://guierrordetector.googlecode.com}.
+{\smaller\url{http://guierrordetector.googlecode.com}}.
 

### 2012-02-11 GUIErrorDetector/paper/related.tex
fix typoes, inconsistency

@@
 Harrold:2000:TR:336512.336532}.
-Various techniques automate GUI testing including model creation
-(for model-based testing)~\cite{androidtesting}, %, Xie:2006:MTC:1172962.1172990},
+Various techniques automate GUI testing including
+%model creation
+%(for model-based testing)~\cite{androidtesting}, %, Xie:2006:MTC:1172962.1172990},
 test generation~\cite{YuanMemonICSE2007},
@@
 is a GUI testing framework for Java and Microsoft Windows applications. 
-Yuan and Memon~\cite{YuanMemonICSE2007} generate event-sequence-based test cases for GUI
+Yuan and Memon~\cite{YuanMemonICSE2007} generated event-sequence-based test cases for GUI
 programs using a structural event generation graph. 

### 2012-02-11 GUIErrorDetector/paper/technique.tex
tweak
Make fit in 11 pages
fix typoes, inconsistency

@@
 
+\vspace{1mm}
 \noindent {\textsc{\textbf{Definition 1 (UI Thread).}}} {The UI thread
@@
 takes charge of the application to handle events from the GUI.
-It spawns new threads to process lengthy operations in the background. }\vspace{1mm}
+It spawns new threads to process lengthy operations in the background. }
+\vspace{1mm}
 
@@
 dynamic call graph of every possible execution. 
-Our algorithm's reports are in terms of methods, as shown in Figure~\ref{fig:report}.
+Based on call graph, our algorithm's reports are in terms of methods, as shown in Figure~\ref{fig:report}.
 
@@
 that may be called by a native method, and added \annotationnum annotations for this program.
-We found such an annotation was useful: one error
+We found such annotations were useful: one error
 is only reported when using the user-provided annotations.
@@
 
-\subsubsection{Sound Filters}
+% \subsubsection{Sound Filters}
 
@@
 
-\subsubsection{Heuristic Filters}
+% \subsubsection{Heuristic Filters}
 %\item

### 2012-02-11 GUIErrorDetector/paper/evaluation.tex
trivial edit

@@
 non-cyclic paths in a graph is exponential in the graph size, and it 
-it is infeasible to enumerate all paths.
+it is infeasible to enumerate all paths
 for a realistic call graph, which often contains thousands of nodes.

### 2012-03-19 GUIErrorDetector/paper/review/response.txt
initial draft

Thanks for your helpful comments.

We agree with reviewer #1 and #2 that this paper addresses one kind of
error (i.e., the invalid thread access error) in GUI application.
However, as shown in Sec 1.2, this error is important, pervasive, and
severe in developing multithreaded GUI applications, and there are no
effective solutions yet. As part of this paper’s contribution is
identifying the invalid thread access problem. We keep our solution
simple to make it generally applicable and sufficient to detect many
real errors [*is such argument useful?*], instead of focusing on finding
certain sophisticated errors. On the other hand, the core idea of
formulating invalid thread access error detection as source-sink
reachability analysis can be extended to other domains, such as finding
Null pointer errors (does a null pointer reach a dereference?), security
vulnerability (does a tainted input reach a security-critical operation?),
or IO-related errors (e.g., does a closed file reach a read operation?).

Reviewer #1 requests additional clarification for Sec. 4.3.4. Here,
by “sound” graph visit algorithm, we mean one that will not miss any true
error path. Given a conservative call graph, BFS and DFS are not sound,
because BFS returns the shortest path and DFS returns the first path it
sees when searching in deep of the graph.  Both of them may return the
false positive paths or miss the true error paths.  We agree that exhaustive
search may not report the exact error path as it appears at runtime, since
static graph traversal cannot precisely reason about the number of loops a
real program execution may take. However, exhaustive path enumeration is
still sound in that it will not miss error paths, since it lists all
non-cyclic paths from a starting node to UI-accessing nodes via thread
spawning node (i.e., Thread.start()), even if a UI-accessing or thread
spawning node is in a cycle. [*I am not quite satisfied with this argument,
but not sure how to make it better*]

### 2012-03-19 trunk/GUIErrorDetector/paper/review/response.txt
Use ASCII

--- 2012-03-19 GUIErrorDetector/paper/review/response.txt
@@
 severe in developing multithreaded GUI applications, and there are no
-effective solutions yet. As part of this paper’s contribution is
+effective solutions yet. As part of this paper's contribution is
 identifying the invalid thread access problem. We keep our solution
@@
 Reviewer #1 requests additional clarification for Sec. 4.3.4. Here,
-by “sound” graph visit algorithm, we mean one that will not miss any true
+by "sound" graph visit algorithm, we mean one that will not miss any true
 error path. Given a conservative call graph, BFS and DFS are not sound,

### 2012-03-20 GUIErrorDetector/paper/review/response.txt
Edit response to reviews.

@@
-Thanks for your helpful comments.
+We thank the reviewers for their comments.
 
-We agree with reviewer #1 and #2 that this paper addresses one kind of
-error (i.e., the invalid thread access error) in GUI application.
-However, as shown in Sec 1.2, this error is important, pervasive, and
-severe in developing multithreaded GUI applications, and there are no
-effective solutions yet. As part of this paper’s contribution is
-identifying the invalid thread access problem. We keep our solution
-simple to make it generally applicable and sufficient to detect many
-real errors [*is such argument useful?*], instead of focusing on finding
-certain sophisticated errors. On the other hand, the core idea of
-formulating invalid thread access error detection as source-sink
-reachability analysis can be extended to other domains, such as finding
-Null pointer errors (does a null pointer reach a dereference?), security
-vulnerability (does a tainted input reach a security-critical operation?),
-or IO-related errors (e.g., does a closed file reach a read operation?).
+We agree that our technique is simple -- but we view elegance as a positive
+rather than a negative!  Part of our contribution is the observation that
+an approach, which is easy to understand and to verify, is also effective
+in solving an important problem that plagues real developers.
 
-Reviewer #1 requests additional clarification for Sec. 4.3.4. Here,
-by “sound” graph visit algorithm, we mean one that will not miss any true
-error path. Given a conservative call graph, BFS and DFS are not sound,
-because BFS returns the shortest path and DFS returns the first path it
-sees when searching in deep of the graph.  Both of them may return the
-false positive paths or miss the true error paths.  We agree that exhaustive
-search may not report the exact error path as it appears at runtime, since
-static graph traversal cannot precisely reason about the number of loops a
-real program execution may take. However, exhaustive path enumeration is
-still sound in that it will not miss error paths, since it lists all
-non-cyclic paths from a starting node to UI-accessing nodes via thread
-spawning node (i.e., Thread.start()), even if a UI-accessing or thread
-spawning node is in a cycle. [*I am not quite satisfied with this argument,
-but not sure how to make it better*]
+A reviewer asked why breadth/depth first search is not sound.  The reason
+is that breadth/depth first search visits every node, but does not traverse
+every path to visit that node.  For example, suppose that there exists some
+fault-revealing path between entry node E and UI-access node U.  A sound
+algorithm is one that reports a fault-revealing path between entry node E
+and UI-access node U.  An unsound algorithm might report an infeasible (and
+therefore non-fault-revealing) path between the nodes.  Figure 8 gives a
+concrete example:  for the graph of Figure 8(b), a shortest-path
+(depth-first) algorithm does report a path between entry() and uiAcc(), but
+not one that reveals the problem.  We can clarify this issue in the paper.
+
+With regard to applicability and generalization, we agree that we have
+applied our technique to one specific (but important) problem.  There is a
+rich history of testing and analysis problems being cast as reachability
+(the work of Tom Reps is one example).  We believe that other problems,
+such as detecting security vulnerabilities, can also be formulated as path
+reachability.

### 2012-03-21 trunk/GUIErrorDetector/paper/review/response.txt
Small tweaks to response

@@
-Thanks for your helpful comments.
+We thank the reviewers for their comments.
 
-We agree with reviewer #1 and #2 that this paper addresses one kind of
-error (i.e., the invalid thread access error) in GUI application.
-However, as shown in Sec 1.2, this error is important, pervasive, and
-severe in developing multithreaded GUI applications, and there are no
-effective solutions yet. As part of this paper's contribution is
-identifying the invalid thread access problem. We keep our solution
-simple to make it generally applicable and sufficient to detect many
-real errors [*is such argument useful?*], instead of focusing on finding
-certain sophisticated errors. On the other hand, the core idea of
-formulating invalid thread access error detection as source-sink
-reachability analysis can be extended to other domains, such as finding
-Null pointer errors (does a null pointer reach a dereference?), security
-vulnerability (does a tainted input reach a security-critical operation?),
-or IO-related errors (e.g., does a closed file reach a read operation?).
+We agree that our technique is simple -- but we view elegance as a positive
+rather than a negative!  Part of our contribution is the observation that
+an approach, that is easy to understand and to verify, is also effective
+in solving an important problem that plagues real developers.
 
-Reviewer #1 requests additional clarification for Sec. 4.3.4. Here,
-by "sound" graph visit algorithm, we mean one that will not miss any true
-error path. Given a conservative call graph, BFS and DFS are not sound,
-because BFS returns the shortest path and DFS returns the first path it
-sees when searching in deep of the graph.  Both of them may return the
-false positive paths or miss the true error paths.  We agree that exhaustive
-search may not report the exact error path as it appears at runtime, since
-static graph traversal cannot precisely reason about the number of loops a
-real program execution may take. However, exhaustive path enumeration is
-still sound in that it will not miss error paths, since it lists all
-non-cyclic paths from a starting node to UI-accessing nodes via thread
-spawning node (i.e., Thread.start()), even if a UI-accessing or thread
-spawning node is in a cycle. [*I am not quite satisfied with this argument,
-but not sure how to make it better*]
+A reviewer asked why breadth/depth first search is not sound.  The reason
+is that breadth/depth first search visits every node, but does not traverse
+every path to visit that node.  For example, suppose that there exists some
+fault-revealing path between entry node E and UI-access node U.  A sound
+algorithm is one that reports some fault-revealing path between entry node
+E and UI-access node U.  An unsound algorithm might report an infeasible
+(and therefore non-fault-revealing) path between the nodes.  Figure 8 gives
+a concrete example:  for the graph of Figure 8(b), a shortest-path
+(depth-first) algorithm does report a path between entry() and uiAcc(), but
+not one that reveals the problem.  We can clarify this issue in the paper.
+
+With regard to applicability and generalization, we agree that we have
+applied our technique to one specific (but important) problem.  There is a
+rich history of testing and analysis problems being cast as reachability
+(the work of Tom Reps is one example).  We believe that other problems,
+such as detecting security vulnerabilities, can also be formulated as path
+reachability.  We have not done so in the current paper.

### 2012-04-23 GUIErrorDetector/paper/evaluation.tex
Improve formatting

@@
 precise call graph built by 1-CFA. Nodes for constructors are omitted for brevity.
+\newline
 Using the less precise call graph, our error

### 2012-04-23 trunk/GUIErrorDetector/paper/technique.tex
Spacing hacks
Improve formatting

@@
 \begin{figure}[t]
+\vspace{3mm}
 \textbf{Input}: a Java program $\mathit{P}$\\
 \textbf{Output}: a call graph $\mathit{cg}$\\
-\vspace{-5mm}
+\vspace{-4mm}
 \begin{algorithmic}[1]

### 2012-04-23 trunk/GUIErrorDetector/paper/implementation.tex
No space around range dash, as in '1--3'

@@
 frameworks, the major framework-specific parts, corresponding to
-lines 3 -- 5 in Figure~\ref{fig:detectalgorithm}, are identifying
+lines 3--5 in Figure~\ref{fig:detectalgorithm}, are identifying
 \textbf{call graph entry nodes}, \textbf{UI-accessing nodes},

### 2012-04-23 trunk/GUIErrorDetector/paper/technique.tex
No space around range dash, as in '1--3'

@@
 then specifies entry nodes, UI-accessing nodes, and safe UI nodes
-for it on lines 3, 4, and 5, respectively. Lines 3 -- 5 are GUI framework-specific.
+for it on lines 3, 4, and 5, respectively. Lines 3--5 are GUI framework-specific.
 As an example, for a SWT desktop application, the entry nodes include
@@
 The algorithm uses Breadth-First Search (BFS) to search for reachable UI-accessing
-methods (lines 9 -- 23).
+methods (lines 9--23).
 The algorithm stops the traversal if it reaches a UI-accessing
-method (lines 15 -- 17) or a safe UI method (lines 18, 19).
+method (lines 15--17) or a safe UI method (lines 18, 19).
 %Specifically, it uses a queue to keep track of the nodes to be visited (line 7),
@@
 Any call graph construction algorithm can be used (line 2). The algorithm
-is parameterized by the three methods in lines 3 -- 5 which are specific to each GUI framework
+is parameterized by the three methods in lines 3--5 which are specific to each GUI framework
  as described in Section~\ref{sec:platforms}.
@@
 \caption{A reflection-aware call graph construction algorithm. Lines
-1 -- 7 are a simple program transformation to replace reflection calls
+1--7 are a simple program transformation to replace reflection calls
 with object creations, and line 8 builds the call graph using
@@
 object by looking up its id declared in the associated XML file. When this button
-is clicked, its event handling code (lines 9 -- 11) updates the text.
+is clicked, its event handling code (lines 9--11) updates the text.
 
@@
 has been created.  The algorithm is shown in Figure~\ref{fig:cgalgorithm}.
-It consists of two steps. The first step (lines 1 -- 7) is a simple program
+It consists of two steps. The first step (lines 1--7) is a simple program
 transformation to replace reflection calls with object creation expressions, and

### 2012-04-29 trunk/GUIErrorDetector/paper/abstract.tex
many tweaks
make some format adjustment

@@
 call graph for some modern GUI applications, because of heavy use of reflection.
-Thus, we present a method to build reflection-aware call graphs.
+Thus, our technique builds reflection-aware call graphs.
 
 We implemented our technique and instantiated it for four popular Java GUI
-platforms: SWT, the Eclipse plugin development framework, Swing, and
+frameworks: SWT, the Eclipse plugin framework, Swing, and
 Android. In an evaluation on \subnum programs comprising \totaloc LOC, our technique
-found both previously-known and unknown errors.
+found 5 previously-known errors and 7 new ones.
 
 \end{abstract}
+
+\smallskip
+\noindent
+\textbf{Categories and Subject Descriptors}:  
+D.2.5 [Software Engineering]: Testing and Debugging.
+\\
+\textbf{General Terms: }
+Reliability, Experimentation.
+\\
+\textbf{Keywords: }
+Static analysis, invalid thread access error.

### 2012-04-29 trunk/GUIErrorDetector/paper/introduction.tex
make some format adjustment

@@
 %ugly hack
-\subsection{\hspace{-1.1ex}\mbox{The}~\mbox{Single-thread}~\mbox{Rule}~\mbox{for}~\mbox{GUI}~\mbox{Object}~\mbox{Access}}
+%\subsection{\hspace{-1.1ex}\mbox{The}~\mbox{Single-thread}~\mbox{Rule}~\mbox{for}~\mbox{GUI}~\mbox{Object}~\mbox{Access}}
+
+\subsection{The Single-thread Rule}
 
@@
 Android~\cite{android}, Qt~\cite{qt}, and MacOS Cocoa~\cite{macos}
-adopt the \textit{single-GUI-thread rule}:
+adopt the \textit{single-GUI-thread rule} for GUI object access:
 

### 2012-04-29 trunk/GUIErrorDetector/paper/conclusion.tex
tweak
refine the related work section

@@
+\smallstep
 \section{Conclusion and Future Work}
@@
 filters to filter likely false positives and redundant warnings.
-%Since graphical user interfaces are often inadequately tested due
-%to the enormously large space of UI interactions and
-%extreme resource constraints during their development, we
-%believe that providing a static analysis can allow developers to find
-%more potential errors %before the application is released to customers (XXX),
-% to improve software reliability.
 We demonstrated the usefulness of our technique
@@
 positives is to integrate with
-dynamic analyses~\cite{Jiang:2008:PPS:1453101.1453110}
-or symbolic analyses~\cite{xie05:symstra, Pasareanu:2011, halfond09issta, BMF97}
+dynamic analyses~\cite{ZhangSBE2011}
+or symbolic analyses~\cite{xie05:symstra, Pasareanu:2011}
 by using more accurate information to guide call graph exploration.
@@
 plan to investigate how to apply recent advance in automated
-testing~\cite{Staats:2011:PTO:1985793.1985847, Jagannath:2011:IMU:2025113.2025145, Muccini_Bertolino_Inverardi_2004, Ricca:2001:ATW:381473.381476, Harman:2007}
+testing~\cite{ZhangSBE2011, Jagannath:2011:IMU:2025113.2025145}
 to the context of multithreaded GUI applications.

### 2012-04-29 trunk/GUIErrorDetector/paper/evaluation.tex
refine the related work section

@@
 \hspace*{-0.2cm}
-\setlength{\tabcolsep}{.70\tabcolsep}
+\setlength{\tabcolsep}{.6\tabcolsep}
 \begin{tabular}{|p{4.4cm}||c|c|c|c|}
@@
 \hspace*{-0.2cm}
-\setlength{\tabcolsep}{.15\tabcolsep}
+\setlength{\tabcolsep}{.14\tabcolsep}
 \begin{tabular}{|l||c|c|c||c|c|c||c|c|c||c|}
@@
   \centering
-  \includegraphics[scale=0.45]{cgexample}
+  \includegraphics[scale=0.44]{cgexample}
   \vspace*{-5.0ex}\caption {{\label{fig:ex} (a) shows example code, in which
@@
  \fontsize{9pt}{\baselineskip}\selectfont
-\setlength{\tabcolsep}{.40\tabcolsep}
+\setlength{\tabcolsep}{.34\tabcolsep}
 \hspace*{-0.2cm}
@@
 in our evaluation. Using other 
-call graph construction algorithms such as XTA~\cite{xta}, VTA~\cite{Sundaresan:2000} or
-an incremental algorithm~\cite{inccg} might achieve different results.
+call graph construction algorithms such as XTA~\cite{xta} or VTA~\cite{Sundaresan:2000} 
+ might achieve different results.
 

### 2012-04-29 trunk/GUIErrorDetector/paper/related.tex
refine the related work section

@@
 
-%\noindent \textit{\textbf{Analysis and Testing for GUI Applications}}
-Automated GUI testing is a challenging task~\cite{Bertolino:2007:STR:1253532.1254712,
-Harrold:2000:TR:336512.336532}.
+Automated GUI testing is a challenging task.
 Various techniques automate GUI testing including
@@
 test generation~\cite{YuanMemonICSE2007},
-test oracle creation~\cite{MemonFSE2000}, test execution~\cite{YuanCohenMemonTSE2011},
+test execution~\cite{YuanCohenMemonTSE2011},
 and test script repairing~\cite{Huang:2010:RGT:1828417.1828465, Daniel:2011:AGR:2002931.2002937}.
@@
 %\noindent \textit{\textbf{Finding Bugs in Multithreaded Programs}}
-A rich body of techniques have been developed to detect bugs in multithreaded programs~\cite{Huang:2011:PPC:2001420.2001438, Weeratunge:2010, Huang:2011:EST}.
+A rich body of techniques have been developed to detect bugs in multithreaded programs~\cite{Huang:2011:PPC:2001420.2001438, Naik:2006, Savage:1997, smc}.
 Static analysis tools such as Chord~\cite{Naik:2006}
@@
 algorithms or some criteria-based automata. 
-More recently, Goldilocks~\cite{Elmas:2007} uses a
-hybrid model that combines the happens-before and lock-based
-approaches to identify data races based on an execution.
+%More recently, Goldilocks~\cite{Elmas:2007} uses a
+%hybrid model that combines the happens-before and lock-based
+%approaches to identify data races based on an execution.
 However, finding invalid-thread-access errors is quite different than detecting data races.
@@
 
-An alternative way to find bugs in multithreaded programs is using model checking~\cite{Nori:2010:ESO, Inverardi:2000, Siegel:2008}.
+An alternative way to find bugs in multithreaded programs is using model checking~\cite{smc}.
 By exhaustively exploring the thread scheduling space, a model checker can

### 2012-04-30 trunk/GUIErrorDetector/paper/evaluation.tex
more edits to address reviewers' comments

@@
 an open library. Second, the subject must use multithreading in its implementation.
-Third, the subject must have undergone at least two years of active development,
-and it is listed in the first 3 result pages based on popularity. This permits us
-to exclude immature subjects that may contain obvious errors.
+Third, the subject is listed in the first 5 result pages.
+This permits us to exclude immature subjects that may contain obvious errors.
 
@@
 We submitted all \newbugs new errors
-to the subject developers. As of February 2012, 1 error in S3dropbox has been confirmed,
-we have reproduced 4 errors, and 2 errors in FileBunker and ArecaBackup
+to the subject developers. As of April 2012, 1 error in S3dropbox has been confirmed,
+we have reproduced 3 errors, and 3 errors in VirgoFTP, FileBunker and ArecaBackup
 had not yet been verified by the developers.
@@
 \begin{figure}[t]
-\hspace{4mm}\small{In class: com.tomczarniecki.s3.gui.DeleteBucketAction}
+\hspace{4mm}{In class: com.tomczarniecki.s3.gui.DeleteBucketAction}
 \vspace{-2mm}
@@
 \begin{figure}[t]
-\hspace{4mm}\small{In class: com.eclipserunner.views.impl.RunnerView}
+\hspace{4mm}{In class: com.eclipserunner.views.impl.RunnerView}
 \vspace{-2mm}
@@
 {\vspace{2mm}
-\hspace{3mm}\small{In class: com.google.android.apps.mytracks.StatsUtilities}
+\hspace{3mm}{In class: com.google.android.apps.mytracks.StatsUtilities}
 \vspace{-2mm}
@@
 used in our experiment are representative of true practice.
-In our evaluation, the studied subjects were selected with a bias towards popularity from
+In our evaluation, we only selected studied subjects from
 open-source repositories. Another threat is that we only employed three

### 2012-04-30 trunk/GUIErrorDetector/paper/introduction.tex
more edits to address reviewers' comments

@@
 \begin{figure}[t]
-\hspace{6mm}\small{In class: org.mozilla.gecko.gfx.LayerView}
+\hspace{6mm}{In class: org.mozilla.gecko.gfx.LayerView}
 \vspace{-2mm}
@@
 \end{CodeOut}
-\hspace{6mm} \small{In Android library class: android.opengl.GLSurfaceView}
+\hspace{6mm} {In Android library class: android.opengl.GLSurfaceView}
 \vspace{-2mm}
@@
 \end{CodeOut}
- \hspace{6mm}\small{In class: org.mozilla.gecko.gfx.LayerRenderer}
+ \hspace{6mm}{In class: org.mozilla.gecko.gfx.LayerRenderer}
 \vspace{-2mm}
@@
 {\vspace{2mm}
-\hspace{3mm}\small{In class: org.mozilla.gecko.gfx.LayerRenderer}
+\hspace{3mm}{In class: org.mozilla.gecko.gfx.LayerRenderer}
 \vspace{-2mm}
@@
 8 more methods in the call chain, shown as
-``\CodeIn{\small{...}}" above, are omitted for brevity.
+``\CodeIn{{...}}" above, are omitted for brevity.
 }} %\vspace{-5mm}
@@
 by our static analysis for the buggy code in Figure~\ref{fig:androiderror}.
-This report clearly indicates how a new, non-UI thread is spawned and
+This report indicates how a new, non-UI thread is spawned and
 accesses GUI objects. The generated report allows  developers to
@@
 popular GUI frameworks: SWT, Eclipse plugin, Swing, and Android (Section~\ref{sec:implementation}). Our
-tool implementation is publicly available at
-{\smaller\url{http://guierrordetector.googlecode.com}}.
+implementation is publicly available at
+{\url{http://guierrordetector.googlecode.com}}.
 

### 2012-04-30 trunk/GUIErrorDetector/paper/evaluation.tex
address reviewers' comments

@@
 \label{sec:subjects}
-
-%library code: 1.4 million
 
@@
 Java methods that a native method may call, and then added \annotationnum \CodeIn{@CalledByNativeMethods}
-annotations for it. Two subjects, MyTracks and Fennec, employ a customized pattern
-to interact with the GUI framework. For example, in MyTracks, all non-UI
-threads are initialized via using the library method \CodeIn{android.os.}\discretionary{}{}{}\CodeIn{handler.handleCallback}.
+annotations for it. 
+%Two subjects, MyTracks and Fennec, employ a customized pattern
+%to interact with the GUI framework. For example, in MyTracks, all non-UI
+%threads are initialized via using the library method \CodeIn{android.os.}\discretionary{}{}{}\CodeIn{handler.handleCallback}.
 % the \CodeIn{safeInvokeXX}
@@
 %message passing. 
-We added \filternum user-defined filters for these two subjects.
-%to indicate
-%that they are safe to be invoked from any thread. 
+We also added \filternum user-defined filters for two subjects
+(MyTracks and Fennec), since they use a customized pattern
+to interact with the GUI framework.
 In this experiment, none of the paper
@@
 for SGTPuzzler). The \newbugs errors found in VirgoFTP, FileBunker, ArecaBackup,
-S3dropbox, and SudokuSolver are previously  unknown. As a comparison, the
+S3dropbox, and SudokuSolver are previously  unknown. The rest \oldbugs errors
+in the other programs have been fixed in their succeeding releases. As a comparison, the
 results of the ``Requiring Wrappers'' approach (Section~\ref{sec:straightforward}),
@@
 the given Sudoku is unsolvable; and the other one happens
-when  JVM fails to launch the %mail composing window of the
-user's default mail client.% (after a user clicks the "eMail Me" button).
+when the program fails to launch the mail composing window of the
+user's default mail client (i.e., the \CodeIn{java.awt.Desktop.mail()}
+method throws an exception).% (after a user clicks the "eMail Me" button).
 
@@
 
-Given a sound call graph, exhaustive search is sound because it does not
+Given a sound call graph, suppose that there exists some
+error-revealing path between an entry node E and a UI-accessing node U.  A sound
+search strategy is one that reports some error-revealing path between
+E and U, while  an unsound strategy might report an infeasible
+path between the nodes.  Exhaustive search is sound because it does not
 miss any possible errors.  However, it is impractical.  Compared to
-exhaustive search, using BFS or DFS can be viewed as a heuristic filtering
+exhaustive search, BFS or DFS is unsound because they visit
+every node, but do not traverse \textit{every} path to visit that node.
+Using BFS or DFS can be viewed as a heuristic filtering
 step, akin to the filters of Section~\ref{sec:heuristic}.
+% The heuristics of Section~\ref{sec:heuristic} are
+%more effective at retaining real errors than the search variants.
+%Given a sound call graph, exhaustive search is sound because it does not
+%miss any possible errors.  However, it is impractical.  Compared to
+%exhaustive search, using BFS or DFS can be viewed as a heuristic filtering
+%step, akin to the filters of Section~\ref{sec:heuristic}.
+%The heuristics of Section~\ref{sec:heuristic} are
+%more effective at retaining real errors than the search variants.
+
 %   The algorithm of
@@
 % multi-source BFS, but
- The heuristics of Section~\ref{sec:heuristic} are
-more effective at retaining real errors than the search variants.
 
@@
 algorithm. Analyzing other subjects using different algorithms took less time.
-Call graph construction took 33--91\% of
-the total analysis time.
-%The performance has not been tuned, and we believe
-%that it could be improved further.
+Call graph construction took 33--91\% of the total time.
 
@@
 used in our experiment are representative of true practice.
-In our evaluation, we only selected studied subjects from
+In our evaluation, we only selected subjects from
 open-source repositories. Another threat is that we only employed three

### 2012-04-30 trunk/GUIErrorDetector/paper/implementation.tex
address reviewers' comments

@@
 
-%We implemented the proposed technique using the WALA framework~\cite{walatutorial}.
-%Our prototype tool takes Java bytecode as input, 
-%automatically detects potential invalid thread access
-%errors, and scales to realistic programs.
+Our tool is built on top of the WALA framework~\cite{walatutorial}.
+It takes Java bytecode as input, 
+automatically detects potential invalid thread access
+errors, and scales to realistic programs.
 
@@
 \item \textbf{UI-accessing nodes:}  the \CodeIn{Widget.checkWidget}
-and \CodeIn{Display.}\discretionary{}{}{}\CodeIn{checkDevice} methods. SWT performs
+and \CodeIn{Display.}\discretionary{}{}{}\CodeIn{check}\discretionary{}{}{}\CodeIn{Device} methods. SWT performs
 runtime checking before accessing a GUI object via these methods.
@@
 
-\subsection{Implementation Details}
+\subsection{Android-specific Implementation Details}
 
-We implemented our error detection tool using
-the WALA framework~\cite{walatutorial}.
-Our tool takes Java bytecode as input, 
-automatically detects potential invalid thread access
-errors, and scales to realistic programs.  
 We implemented the reflection-aware call graph construction

### 2012-04-30 GUIErrorDetector/paper/technique.tex
address reviewers' comments

@@
 \noindent {\textsc{\textbf{Assumption 2.}}} { We assume that each non-UI
-thread is spawned by the UI thread. Under this assumption,
+thread is (transitively) spawned by the UI thread. Under this assumption,
 we ignore all non-UI threads created by the GUI framework
@@
 \textbf{2. Filter Reports with User-Annotated Methods}. Users are
-permitted to explicitly annotate project-specific methods
+permitted to explicitly annotate specific methods
 that will never trigger an error.
@@
 A reported method call chain containing an annotated  method
-can be safely removed. In our experiments, we produced a list of \filternum
-annotated methods for two subjects (Fennec and MyTracks) because they use a customized
-pattern to interact with the GUI framework.
+can be safely removed.
+
+In our experiments, 
+we produced a list of \filternum annotated methods for two
+subjects (MyTracks and Fennec), since they employ a customized pattern
+to interact with the GUI framework. For example, in MyTracks, all non-UI
+threads are initialized via using the library method \CodeIn{android.os.}\discretionary{}{}{}\CodeIn{handler.handleCallback}.
+This method can be invoked from any thread and will never cause an
+invalid thread access error, because it checks whether the current
+thread is the UI thread or not before execution. If not,
+this method will be executed asynchronously via
+message passing.
+
+% we produced a list of \filternum
+%annotated methods for two subjects (Fennec and MyTracks) because they use a customized
+%pattern to interact with the GUI framework.
 

### 2012-05-01 GUIErrorDetector/paper/evaluation.tex
make some format adjustment
revise more

@@
 
-%library code: 1.4 million
+We used a set of open-source projects from SourceForge, Google Code
+and the Eclipse plugin marketplace as evaluation subjects.
 
-We used a set of open-source projects from SourceForge, Google Code,
-and the Eclipse plugin
-marketplace as evaluation subjects. To choose subjects for each supported GUI framework,
-we first searched for the framework keywords (e.g., ``Java Swing'' or ``Java SWT'')
-in the above three source repositories, and then selected subjects based on the following
+Five subjects (EclipseRunner, HudsonEclipse, SGTPuzzler, Fennec, and MyTracks)
+have known invalid thread access errors, all of which have been fixed later.
+We ran our tool on the reported buggy versions to check whether it
+can correctly identify the existing errors. 
+We selected the other five subjects by first searching for the
+framework keywords (e.g., ``Java Swing'' or ``Java SWT'')
+in the above source repositories, and then chosing subjects based on the following
 criteria. First, the subject must be a Java application, not
 an open library. Second, the subject must use multithreading in its implementation.
-Third, the subject must have undergone at least two years of active development,
-and it is listed in the first 3 result pages based on popularity. This permits us
-to exclude immature subjects that may contain obvious errors.
+Third, the subject is listed in the first 5 result pages.
+This permits us to exclude immature subjects that may contain obvious errors.
+We ran our tool on the latest stable release of each project to check whether
+it can find any new errors.
 
@@
 For all \subnum programs, we manually determined the validity of each output warning
-by either searching the
-bug repository to check whether the same error has been reported before,
+by either searching the bug repository to check it with the bug-fixing revision history,
 or submitting a new bug report, or writing a test driver to reproduce
@@
 As shown in Table~\ref{table:results}, our tool found
-real errors in each subject program. Using the 1-CFA
+errors in each subject. Using the 1-CFA
 call graph algorithm, our tool issued 22 warnings, among
@@
 
+%After checking against existing patches, we found
+Our tool correctly identified the \oldbugs known errors, as compared to
+their patches.
 We submitted all \newbugs new errors
-to the subject developers. As of February 2012, 1 error in S3dropbox has been confirmed,
-we have reproduced 4 errors, and 2 errors in FileBunker and ArecaBackup
+to the subject developers. As of April 2012, 1 error in S3dropbox has been confirmed,
+we have reproduced 3 errors, and 3 errors in VirgoFTP, FileBunker and ArecaBackup
 had not yet been verified by the developers.
@@
 the given Sudoku is unsolvable; and the other one happens
-when  JVM fails to launch the %mail composing window of the
-user's default mail client.% (after a user clicks the "eMail Me" button).
+when the program fails to launch the mail composing window of the
+user's default mail client (i.e., the \CodeIn{java.awt.Desktop.mail()}
+method throws an exception after a user clicks the "eMail Me" button).
 
@@
 \noindent \textbf{\textit{Summary.}} Using the 1-CFA 
-algorithm finds more errors than 0-CFA and RTA, and our call
-graph construction algorithm helps to find errors in some
+algorithm finds more errors than 0-CFA and RTA, and our reflection-aware
+call graph construction algorithm helps to find errors in some
 Android applications.
@@
 separate BFS for each entry node.  This section evaluates three variants:
-a multiple-source BFS; a separate DFS for each entry node; and exhaustive
+a multi-source BFS; a separate DFS for each entry node; and exhaustive
 search.
@@
 
-Given a sound call graph, exhaustive search is sound because it does not
-miss any possible errors.  However, it is impractical.  Compared to
-exhaustive search, using BFS or DFS can be viewed as a heuristic filtering
+Given a sound call graph, suppose that there exists some
+error-revealing path between an entry node E and a UI-accessing node U.  A sound
+search strategy is one that reports some error-revealing path between
+E and U, while  an unsound strategy might report an infeasible
+path between the nodes.  Exhaustive search is sound because it does not
+miss any possible paths.  However, it is impractical.  Compared to
+exhaustive search, BFS or DFS is unsound because they visit
+every node, but do not traverse \textit{every} path to visit that node.
+Using BFS or DFS can be viewed as a heuristic filtering
 step, akin to the filters of Section~\ref{sec:heuristic}.
+% The heuristics of Section~\ref{sec:heuristic} are
+%more effective at retaining real errors than the search variants.
+%Given a sound call graph, exhaustive search is sound because it does not
+%miss any possible errors.  However, it is impractical.  Compared to
+%exhaustive search, using BFS or DFS can be viewed as a heuristic filtering
+%step, akin to the filters of Section~\ref{sec:heuristic}.
+%The heuristics of Section~\ref{sec:heuristic} are
+%more effective at retaining real errors than the search variants.
+
 %   The algorithm of
@@
 
-\subsubsection{Evaluating Error Filters}
-\label{sec:filters}
-
-Table~\ref{table:filters} measures the effectiveness of the
-error filters of Section~\ref{sec:heuristic}.
-The five error filters removed 99.96\% of the reported warnings as likely false positives
-or redundant warnings. Specifically, two sound filters 1 and 2 
-removed 34.44\% of the warnings, and three heuristic filters 3, 4, and 5
-removed a further 65.52\% of the warnings. The most effective filter is
-\#4, for removing reports with the same head methods from the entry node to \CodeIn{Thread.start()}.
-
-\vspace{1mm}
-
-\noindent \textbf{\textit{Summary.}} Our proposed error filters are 
-effective in reducing the number of warnings.
-%Although a static analysis may
-%issue false positives or redundant reports, a set of well-designed
-%error filters can remove most of them.
-%Heuristic filter, effective.
-
 \begin{table}[t]
@@
 under column ``1-CFA'' in Table~\ref{table:results}.
-} }
+} } \vspace{-2mm}
 \end{table}
+
+\subsubsection{Evaluating Error Filters}
+\label{sec:filters}
+
+Table~\ref{table:filters} measures the effectiveness of the
+error filters of Section~\ref{sec:heuristic}.
+The five error filters removed 99.96\% of the reported warnings as likely false positives
+or redundant warnings. Specifically, two sound filters 1 and 2 
+removed 34.44\% of the warnings, and three heuristic filters 3, 4, and 5
+removed a further 65.52\% of the warnings. The most effective filter is
+\#4, for removing reports with the same head methods from the entry node to \CodeIn{Thread.start()}.
+
+\vspace{1mm}
+
+\noindent \textbf{\textit{Summary.}} Our proposed error filters are 
+effective in reducing the number of warnings.
+%Although a static analysis may
+%issue false positives or redundant reports, a set of well-designed
+%error filters can remove most of them.
+%Heuristic filter, effective.
 
@@
 were conducted on a 2.67GHz Intel Core PC with 4GB
-physical memory (1GB is allocated for JVM), running Fedora 16.
+physical memory (1GB is allocated for JVM), running Windows 7.
 For the most time-consuming subject, S3dropbox, our tool finished the whole analysis
@@
 used in our experiment are representative of true practice.
-In our evaluation, the studied subjects were selected with a bias towards popularity from
+In our evaluation, we only selected subjects from
 open-source repositories. Another threat is that we only employed three

### 2012-05-01 GUIErrorDetector/paper/implementation.tex
revise more

@@
 We instantiated the proposed technique for four widely-used
-GUI frameworks, namely SWT, Eclipse plugin development, Swing, and Android;
-and implemented an error detection tool.
-
-%We implemented the proposed technique using the WALA framework~\cite{walatutorial}.
-%Our prototype tool takes Java bytecode as input, 
-%automatically detects potential invalid thread access
-%errors, and scales to realistic programs.
+GUI frameworks, namely SWT, Eclipse plugin framework, Swing, and Android;
+and implemented an error detection tool on top of the WALA framework~\cite{walatutorial}.
 
@@
 
-\item \textbf{UI-accessing nodes: } the \CodeIn{Widget.checkWidget}
-and \CodeIn{Display.} \CodeIn{checkDevice} methods. SWT performs
+\item \textbf{UI-accessing nodes:}  the \CodeIn{Widget.checkWidget}
+and \CodeIn{Display.}\discretionary{}{}{}\CodeIn{check}\discretionary{}{}{}\CodeIn{Device} methods. SWT performs
 runtime checking before accessing a GUI object via these methods.
@@
 events. All SWT GUI event handling methods (i.e., the overriden
-methods in the class that implements \CodeIn{org.eclipse.swt.internal.SWTEvent-\\Listener}) are
+methods in the class that implements \CodeIn{org.eclipse.swt.internal.SWTEventListener}) are
 always called back from the UI thread.
@@
 
-\item \textbf{Safe UI methods: } 
-\CodeIn{SwingUtilities.}\CodeIn{invokeLater} and \CodeIn{Swing-\\Utilities.invokeAndWait}, which execute code on the UI thread.
+\item \textbf{Safe UI methods:}  
+\CodeIn{SwingUtilities.}\CodeIn{invokeLater} and \CodeIn{SwingUti-\\lities.invokeAndWait}, which execute code on the UI thread.
 
@@
 
-Instantiating our general technique to  a specific framework
-requires moderate human effort. We wrote around 500 lines of Java code in total to achieve
-the above four instantiations.
+Given a GUI application using a supported framework, our tool 
+takes its Java bytecode as input, 
+plugs in the corresponding instantiation parameters at runtime,
+and automatically detects potential invalid thread access
+errors.
 
-\subsection{Implementation Details}
+\subsection{Android-specific Implementation Details}
 
-We implemented our error detection tool using
-the WALA framework~\cite{walatutorial}.
-Our tool takes Java bytecode as input, 
-automatically detects potential invalid thread access
-errors, and scales to realistic programs.  
 We implemented the reflection-aware call graph construction
@@
 and then intercepts the call graph construction
-process on-the-fly to replace all reflection calls with object creation statements.
+process on-the-fly to replace all reflection calls with object creation expressions.
 Since Android applications are often fully encrypted and shipped in Dalvik

### 2012-05-01 GUIErrorDetector/paper/introduction.tex
revise more

@@
 Figure~\ref{fig:report}.
-}} %\vspace{-5mm}
+}} \vspace{-1.8mm}
 \end{figure}
@@
 
-We implemented an invalid-thread-error detection tool that supports
-four popular GUI frameworks: SWT, Eclipse plugin environment,
+We implemented an invalid-thread-access-error detection tool that supports
+four popular GUI frameworks: SWT, Eclipse plugin framework,
 Swing, and Android. Swing and SWT are the
@@
 instantiated it for four
-popular GUI platforms: SWT, Eclipse plugin, Swing, and Android (Section~\ref{sec:implementation}). Our
-tool implementation is publicly available at
-{\smaller\url{http://guierrordetector.googlecode.com}}.
+popular GUI frameworks: SWT, Eclipse plugin, Swing, and Android (Section~\ref{sec:implementation}). Our
+implementation is publicly available at:
+{\url{http://guierrordetector.googlecode.com}}.
 

### 2012-05-01 GUIErrorDetector/paper/related.tex
revise more

@@
 %requires a large number of test inputs that require substantial human effort.
-In contrast, a static analysis can explore all paths to find potential errors missed by testing.
+In contrast, a sound static analysis can explore all paths to find potential errors missed by testing.
 Compared to software testing, a static analysis tool such as ours may
@@
 nullness analysis, class analysis, and termination analysis.  However,
-their framework does not support detecting invalid-thread-access
+their framework does not support detecting invalid thread access
 errors, and uses a quite different abstraction than ours.
@@
 analysis tools such as Eraser~\cite{Savage:1997}  dynamically detect concurrency bugs using lockset
-algorithms or some criteria-based automata. 
-More recently, Goldilocks~\cite{Elmas:2007} uses a
-hybrid model that combines the happens-before and lock-based
-approaches to identify data races based on an execution.
-However, finding invalid-thread-access errors is quite different than detecting data races.
+algorithms.
+However, finding invalid thread access errors is quite different than detecting data races.
 A data race occurs when two concurrent threads access
@@
 an invalid thread access error occurs when a non-UI thread accesses (reads or writes) a GUI object.
-Unlike detecting data races, finding an invalid-thread-access error does not require monitoring every shared-memory
+Unlike detecting data races, finding an invalid thread access error does not require monitoring every shared-memory
 reference to verify that consistent locking behavior is observed among different threads.
@@
 to build a more precise call graph.  However,
-those algorithms do not build a complete call graph in the presence of reflection.
+those algorithms do not build a sound call graph in the presence of reflection.
 As reflected in our experiments, using standard call graph algorithms
@@
 framework-specific ones (e.g., \CodeIn{View.find-\\ViewById}).
-The standard call graph algorithms implemented in WALA, which we used
-in our experiments, actually handles standard Java
-reflection calls as~\cite{Livshits:2005} does, but still fails to build
-a sufficiently complete call graph for
-Android applications. TamiFlex~\cite{Bodden:2011}, a pure dynamic
+TamiFlex~\cite{Bodden:2011}, a pure dynamic
 approach, records all reflectively-created class instances

### 2012-05-01 trunk/GUIErrorDetector/paper/evaluation.tex
refine wordings

@@
 
-We used a set of open-source projects from SourceForge, Google Code,
-and the Eclipse plugin
-marketplace as evaluation subjects. To choose subjects for each supported GUI framework,
-we first searched for the framework keywords (e.g., ``Java Swing'' or ``Java SWT'')
-in the above three source repositories, and then selected subjects based on the following
+We used 10 open-source projects from SourceForge, Google Code
+and the Eclipse plugin marketplace as evaluation subjects.
+
+Five subjects (EclipseRunner, HudsonEclipse, SGTPuzzler, Fennec, and MyTracks)
+are selected because they have known invalid thread access errors (1 error per subject) and
+all errors have been fixed in later revisions.
+We used the buggy versions to check whether our tool
+can correctly identify those known errors. 
+For the other five subjects, we selected them
+by first searching for the
+framework keywords (e.g., ``Java Swing'' or ``Java SWT'')
+in the above source repositories, and then chosing subjects based on the following
 criteria. First, the subject must be a Java application, not
@@
 This permits us to exclude immature subjects that may contain obvious errors.
+For each selected subject, we ran our tool on the latest stable release to find new errors.
+%of each project to check whether
+%it can find any new errors.
 
@@
 
-We first inspected the source code of each subject to determine whether any
-native methods or project-specific GUI interaction patterns were implemented.
-Only SGTPuzzler uses native methods to interact with
+%We first inspected the source code of each subject to determine whether any
+%native methods or project-specific GUI interaction patterns were implemented.
+
+Subject SGTPuzzler uses native methods to interact with
 the underlying operating system. For it, we manually checked the possible
@@
 annotations for it. 
-%Two subjects, MyTracks and Fennec, employ a customized pattern
-%to interact with the GUI framework. For example, in MyTracks, all non-UI
-%threads are initialized via using the library method \CodeIn{android.os.}\discretionary{}{}{}\CodeIn{handler.handleCallback}.
-% the \CodeIn{safeInvokeXX}
-%method in the XXX subject first checks whether the current thread is the UI-thread, and
-%then determines whether to direct access a GUI object or wrap the code with
-%message passing. 
-We also added \filternum user-defined filters for two subjects
-(MyTracks and Fennec), since they use a customized pattern
-to interact with the GUI framework.
+During experiment, we found two subjects (MyTracks and Fennec)
+use a customized pattern to interact with the GUI framework.
+For them, we added \filternum user-defined filters.
 In this experiment, none of the paper
@@
 For all \subnum programs, we manually determined the validity of each output warning
-by either searching the
-bug repository to check whether the same error has been reported before,
+by either searching the bug repository to check bug-fixing revision histories,
 or submitting a new bug report, or writing a test driver to reproduce
@@
 for SGTPuzzler). The \newbugs errors found in VirgoFTP, FileBunker, ArecaBackup,
-S3dropbox, and SudokuSolver are previously  unknown. The rest \oldbugs errors
-in the other programs have been fixed in their succeeding releases. As a comparison, the
+S3dropbox, and SudokuSolver are previously  unknown. As a comparison, the
 results of the ``Requiring Wrappers'' approach (Section~\ref{sec:straightforward}),
@@
 As shown in Table~\ref{table:results}, our tool found
-real errors in each subject program. Using the 1-CFA
+errors in each subject. Using the 1-CFA
 call graph algorithm, our tool issued 22 warnings, among
-which \bugs warnings reveal \bugs distinct errors (\newbugs were previously unknown),
+which \bugs warnings reveal \bugs distinct errors (\newbugs were previously unknown,
+and the \oldbugs known errors were correctly identified),
 2 warnings are false positives, and the remaining 8 warnings
@@
 
+%After checking against existing patches, we found
+%Our tool correctly identified the \oldbugs known errors, as compared to
+%their patches.
 We submitted all \newbugs new errors
@@
 user's default mail client (i.e., the \CodeIn{java.awt.Desktop.mail()}
-method throws an exception).% (after a user clicks the "eMail Me" button).
+method throws an exception after a user clicks the "eMail Me" button).
 
@@
 path between the nodes.  Exhaustive search is sound because it does not
-miss any possible errors.  However, it is impractical.  Compared to
+miss any possible paths.  However, it is impractical.  Compared to
 exhaustive search, BFS or DFS is unsound because they visit
@@
 using multi-source BFS, DFS, or exhaustive search.
-
-\subsubsection{Evaluating Error Filters}
-\label{sec:filters}
-
-Table~\ref{table:filters} measures the effectiveness of the
-error filters of Section~\ref{sec:heuristic}.
-The five error filters removed 99.96\% of the reported warnings as likely false positives
-or redundant warnings. Specifically, two sound filters 1 and 2 
-removed 34.44\% of the warnings, and three heuristic filters 3, 4, and 5
-removed a further 65.52\% of the warnings. The most effective filter is
-\#4, for removing reports with the same head methods from the entry node to \CodeIn{Thread.start()}.
-
-\vspace{1mm}
-
-\noindent \textbf{\textit{Summary.}} Our proposed error filters are 
-effective in reducing the number of warnings.
-%Although a static analysis may
-%issue false positives or redundant reports, a set of well-designed
-%error filters can remove most of them.
-%Heuristic filter, effective.
 

### 2012-05-09 trunk/GUIErrorDetector/paper/abstract.tex
Mike's edits through section 4.1

@@
 Many GUI frameworks require all GUI objects to be accessed exclusively by the
-UI thread. If a GUI object is accessed through a non-UI thread,
+UI thread. If a GUI object is accessed from a non-UI thread,
 an \textit{invalid thread access} error occurs and the whole
@@
 Static analysis, invalid thread access error.
+
+\label{this-label-makes-etags-order-this-file-properly}
+
+%%% Local Variables: 
+%%% mode: latex
+%%% TeX-master: "guierror"
+%%% TeX-command-default: "PDF"
+%%% End:
+
+%  LocalWords:  multithreaded SWT plugin LOC

### 2012-05-09 GUIErrorDetector/paper/conclusion.tex
Mike's edits through section 4.1

@@
+\smallstep
 \section{Conclusion and Future Work}
 
-In this paper, we presented a general technique to find invalid
-thread access errors for multithreaded GUI applications. 
+This paper presented a general technique to find invalid
+thread access errors in multithreaded GUI applications. 
 Our technique statically explores paths in a call graph to check
@@
 filters to filter likely false positives and redundant warnings.
-%Since graphical user interfaces are often inadequately tested due
-%to the enormously large space of UI interactions and
-%extreme resource constraints during their development, we
-%believe that providing a static analysis can allow developers to find
-%more potential errors %before the application is released to customers (XXX),
-% to improve software reliability.
 We demonstrated the usefulness of our technique
-by an evaluation on \subnum subjects on 4 popular GUI
+by an evaluation on \subnum programs built on 4 popular GUI
 frameworks.
-%Our experiments have shown that we can find bugs
-%in real-world programs.
 
-Besides general issues such as performance or ease of use, our future
+The source code of our tool implementation is available at:
+
+\noindent \url{http://guierrordetector.googlecode.com}
+
+\vspace{1mm}
+
+Besides general issues such as performance and ease of use, our future
 work will concentrate on the following topics:
@@
 positives is to integrate with
-dynamic analyses~\cite{Jiang:2008:PPS:1453101.1453110}%, ZhangSBE2011}
-or symbolic analyses~\cite{xie05:symstra, Pasareanu:2011, halfond09issta, BMF97}
+dynamic analyses~\cite{ZhangSBE2011}
+or symbolic analyses~\cite{xie05:symstra, Pasareanu:2011}
 by using more accurate information to guide call graph exploration.
@@
 %\end{itemize}
+
+%%% Local Variables: 
+%%% mode: latex
+%%% TeX-master: "guierror"
+%%% TeX-command-default: "PDF"
+%%% End:
+
+%  LocalWords:  multithreaded multicore

### 2012-05-09 GUIErrorDetector/paper/evaluation.tex
Mike's edits through section 4.1

@@
 
-We used a set of open-source projects from SourceForge, Google Code
+We used 10 open-source projects from SourceForge, Google Code,
 and the Eclipse plugin marketplace as evaluation subjects.
@@
 Five subjects (EclipseRunner, HudsonEclipse, SGTPuzzler, Fennec, and MyTracks)
-have known invalid thread access errors, all of which have been fixed later.
-We ran our tool on the reported buggy versions to check whether it
-can correctly identify the existing errors. 
-We selected the other five subjects by first searching for the
+are selected because they have known invalid thread access errors (1 error per subject) and
+all errors have been fixed in later revisions.
+We used the buggy versions to check whether our tool
+can correctly identify those known errors. 
+For the other five subjects, we selected them
+by first searching for the
 framework keywords (e.g., ``Java Swing'' or ``Java SWT'')
-in the above source repositories, and then chosing subjects based on the following
+in the above source repositories, and then choosing subjects based on the following
 criteria. First, the subject must be a Java application, not
@@
 This permits us to exclude immature subjects that may contain obvious errors.
-We ran our tool on the latest stable release of each project to check whether
-it can find any new errors.
+For each selected subject, we ran our tool on the latest stable release to find new errors.
+%of each project to check whether
+%it can find any new errors.
 
@@
 \vspace{-15pt}
-\Caption{{\label{table:subjects} Open source programs
+\Caption{{\label{table:subjects} Open-source programs
 used in our evaluation. Column ``LOC'' is the number of non-blank, non-comment lines
@@
 For all \subnum programs, we manually determined the validity of each output warning
-by either searching the bug repository to check it with the bug-fixing revision history,
+by either searching the bug repository to check bug-fixing revision histories,
 or submitting a new bug report, or writing a test driver to reproduce
@@
 call graph algorithm, our tool issued 22 warnings, among
-which \bugs warnings reveal \bugs distinct errors (\newbugs were previously unknown),
+which \bugs warnings reveal \bugs distinct errors (\newbugs were previously unknown,
+and the \oldbugs known errors were correctly identified),
 2 warnings are false positives, and the remaining 8 warnings
@@
 %After checking against existing patches, we found
-Our tool correctly identified the \oldbugs known errors, as compared to
-their patches.
+%Our tool correctly identified the \oldbugs known errors, as compared to
+%their patches.
 We submitted all \newbugs new errors
@@
 do not provide any runtime checks for invalid thread accesses. The Swing
-GUI does not exhibit user-visible faults on some erreoneous executions.
+GUI does not exhibit user-visible faults on some erroneous executions.
 However, as clearly stated in the official documentation~\cite{swing}, %Swing is a single-GUI-threaded GUI toolkit and
@@
 user's default mail client (i.e., the \CodeIn{java.awt.Desktop.mail()}
-method throws an exception after a user clicks the "eMail Me" button).
+method throws an exception after a user clicks the ``eMail Me'' button).
 
@@
 (b) shows a less precise call graph built by RTA or 0-CFA, and (c) shows a more
-precise call graph built by 1-CFA. Nodes for constructors are omitted for brevity.
+precise call graph built by 1-CFA\@. Nodes for constructors are omitted for brevity.
 \newline
@@
 Given a sound call graph, suppose that there exists some
-error-revealing path between an entry node E and a UI-accessing node U.  A sound
+error-revealing path between an entry node E and a UI-accessing node U\@.  A sound
 search strategy is one that reports some error-revealing path between
@@
 \noindent \textbf{\textit{Performance and scalability.}} Our tool
-has been evaluated on \subnum subjects with over \totaloc LOC and frameworks
+has been evaluated on \subnum subjects with \totaloc LOC and frameworks
 with 1.4 MLOC, showing good scalability. Our evaluations
@@
 %  LocalWords:  S3dropbox SudokuSolver Sudoku mutlithreaded SGTPuzzler 9pt
-%  LocalWords:  Fennec MyTracks LOC v9306 plugin LOCC RTA CFA
-%  LocalWords:  CalledByNativeMethods
+%  LocalWords:  Fennec MyTracks LOC v9306 plugin LOCC RTA CFA 9pt eMail g1
+%  LocalWords:  CalledByNativeMethods deleteBucket deleteCurrentBucket g2
+%  LocalWords:  deleteError showErrorMessage getSelectedBucketName uiAcc
+%  LocalWords:  Czarniecki initializeResourceChangeListener getWorkspace
+%  LocalWords:  ResourcesPlugin addResourceChangeListener resourceChanged
+%  LocalWords:  IResourceChangeListener IResourceChangeEvent getViewer BFS
+%  LocalWords:  ResourceChangeEvent msgTextView setLatLong TextView DFS
+%  LocalWords:  findViewById setText getReachableStarts enqueueAll pushAll
+%  LocalWords:  HundsonEclipse subcolumn MLOC 67GHz 4GB 1GB XTA VTA pre

### 2012-05-09 GUIErrorDetector/paper/implementation.tex
Mike's edits through section 4.1

@@
 
+We implemented an error detection tool on top of the WALA framework~\cite{walatutorial}.
 We instantiated the proposed technique for four widely-used
-GUI frameworks, namely SWT, Eclipse plugin framework, Swing, and Android;
-and implemented an error detection tool on top of the WALA framework~\cite{walatutorial}.
+GUI frameworks, namely SWT, Eclipse plugin framework, Swing, and Android.
 
@@
 
+\preitemizespace
+
 \begin{itemize}
-\smallstep
 
-\item \textbf{Call graph entry nodes:}  the main method. Like a normal Java program,
-a SWT desktop application has a single main method as the entry point. By default,
-the main method is executed in the UI thread after the GUI
+\item \textbf{Call graph entry nodes:}  the main method. 
+% Like a normal Java program,
+% a SWT desktop application has a single main method as the entry point. By default,
+% the main method
+It is executed in the UI thread after the GUI
 is initialized.
@@
 \item \textbf{UI-accessing nodes:}  the \CodeIn{Widget.checkWidget}
-and \CodeIn{Display.}\discretionary{}{}{}\CodeIn{check}\discretionary{}{}{}\CodeIn{Device} methods. SWT performs
-runtime checking before accessing a GUI object via these methods.
-If the current thread is a non-UI thread, the \CodeIn{Widget.checkWidget}
-and \CodeIn{Display.checkDevice} methods throw a \CodeIn{RuntimeException}.
+and \CodeIn{Display\-.check\-Device} methods.
+% SWT performs
+% runtime checking before accessing a GUI object via these methods.
+% If the current thread is a non-UI thread, the \CodeIn{Widget.checkWidget}
+% and \CodeIn{Display.checkDevice} methods throw a \CodeIn{RuntimeException}.
+If the current thread is a non-UI thread, these
+methods throw a \CodeIn{RuntimeException}.
 
@@
 \item \textbf{Safe UI methods:}  \CodeIn{Display.asyncExec}
-and \CodeIn{Display.syncExec}. SWT provides these two methods
-to execute code (a)synchro- nizedly on the UI thread.
+and \CodeIn{Display.syncExec}.
+These methods
+execute code (a)synchro\-nously on the UI thread.
 
@@
 
-\smallstep
-\begin{myindentpar}{-2mm}
+\preitemizespace
 
@@
 calls back the overridden methods to handle the
-events. All SWT GUI event handling methods (i.e., the overriden
-methods in the class that implements \CodeIn{org.eclipse.swt.internal.SWTEventListener}) are
+events. All SWT GUI event handling methods (i.e., the overridden
+methods in a class that implements \CodeIn{org.eclipse.swt.internal.SWTEventListener}) are
 always called back from the UI thread.
@@
 
-\item \textbf{UI-accessing nodes} and \textbf{Safe UI methods} are the same as SWT.
+\item \textbf{UI-accessing nodes} and \textbf{Safe UI methods} are the same as SWT\@.
 
 \end{itemize}
-\end{myindentpar}
 
@@
 
-\begin{myindentpar}{-2mm}
+\preitemizespace
+
 \begin{itemize}
-\tinystep
 
@@
 all methods defined in each Swing GUI class except for three thread-safe
-methods: \CodeIn{repaint()}, \CodeIn{revali-\\date()}, and \CodeIn{invalidate()}.
+methods: \CodeIn{repaint()}, \CodeIn{reval\-i\-date()}, and \CodeIn{invalidate()}.
 
@@
 \item \textbf{Safe UI methods:}  
-\CodeIn{SwingUtilities.}\CodeIn{invokeLater} and \CodeIn{SwingUti-\\lities.invokeAndWait}, which execute code on the UI thread.
+\CodeIn{SwingUtilities.}\CodeIn{invokeLater} and \CodeIn{Swing\-Util\-ities.invokeAndWait}, which execute code on the UI thread.
 
 \end{itemize}
-\end{myindentpar}
 
@@
 \item \textbf{UI-accessing nodes:} the \CodeIn{ViewRoot.checkThread} method.
-Like SWT, Android explicitly performs runtime checking before accessing
-a GUI object via the \CodeIn{ViewRoot.checkThread} method. If the current
+% Like SWT, Android explicitly performs runtime checking before accessing
+% a GUI object via the \CodeIn{ViewRoot.checkThread} method.
+If the current
 thread is a non-UI thread, the \CodeIn{ViewRoot.checkThread} method throws
@@
 \end{itemize}
-\end{myindentpar}
 
@@
 ded translator~\cite{ded} to convert
-Dalvik bytecode to Java bytecode before feeding to WALA.  The Android system
+Dalvik bytecode to Java bytecode before feeding to WALA\@.  The Android system
 library (i.e., \CodeIn{android.jar}) uses many ``stub'' classes as
@@
 class files rather than stubs.
+
+%%% Local Variables: 
+%%% mode: latex
+%%% TeX-master: "guierror"
+%%% TeX-command-default: "PDF"
+%%% End:
+
+%  LocalWords:  WALA SWT plugin checkWidget RuntimeException asyncExec apk
+%  LocalWords:  syncExec synchro nously reval SwingUtilities invokeLater
+%  LocalWords:  Util ities invokeAndWait ViewRoot checkThread postDelay
+%  LocalWords:  WALA's Dalvik apktool ded

### 2012-05-09 GUIErrorDetector/paper/introduction.tex
Mike's edits through section 4.1

@@
 End-user satisfaction depends in part on the responsiveness and
-robustness of a software application's GUI.
+robustness of a software application's GUI\@.
 
@@
 
-%\subsection{The Single-thread Rule for GUI Object Access}
+%\subsection{The Single-GUI-Thread Rule for GUI Object Access}
 %ugly hack
@@
 
-\subsection{The Single-thread Rule}
+\subsection{The Single-GUI-Thread Rule}
 
@@
 If not, an \textit{invalid thread access error} will occur. This may
-terminate the application, but it is considered preferable
+terminate the application --- doing so is considered preferable
 to nondeterministic concurrency errors.
@@
 the source of many concurrency bugs~\cite{top3bugs}.
-A Google search for ``SWTException:Invalid thread access''  returns over 11,800 entries,
+A Google search for ``SWTException:Invalid thread access''  returns over 11,800 hits,
 consisting of numerous bug reports, forum posts, and mailing list threads on
@@
 
-%Also, you've got no confidence that your app will continue to work on future CPUs with more and more cores - which are more prone to encountering weird threading issues due to them being truely concurrent rather than just simulated by the OS.
+%Also, you've got no confidence that your app will continue to work on future CPUs with more and more cores - which are more prone to encountering weird threading issues due to them being truely concurrent rather than just simulated by the OS\@.
 
@@
 It is infeasible for testing to cover the enormous space of possible interactions
-with a GUI. Each sequence of GUI events can result in
+with a GUI\@. Each sequence of GUI events can result in
 a different state, and each GUI event may need to be evaluated in all of
@@
 \CodeIn{post} method in class \CodeIn{android.widget.View} is
-a standard way to send asynchronous messages to the UI-thread.}, as follows:
+a standard way to send asynchronous messages to the UI thread.}, as follows:
 
@@
 
-Such an approach is desirable for accesses from non-UI threads, but it is unnecessary.
+Such an approach is desirable for accesses from non-UI threads, but it is
+not necessary for all accesses.
 In our evaluation on real-world programs, we found that a simple analysis that
@@
 an unacceptable number of warnings. %false positives and redundant warnings.
-Furthermore, this approach is dangerous for accesses from the UI thread. Asynchronized message passing offers
+Furthermore, this approach is dangerous for accesses from the UI thread. Asynchronous message passing offers
 no timing guarantee, so a GUI object may have already been
@@
 Static analysis may report false positives due to its
-conservative nature, or multiple warnings that actually correspond
-to the same error. To address such limitations, we devise a set
+conservative nature, or may report multiple warnings that actually correspond
+to the same error. To address such limitations, we devised a set
  of error filters to remove likely false positives and redundant warnings.
@@
 two dominant GUI frameworks for desktop Java applications.
-Eclipse is a widely-used IDE for Java. Android is the \#1 platform for
+Eclipse is the most widely-used IDE for Java. Android is the \#1 platform for
 mobile applications with market share 56\% as of September 2011.
@@
 
-Our tool works in an automatic manner,
+Our tool works in an automatic manner
 and scales to realistic programs.
-We evaluated our implementation on \subnum programs comprising \totaloc LOC.
+We evaluated our implementation on \subnum programs comprising \totaloc LOC\@.
 The experimental results demonstrate
@@
 finding errors in Android applications;
-and our proposed error filters significantly reduce the number of warnings.
+and our proposed error filters significantly reduce the number of warnings
+and thus the programmer effort.
 %false positives and redundant warnings.
@@
 \item \textbf{Technique.} We formulate finding
-the invalid thread access error as a call graph reachability problem,
+invalid thread access errors as an elegant call graph reachability problem,
 and present a general error detection technique.
@@
 \item \textbf{Evaluation.} We applied our tool to \subnum programs 
-from 4 different frameworks, comprising \totaloc LOC. The results
+from 4 different frameworks, comprising \totaloc LOC\@. The results
 show the usefulness of the proposed technique (Section~\ref{sec:evaluation}).
@@
 %%% End:
+
+%  LocalWords:  multithreaded SWT plugin MacOS myquotation 0pt 10pt GL10
+%  LocalWords:  SWTException LayerView LayerController mRenderer mGLThread
+%  LocalWords:  LayerRenderer setRenderer GLThread onSurfaceChanged gl RTA
+%  LocalWords:  glViewport mView setViewportSize IntSize Fennec GUIs init
+%  LocalWords:  GLSurfaceView guardedRun checkThread CFA

### 2012-05-09 GUIErrorDetector/paper/related.tex
Mike's edits through section 4.1

@@
 reflection calls (e.g., \CodeIn{Class.forName}) instead of
-framework-specific ones (e.g., \CodeIn{View.find-\\ViewById}).
+framework-specific ones (e.g., \CodeIn{View.find\-ViewById}).
 TamiFlex~\cite{Bodden:2011}, a pure dynamic
@@
 %approach to call graph construction.
+
+%%% Local Variables: 
+%%% mode: latex
+%%% TeX-master: "guierror"
+%%% TeX-command-default: "PDF"
+%%% End:
+
+%  LocalWords:  multithreaded Memon Xie Payet Spoto lockset Palsberg RTA
+%  LocalWords:  Sundaresan Livshits forName ViewById TamiFlex Spoto's
+%  LocalWords:  findViewById

### 2012-05-09 GUIErrorDetector/paper/technique.tex
revise more
Mike's edits through section 4.1

@@
 GUI initialization. After the GUI becomes visible, the UI thread
-takes charge of the application to handle events from the GUI.
+takes charge of the application to handle events from the GUI\@.
 It spawns new threads to process lengthy operations in the background. }
@@
 \noindent {\textsc{\textbf{Assumption 1.}}} {We assume that each multithreaded
-GUI application has a single global UI thread. This is true for applications
+GUI application has a single UI thread. This is true for applications
 built on top of GUI frameworks adopting the single-GUI-thread rule. The
@@
 we ignore all non-UI threads created by the GUI framework
-before the UI thread has been initialized. That is, all post-initialization
+before the UI thread has been initialized. That is, we assume all post-initialization
 GUI work occurs in the UI thread. Once the GUI is visible, the
@@
 adopt the single-GUI-thread rule must provide methods to permit non-UI threads
-to run code in the UI thread. We call such methods \textit{safe UI methods}, since
+to run code in the UI thread, typically by sending a message to the UI thread.
+We call such methods \textit{safe UI methods}, since
 they can be invoked safely by any thread.}\vspace{1mm}
 
-\noindent  {\textsc{\textbf{Definition 5 (Invalid Thread Access).}}} {An invalid-thread-access error occurs when the UI thread may spawn a non-UI thread, and there
+\noindent  {\textsc{\textbf{Definition 5 (Invalid Thread Access).}}} {An invalid-thread-access error results when the UI thread may spawn a non-UI thread, and there
 exists a path from the non-UI thread's \CodeIn{start} method to any UI-accessing method
@@
 edge ($f$, $g$) indicates that method $f$ may call method $g$.
-A theoretically ideal call graph can be defined as the union of the
+A theoretically ideal call graph is the union of the
 dynamic call graphs over all possible executions of the program. 
@@
 dynamic call graph of every possible execution. 
-Based on call graph, our algorithm's reports are in terms of methods, as shown in Figure~\ref{fig:report}.
+Because it is 
+based on the call graph, our algorithm's reports are in terms of methods, as shown in Figure~\ref{fig:report}.
 
@@
 then specifies entry nodes, UI-accessing nodes, and safe UI nodes
-for it on lines 3, 4, and 5, respectively. Lines 3--5 are GUI framework-specific.
+for it on lines 3, 4, and 5, respectively. Lines 3--5 are GUI-framework-specific.
 As an example, for a SWT desktop application, the entry nodes include
@@
 we empirically compared three different graph search strategies, and demonstrated that
-using BFS, the algorithm found more errors than DFS and
+using BFS, the algorithm found more errors than DFS and was more practical than
 exhaustive path search.
@@
 \IF{isReflectionCall($expression$)}
-\STATE $\mathit{objectSet}$ $\leftarrow$ getAllObjectsThatMaybeCreated($\mathit{expression}$)
+\STATE $\mathit{objectSet}$ $\leftarrow$ getAllObjectsThatMayBeCreated($\mathit{expression}$)
 \STATE $\mathit{newExpr}$ $\leftarrow$ createObjectCreationExpression($\mathit{objectSet}$)
@@
 if the $expression$ is a \CodeIn{findViewById(id)} method call, and the method
-getAllObjectsThatMaybeCreated on line 3 parses the associated XML configuration
+getAllObjectsThatMayBeCreated on line 3 parses the associated XML configuration
 file to extract the class declaration
@@
 
-A static analysis can check possible error paths without executing the code; but may report
+A static analysis can check possible error paths without executing the
+code, but it may report
 paths that do not actually exist (false positives) or multiple paths
- that have the same error cause (redundant warnings). We devise
-5 error filters below to remove likely false positives and redundant warnings.
+that have the same error cause (redundant warnings). We devised
+5 error filters to remove likely false positives and redundant warnings.
 The first 2 filters are sound in that they will not filter real bugs, and
@@
 chain can lexically subsume another one. For example, suppose that two
-reported method call chains; \CodeIn{a()} $\rightarrow$ \CodeIn{b()}
+reported method call chains, \CodeIn{a()} $\rightarrow$ \CodeIn{b()}
 $\rightarrow$ \CodeIn{c()} and 
@@
 are two distinct entry methods. The second call chain can
-be removed without reducing the error detection capability, since
+be removed without missing any errors, since
 the first chain reveals the same error and is shorter 
@@
 %Thus,
-A reported method call chain containing an annotated  method
+Assuming the user annotations are accurate,
+a reported method call chain containing an annotated method
 can be safely removed.
@@
 to interact with the GUI framework. For example, in MyTracks, all non-UI
-threads are initialized via using the library method \CodeIn{android.os.}\discretionary{}{}{}\CodeIn{handler.handleCallback}.
+threads are initialized via using the library method \CodeIn{android.os\-.handler.handleCallback}.
 This method can be invoked from any thread and will never cause an
@@
 thread is the UI thread or not before execution. If not,
-this method will be executed asynchronously via
-message passing.
+this method will use safe UI methods to run the code in the UI thread.
 
@@
 be buggy. For example, the \CodeIn{Runtime.}\CodeIn{shutDown}
-method is called when JVM terminates, and uses multithreading
+method is called when the JVM terminates, and uses multithreading
 to dispose all GUI objects when the program exits.
-We encoded a list of 25 common library calls by proposing
-a basic set of library calls that seemed %natural and
-generally applicable, based on our programming experience.
-We later added other calls we found helpful in analyzing
-programs on different GUI frameworks and that we believed would be generally useful.
+% We encoded a list of 25 common library calls by proposing
+% a basic set of library calls that seemed %natural and
+% generally applicable, based on our programming experience.
+% We later added other calls we found helpful in analyzing
+% programs on different GUI frameworks and that we believed would be generally useful.
+Our experiments use a list of 25 such library calls.
 %We did this only between experiments rather than biasing experiments by tuning
@@
 
-\textbf{4. Filter Report with the Same Head Methods from the Entry Node to \CodeIn{Thread.start()}}. A method can call
+\textbf{4. Filter Reports with the Same Head Methods from the Entry Node to \CodeIn{Thread.start()}}. A method can call
 multiple methods that access GUI objects, such as:
@@
 \vspace{-2mm}
-If method \CodeIn{m()} is invoked by a non-UI thread, method call chains that
-only differ in the last few method nodes may be reported separately, such as:
+If method \CodeIn{m()} is invoked by a non-UI thread, our algorithm will
+report method call chains that
+only differ in the last few method nodes, such as:
 
@@
 
-In fact, these two chains may have the same error root cause: knowing that
+\noindent
+These two chains may have the same error root cause: knowing that
 method \CodeIn{m()} is called by a non-UI thread is sufficient to understand
@@
 %\item
-\textbf{5. Filter Report with the Same Tail Methods from \CodeIn{Thread}.
+\textbf{5. Filter Reports with the Same Tail Methods from \CodeIn{Thread}.
 \CodeIn{start()}
@@
 
-As we will show in our experiments (Section~\ref{sec:filters}), these filters
-work remarkably well by reducing over 99\% of the reported warnings. In addition,
-we also found that using sound filters alone was insufficient. The overwhelming
-number of warnings after sound filters were applied motivated the use
+In our experiments (Section~\ref{sec:filters}), these filters remove
+99.96\% of the reported warnings.
+We also found that using sound filters alone was insufficient, because an overwhelming
+number of warnings remained.  This motivated our use
 of heuristic filters.
@@
 %%% End:
+
+%  LocalWords:  multithreaded pre SWT checkWidget checkDevice asyncExec
+%  LocalWords:  syncExec BFS createErrorReport LayerView init ViewRoot
+%  LocalWords:  checkThread constructCallGraph getEntryNodes newError
+%  LocalWords:  getUIAccessingNodes getSafeUINodes getReachableStarts
+%  LocalWords:  uiAccessingNodes safeUINodes worklist objectSet newExpr

### 2012-05-09 GUIErrorDetector/paper/conclusion.tex
Mike's edits to section 4.2 and onward

@@
 
-This paper presented a general technique to find invalid
+This paper presented a simple, general, effective technique to find invalid
 thread access errors in multithreaded GUI applications. 
@@
 We demonstrated the usefulness of our technique
-by an evaluation on \subnum programs built on 4 popular GUI
+by evaluating it on \subnum programs built on 4 popular GUI
 frameworks.
 
-The source code of our tool implementation is available at:
-
-\noindent \url{http://guierrordetector.googlecode.com}
+The source code of our tool implementation is available at: \\
+\url{http://guierrordetector.googlecode.com}
 
@@
 \textbf{Integration with dynamic and symbolic analyses.} The technique 
-presented in this paper is a call graph-based, pure static analysis. 
+presented in this paper is a call-graph-based, pure static analysis. 
 It suffers from false positives for many GUI applications,

### 2012-05-09 GUIErrorDetector/paper/evaluation.tex
Mike's edits to section 4.2 and onward

@@
 annotations for it. 
-During experiment, we found two subjects (MyTracks and Fennec)
+Two subjects (MyTracks and Fennec)
 use a customized pattern to interact with the GUI framework.
-For them, we added \filternum user-defined filters.
+For them, we added \filternum user-defined filters, described in Section~\ref{sec:heuristic}.
 In this experiment, none of the paper
@@
 
-For all \subnum programs, we manually determined the validity of each output warning
+We manually determined the validity of each warning
 by either searching the bug repository to check bug-fixing revision histories,
-or submitting a new bug report, or writing a test driver to reproduce
-the error.
+writing a test driver to reproduce
+the error,
+or submitting a new bug report.
 
@@
 \Caption{{\label{table:results}Experimental results in finding invalid-thread-access errors
-in multithreaded GUI programs. Column ``CG Size'' shows the
-call graph size in terms of node number. Column ``\#Warning''
-shows the number of warnings issued by our tool. Column ``\#Bug'' shows
-the actual bugs found. Columns ``RTA '', ``0-CFA'',
+in multithreaded GUI programs. Column ``CG Size'' is the number of nodes in the
+call graph. Column ``\#Warning''
+is the number of warnings issued by our tool. Column ``\#Bug'' shows
+the actual bugs found. Column groups ``RTA'', ``0-CFA'',
 and ``1-CFA'' show the results of using different
-call graph construction algorithms. In each cell of the table
-for Android applications, a slash ``/'' separates the result of
+call graph construction algorithms.
+For the Android applications, a slash ``/'' separates the result of
 using standard call graph construction algorithm and our call
@@
 We submitted all \newbugs new errors
-to the subject developers. As of April 2012, 1 error in S3dropbox has been confirmed,
-we have reproduced 3 errors, and 3 errors in VirgoFTP, FileBunker and ArecaBackup
-had not yet been verified by the developers.
+to the respective developers. As of April 2012, 
+we have reproduced 3 errors, the S3dropbox developers have confirmed
+1 error, and 3 errors in VirgoFTP, FileBunker, and ArecaBackup
+have not yet been verified by the developers.
 
@@
 access a Swing GUI object \CodeIn{display} on line 79 from
-a non-UI thread. This error is previously unknown, and has been confirmed by the S3dropbox developers.
+a non-UI thread. This error was previously unknown, and has been confirmed by the S3dropbox developers.
 }} %\vspace{-5mm}
@@
 One error only happens when
-the given Sudoku is unsolvable; and the other one happens
-when the program fails to launch the mail composing window of the
+the given Sudoku is unsolvable.  The other one happens
+when the program fails to launch the mail-composing window of the
 user's default mail client (i.e., the \CodeIn{java.awt.Desktop.mail()}
@@
 the single-GUI-thread rule. However, due to the huge space of
-possible UI interactions, potential
-invalid thread access errors still exist in many corner cases and
-can be hard to find. 
+possible UI interactions, hard-to-find
+invalid thread access errors still exist.
 %Thus, a static analysis as presented in this paper
@@
 invalid thread access errors is to wrap every GUI-accessing operation
-with message passing (i.e., via the safe UI methods). Although
-this approach can give rise to other types of errors, a
-straightforward way to detect potential invalid thread access errors
+with message passing (i.e., via the safe UI methods).  A wrapper is not
+always necessary, and indiscriminate wrapping
+can give rise to other types of errors.  Nonetheless, a
+straightforward and sound way to detect potential invalid thread access errors
 is to issue a warning whenever a GUI-accessing operation
@@
 
-As shown in the far right column of ``Requiring Wrappers'' in
-Table~\ref{table:results}, Requiring Wrappers could identify every
-error that our technique found, but it issued a huge number of warnings,
-most of which are probably false positives.
+This approach identifies every
+error that our technique found.
+However, requiring wrappers 
+issues a huge number of warnings,
+most of which are probably false positives (see the far right column of
+Table~\ref{table:results}).
 The primary reason is that this simple approach
@@
 is because RTA and 0-CFA do not consider the calling context when
-constructing a call graph, and 
+constructing a call graph:  they
 mix calls to the same method from different callers into a single node, thus
@@
   \vspace*{-5.0ex}\caption {{\label{fig:ex} (a) shows example code, in which
-\CodeIn{safe()} is a Safe UI method, and \CodeIn{uiAcc()} is a UI-accessing method.
+\CodeIn{safe()} is a Safe UI method and \CodeIn{uiAcc()} is a UI-accessing method.
 (b) shows a less precise call graph built by RTA or 0-CFA, and (c) shows a more
@@
 
-Another error in SGTPuzzler is only reported when adding \annotationnum native method
+Another error in SGTPuzzler is only reported when adding native method
 annotations (Section~\ref{sec:annotation}).
@@
 search strategy is one that reports some error-revealing path between
-E and U, while  an unsound strategy might report an infeasible
-path between the nodes.  Exhaustive search is sound because it does not
-miss any possible paths.  However, it is impractical.  Compared to
-exhaustive search, BFS or DFS is unsound because they visit
-every node, but do not traverse \textit{every} path to visit that node.
+E and U, while an unsound strategy might report a non-error-revealing
+path between the nodes (Figure~\ref{fig:ex} shows an example).
+Exhaustive search is sound because it does not
+miss any possible (non-cyclic) paths.  However, it is impractical.
+BFS and DFS are unsound because they visit
+every node, but do not traverse every \emph{path} path to visit that node.
 Using BFS or DFS can be viewed as a heuristic filtering
@@
 The five error filters removed 99.96\% of the reported warnings as likely false positives
-or redundant warnings. Specifically, two sound filters 1 and 2 
-removed 34.44\% of the warnings, and three heuristic filters 3, 4, and 5
+or redundant warnings. Specifically, the two sound filters 1 and 2 
+removed 34.44\% of the warnings, and the three heuristic filters 3, 4, and 5
 removed a further 65.52\% of the warnings. The most effective filter is
@@
 were conducted on a 2.67GHz Intel Core PC with 4GB
-physical memory (1GB is allocated for JVM), running Windows 7.
+physical memory (1GB is allocated for the JVM), running Windows 7.
 For the most time-consuming subject, S3dropbox, our tool finished the whole analysis
 within 252 seconds using the most expensive 1-CFA call graph construction
-algorithm. Analyzing other subjects using different algorithms took less time.
+algorithm. Analyzing other subjects or using different algorithms took less time.
 Call graph construction took 33--91\% of the total time.
@@
 is neither sound nor complete. It may miss true positives due
-to the graph search strategy, or
+to the graph search strategy, and it never reports cyclic paths.  It may
 issue false positives due to the conservative nature of

### 2012-05-09 trunk/GUIErrorDetector/paper/related.tex
Mike's edits to section 4.2 and onward

@@
 analyzing and testing GUI applications; (2)
-bug finding techniques for multithreaded programs; and (3)
+bug-finding techniques for multithreaded programs; and (3)
 call graph construction algorithms.
@@
 Michail and Xie~\cite{michail05:helping} proposed a tool-based approach to help users avoid bugs
-in GUI applications. Their approach monitors a user's action in the background,
+in GUI applications. Their approach monitors a user's actions in the background,
 and gives a warning as well as the opportunity to abort the action, when
@@
 analysis tools such as Eraser~\cite{Savage:1997}  dynamically detect concurrency bugs using lockset
-algorithms or some criteria-based automata. 
-%More recently, Goldilocks~\cite{Elmas:2007} uses a
-%hybrid model that combines the happens-before and lock-based
-%approaches to identify data races based on an execution.
-However, finding invalid-thread-access errors is quite different than detecting data races.
+algorithms.
+However, finding invalid thread access errors is quite different than detecting data races.
 A data race occurs when two concurrent threads access
@@
 reflection calls (e.g., \CodeIn{Class.forName}) instead of
-framework-specific ones (e.g., \CodeIn{View.find-\\ViewById}).
-The standard call graph algorithms implemented in WALA, which we used
-in our experiments, actually handles standard Java
-reflection calls as~\cite{Livshits:2005} does, but still fails to build
-a sufficiently complete call graph for
-Android applications. TamiFlex~\cite{Bodden:2011}, a pure dynamic
+framework-specific ones (e.g., \CodeIn{View.find\-ViewById}).
+TamiFlex~\cite{Bodden:2011}, a pure dynamic
 approach, records all reflectively-created class instances

### 2012-05-09 GUIErrorDetector/paper/conclusion.tex
More future work in conclusion

@@
 
+%\item
+\textbf{Generalization.}
+We have applied our graph reachability analysis to one specific, but
+important, problem.  There is a rich history of testing and analysis
+problems being cast as reachability (e.g.,~\cite{RepsHS95}).  In future
+work, we plan to formulate other problems, such as detecting security
+vulnerabilities, as path reachability, and to apply our scalable analysis
+to them.
+
 %\end{itemize}

### 2012-05-09 trunk/GUIErrorDetector/tests/edu/washington/cs/detector/experiments/android/TestFirefoxAndroid.java
remove a useless file

@@ -1,17 +1,0 @@
-package edu.washington.cs.detector.experiments.android;
-
-public class TestFirefoxAndroid extends AbstractAndroidTest {
-
-	@Override
-	protected String getAppPath() {
-		// TODO Auto-generated method stub
-		return null;
-	}
-
-	@Override
-	protected String getDirPath() {
-		// TODO Auto-generated method stub
-		return null;
-	}
-
-}

### 2012-05-09 GUIErrorDetector/tests/edu/washington/cs/detector/experiments/search/ExhaustiveSearcher.java
add comments for the exhaustive searcher class

@@ -13,27 +13,52 @@ import edu.washington.cs.detector.NativeMethodConnector;
 import edu.washington.cs.detector.guider.CGTraverseDefaultGuider;
 import edu.washington.cs.detector.guider.CGTraverseGuider;
 
+/**
+ * The basic algorithm to perform exhaustive search of all
+ * non-cyclic paths on a graph.
+ * */
 abstract public class ExhaustiveSearcher {
 	
+	/**
+	 * If set, stop searching when a certain amount of time reaches
+	 * also see class SimpleClock for reference
+	 * */
 	public static boolean USE_CLOCK = false;
 	
+	/**
+	 * The graph on which the search is performed
+	 * */
 	public final Graph<CGNode> graph;
 	
+	/**
+	 * The starting node for a search
+	 * */
 	public final CGNode startNode;
 	
+	/**
+	 * Customize graph search strategies if needed, e.g., which succ
+	 * nodes to search first. By default, it does nothing.
+	 * */
 	CGTraverseGuider guider = new CGTraverseDefaultGuider();
 	
+	/**
+	 * This connector represents the calling relationship between a native method
+	 * and a Java method. It is initialized by reading the CalledByNativeMethods
+	 * annotations for programs using native methods.
+	 * By default, it does nothing.
+	 * */
 	protected NativeMethodConnector connector = NativeMethodConnector.createEmptyConnector();
 	
+	/**
+	 * Constructors, and several simple setters
+	 * */
 	public ExhaustiveSearcher(Graph<CGNode> graph, CGNode startNode) {
 		this.graph = graph;
 		this.startNode = startNode;
 	}
-	
 	public void setTraverseGuider(CGTraverseGuider guider) {
 		this.guider = guider;
 	}
-	
 	public void setNativeMethodConnector(NativeMethodConnector connector) {
 		if(connector == null) {
 			throw new RuntimeException("The native connector can not be null.");
@@ -41,52 +66,80 @@ abstract public class ExhaustiveSearcher {
 		this.connector = connector;
 	}
 	
+	/**
+	 * A method checking whether the current node is a target node or not.
+	 * It must be overriden by subclasses. For example, when searching all
+	 * paths from starting node to all thread-spawning node. This method
+	 * returns true if node is "Thread.start()".
+	 * */
+	abstract protected boolean isDestNode(CGNode node);
+	
+	/**
+	 * Performs breadth-first exhaustive search. It returns a collection of
+	 * paths (called chains below). Here a path is a list of CGNode.
+	 * 
[…]

### 2012-05-09 trunk/GUIErrorDetector/paper/conclusion.tex
improve the related work and conclusion.

@@
 
+%\item
+\textbf{Generalization.}
+We have applied our graph reachability analysis to one specific, but
+important problem.  There is a rich history of testing and analysis
+problems being cast as reachability (e.g.,~\cite{RepsHS95}).  In future
+work, we plan to formulate other problems, such as detecting security
+vulnerabilities, as path reachability, and to apply our scalable analysis
+to them.
+
 %\end{itemize}
+
+%%% Local Variables: 
+%%% mode: latex
+%%% TeX-master: "guierror"
+%%% TeX-command-default: "PDF"
+%%% End:
+
+%  LocalWords:  multithreaded multicore

### 2012-05-09 GUIErrorDetector/paper/introduction.tex
small tweak of introduction

@@
 Searching for ``SWTException:Invalid thread access'' in Eclipse's bug repository
-and discussion forum returns over 2732 bug reports and 351 distinct discussion threads, respectively. 
+and discussion forum returns 2732 bug reports and 351 distinct discussion threads, respectively. 
 We manually studied all 156 distinct \textit{confirmed} bug reports, and 

### 2012-05-10 trunk/GUIErrorDetector/paper/evaluation.tex
tweak

@@
 
-We used 10 open-source projects from SourceForge, Google Code
+We used 10 open-source projects from SourceForge, Google Code,
 and the Eclipse plugin marketplace as evaluation subjects.
@@
 framework keywords (e.g., ``Java Swing'' or ``Java SWT'')
-in the above source repositories, and then chosing subjects based on the following
+in the above source repositories, and then choosing subjects based on the following
 criteria. First, the subject must be a Java application, not
@@
  \hline
- Fennec (10.0.a.rc3)&  8577 &  51 &  620 \\
+ Fennec (d7fa4814218d)&  8577 &  51 &  620 \\
  \hline
@@
 One error only happens when
-the given Sudoku is unsolvable; and the other one happens
-when the program fails to launch the mail composing window of the
+the given Sudoku is unsolvable.  The other one happens
+when the program fails to launch the mail-composing window of the
 user's default mail client (i.e., the \CodeIn{java.awt.Desktop.mail()}
-method throws an exception after a user clicks the "eMail Me" button).
+method throws an exception after a user clicks the ``eMail Me'' button).
 
@@
   \vspace*{-5.0ex}\caption {{\label{fig:ex} (a) shows example code, in which
-\CodeIn{safe()} is a Safe UI method, and \CodeIn{uiAcc()} is a UI-accessing method.
+\CodeIn{safe()} is a Safe UI method and \CodeIn{uiAcc()} is a UI-accessing method.
 (b) shows a less precise call graph built by RTA or 0-CFA, and (c) shows a more
-precise call graph built by 1-CFA. Nodes for constructors are omitted for brevity.
+precise call graph built by 1-CFA\@. Nodes for constructors are omitted for brevity.
 \newline
@@
 Given a sound call graph, suppose that there exists some
-error-revealing path between an entry node E and a UI-accessing node U.  A sound
+error-revealing path between an entry node E and a UI-accessing node U\@.  A sound
 search strategy is one that reports some error-revealing path between
-E and U, while  an unsound strategy might report an infeasible
-path between the nodes.  Exhaustive search is sound because it does not
-miss any possible paths.  However, it is impractical.  Compared to
-exhaustive search, BFS or DFS is unsound because they visit
-every node, but do not traverse \textit{every} path to visit that node.
+E and U, while an unsound strategy might report a non-error-revealing
+path between the nodes (Figure~\ref{fig:ex} shows an example).
+Exhaustive search is sound because it does not
+miss any possible (non-cyclic) paths.  However, it is impractical.
+BFS and DFS are unsound because they visit
+every node, but do not traverse every \emph{path} path to visit that node.
 Using BFS or DFS can be viewed as a heuristic filtering
@@
 \noindent \textbf{\textit{Performance and scalability.}} Our tool
-has been evaluated on \subnum subjects with over \totaloc LOC and frameworks
+has been evaluated on \subnum subjects with \totaloc LOC and frameworks
 with 1.4 MLOC, showing good scalability. Our evaluations
 were conducted on a 2.67GHz Intel Core PC with 4GB
-physical memory (1GB is allocated for JVM), running Windows 7.
+physical memory (1GB is allocated for the JVM), running Windows 7.
 For the most time-consuming subject, S3dropbox, our tool finished the whole analysis
 within 252 seconds using the most expensive 1-CFA call graph construction
-algorithm. Analyzing other subjects using different algorithms took less time.
+algorithm. Analyzing other subjects or using different algorithms took less time.
 Call graph construction took 33--91\% of the total time.

### 2012-05-10 trunk/GUIErrorDetector/paper/introduction.tex
tweak

@@
 Searching for ``SWTException:Invalid thread access'' in Eclipse's bug repository
-and discussion forum returns over 2732 bug reports and 351 distinct discussion threads, respectively. 
+and discussion forum returns over 2700 bug reports and 350 distinct discussion threads, respectively. 
 We manually studied all 156 distinct \textit{confirmed} bug reports, and 
@@
 Bug 703256 reported on 11/17/2011 in Fennec (Mozilla Firefox for Android)
-release 10.0.a.rc3. On line 74, \CodeIn{LayerView}'s constructor
+revision d7fa4814218d. On line 74, \CodeIn{LayerView}'s constructor
 calls method \CodeIn{setRenderer} which 
@@
 
-We implemented an invalid-thread-error detection tool that supports
+We implemented an invalid-thread-access-error detection tool that supports
 four popular GUI frameworks: SWT, Eclipse plugin framework,
@@
 popular GUI frameworks: SWT, Eclipse plugin, Swing, and Android (Section~\ref{sec:implementation}). Our
-implementation is publicly available at
+implementation is publicly available at:
 {\url{http://guierrordetector.googlecode.com}}.

### 2012-05-10 trunk/GUIErrorDetector/paper/technique.tex
make the number correct

@@
 \noindent {\textsc{\textbf{Assumption 2.}}} { We assume that each non-UI
-thread is spawned by the UI thread. Under this assumption,
+thread is (transitively) spawned by the UI thread. Under this assumption,
 we ignore all non-UI threads created by the GUI framework
-before the UI thread has been initialized. That is, all post-initialization
+before the UI thread has been initialized. That is, we assume all post-initialization
 GUI work occurs in the UI thread. Once the GUI is visible, the
@@
 %Thus,
-A reported method call chain containing an annotated  method
-can be safely removed. In our experiments, we produced a list of \filternum
-annotated methods for two subjects (Fennec and MyTracks) because they use a customized
-pattern to interact with the GUI framework.
+Assuming the user annotations are accurate,
+a reported method call chain containing an annotated method
+can be safely removed.
+
+In our experiments, 
+we produced a list of \filternum annotated methods for two
+subjects (MyTracks and Fennec), since they employ a customized pattern
+to interact with the GUI framework. For example, in MyTracks, all non-UI
+threads are initialized via using the library method \CodeIn{android.os\-.handler.handleCallback}.
+This method can be invoked from any thread and will never cause an
+invalid thread access error, because it checks whether the current
+thread is the UI thread or not before execution. If not,
+this method will use safe UI methods to run the code in the UI thread.
+
+% we produced a list of \filternum
+%annotated methods for two subjects (Fennec and MyTracks) because they use a customized
+%pattern to interact with the GUI framework.
 
@@
 be buggy. For example, the \CodeIn{Runtime.}\CodeIn{shutDown}
-method is called when JVM terminates, and uses multithreading
+method is called when the JVM terminates, and uses multithreading
 to dispose all GUI objects when the program exits.
-We encoded a list of 25 common library calls by proposing
-a basic set of library calls that seemed %natural and
-generally applicable, based on our programming experience.
-We later added other calls we found helpful in analyzing
-programs on different GUI frameworks and that we believed would be generally useful.
-%We did this only between experiments rather than biasing experiments by tuning
-%our tool to specific programs.
+Our experiments use a list of \libnum such library calls.
 
-\textbf{4. Filter Report with the Same Head Methods from the Entry Node to \CodeIn{Thread.start()}}. A method can call
+\textbf{4. Filter Reports with the Same Head Methods from the Entry Node to \CodeIn{Thread.start()}}. A method can call
 multiple methods that access GUI objects, such as:

### 2012-05-10 GUIErrorDetector/paper/technique.tex
add an example figure after section 2.1 and revise the makefile

@@
 non-UI threads spawned by the UI thread, and check whether those non-UI threads
-may invoke a UI-accessing method.
+may invoke a UI-accessing method.\vspace{1mm}
 
-\tinystep
+\noindent  {\textsc{\textbf{Example.}}} Figure~\ref{fig:simplecg} shows an example call graph
+to illustrate the invalid thread access problem.
+
+\begin{figure}[t]
+  \centering
+  \includegraphics[scale=0.44]{simplecg}
+  \vspace*{-1.0ex}\caption {{\label{fig:simplecg} A simple call graph to illustrate the
+invalid thread access problem. The \CodeIn{entry()} node is executing
+in a UI thread. Nodes \CodeIn{uiAcc1()}, \CodeIn{uiAcc2}, and \CodeIn{uiAcc3} are
+three UI-Accessing methods. Node \CodeIn{safe()} is a Safe UI Method.
+Node \CodeIn{start()} is a non-UI thread spawning method. Method call chain:
+\CodeIn{entry()} $\rightarrow$ \CodeIn{start()} $\rightarrow$ \CodeIn{uiAcc3()}
+indicates an invalid thread access error.}}
+\end{figure}
 
@@
 to dispose all GUI objects when the program exits.
-% We encoded a list of 25 common library calls by proposing
-% a basic set of library calls that seemed %natural and
-% generally applicable, based on our programming experience.
-% We later added other calls we found helpful in analyzing
-% programs on different GUI frameworks and that we believed would be generally useful.
-Our experiments use a list of 25 such library calls.
-%We did this only between experiments rather than biasing experiments by tuning
-%our tool to specific programs.
+Our experiments use a list of \libnum such library calls.
 

### 2012-05-10 trunk/GUIErrorDetector/paper/evaluation.tex
tweak the bug revision sentence

@@
  \hline
- EclipseRunner (1.1.0) &  3101 &  48 &  354\\
+ EclipseRunner (1.0.0) &  3101 &  48 &  354\\
  \hline
@@
  \hline
- MyTracks (1.1.13.rc4)&  20297 &  143 &  1374 \\
+ MyTracks (01d5c1e1cd47)&  20297 &  143 &  1374 \\
 \hline
@@
 
-%We first inspected the source code of each subject to determine whether any
-%native methods or project-specific GUI interaction patterns were implemented.
-
 Subject SGTPuzzler uses native methods to interact with
@@
 
-We manually determined the validity of each warning
-by either searching the bug repository to check bug-fixing revision histories,
-writing a test driver to reproduce
-the error,
-or submitting a new bug report.
+We manually determined the validity of each warning.
+For a known error, we compared the generated report (i.e., the
+error-revealing method call chain as Figure~\ref{fig:report} shows) against the
+actual error-fixing patch to check whether our tool correctly identified the
+erroneous method. For a previously-unknown error, we submitted a new bug
+report to its developers, and wrote a test driver to reproduce it.
 

### 2012-05-10 trunk/GUIErrorDetector/paper/technique.tex
small tweak

@@
 non-UI threads spawned by the UI thread, and check whether those non-UI threads
-may invoke a UI-accessing method.
+may invoke a UI-accessing method.\vspace{1mm}
 
-\tinystep
+\noindent  {\textsc{\textbf{Example.}}} Figure~\ref{fig:simplecg} shows an example call graph
+to illustrate the invalid thread access problem.
+
+\begin{figure}[t]
+  \centering
+  \includegraphics[scale=0.40]{simplecg}
+  \vspace*{-1.0ex}\caption {{\label{fig:simplecg} A simple call graph to illustrate the
+invalid thread access problem. The \CodeIn{entry()} node is executing
+in a UI thread. Nodes \CodeIn{uiAcc1()}, \CodeIn{uiAcc2}, and \CodeIn{uiAcc3} are
+three UI-Accessing methods. Node \CodeIn{safe()} is a Safe UI Method.
+Node \CodeIn{start()} is a non-UI thread spawning method. Method call chain:
+\CodeIn{entry()} $\rightarrow$ \CodeIn{start()} $\rightarrow$ \CodeIn{uiAcc3()}
+indicates an invalid thread access error.}}
+\vspace{-2mm}
+\end{figure}
 

### 2012-05-10 GUIErrorDetector/paper/evaluation.tex
small tweak

@@
  \hline
- Fennec (10.0.a.rc3)&  8577 &  51 &  620 \\
+ Fennec (d7fa4814218d)&  8577 &  51 &  620 \\
  \hline
- MyTracks (1.1.13.rc4)&  20297 &  143 &  1374 \\
+ MyTracks (01d5c1e1cd47)&  20297 &  143 &  1374 \\
 \hline
@@
 
-We manually determined the validity of each warning
-by either searching the bug repository to check bug-fixing revision histories,
-writing a test driver to reproduce
-the error,
-or submitting a new bug report.
+We manually determined the validity of each warning.
+For a known error, we compared the generated report (i.e., the
+error-revealing method call chain as Figure~\ref{fig:report} shows) against the
+actual error-fixing patch to check whether our tool correctly identified the
+erroneous method. For a previously-unknown error, we submitted a new bug
+report to its developers, and wrote a test driver to reproduce it.
+%wrote a test driver to
 

### 2012-05-10 trunk/GUIErrorDetector/paper/evaluation.tex
add the number of explored paths

@@
 report to its developers, and wrote a test driver to reproduce it.
+%wrote a test driver to
 
@@
 path spawns a new thread and accesses GUI objects without using safe UI methods.
-This variant ran out of memory on all subjects, and did not output any real
-errors before it terminated.  The number of
-non-cyclic paths in a graph is exponential in the graph size, and it 
-it is infeasible to enumerate all paths
-for a realistic call graph, which often contains thousands of nodes.
+However, the number of non-cyclic paths in a graph is exponential in the graph size,
+and it is infeasible for this variant to enumerate all paths for a realistic
+call graph, which often contains thousands of
+nodes (e.g., $2^{1000}$ $\approx$ 1.07$\times$$10^{301}$). In our experiment,
+we ran this variant on each subject for 1 hour, it explored 1.6$\times$$10^9$ paths on average, but did not
+output any real errors before it terminated.
+
+%for a realistic call graph consisting of thousands
+%of nodes,
+
 %only a very few amount of paths can be enumerated within a practical amount of time.
@@
 BFS and DFS are unsound because they visit
-every node, but do not traverse every \emph{path} path to visit that node.
+every node, but do not traverse every path to visit that node.
 Using BFS or DFS can be viewed as a heuristic filtering
@@
 Second, like many bug-finding techniques, our technique
-is neither sound nor complete. It may miss true positives due
-to the graph search strategy, and it never reports cyclic paths.  It may
-issue false positives due to the conservative nature of
-a static analysis. Designing better call graph construction algorithms,
+is neither sound nor complete. It may issue false positives
+due to the conservative nature of a static analysis.
+It may miss true positives due to the graph search strategy,
+and it never reports cyclic paths. Furthermore, for the
+sake of scalability, our tool implementation uses the default
+configuration of WALA and ignores part of the AWT library. Thus,
+it missed one error in S3dropbox which can be found by using a different
+technique~\cite{JSR308-webpage-201110}.
+Designing better call graph construction algorithms,
 graph search strategies, and filtering heuristics may alleviate this limitation.

### 2012-05-10 trunk/GUIErrorDetector/paper/evaluation.tex
update the num

@@
 nodes (e.g., $2^{1000}$ $\approx$ 1.07$\times$$10^{301}$). In our experiment,
-we ran this variant on each subject for 1 hour, it explored 1.6$\times$$10^9$ paths on average, but did not
+we ran this variant on each subject for 1 hour, it explored 4.9$\times$$10^9$ paths on average, but did not
 output any real errors before it terminated.

### 2012-05-11 GUIErrorDetector/paper/evaluation.tex
add 1 sentence to the limitation section. saying we missed 1 error found by jsr308.
add a link to the bug reports

@@
 
-%After checking against existing patches, we found
-%Our tool correctly identified the \oldbugs known errors, as compared to
-%their patches.
 We submitted all \newbugs new errors
@@
 1 error, and 3 errors in VirgoFTP, FileBunker, and ArecaBackup
-have not yet been verified by the developers.
+have not yet been verified by the developers. All found bugs
+and the tool's output are publicly available at: \url{http://www.cs.washington.edu/homes/szhang/guierror/}.
 
@@
 path spawns a new thread and accesses GUI objects without using safe UI methods.
-This variant ran out of memory on all subjects, and did not output any real
-errors before it terminated.  The number of
-non-cyclic paths in a graph is exponential in the graph size, and it 
-it is infeasible to enumerate all paths
-for a realistic call graph, which often contains thousands of nodes.
+However, the number of non-cyclic paths in a graph is exponential in the graph size,
+and it is infeasible for this variant to enumerate all paths for a realistic
+call graph, which often contains thousands of
+nodes (e.g., $2^{1000}$ $\approx$ 1.07$\times$$10^{301}$). In our experiment,
+we ran this variant on each subject for 1 hour, it explored 5.1$\times$$10^9$ paths on average, but did not
+output any real errors before it terminated.
+
+%for a realistic call graph consisting of thousands
+%of nodes,
+
 %only a very few amount of paths can be enumerated within a practical amount of time.

### 2012-05-12 GUIErrorDetector/paper/technique.tex
tweak

@@
   \centering
-  \includegraphics[scale=0.44]{simplecg}
+  \includegraphics[scale=0.40]{simplecg}
   \vspace*{-1.0ex}\caption {{\label{fig:simplecg} A simple call graph to illustrate the
-invalid thread access problem. The \CodeIn{entry()} node is executing
-in a UI thread. Nodes \CodeIn{uiAcc1()}, \CodeIn{uiAcc2}, and \CodeIn{uiAcc3} are
-three UI-Accessing methods. Node \CodeIn{safe()} is a Safe UI Method.
-Node \CodeIn{start()} is a non-UI thread spawning method. Method call chain:
-\CodeIn{entry()} $\rightarrow$ \CodeIn{start()} $\rightarrow$ \CodeIn{uiAcc3()}
-indicates an invalid thread access error.}}
+invalid thread access problem. The \CodeIn{entry()} node is executed
+in a UI thread. Nodes \CodeIn{uiAcc1()}, \CodeIn{uiAcc2()}, and \CodeIn{uiAcc3()} are
+three UI-accessing methods. Node \CodeIn{safe()} is a Safe UI Method, and
+node \CodeIn{start()} is a (non-UI) thread-spawning method. Methods \CodeIn{uiAcc1()}
+and \CodeIn{uiAcc2()} are executed in the UI thread, but method \CodeIn{uiAcc3()}
+is executed in a non-UI thread, leading to an invalid thread access error.}}
+\vspace{-2mm}
 \end{figure}

### 2012-05-12 trunk/GUIErrorDetector/paper/evaluation.tex
tweak

@@
 
-%After checking against existing patches, we found
-%Our tool correctly identified the \oldbugs known errors, as compared to
-%their patches.
-We submitted all \newbugs new errors
-to the respective developers. As of April 2012, 
-we have reproduced 3 errors, the S3dropbox developers have confirmed
-1 error, and 3 errors in VirgoFTP, FileBunker, and ArecaBackup
+We submitted all \newbugs new errors to the respective developers. As of May 2012, 
+1 error S3dropbox has been confirmed, we have reproduced 2 errors,
+and 4 errors in VirgoFTP, FileBunker, and ArecaBackup
 have not yet been verified by the developers. 
+%2 errors in SudokuSolver can be reproduced by simply
+%clicking its UIs, and the rest 4 errors can be reproduced
+%by writing a test driver have not yet been verified
+%by the developers.
+All found bugs and our experimental results are
+publicly available at: \url{http://www.cs.washington.edu/homes/szhang/guierror/}.
 
@@
 nodes (e.g., $2^{1000}$ $\approx$ 1.07$\times$$10^{301}$). In our experiment,
-we ran this variant on each subject for 1 hour, it explored 4.9$\times$$10^9$ paths on average, but did not
+we ran this variant on each subject for 1 hour, it explored 5.1$\times$$10^9$ paths on average, but did not
 output any real errors before it terminated.

### 2012-05-12 trunk/GUIErrorDetector/paper/evaluation.tex
small tweak

@@
 We manually determined the validity of each warning.
-For a known error, we compared the generated report (i.e., the
-error-revealing method call chain as Figure~\ref{fig:report} shows) against the
-actual error-fixing patch to check whether our tool correctly identified the
-erroneous method. For a previously-unknown error, we submitted a new bug
+For a known error, we compared the generated report (i.e., an
+error-revealing method call chain as shown in Figure~\ref{fig:report}) against the
+actual bug-fixing patch to check whether the tool identified the
+buggy method. For a previously-unknown error, we submitted a new bug
 report to its developers, and wrote a test driver to reproduce it.
@@
 We submitted all \newbugs new errors to the respective developers. As of May 2012, 
-1 error S3dropbox has been confirmed, we have reproduced 2 errors,
-and 4 errors in VirgoFTP, FileBunker, and ArecaBackup
+1 error S3dropbox has been confirmed, and we have reproduced other errors,
+in which 4 errors in VirgoFTP, FileBunker, and ArecaBackup
 have not yet been verified by the developers. 

### 2012-05-12 trunk/GUIErrorDetector/paper/implementation.tex
small tweak

@@
 
+We implemented an error detection tool on top of the WALA framework~\cite{walatutorial}.
 We instantiated the proposed technique for four widely-used
-GUI frameworks, namely SWT, Eclipse plugin framework, Swing, and Android;
-and implemented an error detection tool.
-
-Our tool is built on top of the WALA framework~\cite{walatutorial}.
-It takes Java bytecode as input, 
-automatically detects potential invalid thread access
-errors, and scales to realistic programs.
+GUI frameworks, namely SWT, Eclipse plugin framework, Swing, and Android.
 
@@
 \item \textbf{Safe UI methods:}  \CodeIn{Display.asyncExec}
-and \CodeIn{Display.syncExec}. SWT provides these two methods
-to execute code (a)synchro- nizedly on the UI thread.
+and \CodeIn{Display.syncExec}.
+These methods
+execute code (a)synchro\-nously in the UI thread.
 
@@
 
-\item \textbf{UI-accessing nodes} and \textbf{Safe UI methods} are the same as SWT.
+\item \textbf{UI-accessing nodes} and \textbf{safe UI methods} are the same as SWT\@.
 
 \end{itemize}
-\end{myindentpar}
 
@@
 \item \textbf{Safe UI methods:}  
-\CodeIn{SwingUtilities.}\CodeIn{invokeLater} and \CodeIn{SwingUti-\\lities.invokeAndWait}, which execute code on the UI thread.
+\CodeIn{SwingUtilities.}\CodeIn{invokeLater} and \CodeIn{Swing\-Util\-ities.invokeAndWait}, which execute code in the UI thread.
 
 \end{itemize}
-\end{myindentpar}
 
@@
 \item \textbf{Safe UI methods:}  \CodeIn{View.post}
-and \CodeIn{View.postDelay}, which execute code on the UI thread.
+and \CodeIn{View.postDelay}, which execute code in the UI thread.
 
 \end{itemize}
-\end{myindentpar}
 
@@
 
-Instantiating our general technique to  a specific framework
-requires moderate human effort. We wrote around 500 lines of Java code in total to achieve
-the above four instantiations.
+Given a GUI application using a supported framework, our tool 
+takes its Java bytecode as input, 
+plugs in the corresponding instantiation parameters at runtime,
+and automatically detects potential invalid thread access
+errors.
 

### 2012-05-12 GUIErrorDetector/paper/technique.tex
small tweak

@@
   \vspace*{-1.0ex}\caption {{\label{fig:simplecg} A simple call graph to illustrate the
-invalid thread access problem. The \CodeIn{entry()} node is executed
-in a UI thread. Nodes \CodeIn{uiAcc1()}, \CodeIn{uiAcc2()}, and \CodeIn{uiAcc3()} are
-three UI-accessing methods. Node \CodeIn{safe()} is a Safe UI Method, and
-node \CodeIn{start()} is a (non-UI) thread-spawning method. Methods \CodeIn{uiAcc1()}
-and \CodeIn{uiAcc2()} are executed in the UI thread, but method \CodeIn{uiAcc3()}
+invalid thread access problem. The \CodeIn{entry} method is executed
+in a UI thread. Nodes \CodeIn{uiAcc1}, \CodeIn{uiAcc2}, and \CodeIn{uiAcc3} are
+three UI-accessing methods. Node \CodeIn{safe} is a safe UI Method, and
+node \CodeIn{start} is a (non-UI) thread-spawning method. Methods \CodeIn{uiAcc1}
+and \CodeIn{uiAcc2} are executed in the UI thread, but method \CodeIn{uiAcc3}
 is executed in a non-UI thread, leading to an invalid thread access error.}}

### 2012-05-17 GUIErrorDetector/paper/abstract.tex
fix typoes, inconsistency
remove VirgoFTP

--- 2012-02-09 GUIErrorDetector/paper/abstract.tex
@@
 We implemented our technique and instantiated it for four popular Java GUI
-platforms: SWT, the Eclipse plugin development framework, Swing, and
+frameworks: SWT, the Eclipse plugin framework, Swing, and
 Android. In an evaluation on \subnum programs comprising \totaloc LOC, our technique
-found 5 previously-known errors and 7 new ones.
+found \oldbugs previously-known errors and \newbugs new ones.
 
 \end{abstract}
+
+\smallskip
+\noindent
+\textbf{Categories and Subject Descriptors}:  
+D.2.5 [Software Engineering]: Testing and Debugging.
+\\
+\textbf{General Terms: }
+Reliability, Experimentation.
+\\
+\textbf{Keywords: }
+Static analysis, invalid thread access error.
+
+\label{this-label-makes-etags-order-this-file-properly}
+
+%%% Local Variables: 
+%%% mode: latex
+%%% TeX-master: "guierror"
+%%% TeX-command-default: "PDF"
+%%% End:
+
+%  LocalWords:  multithreaded SWT plugin LOC

### 2012-05-17 trunk/GUIErrorDetector/paper/evaluation.tex
remove VirgoFTP

@@
 
-We used 10 open-source projects from SourceForge, Google Code,
+We used \subnum open-source projects from SourceForge, Google Code,
 and the Eclipse plugin marketplace as evaluation subjects.
@@
 %VirgoFTP~\cite{virgo} and FileBunker~\cite{filebunker} are two useful SWT desktop applications.
-VirgoFTP~\cite{virgo} implements a simple FTP client based on Java and the SWT UI library.
+%VirgoFTP~\cite{virgo} implements a simple FTP client based on Java and the SWT UI library.
 FileBunker~\cite{filebunker} is a file backup application that uses one or more GMail
@@
 \multicolumn{4}{|l|}{SWT desktop applications}   \\
- \hline
- VirgoFTP (1.3.5) &  10815 &  116 &  1955\\
+ %\hline
+ %VirgoFTP (1.3.5) &  10815 &  116 &  1955\\
  \hline
@@
 \hline
- Total &  99458 &  1094 &  11221 \\
+ Total &  \totaloc &  978 &  9266 \\
 \hline
@@
 \multicolumn{11}{|l|}{SWT desktop applications}   \\
- \hline
- VirgoFTP&  12401 &  1 &  1 & 10858 & 1 & 1 & 43598 & 2 & 2& 149  \\
+ %\hline
+ %VirgoFTP&  12401 &  1 &  1 & 10858 & 1 & 1 & 43598 & 2 & 2& 149  \\
  \hline
@@
 \hline
- Total & 199161 / 199724 &  177 / 251 & 5 / 5 & 149441 / 153054& 133 / 137& 6 / 7 & 577821 / 652756& 21 / 22 & 10 / 12 & 6542\\
+ Total & 186760 / 187323&  176 / 250 & 4 / 4 & 138583 / 142196& 132 / 136& 5 / 6 & 534223 / 609158& 19 / 20 & 8 / 10 & 6393\\
 \hline
@@
 with reflection calls and adding \annotationnum native method annotations
-for SGTPuzzler). The \newbugs errors found in VirgoFTP, FileBunker, ArecaBackup,
+for SGTPuzzler). The \newbugs errors found in FileBunker, ArecaBackup,
 S3dropbox, and SudokuSolver are previously  unknown. As a comparison, the
@@
 1 error S3dropbox has been confirmed, and we have reproduced other errors,
-in which 4 errors in VirgoFTP, FileBunker, and ArecaBackup
+in which 2 errors in FileBunker and ArecaBackup
 have not yet been verified by the developers. 
@@
 path spawns a new thread and accesses GUI objects without using safe UI methods.
-However, the number of non-cyclic paths in a graph is exponential in the graph size,
-and it is infeasible for this variant to enumerate all paths for a realistic
-call graph, which often contains thousands of
-nodes (e.g., $2^{1000}$ $\approx$ 1.07$\times$$10^{301}$). In our experiment,
-we ran this variant on each subject for 1 hour, it explored 5.1$\times$$10^9$ paths on average, but did not
-output any real errors before it terminated.
+We ran this variant on each subject for 1 hour, it explored 5.1$\times$$10^9$ paths
+on average, but did not output any real errors before it terminated.
+The number of non-cyclic paths in a graph is exponential in the graph size,
+and it is infeasible to enumerate all paths for a realistic call graph.
+In our experiments, the smallest call graph contains 7201 nodes and the average out-degree
+of each node is 2.15. Thus, a rough estimation for the number of distinct
+non-cyclic paths leads to an astronomically large number: 
+$2.15^{7201}$ $\approx$ 1.07$\times$$10^{2107}$.
 
@@
 \multicolumn{7}{|l|}{SWT desktop applications}   \\
- \hline
- VirgoFTP &  21 &  21 &  21 & 7 &  2 & 2\\
+ %\hline
+ %VirgoFTP &  21 &  21 &  21 & 7 &  2 & 2\\
  \hline
@@
  \hline
- Total &  60631 &  40461 &  39764 &  37421 &  112 & 22 \\
+ Total &  60610 &  40440 &  39753 &  37414 &  110 & \warnings \\
  \hline

### 2012-05-17 trunk/GUIErrorDetector/paper/evaluation.tex
small tweak

@@
 can correctly identify those known errors. 
-For the other five subjects, we selected them
+For the other four subjects, we selected them
 by first searching for the
@@
 error-revealing method call chain as shown in Figure~\ref{fig:report}) against the
-actual bug-fixing patch to check whether the tool identified the
+actual bug fix to check whether the tool identified the
 buggy method. For a previously-unknown error, we submitted a new bug
@@
 errors in each subject. Using the 1-CFA
-call graph algorithm, our tool issued 22 warnings, among
+call graph algorithm, our tool issued \warnings warnings, among
 which \bugs warnings reveal \bugs distinct errors (\newbugs were previously unknown,
@@
 Figure~\ref{fig:detectalgorithm} does.
-This variant reported 10 errors and 12 false positives.   It missed 1 error in S3dropbox and 1 error in
+This variant reported 8 errors and 12 false positives.   It missed 1 error in S3dropbox and 1 error in
 SudokuSolver.
@@
 to pop and pushAll.
-This variant reported 11 errors and 10 false positives.  It missed 1 error in FileBunker.
+This variant reported 9 errors and 10 false positives.  It missed 1 error in FileBunker.
 DFS tends to search deeper into the graph and return longer paths that are

### 2012-05-17 GUIErrorDetector/paper/technique.tex
change figure name

@@
   \centering
-  \includegraphics[scale=0.40]{simplecg}
+  \includegraphics[scale=0.40]{simplecg-no-mark}
   \vspace*{-1.0ex}\caption {{\label{fig:simplecg} A simple call graph to illustrate the
@@
 and \CodeIn{uiAcc2} are executed in the UI thread, but method \CodeIn{uiAcc3}
-is executed in a non-UI thread, leading to an invalid thread access error.}}
+is executed in a non-UI thread, causing an invalid thread access error.}}
 \vspace{-2mm}

### 2012-05-17 GUIErrorDetector/paper/evaluation.tex
make the call graph construction section shorter, and the paper now fits in 11 pages

@@
 We manually determined the validity of each warning.
-For a known error, we compared the generated report (i.e., the
-error-revealing method call chain as Figure~\ref{fig:report} shows) against the
-actual error-fixing patch to check whether our tool correctly identified the
-erroneous method. For a previously-unknown error, we submitted a new bug
+For a known error, we compared the generated report (i.e., an
+error-revealing method call chain as shown in Figure~\ref{fig:report}) against the
+actual bug fix to check whether the tool identified the
+buggy method. For a previously-unknown error, we submitted a new bug
 report to its developers, and wrote a test driver to reproduce it.
@@
 
-We submitted all \newbugs new errors
-to the respective developers. As of April 2012, 
-we have reproduced 3 errors, the S3dropbox developers have confirmed
-1 error, and 3 errors in VirgoFTP, FileBunker, and ArecaBackup
-have not yet been verified by the developers. All found bugs
-and the tool's output are publicly available at: \url{http://www.cs.washington.edu/homes/szhang/guierror/}.
+We submitted all \newbugs new errors to the respective developers. As of May 2012, 
+1 error S3dropbox has been confirmed, and we have reproduced other errors,
+in which 2 errors in FileBunker and ArecaBackup
+have not yet been verified by the developers. 
+%2 errors in SudokuSolver can be reproduced by simply
+%clicking its UIs, and the rest 4 errors can be reproduced
+%by writing a test driver have not yet been verified
+%by the developers.
+All found bugs and our experimental results are
+publicly available at: \url{http://www.cs.washington.edu/homes/szhang/guierror/}.
 
@@
 in our evaluation. Using other 
-call graph construction algorithms such as XTA~\cite{xta} or VTA~\cite{Sundaresan:2000} 
+call graph construction algorithms %such as XTA~\cite{xta} or VTA~\cite{Sundaresan:2000} 
  might achieve different results.

### 2012-05-17 trunk/GUIErrorDetector/paper/related.tex
improve the related work and conclusion.
small tweak for space
make the call graph construction section shorter, and the paper now fits in 11 pages

@@
 A rich body of techniques have been developed to detect bugs in multithreaded programs~\cite{Huang:2011:PPC:2001420.2001438, Naik:2006, Savage:1997, smc}.
+Runtime analysis tools such as Eraser~\cite{Savage:1997} 
+dynamically detect concurrency bugs using lockset algorithms.
 Static analysis tools such as Chord~\cite{Naik:2006}
-explore multithreaded programs. Runtime
-analysis tools such as Eraser~\cite{Savage:1997}  dynamically detect concurrency bugs using lockset
-algorithms.
+exploit a key property of Java - namely the scoped use
+of locks, to further improve the precision of lockset computations.
 However, finding invalid thread access errors is quite different than detecting data races.
@@
 
+%\begin{comment}
+
 \tinystep
@@
 
+\begin{comment}
 %\noindent \textit{\textbf{Call Graph Construction Algorithms}}
@@
 
+\end{comment}
+
+Call graph construction algorithms have been well studied in the literature. However,
+standard algorithms such as RTA~\cite{rta} and k-CFA~\cite{kcfa} do not build
+a sound call graph in the presence of reflection.
+As reflected in our experiments, using standard call graph algorithms
+misses errors in some Android applications.
 Livshits et al.~\cite{Livshits:2005} presented a static analysis
@@
 
+%\end{comment}
+
 %There are few algorithms have been studied to construct call

### 2012-05-17 GUIErrorDetector/paper/introduction.tex
tweak space

@@
                         \itemindent    \listparindent
-                        \leftmargin=10pt%  whatever you need
-                        \rightmargin=0pt%whatever you need
+                        \leftmargin=14pt%  whatever you need
+                        \rightmargin=14pt%whatever you need
                         \topsep=0pt%%%%%  whatever you need
@@
 
-\begin{myquotation}
+%\begin{myquotation}
+%this is on purpose. if not, the code in the next page will be
+%scattered into 2 pages
+\vspace{-2mm}
+\begin{quotation}
 All GUI objects, including visual components and data models, must be
  accessed exclusively from the \textit{event dispatching thread}.
-\end{myquotation}
+\end{quotation}
+\vspace{-2mm}
+%\end{myquotation}
 
@@
 Searching for ``SWTException:Invalid thread access'' in Eclipse's bug repository
-and discussion forum returns 2732 bug reports and 351 distinct discussion threads, respectively. 
+and discussion forum returns over 2700 bug reports and 350 distinct discussion threads, respectively. 
 We manually studied all 156 distinct \textit{confirmed} bug reports, and 
@@
 Figure~\ref{fig:report}.
-}} \vspace{-1.8mm}
+}} %\vspace{-1.8mm}
 \end{figure}

### 2012-05-17 GUIErrorDetector/paper/evaluation.tex
improve sentences
small wording tweak

@@
 We submitted all \newbugs new errors to the respective developers. As of May 2012, 
-1 error S3dropbox has been confirmed, and we have reproduced other errors,
-in which 2 errors in FileBunker and ArecaBackup
-have not yet been verified by the developers. 
+1 error S3dropbox has been confirmed, and we have reproduced other errors.
+All found bugs and our experimental results are
+publicly available at: \url{http://www.cs.washington.edu/homes/szhang/guierror/}.
+%in which 2 errors in FileBunker and ArecaBackup
+%have not yet been verified by the developers. 
 %2 errors in SudokuSolver can be reproduced by simply
@@
 %by the developers.
-All found bugs and our experimental results are
-publicly available at: \url{http://www.cs.washington.edu/homes/szhang/guierror/}.
 
@@
 of each node is 2.15. Thus, a rough estimation for the number of distinct
-non-cyclic paths leads to an astronomically large number: 
+non-cyclic paths gives an astronomically large number: 
 $2.15^{7201}$ $\approx$ 1.07$\times$$10^{2107}$.

### 2012-05-17 trunk/GUIErrorDetector/paper/technique.tex
change back to the graph

@@
   \vspace*{-1.0ex}\caption {{\label{fig:simplecg} A simple call graph to illustrate the
-invalid thread access problem. The \CodeIn{entry()} node is executing
-in a UI thread. Nodes \CodeIn{uiAcc1()}, \CodeIn{uiAcc2}, and \CodeIn{uiAcc3} are
-three UI-Accessing methods. Node \CodeIn{safe()} is a Safe UI Method.
-Node \CodeIn{start()} is a non-UI thread spawning method. Method call chain:
-\CodeIn{entry()} $\rightarrow$ \CodeIn{start()} $\rightarrow$ \CodeIn{uiAcc3()}
-indicates an invalid thread access error.}}
+invalid thread access problem. The \CodeIn{entry} method is executed
+in a UI thread. Nodes \CodeIn{uiAcc1}, \CodeIn{uiAcc2}, and \CodeIn{uiAcc3} are
+three UI-accessing methods. Node \CodeIn{safe} is a safe UI Method, and
+node \CodeIn{start} is a (non-UI) thread-spawning method. Methods \CodeIn{uiAcc1}
+and \CodeIn{uiAcc2} are executed in the UI thread, but method \CodeIn{uiAcc3}
+is executed in a non-UI thread, causing an invalid thread access error.}}
 \vspace{-2mm}

### 2012-05-18 trunk/GUIErrorDetector/paper/evaluation.tex
correct a typo

@@
 to drag and drop files to their Amazon S3 accounts. SudokuSolver~\cite{sudokusolver}
-computes Sudoku solutions using mutlithreaded execution.
+computes Sudoku solutions using multithreaded execution.
 

### 2012-05-19 GUIErrorDetector/paper/evaluation.tex
Small tweaks.  Also adjust spacing to avoid bad page breaks.

@@
 
-We ran our tool on each subject with three call graph construction
+We ran our tool on each subject program with three call graph construction
 algorithms: RTA~\cite{rta}, 0-CFA, and 1-CFA~\cite{kcfa}.  When running
@@
 In this experiment, none of the paper
-authors was familiar with the subjects, but we found it was quite easy
+authors was familiar with the subject programs, but we found it was quite easy
 to add extra annotations and user-defined filters. All these
@@
 As shown in Table~\ref{table:results}, our tool found
-errors in each subject. Using the 1-CFA
+errors in each subject program. Using the 1-CFA
 call graph algorithm, our tool issued \warnings warnings, among
@@
 We submitted all \newbugs new errors to the respective developers. As of May 2012, 
-1 error S3dropbox has been confirmed, and we have reproduced other errors.
+1 error in S3dropbox has been confirmed, and we have reproduced all the other errors.
 All found bugs and our experimental results are
-publicly available at: \url{http://www.cs.washington.edu/homes/szhang/guierror/}.
+publicly available at \url{http://www.cs.washington.edu/homes/szhang/guierror/}.
 %in which 2 errors in FileBunker and ArecaBackup
@@
 
-We found GUI developers have already
+\enlargethispage{5pt}
+
+We found that GUI developers have already
 used design patterns, runtime checks, and testing to avoid violating
@@
 path spawns a new thread and accesses GUI objects without using safe UI methods.
-We ran this variant on each subject for 1 hour, it explored 5.1$\times$$10^9$ paths
-on average, but did not output any real errors before it terminated.
+We ran this variant on each subject program for 1 hour.  It explored 5.1$\times$$10^9$ paths
+on average, but did not output any of the 10 errors before it terminated.
 The number of non-cyclic paths in a graph is exponential in the graph size,
@@
 In our experiments, the smallest call graph contains 7201 nodes and the average out-degree
-of each node is 2.15. Thus, a rough estimation for the number of distinct
-non-cyclic paths gives an astronomically large number: 
+of each node is 2.15.  The number of distinct
+non-cyclic paths is astronomically large; a rough estimate is
 $2.15^{7201}$ $\approx$ 1.07$\times$$10^{2107}$.
@@
 \noindent \textbf{\textit{Performance and scalability.}} Our tool
-has been evaluated on \subnum subjects with \totaloc LOC and frameworks
+has been evaluated on \subnum subject programs with \totaloc LOC and frameworks
 with 1.4 MLOC, showing good scalability. Our evaluations
@@
 configuration of WALA and ignores part of the AWT library. Thus,
-it missed one error in S3dropbox which can be found by using a different
-technique~\cite{JSR308-webpage-201110}.
+it missed one error in S3dropbox which we later found by using pluggable type-checking~\cite{DietlDEMS2011}.
 Designing better call graph construction algorithms,

### 2012-05-19 trunk/GUIErrorDetector/paper/technique.tex
Tweak caption

@@
 invalid thread access problem. The \CodeIn{entry} method is executed
-in a UI thread. Nodes \CodeIn{uiAcc1}, \CodeIn{uiAcc2}, and \CodeIn{uiAcc3} are
-three UI-accessing methods. Node \CodeIn{safe} is a safe UI Method, and
-node \CodeIn{start} is a (non-UI) thread-spawning method. Methods \CodeIn{uiAcc1}
+in the UI thread. Nodes \CodeIn{uiAcc1}, \CodeIn{uiAcc2}, and \CodeIn{uiAcc3} are
+UI-accessing methods. Node \CodeIn{start} is a (non-UI)
+thread-spawning method, and
+node \CodeIn{safe} is a safe UI Method. Methods \CodeIn{uiAcc1}
 and \CodeIn{uiAcc2} are executed in the UI thread, but method \CodeIn{uiAcc3}

### 2012-05-19 trunk/GUIErrorDetector/paper/evaluation.tex
correct typo
margin change

@@
 \Caption{{\label{table:subjects} Open-source programs
-used in our evaluation. Column ``LOC'' is the number of non-blank, non-comment lines
+used in our evaluation. Column ``LOC'' is the number of lines
 of code, as counted by LOCC~\cite{locc}.  Each program is analyzed
 together with its GUI framework, as listed in
-the bottom table.} }
+the bottom table.}} 
 \end{table}
@@
 
+%\vspace{2mm}
+\vspace{-3mm}
 \subsection{Experimental Procedure}
@@
 \tinystep
+%\vspace{1mm}
 \subsection{Results}
@@
 
+\vspace{-1mm}
 \subsubsection{Errors in Multithreaded GUI Applications}
@@
 a non-UI thread. This error was previously unknown, and has been confirmed by the S3dropbox developers.
-}} %\vspace{-5mm}
+}} %\vspace{-1mm}
 \end{figure}
@@
 
+%\vspace{-4mm}
 \subsubsection{Comparison to Requiring Wrappers}

### 2012-05-19 GUIErrorDetector/paper/evaluation.tex
rollback
Remove \enlargethispage

@@
 
-\enlargethispage{5pt}
-
 We found that GUI developers have already

### 2012-05-21 GUIErrorDetector/sampleprogram/test/testsamplecrash/TestCrash.java
uncomit changes

@@ -1,0 +1,42 @@
+package test.testsamplecrash;
+
+import org.eclipse.swt.SWT;
+import org.eclipse.swt.graphics.GC;
+import org.eclipse.swt.graphics.Image;
+import org.eclipse.swt.layout.RowLayout;
+import org.eclipse.swt.widgets.Button;
+import org.eclipse.swt.widgets.Display;
+import org.eclipse.swt.widgets.Shell;
+import org.eclipse.swt.widgets.Text;
+
+
+import junit.framework.TestCase;
+
+public class TestCrash extends TestCase {
+	
+	private static Text helloWorldTest;
+
+	private static Shell shell;
+
+	private static Display display;
+
+	
+	public static void main(String[] args) {
+		display = new Display();
+		
+		
+		
+		
+		Thread t = new Thread() {
+            public void run () {
+            	Image offScreenImage = new Image (display, 1, 1);
+            	GC offScreenImageGC = new GC (offScreenImage);
+//            	display.getSystemFont();
+            	offScreenImageGC.drawImage(offScreenImage, 1, 2);
+//            	helloWorldTest.setText("hello");
+            }
+		};
+        t.start();
+	}
+	
+}

### 2012-05-21 GUIErrorDetector/tests/edu/washington/cs/detector/experiments/swing/TestSudokuPuzzleSolver.java
uncomit changes

@@ -39,8 +39,8 @@ public class TestSudokuPuzzleSolver extends AbstractSwingTest {
 		super.setCGType(CG.RTA);
 //		super.setCGType(CG.ZeroCFA);
 //		super.setCGType(CG.OneCFA);
-		super.setCGType(CG.TempZeroCFA);
-//		super.setCGType(CG.OneCFA);
+//		super.setCGType(CG.TempZeroCFA);
+		super.setCGType(CG.OneCFA);
 		
 		UIAnomalyDetector.setToUseDFS(); //use DFS
 		

### 2012-05-21 trunk/GUIErrorDetector/tests/edu/washington/cs/detector/experiments/swing/TestS3Dropbox.java
uncomit changes

@@ -67,8 +67,8 @@ public class TestS3Dropbox extends AbstractSwingTest {
 		
 		UIAnomalyDetector.DEBUG = true;
 		super.setCGType(CG.OneCFA);
-		super.setCGType(CG.RTA);
-		super.setCGType(CG.ZeroCFA);
+//		super.setCGType(CG.RTA);
+//		super.setCGType(CG.ZeroCFA);
 		
 //		UIAnomalyDetector.setToUseDFS(); //use DFS
 		

### 2012-05-21 trunk/GUIErrorDetector/tests/edu/washington/cs/detector/experiments/search/ExhaustiveSearcher.java
uncomit changes

@@ -12,6 +12,7 @@ import com.ibm.wala.util.graph.Graph;
 import edu.washington.cs.detector.NativeMethodConnector;
 import edu.washington.cs.detector.guider.CGTraverseDefaultGuider;
 import edu.washington.cs.detector.guider.CGTraverseGuider;
+import edu.washington.cs.detector.util.Log;
 
 /**
  * The basic algorithm to perform exhaustive search of all
@@ -83,6 +84,7 @@ abstract public class ExhaustiveSearcher {
 	 *   breadFirst(graph, new LinkedList<CGNode>());  //empty visited nodes at the beginning
 	 *   
 	 * */
+	private static long pathNum = 0;
 	public Collection<List<CGNode>> breadFirst(Graph<CGNode> graph, LinkedList<CGNode> visited) {
 		Collection<List<CGNode>> returnChains = new LinkedHashSet<List<CGNode>>();
 		//return the current visited chains if time is up
@@ -93,6 +95,10 @@ abstract public class ExhaustiveSearcher {
         }
 		//fetch one from the visited list, and get all adjacent nodes.
 		CGNode lastNode = visited.getLast();
+		pathNum++;
+		if(pathNum % 10000000 == 0) {
+			Log.logln("The current number of explored paths: " + pathNum);
+		}
 		LinkedList<CGNode> ajacentNodes = this.getAdjacentNodes(graph, lastNode);
 		//check whether that it is a native method or not
 		//if it is native method, check whether this native method is annotated to be called
@@ -125,6 +131,9 @@ abstract public class ExhaustiveSearcher {
                 //create the path
                 List<CGNode> chain = this.generatePath(visited);
                 returnChains.add(chain);
+//                if(returnChains.size() % 100 == 0) {
+//                	System.out.println("chain num: " + returnChains.size());
+//                }
                 //return if time up
                 if(USE_CLOCK) {
                 	if(SimpleClock.finish()) {

### 2012-05-21 trunk/GUIErrorDetector/tests/edu/washington/cs/detector/experiments/android/AbstractAndroidTest.java
uncomitted changes

@@ -122,7 +122,7 @@ public abstract class AbstractAndroidTest extends TestCase {
 	    builder.makeScopeAndClassHierarchy();
 	    ClassHierarchy cha = builder.getClassHierarchy();
 
-		Log.logConfig("./log.txt");
+		Log.logConfig("./android-log.txt");
 	    
 	    Collection<IClass> runnableInApp = WALAUtils.getRunnablesInApp(cha);
 	    Collection<IClass> runnableInClient = new LinkedHashSet<IClass>();
@@ -303,9 +303,10 @@ public abstract class AbstractAndroidTest extends TestCase {
 			
 			ExhaustiveSearcher.USE_CLOCK = true;
 			SimpleClock.start();
-			SimpleClock.setBudget(1200000); //20 mins
+			SimpleClock.setBudget(1200000*3); //20 mins set the exploration time limit
 			
 			Collection<List<CGNode>> result = searcher.findFullAnomalyCallChains();
+			System.out.println("Number of searched method call chains: " + result.size());
 			
 			SimpleClock.reset();
 			ExhaustiveSearcher.USE_CLOCK = false;

### 2012-05-21 trunk/GUIErrorDetector/tests/edu/washington/cs/detector/experiments/android/TestMozillaFirefox.java

@@ -119,6 +119,7 @@ public class TestMozillaFirefox extends AbstractAndroidTest {
 //		//
 //		return nonRedundant;
 //	}
+	//560000000
 	public void testFindErrors() {
 		CGTraverseGuider ui2startGuider = new CGTraverseAndroidGuider();
 		String[] arrays 
@@ -140,6 +141,7 @@ public class TestMozillaFirefox extends AbstractAndroidTest {
 			type = CG.OneCFA;
 //			type = CG.RTA;
 	
+//			super.setExhaustiveSearch(true);
 //			UIAnomalyDetector.setToUseDFS();
 //			ThreadStartFinder.check_find_all_starts = true;
 			

### 2012-05-21 GUIErrorDetector/tests/edu/washington/cs/detector/experiments/android/TestMytracksAndroid.java
uncomitted changes

@@ -89,6 +89,7 @@ public class TestMytracksAndroid extends AbstractAndroidTest {
 //		
 //		return result;
 //	}
+	//explored 390000000 paths
 	public void testFindErrors() {
 		CGTraverseGuider ui2startGuider = new CGTraverseAndroidGuider();
 		String[] guiderArray = 
@@ -123,6 +124,7 @@ public class TestMytracksAndroid extends AbstractAndroidTest {
 //			type = CG.TempZeroCFA;
 			type = CG.OneCFA;
 			
+//			super.setExhaustiveSearch(true);
 //			UIAnomalyDetector.setToUseDFS();
 			
 			long startT = System.currentTimeMillis();

### 2012-05-21 GUIErrorDetector/tests/edu/washington/cs/detector/experiments/android/TestSGTPuzzle.java

@@ -85,6 +85,7 @@ public class TestSGTPuzzle extends AbstractAndroidTest {
 	    return extraEntrypoints;
 	}
 	
+	//for exhaustive search it outputs 5.0 * 10^8 paths in a hour
 	public void testFindErrors() throws ClassHierarchyException, IOException {
 		CGTraverseGuider ui2startGuider = new CGTraverseAndroidGuider();
 		CGTraverseExploreClientRunnableStrategy start2checkGuider
@@ -134,7 +135,7 @@ public class TestSGTPuzzle extends AbstractAndroidTest {
 			//this finds bugs
 //		  List<AnomalyCallChain> chains = super.findErrorsInAndroidApp(CG.RTA, ui2startGuider, start2checkGuider, connector);
 		  CG type = CG.TempZeroCFA;
-//		  type = CG.OneCFA;
+		  type = CG.OneCFA;
 //		  type = CG.RTA;
 		  
 //		  super.setExhaustiveSearch(true);

### 2012-05-21 GUIErrorDetector/tests/edu/washington/cs/detector/SmallSmokeTest.java
tweak

@@ -16,7 +16,7 @@ public class SmallSmokeTest extends TestCase {
 		PDFViewer.DISABLE_VIEW_CG = true;
 		
 		TestSuite suite = new TestSuite();
-		
+	 
 		//remove this, since it need environment-specific settings
 		//suite.addTest(TestUtils.suite());
 		suite.addTest(TestFileExistence.suite());

### 2012-05-21 GUIErrorDetector/tests/edu/washington/cs/detector/experiments/swt/TestIpScan.java
tweak

@@ -14,6 +14,7 @@ import edu.washington.cs.detector.experiments.filters.MergeSameTailStrategy;
 import edu.washington.cs.detector.experiments.filters.RemoveSystemCallStrategy;
 import edu.washington.cs.detector.guider.CGTraverseSWTGuider;
 import edu.washington.cs.detector.util.Globals;
+import edu.washington.cs.detector.util.Log;
 import edu.washington.cs.detector.util.Utils;
 import edu.washington.cs.detector.util.WALAUtils;
 import junit.framework.TestCase;
@@ -26,11 +27,12 @@ public class TestIpScan extends TestCase {
 	public String libJar =  dir + "swt-win64.jar"
 	     + Globals.pathSep + dir + "picocontainer-1.0.jar";
 
-	String[] packages = new String[]{"net.azib.ipscan"};
+	String[] packages = new String[]{"net.azib.ipscan", "org.savarese"};
 	
 	String logFile = "./logs/ipscan-anomalies.txt";
 	
 	public void testIpscan() throws IOException {
+		Log.logConfig("./log.txt");
 		String path = appPath + Globals.pathSep + libJar;
         UIAnomalyDetector detector = new UIAnomalyDetector(path);
         
@@ -43,6 +45,7 @@ public class TestIpScan extends TestCase {
 //		builder.setCGType(CG.FakeZeroCFA);
 		
 		//UIAnomalyDetector.setToUseDFS();
+		UIAnomalyDetector.DEBUG = true;
 		
 		builder.buildCG();
 		

### 2012-05-21 trunk/GUIErrorDetector/tests/edu/washington/cs/detector/experiments/swt/TestArecaBackup.java
tweak

@@ -10,8 +10,10 @@ import edu.washington.cs.detector.TestCommons;
 import edu.washington.cs.detector.UIAnomalyDetector;
 import edu.washington.cs.detector.CGBuilder.CG;
 import edu.washington.cs.detector.experimental.InvalidThreadAccessDetector;
+import edu.washington.cs.detector.experiments.filters.MergeSameEntryToStartPathStrategy;
 import edu.washington.cs.detector.experiments.filters.MergeSamePrefixToLibCallStrategy;
 import edu.washington.cs.detector.experiments.filters.MergeSameTailStrategy;
+import edu.washington.cs.detector.experiments.filters.RemoveSubsumedChainStrategy;
 import edu.washington.cs.detector.experiments.filters.RemoveSystemCallStrategy;
 import edu.washington.cs.detector.guider.CGTraverseSWTGuider;
 import edu.washington.cs.detector.util.Globals;
@@ -40,6 +42,7 @@ public class TestArecaBackup extends TestCase {
 	    
 	
 	public void testArecaBackup() throws IOException {
+		long start = System.currentTimeMillis();
 		String path = appPath + Globals.pathSep + libJar;
 		
 //        UIAnomalyDetector detector = new UIAnomalyDetector(path);
@@ -51,23 +54,35 @@ public class TestArecaBackup extends TestCase {
 		
 		CGBuilder builder = new CGBuilder(path);
 		builder.setCGType(CG.OneCFA);
-//		builder.setCGType(CG.RTA);
-//		builder.setCGType(CG.FakeZeroCFA);
+		builder.setCGType(CG.RTA);
+		builder.setCGType(CG.TempZeroCFA);
 		
 		//UIAnomalyDetector.setToUseDFS();
 		
+		long cgStart = System.currentTimeMillis();
 		builder.buildCG();
+		long cgEnd = System.currentTimeMillis();
+		System.out.println("cg building time: " + (cgEnd - cgStart));
+//		System.exit(1);
 		
 		WALAUtils.dumpClasses(builder.getClassHierarchy(), "./logs/loaded_classes.txt");
 	    Utils.dumpCollection(WALAUtils.getUnloadedClasses(builder.getClassHierarchy(),
 	    		TestCommons.getJarsFromPath(path)),  "./logs/unloaded_classes.txt");
-		
+	    
 		List<AnomalyCallChain> chains = detector.detectUIAnomaly(builder);
[…]

### 2012-05-21 trunk/GUIErrorDetector/tests/edu/washington/cs/detector/experiments/swt/TestFileBunker.java

@@ -13,6 +13,7 @@ import edu.washington.cs.detector.experimental.InvalidThreadAccessDetector;
 import edu.washington.cs.detector.experiments.filters.MergeSameEntryToStartPathStrategy;
 import edu.washington.cs.detector.experiments.filters.MergeSameTailStrategy;
 import edu.washington.cs.detector.experiments.filters.RemoveContainingNodeStrategy;
+import edu.washington.cs.detector.experiments.filters.RemoveSubsumedChainStrategy;
 import edu.washington.cs.detector.experiments.filters.RemoveSystemCallStrategy;
 import edu.washington.cs.detector.guider.CGTraverseSWTGuider;
 import edu.washington.cs.detector.util.Globals;
@@ -40,12 +41,14 @@ public class TestFileBunker extends TestCase {
 		
 		Log.logConfig("./log.txt");
 		
+		long start = System.currentTimeMillis();
+		
 		UIAnomalyDetector.DEBUG = true;
 		
 		//initialize a UI anomaly detector
-//        UIAnomalyDetector detector = new UIAnomalyDetector(path);
+        UIAnomalyDetector detector = new UIAnomalyDetector(path);
 		
-		InvalidThreadAccessDetector detector = new InvalidThreadAccessDetector(path);
+//		InvalidThreadAccessDetector detector = new InvalidThreadAccessDetector(path);
         
         detector.setThreadStartGuider(new CGTraverseSWTGuider());
         detector.setUIAnomalyGuider(new CGTraverseSWTGuider());
@@ -53,13 +56,18 @@ public class TestFileBunker extends TestCase {
 		//configure the call graph builder, use 1-CFA as default
 		CGBuilder builder = new CGBuilder(path);
 		builder.setCGType(CG.OneCFA);
-//		builder.setCGType(CG.RTA);
+		builder.setCGType(CG.RTA);
 //		builder.setCGType(CG.ZeroCFA);
-//		builder.setCGType(CG.FakeZeroCFA);
+		builder.setCGType(CG.TempZeroCFA);
 		
-//		UIAnomalyDetector.setToUseDFS();
+		UIAnomalyDetector.setToUseDFS();
 		
+		long cgstart = System.currentTimeMillis();
 		builder.buildCG();
+		long cgend = System.currentTimeMillis();
+		System.out.println("CG building time: " + (cgend - cgstart));
+//		System.exit(1);
+		
 		//dump debugging information
[…]

### 2012-05-21 GUIErrorDetector/tests/edu/washington/cs/detector/experiments/swt/TestVirgoFtp.java
comit

@@ -11,8 +11,10 @@ import edu.washington.cs.detector.ThreadStartFinder;
 import edu.washington.cs.detector.UIAnomalyDetector;
 import edu.washington.cs.detector.CGBuilder.CG;
 import edu.washington.cs.detector.experimental.InvalidThreadAccessDetector;
+import edu.washington.cs.detector.experiments.filters.MergeSameEntryToStartPathStrategy;
 import edu.washington.cs.detector.experiments.filters.MergeSamePrefixToLibCallStrategy;
 import edu.washington.cs.detector.experiments.filters.MergeSameTailStrategy;
+import edu.washington.cs.detector.experiments.filters.RemoveSubsumedChainStrategy;
 import edu.washington.cs.detector.experiments.filters.RemoveSystemCallStrategy;
 import edu.washington.cs.detector.guider.CGTraverseSWTGuider;
 import edu.washington.cs.detector.util.Globals;
@@ -33,28 +35,33 @@ public class TestVirgoFtp extends TestCase {
 	    Globals.pathSep + "D:\\research\\guierror\\eclipsews\\virgoftp-1.3.5\\xerces.jar";
 	
 	public void testRunVirgoFtp() throws IOException {
+		long start = System.currentTimeMillis();
 		String path = appPath + Globals.pathSep + libJar;
 		
 		Log.logConfig("./log.txt");
 		
-//        UIAnomalyDetector detector = new UIAnomalyDetector(path);
+        UIAnomalyDetector detector = new UIAnomalyDetector(path);
 		
 		//the worklist based
-        InvalidThreadAccessDetector detector = new InvalidThreadAccessDetector(path);
+//        InvalidThreadAccessDetector detector = new InvalidThreadAccessDetector(path);
         
         detector.setThreadStartGuider(new CGTraverseSWTGuider());
         detector.setUIAnomalyGuider(new CGTraverseSWTGuider());
 		
 		CGBuilder builder = new CGBuilder(path);
 		builder.setCGType(CG.OneCFA);
-//		builder.setCGType(CG.RTA);
-//		builder.setCGType(CG.FakeZeroCFA);
+		builder.setCGType(CG.RTA);
+		builder.setCGType(CG.TempZeroCFA);
 		
-		ThreadStartFinder.check_find_all_starts = true;
+//		ThreadStartFinder.check_find_all_starts = true;
 		
 		//UIAnomalyDetector.setToUseDFS();
 		
+		long cgStart = System.currentTimeMillis();
[…]

### 2012-05-21 trunk/GUIErrorDetector/tests/edu/washington/cs/detector/experiments/swt/TestProgram.java

@@ -1,0 +1,88 @@
+package edu.washington.cs.detector.experiments.swt;
+
+import java.io.IOException;
+import java.util.List;
+
+import edu.washington.cs.detector.AnomalyCallChain;
+import edu.washington.cs.detector.CGBuilder;
+import edu.washington.cs.detector.CallChainFilter;
+import edu.washington.cs.detector.TestCommons;
+import edu.washington.cs.detector.UIAnomalyDetector;
+import edu.washington.cs.detector.CGBuilder.CG;
+import edu.washington.cs.detector.experiments.filters.MergeSamePrefixToLibCallStrategy;
+import edu.washington.cs.detector.experiments.filters.MergeSameTailStrategy;
+import edu.washington.cs.detector.experiments.filters.RemoveSystemCallStrategy;
+import edu.washington.cs.detector.guider.CGTraverseSWTGuider;
+import edu.washington.cs.detector.util.Globals;
+import edu.washington.cs.detector.util.Log;
+import edu.washington.cs.detector.util.Utils;
+import edu.washington.cs.detector.util.WALAUtils;
+import junit.framework.TestCase;
+
+public class TestProgram extends TestCase {
+
+public String appPath = "D:\\research\\guierror\\subjects\\swt-subjects\\oast\\oast.jar";
+
+public String dir
+    = "D:\\research\\guierror\\eclipsews\\crazyguyonbike\\libs\\";
+
+//String swtdir = "D:\\develop-tools\\eclipse\\eclipse\\plugins\\org.eclipse.swt.win32.win32.x86_64.source_3.6.2.v3659c.jar";
+
+public String libJar =
+	"D:\\research\\guierror\\eclipsews\\oast\\commons-lang-2.6.jar"
+	+ Globals.pathSep
+	+ "D:\\research\\guierror\\eclipsews\\oast\\swt-3.6.1-win32-win32-x86_64.jar";
+
+
+
+String[] packages = new String[]{"checks", "com.maxmind", "lm", "oast"};
+
+String logFile = "./logs/anomalies.txt";
+
+public void testFindingErrors() throws IOException {
+	Log.logConfig("./log.txt");
+	String path = appPath + Globals.pathSep + libJar;
+    UIAnomalyDetector detector = new UIAnomalyDetector(path);
+    
+    detector.setThreadStartGuider(new CGTraverseSWTGuider());
+    detector.setUIAnomalyGuider(new CGTraverseSWTGuider());
+	
[…]

### 2012-05-25 GUIErrorDetector/paper/implementation.tex
fix trivial issues in format

@@
 These methods
-execute code (a)synchro\-nously on the UI thread.
+execute code (a)synchro\-nously in the UI thread.
 
@@
 \tinystep
-\subsubsection{Eclipse plugin}
+\subsubsection{Eclipse Plugin}
 
@@
 
-\item \textbf{UI-accessing nodes} and \textbf{Safe UI methods} are the same as SWT\@.
+\item \textbf{UI-accessing nodes} and \textbf{safe UI methods} are the same as SWT\@.
 
@@
 \item \textbf{Safe UI methods:}  
-\CodeIn{SwingUtilities.}\CodeIn{invokeLater} and \CodeIn{Swing\-Util\-ities.invokeAndWait}, which execute code on the UI thread.
+\CodeIn{SwingUtilities.}\CodeIn{invokeLater} and \CodeIn{Swing\-Util\-ities.invokeAndWait}, which execute code in the UI thread.
 
@@
 \item \textbf{Safe UI methods:}  \CodeIn{View.post}
-and \CodeIn{View.postDelay}, which execute code on the UI thread.
+and \CodeIn{View.postDelay}, which execute code in the UI thread.
 
@@
 
-\subsection{Android-specific Implementation Details}
+\subsection{Android-Specific Implementation Details}
 

### 2012-05-26 trunk/GUIErrorDetector/paper/evaluation.tex
make the wording more precisely
address issues besides orphans and widows

@@
 
-The subjects used in our experiment (Table~\ref{table:subjects})
+The subjects used in our experiment (Figure~\ref{table:subjects})
 include end-user applications, programming tools, and games.
@@
 
-\begin{table}[t]
+\begin{figure}[t]
 \begin{center}
@@
 the bottom table.}} 
-\end{table}
+\end{figure}
 
@@
 
-\begin{table*}[ht]
+\begin{figure*}[ht]
 \begin{center}
@@
 are shown at the far right.} }
-\end{table*}
+\end{figure*}
 
@@
 
-%Table~\ref{table:results} show the errors in
-%our subject programs, and Table~\ref{table:filters} show
-%the effect of applying each heuristic filter.
 \smallstep
@@
 
-As shown in Table~\ref{table:results}, our tool found
+As shown in Figure~\ref{table:results}, our tool found
 errors in each subject program. Using the 1-CFA
@@
 most of which are probably false positives (see the far right column of
-Table~\ref{table:results}).
+Figure~\ref{table:results}).
 The primary reason is that this simple approach
@@
 We next compare the 3 call graph construction algorithms (RTA, 0-CFA, and 1-CFA)
-used in our experiments. As shown in Table~\ref{table:results},  1-CFA found
+used in our experiments. As shown in Figure~\ref{table:results},  1-CFA found
 more errors than the other two algorithms. This
@@
 
-The results in Table~\ref{table:results} also show that using the
+The results in Figure~\ref{table:results} also show that using the
 call graph construction algorithm in Section~\ref{sec:cgcon}
@@
 We ran this variant on each subject program for 1 hour.  It explored 5.1$\times$$10^9$ paths
-on average, but did not output any of the 10 errors before it terminated.
+on average, but did not output any potential errors before it terminated.
 The number of non-cyclic paths in a graph is exponential in the graph size,
@@
 The numbers in the last column are the same as the subcolumn ``\#Warning"
-under column ``1-CFA'' in Table~\ref{table:results}.
+under column ``1-CFA'' in Figure~\ref{table:results}.
 } } \vspace{-2mm}
-\end{table}
+\end{figure}
 
@@
 
-Table~\ref{table:filters} measures the effectiveness of the
+Figure~\ref{table:filters} measures the effectiveness of the
 error filters of Section~\ref{sec:heuristic}.

### 2012-05-26 GUIErrorDetector/paper/introduction.tex
change the quotation

@@
                         \itemindent    \listparindent
-                        \leftmargin=14pt%  whatever you need
-                        \rightmargin=14pt%whatever you need
+                        \leftmargin=10pt%  whatever you need
+                        \rightmargin=0pt%whatever you need
                         \topsep=0pt%%%%%  whatever you need
@@
 %scattered into 2 pages
-\vspace{-2mm}
-\begin{quotation}
+%\vspace{-2mm}
+\begin{myquotation}
 All GUI objects, including visual components and data models, must be
  accessed exclusively from the \textit{event dispatching thread}.
-\end{quotation}
-\vspace{-2mm}
+\end{myquotation}
+%\vspace{-2mm}
 %\end{myquotation}

### 2012-05-26 GUIErrorDetector/paper/evaluation.tex
Avoid bad page breaks, mostly by squeezing title

@@
 
+% Hack for final camera-ready
+\vfill
+\pagebreak
+
 \subsubsection{Comparing Call Graph Construction Algorithms}
